### 2014-07-07 paper.tex
removd abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\usepackage{amsmath,amssymb}
\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

\newcommand{\bfc}{W}
\newcommand{\Qinf}{Q_{\infty}}
\newcommand{\st}[1]{_\text{#1}}
\newcommand{\rres}{r\st{res}}
\newcommand{\pos}[1]{(#1)^+}
\newcommand{\depth}{\operatorname{depth}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\convhull}{\operatorname{ConvexHull}}
\newcommand{\minksum}{\operatorname{MinkowskiSum}}

\title{\LARGE \bf
Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainty (Not Finished Work) }

\author{Michael Laskey*, Zoe McCarthy*, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space

\newtheorem{theorem}{Theorem}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\vspace{10pt}
\subsection{Grasp Quality Metrics}
 A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.\\

\subsection{Gaussian Process (GP) Primer}
 Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}, ~\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
The observations are assumed to be noisy measurements from the unknown target function $f$:
\begin{equation}
y_i = f(\bx_i) + \epsilon,
\end{equation}
where $\epsilon \sim \mN(0,\sigma^2)$ is Gaussian noise in the observations.
A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2006}:
\begin{equation}
  p(f_*|\bx_*,\mD) 
  \sim 
  \mN\big(k(\mX,\bx_*)^{\intercal}(K + \sigma_{\epsilon}^2I)^{-1}\by,
\end{equation}
\[
  k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big), \label{eq:GPposterior}
\]
where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$.

The choice of kernel is application-specific, since the function $k(\bx_i,\bx_j)$ is used as a measure of correlation between states $\bx_i$ and $\bx_j$.
A common choice is the squared exponential kernel:
\begin{equation}
k(\bx_i,\bx_j) 
=
\nu^2\exp(-\frac{1}{2}(\bx_i - \bx_j)^{\intercal}\Lambda^{-1}(\bx_i - \bx_j))
\end{equation}
where $\Lambda= \text{diag}(\lambda_1^2,\ldots,\lambda_d^2)$ are the characteristic length scales of each dimension of $\bx$ and $\nu^2$ describes the variability of $f$.
The vector of hyper-parameters $\boldsymbol{\theta} = \{\sigma,\nu,\lambda_1,\ldots,\lambda_d\}$ is chosen or optimized during the training process by minimizing the log likelihood $p(\by|\mX,\boldsymbol{\theta})$ \cite{rasmussen2006}.

%\section{Related Work}

\section{Problem Definition}
Given a grasp $G$ on an object, we can define it by the following tuple $G = \lbrace c_1,...,c_m,n_1,...,n_m,z,\tau\rbrace$. We have a set $I$ of $m$ contacts on the object where $i \in I$ contact is located at $c_i$ with surface normal $n_i$.
The object has a center of mass $z$ and friction coefficient $\mu$.
We demonstrate that one can efficiently compute a closed form distribution for $c_i$,$n_i$ and $z$.
We note though that our metric assumes a known $\mu$ or friction coefficient. \\

 For the following derivations we use the following notation.
 $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$. The set of all elements in the range $[a,b]$ will be denoted by T. 
% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
We assume a bounded rectangular workspace $\mathcal{R}$.
The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig.
 \ref{fig:line_of_action}.
 % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
 We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
% TODO: Michael, did I fill this in correctly? It was left blank initially.

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide1.jpg}
\caption{Parameterized Line of Action along a Object}
\vspace*{-10pt}
\label{fig:line_of_action}
\end{figure}

\section{Distribution of Grasp Parameters}

\subsection{Distribution on Contact Points} The probability along the line $\gamma(g)$ is given by the following:

\begin{equation}
P(f(\gamma(g))|\theta(\gamma(g))) 
=
\mN(\mu_T,\Sigma_T)
\end{equation}

% TODO: What is T?

This gives the distributions along the entire line of action, however we want to compute the marginalization of this where at each point we simply are asking the probability $p(f(\gamma(g=k))=0)$.
We can achieve this by marginalizing out the rest of the points along the line.
With a Gaussian it has the closed form solution as follows:

\begin{equation}
P(c_{i}) =  P(f(\gamma(t))=0|\theta(\gamma(t)))
\end{equation}

\subsection{Distribution on Surface Normals} 
The distribution of surface normals $P(n_i = k)$ can be calculate as follows.
First we assume that some function exists $h(x) = \lbrace \mu_{\nabla}(x), \Sigma_{\nabla}(x) \rbrace$, hence given a point $x$ it returns the parameters for a Gaussian distribution around the gradient.
this function can be computed via learning the gradient \cite{gradient} or analytical differentiation of $f(x)$.
We note that both methods yield a Gaussian distribution.
We now demonstrate how to marginalize out the contact distribution and compute $P(n_i = k)$\\

From our distribution on contact points and Bayes rule we can compute the following:

\begin{equation}
p(c_i = \gamma(g), n_i = k) = p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t))
\end{equation}

Now we can marginalize out the distribution on contacts:

\begin{equation}
P(n_i = k) = \int_T  p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t)) dg
\end{equation}

We then discretize the curve and approximate the integral by a sum:

\begin{equation}
P(n_i = k) = \sum_T  p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t)) dg
\end{equation}

Thus, $P(n_i = k)$ is a multi-modal distributions composed of Gaussians sum together.

\subsection{Distribution on Center of Mass}

We define the quantity $\mathcal{D}(x) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ and note that it is equal to the probability that x is interior to the surface under the current observations.
We assume that the object has uniform mass density and then $\mathcal{D}(x)$ is the expected mass density at x.
Then we can find the expected center of mass as:

\begin{equation}
  \bar{z} 
  =
  \frac
    {\int_{\mathcal{R}}x \mathcal{D}(x) dx}
    {\int_{\mathcal{R}}  \mathcal{D}(x) dx}
\end{equation}

which can be approximated by sampling $\mathcal{R}$ uniformly in a voxel grid and approximating the spatial integral by a sum.

\section{Probabilistic Bound on Grasp Metric}
Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we prove that an extension is possible to give a probabilistic bound on the change in grasp quality.
We rewrite the results here:

\subsection{Prior Work}

We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ for means.  
We re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ refers to the exact $L^1$ grasp quality.
It is denoted by the following

\begin{align}
  Q(g) &= \mbox{max}(0,q(g)) = -d(0,\mbox{Conv}(\{0\} \cup S(g))\\
-d(0,S) &= min_{||z|| = 1} h_{S(z)}\\
h_{S(z)} &= \mbox{sup}_{s\in S}\langle s,z\rangle\\
\end{align}

We denote the Ferrari-Canny version, which approximates the friction cone by a linearized set of wrenches\cite{ferrari1992}, as $Q^-_l(g)$.
The next theorem shows that the linearized wrench set used in Ferrari-Canny calculates a lower bound on $Q(g)$.\\

\begin{theorem}
  \cite{pokorny2013classical}
For any grasp g, we have $0 \leq Q_l^-(g) \leq Q(g)$.
Furthermore, $||Q(g) - Q^-_l(g)|| \rightarrow 0$ as $l \rightarrow \infty$ when $Q_l^-(g)$ is computed using a uniform approximation of the friction cones with $l$ edges. \\
\end{theorem}

\begin{theorem}
\label{lemma35}
  \cite{pokorny2013classical}
For $w \in \mathbb{R}^3$, we have, for $n \in \mathbb{S}^2$ and for friction coefficient $\mu > 0$,

\begin{align}
\mbox{sup}_{x \in C(n)} \langle x,w \rangle = \langle n,w \rangle + \tau||n \times w||
\end{align}

Hence, for $u = (a,b) \in \mathbb{R}^3 \times \mathbb{R}^3 = \mathbb{R}^6$, we have

\[
h_{W_i(g)}(a,b) =
 \langle n_i,a+b\times(c_i-z)\rangle +
\]
\begin{align}
 +\tau ||n_i \times (a+b\times(c_i-z))||
\end{align}

\end{theorem}

\begin{theorem}
  \cite{pokorny2013classical}
We have \\

\begin{align}
q(g) 
=
\min_{u\in \mathbb{R}^6, ||u|| =1} h_{S(g)}(u) 
=
\end{align}
\[
\min_{u\in \mathbb{R}^6, ||u|| =1} \max_{i=1,...,m} h_{W_i(g)}(u),
\]

where $h_{S(g)}$ is convex on $\mathbb{R}^6$.
$q$ is invariant under fixed translation of the grasp center and contact positions.
Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$.
Then $q$ is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1, \dots, c_m,n_1, \dots,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where we use distance measure

\[
  d(g,g') = \sum_i ||(c_i-z)-(c_i'-z')|| + \sum_i ||n_i - n_i'||.
\]

We hence have

\[
|q(g) - q(g')| \leq Ld(g,g'),\  \forall g,g' \in X.
\]

Since $Q(g) = \max(0,q(g))$, $Q$ is also Lipschitz continuous with the same constant $L$ on $X$. 
\end{theorem}

Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|\langle n_i,a+b\times (c_i-z)\rangle - \langle n_i',a+b\times(c_i'-z')\rangle|+\mu|||n_i \times (a+b \times (c_i -z))|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}.
By using the following facts $||a|| \leq 1$, $||b|| \leq 1$, $||v \times w || \leq ||w||||v||$, $|\langle v,w\rangle | \leq ||v||||w||$, we obtain:

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||(c_i - z)-(c_i'-z')|| \\
					&+ \mu(||n_i - n_i'||(1+||c_i - z||)\\
					&+||(c_i - z)-(c_i'-z')||)
\end{align*}

\subsection{Our Extension}

We now define the concept of a probabilistic bound by functions $\sigma(p)_{n_i}$ and $\sigma(p)_{r_i}$, given a probability $p$ they denote the change in grasp parameter from the mean in the distribution.
$\sigma(p)_{n_i}$ references the distribution defined by $p(n_i = k)$.
$r = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma(p)_{r_i}$ references the distribution $p(c_i = k)$.
We now write the bound as follows:

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(p)||(1+\bar{r}|) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

For convenience we rewrite the bound on a given set of graps parameters as :

 \begin{align*}
b_i(p) &= ||\sigma_{n_i}(p)||(1+||\bar{r}||) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

To provide an upper bound overall contact parameters we introduce the following:

\begin{align}
b(p)  = \max_{i} b_i(p)
\end{align}

To prove if  this bound is preserved on

 \begin{align}
 q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
 \end{align}

we turn to the general case.
$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(p)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(p)$ and $\lambda(x)$ is bounded.
Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
We can ensure that is true.

\section{References}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}

### 2014-07-07 paper.tex

@@
 For more detail, refer there.
-$Q(g)$ refers to the exact $L^1$ grasp quality.
+$Q(g)$ is the exact $L^1$ grasp quality.
 It is denoted by the following
@@
 \end{theorem}
+
+The next theorems are used to show that $Q$ is Lipschitz continuous.
 
@@
 					&+ ||(c_i - z)-(c_i'-z')|| \\
-					&+ \mu(||n_i - n_i'||(1+||c_i - z||)\\
+					&+ \tau(||n_i - n_i'||(1+||c_i - z||)\\
 					&+||(c_i - z)-(c_i'-z')||)
@@
 
-We now define the concept of a probabilistic bound by functions $\sigma(p)_{n_i}$ and $\sigma(p)_{r_i}$, given a probability $p$ they denote the change in grasp parameter from the mean in the distribution.
-$\sigma(p)_{n_i}$ references the distribution defined by $p(n_i = k)$.
-$r = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma(p)_{r_i}$ references the distribution $p(c_i = k)$.
-We now write the bound as follows:
+We now define the concept of a probabilistic bound by functions $\sigma_{n_i}(\zeta)$ and $\sigma_{r_i}(\zeta)$, given a probability $\zeta$ they denote the maximum change in grasp parameter from the mean in the distribution for that probability.
+Formally, this is defined as:
+
+\[
+  \sigma_{n_i}(\zeta)
+  =
+  \min_{\mathbb{R}_+}d
+\]
+
+\[
+  s.t. \ \ \left[ \int_{\mathbb{B}(\bar{n}, d)} p(n_i = k) dk \right] \geq \zeta
+\]
+
+and
+
+\[
+  \sigma_{r_i}(\zeta)
+  =
+  \min_{\mathbb{R}_+} d
+\]
+
+\[
+s.t. \ \ \left[ \int_{\mathbb{B}(\bar{r}, d)} p(r_i = k) dk \right]  \geq \zeta
+\]
+
+$\sigma_{n_i}(\zeta)$ references the distribution defined by $p(n_i = k)$.
+$r_i = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma_{r_i}(\zeta)$ references the distribution $p(c_i = k)$.
+We now write the above bound as follows:
 
  \begin{align*}
-|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(p)||(1+\bar{r}|) + ||\sigma_{r_i}(p)|| \\
-                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
+|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||) + ||\sigma_{r_i}(\zeta)|| \\
+                                      &+ \tau(||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||)+||\sigma_{r_i}(\zeta)||)
 \end{align*}
@@
  \begin{align*}
-b_i(p) &= ||\sigma_{n_i}(p)||(1+||\bar{r}||) + ||\sigma_{r_i}(p)|| \\
-                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
+b_i(\zeta) &= ||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||) + ||\sigma_{r_i}(\zeta)|| \\
+                                      &+ \tau(||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||)+||\sigma_{r_i}(\zeta)||)
 \end{align*}
@@
 \begin{align}
-b(p)  = \max_{i} b_i(p)
+b(\zeta)  = \max_{i} b_i(\zeta)
 \end{align}
@@
 we turn to the general case.
-$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(p)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(p)$ and $\lambda(x)$ is bounded.
+$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
 Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.

### 2014-07-08 paper.tex
added uni-modal distribution on contact points

@@
 \title{\LARGE \bf
-Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainty (Not Finished Work) }
+Grasp Metric for Shape Uncertainity with Gaussian Proccess Implicit Surface Representation (Not Finished Work) }
 
@@
 \vspace{10pt}
-\subsection{Grasp Quality Metrics}
  A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
-We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
-We also consider the general case where there is friction at the contact points.\\
+However, only recently have people started looking into a metric's robustness to uncertainty.
+Prior work by Zheng et al \cite{zheng2005}, looked at how to efficiently include uncertainty in friction coefficient and movement of gripper arm.
+However, they assumed a known surface of the object.
+In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}.
+\\
 
-\subsection{Gaussian Process (GP) Primer}
+ We use Gaussian Processes \cite{rasmussen2006} to convert the discrete mesh into an implicit surface with a measurement of uncertainty about the shape.
+Our contribution extends wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces, to incorporate shape uncertainty.
+We use recent results on a Lipschitz  constant for the Ferrari-Canny metric \cite{pokorny2013classical}, and prove a tight probabilistic bound on the change in grasp quality under shape uncertainty.
+We also provide an efficient way to calculate the distributions on the grasp parameters and include a way to update them quickly with new observations.
+We work in the general case where friction is at the contact points.
+
+\section{Gaussian Process Primer}
  Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
@@
 
-\subsection{Distribution on Contact Points} The probability along the line $\gamma(g)$ is given by the following:
+\subsection{Distribution on Contact Points} The probability along the line $\gamma(t)$ is given by the following:
 
 \begin{equation}
-P(f(\gamma(g))|\theta(\gamma(g))) 
+P(f(\gamma(a:b))|\theta(\gamma(a:b))) 
 =
@@
 
-% TODO: What is T?
+This gives the distributions along the entire line of action, however we want to compute the joint probability   $p(c_i=k) = p(f(\gamma(t))=0, f(\gamma(t-1:0))\neq 0)$.
+Hence we want to know at a point what the distribution  is that it is at the surface and no points before it on line are on the surface as well, this avoids the problem of the line of action intersecting multiple points on the surface.
+We now derive a way to compute an upper-bound on this distribution
 
-This gives the distributions along the entire line of action, however we want to compute the marginalization of this where at each point we simply are asking the probability $p(f(\gamma(g=k))=0)$.
-We can achieve this by marginalizing out the rest of the points along the line.
-With a Gaussian it has the closed form solution as follows:
+\begin{align*}
+p(c_i = k) &= p(f(\gamma(t)) = 0)\\
+               &*p(f(\gamma(t-1:0)) \neq 0 | f(\gamma(t)) = 0)
+\end{align*}
 
-\begin{equation}
-P(c_{i}) =  P(f(\gamma(t))=0|\theta(\gamma(t)))
-\end{equation}
+Using the first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second one can be rewritten by conditioning the distribution \cite{petersen2008matrix}.
+
+\begin{align*}
+p(f(\gamma(t-1:0)) \neq 0 | f(\gamma(t)) = 0) = p_c(f(\gamma(t-1:0)))
+\end{align*}
+
+\begin{align*}
+p_c(f(\gamma(t-1:0))) &= p(f(\gamma(t-1)) \neq 0) \\
+                                  &*p(f(\gamma(t-1:0)) \neq 0 | f(\gamma(t-1) \neq 0))
+\end{align*}
+
+It is now clear that the following can be said
+
+\begin{align*}
+p_c(f(\gamma(t-1:0))) &\leq p(f(\gamma(t-1)) \neq 0)\\
+                                  &* p(f(\gamma(t-1:0)) \neq 0))
+\end{align*}
+
+We can furthermore conclude
+
+\begin{align*}
+p_c(f(\gamma(t-1:0))) &\leq p(f(\gamma(t-1)) \neq 0) \\
+				   &*..*p(f(\gamma(0)) \neq 0))
+\end{align*}
+
+Or in other words the independence assumption provides an upper bound on the distribution, which would otherwise be intractable to calculate.
+We can know write the conservative approximation to the distribution as follows:
+
+\begin{align*}
+p(c_i = \gamma(t)) &\leq p(f(\gamma(t-1)) \neq 0) \\
+				   &*..*p(f(\gamma(0)) \neq 0))
+				   &*p(f\gamma(t) = 0)
+\end{align*}
 
@@
 \subsection{Our Extension}
-
 We now define the concept of a probabilistic bound by functions $\sigma_{n_i}(\zeta)$ and $\sigma_{r_i}(\zeta)$, given a probability $\zeta$ they denote the maximum change in grasp parameter from the mean in the distribution for that probability.
@@
 
-\section{References}
-
-\bibliographystyle{plainnat}
+\bibliographystyle{ieeetr}
 \bibliography{references}

### 2014-07-12 paper.tex
Cleaned up notation, fixed contact point distribution, added a way to compute probability on not achieving force closure

@@
 In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}.
-\\
 
@@
 \section{Gaussian Process Primer}
+\textbf{TODO:FIX THIS SECTION AND MAKE NOTATION CONSISTENT}
  Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
@@
 \section{Problem Definition}
-Given a grasp $G$ on an object, we can define it by the following tuple $G = \lbrace c_1,...,c_m,n_1,...,n_m,z,\tau\rbrace$.
-We have a set $I$ of $m$ contacts on the object where $i \in I$ contact is located at $c_i$ with surface normal $n_i$.
-The object has a center of mass $z$ and friction coefficient $\mu$.
-We demonstrate that one can efficiently compute a closed form distribution for $c_i$,$n_i$ and $z$.
-We note though that our metric assumes a known $\mu$ or friction coefficient. \\
 
- For the following derivations we use the following notation.
- $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
-We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$. The set of all elements in the range $[a,b]$ will be denoted by T. 
-% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
+The objective of our algorithm is to provide an expected quality of grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and the probability $\zeta$ of not obtaining force closure.
+
+Given a grasp $g$ on an object, we can define it by the following tuple $g = \lbrace \textbf{c}_0,...,\textbf{c}_m,\textbf{n}_0,...,\textbf{n}_m,\textbf{z},\tau\rbrace$.
+We have a set $I$ of $m$  point contacts and surface normal on the object where $i \in I$s is located at $c_i$ with surface normal $n_i$.
+The object has a center of mass $z$ and friction coefficient $\tau$.
+
+Since we have uncertainty in the shape we only have a distribution on the grasp parameters, hence $p(g) = \lbrace p(\textbf{c}_0),...,p(\textbf{c}_m),p(\textbf{n}_0),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau \rbrace$.
+We note that $\tau$ is considered known and $\bar{z}$ is only the expected center of mass.
+In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute this distribution.
+
+With distribution on $p(g)$ we then use recent results on a Lipschitz constant for Ferrari-Canny Metric \cite{pokorny2013classical} to provide $\zeta$ or the probability the grasp will lose force closure and the expected quality of the grasp $Q_l^-(\bar{g})$, where $\bar(g) = \lbrace \bar{\textbf{c}}_0,...,\bar{\textbf{c}}_m),\bar{\textbf{n}}_0,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
+Details of this computation can be found in section \ref{sec:bound}.
+
+\section{Distribution of Grasp Parameters}
+\label{sec:distgrasp}
+
+ For the following derivations we introduce the following,
+ $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, where $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS model \cite{rasmussen2006} .
+
+ To calculate $p(g)$, we assume a gripper contacts approaches along a line of action, or a 1-dimensional curve in the work space, defined by $\gamma(t)$.
+See Fig \ref{fig:line_of_action}, for a detailed illustration.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = \lbrace \gamma_0(t),...,\gamma_m(t) \rbrace$, these approach trajectories are then used to compute a distribution on grasp parameters.
+
 We assume a bounded rectangular workspace $\mathcal{R}$.
@@
  \ref{fig:line_of_action}.
- % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
- We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
-% TODO: Michael, did I fill this in correctly? It was left blank initially.
+
+ We also define the function level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
 
@@
 \end{figure}
-
-\section{Distribution of Grasp Parameters}
-
-\subsection{Distribution on Contact Points} The probability along the line $\gamma(t)$ is given by the following:
+\textbf{TODO:MORE DESCRIPTIVE GRAPHIC}
+\subsection{Distribution on Contact Points} The probability distribution along the line $\gamma(t)$ is given by the following:
 
 \begin{equation}
-P(f(\gamma(a:b))|\theta(\gamma(a:b))) 
+p\big(f(\gamma(t))|\theta(\gamma(t)): \forall t \in [a,b] \big) 
 =
-\mN(\mu_T,\Sigma_T)
+\mN(\mu_{a:b},\Sigma_{a:b})
 \end{equation}
 
-This gives the distributions along the entire line of action, however we want to compute the joint probability   $p(c_i=k) = p(f(\gamma(t))=0, f(\gamma(t-1:0))\neq 0)$.
-Hence we want to know at a point what the distribution  is that it is at the surface and no points before it on line are on the surface as well, this avoids the problem of the line of action intersecting multiple points on the surface.
+This gives the distributions along the entire line of action in the workspace, however we want to compute the joint distribution   $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$.
+Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface.
+points before it on line are on the surface as well, this avoids the problem of the distribution producing multiple modes for each intersection with the surface.
 We now derive a way to compute an upper-bound on this distribution
@@
 \begin{align*}
-p(c_i = k) &= p(f(\gamma(t)) = 0)\\
-               &*p(f(\gamma(t-1:0)) \neq 0 | f(\gamma(t)) = 0)
+p\big(\textbf{c}_i = \gamma(t)\big) &\propto p\big(f(\gamma(t)) = 0\big)\\
+               &*P\big(f(\gamma(\tau)) > 0 | f(\gamma(t)) = 0: \forall \tau \in [0,t)\big)
 \end{align*}
@@
 \begin{align*}
-p(f(\gamma(t-1:0)) \neq 0 | f(\gamma(t)) = 0) = p_c(f(\gamma(t-1:0)))
-\end{align*}
-
-\begin{align*}
-p_c(f(\gamma(t-1:0))) &= p(f(\gamma(t-1)) \neq 0) \\
-                                  &*p(f(\gamma(t-1:0)) \neq 0 | f(\gamma(t-1) \neq 0))
+p_c\big(f(\gamma(\tau)): \forall \tau \in [0,t)\big) = p\big(f(\gamma(\tau))  | f(\gamma(t)) = 0\big)  
 \end{align*}
@@
 \begin{align*}
-p_c(f(\gamma(t-1:0))) &\leq p(f(\gamma(t-1)) \neq 0)\\
-                                  &* p(f(\gamma(t-1:0)) \neq 0))
+p\big(\textbf{c}_i = \gamma(t)\big) &= \frac{1}{\eta} p(f\gamma(t) = 0) \\
+				   &*P_c\big(f(\gamma(\tau)) < 0): \forall \tau \in [0,t)\big)			 
 \end{align*}
 
-We can furthermore conclude
-
-\begin{align*}
-p_c(f(\gamma(t-1:0))) &\leq p(f(\gamma(t-1)) \neq 0) \\
-				   &*..*p(f(\gamma(0)) \neq 0))
-\end{align*}
-
-Or in other words the independence assumption provides an upper bound on the distribution, which would otherwise be intractable to calculate.
-We can know write the conservative approximation to the distribution as follows:
-
-\begin{align*}
-p(c_i = \gamma(t)) &\leq p(f(\gamma(t-1)) \neq 0) \\
-				   &*..*p(f(\gamma(0)) \neq 0))
-				   &*p(f\gamma(t) = 0)
-\end{align*}
+The second product term can be efficiently evaluated by looking up the cumulative distribution of a multivariate Gaussian, which is common in most software packages \cite{matlab}.
 
 \subsection{Distribution on Surface Normals} 
-The distribution of surface normals $P(n_i = k)$ can be calculate as follows.
-First we assume that some function exists $h(x) = \lbrace \mu_{\nabla}(x), \Sigma_{\nabla}(x) \rbrace$, hence given a point $x$ it returns the parameters for a Gaussian distribution around the gradient.
-this function can be computed via learning the gradient \cite{gradient} or analytical differentiation of $f(x)$.
+The distribution of surface normals $p(\textbf{n}_i = \textbf{k})$ can be calculate as follows.
+First we assume that some function exists $h(x) = \lbrace \mu_{\nabla}(x), \Sigma_{\nabla}(x) \rbrace$, hence given a point $\bf{x}$ it returns the parameters for a Gaussian distribution around the gradient.
+this function can be computed via learning the gradient \cite{solak2003derivative} or analytical differentiation of $f(x)$.
 We note that both methods yield a Gaussian distribution.
-We now demonstrate how to marginalize out the contact distribution and compute $P(n_i = k)$\\
+We now demonstrate how to marginalize out the contact distribution and compute $p(\textbf{n}_i = \textbf{k})$\\
 
@@
 \begin{equation}
-p(c_i = \gamma(g), n_i = k) = p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t))
+p(\textbf{c}_i = \gamma(t), \textbf{n}_i = \textbf{k}) = p\big(\textbf{n}_i = \textbf{k} | h(\gamma(t))\big)*p\big(\textbf{c}_i = \gamma(t)\big)
 \end{equation}
@@
 \begin{equation}
-P(n_i = k) = \int_T  p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t)) dg
+p(\textbf{n}_i = \textbf{k}) = \int_a^b  p \big(\textbf{n}_i = \textbf{k} | \textbf{c}_i = \gamma(t) \big)*p(\textbf{c}_i = \gamma(t)) dt
 \end{equation}
 
-We then discretize the curve and approximate the integral by a sum:
+\begin{equation}
+p\big(\textbf{n}_i = \textbf{k}\big) = \int_a^b  p \big(\textbf{n}_i = \textbf{k} | h(\gamma(t))\big)*p\big(\textbf{c}_i = \gamma(t)\big) dt
+\end{equation}
+
+We approximate this by uniformly sampling the integral along the function $\gamma(t)$ and achieve the following:
 
 \begin{equation}
-P(n_i = k) = \sum_T  p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t)) dg
+p\big( \textbf{n}_i = \textbf{k} \big) = \sum_T  p \big( \textbf{n}_i = k | h(\gamma(t)) \big) *p\big(c_i = \gamma(t)\big) dt
 \end{equation}
 
-Thus, $P(n_i = k)$ is a multi-modal distributions composed of Gaussians sum together.
+Thus, $p(\textbf{n}_i = \textbf{k})$ is approximated by a Gaussian Mixture Model.
 
-\subsection{Distribution on Center of Mass}
+\subsection{Expected Center of Mass}
 
@@
 \section{Probabilistic Bound on Grasp Metric}
+\label{sec:bound}
 Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we prove that an extension is possible to give a probabilistic bound on the change in grasp quality.
@@
 
+\textbf{TODO:WORK IN PRIOR WORK BETTER}
 We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ for means.  
@@
 \subsection{Our Extension}
-We now define the concept of a probabilistic bound by functions $\sigma_{n_i}(\zeta)$ and $\sigma_{r_i}(\zeta)$, given a probability $\zeta$ they denote the maximum change in grasp parameter from the mean in the distribution for that probability.
+We now define the concept of a probabilistic bound by functions $\sigma_i(\zeta) = \lbrace\Delta \textbf{r}_{i,\zeta}, \Delta \textbf{n}_{i,\zeta}\rbrace$.
+Given a probability $\zeta$, $\sigma_i$ returns the tuple denoting the maximum change in grasp parameter from the mean in the distribution for that probability.
+$\Delta \textbf{n}_i$ is the change in surface normal and $\Delta \textbf{r}_i$ is the change in moment arm defined as $\textbf{r}_i = \textbf{c}_i - \bar{\textbf{z}}$.
 Formally, this is defined as:
@@
 \[
-  \sigma_{n_i}(\zeta)
+  \sigma_i(\zeta)
   =
-  \min_{\mathbb{R}_+}d
+  \min_{\mathbb{R}_+} \textbf{d}
 \]
@@
 \[
-  s.t. \ \ \left[ \int_{\mathbb{B}(\bar{n}, d)} p(n_i = k) dk \right] \geq \zeta
+  s.t. \ \ \left[ \int_{\mathbb{B}([\bar{t},\bar{\textbf{n}}], d)} p(\textbf{n}_i = \textbf{k},\textbf{c}_i=\gamma(t)) d[t,\textbf{k}] \right] \geq \zeta
 \]
 
-and
-
-\[
-  \sigma_{r_i}(\zeta)
-  =
-  \min_{\mathbb{R}_+} d
-\]
-
-\[
-s.t. \ \ \left[ \int_{\mathbb{B}(\bar{r}, d)} p(r_i = k) dk \right]  \geq \zeta
-\]
-
-$\sigma_{n_i}(\zeta)$ references the distribution defined by $p(n_i = k)$.
-$r_i = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma_{r_i}(\zeta)$ references the distribution $p(c_i = k)$.
-We now write the above bound as follows:
+We now write the above bound as follows for a given $\sigma_i(\zeta)$:
 
  \begin{align*}
-|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||) + ||\sigma_{r_i}(\zeta)|| \\
-                                      &+ \tau(||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||)+||\sigma_{r_i}(\zeta)||)
+|l_{i,a,b}(g) - l_{i,a,b}(g')| & =||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
+                                      &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
 \end{align*}
 
-For convenience we rewrite the bound on a given set of graps parameters as :
+For convenience we rewrite the bound on a given set of grasp parameters as :
 
  \begin{align*}
-b_i(\zeta) &= ||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||) + ||\sigma_{r_i}(\zeta)|| \\
-                                      &+ \tau(||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||)+||\sigma_{r_i}(\zeta)||)
+b_i(\zeta) &= ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
+                                      &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
 \end{align*}
@@
 
+Lastly if one wants to find the probability they would lose force closure, they can simply solve the following
+
+\[
+  \zeta
+  =
+  \argmin_{\zeta} b(\zeta)
+\]
+
+\[
+  s.t. \ \  b(\zeta) \geq q(\bar(g))
+\]
+
+This would be pretty computationally expensive, so still a work in progress. \textbf{TODO:MAKE THIS EFFICIENT}
+
 \bibliographystyle{ieeetr}

### 2014-07-14 paper.tex
added stuff

@@
  A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
+In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}.
+As shown in Fig.
+\ref{fig:noisy data}, the noise in object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.
 However, only recently have people started looking into a metric's robustness to uncertainty.
 Prior work by Zheng et al \cite{zheng2005}, looked at how to efficiently include uncertainty in friction coefficient and movement of gripper arm.
+.
 However, they assumed a known surface of the object.
-In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}.
 
@@
 We work in the general case where friction is at the contact points.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide2.jpg}
+\caption{An example of the noise from a Kinect Like Sensor}
+\vspace*{-10pt}
+\label{fig:noisy data}
+\end{figure}
 
@@
 
- We also define the function level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
+ We also define the  level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
 
@@
 \includegraphics[scale = 0.3]{figures/Slide1.jpg}
-\caption{Parameterized Line of Action along a Object}
+\caption{Parametrized Line of Action along a Object}
 \vspace*{-10pt}
@@
 This gives the distributions along the entire line of action in the workspace, however we want to compute the joint distribution   $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$.
-Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface.
-points before it on line are on the surface as well, this avoids the problem of the distribution producing multiple modes for each intersection with the surface.
-We now derive a way to compute an upper-bound on this distribution
+Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface, this avoids the problem of the distribution producing multiple modes for each intersection with the surface.
+We now derive a  this distribution
 
@@
  \begin{align*}
-|l_{i,a,b}(g) - l_{i,a,b}(g')| & =||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
+|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
                                       &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)

### 2014-07-17 paper.tex
added slide 2
some changes to intro, fixed derivative ref

@@
  A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
-In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}.
+Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}.
 As shown in Fig.
-\ref{fig:noisy data}, the noise in object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.
+\ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.
 However, only recently have people started looking into a metric's robustness to uncertainty.
 Prior work by Zheng et al \cite{zheng2005}, looked at how to efficiently include uncertainty in friction coefficient and movement of gripper arm.
-.
 However, they assumed a known surface of the object.
 
- We use Gaussian Processes \cite{rasmussen2006} to convert the discrete mesh into an implicit surface with a measurement of uncertainty about the shape.
-Our contribution extends wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces, to incorporate shape uncertainty.
-We use recent results on a Lipschitz  constant for the Ferrari-Canny metric \cite{pokorny2013classical}, and prove a tight probabilistic bound on the change in grasp quality under shape uncertainty.
-We also provide an efficient way to calculate the distributions on the grasp parameters and include a way to update them quickly with new observations.
-We work in the general case where friction is at the contact points.
+We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
+We assume friction is at the contact points. 
+The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
+%\section{Goals and Current Progress}
+We are working to extend this metric to incorporate shape uncertainty.
+For our grasping model, we make a simplifying assumption that each gripper approaches the object along a fixed line of action and thus the contact points lie on this line.
+We would like to analyze the induced distributions over grasp parameters and the Ferrari-Canny metric.
+Specifically, we would like to answer the following question:
+What is the probability of achieving force closure under the given grasp approach directions and implicit surface distribution?
+%We use recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical}, and prove a tight probabilistic bound on the change in grasp quality under shape uncertainty.
+%We also provide an efficient way to calculate the distributions on the grasp parameters and include a way to update them quickly with new observations.
 
@@
 \includegraphics[scale = 0.3]{figures/Slide2.jpg}
-\caption{An example of the noise from a Kinect Like Sensor}
+\caption{An example of the noise from a Kinect-like sensor}
 \vspace*{-10pt}
@@
 \section{Gaussian Process Primer}
-\textbf{TODO:FIX THIS SECTION AND MAKE NOTATION CONSISTENT}
+%\textbf{TODO:FIX THIS SECTION AND MAKE NOTATION CONSISTENT}
  Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
@@
   \sim 
-  \mN\big(k(\mX,\bx_*)^{\intercal}(K + \sigma_{\epsilon}^2I)^{-1}\by,
+  \mN\big(k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by,
 \end{equation}
@@
 
-Given a grasp $g$ on an object, we can define it by the following tuple $g = \lbrace \textbf{c}_0,...,\textbf{c}_m,\textbf{n}_0,...,\textbf{n}_m,\textbf{z},\tau\rbrace$.
+Given a grasp $g$ on an object, we can define it by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\textbf{z},\tau\rbrace$.
 We have a set $I$ of $m$  point contacts and surface normal on the object where $i \in I$s is located at $c_i$ with surface normal $n_i$.
@@
 
-Since we have uncertainty in the shape we only have a distribution on the grasp parameters, hence $p(g) = \lbrace p(\textbf{c}_0),...,p(\textbf{c}_m),p(\textbf{n}_0),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau \rbrace$.
+Since we have uncertainty in the shape we only have a distribution on the grasp parameters, hence $p(g) = \lbrace p(\textbf{c}_1),...,p(\textbf{c}_m),p(\textbf{n}_1),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau \rbrace$.
 We note that $\tau$ is considered known and $\bar{z}$ is only the expected center of mass.
@@
 
-With distribution on $p(g)$ we then use recent results on a Lipschitz constant for Ferrari-Canny Metric \cite{pokorny2013classical} to provide $\zeta$ or the probability the grasp will lose force closure and the expected quality of the grasp $Q_l^-(\bar{g})$, where $\bar(g) = \lbrace \bar{\textbf{c}}_0,...,\bar{\textbf{c}}_m),\bar{\textbf{n}}_0,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
+With distribution on $p(g)$ we then use recent results on a Lipschitz constant for Ferrari-Canny Metric \cite{pokorny2013classical} to provide $\zeta$ or the probability the grasp will lose force closure and the expected quality of the grasp $Q_l^-(\bar{g})$, where $\bar{g} = \lbrace \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
 Details of this computation can be found in section \ref{sec:bound}.
@@
 See Fig \ref{fig:line_of_action}, for a detailed illustration.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = \lbrace \gamma_0(t),...,\gamma_m(t) \rbrace$, these approach trajectories are then used to compute a distribution on grasp parameters.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = \lbrace \gamma_1(t),...,\gamma_m(t) \rbrace$, these approach trajectories are then used to compute a distribution on grasp parameters.
 
@@
 \includegraphics[scale = 0.3]{figures/Slide1.jpg}
-\caption{Parametrized Line of Action along a Object}
+\caption{Parametrized Line of Action along an object}
 \vspace*{-10pt}
@@
 p\big(\textbf{c}_i = \gamma(t)\big) &= \frac{1}{\eta} p(f\gamma(t) = 0) \\
-				   &*P_c\big(f(\gamma(\tau)) < 0): \forall \tau \in [0,t)\big)			 
+				   &*P_c\big(f(\gamma(\tau)) > 0): \forall \tau \in [0,t)\big)			 
 \end{align*}
@@
 \textbf{TODO:WORK IN PRIOR WORK BETTER}
-We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ for means.  
+We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ to refer to means.  
 We re-state some of their central theorems for our use here.

### 2014-07-17 paper.tex
Edited intro a lot

@@
 What is the probability of achieving force closure under the given grasp approach directions and implicit surface distribution?
-%We use recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical}, and prove a tight probabilistic bound on the change in grasp quality under shape uncertainty.
-%We also provide an efficient way to calculate the distributions on the grasp parameters and include a way to update them quickly with new observations.
+So far, we have explicit formulas for the distributions of the contact points along the line of action and surface normal vectors and the expected center of mass of the object to be grasped.
+We are thoroughly investigating utilizing recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical} in order to prove probabalistic bounds on the change in grasp quality under shape uncertainty.
+We are also investigating efficient ways to calculate the distributions on the grasp parameters and ways to update them quickly with new observations.
 

### 2014-07-17 paper.tex
went through whole paper, many edits and style changes, basically erased prob bound section to pave way for new foundations and explain why its not there

@@
 What is the probability of achieving force closure under the given grasp approach directions and implicit surface distribution?
+We are also interested in the grasp quality of the expected grasp.
 So far, we have explicit formulas for the distributions of the contact points along the line of action and surface normal vectors and the expected center of mass of the object to be grasped.
@@
 We are also investigating efficient ways to calculate the distributions on the grasp parameters and ways to update them quickly with new observations.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide4.jpg}
+\caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
+Right: Induced distribution on the contact point as a function of x-axis position along the approach line.}
+\vspace*{-10pt}
+\label{fig:IntroTopPic}
+\end{figure}
 
@@
 
+We represent surfaces as a Gaussian Process trained to predict the Truncated Signed Distance Field of a surface by noisy samples from that TSDF, as indicated in Fig.
+ \ref{fig:GPIS_TSDF}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide3.jpg}
+\caption{Left: A surface represented as a Truncated Signed Distance Field (TSDF).
+Right: A GPIS reconstruction from noisy samples of the left surface's TSDF.}
+\vspace*{-10pt}
+\label{fig:GPIS_TSDF}
+\end{figure}
 %\section{Related Work}
@@
 
-The objective of our algorithm is to provide an expected quality of grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and the probability $\zeta$ of not obtaining force closure.
+The objective of our algorithm is to provide a quality of the expected grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and the probability $\zeta$ of obtaining force closure.
 
-Given a grasp $g$ on an object, we can define it by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\textbf{z},\tau\rbrace$.
-We have a set $I$ of $m$  point contacts and surface normal on the object where $i \in I$s is located at $c_i$ with surface normal $n_i$.
+We assume a bounded rectangular workspace $\mathcal{R}$.
+We parameterize a given grasp $g$ on an object with the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\textbf{z},\tau\rbrace$.
+We have an indexing set $I$ of $m$ point contacts and surface normal on the object: for $i \in I$ the contact is located at $c_i$ with surface normal $n_i$.
 The object has a center of mass $z$ and friction coefficient $\tau$.
+The line segment $\gamma(\cdot)$ has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig. 
+ \ref{fig:line_of_action}.
 
-Since we have uncertainty in the shape we only have a distribution on the grasp parameters, hence $p(g) = \lbrace p(\textbf{c}_1),...,p(\textbf{c}_m),p(\textbf{n}_1),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau \rbrace$.
-We note that $\tau$ is considered known and $\bar{z}$ is only the expected center of mass.
-In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute this distribution.
+Since we have uncertainty in the shape we have a distribution on the grasp parameters, hence $p(g) = \lbrace p(\textbf{c}_1),...,p(\textbf{c}_m),p(\textbf{n}_1),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau \rbrace$.
+We note that $\tau$ is considered known and $\bar{z}$ is only the expected center of mass, not a full distribution.
+We would like to replace this with the distribution on the center of mass, but it is unclear how to proceed in that direction.
+In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute these distributions on contact points and surface normals.
 
-With distribution on $p(g)$ we then use recent results on a Lipschitz constant for Ferrari-Canny Metric \cite{pokorny2013classical} to provide $\zeta$ or the probability the grasp will lose force closure and the expected quality of the grasp $Q_l^-(\bar{g})$, where $\bar{g} = \lbrace \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
-Details of this computation can be found in section \ref{sec:bound}.
+With distribution on $p(g)$ we then aim to use recent results on a Lipschitz constant for Ferrari-Canny Metric \cite{pokorny2013classical} to provide $\zeta$ or the probability the grasp will attain force closure and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = \lbrace \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
+We can compute $Q_l^-(\bar{g})$ and have a few plans of attack to be able to use the Lipschitz bound, but it is complicated to directly apply.
+We should have more progress on this front by working with Florian in the next couple of days.
 
@@
 
- To calculate $p(g)$, we assume a gripper contacts approaches along a line of action, or a 1-dimensional curve in the work space, defined by $\gamma(t)$.
+ To calculate $p(g)$, we assume a gripper contacts approaches along a parameterized line of action, or a 1-dimensional curve in the work space, defined by $\gamma(t)$.
 See Fig \ref{fig:line_of_action}, for a detailed illustration.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = \lbrace \gamma_1(t),...,\gamma_m(t) \rbrace$, these approach trajectories are then used to compute a distribution on grasp parameters.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = \lbrace \gamma_1(\cdot),...,\gamma_m(\cdot) \rbrace$, these approach trajectories are then used to compute a distribution on grasp parameters.
 
-We assume a bounded rectangular workspace $\mathcal{R}$.
-The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig. 
- \ref{fig:line_of_action}.
-
- We also define the  level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
+ %We also define the  level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
 
@@
 \includegraphics[scale = 0.3]{figures/Slide1.jpg}
-\caption{Parametrized Line of Action along an object}
+\caption{Parameterized Line of Action along an object}
 \vspace*{-10pt}
@@
 \end{figure}
-\textbf{TODO:MORE DESCRIPTIVE GRAPHIC}
-\subsection{Distribution on Contact Points} The probability distribution along the line $\gamma(t)$ is given by the following:
+%\textbf{TODO:MORE DESCRIPTIVE GRAPHIC}
+\subsection{Distribution on Contact Points} 
+In our implementation we discretize along the line $\gamma(t)$ evenly but write the derivation in continuous form for generality.
+The probability distribution along the line $\gamma(t)$ is given by the following:
 
@@
 =
-\mN(\mu_{a:b},\Sigma_{a:b})
+\mN(\mu_{a:b},\Sigma_{a:b}).
 \end{equation}
 
-This gives the distributions along the entire line of action in the workspace, however we want to compute the joint distribution   $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$.
-Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface, this avoids the problem of the distribution producing multiple modes for each intersection with the surface.
-We now derive a  this distribution
+This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate gaussian.
+We would like to find the distribution on the first contact point, which we can define as when the signed distance function $f(\gamma(t))$ is $0$ and all previous times $\tau$ we have $f(\gamma(\tau)) > 0$ for $0 \leq \tau < t$.
+This ensures $t$ is at the edge of the surface (having $f(\gamma(t)) = 0$) and that for all previous $\tau$ the gripper was outside of the surface (having $f(\gamma(\tau)) > 0$).
+We thus compute this as the joint distribution $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$.
+%Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface,
+This avoids the problem of the distribution producing multiple modes along the line: one for each intersection with the surface.
+We now derive this distribution
 
@@
 
+where we only indicate proportionality and will later normalize to probability $1$.
 Using the first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second one can be rewritten by conditioning the distribution \cite{petersen2008matrix}.
@@
 
-It is now clear that the following can be said
+The following can now be said:
 
@@
 
-The second product term can be efficiently evaluated by looking up the cumulative distribution of a multivariate Gaussian, which is common in most software packages \cite{matlab}.
+for the appropriate $\eta$ normalization factor.
+The second product term can be evaluated by calculating the cumulative distribution of a multivariate Gaussian, which we calculate with the Matlab function $mvncdf$.
+We show again the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and approach direction in Fig.
+\ref{fig:GraspContactPt}.
+%efficiently evaluated by looking up the cumulative distribution of a multivariate Gaussian, which is common in most software packages \cite{matlab}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide4.jpg}
+\caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
+Right: Induced distribution on the contact point as a function of x-axis position along the approach line.}
+\vspace*{-10pt}
+\label{fig:GraspContactPt}
+\end{figure}
 
@@
 We note that both methods yield a Gaussian distribution.
-We now demonstrate how to marginalize out the contact distribution and compute $p(\textbf{n}_i = \textbf{k})$\\
+We now demonstrate how to marginalize out the contact distribution and compute $p(\textbf{n}_i = \textbf{k})$.\\
 
@@
 \begin{equation}
-p(\textbf{c}_i = \gamma(t), \textbf{n}_i = \textbf{k}) = p\big(\textbf{n}_i = \textbf{k} | h(\gamma(t))\big)*p\big(\textbf{c}_i = \gamma(t)\big)
+p(\textbf{c}_i = \gamma(t), \textbf{n}_i = \textbf{k}) = p\big(\textbf{n}_i = \textbf{k} | \textbf{c}_i = \gamma(t) \big)*p\big(\textbf{c}_i = \gamma(t)\big)
 \end{equation}
@@
 \begin{equation}
-p\big( \textbf{n}_i = \textbf{k} \big) = \sum_T  p \big( \textbf{n}_i = k | h(\gamma(t)) \big) *p\big(c_i = \gamma(t)\big) dt
+p\big( \textbf{n}_i = \textbf{k} \big) = \sum_T  p \big( \textbf{n}_i = \textbf{k} | h(\gamma(t)) \big) *p\big(\textbf{c}_i = \gamma(t)\big) \Delta t
 \end{equation}
@@
 Thus, $p(\textbf{n}_i = \textbf{k})$ is approximated by a Gaussian Mixture Model.
+Note that the Ferrari-Canny metric requires $\textbf{n}_i$ be normalized, or, equivalently, a member of $\mathcal{S}^{d-1}$.
+We still have to fully investigate our un-normalized normal vectors interact with the grasp metric, and possible ways to project the distribution onto the sphere.
+We are especially interested in the von Mises-Fisher distribution, and any role it might play here, since it is the analogue of the Gaussian distribution defined on the surface of a $d-1$ sphere.
+We show the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach direction in Fig.
+\ref{fig:GraspSurfaceNormals}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide5.jpg}
+\caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
+Right: Induced distribution on the surface normals.}
+\vspace*{-10pt}
+\label{fig:GraspSurfaceNormals}
+\end{figure}
 
@@
 We define the quantity $\mathcal{D}(x) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ and note that it is equal to the probability that x is interior to the surface under the current observations.
+$\mathcal{D}(x)$ can be calculated as the CDF of $f(x)$ at $0$.
 We assume that the object has uniform mass density and then $\mathcal{D}(x)$ is the expected mass density at x.
@@
 \label{sec:bound}
-Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we prove that an extension is possible to give a probabilistic bound on the change in grasp quality.
-We rewrite the results here:
+Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we would like to prove an extension to give a probabilistic bound on the change in grasp quality.
+We restate several of their results here:
 
@@
 
-\textbf{TODO:WORK IN PRIOR WORK BETTER}
+%\textbf{TODO:WORK IN PRIOR WORK BETTER}
 We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ to refer to means.  
@@
 \subsection{Our Extension}
-We now define the concept of a probabilistic bound by functions $\sigma_i(\zeta) = \lbrace\Delta \textbf{r}_{i,\zeta}, \Delta \textbf{n}_{i,\zeta}\rbrace$.
+This area is in constant flux at the moment.
+We are trying to obtain a lower bound on the probability that force closure is attained (ideally that exact probability, but a lower bound tells us something useful as well).
+The distributions on grasp parameters induce a distribution on the quality metric.
+We show a histogram of the quality metric for a two-finger grasp for two approach directions on a given GPIS surface in Fig.
+\ref{fig:HistogramMetric}.
+The 100 different samples are over samples of the surface via the GPIS and then result in contacts and normals.
+
+We should be able to fill in this section more after a discussion with Florian on Thursday and Friday to sort out some details with the bound calculation.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide6.jpg}
+\caption{Histogram of Ferrari-Canny grasp quality metric for 100 samples of a GPIS surface for the same two finger approach directions.}
+\vspace*{-10pt}
+\label{fig:HistogramMetric}
+\end{figure}
+
+%We now define the concept of a probabilistic bound by functions $\sigma_i(\zeta) = \lbrace\Delta \textbf{r}_{i,\zeta}, \Delta \textbf{n}_{i,\zeta}\rbrace$.
 Given a probability $\zeta$, $\sigma_i$ returns the tuple denoting the maximum change in grasp parameter from the mean in the distribution for that probability.
 $\Delta \textbf{n}_i$ is the change in surface normal and $\Delta \textbf{r}_i$ is the change in moment arm defined as $\textbf{r}_i = \textbf{c}_i - \bar{\textbf{z}}$.
-Formally, this is defined as:
-
-\[
-  \sigma_i(\zeta)
-  =
-  \min_{\mathbb{R}_+} \textbf{d}
-\]
-
-\[
-  s.t. \ \ \left[ \int_{\mathbb{B}([\bar{t},\bar{\textbf{n}}], d)} p(\textbf{n}_i = \textbf{k},\textbf{c}_i=\gamma(t)) d[t,\textbf{k}] \right] \geq \zeta
-\]
-
-We now write the above bound as follows for a given $\sigma_i(\zeta)$:
-
- \begin{align*}
-|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
-                                      &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
-\end{align*}
-
-For convenience we rewrite the bound on a given set of grasp parameters as :
-
- \begin{align*}
-b_i(\zeta) &= ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
-                                      &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
-\end{align*}
-
-To provide an upper bound overall contact parameters we introduce the following:
-
-\begin{align}
-b(\zeta)  = \max_{i} b_i(\zeta)
-\end{align}
-
-To prove if  this bound is preserved on
-
- \begin{align}
- q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
- \end{align}
-
-we turn to the general case.
-$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
-Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
-We can ensure that is true.
-
-Lastly if one wants to find the probability they would lose force closure, they can simply solve the following
-
-\[
-  \zeta
-  =
-  \argmin_{\zeta} b(\zeta)
-\]
-
-\[
-  s.t. \ \  b(\zeta) \geq q(\bar(g))
-\]
-
-This would be pretty computationally expensive, so still a work in progress. \textbf{TODO:MAKE THIS EFFICIENT}
+%Formally, this is defined as:
+%
+%\[
+  %\sigma_i(\zeta)
+  %=
+  %\min_{\mathbb{R}_+} \textbf{d}
+%\]
+%
+%\[
+  %s.t. \ \ \left[ \int_{\mathbb{B}([\bar{t},\bar{\textbf{n}}], d)} p(\textbf{n}_i = \textbf{k},\textbf{c}_i=\gamma(t)) d[t,\textbf{k}] \right] \geq \zeta
+%\]
+%
+%
+%
+%We now write the above bound as follows for a given $\sigma_i(\zeta)$: 
+%
+ %\begin{align*}
+%|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
+                                      %&+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
+%\end{align*}
+%
+%For convenience we rewrite the bound on a given set of grasp parameters as : 
+%
+ %\begin{align*}
+%b_i(\zeta) &= ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
+                                      %&+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
+%\end{align*}
+%
+%To provide an upper bound overall contact parameters we introduce the following: 
+%
+%\begin{align}
+%b(\zeta)  = \max_{i} b_i(\zeta)
+%\end{align}
+%
+%To prove if  this bound is preserved on
+%
+ %\begin{align}
+ %q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
+ %\end{align}
+ %
+%we turn to the general case.
+%$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
+%Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
+%We can ensure that is true.
+%
+%Lastly if one wants to find the probability they would lose force closure, they can simply solve the following 
+%
+%\[
+  %\zeta
+  %=
+  %\argmin_{\zeta} b(\zeta)
+%\]
+%
+%\[
+  %s.t. \ \  b(\zeta) \geq q(\bar(g))
+%\]
+%
+%This would be pretty computationally expensive, so still a work in progress. \textbf{TODO:MAKE THIS EFFICIENT}
 

### 2014-07-31 paper.tex
Added related work, new derivations and revised notation

@@
 
-\author{Michael Laskey*, Zoe McCarthy*, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
+\author{Michael Laskey*, Zoe McCarthy*, Florian T. Pokorny, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
 
@@
 
-We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
-We assume friction is at the contact points. 
-The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
-%\section{Goals and Current Progress}
+We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
 We are working to extend this metric to incorporate shape uncertainty.
-For our grasping model, we make a simplifying assumption that each gripper approaches the object along a fixed line of action and thus the contact points lie on this line.
 We would like to analyze the induced distributions over grasp parameters and the Ferrari-Canny metric.
-Specifically, we would like to answer the following question:
-What is the probability of achieving force closure under the given grasp approach directions and implicit surface distribution?
-We are also interested in the grasp quality of the expected grasp.
-So far, we have explicit formulas for the distributions of the contact points along the line of action and surface normal vectors and the expected center of mass of the object to be grasped.
-We are thoroughly investigating utilizing recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical} in order to prove probabalistic bounds on the change in grasp quality under shape uncertainty.
+We are thoroughly investigating utilizing recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical} in order to prove probabilistic bounds on the change in grasp quality under shape uncertainty.
 We are also investigating efficient ways to calculate the distributions on the grasp parameters and ways to update them quickly with new observations.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide4.jpg}
-\caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
-Right: Induced distribution on the contact point as a function of x-axis position along the approach line.}
-\vspace*{-10pt}
-\label{fig:IntroTopPic}
-\end{figure}
 
@@
 \end{figure}
+
+\section{Related Work}
+
+While a variety of grasp metrics have been proposed, few explicitly looked at uncertainty in grasp parameters.
+Zheng et al.
+looked at friction and contact point uncertainty \cite{zheng2005}.
+He computed the maximum distance a contact point was allowed to deviate from its expected grasp, while maintaining force closure.
+Kehoe et al.
+looked at shape uncertainty for push grasps, however this was limited to parallel jaw grippers and only measured the probability of force closure \cite{kehoe2012toward}.
+More closely related to our approach is the work of Christopoulos and Schrater \cite{christopoulos2007handling}.
+They use a spline representation for uncertainty and sample from a distribution of losing force closure, their approach though is limited to two contacts.
+Our method looks at not only force closure, but provides a lower bound on the Ferrari-Canny metric within some user set distributions.
+
+The choice of using a Gaussian Process Implicit Surface (GPIS) to represent our uncertainty, stems from the fact that it provides a formal way to include various sources of noise in observations.
+Prior work has used uncertainty representation such as independent Gaussian noise on each vertex in a Polygonal mesh \cite{kehoe2012toward}.
+However, this doesn't provide a continuous function one can easily compute distributions on grasp parameters with.
+GPIS is also becoming more prevalent in the grasping community with recent work by Dragiev et al.
+\cite{dragiev2011} .
 
@@
 
-The objective of our algorithm is to provide a quality of the expected grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and the probability $\zeta$ of obtaining force closure.
+The objective of our algorithm is to provide a quality of the expected grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and a lower bound $b$ that is the expected deviation from the quality of the expected grasp.
 
@@
 We note that $\tau$ is considered known and $\bar{z}$ is only the expected center of mass, not a full distribution.
-We would like to replace this with the distribution on the center of mass, but it is unclear how to proceed in that direction.
 In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute these distributions on contact points and surface normals.
 
-With distribution on $p(g)$ we then aim to use recent results on a Lipschitz constant for Ferrari-Canny Metric \cite{pokorny2013classical} to provide $\zeta$ or the probability the grasp will attain force closure and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = \lbrace \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
-We can compute $Q_l^-(\bar{g})$ and have a few plans of attack to be able to use the Lipschitz bound, but it is complicated to directly apply.
-We should have more progress on this front by working with Florian in the next couple of days.
+With a distribution on $p(g)$ we then aim to use recent results on a Lipschitz constant for the Ferrari-Canny Metric \cite{pokorny2013classical} to provide $b$ or a lower bound on the change in grasp quality from the expected deviation in grasp and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = \lbrace \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
 
@@
 
-Thus, $p(\textbf{n}_i = \textbf{k})$ is approximated by a Gaussian Mixture Model.
-Note that the Ferrari-Canny metric requires $\textbf{n}_i$ be normalized, or, equivalently, a member of $\mathcal{S}^{d-1}$.
-We still have to fully investigate our un-normalized normal vectors interact with the grasp metric, and possible ways to project the distribution onto the sphere.
-We are especially interested in the von Mises-Fisher distribution, and any role it might play here, since it is the analogue of the Gaussian distribution defined on the surface of a $d-1$ sphere.
-We show the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach direction in Fig.
-\ref{fig:GraspSurfaceNormals}.
+The traditional grasp metrics, such as  Ferrari-Canny, requires $\textbf{n}_i$ be normalized, or, equivalently, a member of $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
+To account for this we project the Gaussian distribution $p \big(\textbf{n}_i = \textbf{k} |\textbf{c}_i = \gamma(t) \big)$  onto $\mathcal{S}^{d-1}$.
+We use a stereographic projection technique developed by Olano and North \cite{olano1997normal}.
+In Fig.6
+\ref{fig:GraspSurfaceNormals}, we show the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach direction .
 
@@
 which can be approximated by sampling $\mathcal{R}$ uniformly in a voxel grid and approximating the spatial integral by a sum.
+We show the computed density and caculated expected center of mass in Fig.
+\ref{fig:GPIS_MASS}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide6.jpg}
+\caption{Left: A surface with GPIS construction and expected center of mass (blue X)
+Right: The distribution on the density of each point assuming uniform center of mass}
+\vspace*{-10pt}
+\label{fig:GPIS_MASS}
+\end{figure}
 
@@
 
-\subsection{Prior Work}
+\subsection{Derivation of Lipschitz Constant }
 
-%\textbf{TODO:WORK IN PRIOR WORK BETTER}
 We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ to refer to means.  
@@
 
-\subsection{Our Extension}
-This area is in constant flux at the moment.
-We are trying to obtain a lower bound on the probability that force closure is attained (ideally that exact probability, but a lower bound tells us something useful as well).
-The distributions on grasp parameters induce a distribution on the quality metric.
-We show a histogram of the quality metric for a two-finger grasp for two approach directions on a given GPIS surface in Fig.
-\ref{fig:HistogramMetric}.
-The 100 different samples are over samples of the surface via the GPIS and then result in contacts and normals.
+\subsection{Lower Bound on Expected Grasp Quality}
+Given a the distributions on a line of action, $p\big(\textbf{n}_i = \textbf{k}\big)$ and $p\big(\textbf{c}_i=\gamma(t) \big)$ and the expected values $\bar{\textbf{c}_i}$ and $\bar{\textbf{n}_i}$.
+We are interested in finding the expected deviations for the two parameters, $||\Delta n_i||$ and  $||\Delta c_i||$.
+Using these expected deviations we then derive a lower bound $b$ for the quality of the expected grasp.
 
-We should be able to fill in this section more after a discussion with Florian on Thursday and Friday to sort out some details with the bound calculation.
+\[
+  ||\Delta n_i|| =  \int_{\mathbb{B}(\bar{\textbf{n}_i})} ||\textbf{k} - \bar{\textbf{n}_i}|| p(\textbf{n}_i = \textbf{k}) d\textbf{k}
+\]
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide6.jpg}
-\caption{Histogram of Ferrari-Canny grasp quality metric for 100 samples of a GPIS surface for the same two finger approach directions.}
-\vspace*{-10pt}
-\label{fig:HistogramMetric}
-\end{figure}
+\[
+  ||\Delta c_i|| =  \int_{\mathbb{B}(\bar{\textbf{c}_i)}} ||\gamma(t) - \bar{\textbf{c}_i}|| p(\textbf{c}_i = \textbf{k}) dt
+\]
 
-%We now define the concept of a probabilistic bound by functions $\sigma_i(\zeta) = \lbrace\Delta \textbf{r}_{i,\zeta}, \Delta \textbf{n}_{i,\zeta}\rbrace$.
-Given a probability $\zeta$, $\sigma_i$ returns the tuple denoting the maximum change in grasp parameter from the mean in the distribution for that probability.
-$\Delta \textbf{n}_i$ is the change in surface normal and $\Delta \textbf{r}_i$ is the change in moment arm defined as $\textbf{r}_i = \textbf{c}_i - \bar{\textbf{z}}$.
-%Formally, this is defined as:
-%
-%\[
-  %\sigma_i(\zeta)
-  %=
-  %\min_{\mathbb{R}_+} \textbf{d}
-%\]
-%
-%\[
-  %s.t. \ \ \left[ \int_{\mathbb{B}([\bar{t},\bar{\textbf{n}}], d)} p(\textbf{n}_i = \textbf{k},\textbf{c}_i=\gamma(t)) d[t,\textbf{k}] \right] \geq \zeta
-%\]
-%
-%
-%
-%We now write the above bound as follows for a given $\sigma_i(\zeta)$: 
-%
- %\begin{align*}
-%|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
-                                      %&+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
-%\end{align*}
-%
-%For convenience we rewrite the bound on a given set of grasp parameters as : 
-%
- %\begin{align*}
-%b_i(\zeta) &= ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
-                                      %&+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
-%\end{align*}
-%
-%To provide an upper bound overall contact parameters we introduce the following: 
-%
-%\begin{align}
-%b(\zeta)  = \max_{i} b_i(\zeta)
-%\end{align}
-%
-%To prove if  this bound is preserved on
-%
- %\begin{align}
- %q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
- %\end{align}
- %
-%we turn to the general case.
-%$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
-%Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
-%We can ensure that is true.
-%
-%Lastly if one wants to find the probability they would lose force closure, they can simply solve the following 
-%
-%\[
-  %\zeta
-  %=
-  %\argmin_{\zeta} b(\zeta)
-%\]
-%
-%\[
-  %s.t. \ \  b(\zeta) \geq q(\bar(g))
-%\]
-%
-%This would be pretty computationally expensive, so still a work in progress. \textbf{TODO:MAKE THIS EFFICIENT}
+We now write the above bound as follows for a given line of action $i$:
+
+ \begin{align*}
+|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq (1+\tau)||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| \\
+  \end{align*}
+
+Here $\bar{\textbf{r}}_i = \bar{\textbf{c}}_i - \bar{\textbf{z}}_i$. For convenience we rewrite the bound on a given set of grasp parameters as :
+
+ \begin{align*}
+b_i &= (1+\tau)||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| \\
+\end{align*}
+
+To provide an upper bound overall contact parameters we introduce the following:
+
+\begin{align}
+b(\zeta)  = \max_{i} b_i(\zeta)
+\end{align}
+
+To prove if  this bound is preserved on
+
+ \begin{align}
+ q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
+ \end{align}
+
+we turn to the general case.
+$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
+Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
+We can ensure that is true.
+
+\subsection{Tightening Bounds on Change in Grasp Quality}
+
+Experimentally we found the Lipschitz bound to be looser than we would like, despite the fact that it is a local bound.
+We are currently working on tightening the bound by using the following property:
+
+For a $x,x_0$ in a bounded set $U$ in $\mathbb{R}^n$, for a given $f(x):\mathbb{R}^n \rightarrow \mathbb{R}$.
+
+\[
+  f(x) = f(x_0) + <R(x),x-x_0>
+\]
+
+\[
+  R(x) = \int_0^1 \frac{d}{dx}f(x_0+t(x-x_0)) dt
+\]
+
+Then let $L = \mbox{sup}_{s \in U} |\frac{df(x)}{dx} |$, so $|R(x)| \leq L$ and
+
+\[
+  |f(x)-f(x_0)| = |<R(x),x-x_0>| \leq L |x-x_0|
+\]
+
+Since we are currently working in 2D, there is no need to approximate the friction cone and the Ferrari-Canny is equal to the true grasp quality.
+What that means is that one could look at the analytical derivative of the active facet and use that to bound the metric.
+Looking at a single facet on the convex hull computed by Ferrari-Canny, one simply computes the derivative of the function $h(W,\textbf{z},\tau)$, where $h$ returns the absolute distance to the origin $d$ from the facet described by the input parameters.
+
+While we can compute the derivative using symbolic software \cite{SymPy}, it is still on going work to quickly determine either the set $U$ that the bound is valid or supremum of the derivative in a given set.
+
+\subsection{Approximation of True Metric}
+While we work on the tightening the bound, we will present a metric that should give an intuitive idea of what is import in our grasp metric.
+Our grasp metric currently returns $Q(\bar{g})$ and an upper bound $b$ on the expected change in grasp.
+Ideally we want to rate grasps by the highest value $Q_l = Q(\bar{g}) - b$, thus being the lowest quality given the bound.
+
+Currently though the two values $Q(\bar{g})$ and $b$ are two different magnitudes, but both are informative.
+We can approximate a the effect of a tighter bound by simply projecting both $Q(\bar{g})$ and $b$ to the unit ball, then subtracting.
+
+\section{Experiments}
+
+To provide a better understanding of our metric, we will run the approximate one on different objects with varying level of noise.
+Given a set of 100 randomly chosen grasps for each object, we will look at what one our metric rates highest.
 

### 2014-07-31 paper.tex
langle rangle fix
Added experiments and GPIS

@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide2.jpg}
+\includegraphics[scale = 0.3]{figures/Slide02.jpg}
 \caption{An example of the noise from a Kinect-like sensor}
@@
 
-\section{Gaussian Process Primer}
-%\textbf{TODO:FIX THIS SECTION AND MAKE NOTATION CONSISTENT}
- Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
-In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}, ~\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
+\section{Gaussian Process Implicit Surfaces}
+
+In this section we describe the mathematical derivation of Gaussian Process Implicit Surface representations.
+
+\subsection{Gaussian Process (GP) Background}
+
+Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006gaussian}.
+In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}$, $\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
 The observations are assumed to be noisy measurements from the unknown target function $f$:
@@
 A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2006}:
-\begin{equation}
-  p(f_*|\bx_*,\mD) 
-  \sim 
-  \mN\big(k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by,
-\end{equation}
-\[
-  k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big), \label{eq:GPposterior}
-\]
+Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2006gaussian}:
+\begin{align}
+	p(f_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \label{eq:GPposterior} \\
+	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \label{eq:GPmean} \\
+	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) \label{eq:GPvar}
+\end{align}
 where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
+This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:
 
+\begin{align*}
+	\text{cov}\left(f(\bx_i), f(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
+	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \\
+	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)
+\end{align*}
+
+\subsection{Kernel Selection}
 The choice of kernel is application-specific, since the function $k(\bx_i,\bx_j)$ is used as a measure of correlation between states $\bx_i$ and $\bx_j$.
@@
 \begin{equation}
-k(\bx_i,\bx_j) 
-=
-\nu^2\exp(-\frac{1}{2}(\bx_i - \bx_j)^{\intercal}\Lambda^{-1}(\bx_i - \bx_j))
+	k(\bx_i,\bx_j) = \nu^2\exp(-\frac{1}{2}(\bx_i - \bx_j)^{\intercal}\Lambda^{-1}(\bx_i - \bx_j))
 \end{equation}
 where $\Lambda= \text{diag}(\lambda_1^2,\ldots,\lambda_d^2)$ are the characteristic length scales of each dimension of $\bx$ and $\nu^2$ describes the variability of $f$.
-The vector of hyper-parameters $\boldsymbol{\theta} = \{\sigma,\nu,\lambda_1,\ldots,\lambda_d\}$ is chosen or optimized during the training process by minimizing the log likelihood $p(\by|\mX,\boldsymbol{\theta})$ \cite{rasmussen2006}.
+Other common kernels relevant to GPIS are the thin-plate splines kernel \cite{williams2007} and the Matern kernel \cite{bjorkman2013enhancing}.
 
-We represent surfaces as a Gaussian Process trained to predict the Truncated Signed Distance Field of a surface by noisy samples from that TSDF, as indicated in Fig.
- \ref{fig:GPIS_TSDF}.
+The measurement noise parameter $\sigma$ is usually estimated based on a model of the sensor used to collect measurements
+The vector of remaining hyperparameters $\boldsymbol{\theta} = \{\nu, \lambda_1,\ldots,\lambda_d\}$ is optimized during the training process by maximizing the log-likelihood $p(\by|\mX,\boldsymbol{\theta})$, usually using gradient descent \cite{rasmussen2006gaussian}.
+The log-likelihood function is subject to local maxima, and therefore the hyperparamter search often involves a search over the maxima found from several random initializations of the hyperparamters.
+
+\subsection{Training}
+Given the hyperparameters, the training phase consists of evaluating the vector 
+\begin{equation}
+\alpha = (K + \sigma^2 I)^{-1}\by,
+\end{equation}
+which needs the inversion of a $n \times n$ matrix $(K + \sigma^2I)$.
+Direct computation of the inverse of the symmetric matrix requires $O(n^3)$ operations and $O(n^2)$ storage, which makes it impractical for real-world applications consisting of thousands of data points.
+
+For larger systems, it is more efficient to solve the system
+\begin{equation}
+	\tilde{K}\alpha = \by, ~\text{where} ~\tilde{K} = (K + \sigma^2I),
+\end{equation}
+using iterative methods.
+Since $\tilde{K}$ is symmetric and positive-definite, the conjugate gradient (CG) method or an incomplete Cholesky factorizatoin can be used to iteratively solve the equation to some error tolerance \cite{gibbs1997}.
+The computational complexity of the CG method is $O(kdn^2)$ where $d$ is the dimensionality of the data and $k$ iterations of the CG method are required for convergence.
+Fast approximate matrix-vector products using the Improved Fast Gaussian Transform (IGFT) can reduce the complexity of computing the $\alpha$ vector to $O(n)$ for the squared exponential kernel \cite{raykar2007}.
+Alternatively Fast Multipole Methods can be used to reduce the complexity of computing the kernel matrices and vectors to $O(n \log n)$ \cite{gumerov2005fast}.
+
+A large variety of methods haven been proposed for further speeding up the GP training phase including, but not limited to, training on a subset of data chosen either randomly or using an information-theoretic criterion, or local methods that only rely on neighboring data points for making predictions in a given region of space.
+The subset selection methods can be separated into two groups: subset of data (SoD) and subset of regressors (SoR) \cite{quinonero2005unifying}.
+In SoD approaches, a criterion is used to select an `active' subset of training data to be used in inference, and all other `inactive' training data is discarded.
+In SoR approaches the relation of the inactive points to the active points is retained by replacing the kernel function with the alternative function
+\begin{equation}
+	k(\textbf{x}_i,\textbf{x}_j) = k(\textbf{x}_i,\textbf{u}) K_{\textbf{u}, \textbf{u}}^{-1} k(\textbf{u},\textbf{x}_j).
+\end{equation}
+\noindent We refer the reader to \cite{chalupka2013} for an extensive comparison of these methods.
+In this paper we consider objects that can be represented with few enough points that computational tractability is not an issue, and we defer the question of which methods are most effective for the special case of constructing GPIS to future work.
 
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide3.jpg}
+\includegraphics[scale = 0.3]{figures/Slide03.jpg}
 \caption{Left: A surface represented as a Truncated Signed Distance Field (TSDF).
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide1.jpg}
+\includegraphics[scale = 0.3]{figures/Slide01.jpg}
 \caption{Parameterized Line of Action along an object}
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide4.jpg}
+\includegraphics[scale = 0.3]{figures/Slide04.jpg}
 \caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide5.jpg}
+\includegraphics[scale = 0.3]{figures/Slide05.jpg}
 \caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide6.jpg}
+\includegraphics[scale = 0.3]{figures/Slide06.jpg}
 \caption{Left: A surface with GPIS construction and expected center of mass (blue X)
@@
 
-To provide a better understanding of our metric, we will run the approximate one on different objects with varying level of noise.
-Given a set of 100 randomly chosen grasps for each object, we will look at what one our metric rates highest.
+To validate our theoretical caculations, we compared them to empirical distributions found via Monte-Carlo Sampling.
+The qualitative results for surface normals and contacts can be found in Figures \ref{fig:Contact_Dist} and \ref{fig:Normal_Dist} respectively.
+We present the numerical comparison with KL-Divergence in Table 1, as you can see the distributions are very closely related.
+
+\begin{table}[ht!]
+        \begin{tabular}{ l | c c c}
+         Distribution & \bf Marker & \bf Tape & \bf Loofa \\ 
+        \hline \\
+         p($\textbf{c}_i$) & 0.14 & 0.08 & 0.02 \\
+        \hline \\
+        p($\textbf{n}_i$ )& 0.35 & 0.12 & 0.16 \\
+        \hline 
+        \end{tabular}
+        \caption{The KL-Divergence for different distributions on the contact points and surface normals}
+
+\vspace*{-20pt}
+\end{table}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide07.jpg}
+\caption{Top: A surface with GPIS construction and line of action with the start pointed denoted by green x.
+Middle: Theoretical distribution computed on contact point
+Bottom: Empirically sampled distribution}
+\vspace*{-10pt}
+\label{fig:Contact_Dist}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide08.jpg}
+\caption{Top: A surface with GPIS construction and line of action with the start pointed denoted by green x.
+Middle: Theoretical distribution computed for surface normals
+Bottom: Empirically sampled distribution}
+\vspace*{-10pt}
+\label{fig:Normal_Dist}
+\end{figure}
+
+To better understand the quality of grasp that our proposed metric will find, we present results on a variety of grasps as shown in Fig.
+\ref{fig:Grasps}.
+The numerical values in terms are presented in Table 2.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide09.jpg} \includegraphics[scale = 0.3]{figures/Slide10.jpg}
+\caption{Example grasps on the provided dataset with the histrograms of grasp quality given the uncertainity}
+\vspace*{-10pt}
+\label{fig:Grasps}
+\end{figure}
+
+\begin{table}[ht!]
+        \begin{tabular}{ l | c c c c}
+         Distribution & \bf Marker & \bf Tape & \bf Loofa & \bf Stapler \\ 
+        \hline \\
+         $\bar{Q(g)}$ & -0.003 & 0.022 & 0.000 &  0.018\\
+        \hline \\
+        var $Q(g)$ & 0.025 & 0.016 & 0.017 &  0.054\\
+        \hline 
+        $Q(\bar{g})$ & 0.030 & 0.024 & -0.012 & 0.014\\
+        \hline 
+        $b$ & 1.634 & 0.540 & 2.220 & 2.600 \\
+        \hline 
+        $h$ & 0.025 & 0.016 & 0.017 & 0.097 \\
+        \hline 
+        \end{tabular}
+        \caption{A comparison of all the different values that characterize a grasp.}
+
+\vspace*{-20pt}
+\end{table}
 

### 2014-07-31 paper.tex
Many edits to writing, intro, added Contributions To Date section

@@
 \title{\LARGE \bf
-Grasp Metric for Shape Uncertainity with Gaussian Proccess Implicit Surface Representation (Not Finished Work) }
+Grasp Distributions and a Metric for Shape Uncertainty with Gaussian Process Implicit Surface Representation (Draft: Not Finished Work) }
 
-\author{Michael Laskey*, Zoe McCarthy*, Florian T. Pokorny, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
+\author{Michael Laskey*, Zoe McCarthy*, Florian T. Pokorny, Jeff Mahler, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
 
@@
 We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
-We are working to extend this metric to incorporate shape uncertainty.
-We would like to analyze the induced distributions over grasp parameters and the Ferrari-Canny metric.
-We are thoroughly investigating utilizing recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical} in order to prove probabilistic bounds on the change in grasp quality under shape uncertainty.
-We are also investigating efficient ways to calculate the distributions on the grasp parameters and ways to update them quickly with new observations.
+We are working to extend this metric to incorporate shape uncertainty, and to do that we analyze the resulting distributions over grasp parameters induced by the shape uncertainty.
 
@@
 \end{figure}
+
+\section{Contributions To Date}
+We assume that a robot's $m$ grippers approach the grasped object along straight lines (which we call lines of action), and analyze how this grasping model interacts with the probability distribution on shapes described by a Gaussian Process Implicit Surface (GPIS).
+We calculate and visualize the theoretical probability distributions on grasp contact points and normals and the expected center of mass induced by the GPIS and line of action.
+We empirically validate our calculated distributions by measuring their KL-divergence from the empirical probability distributions obtained by sampling from the GPIS distribution and calculating the contact point along the line of action and the corresponding normal for several example shapes.
+
+We show ongoing work in adapting the Ferari-Canny grasp metric to this setting.
+We present an algorithm to compute an upper bound on the expected deviation in grasp quality from the metric evaluated at a single grasp using a recent result that Ferrari-Canny is Lipschitz continuous \cite{pokorny2013classical}.
+In order to improve the tightness of these bounds and thus improve our algorithm, we show initial investigations into calculating gradients for Ferrari-Canny in order to find very tight locally Lipschitz bounds.
+We present a heuristic algorithm based off of the previous algorithm that normalizes the
 
@@
 
-The choice of using a Gaussian Process Implicit Surface (GPIS) to represent our uncertainty, stems from the fact that it provides a formal way to include various sources of noise in observations.
+The choice of using a Gaussian Process Implicit Surface to represent our uncertainty, stems from the fact that it provides a formal way to include various sources of noise in observations.
 Prior work has used uncertainty representation such as independent Gaussian noise on each vertex in a Polygonal mesh \cite{kehoe2012toward}.
@@
 
-The objective of our algorithm is to provide a quality of the expected grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and a lower bound $b$ that is the expected deviation from the quality of the expected grasp.
+%The objective of our algorithm is to provide a quality of the expected grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and a lower bound $b$ that is the expected deviation from the quality of the expected grasp.
 
-We assume a bounded rectangular workspace $\mathcal{R}$.
-We parameterize a given grasp $g$ on an object with the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\textbf{z},\tau\rbrace$.
+We assume a bounded 2-d rectangular workspace $\mathcal{R}$.
+We parameterize a single grasp $g$ on an object with the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\textbf{z},\tau )$.
 We have an indexing set $I$ of $m$ point contacts and surface normal on the object: for $i \in I$ the contact is located at $c_i$ with surface normal $n_i$.
@@
 
-Since we have uncertainty in the shape we have a distribution on the grasp parameters, hence $p(g) = \lbrace p(\textbf{c}_1),...,p(\textbf{c}_m),p(\textbf{n}_1),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau \rbrace$.
-We note that $\tau$ is considered known and $\bar{z}$ is only the expected center of mass, not a full distribution.
-In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute these distributions on contact points and surface normals.
-
-With a distribution on $p(g)$ we then aim to use recent results on a Lipschitz constant for the Ferrari-Canny Metric \cite{pokorny2013classical} to provide $b$ or a lower bound on the change in grasp quality from the expected deviation in grasp and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = \lbrace \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau \rbrace$.
+We assume that the robot grippers move along the line of action until they make contact with the object and stop.
+Since we have uncertainty in the shape this induces a distribution on the grasp parameters subject to the line, hence $p(g) = ( p(\textbf{c}_1),...,p(\textbf{c}_m),p(\textbf{n}_1),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau )$.
+We note that $\tau$ is considered known and $\bar{z}$ is the expected center of mass, not a full probability distribution.
+In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute the distributions on contact points and surface normals and expected center of mass.
 
@@
  For the following derivations we introduce the following,
- $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, where $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS model \cite{rasmussen2006} .
+ $\theta(x) = ( \mu(x),\Sigma(x) )$, where $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS model \cite{rasmussen2006} .
 
@@
 See Fig \ref{fig:line_of_action}, for a detailed illustration.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = \lbrace \gamma_1(\cdot),...,\gamma_m(\cdot) \rbrace$, these approach trajectories are then used to compute a distribution on grasp parameters.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, these approach trajectories are then used to compute a distribution on grasp parameters.
 
@@
 
-\begin{align*}
-p\big(\textbf{c}_i = \gamma(t)\big) &\propto p\big(f(\gamma(t)) = 0\big)\\
-               &*P\big(f(\gamma(\tau)) > 0 | f(\gamma(t)) = 0: \forall \tau \in [0,t)\big)
-\end{align*}
+\[
+  p\big(\textbf{c}_i = \gamma(t)\big) \propto 
+\]
+\[
+  p\big(f(\gamma(t)) = 0\big)P\big(f(\gamma(\tau)) > 0 | f(\gamma(t)) = 0: \forall \tau \in [0,t)\big)
+\]
 
@@
 
-\begin{align*}
-p\big(\textbf{c}_i = \gamma(t)\big) &= \frac{1}{\eta} p(f\gamma(t) = 0) \\
-				   &*P_c\big(f(\gamma(\tau)) > 0): \forall \tau \in [0,t)\big)			 
-\end{align*}
+\[
+  p\big(\textbf{c}_i = \gamma(t)\big) = 
+\]
+\[
+  = \frac{1}{\eta} p(f(\gamma(t)) = 0) P_c\big(f(\gamma(\tau)) > 0): \forall \tau \in [0,t)\big)			 
+\]
 
@@
 \subsection{Distribution on Surface Normals} 
-The distribution of surface normals $p(\textbf{n}_i = \textbf{k})$ can be calculate as follows.
-First we assume that some function exists $h(x) = \lbrace \mu_{\nabla}(x), \Sigma_{\nabla}(x) \rbrace$, hence given a point $\bf{x}$ it returns the parameters for a Gaussian distribution around the gradient.
+The distribution of surface normals $p(\textbf{n}_i = \textbf{v})$ can be calculate as follows.
+First we assume that some function exists $h(x) = ( \mu_{\nabla}(x), \Sigma_{\nabla}(x) )$, hence given a point $\bf{x}$ it returns the parameters for a Gaussian distribution around the gradient.
 this function can be computed via learning the gradient \cite{solak2003derivative} or analytical differentiation of $f(x)$.
 We note that both methods yield a Gaussian distribution.
-We now demonstrate how to marginalize out the contact distribution and compute $p(\textbf{n}_i = \textbf{k})$.\\
+We now demonstrate how to marginalize out the contact distribution and compute $p(\textbf{n}_i = \textbf{v})$.\\
 
@@
 \begin{equation}
-p(\textbf{c}_i = \gamma(t), \textbf{n}_i = \textbf{k}) = p\big(\textbf{n}_i = \textbf{k} | \textbf{c}_i = \gamma(t) \big)*p\big(\textbf{c}_i = \gamma(t)\big)
+p(\textbf{c}_i = \gamma(t), \textbf{n}_i = \textbf{v}) = p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big)
 \end{equation}
@@
 \begin{equation}
-p(\textbf{n}_i = \textbf{k}) = \int_a^b  p \big(\textbf{n}_i = \textbf{k} | \textbf{c}_i = \gamma(t) \big)*p(\textbf{c}_i = \gamma(t)) dt
+p(\textbf{n}_i = \textbf{v}) = \int_a^b  p \big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p(\textbf{c}_i = \gamma(t)) dt
 \end{equation}
@@
 \begin{equation}
-p\big(\textbf{n}_i = \textbf{k}\big) = \int_a^b  p \big(\textbf{n}_i = \textbf{k} | h(\gamma(t))\big)*p\big(\textbf{c}_i = \gamma(t)\big) dt
+p\big(\textbf{n}_i = \textbf{v}\big) = \int_a^b  p \big(\textbf{n}_i = \textbf{v} | h(\gamma(t))\big)p\big(\textbf{c}_i = \gamma(t)\big) dt
 \end{equation}
@@
 \begin{equation}
-p\big( \textbf{n}_i = \textbf{k} \big) = \sum_T  p \big( \textbf{n}_i = \textbf{k} | h(\gamma(t)) \big) *p\big(\textbf{c}_i = \gamma(t)\big) \Delta t
+p\big( \textbf{n}_i = \textbf{v} \big) = \sum_T  p \big( \textbf{n}_i = \textbf{v} | h(\gamma(t)) \big) p\big(\textbf{c}_i = \gamma(t)\big) \Delta t
 \end{equation}
 
-The traditional grasp metrics, such as  Ferrari-Canny, requires $\textbf{n}_i$ be normalized, or, equivalently, a member of $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
-To account for this we project the Gaussian distribution $p \big(\textbf{n}_i = \textbf{k} |\textbf{c}_i = \gamma(t) \big)$  onto $\mathcal{S}^{d-1}$.
-We use a stereographic projection technique developed by Olano and North \cite{olano1997normal}.
-In Fig.6
-\ref{fig:GraspSurfaceNormals}, we show the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach direction .
+Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
+To account for this we project the Gaussian distribution $p \big(\textbf{n}_i = \textbf{v} |\textbf{c}_i = \gamma(t) \big)$  onto $\mathcal{S}^{d-1}$.
+We use a projection technique developed by Olano and North \cite{olano1997normal}.
+In Fig.
+\ref{fig:GraspSurfaceNormals}, we show the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach direction.
 
@@
 
-We define the quantity $\mathcal{D}(x) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ and note that it is equal to the probability that x is interior to the surface under the current observations.
-$\mathcal{D}(x)$ can be calculated as the CDF of $f(x)$ at $0$.
-We assume that the object has uniform mass density and then $\mathcal{D}(x)$ is the expected mass density at x.
+We recall the quantity CDF$(f(x))(0) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ as the cumulative distribution function of $f(x)$ evalutated at 0 and note that it is equal to the probability that $x$ is interior to the surface under the current observations.
+We assume that the object has uniform mass density and then CDF$(f(x))(0)$ is the expected mass density at $x$.
 Then we can find the expected center of mass as:
@@
   \frac
-    {\int_{\mathcal{R}}x \mathcal{D}(x) dx}
-    {\int_{\mathcal{R}}  \mathcal{D}(x) dx}
+    {\int_{\mathcal{R}}x CDF(f(x))(0) dx}
+    {\int_{\mathcal{R}}  CDF(f(x))(0) dx}
 \end{equation}
 
-which can be approximated by sampling $\mathcal{R}$ uniformly in a voxel grid and approximating the spatial integral by a sum.
-We show the computed density and caculated expected center of mass in Fig.
+which can be approximated by sampling $\mathcal{R}$ uniformly in a grid and approximating the spatial integral by a sum.
+We show the computed density and calculated expected center of mass for a marker in Fig.
 \ref{fig:GPIS_MASS}.
@@
 Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we would like to prove an extension to give a probabilistic bound on the change in grasp quality.
+
+With a distribution on $p(g)$ we then use recent results on a Lipschitz constant for the Ferrari-Canny Metric \cite{pokorny2013classical} to provide $b$ or an upper bound on the change in grasp quality from the expected deviation in grasp and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = ( \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau )$.
+
 We restate several of their results here:
 
-\subsection{Derivation of Lipschitz Constant }
+\subsection{Prior Work: Derivation of Lipschitz Constant }
 
-We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ to refer to means.  
+We follow the notation of \cite{pokorny2013classical} except that the friction coefficient is $\mu$ in that paper and $\tau$ in this paper since we use $\mu$ to refer to mean vectors.  
 We re-state some of their central theorems for our use here.
@@
 
-\subsection{Lower Bound on Expected Grasp Quality}
-Given a the distributions on a line of action, $p\big(\textbf{n}_i = \textbf{k}\big)$ and $p\big(\textbf{c}_i=\gamma(t) \big)$ and the expected values $\bar{\textbf{c}_i}$ and $\bar{\textbf{n}_i}$.
+\subsection{Upper Bound on Expected Deviation of Grasp Quality}
+Given a the distributions on a line of action, $p\big(\textbf{n}_i = \textbf{v}\big)$ and $p\big(\textbf{c}_i=\gamma(t) \big)$ and the expected values $\bar{\textbf{c}_i}$ and $\bar{\textbf{n}_i}$.
 We are interested in finding the expected deviations for the two parameters, $||\Delta n_i||$ and  $||\Delta c_i||$.
-Using these expected deviations we then derive a lower bound $b$ for the quality of the expected grasp.
+Using these expected deviations we then derive an upper bound $b$ for the expected deviation from the quality of the expected grasp.
 
 \[
-  ||\Delta n_i|| =  \int_{\mathbb{B}(\bar{\textbf{n}_i})} ||\textbf{k} - \bar{\textbf{n}_i}|| p(\textbf{n}_i = \textbf{k}) d\textbf{k}
+  ||\Delta n_i|| =  \int_{\mathbb{S}^1} ||\textbf{v} - \bar{\textbf{n}_i}|| p(\textbf{n}_i = \textbf{v}) d\textbf{v}
 \]
@@
 \[
-  ||\Delta c_i|| =  \int_{\mathbb{B}(\bar{\textbf{c}_i)}} ||\gamma(t) - \bar{\textbf{c}_i}|| p(\textbf{c}_i = \textbf{k}) dt
+  ||\Delta c_i|| =  \int_{\mathbb{R}} ||\gamma(t) - \bar{\textbf{c}_i}|| p(\textbf{c}_i = \textbf{v}) dt
 \]
@@
  \begin{align*}
-b_i &= (1+\tau)||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| \\
+b_i &= (1+\tau)(||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| )\\
 \end{align*}
@@
 \begin{align}
-b(\zeta)  = \max_{i} b_i(\zeta)
+b  = \max_{i} b_i
 \end{align}
@@
 we turn to the general case.
-$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
+$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b$ and $\lambda(x)$ is bounded.
 Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
-We can ensure that is true.
 
@@
 \[
-  f(x) = f(x_0) + <R(x),x-x_0>
+  f(x) = f(x_0) + \langle R(x),x-x_0 \rangle
 \]
@@
 \[
-  |f(x)-f(x_0)| = |<R(x),x-x_0>| \leq L |x-x_0|
+  |f(x)-f(x_0)| = |\langle R(x),x-x_0 \rangle| \leq L |x-x_0|
 \]
@@
 Since we are currently working in 2D, there is no need to approximate the friction cone and the Ferrari-Canny is equal to the true grasp quality.
-What that means is that one could look at the analytical derivative of the active facet and use that to bound the metric.
-Looking at a single facet on the convex hull computed by Ferrari-Canny, one simply computes the derivative of the function $h(W,\textbf{z},\tau)$, where $h$ returns the absolute distance to the origin $d$ from the facet described by the input parameters.
+What that means is that one could look at the analytical derivative of the closest facet and use that to bound the metric.
+Looking at a single facet on the convex hull computed during Ferrari-Canny, one simply computes the derivative of the function $h(g)$, where $h$ returns the absolute distance to the origin $d$ from the facet described by
+the input parameters.
+If a single facet is the closest facet to the origin, then the gradient of the Ferrari-Canny metric at that point is the gradient of the distance of that facet to the origin, calculated using the chain rule.
 
-While we can compute the derivative using symbolic software \cite{SymPy}, it is still on going work to quickly determine either the set $U$ that the bound is valid or supremum of the derivative in a given set.
+While we can compute the derivative using the computer algebra system sympy \cite{SymPy}, it is still on going work to quickly determine either the set $U$ that the bound is valid or supremum of the derivative in a given set.
 
@@
 While we work on the tightening the bound, we will present a metric that should give an intuitive idea of what is import in our grasp metric.
-Our grasp metric currently returns $Q(\bar{g})$ and an upper bound $b$ on the expected change in grasp.
+Our grasp metric currently returns $Q(\bar{g})$ and an upper bound $b$ on the expected change in grasp quality.
 Ideally we want to rate grasps by the highest value $Q_l = Q(\bar{g}) - b$, thus being the lowest quality given the bound.
@@
 Currently though the two values $Q(\bar{g})$ and $b$ are two different magnitudes, but both are informative.
-We can approximate a the effect of a tighter bound by simply projecting both $Q(\bar{g})$ and $b$ to the unit ball, then subtracting.
+We can heuristically approximate a the effect of a tighter bound by simply projecting both $Q(\bar{g})$ and $b$ to the unit ball, then performing the subtraction.
 
@@
 The qualitative results for surface normals and contacts can be found in Figures \ref{fig:Contact_Dist} and \ref{fig:Normal_Dist} respectively.
-We present the numerical comparison with KL-Divergence in Table 1, as you can see the distributions are very closely related.
+We present the numerical comparison with KL-divergence in Table 1, as you can see the distributions are very closely related.
 
-\begin{table}[ht!]
+\begin{table}[h]
         \begin{tabular}{ l | c c c}
@@
         \hline \\
-        p($\textbf{n}_i$ )& 0.35 & 0.12 & 0.16 \\
+        p($\textbf{n}_i$)& 0.35 & 0.12 & 0.16 \\
         \hline 
@@
 
-\vspace*{-20pt}
+        \vspace*{-10pt}
 \end{table}
 
-\begin{figure}[ht!]
+\begin{figure}[h]
 \centering
@@
 \includegraphics[scale = 0.3]{figures/Slide09.jpg} \includegraphics[scale = 0.3]{figures/Slide10.jpg}
-\caption{Example grasps on the provided dataset with the histrograms of grasp quality given the uncertainity}
+\caption{Example grasps on the provided dataset with the histograms of grasp quality given the uncertainity}
 \vspace*{-10pt}
@@
         \hline \\
-         $\bar{Q(g)}$ & -0.003 & 0.022 & 0.000 &  0.018\\
+        $E[Q(p(g))]$ & -0.003 & 0.022 & 0.000 &  0.018\\
         \hline \\

### 2014-08-01 paper.tex
Added references improved writing

@@
 \vspace{10pt}
- A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
 Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}.
@@
 \ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.
+A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
 However, only recently have people started looking into a metric's robustness to uncertainty.
-Prior work by Zheng et al \cite{zheng2005}, looked at how to efficiently include uncertainty in friction coefficient and movement of gripper arm.
-However, they assumed a known surface of the object.
 
@@
 In order to improve the tightness of these bounds and thus improve our algorithm, we show initial investigations into calculating gradients for Ferrari-Canny in order to find very tight locally Lipschitz bounds.
-We present a heuristic algorithm based off of the previous algorithm that normalizes the
+We present a heuristic algorithm based off of the previous algorithm that normalizes the looser bound and quality of expected values and ranks by the difference between them.
 
@@
 More closely related to our approach is the work of Christopoulos and Schrater \cite{christopoulos2007handling}.
-They use a spline representation for uncertainty and sample from a distribution of losing force closure, their approach though is limited to two contacts.
-Our method looks at not only force closure, but provides a lower bound on the Ferrari-Canny metric within some user set distributions.
+They use a spline representation for uncertainty and measure the probability of losing force closure, their approach though is limited to two contacts.
+Our method looks at not only force closure, but provides the quality of the expected grasp and an upper bound on the expexted change from that quality.
 
@@
 \cite{dragiev2011} .
+The utilization of uncertainity around an implicit surface allows us to compute explicit distributions on contacts and surface normals, which to our knowledge has not been done formally.
 
@@
 
-Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006gaussian}.
+Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2010gaussian}.
 In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}$, $\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
@@
 A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2006gaussian}:
+Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
 \begin{align}
@@
 The measurement noise parameter $\sigma$ is usually estimated based on a model of the sensor used to collect measurements
-The vector of remaining hyperparameters $\boldsymbol{\theta} = \{\nu, \lambda_1,\ldots,\lambda_d\}$ is optimized during the training process by maximizing the log-likelihood $p(\by|\mX,\boldsymbol{\theta})$, usually using gradient descent \cite{rasmussen2006gaussian}.
+The vector of remaining hyperparameters $\boldsymbol{\theta} = \{\nu, \lambda_1,\ldots,\lambda_d\}$ is optimized during the training process by maximizing the log-likelihood $p(\by|\mX,\boldsymbol{\theta})$, usually using gradient descent \cite{rasmussen2010gaussian}.
 The log-likelihood function is subject to local maxima, and therefore the hyperparamter search often involves a search over the maxima found from several random initializations of the hyperparamters.
-
-\subsection{Training}
-Given the hyperparameters, the training phase consists of evaluating the vector 
-\begin{equation}
-\alpha = (K + \sigma^2 I)^{-1}\by,
-\end{equation}
-which needs the inversion of a $n \times n$ matrix $(K + \sigma^2I)$.
-Direct computation of the inverse of the symmetric matrix requires $O(n^3)$ operations and $O(n^2)$ storage, which makes it impractical for real-world applications consisting of thousands of data points.
-
-For larger systems, it is more efficient to solve the system
-\begin{equation}
-	\tilde{K}\alpha = \by, ~\text{where} ~\tilde{K} = (K + \sigma^2I),
-\end{equation}
-using iterative methods.
-Since $\tilde{K}$ is symmetric and positive-definite, the conjugate gradient (CG) method or an incomplete Cholesky factorizatoin can be used to iteratively solve the equation to some error tolerance \cite{gibbs1997}.
-The computational complexity of the CG method is $O(kdn^2)$ where $d$ is the dimensionality of the data and $k$ iterations of the CG method are required for convergence.
-Fast approximate matrix-vector products using the Improved Fast Gaussian Transform (IGFT) can reduce the complexity of computing the $\alpha$ vector to $O(n)$ for the squared exponential kernel \cite{raykar2007}.
-Alternatively Fast Multipole Methods can be used to reduce the complexity of computing the kernel matrices and vectors to $O(n \log n)$ \cite{gumerov2005fast}.
-
-A large variety of methods haven been proposed for further speeding up the GP training phase including, but not limited to, training on a subset of data chosen either randomly or using an information-theoretic criterion, or local methods that only rely on neighboring data points for making predictions in a given region of space.
-The subset selection methods can be separated into two groups: subset of data (SoD) and subset of regressors (SoR) \cite{quinonero2005unifying}.
-In SoD approaches, a criterion is used to select an `active' subset of training data to be used in inference, and all other `inactive' training data is discarded.
-In SoR approaches the relation of the inactive points to the active points is retained by replacing the kernel function with the alternative function
-\begin{equation}
-	k(\textbf{x}_i,\textbf{x}_j) = k(\textbf{x}_i,\textbf{u}) K_{\textbf{u}, \textbf{u}}^{-1} k(\textbf{u},\textbf{x}_j).
-\end{equation}
-\noindent We refer the reader to \cite{chalupka2013} for an extensive comparison of these methods.
-In this paper we consider objects that can be represented with few enough points that computational tractability is not an issue, and we defer the question of which methods are most effective for the special case of constructing GPIS to future work.
 
@@
 We can heuristically approximate a the effect of a tighter bound by simply projecting both $Q(\bar{g})$ and $b$ to the unit ball, then performing the subtraction.
+Thus we define the following:
+
+\begin{align*}
+Q_h = \frac{Q(\bar{g})}{||Q(\bar{g})||} - \frac{b}{||b||}
+\end{align*}
 
@@
         \hline 
-        $h$ & 0.025 & 0.016 & 0.017 & 0.097 \\
+        $Q_h$ & -0.031 & 0.451 & -0.530 & -0.640 \\
         \hline 

### 2014-09-17 paper.tex
added sampling and adaptive sampling

@@
 \usepackage{amsmath,amssymb}
+
 \usepackage{tikz,hyperref,graphicx,units,subfig}
+\usepackage{benktools}
+
 \usepackage{sidecap,wrapfig}
@@
 \title{\LARGE \bf
-Grasp Distributions and a Metric for Shape Uncertainty with Gaussian Process Implicit Surface Representation (Draft: Not Finished Work) }
+Efficient Sampling for Grasp Quality Evaluation with Gaussian Process Implicit Surface Representation }
 
-\author{Michael Laskey*, Zoe McCarthy*, Florian T. Pokorny, Jeff Mahler, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
+\author{Michael Laskey, Zoe McCarthy, Florian T. Pokorny, Jeff Mahler, Sachin Patil,\\ Danica Kragic, Jur Van Den Berg, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
 
@@
 \vspace{10pt}
+
+\todo{Write a better Intro, needs to have a better sell}
 Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}.
@@
 
-We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
-We are working to extend this metric to incorporate shape uncertainty, and to do that we analyze the resulting distributions over grasp parameters induced by the shape uncertainty.
+We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
+Gaussian Processes provide a formal way to incorporate uncertainty, however this sophisticated representation presents new challenges for evaluating the expected grasp quality.
+The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
+
+We assume that a robot's $m$ grippers approach the grasped object along straight lines (which we call lines of action), and analyze how this grasping model interacts with the probability distribution on shapes described by a Gaussian Process Implicit Surface (GPIS).
+We calculate and visualize the theoretical probability distributions on grasp contact points and normals and the expected center of mass induced by the GPIS and line of action.
+Then demonstrate how sampling from this explicit grasp distribution can be used to reduce the complexity associated with Monte-Carlo integration of the expected grasp quality over the distribution of shapes.
+
+We also treat the problem of finding the best grasp in a set of proposed grasps as a n-arm bandit problem and propose an $\epsilon$ - greedy policy for finding the best grasp in the set in an anytime like manner.
 
@@
 
-\section{Contributions To Date}
-We assume that a robot's $m$ grippers approach the grasped object along straight lines (which we call lines of action), and analyze how this grasping model interacts with the probability distribution on shapes described by a Gaussian Process Implicit Surface (GPIS).
-We calculate and visualize the theoretical probability distributions on grasp contact points and normals and the expected center of mass induced by the GPIS and line of action.
-We empirically validate our calculated distributions by measuring their KL-divergence from the empirical probability distributions obtained by sampling from the GPIS distribution and calculating the contact point along the line of action and the corresponding normal for several example shapes.
-
-We show ongoing work in adapting the Ferari-Canny grasp metric to this setting.
-We present an algorithm to compute an upper bound on the expected deviation in grasp quality from the metric evaluated at a single grasp using a recent result that Ferrari-Canny is Lipschitz continuous \cite{pokorny2013classical}.
-In order to improve the tightness of these bounds and thus improve our algorithm, we show initial investigations into calculating gradients for Ferrari-Canny in order to find very tight locally Lipschitz bounds.
-We present a heuristic algorithm based off of the previous algorithm that normalizes the looser bound and quality of expected values and ranks by the difference between them.
+\todo{Get an actual Kinect Image}
 
@@
 The utilization of uncertainity around an implicit surface allows us to compute explicit distributions on contacts and surface normals, which to our knowledge has not been done formally.
+
+\todo{Write about n-arm bandit literature}
 
@@
  %We also define the  level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
+
+\todo{Get a better figure for line of action model}
 
@@
 
-We recall the quantity CDF$(f(x))(0) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ as the cumulative distribution function of $f(x)$ evalutated at 0 and note that it is equal to the probability that $x$ is interior to the surface under the current observations.
+We recall the quantity CDF$(f(x))(0) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ as the cumulative distribution function of $f(x)$ evaluated at 0 and note that it is equal to the probability that $x$ is interior to the surface under the current observations.
 We assume that the object has uniform mass density and then CDF$(f(x))(0)$ is the expected mass density at $x$.
@@
 
-\section{Probabilistic Bound on Grasp Metric}
-\label{sec:bound}
-Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we would like to prove an extension to give a probabilistic bound on the change in grasp quality.
+\section{Sampling from a GPIS}
+Prior work that consider shape uncertainty purposed sampling from distribution on the shape itself \cite{kehoe2012toward}.
+However, with a more complicated model on the shape distribution this technique would scale poorly.
 
-With a distribution on $p(g)$ we then use recent results on a Lipschitz constant for the Ferrari-Canny Metric \cite{pokorny2013classical} to provide $b$ or an upper bound on the change in grasp quality from the expected deviation in grasp and the quality of the expected grasp $Q_l^-(\bar{g})$, where $\bar{g} = ( \bar{\textbf{c}}_1,...,\bar{\textbf{c}}_m,\bar{\textbf{n}}_1,...,\bar{\textbf{n}}_m,\bar{\textbf{z}},\tau )$.
+Given a work space $\mathcal{R}^{n\times n}$, the complexity of sampling a work space is show to be $O(n^6)$.
+This is due to the necessary inversion of a $n \times n$.
+In typical cases $n$ would be on the order of 100 making this very computationally intensive even in the 2D case.
 
-We restate several of their results here:
+If we instead sample from our proposed grasp distributions and use a line of action that is roughly equal to $n$, the complexity can be rewritten as $O(T*n^3)$,  where $T$ is the number of grasps that are evaluated.
 
-\subsection{Prior Work: Derivation of Lipschitz Constant }
+\section{Adaptive Sampling for Grasp Selection}
+In a possible grasping scenario, one would be presented with a set $G$ of $T$ grasps.
+The goal would be to identify, which one is the best grasp given the set $G$ and for each grasp the $p(g)$.
+While a naive approach to solving this problem would be to simply perform Monte-Carlo integration on each one and compute the expected grasp quality, we propose treating the problem as an n-arm bandit problem and forming a policy for selecting which grasp to sample.
+The motivation behind this is due to the expensive evaluation that each Ferrari-Canny computation takes \cite{ferrari1992}.
 
-We follow the notation of \cite{pokorny2013classical} except that the friction coefficient is $\mu$ in that paper and $\tau$ in this paper since we use $\mu$ to refer to mean vectors.  
-We re-state some of their central theorems for our use here.
-For more detail, refer there.
-$Q(g)$ is the exact $L^1$ grasp quality.
-It is denoted by the following
+An n-arm bandit problem can be defined as follows: an agent is presented with a $n$ slot machines and receives a reward each time a lever is pulled that is drawn from the distribution associated with the slot machine.
+The goal of the agent is to maximize the expected reward received, by balancing exploration and exploitation \cite{barto1998reinforcement}.
 
-\begin{align}
-  Q(g) &= \mbox{max}(0,q(g)) = -d(0,\mbox{Conv}(\{0\} \cup S(g))\\
--d(0,S) &= min_{||z|| = 1} h_{S(z)}\\
-h_{S(z)} &= \mbox{sup}_{s\in S}\langle s,z\rangle\\
-\end{align}
+For selecting grasps we use an $\epsilon$-greedy policy, where the greedy action is selected with probability $1-\epsilon$ and a random action is chosen otherwise.
+The greedy option is defined as the grasp with the highest approximate upper confidence bound $v$, which is computed via the following \cite{mc}
 
-We denote the Ferrari-Canny version, which approximates the friction cone by a linearized set of wrenches\cite{ferrari1992}, as $Q^-_l(g)$.
-The next theorem shows that the linearized wrench set used in Ferrari-Canny calculates a lower bound on $Q(g)$.\\
-
-\begin{theorem}
-  \cite{pokorny2013classical}
-For any grasp g, we have $0 \leq Q_l^-(g) \leq Q(g)$.
-Furthermore, $||Q(g) - Q^-_l(g)|| \rightarrow 0$ as $l \rightarrow \infty$ when $Q_l^-(g)$ is computed using a uniform approximation of the friction cones with $l$ edges. \\
-\end{theorem}
-
-The next theorems are used to show that $Q$ is Lipschitz continuous.
-
-\begin{theorem}
-\label{lemma35}
-  \cite{pokorny2013classical}
-For $w \in \mathbb{R}^3$, we have, for $n \in \mathbb{S}^2$ and for friction coefficient $\mu > 0$,
-
-\begin{align}
-\mbox{sup}_{x \in C(n)} \langle x,w \rangle = \langle n,w \rangle + \tau||n \times w||
-\end{align}
-
-Hence, for $u = (a,b) \in \mathbb{R}^3 \times \mathbb{R}^3 = \mathbb{R}^6$, we have
-
-\[
-h_{W_i(g)}(a,b) =
- \langle n_i,a+b\times(c_i-z)\rangle +
-\]
-\begin{align}
- +\tau ||n_i \times (a+b\times(c_i-z))||
-\end{align}
-
-\end{theorem}
-
-\begin{theorem}
-  \cite{pokorny2013classical}
-We have \\
-
-\begin{align}
-q(g) 
-=
-\min_{u\in \mathbb{R}^6, ||u|| =1} h_{S(g)}(u) 
-=
-\end{align}
-\[
-\min_{u\in \mathbb{R}^6, ||u|| =1} \max_{i=1,...,m} h_{W_i(g)}(u),
-\]
-
-where $h_{S(g)}$ is convex on $\mathbb{R}^6$.
-$q$ is invariant under fixed translation of the grasp center and contact positions.
-Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$.
-Then $q$ is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1, \dots, c_m,n_1, \dots,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where we use distance measure
-
-\[
-  d(g,g') = \sum_i ||(c_i-z)-(c_i'-z')|| + \sum_i ||n_i - n_i'||.
-\]
-
-We hence have
-
-\[
-|q(g) - q(g')| \leq Ld(g,g'),\  \forall g,g' \in X.
-\]
-
-Since $Q(g) = \max(0,q(g))$, $Q$ is also Lipschitz continuous with the same constant $L$ on $X$. 
-\end{theorem}
-
-Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|\langle n_i,a+b\times (c_i-z)\rangle - \langle n_i',a+b\times(c_i'-z')\rangle|+\mu|||n_i \times (a+b \times (c_i -z))|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}.
-By using the following facts $||a|| \leq 1$, $||b|| \leq 1$, $||v \times w || \leq ||w||||v||$, $|\langle v,w\rangle | \leq ||v||||w||$, we obtain:
-
-\begin{align*}
-|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
-					&+ ||(c_i - z)-(c_i'-z')|| \\
-					&+ \tau(||n_i - n_i'||(1+||c_i - z||)\\
-					&+||(c_i - z)-(c_i'-z')||)
-\end{align*}
-
-\subsection{Upper Bound on Expected Deviation of Grasp Quality}
-Given a the distributions on a line of action, $p\big(\textbf{n}_i = \textbf{v}\big)$ and $p\big(\textbf{c}_i=\gamma(t) \big)$ and the expected values $\bar{\textbf{c}_i}$ and $\bar{\textbf{n}_i}$.
-We are interested in finding the expected deviations for the two parameters, $||\Delta n_i||$ and  $||\Delta c_i||$.
-Using these expected deviations we then derive an upper bound $b$ for the expected deviation from the quality of the expected grasp.
-
-\[
-  ||\Delta n_i|| =  \int_{\mathbb{S}^1} ||\textbf{v} - \bar{\textbf{n}_i}|| p(\textbf{n}_i = \textbf{v}) d\textbf{v}
-\]
-
-\[
-  ||\Delta c_i|| =  \int_{\mathbb{R}} ||\gamma(t) - \bar{\textbf{c}_i}|| p(\textbf{c}_i = \textbf{v}) dt
-\]
-
-We now write the above bound as follows for a given line of action $i$:
-
- \begin{align*}
-|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq (1+\tau)||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| \\
-  \end{align*}
-
-Here $\bar{\textbf{r}}_i = \bar{\textbf{c}}_i - \bar{\textbf{z}}_i$. For convenience we rewrite the bound on a given set of grasp parameters as :
-
- \begin{align*}
-b_i &= (1+\tau)(||\Delta \textbf{n}_{i}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{c}_{i}}|| )\\
-\end{align*}
-
-To provide an upper bound overall contact parameters we introduce the following:
-
-\begin{align}
-b  = \max_{i} b_i
-\end{align}
-
-To prove if  this bound is preserved on
-
- \begin{align}
- q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
- \end{align}
-
-we turn to the general case.
-$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b$ and $\lambda(x)$ is bounded.
-Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
-
-\subsection{Tightening Bounds on Change in Grasp Quality}
-
-Experimentally we found the Lipschitz bound to be looser than we would like, despite the fact that it is a local bound.
-We are currently working on tightening the bound by using the following property:
-
-For a $x,x_0$ in a bounded set $U$ in $\mathbb{R}^n$, for a given $f(x):\mathbb{R}^n \rightarrow \mathbb{R}$.
-
-\[
-  f(x) = f(x_0) + \langle R(x),x-x_0 \rangle
-\]
-
-\[
-  R(x) = \int_0^1 \frac{d}{dx}f(x_0+t(x-x_0)) dt
-\]
-
-Then let $L = \mbox{sup}_{s \in U} |\frac{df(x)}{dx} |$, so $|R(x)| \leq L$ and
-
-\[
-  |f(x)-f(x_0)| = |\langle R(x),x-x_0 \rangle| \leq L |x-x_0|
-\]
-
-Since we are currently working in 2D, there is no need to approximate the friction cone and the Ferrari-Canny is equal to the true grasp quality.
-What that means is that one could look at the analytical derivative of the closest facet and use that to bound the metric.
-Looking at a single facet on the convex hull computed during Ferrari-Canny, one simply computes the derivative of the function $h(g)$, where $h$ returns the absolute distance to the origin $d$ from the facet described by
-the input parameters.
-If a single facet is the closest facet to the origin, then the gradient of the Ferrari-Canny metric at that point is the gradient of the distance of that facet to the origin, calculated using the chain rule.
-
-While we can compute the derivative using the computer algebra system sympy \cite{SymPy}, it is still on going work to quickly determine either the set $U$ that the bound is valid or supremum of the derivative in a given set.
-
-\subsection{Approximation of True Metric}
-While we work on the tightening the bound, we will present a metric that should give an intuitive idea of what is import in our grasp metric.
-Our grasp metric currently returns $Q(\bar{g})$ and an upper bound $b$ on the expected change in grasp quality.
-Ideally we want to rate grasps by the highest value $Q_l = Q(\bar{g}) - b$, thus being the lowest quality given the bound.
-
-Currently though the two values $Q(\bar{g})$ and $b$ are two different magnitudes, but both are informative.
-We can heuristically approximate a the effect of a tighter bound by simply projecting both $Q(\bar{g})$ and $b$ to the unit ball, then performing the subtraction.
-Thus we define the following:
-
-\begin{align*}
-Q_h = \frac{Q(\bar{g})}{||Q(\bar{g})||} - \frac{b}{||b||}
-\end{align*}
+\begin{equation}
+v = \bar{X} + \frac{1.96 \bar{\sigma}_N}{\sqrt{n}}
+\end{equation}
 
@@
 
-To validate our theoretical caculations, we compared them to empirical distributions found via Monte-Carlo Sampling.
+\subsection{Validation of Grasp Distributions}
+
+To validate our theoretical calculations, we compared them to empirical distributions found via Monte-Carlo Sampling.
 The qualitative results for surface normals and contacts can be found in Figures \ref{fig:Contact_Dist} and \ref{fig:Normal_Dist} respectively.
@@
 
-To better understand the quality of grasp that our proposed metric will find, we present results on a variety of grasps as shown in Fig.
-\ref{fig:Grasps}.
-The numerical values in terms are presented in Table 2.
+\subsection{Sampling from Grasps Vs. Shape}
+We first demonstrate that sampling from the two different method converges to near the same expected value, see Fig.
+\ref{fig:sampling_convergence}.
+After confirming the distributions converge to the same value we show the computational complexity in Fig.
+\ref{fig:speed_dif} of the two methods for evaluating 100 grasps on an $n \times n$ grid.
 
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide09.jpg} \includegraphics[scale = 0.3]{figures/Slide10.jpg}
-\caption{Example grasps on the provided dataset with the histograms of grasp quality given the uncertainity}
+\includegraphics[scale = 0.3]{figures/Slide11.jpg}
+\caption{Left: Sampling from grasp distributions
+Right: Sampling from distribution on shape}
 \vspace*{-10pt}
-\label{fig:Grasps}
+\label{fig:sampling_convergence}
 \end{figure}
 
-\begin{table}[ht!]
-        \begin{tabular}{ l | c c c c}
-         Distribution & \bf Marker & \bf Tape & \bf Loofa & \bf Stapler \\ 
-        \hline \\
-        $E[Q(p(g))]$ & -0.003 & 0.022 & 0.000 &  0.018\\
-        \hline \\
-        var $Q(g)$ & 0.025 & 0.016 & 0.017 &  0.054\\
-        \hline 
-        $Q(\bar{g})$ & 0.030 & 0.024 & -0.012 & 0.014\\
-        \hline 
-        $b$ & 1.634 & 0.540 & 2.220 & 2.600 \\
-        \hline 
-        $Q_h$ & -0.031 & 0.451 & -0.530 & -0.640 \\
-        \hline 
-        \end{tabular}
-        \caption{A comparison of all the different values that characterize a grasp.}
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide12.jpg}
+\caption{Comparison of the computational complexity of the two methods with respect to the work space dimensions}
+\vspace*{-10pt}
+\label{fig:speed_dif}
+\end{figure}
 
-\vspace*{-20pt}
-\end{table}
+\subsection{Adaptive Sampling Technique}
 
+We consider the problem of selecting the best grasp out of a set $G$ given a fix number of iterations $I$.
+For our experiments we look at selecting the best grasp out of a size of $|G| = 100$ and given a fix iteration limit of $I = 1000$.
+We show the results for both the marker and tape, in Fig.
+\ref{fig:marker_bandit} and Fig.
+\ref{fig:tape_bandit} respectively.
+We note that in both cases the policy was able to select the best grasp without sufficiently sample the set of possible grasps.
+
+\todo{Add experiments demonstrating ordering and trials over large number of runs, also fix visualizations}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide09.jpg}
+\caption{Left: $\epsilon$-greedy policy for sampling (Top 10 grasps plotted)
+Right: Monte-Carlo Sampling for 1000 iterations (Top 10 grasps plotted)}
+\vspace*{-10pt}
+\label{fig:marker_bandit}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide10.jpg}
+\caption{Left: $\epsilon$-greedy policy for sampling (Top 10 grasps plotted)
+Right: Monte-Carlo Sampling for 1000 iterations (Top 10 grasps plotted)}
+\vspace*{-10pt}
+\label{fig:tape_bandit}
+\end{figure}
+
+\todo{Write Conclusion}
 \bibliographystyle{ieeetr}

### 2014-09-17 paper.tex
fixed introduction and added related work

@@
 
-\todo{Write a better Intro, needs to have a better sell}
-Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}.
-As shown in Fig.
-\ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.
-A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
-However, only recently have people started looking into a metric's robustness to uncertainty.
+A robot in the wild is expected to encounter an object, grasp and manipulate it.
+In order to do so it must use its noisy sensor data to build a model of the object, for which to plan grasps on.
+While most grasp planning algorithms currently assume a polygonal mesh \cite{grasp_it}, their is no easy way to handle the uncertainty associated with partial visibility, sensor noise and surface properties such as specularity and transparency.
+We thus propose a Bayesian approach to this problem to formally go from point cloud to an uncertainty representation using Gaussian Processes.
 
-We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
-Gaussian Processes provide a formal way to incorporate uncertainty, however this sophisticated representation presents new challenges for evaluating the expected grasp quality.
-The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
+An alternative to polygonal mesh representation is the signed distance field, which is zero-valued at the object surface, positive valued outside the object, and negative valued in the object interior \cite{newcombe2011kinectfusion}.
+We look at encoding uncertainty into this model with a Bayesian representation known as Gaussian Process Implicit Surface (GPIS).
+The key idea behind GPIS is to represent shape uncertainty as a distribution overall possible SDFs that could represent the shape.
+For example, GPIS-based models have large variance where data is known to be unreliable (e.g.
+occlusions, specularities) and lower variance where measurements are more reliable.
+
+ While a GPIS is a formal method for representation of uncertainty and can offer continuous function that can be used for local grasp optimization \cite{jeff_paper}.
+Evaluation of grasp quality through techniques like Monte-Carlo Integration on a GPIS requires an exhaustive sampling of SDFs, which is extremely computationally expensive and not suited for a real time application.
+We purpose an alternative to sampling SDFs by computing a distribution on explicit grasp parameters and performing Monte-Carlo integration on that instead.
 
@@
 
-We also treat the problem of finding the best grasp in a set of proposed grasps as a n-arm bandit problem and propose an $\epsilon$ - greedy policy for finding the best grasp in the set in an anytime like manner.
+To further improve the efficiency of grasp quality evaluation, for a given set of grasps.
+We demonstrate that formulating the problem as an n-arm bandit problem allows us to formulate a policy that intelligently select which grasps to sample next.
+N-arm bandit problems look at the situation of an agent being presented with N slot machines, where each slot machine gives a reward from some unknown distribution.
+The goal of the agent is to efficiently explore the slot machines and then maximize reward by exploiting the best one.
+In our problem each lever pull is an evaluation of a grasp metric (e.g.
+Ferrari-Canny), which is computationally expensive.
+Thus finding a policy to minimize evaluations is essential for real time applications.
 
@@
 \section{Related Work}
+Many different methods for representing objects exist, most of which were developed in the graphics community for making rendering and simulations computationally tractable; see \cite{van2014computer} for an overview.
+Polygonal mesh models are the most common representation in robotics but these models usual assume perfectly known geometry.
+Extension of mesh models to include  uncertainty generally assume independent noise on the vertex locations, ignoring noise correlation \cite{kehoe2012toward}.
+As an alternative, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric},\cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}.
+These representation include a confidence estimate based on a sensor noise model, but they cannot estimate the location in the surface regions where no measurements were obtained or represent correlations between voxels \cite{curless1996volumetric}.
 
-While a variety of grasp metrics have been proposed, few explicitly looked at uncertainty in grasp parameters.
-Zheng et al.
-looked at friction and contact point uncertainty \cite{zheng2005}.
-He computed the maximum distance a contact point was allowed to deviate from its expected grasp, while maintaining force closure.
-Kehoe et al.
-looked at shape uncertainty for push grasps, however this was limited to parallel jaw grippers and only measured the probability of force closure \cite{kehoe2012toward}.
-More closely related to our approach is the work of Christopoulos and Schrater \cite{christopoulos2007handling}.
-They use a spline representation for uncertainty and measure the probability of losing force closure, their approach though is limited to two contacts.
-Our method looks at not only force closure, but provides the quality of the expected grasp and an upper bound on the expexted change from that quality.
+Choosing grasps given a surface representation of an object usually focuses on improving grasps for a  object shape \cite{ferrari1992}.
+Past work on grasping has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
+Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
+for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this assumed extruded polygons with independent noise at each vertex.
+Christopoulus et al.
+sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainity, but did not have a formal method for representing uncertainity and only calculated the probability of achieving force closure.
+.
 

### 2014-09-30 paper.tex
changed everything

--- 2014-09-17 paper.tex
@@
 \title{\LARGE \bf
-Efficient Sampling for Grasp Quality Evaluation with Gaussian Process Implicit Surface Representation }
+Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]}
 
-\author{Michael Laskey, Zoe McCarthy, Florian T. Pokorny, Jeff Mahler, Sachin Patil,\\ Danica Kragic, Jur Van Den Berg, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
+\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
 
@@
 
+\begin{abstract}
+Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.
+Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
+The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$..
+We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp.
+We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.
+\end{abstract}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{Write a better Intro, needs to have a better sell}
-Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}.
-As shown in Fig.
-\ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.
-A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
-However, only recently have people started looking into a metric's robustness to uncertainty.
+\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
+Consider a robot packing boxes in a shipping warehouse environment.
+The robot will frequently encounter objects that it has not seen before.
+The robot will have to plan stable grasps without any prior information other than its sensor data.
+As seen in Fig.
+\ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations.
+Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
+To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..
 
-We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
-Gaussian Processes provide a formal way to incorporate uncertainty, however this sophisticated representation presents new challenges for evaluating the expected grasp quality.
-The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
-
-We assume that a robot's $m$ grippers approach the grasped object along straight lines (which we call lines of action), and analyze how this grasping model interacts with the probability distribution on shapes described by a Gaussian Process Implicit Surface (GPIS).
-We calculate and visualize the theoretical probability distributions on grasp contact points and normals and the expected center of mass induced by the GPIS and line of action.
-Then demonstrate how sampling from this explicit grasp distribution can be used to reduce the complexity associated with Monte-Carlo integration of the expected grasp quality over the distribution of shapes.
-
-We also treat the problem of finding the best grasp in a set of proposed grasps as a n-arm bandit problem and propose an $\epsilon$ - greedy policy for finding the best grasp in the set in an anytime like manner.
+While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
+This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}.
+To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.
 
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide02.jpg}
-\caption{An example of the noise from a Kinect-like sensor}
+\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
+\caption{\footnotesize
+Left: HD image of a common measuring cup from in a household environment.
+Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
 \vspace*{-10pt}
@@
 
-\todo{Get an actual Kinect Image}
+Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}.
+Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
+Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}.
+We constrain the contact points by considering the approach trajectory of a gripper.
+Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory.
+In light of this our contributions are the following:
+
+\begin{enumerate}
+	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
+	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
+	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
+\end{enumerate}
 
@@
 
-While a variety of grasp metrics have been proposed, few explicitly looked at uncertainty in grasp parameters.
-Zheng et al.
-looked at friction and contact point uncertainty \cite{zheng2005}.
-He computed the maximum distance a contact point was allowed to deviate from its expected grasp, while maintaining force closure.
-Kehoe et al.
-looked at shape uncertainty for push grasps, however this was limited to parallel jaw grippers and only measured the probability of force closure \cite{kehoe2012toward}.
-More closely related to our approach is the work of Christopoulos and Schrater \cite{christopoulos2007handling}.
-They use a spline representation for uncertainty and measure the probability of losing force closure, their approach though is limited to two contacts.
-Our method looks at not only force closure, but provides the quality of the expected grasp and an upper bound on the expexted change from that quality.
+ Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
+Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
+for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.
+Christopoulo et al.
+sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.
 
-The choice of using a Gaussian Process Implicit Surface to represent our uncertainty, stems from the fact that it provides a formal way to include various sources of noise in observations.
-Prior work has used uncertainty representation such as independent Gaussian noise on each vertex in a Polygonal mesh \cite{kehoe2012toward}.
-However, this doesn't provide a continuous function one can easily compute distributions on grasp parameters with.
-GPIS is also becoming more prevalent in the grasping community with recent work by Dragiev et al.
-\cite{dragiev2011} .
-The utilization of uncertainity around an implicit surface allows us to compute explicit distributions on contacts and surface normals, which to our knowledge has not been done formally.
+ The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual.
+Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}\cite{newcombe2011kinectfusion}\cite{hornung2013octomap}.
+Some exciting work done with GPIS representation are the following: Hollinger et al.
+used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
+Dragiev et al.
+showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
+Mahler et al.
+used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.
 
-\todo{Write about n-arm bandit literature}
+  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
+With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace.
+We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.
 
-\section{Gaussian Process Implicit Surfaces}
+Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}.
+While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}\cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
+Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}.
+Prior work by Kehoe et al.
+\cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed.
+To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}.
+Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.
+
+\section{Preliminaries and Problem Statement}
 
@@
 \subsection{Gaussian Process (GP) Background}
-
+GPs provide an infinite dimensional analogue of Multivariate
+Gaussian Distributions which allow us to model distributions over
+functions.
 Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2010gaussian}.
@@
 Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
-\begin{align}
-	p(f_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \label{eq:GPposterior} \\
-	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \label{eq:GPmean} \\
-	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) \label{eq:GPvar}
-\end{align}
+\begin{align*}
+	p(f_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
+	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
+	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
+\end{align*}
 where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
@@
 
-\begin{align*}
+\vspace{-2ex}
+\begin{align}
 	\text{cov}\left(f(\bx_i), f(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)
-\end{align*}
-
-\subsection{Kernel Selection}
-The choice of kernel is application-specific, since the function $k(\bx_i,\bx_j)$ is used as a measure of correlation between states $\bx_i$ and $\bx_j$.
-A common choice is the squared exponential kernel:
-\begin{equation}
-	k(\bx_i,\bx_j) = \nu^2\exp(-\frac{1}{2}(\bx_i - \bx_j)^{\intercal}\Lambda^{-1}(\bx_i - \bx_j))
-\end{equation}
-where $\Lambda= \text{diag}(\lambda_1^2,\ldots,\lambda_d^2)$ are the characteristic length scales of each dimension of $\bx$ and $\nu^2$ describes the variability of $f$.
-Other common kernels relevant to GPIS are the thin-plate splines kernel \cite{williams2007} and the Matern kernel \cite{bjorkman2013enhancing}.
-
-The measurement noise parameter $\sigma$ is usually estimated based on a model of the sensor used to collect measurements
-The vector of remaining hyperparameters $\boldsymbol{\theta} = \{\nu, \lambda_1,\ldots,\lambda_d\}$ is optimized during the training process by maximizing the log-likelihood $p(\by|\mX,\boldsymbol{\theta})$, usually using gradient descent \cite{rasmussen2010gaussian}.
-The log-likelihood function is subject to local maxima, and therefore the hyperparamter search often involves a search over the maxima found from several random initializations of the hyperparamters.
+	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
+	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
+\end{align}
 
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide03.jpg}
-\caption{Left: A surface represented as a Truncated Signed Distance Field (TSDF).
-Right: A GPIS reconstruction from noisy samples of the left surface's TSDF.}
+\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
+\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
+Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
+}
 \vspace*{-10pt}
@@
 
-\section{Problem Definition}
+For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability.
+Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
 
-%The objective of our algorithm is to provide a quality of the expected grasp, $Q_l^-(\bar{g})$ \cite{ferrari1992}, and a lower bound $b$ that is the expected deviation from the quality of the expected grasp.
+We construct a GPIS by learning a Gaussian Process to fit measurements of a signed distance field of an unknown object.
+Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
 
-We assume a bounded 2-d rectangular workspace $\mathcal{R}$.
-We parameterize a single grasp $g$ on an object with the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\textbf{z},\tau )$.
-We have an indexing set $I$ of $m$ point contacts and surface normal on the object: for $i \in I$ the contact is located at $c_i$ with surface normal $n_i$.
-The object has a center of mass $z$ and friction coefficient $\tau$.
-The line segment $\gamma(\cdot)$ has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig. 
+\subsection{Line of Action}
+Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
 \ref{fig:line_of_action}.
+A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
 
-We assume that the robot grippers move along the line of action until they make contact with the object and stop.
-Since we have uncertainty in the shape this induces a distribution on the grasp parameters subject to the line, hence $p(g) = ( p(\textbf{c}_1),...,p(\textbf{c}_m),p(\textbf{n}_1),...,p(\textbf{n}_m),\bar{\textbf{z}},\tau )$.
-We note that $\tau$ is considered known and $\bar{z}$ is the expected center of mass, not a full probability distribution.
-In section \ref{sec:distgrasp}, we demonstrate how to efficiently compute the distributions on contact points and surface normals and expected center of mass.
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide01.jpg}
+\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+\vspace*{-10pt}
+\label{fig:line_of_action}
+\end{figure}
+
+\subsection{Problem Definition}
+
+Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model and set of possible grasp plans $G$. We are interested in determining
+
+\begin{align}\label{eq:problem_def}
+\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
+\end{align}
+
+with respect to a chosen grasp metric Q.
+
+\section{Evaluating a Grasp}
+In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$.
+We will first discuss which grasp metric $Q$ we chose and then proceed into evaluating the expectation $E$ efficiently.
+
+\subsection{Grasp Metric}
+In their pioneering work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
+Importantly the magnitude of Q yields a measurement that allows one to rank grasps by their physical stability and evaluate the property of force-closure.
+Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
+
+The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$.
+Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+A wrench is defined as concatenation of a force and torque vector.
+If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
+Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}\cite{li1988task}.
+
+\subsection{Calculating the Expected Grasp Quality}
+Given a proposed grasp plan $\Gamma$, the expected grasp quality can be evaluated as follows:
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+E(Q(\Gamma)) = \int Q(g|S,\Gamma) p(S) dS
+\end{align}
+
+Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
+See Fig.
+\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
+For computational reasons we approximate the integral via Monte-Carlo Integration.
+We use importance sampling to draw from the distribution induced by GPIS and calculate the following
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 8.5cm, height= 5cm ]{figures/Slide13.jpg}
+\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
+\vspace*{-10pt}
+\label{fig:shape_samples}
+\end{figure}
+
+\begin{align*}
+E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
+\end{align*}
+
+To compute the above distribution we must draw samples from $p(S)$.
+In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$.
+Since this is a GPIS, we know the following
+
+\begin{align}\label{eq:joint_shape}
+p(S) = p(sd(\mathcal{W})) \sim N(\mu(\mathcal{W}),\Sigma(\mathcal{W}))
+\end{align}
+
+Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
+Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}.
+Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
+
+To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves.
+We recall that a grasp according to our metric is defined as the tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z \rbrace$.
+We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$.
+The distribution on a grasp is defined then as:
+
+\begin{align}\label{eq:joint_on_shape}
+p(g) = p\big(\textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m|\Gamma,\mu(x),\Sigma(x)\big)
+\end{align}
+
+We note here that we currently use the friction coefficient $\mu$ and the expected center of mass $\bar{z}$ as deterministic values.
+For grippers that do not approach along the same line of action (i.e.
+non-parallel jaw grippers) we make the assumption that each contact and normal pair is independent, or
+
+\vspace{-2ex}
+\begin{align}\label{eq:independence}
+p(g) = &\prod_{i=1}^mp\big(\textbf{c}_i,\textbf{n}_i|\gamma_i(t),\mu(x),\Sigma(x)\big)
+\end{align}
+
+We compute the expected grasp quality now as follows:
+
+\vspace{-2ex}
+\begin{align}\label{eq:grasp_sampling}
+E(Q(\Gamma)) = \sum_{i=1}^N Q(g_i) , g_i \in p(g)
+\end{align}
+
+We will now show how these distributions can be computed and how the complexity for evaluating a grasp is reduced from $O(n^6)$ to $O(n^3)$.
 
@@
 
- For the following derivations we introduce the following,
- $\theta(x) = ( \mu(x),\Sigma(x) )$, where $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS model \cite{rasmussen2006} .
+ To sample from $p(g)$, we need to compute the distributions associated with a line of action $p(n_i|c_i)p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ on each of the parameters: contact points $c_i$, surface normals $n_i$  and expected center of mass $\bar{z}$.
+ .
+\subsection{Distribution on Contact Points} 
+The probability distribution along the line $\gamma(t)$ is given by:
 
- To calculate $p(g)$, we assume a gripper contacts approaches along a parameterized line of action, or a 1-dimensional curve in the work space, defined by $\gamma(t)$.
-See Fig \ref{fig:line_of_action}, for a detailed illustration.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, these approach trajectories are then used to compute a distribution on grasp parameters.
-
- %We also define the  level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
-
-\todo{Get a better figure for line of action model}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide01.jpg}
-\caption{Parameterized Line of Action along an object}
-\vspace*{-10pt}
-\label{fig:line_of_action}
-\end{figure}
-%\textbf{TODO:MORE DESCRIPTIVE GRAPHIC}
-\subsection{Distribution on Contact Points} 
-In our implementation we discretize along the line $\gamma(t)$ evenly but write the derivation in continuous form for generality.
-The probability distribution along the line $\gamma(t)$ is given by the following:
-
-\begin{equation}
-p\big(f(\gamma(t))|\theta(\gamma(t)): \forall t \in [a,b] \big) 
-=
-\mN(\mu_{a:b},\Sigma_{a:b}).
+\vspace{-2ex}
+\begin{equation} \label{eq:line_of_act_dist}
+p\big(sd(\gamma(t)) ; \mu(t),\Sigma(t)\big) \ \forall t \in [a,b] 
 \end{equation}
 
-This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate gaussian.
-We would like to find the distribution on the first contact point, which we can define as when the signed distance function $f(\gamma(t))$ is $0$ and all previous times $\tau$ we have $f(\gamma(\tau)) > 0$ for $0 \leq \tau < t$.
-This ensures $t$ is at the edge of the surface (having $f(\gamma(t)) = 0$) and that for all previous $\tau$ the gripper was outside of the surface (having $f(\gamma(\tau)) > 0$).
-We thus compute this as the joint distribution $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$.
-%Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface,
-This avoids the problem of the distribution producing multiple modes along the line: one for each intersection with the surface.
-We now derive this distribution
+This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian.
+One could think of this as a marginalization of all other points in signed distance field except the line of action.
+We would like to find the distribution on the first contact point, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
 
-\[
-  p\big(\textbf{c}_i = \gamma(t)\big) \propto 
-\]
-\[
-  p\big(f(\gamma(t)) = 0\big)P\big(f(\gamma(\tau)) > 0 | f(\gamma(t)) = 0: \forall \tau \in [0,t)\big)
-\]
+We now derive this distribution:
 
-where we only indicate proportionality and will later normalize to probability $1$.
-Using the first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second one can be rewritten by conditioning the distribution \cite{petersen2008matrix}.
+\vspace{-2ex}
+\begin{align}
+ & p\big(\textbf{c}_i = \gamma(t)\big) = \label{eq:contact_theory} \\
+  & \frac{1}{\eta} p\big(sd(\gamma(t)) = 0\big)P\big(sd(\gamma(\tau)) > 0 | sd(\gamma(t)) = 0\big) \\
+  & \forall \tau \in [0,t)
+\end{align}
 
+Where $\eta$ is a proportionality constant.
+The first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second term can be solved by first conditioning on the joint $p(sd(\gamma(t))|sd(\gamma(t)) = 0)$ and then computing the cumulative distribution function  \cite{petersen2008matrix}.
+We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig.
+\ref{fig:GraspDist}.
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
+\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
+Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
+The two modes correspond to the different potential contact points, either the handle or the base of the cup.
+Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}.
+}
+\vspace*{-10pt}
+\label{fig:GraspDist}
+\end{figure*}
+
+In practice Eq.
+\ref{eq:contact_theory} is not efficient to compute because it requires computation of the cumulative distribution function of a large multivariate Gaussian, so instead we sample from Eq.
+\ref{eq:line_of_act_dist} and find the first positive to negative zero-crossing of the sample along the line.
+
+\subsection{Distribution on Surface Normals} 
+Using Eq.
+\ref{eq:mean_gradient} and Eq.
+\ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively.
+Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$.
+We can now write
+
+\vspace{-2ex}
 \begin{align*}
-p_c\big(f(\gamma(\tau)): \forall \tau \in [0,t)\big) = p\big(f(\gamma(\tau))  | f(\gamma(t)) = 0\big)  
+p\big(\textbf{n}_i|\textbf{c}_i = \gamma(t)\big) = p\big(\textbf{n}_i |\mu(\gamma(t)), \Sigma(\gamma(t)) \big)
 \end{align*}
 
-The following can now be said:
+One interesting effect of this technique is that we can now marginalize out the line of action model and visual what the surface normal distribution is along a given line of action.
+To our knowledge this is the first attempt to visual surface normals along a grasp plan.
+Marginalization can be performed as follows:
 
-\[
-  p\big(\textbf{c}_i = \gamma(t)\big) = 
-\]
-\[
-  = \frac{1}{\eta} p(f(\gamma(t)) = 0) P_c\big(f(\gamma(\tau)) > 0): \forall \tau \in [0,t)\big)			 
-\]
-
-for the appropriate $\eta$ normalization factor.
-The second product term can be evaluated by calculating the cumulative distribution of a multivariate Gaussian, which we calculate with the Matlab function $mvncdf$.
-We show again the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and approach direction in Fig.
-\ref{fig:GraspContactPt}.
-%efficiently evaluated by looking up the cumulative distribution of a multivariate Gaussian, which is common in most software packages \cite{matlab}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide04.jpg}
-\caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
-Right: Induced distribution on the contact point as a function of x-axis position along the approach line.}
-\vspace*{-10pt}
-\label{fig:GraspContactPt}
-\end{figure}
-
-\subsection{Distribution on Surface Normals} 
-The distribution of surface normals $p(\textbf{n}_i = \textbf{v})$ can be calculate as follows.
-First we assume that some function exists $h(x) = ( \mu_{\nabla}(x), \Sigma_{\nabla}(x) )$, hence given a point $\bf{x}$ it returns the parameters for a Gaussian distribution around the gradient.
-this function can be computed via learning the gradient \cite{solak2003derivative} or analytical differentiation of $f(x)$.
-We note that both methods yield a Gaussian distribution.
-We now demonstrate how to marginalize out the contact distribution and compute $p(\textbf{n}_i = \textbf{v})$.\\
-
-From our distribution on contact points and Bayes rule we can compute the following:
-
+\vspace{-2ex}
 \begin{equation}
-p(\textbf{c}_i = \gamma(t), \textbf{n}_i = \textbf{v}) = p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big)
+p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt
 \end{equation}
 
-Now we can marginalize out the distribution on contacts:
-
-\begin{equation}
-p(\textbf{n}_i = \textbf{v}) = \int_a^b  p \big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p(\textbf{c}_i = \gamma(t)) dt
-\end{equation}
-
-\begin{equation}
-p\big(\textbf{n}_i = \textbf{v}\big) = \int_a^b  p \big(\textbf{n}_i = \textbf{v} | h(\gamma(t))\big)p\big(\textbf{c}_i = \gamma(t)\big) dt
-\end{equation}
-
-We approximate this by uniformly sampling the integral along the function $\gamma(t)$ and achieve the following:
-
-\begin{equation}
-p\big( \textbf{n}_i = \textbf{v} \big) = \sum_T  p \big( \textbf{n}_i = \textbf{v} | h(\gamma(t)) \big) p\big(\textbf{c}_i = \gamma(t)\big) \Delta t
-\end{equation}
-
-Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
-To account for this we project the Gaussian distribution $p \big(\textbf{n}_i = \textbf{v} |\textbf{c}_i = \gamma(t) \big)$  onto $\mathcal{S}^{d-1}$.
-We use a projection technique developed by Olano and North \cite{olano1997normal}.
-In Fig.
-\ref{fig:GraspSurfaceNormals}, we show the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach direction.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide05.jpg}
-\caption{Left: Grasp approach direction on an uncertain surface, represented by a Gaussian Process Implicit Surface.
-Right: Induced distribution on the surface normals.}
-\vspace*{-10pt}
-\label{fig:GraspSurfaceNormals}
-\end{figure}
+Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
+To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.
+In Fig.\ref{fig:GraspDIst}, we visualize the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
 
@@
 
-We recall the quantity CDF$(f(x))(0) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ as the cumulative distribution function of $f(x)$ evaluated at 0 and note that it is equal to the probability that $x$ is interior to the surface under the current observations.
-We assume that the object has uniform mass density and then CDF$(f(x))(0)$ is the expected mass density at $x$.
+We recall the quantity $P(sd(x) < 0) = \int_{-\infty}^{0} p(sd(x) =  s \ | \ \mu(x),\Sigma(x)) ds$ is equal to the probability that $x$ is interior to the surface under the current observations.
+We assume that the object has uniform mass density and then $P(sd(x) < 0)$ is the expected mass density at $x$.
 Then we can find the expected center of mass as:
@@
   \frac
-    {\int_{\mathcal{R}}x CDF(f(x))(0) dx}
-    {\int_{\mathcal{R}}  CDF(f(x))(0) dx}
+    {\int_{\mathcal{W}}x P(sd(x)<0) dx}
+    {\int_{\mathcal{W}}  P(sd(x)<0) dx}
 \end{equation}
 
-which can be approximated by sampling $\mathcal{R}$ uniformly in a grid and approximating the spatial integral by a sum.
+which can be approximated by sampling $\mathcal{W}$ in a grid and approximating the spatial integral by a sum.
+Since this operation involves the entire SDF, one would want to use a low resolution grid for computational efficiency.
 We show the computed density and calculated expected center of mass for a marker in Fig.
@@
 \includegraphics[scale = 0.3]{figures/Slide06.jpg}
-\caption{Left: A surface with GPIS construction and expected center of mass (blue X)
-Right: The distribution on the density of each point assuming uniform center of mass}
+\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
+Right: The distribution on the density of each point assuming uniform density}
 \vspace*{-10pt}
@@
 
-\section{Sampling from a GPIS}
-Prior work that consider shape uncertainty purposed sampling from distribution on the shape itself \cite{kehoe2012toward}.
-However, with a more complicated model on the shape distribution this technique would scale poorly.
+\subsection{Complexity Analysis on Sampling From Grasps Distributions}
 
-Given a work space $\mathcal{R}^{n\times n}$, the complexity of sampling a work space is show to be $O(n^6)$.
-This is due to the necessary inversion of a $n \times n$.
-In typical cases $n$ would be on the order of 100 making this very computationally intensive even in the 2D case.
+After formally deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
+\ref{eq:independence}.
+This can be done by drawing samples from Eq.
+\ref{eq:joint_contact_normal}.
+and using our projection technique for the normal distribution.
 
-If we instead sample from our proposed grasp distributions and use a line of action that is roughly equal to $n$, the complexity can be rewritten as $O(T*n^3)$,  where $T$ is the number of grasps that are evaluated.
+Having a distribution along a line of action model allows us to sample from those instead of the joint distribution $p(sd(\mathcal{W}))$.
+Assuming the line of action is on the order of $n$, sampling from this distribution for a single grasp is $O(n^3)$.
+However, each proposed grasp plan $\Gamma$ requires the distribution to be computed, so if we have $T=|G|$ then the complexity is $O(Tn^3)$.
+In practice, this should be much smaller than $O(n^6)$.
 
 \section{Adaptive Sampling for Grasp Selection}
-In a possible grasping scenario, one would be presented with a set $G$ of $T$ grasps.
-The goal would be to identify, which one is the best grasp given the set $G$ and for each grasp the $p(g)$.
-While a naive approach to solving this problem would be to simply perform Monte-Carlo integration on each one and compute the expected grasp quality, we propose treating the problem as an n-arm bandit problem and forming a policy for selecting which grasp to sample.
-The motivation behind this is due to the expensive evaluation that each Ferrari-Canny computation takes \cite{ferrari1992}.
-
-An n-arm bandit problem can be defined as follows: an agent is presented with a $n$ slot machines and receives a reward each time a lever is pulled that is drawn from the distribution associated with the slot machine.
-The goal of the agent is to maximize the expected reward received, by balancing exploration and exploitation \cite{barto1998reinforcement}.
-
-For selecting grasps we use an $\epsilon$-greedy policy, where the greedy action is selected with probability $1-\epsilon$ and a random action is chosen otherwise.
-The greedy option is defined as the grasp with the highest approximate upper confidence bound $v$, which is computed via the following \cite{mc}
-
-\begin{equation}
-v = \bar{X} + \frac{1.96 \bar{\sigma}_N}{\sqrt{n}}
-\end{equation}
-
-\section{Experiments}
-
-\subsection{Validation of Grasp Distributions}
-
-To validate our theoretical calculations, we compared them to empirical distributions found via Monte-Carlo Sampling.
-The qualitative results for surface normals and contacts can be found in Figures \ref{fig:Contact_Dist} and \ref{fig:Normal_Dist} respectively.
-We present the numerical comparison with KL-divergence in Table 1, as you can see the distributions are very closely related.
-
-\begin{table}[h]
-        \begin{tabular}{ l | c c c}
-         Distribution & \bf Marker & \bf Tape & \bf Loofa \\ 
-        \hline \\
-         p($\textbf{c}_i$) & 0.14 & 0.08 & 0.02 \\
-        \hline \\
-        p($\textbf{n}_i$)& 0.35 & 0.12 & 0.16 \\
-        \hline 
-        \end{tabular}
-        \caption{The KL-Divergence for different distributions on the contact points and surface normals}
-
-        \vspace*{-10pt}
-\end{table}
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide07.jpg}
-\caption{Top: A surface with GPIS construction and line of action with the start pointed denoted by green x.
-Middle: Theoretical distribution computed on contact point
-Bottom: Empirically sampled distribution}
-\vspace*{-10pt}
-\label{fig:Contact_Dist}
-\end{figure}
+After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq.
+\ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$.
+While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
+The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig.
+\ref{fig:sampling_convergence}.
 
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide08.jpg}
-\caption{Top: A surface with GPIS construction and line of action with the start pointed denoted by green x.
-Middle: Theoretical distribution computed for surface normals
-Bottom: Empirically sampled distribution}
+\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
+\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
+You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
 \vspace*{-10pt}
-\label{fig:Normal_Dist}
+\label{fig:sampling_convergence}
 \end{figure}
 
+\subsection{Preliminaries}
+Compared to classical multi-arm bandit problems where the agent is evaluated on cumulative reward at each time-step, we are interested in a decoupling of the exploration and exploitation stage.
+The decoupling is because the agent only needs to select one grasp plan $\Gamma*$ to execute after it has sufficiently explored the other grasp plans.
+The agent is expected to explore the states and then at a given time, stop and choose the best grasp plan.
+This type of pure exploration problem with a limited amount of resources (i.e.
+computation time) is defined as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
+
+More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.
+At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$.
+This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.
+
+Performance of our polices $\psi_t$ and $\zeta_t$ are measured according to simple regret $r_t$ \cite{bubeck2009pure}.
+
+\vspace{-2ex}
+\begin{align}\label{eq:simple_regret}
+&r_t = r(\zeta_t) = \mu^* - \mu_{\zeta_t} \\
+&\mu^* = \mu_j* = \max_{j=1,..,K} \mu_j
+\end{align}
+
+As shown in Eq.
+\ref{eq:simple_regret}, simple regret is defined as the difference between the true expected value of the grasp plan your recommendation, $\mu_{\zeta_t}$ and the true expected value of the best grasp plan $\mu^*$ in the set $G$.
+
+\subsection{Our Implementation}
+In solving Eq.
+\ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
+Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$.
+Thus, we are restricted to the type of bandit policies available to us.
+
+In light of this we implement our allocation policy $\psi_t$ as simple uniform allocation.
+This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
+We adapt pure uniform allocation by measuring the $95\%$ confidence interval of each arm based on previous observations.If a given arm $i$ is pulled $n_i$ times, the confidence interval $C_{n, i}$ is defined as \cite{caflisch1998monte}.
+
+\vspace{-2ex}
+\begin{align}
+C_{ i} = \frac{1.96 \sigma_i}{\sqrt{n_i}}
+\end{align}
+
+An arm $i$ is then removed from the possible options if
+
+\vspace{-2ex}
+\begin{align*}
+\mu_{\zeta_t} - C_{\zeta_t} >   \mu_{i}+C_{i}
+\end{align*}
+
+Our recommendation strategy $\zeta_t$ is to take the highest expected grasp quality at time $t$. In future work, we will look at using other allocation and recommendation strategies.
+
+\section{Experiments}
+For the experiments below we used common household objects shown in Fig.
+\ref{fig:GPIS_TSDF}.
+We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor.
+To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
+Our visualization technique follows the approach of \cite{jeffs} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
+
+We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
+We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
+
 \subsection{Sampling from Grasps Vs. Shape}
-We first demonstrate that sampling from the two different method converges to near the same expected value, see Fig.
-\ref{fig:sampling_convergence}.
-After confirming the distributions converge to the same value we show the computational complexity in Fig.
+We first tested 1000 grasp plans and sampled each one 5000 times  and measured the RMS error between converged expected grasp plan qualities for sampling shape Eq.
+\ref{eq:shape_sampling} vs.
+grasps  Eq.
+\ref{eq:grasp_sampling} was 0.004.
+After confirming the distributions converged close to the same value, we show the computational complexity in Fig.
 \ref{fig:speed_dif} of the two methods for evaluating 100 grasps on an $n \times n$ grid.
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide11.jpg}
-\caption{Left: Sampling from grasp distributions
-Right: Sampling from distribution on shape}
-\vspace*{-10pt}
-\label{fig:sampling_convergence}
-\end{figure}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide12.jpg}
-\caption{Comparison of the computational complexity of the two methods with respect to the work space dimensions}
+\includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
+\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace.
+Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Green is sampling from $p(g)$ or the calculated distribution on grasps.
+As you can see sampling from the calculated distributions scales much better.
+}
 \vspace*{-10pt}
@@
 We consider the problem of selecting the best grasp out of a set $G$ given a fix number of iterations $I$.
-For our experiments we look at selecting the best grasp out of a size of $|G| = 100$ and given a fix iteration limit of $I = 1000$.
-We show the results for both the marker and tape, in Fig.
-\ref{fig:marker_bandit} and Fig.
-\ref{fig:tape_bandit} respectively.
-We note that in both cases the policy was able to select the best grasp without sufficiently sample the set of possible grasps.
-
-\todo{Add experiments demonstrating ordering and trials over large number of runs, also fix visualizations}
+For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$ and $I= 7000$ or when the set of grasps is a single grasp.
+In Fig.
+\ref{fig:simple_regret}, we plotted the simple regret, Eq.
+\ref{eq:simple_regret}, averaged over 20 runs and compare it to the naive Monte-Carlo method that randomly chooses a grasp plan to draw a sample from .
+The most interesting thing is that the regret is minimized an order of magnitude faster than the naive approach, thus motivating the use of including observations as you select samples.
 
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide09.jpg}
-\caption{Left: $\epsilon$-greedy policy for sampling (Top 10 grasps plotted)
-Right: Monte-Carlo Sampling for 1000 iterations (Top 10 grasps plotted)}
+\includegraphics[width=8.5cm,height=9cm]{figures/Slide09.jpg}
+\caption{ \footnotesize Comparison of two sampling methods.
+Green is the adaptive bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
+We measure their ability to converge in terms of simple regret Eq.
+\ref{eq:simple_regret} averaged over 100 runs.
+We had them determine the best grasp when $|G|=1000$.
+As you can see our method converges much faster with an average of evaluation of 4 samples per grasp.
+We start the process though by deterministically evaluating every grasp 2 times to achieve a baseline, which explains the first part of the graph.}
 \vspace*{-10pt}
-\label{fig:marker_bandit}
+\label{fig:simple_regret}
 \end{figure}
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide10.jpg}
-\caption{Left: $\epsilon$-greedy policy for sampling (Top 10 grasps plotted)
-Right: Monte-Carlo Sampling for 1000 iterations (Top 10 grasps plotted)}
-\vspace*{-10pt}
-\label{fig:tape_bandit}
-\end{figure}
+\section{Limitations and Future Work}
+Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{jeffs}.
 
-\todo{Write Conclusion}
+An additional problem is that we only have an expected center of mass and not a distribution on the center of mass.
+This might prove to be to expensive to compute, however recent work by Panahi et al.
+showed a way to bound the center of mass for convex parts.
+Extension of his work to implicit surfaces could be of possible interest \cite{panahi2014bounding}.
+
+Our budgeted multi-arm bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
+Future work will be building an efficient construction of GPIS to scale to 3D.
+Lastly, we are interested in investigating how well our algorithm works in parallel computing to be used in the cloud computing context.
+Furthermore, their is a large literature on formulating bandit policies and experimenting with them all will need to be done to see which one works best.
+
 \bibliographystyle{ieeetr}

### 2014-10-01 paper-pieter-feedback.tex
gitignore, changed citation style

--- 2014-09-30 paper.tex
@@
 Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.
-Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
-The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$..
-We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp.
+%%PA: not sure what "Bayesian shape represenation" means -- isn't it just a distribution over shapes that it represents, which happens to allow for performing Bayesian inference?
+language not very precise I guess...
+Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. The standard approach of drawing samples from a GPIS in 2D by means of a %%PA: a -> an
+ evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$.%%PA: grouping of words should try to make things easier to read/follow along; does 2D only apply to the O(n^6) or to the entire sentence?
+aside from sentence structuring, it's hard to understand this previous sentence, what is the n^9 about?
+what is a grid step?
+does it mean number of discretization levels for dimension?
+%%PA: also, why ".." rather than "." to end the sentence?
+We propose an alternative approximation%%PA: grouping of words is off; it's not an alternative approximation, it 's an alternative to sampling from shape distributions ..
+ to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp. 
+%%PA: how about including some intuition about what the alternative is / what main idea it is leveraging?
 We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.
+%%PA: --> cool!!
 \end{abstract}
@@
 \vspace{10pt}
+
+%%PA: this citation type-setting is a bit funny to me, I am much more used to [12, 8, 10] or [12], [8], [10] rather than the current paper's typesetting as [12] [8] [10].
+If you have seen it in a reputable place and it's the style you guys prefer then I am fine with it, of course
+%%ZM: will fix as going through
 
@@
 Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..
+To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
+ in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %% ZM fixed
 
@@
 To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape,
+%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable?
+which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
 
@@
 \includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
-\caption{\footnotesize
-Left: HD image of a common measuring cup from in a household environment.
+\caption{Left: HD image of a common measuring cup from in a household environment.
 Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
@@
 
-Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}.
+Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
 Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
 Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}.
+%%PA: that's neat!  let's have you include some of that in the abstract!
+%%PA: also n^3 independent as to whether it's a 2-D or 3-D problem, or is n^3 specific to a particular dimensionality?
 We constrain the contact points by considering the approach trajectory of a gripper.
@@
 \begin{enumerate}
-	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
-	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
+	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.%%PA: grammar off
+	\item  Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.%%PA: -> computational %%ZM: fixed
 	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
@@
 
- Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
+ Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic}, \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}, \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
 Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
@@
  The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual.
-Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}\cite{newcombe2011kinectfusion}\cite{hornung2013octomap}.
+Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}, \cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}.
 Some exciting work done with GPIS representation are the following: Hollinger et al.
@@
 used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.
+%%PA: locally optimal anti-podal grasps?
 
-  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
+  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
 With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace.
@@
 Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}.
-While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}\cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
+While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}, \cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
 Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}.
@@
 \includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
-\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
+\caption{Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
 Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
@@
 Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
+%%PA: motivation seems a little weak; did you compare performance with other kernels?
+(must be other differentiable ones?) could something be added about why differentiability is important to our approach?
 
@@
 If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
-Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}\cite{li1988task}.
+Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
 
@@
 \begin{align*}
-E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
+E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S) %%PA: 1/N missing?
 \end{align*}
@@
 Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}.
+%%PA: that last use of $n$ has a different meaning, that's confusing, use a different symbol than n, or just say in words it's cubic in the number of grid points
 Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
@@
 \includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
-\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
+\caption{(Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
 Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
@@
 \ref{eq:line_of_act_dist} and find the first positive to negative zero-crossing of the sample along the line.
+
+%%PA: it's not clear to me where the savings are coming from; the goal was to avoid sampling from the GPIS; but now it seems the algorithm needs to sample from the GPIS after all to obtain the grasp parameters?
+What am I missing here?
+Please address not just in the paper, but also via email
+
+%%PA: if you are indeed avoiding sampling from th GPIS now, then it'd be good to highlight that, and explain exactly how that was enabled...
+
+%%PA: the entire Section V. is a bit confusing; reads very procedural, but not a very clean straightforwardly explained procedure, and the rationale / context / big idea is not explained...
 
@@
 \includegraphics[scale = 0.3]{figures/Slide06.jpg}
-\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
+\caption{Left: A surface with GPIS construction and expected center of mass (black X)
 Right: The distribution on the density of each point assuming uniform density}
@@
 \ref{fig:sampling_convergence}.
+%%PA:-> grammar?
 
@@
 \includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
-\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
+\caption{Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
 You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
@@
 
-More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.
+More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.%%PA: -> rewards?  
  At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$.
@@
 \end{align}
+
+%%PA: hard to follow along, lots of notation, is it really necessary to introduce that many new symbols to get the point across?
 
@@
 \end{align}
+
+%%PA: how does a single number define an interval?
+
+%%PA: again lots of notation and symbols, how about explaining it primarily in plain words, would anything be lost? if so, introduce symbols / equations for what you lose as necessary...
+
+%%PA: to me this doesn't sound like uniform allocation; while I can't actually follow along, my hunch is that you have confidence intervals, and at each step you consider which grasps are still in contention for being a winner based on their confidence intervals, and then sample a shape (is is a shape?
+is it something else that you sample?) once for each grasp
 
@@
 
+%%PA: it'd be nice to have the text be such that you can read it, and from that understand what the conclusions are from the experimentation...
+
 \begin{figure}[ht!]
@@
 \includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
-\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace.
+\caption{Time it took to sample from 100 grasp distributions for a given resulution of the workspace.
 Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Green is sampling from $p(g)$ or the calculated distribution on grasps.
@@
 \includegraphics[width=8.5cm,height=9cm]{figures/Slide09.jpg}
-\caption{ \footnotesize Comparison of two sampling methods.
+\caption{Comparison of two sampling methods.
 Green is the adaptive bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
@@
 \end{figure}
+
+%%PA: was this an experiment on one shape distribution? that'd be rather anecdotal then... Did you run more extensive experiments?
 

### 2014-10-01 paper.tex
changed section V

@@
 
- To sample from $p(g)$, we need to compute the distributions associated with a line of action $p(n_i|c_i)p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ on each of the parameters: contact points $c_i$, surface normals $n_i$  and expected center of mass $\bar{z}$.
+ To sample from $p(g)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Using Bayes rule we can rewrite this as
+
+ \vspace{-2ex}
+ \begin{align*}
+ &p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))=\\
+ &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))p(c_i|\gamma_i(t),\mu(x),\Sigma(x))
+ \end{align*}
+
+ In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$.
+Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))$ and present a novel visualization technique for the distribution on surface normals.
+Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.
  .
-\subsection{Distribution on Contact Points} 
+\subsection{Distribution on Contact Points}\label{sec:contact} 
+We would like to find the distribution on contact point $\textbf{c}_i$.
+A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface.
+We express this as the following conditions \\
+
+\begin{enumerate}
+	\item $sd(\gamma(t)) = 0$
+	\item $sd(\gamma(\tau)) > 0$ $\forall \tau \in [a,t)$
+\end{enumerate}
+
+We now formally derive the distribution on contact point $p(\textbf{c}_i)$ using these conditions.  
+. 
 The probability distribution along the line $\gamma(t)$ is given by:
@@
 One could think of this as a marginalization of all other points in signed distance field except the line of action.
-We would like to find the distribution on the first contact point, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
+We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
 
@@
 
-\subsection{Distribution on Surface Normals} 
+\subsection{Distribution on Surface Normals}\label{sec:normals} 
 Using Eq.
@@
 
-\subsection{Expected Center of Mass}
+\subsection{Expected Center of Mass}\label{sec:mass}
 

### 2014-10-01 paper.tex
added en tools

@@
 A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface.
-We express this as the following conditions \\
+We express this as the following conditions:
 
-\begin{enumerate}
-	\item $sd(\gamma(t)) = 0$
-	\item $sd(\gamma(\tau)) > 0$ $\forall \tau \in [a,t)$
-\end{enumerate}
+\vspace{-2ex}
+\begin{align}
+ &sd(\gamma(t)) = 0 \label{eq:density_cond} \\
+&sd(\gamma(\tau)) > 0, \: \forall \tau \in [a,t) \label{eq:cdf_cond}
+\end{align}
 
-We now formally derive the distribution on contact point $p(\textbf{c}_i)$ using these conditions.  
-. 
+We will now demonstrate how to efficiently sample from these distributions and then show what this implies formally.
+
 The probability distribution along the line $\gamma(t)$ is given by:
@@
 One could think of this as a marginalization of all other points in signed distance field except the line of action.
+To sample contact points, one can simply draw samples from Eq.
+\ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies conditions \ref{list:contact_cond}.
+
 We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.

### 2014-10-01 paper-pieter-feedback.tex
mostly merge some pieter edits

@@
 If you have seen it in a reputable place and it's the style you guys prefer then I am fine with it, of course
-%%ZM: will fix as going through
+%%ZM: fixed
 
@@
 To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
- in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %% ZM fixed
+ in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed
 
-While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}.
+While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous real-valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
+This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
 To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape,
-%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable?
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they also allow for a differentiable function as a shape representation,
+%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable? %%ZM: fixed
 which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.

### 2014-10-01 paper.tex
mostly merge some pieter edits

--- 2014-10-01 paper.tex
@@
 \vspace{10pt}
+
+%%PA: this citation type-setting is a bit funny to me, I am much more used to [12, 8, 10] or [12], [8], [10] rather than the current paper's typesetting as [12] [8] [10].
+If you have seen it in a reputable place and it's the style you guys prefer then I am fine with it, of course
+%%ZM: fixed
 
@@
 Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..
+To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
+ in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed
 
-While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}.
+While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous real-valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
+This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
 To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they also allow for a differentiable function as a shape representation,
+%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable? %%ZM: fixed
+which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
 
@@
 \begin{enumerate}
-	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
-	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
+	\item Derivation of distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.%%PA: grammar off
+	\item Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.%%PA: -> computational %%ZM: fixed
 	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
@@
 Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
 See Fig.

### 2014-10-01 paper.tex
some edits

@@
 Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
+To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty%%PA: --> spelling %%ZM: fixed
  in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed
@@
 
-More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.
+More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the rewards seen.
 At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$.

### 2014-10-01 paper.tex
mergy

--- 2014-10-01 paper.tex
@@
 Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.
-%%PA: not sure what "Bayesian shape represenation" means -- isn't it just a distribution over shapes that it represents, which happens to allow for performing Bayesian inference?
-language not very precise I guess...
-Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. The standard approach of drawing samples from a GPIS in 2D by means of a %%PA: a -> an
- evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$.%%PA: grouping of words should try to make things easier to read/follow along; does 2D only apply to the O(n^6) or to the entire sentence?
-aside from sentence structuring, it's hard to understand this previous sentence, what is the n^9 about?
-what is a grid step?
-does it mean number of discretization levels for dimension?
-%%PA: also, why ".." rather than "." to end the sentence?
-We propose an alternative approximation%%PA: grouping of words is off; it's not an alternative approximation, it 's an alternative to sampling from shape distributions ..
- to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp. 
-%%PA: how about including some intuition about what the alternative is / what main idea it is leveraging?
+Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
+The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$..
+We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp.
 We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.
-%%PA: --> cool!!
 \end{abstract}
@@
 \vspace{10pt}
-
-%%PA: this citation type-setting is a bit funny to me, I am much more used to [12, 8, 10] or [12], [8], [10] rather than the current paper's typesetting as [12] [8] [10].
-If you have seen it in a reputable place and it's the style you guys prefer then I am fine with it, of course
-%%ZM: fixed
 
@@
 Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
- in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed
+To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..
 
-While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous real-valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
+While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
+This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}.
 To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they also allow for a differentiable function as a shape representation,
-%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable? %%ZM: fixed
-which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.
 
@@
 \includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
-\caption{Left: HD image of a common measuring cup from in a household environment.
+\caption{\footnotesize
+Left: HD image of a common measuring cup from in a household environment.
 Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
@@
 
-Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
+Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}.
 Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
 Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}.
-%%PA: that's neat!  let's have you include some of that in the abstract!
-%%PA: also n^3 independent as to whether it's a 2-D or 3-D problem, or is n^3 specific to a particular dimensionality?
 We constrain the contact points by considering the approach trajectory of a gripper.
@@
 \begin{enumerate}
-	\item Derivation of distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.%%PA: grammar off
-	\item Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.%%PA: -> computational %%ZM: fixed
+	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
+	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
 	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
@@
 
- Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic}, \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}, \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
+ Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
 Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
@@
  The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual.
-Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}, \cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}.
+Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}\cite{newcombe2011kinectfusion}\cite{hornung2013octomap}.
 Some exciting work done with GPIS representation are the following: Hollinger et al.
@@
 used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.
-%%PA: locally optimal anti-podal grasps?
 
-  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
+  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
 With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace.
@@
 Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}.
-While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}, \cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
+While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}\cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
 Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}.
@@
 \includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
-\caption{Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
+\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
 Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
@@
 Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
-%%PA: motivation seems a little weak; did you compare performance with other kernels?
-(must be other differentiable ones?) could something be added about why differentiability is important to our approach?
 
@@
 If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
-Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
+Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}\cite{li1988task}.
 
@@
 Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
 See Fig.
@@
 \begin{align*}
-E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S) %%PA: 1/N missing?
+E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
 \end{align*}
@@
 Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}.
-%%PA: that last use of $n$ has a different meaning, that's confusing, use a different symbol than n, or just say in words it's cubic in the number of grid points
 Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
@@
 To sample contact points, one can simply draw samples from Eq.
-\ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies conditions \ref{list:contact_cond}.
+\ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies  Eq.
+\ref{eq:density_cond} and Eq.
+\ref{eq:cdf_cond}.
 
-We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
+We also derive what the actual distribution $p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ in case the reader wanted the actual distribution and not samples.
+Using the conditions described above for a contact point( Eq.
+\ref{eq:density_cond} and Eq.
+\ref{eq:cdf_cond}).
+We write the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
 
@@
 The first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second term can be solved by first conditioning on the joint $p(sd(\gamma(t))|sd(\gamma(t)) = 0)$ and then computing the cumulative distribution function  \cite{petersen2008matrix}.
-We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig.
-\ref{fig:GraspDist}.
+We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig \ref{fig:GraspDist}.
+As mentioned earlier, Eq.
+\ref{eq:contact_theory} is not efficeint to compute due to cumulative distribution function of a large multi-variate Gaussian, however GPIS's ability to give a distribution on contact points is still interesting.
 
@@
 \end{figure*}
-
-In practice Eq.
-\ref{eq:contact_theory} is not efficient to compute because it requires computation of the cumulative distribution function of a large multivariate Gaussian, so instead we sample from Eq.
-\ref{eq:line_of_act_dist} and find the first positive to negative zero-crossing of the sample along the line.
 

### 2014-10-01 paper.tex
added multi-arm bandit preliminaries

@@
 \title{\LARGE \bf
-Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]}
+Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-13 09-30-2014]}
 
-\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
+\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\ Jur Van Den Berg,  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
 
@@
 \begin{abstract}
-Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.
+Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.
 Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
-The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$..
-We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp.
-We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.
+Given a GPIS model this would mean sampling from the signed distance field in a uniform grid of side length $n$.
+The computational complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
+We propose an alternative to sampling from shape distributions and demonstrate how this reduces the computational complexity to $O(n^3)$ in both 3D and 2D for evaluation of a single grasp.
+We furthermore introduce the idea of adaptive sampling in the context of choosing the best grasp given a set of grasps and a GPIS object model by formulating it as a budgeted multi-arm bandit problem.
+We show an order of magnitude reduction in the number of samples needed vs.
+a non-adaptive approach and we have statistical guarantees with our method.
 \end{abstract}
@@
 Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..
+To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
 
 While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}.
+This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
 To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
 
@@
 
-Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}.
+Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
 Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
@@
 	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
-	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
+	\item  Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.
 	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
@@
 
- Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
+ Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic},  \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling},  \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
 Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
@@
 Mahler et al.
-used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.
+used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{jeff}.
 
-  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
+  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating},  \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
 With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace.
@@
 
-\subsection{Gaussian Process (GP) Background}
+\subsection{Multi-Arm Bandit Problem}
+The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to optimize his decisions, while improving his information at the same time.
+In a multi-arm bandit problem the gambler has K independent slot machine arms and tries to infer, which one will yield the highest return.
+A good gambler would want to exploit the machine that currently yields a high reward and explore new machines to see if he can better his chances.
+Developing a policy that successfully does this trade has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}\cite{robbins1985some} \cite{bergemann2006bandit}.
+
+There is a number of algorithms for developing policies to balance exploration and exploitation.
+Algorithms that have theoretical guarantees are based on UCB \todo{descibe UCB}.
+Those that are derived from emprical methods are developed off of the $\epsilon-$greedy approach.
+$\epsilon-$ greedy is the idea of choosing the arm with the current best expected value with $1-\epsilon$ probability and choosing a different arm with probability $\epsilon$.
+\cite{barto1998reinforcement}.
+In practice, when the distribution on the arm is not in closed form, like not in the exponential family, the empirical methods have shown to have better performance \cite{audibert2010best}.
+
+In the problem of choosing the best grasp, one must intelligently allocate samples based on the observations received so far.
+As you can in Fig.
+\ref{fig:sampling_convergence}, a typical grasp can take hundreds of iterations for convergence of the expected value to be reach.
+Thus if one had 1000 grasps to choose from, it would take on the order of millions grasp metric evaluations to choose the best grasp in the naive way.
+If we can develop a policy to intelligently explore the proposed grasps and select the best one, we can reduce the computationally complexity of grasping with uncertainty.
+
+\todo{Add Multi arm bandit preliminary make it long}
+
+\subsection{Gaussian Process (GP) Background} \todo{massive trim down}
 GPs provide an infinite dimensional analogue of Multivariate
@@
 Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
+While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on.
+Future work will look at how to efficiently sample when the approach trajectory has noise.
 
@@
 
+\section{Adaptive Sampling for Grasp Selection}
+After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq.
+\ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$.
+While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
+The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig.
+\ref{fig:sampling_convergence}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
+\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
+You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
+\vspace*{-10pt}
+\label{fig:sampling_convergence}
+\end{figure}
+
+\subsection{Preliminaries}
+Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+We can formulate this problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
+We  have a policy for exploration of different grasp plans (i.e.
+choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far.
+
+We measured performance of our polices in terms of simple regret, which is the difference of the true expected value of the actual best grasp plan and the true expected value of the selected grasp plan at the given stopping time \cite{bubeck2009pure}.
+The number of samples needed before the simple regret reaches zero, determines how effective an exploration  policy is for grasp evaluation.
+
+\subsection{Our Implementation}
+In solving Eq.
+\ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
+Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
+Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information.
+\todo{double check with Dylan}
+
+For our exploration policy, we maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
+During exploration, we sample uniformly from this subset.  This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
+For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
+The width of the confidence interval for a grasp plan $i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
+
+\vspace{-2ex}
+\begin{align}
+C_{ i} := \frac{1.96 \sigma_i}{\sqrt{n_i}}.
+\end{align}
+
+Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.  Thus the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
+After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
+Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}.
+In future work, we will look at using other exploration strategies.
+
 \section{Evaluating a Grasp}
@@
 Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
 See Fig.
@@
 \centering
-\includegraphics[width = 8.5cm, height= 5cm ]{figures/Slide13.jpg}
+\includegraphics[width = 8.5cm, height= 7cm ]{figures/Slide13.jpg}
 \caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
@@
 \begin{align*}
-E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
+E(Q(\Gamma)) \approx \frac{1}{N} \sum_{i=1}^N Q(g|S_i,\Gamma) , \ \  S_i \sim p(S)
 \end{align*}
@@
 \begin{align}\label{eq:grasp_sampling}
-E(Q(\Gamma)) = \sum_{i=1}^N Q(g_i) , g_i \in p(g)
+E(Q(\Gamma)) = \frac{1}{N} \sum_{i=1}^N Q(g_i) , \ \ g_i \sim p(g)
 \end{align}
@@
 
-We will now demonstrate how to efficiently sample from these distributions and then show what this implies formally.
+We will now demonstrate how to efficiently sample from $p(\textbf{c}_i|\mu{x},\Sigma{x},\gamma_i{t})$
 
@@
 \ref{eq:cdf_cond}.
-
-We also derive what the actual distribution $p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ in case the reader wanted the actual distribution and not samples.
-Using the conditions described above for a contact point( Eq.
-\ref{eq:density_cond} and Eq.
-\ref{eq:cdf_cond}).
-We write the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
-
-We now derive this distribution:
-
-\vspace{-2ex}
-\begin{align}
- & p\big(\textbf{c}_i = \gamma(t)\big) = \label{eq:contact_theory} \\
-  & \frac{1}{\eta} p\big(sd(\gamma(t)) = 0\big)P\big(sd(\gamma(\tau)) > 0 | sd(\gamma(t)) = 0\big) \\
-  & \forall \tau \in [0,t)
-\end{align}
-
-Where $\eta$ is a proportionality constant.
-The first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second term can be solved by first conditioning on the joint $p(sd(\gamma(t))|sd(\gamma(t)) = 0)$ and then computing the cumulative distribution function  \cite{petersen2008matrix}.
-We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig \ref{fig:GraspDist}.
-As mentioned earlier, Eq.
-\ref{eq:contact_theory} is not efficeint to compute due to cumulative distribution function of a large multi-variate Gaussian, however GPIS's ability to give a distribution on contact points is still interesting.
 
@@
 
-\section{Adaptive Sampling for Grasp Selection}
-After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq.
-\ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$.
-While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
-The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig.
-\ref{fig:sampling_convergence}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
-\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
-You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
-\vspace*{-10pt}
-\label{fig:sampling_convergence}
-\end{figure}
-
-\subsection{Preliminaries}
-Compared to classical multi-arm bandit problems where the agent is evaluated on cumulative reward at each time-step, we are interested in a decoupling of the exploration and exploitation stage.
-The decoupling is because the agent only needs to select one grasp plan $\Gamma*$ to execute after it has sufficiently explored the other grasp plans.
-The agent is expected to explore the states and then at a given time, stop and choose the best grasp plan.
-This type of pure exploration problem with a limited amount of resources (i.e.
-computation time) is defined as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
-
-More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.
-At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$.
-This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.
-
-Performance of our polices $\psi_t$ and $\zeta_t$ are measured according to simple regret $r_t$ \cite{bubeck2009pure}.
-
-\vspace{-2ex}
-\begin{align}\label{eq:simple_regret}
-&r_t = r(\zeta_t) = \mu^* - \mu_{\zeta_t} \\
-&\mu^* = \mu_j* = \max_{j=1,..,K} \mu_j
-\end{align}
-
-As shown in Eq.
-\ref{eq:simple_regret}, simple regret is defined as the difference between the true expected value of the grasp plan your recommendation, $\mu_{\zeta_t}$ and the true expected value of the best grasp plan $\mu^*$ in the set $G$.
-
-\subsection{Our Implementation}
-In solving Eq.
-\ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
-Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$.
-Thus, we are restricted to the type of bandit policies available to us.
-
-In light of this we implement our allocation policy $\psi_t$ as simple uniform allocation.
-This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
-We adapt pure uniform allocation by measuring the $95\%$ confidence interval of each arm based on previous observations.If a given arm $i$ is pulled $n_i$ times, the confidence interval $C_{n, i}$ is defined as \cite{caflisch1998monte}.
-
-\vspace{-2ex}
-\begin{align}
-C_{ i} = \frac{1.96 \sigma_i}{\sqrt{n_i}}
-\end{align}
-
-An arm $i$ is then removed from the possible options if
-
-\vspace{-2ex}
-\begin{align*}
-\mu_{\zeta_t} - C_{\zeta_t} >   \mu_{i}+C_{i}
-\end{align*}
-
-Our recommendation strategy $\zeta_t$ is to take the highest expected grasp quality at time $t$. In future work, we will look at using other allocation and recommendation strategies.
-
 \section{Experiments}

### 2014-10-01 paper.tex
changed preliminaries to be better for multi-arm bandits, talked about budgeting, moved simple regret to preliminaries

@@
 
-In this section we describe the mathematical derivation of Gaussian Process Implicit Surface representations.
+In this section we describe the multi-arm bandit problem and how it relates to grasping.
 
 \subsection{Multi-Arm Bandit Problem}
-The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to optimize his decisions, while improving his information at the same time.
-In a multi-arm bandit problem the gambler has K independent slot machine arms and tries to infer, which one will yield the highest return.
-A good gambler would want to exploit the machine that currently yields a high reward and explore new machines to see if he can better his chances.
-Developing a policy that successfully does this trade has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}\cite{robbins1985some} \cite{bergemann2006bandit}.
+The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
+The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
+A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
+Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
 
-There is a number of algorithms for developing policies to balance exploration and exploitation.
-Algorithms that have theoretical guarantees are based on UCB \todo{descibe UCB}.
-Those that are derived from emprical methods are developed off of the $\epsilon-$greedy approach.
-$\epsilon-$ greedy is the idea of choosing the arm with the current best expected value with $1-\epsilon$ probability and choosing a different arm with probability $\epsilon$.
-\cite{barto1998reinforcement}.
-In practice, when the distribution on the arm is not in closed form, like not in the exponential family, the empirical methods have shown to have better performance \cite{audibert2010best}.
+There are a number of algorithms for developing policies to balance exploration and exploitation.
+One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
+A class of algorithms that have theoretical guarantees are Upper Confidence Bound (UCB).
+UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times has been sampled for each arm.
+The algorithm chooses the arm at each step which has the highest upper bound on expected reward, since that is the most potentially promising arm.
+When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
+In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance \cite{kuleshov}.
 
-In the problem of choosing the best grasp, one must intelligently allocate samples based on the observations received so far.
-As you can in Fig.
-\ref{fig:sampling_convergence}, a typical grasp can take hundreds of iterations for convergence of the expected value to be reach.
-Thus if one had 1000 grasps to choose from, it would take on the order of millions grasp metric evaluations to choose the best grasp in the naive way.
-If we can develop a policy to intelligently explore the proposed grasps and select the best one, we can reduce the computationally complexity of grasping with uncertainty.
+\subsection{Budgeted Multi-Arm Bandit Problem and Grasping}
+%In the problem of choosing the best grasp, one must intelligently allocate samples based on the observations received so far.
+%As you can in Fig. \ref{fig:sampling_convergence}, a typical grasp can take hundreds of iterations for convergence of the expected value to be reach.
+%Thus if one had 1000 grasps to choose from, it would take on the order of millions grasp metric evaluations to choose the best grasp in the naive way.
+%If we can develop a policy to intelligently explore the proposed grasps and select the best one, we can reduce the computationally complexity of grasping with uncertainty.
+
+In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
+Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+We can formulate this problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
+Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
+The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
+We have a policy for exploration of different grasp plans (i.e.
+choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.
+
+We measured performance of our polices in terms of simple regret, which is the difference of the true expected value of the actual best grasp plan and the true expected value of the selected grasp plan at the given stopping time \cite{bubeck2009pure}.
+The number of samples needed before the simple regret reaches zero, determines how effective an exploration  policy is for grasp evaluation.
 
@@
 \end{figure}
-
-\subsection{Preliminaries}
-Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-We can formulate this problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
-We  have a policy for exploration of different grasp plans (i.e.
-choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far.
-
-We measured performance of our polices in terms of simple regret, which is the difference of the true expected value of the actual best grasp plan and the true expected value of the selected grasp plan at the given stopping time \cite{bubeck2009pure}.
-The number of samples needed before the simple regret reaches zero, determines how effective an exploration  policy is for grasp evaluation.
 

### 2014-10-02 paper.tex
changed stuff

--- 2014-10-01 paper.tex
@@
 
-While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
-To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
+A common method to evaluate a grasp with uncertainty is to perform Monte-Carlo integration on a grasp evaluation method.
+Methods to evaluate a grasp can either be a physics based algorithm \cite{ferrari1992}\cite{pokorny2013classical} or actually trying the grasp in simulation \cite{miller2004graspit} \cite{73}.
+Since, Monte-Carlo integration requires many evaluations to reach convergences this can be a very computationally intensive operation, when dealing with the problem of choosing the best grasp to select.
+We show that by framing this problem as a multi-arm bandit problem \cite{barto1998reinforcement}, we can intelligently select which grasps to sample from and  have shown empirically to find the best grasp an order of magnitude faster than a simple uniform sampling policy using only the simplest methods from this field.
 
@@
 
-Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
+We apply our multi-arm bandit approach to an emerging new representation in shape uncertainty, the Gaussian Process Implicit Surface, which puts a Gaussian prior on signed distance fields.
+The signed distance fields (SDFs), is a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
+This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
+To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
+Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
+
+Given a method to represent shape uncertainty a policy for grasp sampling, we still need to draw samples from a distribution to evaulate a grasp.
+A common technique is to sample from the distribution on shape and calculate the quality of grasp on that shape\cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
 Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
@@
 \begin{enumerate}
+\item Framing the selection of a grasp as from a given set as a mutli-arm bandit problem 
 	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
 	\item  Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.
-	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
+
 \end{enumerate}
@@
 
-\section{Adaptive Sampling for Grasp Selection}
-After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq.
-\ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$.
-While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
-The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig.
-\ref{fig:sampling_convergence}.
+\section{Multi-Arm Bandit for Grasp Selection}
+While a standard approach to solving the problem in Eq.
+\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
 
@@
 
-\section{Limitations and Future Work}
+\section{Limitations} 
 Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{jeffs}.
@@
 
+\section{Future Work}
+We have demonstrated how the multi-arm bandit problem can be used to sample grasps with shape uncertainty.
+However, one could imagine this approach to work with other forms of uncertainity like pose, center of mass, friction coefficient or motion.
+
+We are interested in seeing how we can apply this to different shape representations other than GPIS like polygonal \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
+Furthermore, we want to extend this to 3D and see if our simplest bandit method still works well.
+There are many different methods for exploration policies, so it would be interesting to see how well they perform in 3D as well.
+
+\section{Conclusion}
+
+We demonstrate how formulation the problem of grasp selection as multi-arm bandit method enables much more efficeint sampling of grasp plans.
+We applied this to a new method for shape uncertainity, GPIS.
+While GPIS has been used before for very interesting applications \cite{hollinger2013},\cite{jeff},\cite{dragiev2011} evaluating a grasp on it remained to computationally intensive if one sampled from the distribution on shape, $p(S)$, we present a an alternative distribution to sample from and demonstrate how it reduces computational complexity of sampling.
+
 \bibliographystyle{ieeetr}

### 2014-10-02 paper.tex
Updated the references to focus on multi-armed bandits.

--- 2014-10-01 paper.tex
@@
 
- Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic},  \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling},  \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
-Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
-for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.
-Christopoulo et al.
-sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.
+Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}, or uncertainty in contact locations with an object \cite{zheng2005}.
+The effect of uncertainty in object geometry on grasp selectiong has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
 
- The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual.
-Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}, \cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}.
-Some exciting work done with GPIS representation are the following: Hollinger et al.
-used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
-Dragiev et al.
-showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al.
-used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{jeff}.
+Currently, the most common method of evaluating grasp quality under shape and pose uncertainty is to rank a set of random grasps on an object using Monte-Carlo integration on shape and / or pose samples to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shape.
+To address this, Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} demonstrated a procedure for finding a minumum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo integration in order to rank grasps, but the method could potentially remove high quality grasps.
+Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte Carlo (MCMC) sampling to estimate grasp stability and object pose online under shape and pose uncertainty.
+MCMC simplified sampling from complicated distributions on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.
 
-  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating},  \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
-With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace.
-We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.
+The multi-armed bandit problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} is to maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probablistic reward function.
+The optimal sequence of choices if the rewards are known is to always pick the option with the maximum expected reward over the set of possible options.
+However, to discover which choice is optimal requires a balance between exploration, or choosing options that are not well known, and exploitation, or choosing the current `best' option~\cite{barto1998reinforcement}.
+Solutions to this problem, called {\it policies}, include choosing the next option based on Thompson sampling~\cite{agrawal2011analysis}, the Gittins index policy~\cite{weber1992gittins}, and by using an upper confidence bound (UCB) for the expected reward of each option~\cite{auer2002finite}.
+The UCB can be computed from the sample mean~\cite{agrawal1995sample}, Kullback-Leibler divergence~\cite{cappe2013kullback}, or a prior on the rewards~\cite{kaufmann2012bayesian}.
+Solutions to the multi-armed bandit problem are well suited to applications for which it is expensive to exhaustively evaluate all possible options, and therefore these methods have been applied to optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}.
-While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}, \cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
-Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}.
-Prior work by Kehoe et al.
-\cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed.
-To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}.
-Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.
+In this paper we consider the "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent can only explore for a finite time before deciding which arm to exploit~\cite{madani2004budgeted}.
+
+We study using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on its ability to combine various modes of nois observations such as tactile, laser and visual.
+GPIS representations model a distribution over implicit surface functions, which are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric, newcombe2011kinectfusion}.
+GPIS representations have recently been used in a number of robotic appications.
+Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
+Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
+Mahler et al. used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{jeff}. 
+Sampling from GPIS for grasp quality evaluation is computationally intensive, however, because it involves the Cholesky decomposition of an $m \times m$ matrix which takes $O(m^6)$ time, where $m$ is the dimension for a 2D grid over and object \cite{morrison1990multivariate}.
 

### 2014-10-02 paper.tex
merge jeff and zoe
New intro

@@
 \begin{abstract}
-Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.
+% Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.
 Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
@@
 a non-adaptive approach and we have statistical guarantees with our method.
+%Grasp quality evaluation under uncertainty is ...
+In new robotic environments, uncertainty in pose and shape can arise from sensor noise, occlusions, and surface properties such as transparency and specularity.
+We show that framing grasp quality evaluation as a multi-armed bandit problem provides a principled way to reason about evaluating multiple grasps on an uncertain shape quickly.
+We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS).
+We utilize successive elimination to solve a multi-armed bandit problem and show a speedup in sample complexity versus evaluating grasps using Monte-Carlo integration, a popular method.
 \end{abstract}
@@
 \todo{Get High res GPIS visualizations, Incorporate next round of feedback}
-Consider a robot packing boxes in a shipping warehouse environment.
-The robot will frequently encounter objects that it has not seen before.
-The robot will have to plan stable grasps without any prior information other than its sensor data.
-As seen in Fig.
-\ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations.
-Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
 
-A common method to evaluate a grasp with uncertainty is to perform Monte-Carlo integration on a grasp evaluation method.
-Methods to evaluate a grasp can either be a physics based algorithm \cite{ferrari1992}\cite{pokorny2013classical} or actually trying the grasp in simulation \cite{miller2004graspit} \cite{73}.
-Since, Monte-Carlo integration requires many evaluations to reach convergences this can be a very computationally intensive operation, when dealing with the problem of choosing the best grasp to select.
-We show that by framing this problem as a multi-arm bandit problem \cite{barto1998reinforcement}, we can intelligently select which grasps to sample from and  have shown empirically to find the best grasp an order of magnitude faster than a simple uniform sampling policy using only the simplest methods from this field.
+Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
+The robot may need to plan grasps for these objects without prior knowledge of their shape and pose.
+However, the robot may not be able to measure these quantities exactly due to sensor noise and missing data due to partial visibility and object properties such as transparency.
+Grasp planners that assume an exact measurement of shape and pose may fail, for example wh
+This motivates using a representation of shape uncertainty to select grasps, but most current methods for evaluating quality under these representations use a brute-force sampling of shapes to evaluate grasp quality, which can be slow.
+
+%To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
+Often when evaluating grasps in this manner, there are a number of grasps that can be quickly shown to be inferior.
+When allocating resources to determine the best grasp, this information should be used in order to spend less time evaluating bad grasps.
+Multi-armed bandits provide a principled way to reason about evaluating multiple grasps and discarding grasps that are likely to be inferior.
 
@@
 
-We apply our multi-arm bandit approach to an emerging new representation in shape uncertainty, the Gaussian Process Implicit Surface, which puts a Gaussian prior on signed distance fields.
-The signed distance fields (SDFs), is a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}.
-To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
+We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
+GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
 
-Given a method to represent shape uncertainty a policy for grasp sampling, we still need to draw samples from a distribution to evaulate a grasp.
+%Given a method to represent shape uncertainty a policy for grasp sampling, we still need to draw samples from a distribution to evaulate a grasp.
 A common technique is to sample from the distribution on shape and calculate the quality of grasp on that shape\cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
@@
 Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory.
-In light of this our contributions are the following:
+
+Our contributions are the following:
 
 \begin{enumerate}
-\item Framing the selection of a grasp as from a given set as a mutli-arm bandit problem 
-	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
-	\item  Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.
-
+	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
+	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.
 \end{enumerate}

### 2014-10-02 paper.tex
reordered MAB, related work, problem def and line of action and clarified and expanded MAB

--- 2014-10-02 paper.tex
@@
 
+The multi-armed bandit problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} is to maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probabilistic reward function.
+The optimal sequence of choices if the rewards are known is to always pick the option with the maximum expected reward over the set of possible options.
+However, to discover which choice is optimal requires a balance between exploration, or choosing options that are not well known, and exploitation, or choosing the current `best' option~\cite{barto1998reinforcement}.
+Solutions to this problem, called {\it policies}, include choosing the next option based on Thompson sampling~\cite{agrawal2011analysis}, the Gittins index policy~\cite{weber1992gittins}, and by using an upper confidence bound (UCB) for the expected reward of each option~\cite{auer2002finite}.
+The UCB can be computed from the sample mean~\cite{agrawal1995sample}, Kullback-Leibler divergence~\cite{cappe2013kullback}, or a prior on the rewards~\cite{kaufmann2012bayesian}.
+Solutions to the multi-armed bandit problem are well suited to applications for which it is expensive to exhaustively evaluate all possible options, and therefore these methods have been applied to optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+In this paper we consider the "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent can only explore for a finite time before deciding which arm to exploit~\cite{madani2004budgeted}.
+
 Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}, or uncertainty in contact locations with an object \cite{zheng2005}.
@@
 
-The multi-armed bandit problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} is to maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probablistic reward function.
-The optimal sequence of choices if the rewards are known is to always pick the option with the maximum expected reward over the set of possible options.
-However, to discover which choice is optimal requires a balance between exploration, or choosing options that are not well known, and exploitation, or choosing the current `best' option~\cite{barto1998reinforcement}.
-Solutions to this problem, called {\it policies}, include choosing the next option based on Thompson sampling~\cite{agrawal2011analysis}, the Gittins index policy~\cite{weber1992gittins}, and by using an upper confidence bound (UCB) for the expected reward of each option~\cite{auer2002finite}.
-The UCB can be computed from the sample mean~\cite{agrawal1995sample}, Kullback-Leibler divergence~\cite{cappe2013kullback}, or a prior on the rewards~\cite{kaufmann2012bayesian}.
-Solutions to the multi-armed bandit problem are well suited to applications for which it is expensive to exhaustively evaluate all possible options, and therefore these methods have been applied to optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-
-In this paper we consider the "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent can only explore for a finite time before deciding which arm to exploit~\cite{madani2004budgeted}.
-
-We study using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on its ability to combine various modes of nois observations such as tactile, laser and visual.
+We study using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on its ability to combine various modes of noise observations such as tactile, laser and visual.
 GPIS representations model a distribution over implicit surface functions, which are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric, newcombe2011kinectfusion}.
@@
 
-In this section we describe the multi-arm bandit problem and how it relates to grasping.
+In this section we describe the multi-arm bandit problem and the formal definition of our problem.
 
@@
 When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
-In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance \cite{kuleshov}.
+In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
 
-\subsection{Budgeted Multi-Arm Bandit Problem and Grasping}
-%In the problem of choosing the best grasp, one must intelligently allocate samples based on the observations received so far.
-%As you can in Fig. \ref{fig:sampling_convergence}, a typical grasp can take hundreds of iterations for convergence of the expected value to be reach.
-%Thus if one had 1000 grasps to choose from, it would take on the order of millions grasp metric evaluations to choose the best grasp in the naive way.
-%If we can develop a policy to intelligently explore the proposed grasps and select the best one, we can reduce the computationally complexity of grasping with uncertainty.
+We can formulate our problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
+The budgeted multi-arm bandit problem has a finite stopping time.
+The objective of the budgeted multi-arm bandit problem is to minimize the "simple regret", which is the difference between the true expected value of the actual best arm and the true expected value of the arm pulled at the stopping time.
+Thus the budgeted multi-arm bandit problem reduces to exploration until the very last time step, at which time one exploitation step is taken.
 
+\subsection{Line of action}
+Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
+\ref{fig:line_of_action}.
+A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
+\todo{move the next two lines}
+While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
+Future work will look at how to efficiently sample when the approach trajectory has noise.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide01.jpg}
+\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+\vspace*{-10pt}
+\label{fig:line_of_action}
+\end{figure}
+
+\subsection{Problem Definition}
+
+Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model (we will describe the GPIS model later) and set of possible grasp plans $G$.
+We are interested in determining
+
+\begin{align}\label{eq:problem_def}
+\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
+\end{align}
+
+with respect to a chosen grasp metric Q.
+
+\subsection{Multi-Arm Bandits for Grasping}
 In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
 Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-We can formulate this problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
 Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
@@
 choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.
-
-We measured performance of our polices in terms of simple regret, which is the difference of the true expected value of the actual best grasp plan and the true expected value of the selected grasp plan at the given stopping time \cite{bubeck2009pure}.
 The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.
-
-\todo{Add Multi arm bandit preliminary make it long}
 
@@
 Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\subsection{Line of Action}
-Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
-\ref{fig:line_of_action}.
-A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on.
-Future work will look at how to efficiently sample when the approach trajectory has noise.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide01.jpg}
-\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-\vspace*{-10pt}
-\label{fig:line_of_action}
-\end{figure}
-
-\subsection{Problem Definition}
-
-Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model and set of possible grasp plans $G$. We are interested in determining
-
-\begin{align}\label{eq:problem_def}
-\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
-\end{align}
-
-with respect to a chosen grasp metric Q.
 

### 2014-10-02 paper.tex
Intro is quite a bit better methinks

--- 2014-10-02 paper.tex
@@
 %Grasp quality evaluation under uncertainty is ...
-In new robotic environments, uncertainty in pose and shape can arise from sensor noise, occlusions, and surface properties such as transparency and specularity.
-We show that framing grasp quality evaluation as a multi-armed bandit problem provides a principled way to reason about evaluating multiple grasps on an uncertain shape quickly.
-We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS).
-We utilize successive elimination to solve a multi-armed bandit problem and show a speedup in sample complexity versus evaluating grasps using Monte-Carlo integration, a popular method.
+In unknown or changing environments such as warehouses for consumer goods, robots may need to quickly plan grasps on previously unknown objects.
+Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
+Dealing with this uncertainty can be computationally demanding
+Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
+In this paper, we show that framing grasp planning as a multi-armed bandit problem, a standard framework for making sequential descisions, provides a principled way to quickly select a grasp from a set of candidates on an uncertain shape.
+We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
+We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of T versus planning grasps using existing methods.
 \end{abstract}
@@
 
-\vspace{10pt}
-
-\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
+%\vspace{10pt}
+%\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
 
 Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
-The robot may need to plan grasps for these objects without prior knowledge of their shape and pose.
+The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape and pose.
 However, the robot may not be able to measure these quantities exactly due to sensor noise and missing data due to partial visibility and object properties such as transparency.
-Grasp planners that assume an exact measurement of shape and pose may fail, for example wh
-This motivates using a representation of shape uncertainty to select grasps, but most current methods for evaluating quality under these representations use a brute-force sampling of shapes to evaluate grasp quality, which can be slow.
+Grasp planners that assume an exact measurement of shape, pose, or its own state may fail.
 
-%To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
-Often when evaluating grasps in this manner, there are a number of grasps that can be quickly shown to be inferior.
-When allocating resources to determine the best grasp, this information should be used in order to spend less time evaluating bad grasps.
-Multi-armed bandits provide a principled way to reason about evaluating multiple grasps and discarding grasps that are likely to be inferior.
+This motivates using knowledge of uncertainty to select grasps, but most current methods for evaluating the quality of a single grasp in the presence of uncertainty require use an exhaustive sampling over the possible values of the uncertain quantity \cite{kehoe2012toward, kim2012physically, weisz2012pose}.
+To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
+However, when ranking a set of grasps we may be able to determine the relative quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
+Thus, we can adaptively concentrate grasp evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
 
-\begin{figure}[ht!]
+The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+%Solutions to the MAB problem are well-suited to applications for which it is too expensive to evaluate all possible options and have therefore been applied to the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
+Solutions to the MAB problem are most useful in applications where it is too expensive to fully evaluate a set of options and have therefore been applied to the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+
+\todo{ref figure}
+
+Our main contribution in this paper is formulating the problem of selecting grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
+We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
+
+\begin{figure}[t!]
 \centering
@@
 
-We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
-GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
+%We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
+%GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
 
@@
 
-Our contributions are the following:
-
-\begin{enumerate}
-	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
-	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.
-\end{enumerate}
+%Our contributions are the following:
+% 
+%\begin{enumerate}
+%	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
+%	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.
+%\end{enumerate}
 

### 2014-10-02 paper.tex
MAB for grasping changed

--- 2014-10-02 paper.tex
@@
 
-\subsection{Multi-Arm Bandits for Grasping}
+\subsection{Multi-Arm Bandits for Grasp Selection}
+While a standard approach to solving the problem in Eq.
+\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
 In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
@@
 The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.
+
+In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
+Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
+Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information. \todo{double check with Dylan}
+
+For our exploration policy, we maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
+During exploration, we sample uniformly from this subset.
+This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
+For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
+The width of the confidence interval for a grasp plan $i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
+
+\vspace{-2ex}
+\begin{align}
+C_{ i} := \frac{1.96 \sigma_i}{\sqrt{n_i}}.
+\end{align}
+
+Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.
+Then the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
+After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
+Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}.
+In future work, we will look at using other exploration strategies.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
+\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
+You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
+\vspace*{-10pt}
+\label{fig:sampling_convergence}
+\end{figure}
 
@@
 Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\section{Multi-Arm Bandit for Grasp Selection}
-While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
-\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
-You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
-\vspace*{-10pt}
-\label{fig:sampling_convergence}
-\end{figure}
-
-\subsection{Our Implementation}
-In solving Eq.
-\ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
-Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
-Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information.
-\todo{double check with Dylan}
-
-For our exploration policy, we maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
-During exploration, we sample uniformly from this subset.  This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
-For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
-The width of the confidence interval for a grasp plan $i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
-
-\vspace{-2ex}
-\begin{align}
-C_{ i} := \frac{1.96 \sigma_i}{\sqrt{n_i}}.
-\end{align}
-
-Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.  Thus the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
-After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
-Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}.
-In future work, we will look at using other exploration strategies.
 

### 2014-10-02 paper.tex

--- 2014-10-02 paper.tex
@@
 When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
-In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance \cite{kuleshov}.
+In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
 
-\subsection{Budgeted Multi-Arm Bandit Problem and Grasping}
-%In the problem of choosing the best grasp, one must intelligently allocate samples based on the observations received so far.
-%As you can in Fig. \ref{fig:sampling_convergence}, a typical grasp can take hundreds of iterations for convergence of the expected value to be reach.
-%Thus if one had 1000 grasps to choose from, it would take on the order of millions grasp metric evaluations to choose the best grasp in the naive way.
-%If we can develop a policy to intelligently explore the proposed grasps and select the best one, we can reduce the computationally complexity of grasping with uncertainty.
+We can formulate our problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
+The budgeted multi-arm bandit problem has a finite stopping time.
+The objective of the budgeted multi-arm bandit problem is to minimize the "simple regret", which is the difference between the true expected value of the actual best arm and the true expected value of the arm pulled at the stopping time.
+Thus the budgeted multi-arm bandit problem reduces to exploration until the very last time step, at which time one exploitation step is taken.
 
+\subsection{Line of action}
+Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
+\ref{fig:line_of_action}.
+A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
+\todo{move the next two lines}
+While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
+Future work will look at how to efficiently sample when the approach trajectory has noise.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide01.jpg}
+\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+\vspace*{-10pt}
+\label{fig:line_of_action}
+\end{figure}
+
+\subsection{Problem Definition}
+
+Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model (we will describe the GPIS model later) and set of possible grasp plans $G$.
+We are interested in determining
+
+\begin{align}\label{eq:problem_def}
+\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
+\end{align}
+
+with respect to a chosen grasp metric Q.
+
+\subsection{Multi-Arm Bandits for Grasp Selection}
+While a standard approach to solving the problem in Eq.
+\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
 In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
 Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-We can formulate this problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
 Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
@@
 choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.
-
-We measured performance of our polices in terms of simple regret, which is the difference of the true expected value of the actual best grasp plan and the true expected value of the selected grasp plan at the given stopping time \cite{bubeck2009pure}.
 The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.
 
-\todo{Add Multi arm bandit preliminary make it long}
+In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
+Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
+Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information. \todo{double check with Dylan}
+
+For our exploration policy, we maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
+During exploration, we sample uniformly from this subset.
+This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
+For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
+The width of the confidence interval for a grasp plan $i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
+
+\vspace{-2ex}
+\begin{align}
+C_{ i} := \frac{1.96 \sigma_i}{\sqrt{n_i}}.
+\end{align}
+
+Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.
+Then the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
+After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
+Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}.
+In future work, we will look at using other exploration strategies.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
+\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
+You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
+\vspace*{-10pt}
+\label{fig:sampling_convergence}
+\end{figure}
 
@@
 Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\subsection{Line of Action}
-Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
-\ref{fig:line_of_action}.
-A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on.
-Future work will look at how to efficiently sample when the approach trajectory has noise.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide01.jpg}
-\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-\vspace*{-10pt}
-\label{fig:line_of_action}
-\end{figure}
-
-\subsection{Problem Definition}
-
-Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model and set of possible grasp plans $G$. We are interested in determining
-
-\begin{align}\label{eq:problem_def}
-\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
-\end{align}
-
-with respect to a chosen grasp metric Q.
-
-\section{Multi-Arm Bandit for Grasp Selection}
-While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
-\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
-You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
-\vspace*{-10pt}
-\label{fig:sampling_convergence}
-\end{figure}
-
-\subsection{Our Implementation}
-In solving Eq.
-\ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
-Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
-Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information.
-\todo{double check with Dylan}
-
-For our exploration policy, we maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
-During exploration, we sample uniformly from this subset.  This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
-For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
-The width of the confidence interval for a grasp plan $i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
-
-\vspace{-2ex}
-\begin{align}
-C_{ i} := \frac{1.96 \sigma_i}{\sqrt{n_i}}.
-\end{align}
-
-Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.  Thus the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
-After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
-Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}.
-In future work, we will look at using other exploration strategies.
 

### 2014-10-02 paper.tex
changed experiments

--- 2014-10-02 paper.tex
@@
 \title{\LARGE \bf
-Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-13 09-30-2014]}
+Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]}
 
@@
 \begin{abstract}
+
 % Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.
@@
 a non-adaptive approach and we have statistical guarantees with our method.
+
 %Grasp quality evaluation under uncertainty is ...
-In unknown or changing environments such as warehouses for consumer goods, robots may need to quickly plan grasps on previously unknown objects.
-Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
-Dealing with this uncertainty can be computationally demanding
-Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
-In this paper, we show that framing grasp planning as a multi-armed bandit problem, a standard framework for making sequential descisions, provides a principled way to quickly select a grasp from a set of candidates on an uncertain shape.
-We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
-We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of T versus planning grasps using existing methods.
+
+In new robotic environments, uncertainty in pose and shape can arise from sensor noise, occlusions, and surface properties such as transparency and specularity.
+
+We show that framing grasp quality evaluation as a multi-armed bandit problem provides a principled way to reason about evaluating multiple grasps on an uncertain shape quickly.
+
+We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS).
+
+We utilize successive elimination to solve a multi-armed bandit problem and show a speedup in sample complexity versus evaluating grasps using Monte-Carlo integration, a popular method.
+
 \end{abstract}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
 
-%\vspace{10pt}
-%\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
+\vspace{10pt}
+
+\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
 
 Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
-The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape and pose.
-However, the robot may not be able to measure these quantities exactly due to sensor noise and missing data due to partial visibility and object properties such as transparency.
-Grasp planners that assume an exact measurement of shape, pose, or its own state may fail.
 
-This motivates using knowledge of uncertainty to select grasps, but most current methods for evaluating the quality of a single grasp in the presence of uncertainty require use an exhaustive sampling over the possible values of the uncertain quantity \cite{kehoe2012toward, kim2012physically, weisz2012pose}.
-To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
-However, when ranking a set of grasps we may be able to determine the relative quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
-Thus, we can adaptively concentrate grasp evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
+The robot may need to plan grasps for these objects without any prior information other than its sensor data.
 
-The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
-%Solutions to the MAB problem are well-suited to applications for which it is too expensive to evaluate all possible options and have therefore been applied to the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
-Solutions to the MAB problem are most useful in applications where it is too expensive to fully evaluate a set of options and have therefore been applied to the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+As seen in Fig. \ref{fig:noisy data}, it is unavoidable that sensors will have missing or noisy data due to surface properties, such as specularity and transparency.
 
-\todo{ref figure}
+Grasp planners based on an exact representation of shape may fail.
 
-Our main contribution in this paper is formulating the problem of selecting grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
-We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
+This motivates using a representation of shape uncertainty to select grasps, but most current methods for evaluating quality under these representations use a brute-force sampling of shapes to evaluate grasp quality, which can be slow.
 
-\begin{figure}[t!]
+%To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
+
+Often when evaluating grasps in this manner, there are a number of grasps that can be quickly shown to be inferior.
+
+When allocating resources to determine the best grasp, this information should be used in order to spend less time evaluating bad grasps.
+
+Multi-armed bandits provide a principled way to reason about evaluating multiple grasps and discarding grasps that are likely to be inferior.
+
+\begin{figure}[ht!]
 \centering
-\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
+\includegraphics[width=8.5cm,height=8cm]{figures/Slide02.jpg}
 \caption{\footnotesize
-Left: HD image of a common measuring cup from in a household environment.
-Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
+Convergance in regret of the bandit sampling method (red), compared to the traditional Monte-Carlo method.
+The fast convergence of the bandit method is due to its ability to intelligently pick what grasp to sample next in a given set of proposed grasps on an object with shape uncertainty}
 \vspace*{-10pt}
@@
 
-%We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
-%GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
+We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
+
+GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
 
@@
 
-%Our contributions are the following:
-% 
-%\begin{enumerate}
-%	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
-%	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.
-%\end{enumerate}
+Our contributions are the following:
+
+\begin{enumerate}
+
+	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
+
+	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.
+
+\end{enumerate}
 
@@
 
+\subsection{Multi-Arm Bandit Experiments}
+
+We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$.
+For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$.
+In Fig.
+\ref{fig:simple_regret}, we plotted the simple regret for three of the shapes in our data set averaged over 100 runs and compare it to the Monte-Carlo method that randomly chooses a grasp plan to draw a sample from.
+We initialize both the Monte-Carlo and bandit technique by sampling each grasp 2 times this is to achieve the standard deviation.
+We draw samples from our calculated distributions $p(g)$.
+The most interesting thing is that the regret is minimized at least an order of magnitude faster than the naive approach for the shapes we considered, thus motivating the use of including observations as you select samples.
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 17cm, height = 12cm]{figures/Slide09.jpg}
+\caption{ \footnotesize Top: Comparison of two sampling methods.
+Red is the multi-arm bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
+We measure their ability to converge in terms of simple regret averaged over 100 runs.
+We had them determine the best grasp when $|G|=1000$.
+In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration.
+Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{jeffs}}
+\vspace*{-10pt}
+\label{fig:simple_regret}
+\end{figure*}
+
 \subsection{Sampling from Grasps Vs. Shape}
@@
 \caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace.
-Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Green is sampling from $p(g)$ or the calculated distribution on grasps.
+Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Red is sampling from $p(g)$ or the calculated distribution on grasps.
 As you can see sampling from the calculated distributions scales much better.
@@
 
-\subsection{Adaptive Sampling Technique}
+\section{Limitations}
 
-We consider the problem of selecting the best grasp out of a set $G$ given a fix number of iterations $I$.
-For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$ and $I= 7000$ or when the set of grasps is a single grasp.
-In Fig.
-\ref{fig:simple_regret}, we plotted the simple regret, Eq.
-\ref{eq:simple_regret}, averaged over 20 runs and compare it to the naive Monte-Carlo method that randomly chooses a grasp plan to draw a sample from .
-The most interesting thing is that the regret is minimized an order of magnitude faster than the naive approach, thus motivating the use of including observations as you select samples.
+Our budgeted multi-arm bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
+Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.
+While we have empirically seen the bandit method always converge to the correct value, our method only has a statistical guarantee of doing so.
+A low quality grasp plan could be found, albeit with a low probability.
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide09.jpg}
-\caption{ \footnotesize Comparison of two sampling methods.
-Green is the adaptive bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
-We measure their ability to converge in terms of simple regret Eq.
-\ref{eq:simple_regret} averaged over 100 runs.
-We had them determine the best grasp when $|G|=1000$.
-As you can see our method converges much faster with an average of evaluation of 4 samples per grasp.
-We start the process though by deterministically evaluating every grasp 2 times to achieve a baseline, which explains the first part of the graph.}
-\vspace*{-10pt}
-\label{fig:simple_regret}
-\end{figure}
-
-\section{Limitations} 
 Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{jeffs}.
@@
 
-Our budgeted multi-arm bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
-Future work will be building an efficient construction of GPIS to scale to 3D.
-Lastly, we are interested in investigating how well our algorithm works in parallel computing to be used in the cloud computing context.
-Furthermore, their is a large literature on formulating bandit policies and experimenting with them all will need to be done to see which one works best.
+\section{Conclusion}
+Assessing grasp quality under shape uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
+In this work, we proposed a multi-arm bandit approach to efficiently identify high-quality grasps under shape uncertainty. 
+A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
+ we found that the Successive Elimination multi-arm bandit approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
+A pre-requisite for applying a bandit approach is to formulate an efficient representation of how shape uncertainty affects grasp parameters and thus grasp quality.
+We modeled uncertainty with Gaussian Process Implicit Surfaces (GPIS) and derived the distribution of grasp parameters when a nominal grasp is applied to the GPIS.
+As a result, we were able to more efficiently sample from a distribution of grasps executions rather than the shape; leading to a complexity improvement of $n^3$ in the resolution of the representation.
+We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it performs on average a magnitude faster than a naive uniform sampling approach in our experiments, and (3) sampling from the grasp contacts is 12x faster than sampling from shapes for a 64x64 grid.
 
 \section{Future Work}
-We have demonstrated how the multi-arm bandit problem can be used to sample grasps with shape uncertainty.
-However, one could imagine this approach to work with other forms of uncertainity like pose, center of mass, friction coefficient or motion.
-
-We are interested in seeing how we can apply this to different shape representations other than GPIS like polygonal \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
-Furthermore, we want to extend this to 3D and see if our simplest bandit method still works well.
-There are many different methods for exploration policies, so it would be interesting to see how well they perform in 3D as well.
-
-\section{Conclusion}
-
-We demonstrate how formulation the problem of grasp selection as multi-arm bandit method enables much more efficeint sampling of grasp plans.
-We applied this to a new method for shape uncertainity, GPIS.
-While GPIS has been used before for very interesting applications \cite{hollinger2013},\cite{jeff},\cite{dragiev2011} evaluating a grasp on it remained to computationally intensive if one sampled from the distribution on shape, $p(S)$, we present a an alternative distribution to sample from and demonstrate how it reduces computational complexity of sampling.
+Our results are promising and they suggest many avenues of future work.
+First, we are actively working to apply this approach to 3D environments.
+In particular, we are interested in investigating the entire end-to-end pipeline of perception, grasp planning, and grasp execution.
+Next, in principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
+It can further be applied to other grasp quality metrics.
+Next, we are investigating the application of recent results from reinforcement learning or bandit theory for analytic stopping criteria for the sampling.
+One particular challenge is that shape uncertainty is rarely parametric leading to problems with many recent bounds and optimality conditions.
 

### 2014-10-02 paper.tex

@@
 \begin{abstract}
-
-% Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.
-Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
-Given a GPIS model this would mean sampling from the signed distance field in a uniform grid of side length $n$.
-The computational complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
-We propose an alternative to sampling from shape distributions and demonstrate how this reduces the computational complexity to $O(n^3)$ in both 3D and 2D for evaluation of a single grasp.
-We furthermore introduce the idea of adaptive sampling in the context of choosing the best grasp given a set of grasps and a GPIS object model by formulating it as a budgeted multi-arm bandit problem.
-We show an order of magnitude reduction in the number of samples needed vs.
-a non-adaptive approach and we have statistical guarantees with our method.
-
-%Grasp quality evaluation under uncertainty is ...
-
-In new robotic environments, uncertainty in pose and shape can arise from sensor noise, occlusions, and surface properties such as transparency and specularity.
-
-We show that framing grasp quality evaluation as a multi-armed bandit problem provides a principled way to reason about evaluating multiple grasps on an uncertain shape quickly.
-
-We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS).
-
-We utilize successive elimination to solve a multi-armed bandit problem and show a speedup in sample complexity versus evaluating grasps using Monte-Carlo integration, a popular method.
-
+In unknown or changing environments such as warehouses for consumer goods, robots may need to quickly plan grasps on previously unknown objects.
+Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
+Dealing with this uncertainty can be computationally demanding
+Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
+In this paper, we show that framing grasp planning as a multi-armed bandit problem, a standard framework for making sequential descisions, provides a principled way to quickly select a grasp from a set of candidates on an uncertain shape.
+We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
+We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of T versus planning grasps using existing methods.
 \end{abstract}
@@
 
-\vspace{10pt}
-
-\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
+%\vspace{10pt}
+%\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
 
 Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
+The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape and pose.
+However, the robot may not be able to measure these quantities exactly due to sensor noise and missing data due to partial visibility and object properties such as transparency.
+Grasp planners that assume an exact measurement of shape, pose, or its own state may fail.
 
-The robot may need to plan grasps for these objects without any prior information other than its sensor data.
+This motivates using knowledge of uncertainty to select grasps, but most current methods for evaluating the quality of a single grasp in the presence of uncertainty require use an exhaustive sampling over the possible values of the uncertain quantity \cite{kehoe2012toward, kim2012physically, weisz2012pose}.
+To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
+However, when ranking a set of grasps we may be able to determine the relative quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
+Thus, we can adaptively concentrate grasp evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
 
-As seen in Fig. \ref{fig:noisy data}, it is unavoidable that sensors will have missing or noisy data due to surface properties, such as specularity and transparency.
+The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
+Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-Grasp planners based on an exact representation of shape may fail.
+\todo{ref figure}
 
-This motivates using a representation of shape uncertainty to select grasps, but most current methods for evaluating quality under these representations use a brute-force sampling of shapes to evaluate grasp quality, which can be slow.
+Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
+We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
 
-%To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
-
-Often when evaluating grasps in this manner, there are a number of grasps that can be quickly shown to be inferior.
-
-When allocating resources to determine the best grasp, this information should be used in order to spend less time evaluating bad grasps.
-
-Multi-armed bandits provide a principled way to reason about evaluating multiple grasps and discarding grasps that are likely to be inferior.
-
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
@@
 \end{figure}
-
-We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
-
-GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.
-
-%Given a method to represent shape uncertainty a policy for grasp sampling, we still need to draw samples from a distribution to evaulate a grasp.
-A common technique is to sample from the distribution on shape and calculate the quality of grasp on that shape\cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}.
-Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
-Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}.
-We constrain the contact points by considering the approach trajectory of a gripper.
-Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory.
-
-Our contributions are the following:
-
-\begin{enumerate}
-
-	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
-
-	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.
-
-\end{enumerate}
 

### 2014-10-02 paper.tex
sections for MAB and problem def

@@
 
-\section{Preliminaries and Problem Statement}
-
-In this section we describe the multi-arm bandit problem and the formal definition of our problem.
-
-\subsection{Multi-Arm Bandit Problem}
+\section{Multi-Arm Bandit Problem}
 The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
@@
 Thus the budgeted multi-arm bandit problem reduces to exploration until the very last time step, at which time one exploitation step is taken.
+
+\section{Problem Definition}
+Before we present the problem definition, we introduce the grasping model, the line of action.
 
@@
 
-\subsection{Multi-Arm Bandits for Grasp Selection}
+\section{Multi-Arm Bandits for Grasp Selection}
 While a standard approach to solving the problem in Eq.

### 2014-10-02 paper.tex
author list attributions

@@
 
-\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\ Jur Van Den Berg,  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
+\author{Michael Laskey$^1$, Zoe McCarthy$^1$, Jeff Mahler$^1$, Florian T.
+Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
+\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\tt\small goldberg@berkeley.edu}}%
+\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
+\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\tt\small \{fpokorny, dani\}@kth.se}}%
+\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\tt\small jurvandenberg@gmail.com}}%
+}
 

### 2014-10-02 paper.tex
Edited intro, related work, fixed references

--- 2014-10-02 paper.tex
@@
 Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
-Dealing with this uncertainty can be computationally demanding
 Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
@@
 
-The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
 The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
@@
 We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
+We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
 Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
@@
 
-The multi-armed bandit problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} is to maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probabilistic reward function.
-The optimal sequence of choices if the rewards are known is to always pick the option with the maximum expected reward over the set of possible options.
-However, to discover which choice is optimal requires a balance between exploration, or choosing options that are not well known, and exploitation, or choosing the current `best' option~\cite{barto1998reinforcement}.
+The multi-armed bandit (MAB) problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} considers maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probabilistic reward function.
 Solutions to this problem, called {\it policies}, include choosing the next option based on Thompson sampling~\cite{agrawal2011analysis}, the Gittins index policy~\cite{weber1992gittins}, and by using an upper confidence bound (UCB) for the expected reward of each option~\cite{auer2002finite}.
 The UCB can be computed from the sample mean~\cite{agrawal1995sample}, Kullback-Leibler divergence~\cite{cappe2013kullback}, or a prior on the rewards~\cite{kaufmann2012bayesian}.
-Solutions to the multi-armed bandit problem are well suited to applications for which it is expensive to exhaustively evaluate all possible options, and therefore these methods have been applied to optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+Solutions to the multi-armed bandit problem have been used in applications for which evaluating all possible options is expeinsive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 In this paper we consider the "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent can only explore for a finite time before deciding which arm to exploit~\cite{madani2004budgeted}.
 
-Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}, or uncertainty in contact locations with an object \cite{zheng2005}.
-The effect of uncertainty in object geometry on grasp selectiong has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
+Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
+The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
 
-Currently, the most common method of evaluating grasp quality under shape and pose uncertainty is to rank a set of random grasps on an object using Monte-Carlo integration on shape and / or pose samples to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+Currently, the most common method of evaluating grasp quality under shape and pose uncertainty is to rank a set of random grasps on an object using Monte-Carlo integration on shape and pose samples to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
 Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shape.
-To address this, Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} demonstrated a procedure for finding a minumum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo integration in order to rank grasps, but the method could potentially remove high quality grasps.
+To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minumum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo integration in order to rank grasps, but the adaptive sampling method involes several hyperparameters whereas our proposed budgeted MAB solution does not.
 Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte Carlo (MCMC) sampling to estimate grasp stability and object pose online under shape and pose uncertainty.
@@
 
-We study using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on its ability to combine various modes of noise observations such as tactile, laser and visual.
-GPIS representations model a distribution over implicit surface functions, which are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric, newcombe2011kinectfusion}.
-GPIS representations have recently been used in a number of robotic appications.
+We study our MAB sampling method using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on the ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
 Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
 Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al. used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{jeff}. 
-Sampling from GPIS for grasp quality evaluation is computationally intensive, however, because it involves the Cholesky decomposition of an $m \times m$ matrix which takes $O(m^6)$ time, where $m$ is the dimension for a 2D grid over and object \cite{morrison1990multivariate}.
+Mahler et al. used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}. 
+However, sampling from GPIS for grasp quality evaluation is computationally intensive because it involves the Cholesky decomposition of an $m \times m$ matrix which takes $O(m^6)$ time, where $m$ is the dimension for a 2D grid over and object \cite{morrison1990multivariate}.
+Therefore, GPIS is a good illustration of benefits provided by our efficient MAB approach to grasp planning.
 
@@
 \subsection{Multi-Arm Bandit Problem}
-The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
+The multi-arm bandit problem originally described by Robbins \cite{robbins1952some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
 The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
 A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
-Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
+Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
 
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
-\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
+%\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
 Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
 }
-\vspace*{-10pt}
-\label{fig:GPIS_TSDF}
-\end{figure}
+%\vspace*{-10pt}
+%\label{fig:GPIS_TSDF}
+%\end{figure}
 %\section{Related Work}
@@
 
-\bibliographystyle{ieeetr}
+\bibliographystyle{IEEEtranS}
 \bibliography{references}

### 2014-10-02 paper.tex

@@
 
-\section{Preliminaries and Problem Statement}
-
-In this section we describe the multi-arm bandit problem and the formal definition of our problem.
-
-\subsection{Multi-Arm Bandit Problem}
-The multi-arm bandit problem originally described by Robbins \cite{robbins1952some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
+\section{Multi-Arm Bandit Problem}
+The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
 The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.

### 2014-10-02 paper.tex
changes michael

--- 2014-10-02 paper.tex
@@
 
-\author{Michael Laskey$^1$, Zoe McCarthy$^1$, Jeff Mahler$^1$, Florian T.
-Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
-\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\tt\small goldberg@berkeley.edu}}%
-\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
-\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\tt\small \{fpokorny, dani\}@kth.se}}%
-\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\tt\small jurvandenberg@gmail.com}}%
-}
+\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\ Jur Van Den Berg,  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
 
@@
 
-\subsection{Gaussian Process (GP) Background} \todo{massive trim down}
-GPs provide an infinite dimensional analogue of Multivariate
-Gaussian Distributions which allow us to model distributions over
-functions.
-Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2010gaussian}.
-In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}$, $\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
-The observations are assumed to be noisy measurements from the unknown target function $f$:
-\begin{equation}
-y_i = f(\bx_i) + \epsilon,
-\end{equation}
-where $\epsilon \sim \mN(0,\sigma^2)$ is Gaussian noise in the observations.
-A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
+\section{Evaluating a Grasp}
+ In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$.
+We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating the expectation $E$ efficiently.
+
+\subsection{Gaussian Process (GP) Background}
+Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
 \begin{align*}
-	p(f_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
+	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
 	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
@@
 \begin{align}
-	\text{cov}\left(f(\bx_i), f(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
+	\text{cov}\left(sd(\bx_i), sd(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
+	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, sd(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
+	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, \frac{\partial sd (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
 \end{align}
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
-\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
-Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
-}
-\vspace*{-10pt}
-\label{fig:GPIS_TSDF}
-\end{figure}
-%\section{Related Work}
-
-For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability.
+For our kernel choice we decided to use the square exponential kernel, similar to \cite{dragiev2011}.
 Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
@@
 Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\section{Evaluating a Grasp}
- In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$.
-We will first discuss which grasp metric $Q$ we chose and then proceed into evaluating the expectation $E$ efficiently.
 

### 2014-10-02 paper.tex

--- 2014-10-02 paper.tex
@@
 \begin{align}
-	\text{cov}\left(f(\bx_i), f(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
+	\text{cov}\left(sd(\bx_i), sd(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
+	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, sd(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
+	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, \frac{\partial sd (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
 \end{align}
 
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
-%\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
-Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
-}
-%\vspace*{-10pt}
-%\label{fig:GPIS_TSDF}
-%\end{figure}
-%\section{Related Work}
-
-For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability.
+For our kernel choice we decided to use the square exponential kernel, similar to \cite{dragiev2011}.
 Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.

### 2014-10-02 paper.tex
changed n to l for GP

@@
 \end{align*}
-where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
+where $K \in \mathbb{R}^{l \times l}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_l,\bx_*)]^{\intercal}$. 
 This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:

### 2014-10-02 paper.tex
got rid of todos

@@
 
-\todo{ref figure}
-
 Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
@@
 Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-\todo{move the next two lines}
 While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
@@
 Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
-Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information. \todo{double check with Dylan}
 
@@
 If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
-Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
+Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
 
@@
 To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves.
-We recall that a grasp according to our metric is defined as the tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z \rbrace$.
+We recall that a grasp according to our metric is defined as the tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z )$.
 We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$.

### 2014-10-02 paper.tex
fixed intro

--- 2014-10-02 paper.tex
@@
 We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
-We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of T versus planning grasps using existing methods.
+We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of 10x versus planning grasps using existing methods.
 \end{abstract}
@@
 
-The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
-The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
-Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-
-\todo{ref figure}
-
-Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
-We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
-We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
-
 \begin{figure}[t!]
@@
 \end{figure}
+
+The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
+The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
+Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+
+Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
+We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
+We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation and use those to efficiently sample from the GPIS for grasp quality evaluation, which reduces computational complexity of sampling from $O(n^6)$ to $O(n^3)$ for a 2D $n \times n$ workspace.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
 
@@
 In future work, we will look at using other exploration strategies.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
-\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
-You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
-\vspace*{-10pt}
-\label{fig:sampling_convergence}
-\end{figure}
 

### 2014-10-02 paper.tex

--- 2014-10-02 paper.tex
@@
 We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x over other grasp evaluation methods.
 

### 2014-10-02 paper.tex
fixed many little bugs

--- 2014-10-02 paper.tex
@@
 \begin{equation}
-p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt
+    p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt \label{eq:normal_dist}
 \end{equation}
@@
 To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.
-In Fig.\ref{fig:GraspDIst}, we visualize the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
+In Fig.\ref{fig:GraspDist}, we visualize the distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
 
@@
 \ref{eq:independence}.
-This can be done by drawing samples from Eq.
-\ref{eq:joint_contact_normal}.
-and using our projection technique for the normal distribution.
+This can be done by drawing samples from the GP for signed distance and normals simultaneously and using our projection technique for the normal distribution.
 
@@
 \section{Experiments}
-For the experiments below we used common household objects shown in Fig.
-\ref{fig:GPIS_TSDF}.
-We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor.
+For the experiments below we used common household objects.
+The objects used can be found at \url{http://rll.berkeley.edu/grasping/} We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor.
 To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
 The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-Our visualization technique follows the approach of \cite{jeffs} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
+Our visualization technique follows the approach of \cite{mahler2015opt} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
 
@@
 In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration.
-Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{jeffs}}
+Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{mahler2015opt}}
 \vspace*{-10pt}
@@
 
-Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{jeffs}.
+Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{mahler2015opt}.
 

### 2014-10-02 paper.tex

@@
 
-The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
-The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
-Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-
-Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
-We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
-We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
-
 \begin{figure}[t!]
@@
 \end{figure}
+
+The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
+The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
+Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+
+Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
+We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
+We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x over other grasp evaluation methods.
+
+The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
+The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
+Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+
+Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
+We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
+We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation and use those to efficiently sample from the GPIS for grasp quality evaluation, which reduces computational complexity of sampling from $O(n^6)$ to $O(n^3)$ for a 2D $n \times n$ workspace.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
 
@@
 When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
-In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
+%In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
 

### 2014-10-02 paper.tex
8 pages

@@
 \centering
-\includegraphics[width = 8.5cm, height= 7cm ]{figures/Slide13.jpg}
+\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
 \caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
@@
 \centering
-\includegraphics[width = 17cm, height = 12cm]{figures/Slide09.jpg}
+\includegraphics[width = 14cm, height = 9cm]{figures/Slide09.jpg}
 \caption{ \footnotesize Top: Comparison of two sampling methods.
@@
 \centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
+\includegraphics[width=5.7cm,height=6cm]{figures/Slide12.jpg}
 \caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace.

### 2014-10-03 paper.tex
v15

@@
 
+\usepackage{caption}
+\renewcommand{\captionfont}{\footnotesize}
 \usepackage{sidecap,wrapfig}
@@
 \title{\LARGE \bf
-Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]}
+Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty}
 
@@
 \begin{abstract}
-In unknown or changing environments such as warehouses for consumer goods, robots may need to quickly plan grasps on previously unknown objects.
-Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
-Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
-In this paper, we show that framing grasp planning as a multi-armed bandit problem, a standard framework for making sequential descisions, provides a principled way to quickly select a grasp from a set of candidates on an uncertain shape.
-We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
-We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of 10x versus planning grasps using existing methods.
+Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
+Monte Carlo sampling is computationally demanding, even for planar models.
+We consider an alternative based on the multi-armed bandit (MAB) framework for making sequential decisions, which can apply to a variety of uncertainty models.
+We formulate grasp planning as a ``budgeted multi-arm bandit problem” with finite stopping time to minimize ``simple regret”, the difference between the expected value of the best grasp and the expected value of the grasp evaluated at the stopping time.
+To evaluated MAB-based sampling, we compare it with Monte Carlo sampling for grasping a planar object defined by a Gaussian Process Implicit Surface (GPIS).
+We derive distributions on contact points, surface normal, and center of mass and use these solve the associated MAB problem, finding that it computes grasps of similar quality and can reduce computation time by an order of magnitude.
+This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
 \end{abstract}
@@
 Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
-The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape and pose.
-However, the robot may not be able to measure these quantities exactly due to sensor noise and missing data due to partial visibility and object properties such as transparency.
-Grasp planners that assume an exact measurement of shape, pose, or its own state may fail.
+The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and even material properties like friction coefficient or center of mass.
+Due to sensor noise and missing data due to partial visibility and object properties such as transparency, the robot may not be able to measure these quantities exactly.
+Grasp planners that assume prior knowledge of object geometry or an exact measurement of pose may fail in this environment.
 
-This motivates using knowledge of uncertainty to select grasps, but most current methods for evaluating the quality of a single grasp in the presence of uncertainty require use an exhaustive sampling over the possible values of the uncertain quantity \cite{kehoe2012toward, kim2012physically, weisz2012pose}.
+Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaulate a grasp assuming all the parameters are known \cite{ferrari1992}
+This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quality \cite{kehoe2012toward, kim2012physically, weisz2012pose}.
 To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
-However, when ranking a set of grasps we may be able to determine the relative quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
-Thus, we can adaptively concentrate grasp evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
+However, when evaluating a set of grasps we may be able to determine the difference of quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
+Thus, we can adaptively concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
 
@@
 
-The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
-The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
+The multi-armed bandit (MAB) model, a framework for sequential decision making problems,\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration.
+The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected reward of such decisions is maximized.
 Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
-We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
-We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x over other grasp evaluation methods.
-
-The multi-armed bandit (MAB) problem, a framework for sequential decision making problems, provide a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some}.
-The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected value of such decisions is maximized.
-Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-
-Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
-We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
-We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation and use those to efficiently sample from the GPIS for grasp quality evaluation, which reduces computational complexity of sampling from $O(n^6)$ to $O(n^3)$ for a 2D $n \times n$ workspace.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
+Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a budgeted multi-armed bandit problem.
+We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality \cite{ferrari1992} under shape uncertainty.
+We chose representation known as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}.
+We also show how to estimate distributions on the contact points and surface normals and center of mass using a GPIS shape representation.
+We then leverage these distributions to reduce the computational complexity of sampling from the GPIS model from $O(n^6)$ to $O(n^3)$, where the workspace is discretized as a $nxn$ grid.
+Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach.
+The promising results suggest that our MAB approach could be used on other types of uncertainity, such as pose, friction coefficent or center of mass and provide significant speed improvements.
 
 \section{Related Work}
-
-The multi-armed bandit (MAB) problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} considers maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probabilistic reward function.
-Solutions to this problem, called {\it policies}, include choosing the next option based on Thompson sampling~\cite{agrawal2011analysis}, the Gittins index policy~\cite{weber1992gittins}, and by using an upper confidence bound (UCB) for the expected reward of each option~\cite{auer2002finite}.
-The UCB can be computed from the sample mean~\cite{agrawal1995sample}, Kullback-Leibler divergence~\cite{cappe2013kullback}, or a prior on the rewards~\cite{kaufmann2012bayesian}.
-Solutions to the multi-armed bandit problem have been used in applications for which evaluating all possible options is expeinsive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-In this paper we consider the "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent can only explore for a finite time before deciding which arm to exploit~\cite{madani2004budgeted}.
 
@@
 
-Currently, the most common method of evaluating grasp quality under shape and pose uncertainty is to rank a set of random grasps on an object using Monte-Carlo integration on shape and pose samples to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
-Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shape.
-To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minumum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo integration in order to rank grasps, but the adaptive sampling method involes several hyperparameters whereas our proposed budgeted MAB solution does not.
-Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte Carlo (MCMC) sampling to estimate grasp stability and object pose online under shape and pose uncertainty.
-MCMC simplified sampling from complicated distributions on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.
+Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
+To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps.
+The adaptive sampling pruned grasps  though based only the sample mean and didn't take into account how accurate the current sample mean is.
+Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
+MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.
 
-We study our MAB sampling method using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on the ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
-Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
-Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al. used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}. 
-However, sampling from GPIS for grasp quality evaluation is computationally intensive because it involves the Cholesky decomposition of an $m \times m$ matrix which takes $O(m^6)$ time, where $m$ is the dimension for a 2D grid over and object \cite{morrison1990multivariate}.
-Therefore, GPIS is a good illustration of benefits provided by our efficient MAB approach to grasp planning.
+We chose to study our MAB sampling method for shape uncertainty using a Gaussian Process Implicit Surface representation.
+Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
+Hollinger et al. used GPIS as a model of uncertainty and performed active sensing on the hulls in underwater boats \cite{hollinger2013}.
+Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
+Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}.
 
-\section{Multi-Arm Bandit Problem}
-The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
-The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
+\section{Multi-Armed Bandit Model}
+The multi-arm bandit problem, originally described by Robbins \cite{robbins1985some}, is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
+The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
 A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
 Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
+Solutions to the multi-armed bandit problem have been used in applications for which evaluating all possible options is expeinsive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
@@
 One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
-A class of algorithms that have theoretical guarantees are Upper Confidence Bound (UCB).
-UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times has been sampled for each arm.
-The algorithm chooses the arm at each step which has the highest upper bound on expected reward, since that is the most potentially promising arm.
+A class of algorithms that have stronger theoretical guarantees are from the Upper Confidence Bound (UCB) family.
+UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times each arm has been sampled.
+The algorithm chooses the next option based on Thompson sampling~\cite{agrawal2011analysis} or the Gittins index policy~\cite{weber1992gittins}.
 When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
@@
 
-We can formulate our problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
-The budgeted multi-arm bandit problem has a finite stopping time.
-The objective of the budgeted multi-arm bandit problem is to minimize the "simple regret", which is the difference between the true expected value of the actual best arm and the true expected value of the arm pulled at the stopping time.
+In the grasping context, one is only interesting in choosing the best grasp at the end of an exploration cycle.
+We can formulate our problem as a   ``budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
+The budgeted multi-arm bandit problem focuses on efficiently exploring the arms until a finite stopping time is reached. 
+The objective of the budgeted multi-arm bandit problem is to minimize the ``simple regret", which is the difference between the true expected value of the actual best arm and the true expected value of the arm pulled at the stopping time.
 Thus the budgeted multi-arm bandit problem reduces to exploration until the very last time step, at which time one exploitation step is taken.
@@
 \section{Problem Definition}
-Before we present the problem definition, we introduce the grasping model, the line of action.
+Before we present the problem definition, we introduce the our grasping model, the line of action.
 
@@
 
-Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model (we will describe the GPIS model later) and set of possible grasp plans $G$.
+Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model, which we describe in Section \ref{sec:GP} and set of possible grasp plans $G$.
 We are interested in determining
@@
 While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
+\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit problem and forming a policy for selecting which grasp to sample.
 In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
@@
 In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
-Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
+Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form, which limits the bandit algorithms available to us.
 
-For our exploration policy, we maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
+For our exploration policy, we chose to use a method called \textit{successive elimination}.
+We maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
 During exploration, we sample uniformly from this subset.
@@
 For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
-The width of the confidence interval for a grasp plan $i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
+The width of the confidence interval for a grasp plan $\Gamma_i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
 
@@
 
-\subsection{Gaussian Process (GP) Background}
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
+\subsection{Gaussian Process (GP) Background}\label{sec:GP}
+We refer the reader to \cite{mahler2015opt} for a more detailed explanation of the GP construction, which we summarize here.
+Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$, or the distribution on signed distance field, at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
 \begin{align*}
@@
 \subsection{Grasp Metric}
-In their pioneering work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
+In their work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
 Importantly the magnitude of Q yields a measurement that allows one to rank grasps by their physical stability and evaluate the property of force-closure.
@@
 
-We will now show how these distributions can be computed and how the complexity for evaluating a grasp is reduced from $O(n^6)$ to $O(n^3)$.
+We will now show how these distributions can be computed and how the computational complexity for sampling form a grasp plan is reduced from $O(n^6)$ to $O(n^3)$ for a GPIS model.
 
@@
 We draw samples from our calculated distributions $p(g)$.
-The most interesting thing is that the regret is minimized at least an order of magnitude faster than the naive approach for the shapes we considered, thus motivating the use of including observations as you select samples.
+The most interesting thing is that the regret is minimized at least an order of magnitude faster than the traditional approach for the shapes we considered, thus motivating the use of including observations as you select samples.
 
@@
 \centering
-\includegraphics[width = 14cm, height = 9cm]{figures/Slide09.jpg}
+\includegraphics[width = 16.5cm, height = 9cm]{figures/Slide09.jpg}
 \caption{ \footnotesize Top: Comparison of two sampling methods.

### 2014-10-03 paper.tex
went over related work, changed structure

@@
 
-\section{Problem Definition}
-Before we present the problem definition, we introduce the our grasping model, the line of action.
+\section{Preliminaries and Problem Definition}
+Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
+
+\subsection{Grasp Metric}
+In their work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
+Importantly the magnitude of Q yields a measurement that allows one to rank grasps by their physical stability and evaluate the property of force-closure.
+Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
+
+The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$.
+Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+A wrench is defined as concatenation of a force and torque vector.
+If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
+Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
+
+Since we are in an uncertain environment, we are interested in calculating the expected quality, or $E(Q)$.
+$E(Q)$ is computed by sampling from our distributions on pose, shape or material properties (friction coefficient or density) and averaging the qualities that are computed.
+Reducing the time to do this for a large number of grasps is the primary focus of the paper.
 
 \subsection{Line of action}
+In an uncertain environment one wouldn't actually know the true $g$, thus we have to work with the trajectory of the gripper.
 Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
@@
 
-\section{Evaluating a Grasp}
+\section{Evaluating a Grasp on Gaussian Process Implicit Surface}
  In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$.
@@
 Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\subsection{Grasp Metric}
-In their work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
-Importantly the magnitude of Q yields a measurement that allows one to rank grasps by their physical stability and evaluate the property of force-closure.
-Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
-
-The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$.
-Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-A wrench is defined as concatenation of a force and torque vector.
-If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
-Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
 
@@
 Our results are promising and they suggest many avenues of future work.
-First, we are actively working to apply this approach to 3D environments.
-In particular, we are interested in investigating the entire end-to-end pipeline of perception, grasp planning, and grasp execution.
-Next, in principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
+The advantage of this model is that we can have uncertainty in all elements that compose a grasp: shape, pose, friction coefficient and center of mass.
+While at the same time not exhaustively sampling all of our potential grasp plans.
+
+In principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
 It can further be applied to other grasp quality metrics.
-Next, we are investigating the application of recent results from reinforcement learning or bandit theory for analytic stopping criteria for the sampling.
-One particular challenge is that shape uncertainty is rarely parametric leading to problems with many recent bounds and optimality conditions.
+
+Future work, will consider applying BMAB approach to grasp planners like GraspIt!
+\cite{miller2004graspit} to see if we can handle uncertainty and still maintain the time constraints needed for most real time applications.
+Also, we currently have only tested out one bandit algorithm, succesive elimination, and had very successful results.
+As we scale to more complicated models, we will have a large area of research to draw from and improve our method \cite{bergemann2006bandit}.
 

### 2014-10-03 paper.tex
updated figures
many sachin changes

--- 2014-10-03 paper.tex
@@
 Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
-\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\tt\small goldberg@berkeley.edu}}%
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
+\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
 \thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
-\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\tt\small \{fpokorny, dani\}@kth.se}}%
-\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\tt\small jurvandenberg@gmail.com}}%
+\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\small \{fpokorny, dani\}@kth.se}}%
+\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\small jurvandenberg@gmail.com}}%
 }
@@
 Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
-Monte Carlo sampling is computationally demanding, even for planar models.
-We consider an alternative based on the multi-armed bandit (MAB) framework for making sequential decisions, which can apply to a variety of uncertainty models.
-We formulate grasp planning as a ``budgeted multi-arm bandit problem” with finite stopping time to minimize ``simple regret”, the difference between the expected value of the best grasp and the expected value of the grasp evaluated at the stopping time.
-To evaluated MAB-based sampling, we compare it with Monte Carlo sampling for grasping a planar object defined by a Gaussian Process Implicit Surface (GPIS).
-We derive distributions on contact points, surface normal, and center of mass and use these solve the associated MAB problem, finding that it computes grasps of similar quality and can reduce computation time by an order of magnitude.
+Monte-Carlo sampling is computationally demanding, even for planar models.
+We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.
+We formulate grasp planning as a ``budgeted multi-armed bandit model" with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.
+To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object defined by a Gaussian process implicit surface (GPIS), but the method is applicable to other models of uncertainty.
+We derive distributions on contact points, surface normal, and center of mass and use these solve the associated MAB model, finding that it computes grasps of similar quality and can reduce computation time by an order of magnitude.
 This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
@@
 
-Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaulate a grasp assuming all the parameters are known \cite{ferrari1992}
-This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quality \cite{kehoe2012toward, kim2012physically, weisz2012pose}.
+Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaulate a grasp assuming all the parameters are known \cite{ferrari1992}.
+This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
 To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
@@
 
-The multi-armed bandit (MAB) model, a framework for sequential decision making problems,\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a principled way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration.
-The goal in MAB problems is to make a sequence of decisions over a set of possible options such that a measure of the expected reward of such decisions is maximized.
-Solutions to the MAB problem are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration.
+The goal in a MAB model is to make a sequence of decisions over a set of possible options such that a measure of the expected reward of such decisions is maximized.
+Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model with a finite stopping time where the objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
 
-Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a budgeted multi-armed bandit problem.
+Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a budgeted multi-armed bandit model.
 We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality \cite{ferrari1992} under shape uncertainty.
-We chose representation known as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}.
+We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the expected quality of many potential grasp plans.
+We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}, however the method applies to any model of uncertainty that can be sampled.
 We also show how to estimate distributions on the contact points and surface normals and center of mass using a GPIS shape representation.
-We then leverage these distributions to reduce the computational complexity of sampling from the GPIS model from $O(n^6)$ to $O(n^3)$, where the workspace is discretized as a $nxn$ grid.
+We then leverage these distributions to reduce the computational complexity of sampling from the GPIS model from $O(n^6)$ to $O(n^3)$, where the workspace is discretized as a $n \times n$ grid.
 Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach.
-The promising results suggest that our MAB approach could be used on other types of uncertainity, such as pose, friction coefficent or center of mass and provide significant speed improvements.
+These promising results suggest that our MAB approach could be used on other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements.
 
@@
 Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
-To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps.
-The adaptive sampling pruned grasps  though based only the sample mean and didn't take into account how accurate the current sample mean is.
-Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
+To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps.
+The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is.
+Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
 MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.
 
-We chose to study our MAB sampling method for shape uncertainty using a Gaussian Process Implicit Surface representation.
+We chose to study our MAB sampling method for shape uncertainty using a Gaussian process implicit surface representation.
 Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
@@
 \section{Multi-Armed Bandit Model}
-The multi-arm bandit problem, originally described by Robbins \cite{robbins1985some}, is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
-The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
+The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
+The traditional setting of a multi-armed bandit model is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
 A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
 Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
-Solutions to the multi-armed bandit problem have been used in applications for which evaluating all possible options is expeinsive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
@@
 The algorithm chooses the next option based on Thompson sampling~\cite{agrawal2011analysis} or the Gittins index policy~\cite{weber1992gittins}.
-When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
+When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
 %In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
@@
 In the grasping context, one is only interesting in choosing the best grasp at the end of an exploration cycle.
-We can formulate our problem as a   ``budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
-The budgeted multi-arm bandit problem focuses on efficiently exploring the arms until a finite stopping time is reached. 
-The objective of the budgeted multi-arm bandit problem is to minimize the ``simple regret", which is the difference between the true expected value of the actual best arm and the true expected value of the arm pulled at the stopping time.
-Thus the budgeted multi-arm bandit problem reduces to exploration until the very last time step, at which time one exploitation step is taken.
+We can formulate our problem as a   ``budgeted multi-armed bandit model" \cite{madani2004budgeted}.
+The budgeted multi-armed bandit model focuses on efficiently exploring the arms until a finite stopping time is reached. 
+The objective of the budgeted multi-armed bandit model is to minimize the ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
+Thus the budgeted multi-armed bandit model reduces to exploration until the very last time step, at which time one exploitation step is taken.
 
@@
 
-\section{Multi-Arm Bandits for Grasp Selection}
+\section{Multi-Armed Bandits for Grasp Selection}
 While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit problem and forming a policy for selecting which grasp to sample.
+\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
 In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
@@
 
-We construct a GPIS by learning a Gaussian Process to fit measurements of a signed distance field of an unknown object.
+We construct a GPIS by learning a Gaussian process to fit measurements of a signed distance field of an unknown object.
 Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
@@
 
-\subsection{Multi-Arm Bandit Experiments}
+\subsection{Multi-Armed Bandit Experiments}
 
@@
 \caption{ \footnotesize Top: Comparison of two sampling methods.
-Red is the multi-arm bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
+Red is the multi-armed bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
 We measure their ability to converge in terms of simple regret averaged over 100 runs.
@@
 
-Our budgeted multi-arm bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
+Our budgeted multi-armed bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
 Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.
@@
 Assessing grasp quality under shape uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
-In this work, we proposed a multi-arm bandit approach to efficiently identify high-quality grasps under shape uncertainty. 
+In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under shape uncertainty. 
 A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
- we found that the Successive Elimination multi-arm bandit approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
+ we found that the Successive Elimination multi-armed bandit approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
 A pre-requisite for applying a bandit approach is to formulate an efficient representation of how shape uncertainty affects grasp parameters and thus grasp quality.
-We modeled uncertainty with Gaussian Process Implicit Surfaces (GPIS) and derived the distribution of grasp parameters when a nominal grasp is applied to the GPIS.
+We modeled uncertainty with Gaussian process implicit surfaces (GPIS) and derived the distribution of grasp parameters when a nominal grasp is applied to the GPIS.
 As a result, we were able to more efficiently sample from a distribution of grasps executions rather than the shape; leading to a complexity improvement of $n^3$ in the resolution of the representation.

### 2014-10-03 paper.tex
updated figures

--- 2014-10-03 paper.tex
@@
 \centering
-\includegraphics[scale = 0.3]{figures/Slide01.jpg}
+\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
 \caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
@@
 \caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
+Visualization technique comes from \cite{mahler2015opt}.
 Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
@@
 Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}.
+We plotted the probability mass along the unit circle, to reflect the normalization of the surface normals.
 }
@@
 Our results are promising and they suggest many avenues of future work.
-The advantage of this model is that we can have uncertainty in all elements that compose a grasp: shape, pose, friction coefficient and center of mass.
-While at the same time not exhaustively sampling all of our potential grasp plans.
+By utilizing the BMAB model, we can simply encode uncertainty in the grasp parameters and then leverage the existing algorithms to efficiently find the best grasp.
 
 In principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
-It can further be applied to other grasp quality metrics.
+It can further be applied to other grasp quality metrics or even simulation based evaluation methods \cite{73}.
 
-Future work, will consider applying BMAB approach to grasp planners like GraspIt!
+Future work, will also consider applying BMAB approach to grasp planners like GraspIt!
 \cite{miller2004graspit} to see if we can handle uncertainty and still maintain the time constraints needed for most real time applications.
-Also, we currently have only tested out one bandit algorithm, succesive elimination, and had very successful results.
-As we scale to more complicated models, we will have a large area of research to draw from and improve our method \cite{bergemann2006bandit}.
+We currently have only tested one bandit algorithm, successive elimination.
+While our results were impressive, it remains to be seen how well it scales to the more complicated 3D models.
+However, the BMAB model has a large amount of literature to draw from as we encounter new and more challenging problems \cite{bergemann2006bandit}.
 

### 2014-10-03 paper.tex

--- 2014-10-03 paper.tex
@@
 We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.
-We formulate grasp planning as a ``budgeted multi-armed bandit model" with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.
+We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.
 To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object defined by a Gaussian process implicit surface (GPIS), but the method is applicable to other models of uncertainty.

### 2014-10-03 paper.tex
many typos and grammars changed

@@
 A wrench is defined as concatenation of a force and torque vector.
-If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
+If the convex hull does not enclose the origin, the grasp is not in force-closure.
 Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
@@
 $E(Q)$ is computed by sampling from our distributions on pose, shape or material properties (friction coefficient or density) and averaging the qualities that are computed.
-Reducing the time to do this for a large number of grasps is the primary focus of the paper.
+Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.
 
 \subsection{Line of action}
-In an uncertain environment one wouldn't actually know the true $g$, thus we have to work with the trajectory of the gripper.
+In an uncertain environment one would not actually know the true $g$, thus we have to work with the trajectory of the gripper.
 Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
@@
 Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
+While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial robots. 
 Future work will look at how to efficiently sample when the approach trajectory has noise.
@@
 While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
+\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
 In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
@@
 After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
-Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}.
+Since we prune grasps that are below a confidence interval we have statistical guarantees unlike earlier approaches to this problem \cite{kehoe2012toward}.
 In future work, we will look at using other exploration strategies.
@@
 Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
-Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}.
+Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way scales with the cube of the number of input dimensions \cite{petersen2008matrix}.
 Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
@@
 
-We will now show how these distributions can be computed and how the computational complexity for sampling form a grasp plan is reduced from $O(n^6)$ to $O(n^3)$ for a GPIS model.
+We will now show how these distributions can be computed and how the computational complexity for sampling from a grasp plan is reduced from $O(n^6)$ to $O(n^3)$ for a GPIS model.
 
@@
 One could think of this as a marginalization of all other points in signed distance field except the line of action.
-To sample contact points, one can simply draw samples from Eq.
+To sample contact points, one can draw samples from Eq.
 \ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies  Eq.
@@
 
-After formally deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
+After deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
 \ref{eq:independence}.
@@
 Having a distribution along a line of action model allows us to sample from those instead of the joint distribution $p(sd(\mathcal{W}))$.
-Assuming the line of action is on the order of $n$, sampling from this distribution for a single grasp is $O(n^3)$.
+Assuming the number of discretization points along the line of action is $n$, sampling from this distribution for a single grasp is $O(n^3)$.
 However, each proposed grasp plan $\Gamma$ requires the distribution to be computed, so if we have $T=|G|$ then the complexity is $O(Tn^3)$.
@@
 For the experiments below we used common household objects.
-The objects used can be found at \url{http://rll.berkeley.edu/grasping/} We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor.
+The objects used can be found at \url{http://rll.berkeley.edu/grasping/} We manually created a 25 x 25 grid, by tracing a point cloud of the object on a table taken with a Primesense Carmine depth sensor.
 To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
@@
 \ref{fig:simple_regret}, we plotted the simple regret for three of the shapes in our data set averaged over 100 runs and compare it to the Monte-Carlo method that randomly chooses a grasp plan to draw a sample from.
-We initialize both the Monte-Carlo and bandit technique by sampling each grasp 2 times this is to achieve the standard deviation.
+We initialize both the Monte-Carlo and bandit technique by sampling each grasp 2 times.
+This is to seed the standard deviation.
 We draw samples from our calculated distributions $p(g)$.
-The most interesting thing is that the regret is minimized at least an order of magnitude faster than the traditional approach for the shapes we considered, thus motivating the use of including observations as you select samples.
+Interestingly, regret is minimized at least an order of magnitude faster than the baseline approach for the shapes we considered, thus motivating the use of sampled observations to choose what to sample next.
 
@@
 \caption{ \footnotesize Top: Comparison of two sampling methods.
-Red is the multi-armed bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
+Red is the multi-armed bandit method that actively chooses which one to sample and Blue is the Monte-Carlo method.
 We measure their ability to converge in terms of simple regret averaged over 100 runs.
@@
 
-\subsection{Sampling from Grasps Vs. Shape}
+\subsection{Sampling from Grasps vs. Shape}
 We first tested 1000 grasp plans and sampled each one 5000 times  and measured the RMS error between converged expected grasp plan qualities for sampling shape Eq.
@@
 Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.
-While we have empirically seen the bandit method always converge to the correct value, our method only has a statistical guarantee of doing so.
-A low quality grasp plan could be found, albeit with a low probability.
+While we have seen the bandit method always converge to the correct value in our experiments, our method only has a statistical guarantee of doing so.
+A non-optimal grasp plan could be found, albeit with a low probability.
 
@@
 Extension of his work to implicit surfaces could be of possible interest \cite{panahi2014bounding}.
+When using the shape sampling approach on the GPIS instead of sampling along the grasp plan trajectory, the center of mass is easy to compute on a sampled shape, so this is a limitation of our sampling method.
 
@@
 We modeled uncertainty with Gaussian process implicit surfaces (GPIS) and derived the distribution of grasp parameters when a nominal grasp is applied to the GPIS.
-As a result, we were able to more efficiently sample from a distribution of grasps executions rather than the shape; leading to a complexity improvement of $n^3$ in the resolution of the representation.
-We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it performs on average a magnitude faster than a naive uniform sampling approach in our experiments, and (3) sampling from the grasp contacts is 12x faster than sampling from shapes for a 64x64 grid.
+As a result, we were able to more efficiently sample from a distribution of grasps executions rather than the shape; leading to a complexity improvement of $n^3$ in the resolution of the discretization $n$.
+We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it converges on average an order of magnitude faster than a uniform sampling approach in our experiments, and (3) sampling from the grasp contacts is 12x faster than sampling from shapes for a 64x64 grid.
 
@@
 Our results are promising and they suggest many avenues of future work.
-By utilizing the BMAB model, we can simply encode uncertainty in the grasp parameters and then leverage the existing algorithms to efficiently find the best grasp.
+By utilizing the BMAB model, we can encode uncertainty in the grasp parameters and then leverage the existing algorithms to efficiently find the best grasp.
 
 In principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
-It can further be applied to other grasp quality metrics or even simulation based evaluation methods \cite{73}.
+It can further be applied to other grasp quality metrics or simulation based evaluation methods \cite{73}.
 
-Future work, will also consider applying BMAB approach to grasp planners like GraspIt!
-\cite{miller2004graspit} to see if we can handle uncertainty and still maintain the time constraints needed for most real time applications.
+Future work will also consider applying BMAB approach to grasp planners like GraspIt!
+\cite{miller2004graspit} to see if our method can handle uncertainty while working under the time constraints needed for most real time applications.
 We currently have only tested one bandit algorithm, successive elimination.
-While our results were impressive, it remains to be seen how well it scales to the more complicated 3D models.
+While our results are promising, it remains to be seen how well it deals with the increased complexity of 3D models over 2D models and larger scale experiments.
 However, the BMAB model has a large amount of literature to draw from as we encounter new and more challenging problems \cite{bergemann2006bandit}.

### 2014-12-15 paper.tex
changed to TASE paper v0

@@
 \usepackage{benktools}
-
 \usepackage{caption}
@@
 UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times each arm has been sampled.
-The algorithm chooses the next option based on Thompson sampling~\cite{agrawal2011analysis} or the Gittins index policy~\cite{weber1992gittins}.
-When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
+Traditional bandit algorithms minimize cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
 %In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
 
-In the grasping context, one is only interesting in choosing the best grasp at the end of an exploration cycle.
-We can formulate our problem as a   ``budgeted multi-armed bandit model" \cite{madani2004budgeted}.
-The budgeted multi-armed bandit model focuses on efficiently exploring the arms until a finite stopping time is reached. 
-The objective of the budgeted multi-armed bandit model is to minimize the ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
-Thus the budgeted multi-armed bandit model reduces to exploration until the very last time step, at which time one exploitation step is taken.
+Different to the normal bandit problem, we do not actually care about cumulative regret because the exploration and exploitation stage is decoupled from each other.
+For example in medical testing for patients it is important to always administer the best treatment for the given patient.
+However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
+
+Best arm identification has a wide variety of literature that largely falls into two camps.
+One where the algorithm terminates once a fixed confidence interval around the best arm is met and one where a set horizon is given and the algorithm has to choose a arm at that stopping time.
+
+\subsection{Fixed Confidence}
+In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates.
+Originally the problem was solved by racing algorithms, were methods used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were deemed not likely to succeed and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
+These methods were later extended to include not only the best arm, but return the top m arms \cite{gabillon2012best}.
+
+\subsection{Fixed Budget}
+In the fixed budget setting the algorithm is given a stopping time and needs to return the best arm at that stopping time.
+Audibert el al.
+demonstrated an algorithm called Successive Rejects that given a budget divides up the time each arm is pull an can return the best arm with near optimal probability depending on the hardness of the problem \cite{audibert2010best}.
+Other UCB like methods have been proposed as well that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
+In \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed
+for the analysis of the existing bandit algorithms like UCB1.
+
+For the case of choosing the best grasp, we are working in the scenario where the robot has a fix amount of time to choose a grasp and thus the fixed budget setting is more appropriate.
 
@@
 
-Since we are in an uncertain environment, we are interested in calculating the expected quality, or $E(Q)$.
-$E(Q)$ is computed by sampling from our distributions on pose, shape or material properties (friction coefficient or density) and averaging the qualities that are computed.
+Since we are in an uncertain environment, we are interested in calculating the expected quality, or $P(Q>0)$, or the probability of achieving force closure, similar too  \cite{christopoulos2007handling}\cite{kehoe2012toward} .
+$P(Q>0)$ is computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
 Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.
+
+\subsection{Types of Uncertainty}
+In this work we consider the following types of uncertainty shape, pose, center of mass and friction coefficient.
+The probabilistic relationship of all these types of uncertainty can be seen in Fig.
+\ref{fig:graphical_model}.
+We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.
+
+For shape, we use a GPIS representation as described in Sec.
+\ref{sec:GP}.
+For pose we sample the centroid of the GPIS from a Gaussian distribution with user covariance matrix.
+Center of mass a Gaussian  with mean as the expected center of mass, as defined in Eq.
+\ref{eq:mass}, assuming uniform mass distribution.
+Lastly, for friction coefficient we represent it as Gaussian with mean around the expected friction coefficient provided by a user.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 6cm, height = 4cm]{figures/Slide8.jpg}
+\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
+Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.
+}
+\vspace*{-10pt}
+\label{fig:graphical_model}
+\end{figure}
 
@@
 Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial robots. 
-Future work will look at how to efficiently sample when the approach trajectory has noise.
 
@@
 
+While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial robots. 
+Future work will look at how to efficiently sample when the approach trajectory has noise.
+
 \subsection{Problem Definition}
@@
 \begin{align}\label{eq:problem_def}
-\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
+\Gamma^* \in \mbox{argmax}_{\Gamma \in G} P(Q(\Gamma)>0)
 \end{align}
@@
 
-In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
-Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form, which limits the bandit algorithms available to us.
+In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $P(Q(\Gamma)>0)$ determined via Monte-Carlo Integration.
+Since the function to test force closure is boolean, we can model our problem as choosing the best arm for a Beta-Bernoulli Process.
+Methods with very strong guarantees are now available to us \cite{review}.
+We now review some of them.
+\section{Bandit Algorithms For Best Arm Identification}
+\subsection{Thompson Sampling}
+Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
+The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled.
+Then sample from the prior distribution on all arms and pull the arm with the highest sample drawn.
+The full algorithm is shown in Algorithm 1.
+Empirically this method has been shown to outperform frequentist methods like UCB \cite{chapelle2011empirical}
 
-For our exploration policy, we chose to use a method called \textit{successive elimination}.
-We maintain a subset of the possible grasp plans that are statistically indistinguishable from the best grasp plan.
-During exploration, we sample uniformly from this subset.
-This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
-For each grasp plan, we maintain a $95\%$ confidence interval around the expected quality of the grasp plan.
-The width of the confidence interval for a grasp plan $\Gamma_i$ that has been sampled $n_i$ times and the samples have standard deviation $\sigma_i$ is:
+\subsection{Upper Confidence Bound (UCB)}
+The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards.
+It basically assumes a frequenist perspective and estimates an empirical confidence bound for each arm based on the observations seen so far.
+Then it pulls the arm with the highest confidence bound.
 
-\vspace{-2ex}
-\begin{align}
-C_{ i} := \frac{1.96 \sigma_i}{\sqrt{n_i}}.
-\end{align}
+\subsection{Gittins Index} 
+Gittins index treats the bandit problem as an Markov Decision Process where each lever pull is taking a step along a Markov Chain.
+While, normally the cost of computing an optimal policy would be exponential in the number of K arms.
+The independence assumption between each arms allows us to decouple them and solve for a policy that models taking pulls along one arm or selecting a reference arm that represents selecting a different possible value.
+We computed the Gittins indices using the restart method proposed by Katehakis et al.
+\cite{katehakis1987multi}.
 
-Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.
-Then the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
-After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans.
-Since we prune grasps that are below a confidence interval we have statistical guarantees unlike earlier approaches to this problem \cite{kehoe2012toward}.
-In future work, we will look at using other exploration strategies.
+\begin{algorithm}
+ \KwResult{Best Arm, $g^*$ }
+ For Beta(1,1) prior: \\
+\For{ t=1,2,...}{ 
+ Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
+ Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
+ Observe reward $X_{I_t,t}$\\
+ Update poster:\\
+ Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
+ Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
+
+ }
+ \caption{Thompson Sampling}
+\end{algorithm}
 
 \section{Evaluating a Grasp on Gaussian Process Implicit Surface}
- In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$.
-We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating the expectation $E$ efficiently.
+ In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$.
+We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.
 
@@
 
-\subsection{Calculating the Expected Grasp Quality}
-Given a proposed grasp plan $\Gamma$, the expected grasp quality can be evaluated as follows:
+\subsection{Calculating the Probability of Force Closure}
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (S )$, the distribution on center of mass $P (z)$ and the distribution on friction coefficient $P (\mu)$.
+The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Thus, we can write the probability of force closure as follows
 
@@
 \begin{align}\label{eq:shape_sampling}
-E(Q(\Gamma)) = \int Q(g|S,\Gamma) p(S) dS
+P(Q(\Gamma|S,\mu,z) > 0) = \frac{\alpha}{\alpha + \beta}
 \end{align}
 
-Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$.
+Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(z)$,$p(\mu)$.
 To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
@@
 For computational reasons we approximate the integral via Monte-Carlo Integration.
-We use importance sampling to draw from the distribution induced by GPIS and calculate the following
+We use importance sampling to draw from the distribution induced by GPIS and  count the number of sucesses of the grasp $S$ and the number of failures $F$ and calculate the following
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
-\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
-\vspace*{-10pt}
-\label{fig:shape_samples}
-\end{figure}
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|S,\mu,z) > 0) \approx \frac{(S + \alpha_0)}{(\alpha_0 + S) +( \beta_0 + F)}
+\end{align}
 
-\begin{align*}
-E(Q(\Gamma)) \approx \frac{1}{N} \sum_{i=1}^N Q(g|S_i,\Gamma) , \ \  S_i \sim p(S)
-\end{align*}
-
+Here $\alpha_0$ and $\beta_0$ correspond to the intial shape parameters.
 To compute the above distribution we must draw samples from $p(S)$.
@@
 Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
+\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
+\vspace*{-10pt}
+\label{fig:shape_samples}
+\end{figure}
 
@@
 p(g) = &\prod_{i=1}^mp\big(\textbf{c}_i,\textbf{n}_i|\gamma_i(t),\mu(x),\Sigma(x)\big)
-\end{align}
-
-We compute the expected grasp quality now as follows:
-
-\vspace{-2ex}
-\begin{align}\label{eq:grasp_sampling}
-E(Q(\Gamma)) = \frac{1}{N} \sum_{i=1}^N Q(g_i) , \ \ g_i \sim p(g)
 \end{align}
@@
 
+\label{eq:mass}
 \begin{equation}
@@
 In Fig.
-\ref{fig:simple_regret}, we plotted the simple regret for three of the shapes in our data set averaged over 100 runs and compare it to the Monte-Carlo method that randomly chooses a grasp plan to draw a sample from.
-We initialize both the Monte-Carlo and bandit technique by sampling each grasp 2 times.
-This is to seed the standard deviation.
+\ref{fig:simple_regret}, we plotted the simple regret averaged over 100 of the shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation).
+We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time.
 We draw samples from our calculated distributions $p(g)$.
-Interestingly, regret is minimized at least an order of magnitude faster than the baseline approach for the shapes we considered, thus motivating the use of sampled observations to choose what to sample next.
+Interestingly, Gittins and Thompson converge much faster than random and UCB.
+In Fig.
+\ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus it is quickly able to ignore the low quality grasps.
+UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.
 
@@
 \centering
-\includegraphics[width = 16.5cm, height = 9cm]{figures/Slide09.jpg}
-\caption{ \footnotesize Top: Comparison of two sampling methods.
-Red is the multi-armed bandit method that actively chooses which one to sample and Blue is the Monte-Carlo method.
-We measure their ability to converge in terms of simple regret averaged over 100 runs.
-We had them determine the best grasp when $|G|=1000$.
-In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration.
-Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{mahler2015opt}}
+\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simple_regret.eps}
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
+UCB does poorly on simple regret which is expected \cite{best_arm}}
 \vspace*{-10pt}
 \label{fig:simple_regret}
+\end{figure*}
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
+\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+Graph is averaged over 100 shapes from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+The best grasps are ranked 1 and worst are 1000.
+As you can see the Thompson and Gittins method have a tendency to pull grasps with high ranking, while UCB has a more conservative policy \cite{best_arm}}
+\vspace*{-10pt}
+\label{fig:pulls_per_grasp}
 \end{figure*}

### 2014-12-19 paper.tex
changed structure, pushed GPIS stuff to appendix, changed story to be sampled from graphical model

@@
 
-\author{Michael Laskey$^1$, Zoe McCarthy$^1$, Jeff Mahler$^1$, Florian T.
+\author{Michael Laskey$^1$,Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T.
 Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
@@
 Due to sensor noise and missing data due to partial visibility and object properties such as transparency, the robot may not be able to measure these quantities exactly.
-Grasp planners that assume prior knowledge of object geometry or an exact measurement of pose may fail in this environment.
+Grasp planners that assume exact prior knowledge of object geometry or an exact measurement of pose may fail in this environment.
 
-Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaulate a grasp assuming all the parameters are known \cite{ferrari1992}.
+Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
 This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
@@
 We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}, however the method applies to any model of uncertainty that can be sampled.
+
 We also show how to estimate distributions on the contact points and surface normals and center of mass using a GPIS shape representation.
@@
 Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
-MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.
+MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.
 
@@
 
+Traditional bandit algorithms minimize cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
 There are a number of algorithms for developing policies to balance exploration and exploitation.
@@
 UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times each arm has been sampled.
-Traditional bandit algorithms minimize cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
+
 %In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
@@
 However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
+Thus, performance of Budgeted Multi-Armed Bandit models is measured in terms of the convergence of simple regret.
+Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}\mu_k}$.
+The regret at time $t$ is given by Eq.
+\ref{eq:simple_regret}, where $\mu_t$ is the estimate of the best arm at time $t$ from the previous observations.
 
-Best arm identification has a wide variety of literature that largely falls into two camps.
-One where the algorithm terminates once a fixed confidence interval around the best arm is met and one where a set horizon is given and the algorithm has to choose a arm at that stopping time.
+\vspace{-2ex}
+\begin{align}\label{eq:simple_regret}
+r_t = \mu^* - \mu_t
+\end{align}
+
+Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and one where a set horizon is given and the algorithm has to choose a arm at that stopping time.
 
@@
 Originally the problem was solved by racing algorithms, were methods used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were deemed not likely to succeed and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
-These methods were later extended to include not only the best arm, but return the top m arms \cite{gabillon2012best}.
+These methods were later extended to include not only the best arm, but return the top $m$ arms \cite{gabillon2012best}.
 
@@
 Audibert el al.
-demonstrated an algorithm called Successive Rejects that given a budget divides up the time each arm is pull an can return the best arm with near optimal probability depending on the hardness of the problem \cite{audibert2010best}.
+demonstrated an algorithm called Successive Rejects that given a budget divides up the time each arm is pull an can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
 Other UCB like methods have been proposed as well that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
-In \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed
-for the analysis of the existing bandit algorithms like UCB1.
+In \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.
 
 For the case of choosing the best grasp, we are working in the scenario where the robot has a fix amount of time to choose a grasp and thus the fixed budget setting is more appropriate.
+
+\section{Bandit Algorithms For Best Arm Identification}\label{sec:algorithms}
+\subsection{Thompson Sampling}
+Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
+The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled.
+Then sample from the prior distribution on all arms and pull the arm with the highest sample drawn.
+The full algorithm is shown in Algorithm 1.
+Empirically this method has been shown to outperform frequentist methods like UCB \cite{chapelle2011empirical}
+
+\begin{algorithm}
+ \KwResult{Best Arm, $g^*$ }
+ For Beta(1,1) prior: \\
+\For{ t=1,2,...}{ 
+ Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
+ Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
+ Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
+ Update posterior:\\
+ Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
+ Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
+
+ }
+ \caption{Thompson Sampling for Beta-Bernoulli Process}
+\end{algorithm}
+
+\subsection{Upper Confidence Bound (UCB)}
+The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards.
+UCB estimates an empirical confidence bound for each arm based on the observations seen so far.
+Then it pulls the arm with the highest confidence bound.
+The confidence interval is derived from various concentration inequalities and assumes the reward function is bounded.
+The algorithm is in Algorithm 2 and assumes a Beta-Bernoulli Distribution, which is the case in our grasping.
+
+\begin{algorithm}
+ \KwResult{Best Arm, $g^*$ }
+\For{ t=1,2,...}{ 
+ Pick arm: $ k = \underset{k\in{1,...,K}}{\mbox{argmax}} \mu_k + \sqrt{\frac{6\mbox{log}(t)}{T_k}}$\\
+ Observe reward $X_{k_t,t} \in \lbrace 0,1 \rbrace$\\
+ Update\\
+ $T_k= T_k +1$\\
+ $\mu_k = \frac{T_k-1}{T_k}*\mu_k + \frac{1}{T_k}*X_{k,t}$\\
+ }
+ \caption{UCB for Beta-Bernoulli Process}
+\end{algorithm}
+
+\subsection{The Gittins Index Method} 
+One possible solution to solve the MAB problem is to treat is as an Markov Decision Process (MDP) and use Markov Decision theory.
+This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$.
+
+However, the \textit{curse of dimensionality} effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your arms then your state space is on the order of $T^{2*K}$.
+Hence the complexity of solving MAB using Markov Decision theory increases exponentially with the number of bandit processes.
+A key insight though was given by Gittins, who showed that instead of solving the $k$-dimensional MDP one can instead solve a $k$ 1-dimensional optimization problems: for each arm $i$, $i= 1,...,k$, and for each state of $x^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$.
+
+\vspace{-2ex}
+\label{eq:git_indices}
+\begin{align}
+	v^i(x^i) = \underset{\tau>0}{\mbox{max}} \frac{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^tr^i(X_t^i)|X_0^i = x_i]}{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^t|X_0^i = x_i]}
+\end{align}
+
+The indices can be considered as a computation of the value in choosing an arm conditioned on the fact that you will give up an choose another arm at some point.
+Once you know the state of your $k$ arms, the algorithm is to select the one with the highest index.
+For Best Arm Identification you want your discount factor $\gamma$ to approach 1, since you should never stop pulling the best arm.
+We computed the Gittins indices offline using the restart method proposed by Katehakis et al.
+\cite{katehakis1987multi}.
+
+\begin{algorithm}
+ \KwResult{Best Arm, $g^*$ }
+ For Beta(1,1) prior, Table of Indices $v$, Discount Factor $\gamma$: \\
+\For{ t=1,2,...}{ 
+ Pull arm $k = \underset{x_k \in X}{\mbox{argmax}} v(x_k)$\\
+ Observe reward $R_{I_t,t} \in \lbrace 0,1 \rbrace$\\
+ Update posterior:\\
+ Set $S_{I_t,t+1} = S_{I_t,t} + R_{I_t,t}$ \\
+ Set $F_{I_t,t+1} = F_{I_t,t} + 1 - R_{I_t,t}$\\
+ Set $x_k = \lbrace 1 + S{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
+}
+ \caption{The Gittins Index Method for Beta-Bernoulli Process}
+\end{algorithm}
 
@@
 
-The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$.
+The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
 Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
@@
 If the convex hull does not enclose the origin, the grasp is not in force-closure.
-Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.
+Formally, not being in force closure means there exists a wrench for which the grasp is not able to resist against, which occurs if the Quality metric $Q$ is less than zero.
+Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.
 
-Since we are in an uncertain environment, we are interested in calculating the expected quality, or $P(Q>0)$, or the probability of achieving force closure, similar too  \cite{christopoulos2007handling}\cite{kehoe2012toward} .
+Since we are in an uncertain environment, we are interested in calculating the probability of achieving force closure, or $P(Q>0)$, similar to  \cite{christopoulos2007handling}\cite{kehoe2012toward} .
 $P(Q>0)$ is computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
@@
 
+\subsection{Line of action}
+In an uncertain environment one would not actually know the true $g$ because the actual grasp that is executed is non-deterministic.
+Thus, we have to work with the trajectory of the gripper.
+Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
+\ref{fig:line_of_action}.
+A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
+
 \subsection{Types of Uncertainty}
-In this work we consider the following types of uncertainty shape, pose, center of mass and friction coefficient.
-The probabilistic relationship of all these types of uncertainty can be seen in Fig.
+In this work we consider the following types of uncertainty shape, pose, movement  and friction coefficient.
+The property of force closure is not effected, by the location of center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.
+Thus we calculate the expected The probabilistic relationship of all these types of uncertainty can be seen in Fig.
 \ref{fig:graphical_model}.
@@
 
-For shape, we use a GPIS representation as described in Sec.
-\ref{sec:GP}.
-For pose we sample the centroid of the GPIS from a Gaussian distribution with user covariance matrix.
-Center of mass a Gaussian  with mean as the expected center of mass, as defined in Eq.
-\ref{eq:mass}, assuming uniform mass distribution.
-Lastly, for friction coefficient we represent it as Gaussian with mean around the expected friction coefficient provided by a user.
+\subsubsection{Distribution on Shape}
+
+For shape we use a GPIS representation, which is explained in detail in Sec.
+\ref{sec:Appendix}.
+Essenttialy, a GPIS is a Gaussian distribution on a signed distance function that describes the workspace.
+The GPIS can be sampled from vian $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
+For our application we set $x$ to discretized points along each line of action $\gamma_i$ and for each sample see where the sample is equal to zero.
+We will furthermore represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \rbrace\mu(x), \Sigma(x)\lbrace$.
+
+\subsubsection{Distribution on Pose}
+ \todo{Jeff can you write about Pose}
+
+ \subsubsection{Distribution on Movement}
+ In practice a robot may not be able to execute a desired
+grasp plan $\Gamma$ exactly due to errors in trajectory following or
+registration to the object \cite{kehoe2012estimating}.
+To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$.
+In practice $\sigma^2$ can be set from repeatibility measurements for a robot \cite{mooring1986determination}.
+
+ \subsubsection{Distribution on Friction Coefficient}
+As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation.
+The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table.
+However, because their could be material in between the objects surface and the robot gripper (i.e.
+dust, water, moisture).
+It is important to assume noise.
+Thus, we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.
+
+Thus to evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
+\ref{fig:graphical_model}.
+In the naive way sampling from the graphical model could be slow, however our goal is not to actually determine the probability of force closure but instead to determine the best grasp in a set $G$.
+Thus, our BMAB algorithms can efficiently sample from theses priors on the different types of uncertainty.
 
@@
 
-\subsection{Line of action}
-In an uncertain environment one would not actually know the true $g$, thus we have to work with the trajectory of the gripper.
-Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
-\ref{fig:line_of_action}.
-A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-
 \begin{figure}[ht!]
@@
 
-While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial robots. 
-Future work will look at how to efficiently sample when the approach trajectory has noise.
-
 \subsection{Problem Definition}
 
-Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model, which we describe in Section \ref{sec:GP} and set of possible grasp plans $G$.
-We are interested in determining
-
-\begin{align}\label{eq:problem_def}
-\Gamma^* \in \mbox{argmax}_{\Gamma \in G} P(Q(\Gamma)>0)
-\end{align}
-
-with respect to a chosen grasp metric Q.
-
-\section{Multi-Armed Bandits for Grasp Selection}
-While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
-In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
-Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
-The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
-We have a policy for exploration of different grasp plans (i.e.
-choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.
-The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.
-
-In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $P(Q(\Gamma)>0)$ determined via Monte-Carlo Integration.
-Since the function to test force closure is boolean, we can model our problem as choosing the best arm for a Beta-Bernoulli Process.
-Methods with very strong guarantees are now available to us \cite{review}.
-We now review some of them.
-\section{Bandit Algorithms For Best Arm Identification}
-\subsection{Thompson Sampling}
-Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
-The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled.
-Then sample from the prior distribution on all arms and pull the arm with the highest sample drawn.
-The full algorithm is shown in Algorithm 1.
-Empirically this method has been shown to outperform frequentist methods like UCB \cite{chapelle2011empirical}
-
-\subsection{Upper Confidence Bound (UCB)}
-The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards.
-It basically assumes a frequenist perspective and estimates an empirical confidence bound for each arm based on the observations seen so far.
-Then it pulls the arm with the highest confidence bound.
-
-\subsection{Gittins Index} 
-Gittins index treats the bandit problem as an Markov Decision Process where each lever pull is taking a step along a Markov Chain.
-While, normally the cost of computing an optimal policy would be exponential in the number of K arms.
-The independence assumption between each arms allows us to decouple them and solve for a policy that models taking pulls along one arm or selecting a reference arm that represents selecting a different possible value.
-We computed the Gittins indices using the restart method proposed by Katehakis et al.
-\cite{katehakis1987multi}.
-
-\begin{algorithm}
- \KwResult{Best Arm, $g^*$ }
- For Beta(1,1) prior: \\
-\For{ t=1,2,...}{ 
- Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
- Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
- Observe reward $X_{I_t,t}$\\
- Update poster:\\
- Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
- Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
-
- }
- \caption{Thompson Sampling}
-\end{algorithm}
-
-\section{Evaluating a Grasp on Gaussian Process Implicit Surface}
- In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$.
-We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.
-
-\subsection{Gaussian Process (GP) Background}\label{sec:GP}
-We refer the reader to \cite{mahler2015opt} for a more detailed explanation of the GP construction, which we summarize here.
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$, or the distribution on signed distance field, at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
-\begin{align*}
-	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
-	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
-	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
-\end{align*}
-where $K \in \mathbb{R}^{l \times l}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_l,\bx_*)]^{\intercal}$. 
-This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:
+Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model, which we describe in Section \ref{sec:GP} and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
+We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.
 
 \vspace{-2ex}
-\begin{align}
-	\text{cov}\left(sd(\bx_i), sd(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, sd(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
-	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, \frac{\partial sd (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
+\begin{align}\label{eq:problem_def}
+\Gamma^* \in \underset{\Gamma \in G}{\mbox{argmax}} P(Q(\Gamma)>0)
 \end{align}
-
-For our kernel choice we decided to use the square exponential kernel, similar to \cite{dragiev2011}.
-Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
-
-We construct a GPIS by learning a Gaussian process to fit measurements of a signed distance field of an unknown object.
-Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\subsection{Calculating the Probability of Force Closure}
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (S )$, the distribution on center of mass $P (z)$ and the distribution on friction coefficient $P (\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the probability of force closure as follows
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|S,\mu,z) > 0) = \frac{\alpha}{\alpha + \beta}
-\end{align}
-
-Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(z)$,$p(\mu)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
-See Fig.
-\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
-For computational reasons we approximate the integral via Monte-Carlo Integration.
-We use importance sampling to draw from the distribution induced by GPIS and  count the number of sucesses of the grasp $S$ and the number of failures $F$ and calculate the following
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|S,\mu,z) > 0) \approx \frac{(S + \alpha_0)}{(\alpha_0 + S) +( \beta_0 + F)}
-\end{align}
-
-Here $\alpha_0$ and $\beta_0$ correspond to the intial shape parameters.
-To compute the above distribution we must draw samples from $p(S)$.
-In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$.
-Since this is a GPIS, we know the following
-
-\begin{align}\label{eq:joint_shape}
-p(S) = p(sd(\mathcal{W})) \sim N(\mu(\mathcal{W}),\Sigma(\mathcal{W}))
-\end{align}
-
-Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
-Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way scales with the cube of the number of input dimensions \cite{petersen2008matrix}.
-Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
-\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
-\vspace*{-10pt}
-\label{fig:shape_samples}
-\end{figure}
-
-To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves.
-We recall that a grasp according to our metric is defined as the tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z )$.
-We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$.
-The distribution on a grasp is defined then as:
-
-\begin{align}\label{eq:joint_on_shape}
-p(g) = p\big(\textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m|\Gamma,\mu(x),\Sigma(x)\big)
-\end{align}
-
-We note here that we currently use the friction coefficient $\mu$ and the expected center of mass $\bar{z}$ as deterministic values.
-For grippers that do not approach along the same line of action (i.e.
-non-parallel jaw grippers) we make the assumption that each contact and normal pair is independent, or
-
-\vspace{-2ex}
-\begin{align}\label{eq:independence}
-p(g) = &\prod_{i=1}^mp\big(\textbf{c}_i,\textbf{n}_i|\gamma_i(t),\mu(x),\Sigma(x)\big)
-\end{align}
-
-We will now show how these distributions can be computed and how the computational complexity for sampling from a grasp plan is reduced from $O(n^6)$ to $O(n^3)$ for a GPIS model.
 
@@
 
- To sample from $p(g)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Using Bayes rule we can rewrite this as
+ To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\theta, \rho)$.
+Using Bayes rule and our graphical model we can rewrite this as
 
@@
  \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))=\\
- &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))p(c_i|\gamma_i(t),\mu(x),\Sigma(x))
+ &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\rho)=\\
+ &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\theta,\rho)p(\textbf{c}_i|\gamma_i(t),\theta,\rho)
  \end{align*}
 
- In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$.
-Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))$ and present a novel visualization technique for the distribution on surface normals.
+ In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$ from a GPIS model.
+Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\theta,\rho)$ and present a novel visualization technique for the distribution on surface normals.
 Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.
  .
-\subsection{Distribution on Contact Points}\label{sec:contact} 
-We would like to find the distribution on contact point $\textbf{c}_i$.
-A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface.
-We express this as the following conditions:
-
-\vspace{-2ex}
-\begin{align}
- &sd(\gamma(t)) = 0 \label{eq:density_cond} \\
-&sd(\gamma(\tau)) > 0, \: \forall \tau \in [a,t) \label{eq:cdf_cond}
-\end{align}
-
-We will now demonstrate how to efficiently sample from $p(\textbf{c}_i|\mu{x},\Sigma{x},\gamma_i{t})$
-
-The probability distribution along the line $\gamma(t)$ is given by:
-
-\vspace{-2ex}
-\begin{equation} \label{eq:line_of_act_dist}
-p\big(sd(\gamma(t)) ; \mu(t),\Sigma(t)\big) \ \forall t \in [a,b] 
-\end{equation}
-
-This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian.
-One could think of this as a marginalization of all other points in signed distance field except the line of action.
-To sample contact points, one can draw samples from Eq.
-\ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies  Eq.
-\ref{eq:density_cond} and Eq.
-\ref{eq:cdf_cond}.
-
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
-\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
-Visualization technique comes from \cite{mahler2015opt}.
-Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
-The two modes correspond to the different potential contact points, either the handle or the base of the cup.
-Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}.
-We plotted the probability mass along the unit circle, to reflect the normalization of the surface normals.
-}
-\vspace*{-10pt}
-\label{fig:GraspDist}
-\end{figure*}
-
 \subsection{Distribution on Surface Normals}\label{sec:normals} 
@@
 We can now write
-
-\vspace{-2ex}
-\begin{align*}
-p\big(\textbf{n}_i|\textbf{c}_i = \gamma(t)\big) = p\big(\textbf{n}_i |\mu(\gamma(t)), \Sigma(\gamma(t)) \big)
-\end{align*}
 
@@
 
-\subsection{Complexity Analysis on Sampling From Grasps Distributions}
+\section{Multi-Armed Bandits for Grasp Selection}
+While a standard approach to solving the problem in Eq.
+\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
+In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
+Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
+The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
 
-After deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
-\ref{eq:independence}.
-This can be done by drawing samples from the GP for signed distance and normals simultaneously and using our projection technique for the normal distribution.
+We can now model the distribution on rewards as a Beta-Bernoulli process.
+Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
+The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
 
-Having a distribution along a line of action model allows us to sample from those instead of the joint distribution $p(sd(\mathcal{W}))$.
-Assuming the number of discretization points along the line of action is $n$, sampling from this distribution for a single grasp is $O(n^3)$.
-However, each proposed grasp plan $\Gamma$ requires the distribution to be computed, so if we have $T=|G|$ then the complexity is $O(Tn^3)$.
-In practice, this should be much smaller than $O(n^6)$.
+Since, we have framed the method as a Beta-Bernoulli problem we can use the methods in Sec.\ref{sec:algorithms} and obtain guarantees in the convergence properties of regret and overall performance of our policy for grasp allocation.
+
+\section{Calculating the Probability of Force Closure}
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (S )$, the distribution on center of mass $P (z)$ and the distribution on friction coefficient $P (\mu)$.
+The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Thus, we can write the probability of force closure as follows
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|S,\mu,z) > 0) = \frac{\alpha}{\alpha + \beta}
+\end{align}
+
+Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(z)$,$p(\mu)$.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
+See Fig.
+\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
+For computational reasons we approximate the integral via Monte-Carlo Integration.
+We use importance sampling to draw from the distribution induced by GPIS and  count the number of sucesses of the grasp $S$ and the number of failures $F$ and calculate the following
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|S,\mu,z) > 0) \approx \frac{(S + \alpha_0)}{(\alpha_0 + S) +( \beta_0 + F)}
+\end{align}
+
+Here $\alpha_0$ and $\beta_0$ correspond to the initial shape parameters, we initialize them both to $\alpha_0 = \beta_0 = 1$ to reflect a uniform distribution on the probability of force closure .
 
@@
 
+\section{Appendix} \label{sec:Appendix}
+ In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$.
+We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.
+
+\subsection{Gaussian Process (GP) Background}\label{sec:GP}
+We refer the reader to \cite{mahler2015opt} for a more detailed explanation of the GP construction, which we summarize here.
+Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$, or the distribution on signed distance field, at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
+\begin{align*}
+	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
+	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
+	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
+\end{align*}
+where $K \in \mathbb{R}^{l \times l}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_l,\bx_*)]^{\intercal}$. 
+This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:
+
+\vspace{-2ex}
+\begin{align}
+	\text{cov}\left(sd(\bx_i), sd(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
+	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, sd(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
+	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, \frac{\partial sd (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
+\end{align}
+
+For our kernel choice we decided to use the square exponential kernel, similar to \cite{dragiev2011}.
+Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
+
+We construct a GPIS by learning a Gaussian process to fit measurements of a signed distance field of an unknown object.
+Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
+
+\subsection{Calculating the Probability of Force Closure}
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (S )$, the distribution on center of mass $P (z)$ and the distribution on friction coefficient $P (\mu)$.
+The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Thus, we can write the probability of force closure as follows
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|S,\mu,z) > 0) = \frac{\alpha}{\alpha + \beta}
+\end{align}
+
+Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(z)$,$p(\mu)$.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
+See Fig.
+\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
+For computational reasons we approximate the integral via Monte-Carlo Integration.
+We use importance sampling to draw from the distribution induced by GPIS and  count the number of sucesses of the grasp $S$ and the number of failures $F$ and calculate the following
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|S,\mu,z) > 0) \approx \frac{(S + \alpha_0)}{(\alpha_0 + S) +( \beta_0 + F)}
+\end{align}
+
+Here $\alpha_0$ and $\beta_0$ correspond to the initial shape parameters, we initialize them both to $\alpha_0 = \beta_0 = 1$ to reflect a uniform distribution on the probability of force closure .
+To compute the above distribution we must draw samples from $p(S)$.
+In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$.
+Since this is a GPIS, we know the following
+
+\begin{align}\label{eq:joint_shape}
+p(S) = p(sd(\mathcal{W})) \sim N(\mu(\mathcal{W}),\Sigma(\mathcal{W}))
+\end{align}
+
+Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
+Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way scales with the cube of the number of input dimensions \cite{petersen2008matrix}.
+Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
+\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
+\vspace*{-10pt}
+\label{fig:shape_samples}
+\end{figure}
+
+To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves.
+We recall that a grasp according to our metric is defined as the tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z )$.
+We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$.
+The distribution on a grasp is defined then as:
+
+\begin{align}\label{eq:joint_on_shape}
+p(g) = p\big(\textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m|\Gamma,\mu(x),\Sigma(x)\big)
+\end{align}
+
+We note here that we currently use the friction coefficient $\mu$ and the expected center of mass $\bar{z}$ as deterministic values.
+For grippers that do not approach along the same line of action (i.e.
+non-parallel jaw grippers) we make the assumption that each contact and normal pair is independent, or
+
+\vspace{-2ex}
+\begin{align}\label{eq:independence}
+p(g) = &\prod_{i=1}^mp\big(\textbf{c}_i,\textbf{n}_i|\gamma_i(t),\mu(x),\Sigma(x)\big)
+\end{align}
+
+We will now show how these distributions can be computed and how the computational complexity for sampling from a grasp plan is reduced from $O(n^6)$ to $O(n^3)$ for a GPIS model.
+
+\subsection{Distribution on Contact Points}\label{sec:contact} 
+We would like to find the distribution on contact point $\textbf{c}_i$.
+A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface.
+We express this as the following conditions:
+
+\vspace{-2ex}
+\begin{align}
+ &sd(\gamma(t)) = 0 \label{eq:density_cond} \\
+&sd(\gamma(\tau)) > 0, \: \forall \tau \in [a,t) \label{eq:cdf_cond}
+\end{align}
+
+We will now demonstrate how to efficiently sample from $p(\textbf{c}_i|\mu{x},\Sigma{x},\gamma_i{t})$
+
+The probability distribution along the line $\gamma(t)$ is given by:
+
+\vspace{-2ex}
+\begin{equation} \label{eq:line_of_act_dist}
+p\big(sd(\gamma(t)) ; \mu(t),\Sigma(t)\big) \ \forall t \in [a,b] 
+\end{equation}
+
+This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian.
+One could think of this as a marginalization of all other points in signed distance field except the line of action.
+To sample contact points, one can draw samples from Eq.
+\ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies  Eq.
+\ref{eq:density_cond} and Eq.
+\ref{eq:cdf_cond}.
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
+\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
+Visualization technique comes from \cite{mahler2015opt}.
+Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
+The two modes correspond to the different potential contact points, either the handle or the base of the cup.
+Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}.
+We plotted the probability mass along the unit circle, to reflect the normalization of the surface normals.
+}
+\vspace*{-10pt}
+\label{fig:GraspDist}
+\end{figure*}
+
+\subsection{Complexity Analysis on Sampling From Grasps Distributions}
+
+After deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
+\ref{eq:independence}.
+This can be done by drawing samples from the GP for signed distance and normals simultaneously and using our projection technique for the normal distribution.
+
+Having a distribution along a line of action model allows us to sample from those instead of the joint distribution $p(sd(\mathcal{W}))$.
+Assuming the number of discretization points along the line of action is $n$, sampling from this distribution for a single grasp is $O(n^3)$.
+However, each proposed grasp plan $\Gamma$ requires the distribution to be computed, so if we have $T=|G|$ then the complexity is $O(Tn^3)$.
+In practice, this should be much smaller than $O(n^6)$.
+
 \end{document}

### 2014-12-19 paper.tex
second pass of the day

@@
 
-We also show how to estimate distributions on the contact points and surface normals and center of mass using a GPIS shape representation.
-We then leverage these distributions to reduce the computational complexity of sampling from the GPIS model from $O(n^6)$ to $O(n^3)$, where the workspace is discretized as a $n \times n$ grid.
+We also show how to estimate distributions on the contact points and surface normals and center of mass using a graphical model to represent uncertainty in motion, shape, pose and friction coefficient.
 Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach.
@@
 \ref{sec:Appendix}.
-Essenttialy, a GPIS is a Gaussian distribution on a signed distance function that describes the workspace.
-The GPIS can be sampled from vian $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
+Essentially, a GPIS is a Gaussian distribution on a signed distance function that describes the workspace.
+The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
 For our application we set $x$ to discretized points along each line of action $\gamma_i$ and for each sample see where the sample is equal to zero.
@@
 
-Thus to evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
+To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
 \ref{fig:graphical_model}.
@@
 \section{Calculating the Probability of Force Closure}
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (S )$, the distribution on center of mass $P (z)$ and the distribution on friction coefficient $P (\mu)$.
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\Delta)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
 The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the probability of force closure as follows
+Thus, we can write the expected probability of force closure as follows
 
@@
 \begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|S,\mu,z) > 0) = \frac{\alpha}{\alpha + \beta}
+P(Q(\Gamma|\theta,\mu,\Delta,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
 \end{align}
 
-Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(z)$,$p(\mu)$.
+Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(\Delta)$,$p(\rho)$ and $p(\mu)$.
 To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
-See Fig.
-\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
-For computational reasons we approximate the integral via Monte-Carlo Integration.
-We use importance sampling to draw from the distribution induced by GPIS and  count the number of sucesses of the grasp $S$ and the number of failures $F$ and calculate the following
+Whats interesting in the context of a BMAB problem our complicated graphical model in Fig.
+\ref{fig:graphical_model}, can now be replaced by \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
+It is this intuition that helps explain the performance of the BMAB algorithm.
 
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|S,\mu,z) > 0) \approx \frac{(S + \alpha_0)}{(\alpha_0 + S) +( \beta_0 + F)}
-\end{align}
-
-Here $\alpha_0$ and $\beta_0$ correspond to the initial shape parameters, we initialize them both to $\alpha_0 = \beta_0 = 1$ to reflect a uniform distribution on the probability of force closure .
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
+\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
+\vspace*{-10pt}
+\label{fig:beta_model}
+\end{figure}
 
@@
 \subsection{Multi-Armed Bandit Experiments}
-
+\todo{Running experiments over break, going to fill this in as results come in}
 We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$.
@@
 
-\subsection{Calculating the Probability of Force Closure}
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (S )$, the distribution on center of mass $P (z)$ and the distribution on friction coefficient $P (\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the probability of force closure as follows
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|S,\mu,z) > 0) = \frac{\alpha}{\alpha + \beta}
-\end{align}
-
-Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(z)$,$p(\mu)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
-See Fig.
-\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
-For computational reasons we approximate the integral via Monte-Carlo Integration.
-We use importance sampling to draw from the distribution induced by GPIS and  count the number of sucesses of the grasp $S$ and the number of failures $F$ and calculate the following
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|S,\mu,z) > 0) \approx \frac{(S + \alpha_0)}{(\alpha_0 + S) +( \beta_0 + F)}
-\end{align}
-
-Here $\alpha_0$ and $\beta_0$ correspond to the initial shape parameters, we initialize them both to $\alpha_0 = \beta_0 = 1$ to reflect a uniform distribution on the probability of force closure .
-To compute the above distribution we must draw samples from $p(S)$.
+\subsection{Sampling Shape from GPIS Distribution }
+To compute the above distribution we must draw samples from $p(\theta)$.
 In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$.
@@
 
-\subsection{Distribution on Contact Points}\label{sec:contact} 
+\subsection{Sampling Line of Action from GPIS Distribution}\label{sec:contact} 
 We would like to find the distribution on contact point $\textbf{c}_i$.

### 2014-12-19 paper.tex
Made edits to the first four pages of the paper. Most edits were made to wording in the intro. 	modified:   paper.tex

@@
 \newcommand{\bw}{\mathbf{w}}
+\newcommand{\bt}{\mathbf{t}}
 \newcommand{\by}{\mathbf{y}}
@@
 We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.
-To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object defined by a Gaussian process implicit surface (GPIS), but the method is applicable to other models of uncertainty.
-We derive distributions on contact points, surface normal, and center of mass and use these solve the associated MAB model, finding that it computes grasps of similar quality and can reduce computation time by an order of magnitude.
+To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.
+We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
 This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
@@
 Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
-The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and even material properties like friction coefficient or center of mass.
-Due to sensor noise and missing data due to partial visibility and object properties such as transparency, the robot may not be able to measure these quantities exactly.
+The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and material properties like friction coefficient or center of mass. 
+Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from partial visibility and object properties such as transparency, .
 Grasp planners that assume exact prior knowledge of object geometry or an exact measurement of pose may fail in this environment.
@@
 Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
-This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
-To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
+Recent work motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty requires exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
+To select a grasp with high quality this evaluation must be performed for a large set of potential grasps, which can be very time-consuming.
 However, when evaluating a set of grasps we may be able to determine the difference of quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
@@
 The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration.
-The goal in a MAB model is to make a sequence of decisions over a set of possible options such that a measure of the expected reward of such decisions is maximized.
+The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of the expected reward of such decisions is maximized.
 Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
@@
 
-Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a budgeted multi-armed bandit model.
-We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality \cite{ferrari1992} under shape uncertainty.
-We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the expected quality of many potential grasp plans.
-We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}, however the method applies to any model of uncertainty that can be sampled.
+Our main contribution in this paper is formulating the problem of planning grasps with a high probabilty of success in the presence of uncertainty as a budgeted multi-armed bandit model.
+We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under shape uncertainty.
+We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the probability of success for many potential grasp plans.
+We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}, but our method applies to any model of uncertainty that can be sampled.
 
@@
 A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
-Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
+Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
 Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-Traditional bandit algorithms minimize cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
+A common measure of success in MAB problems is {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
+Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices.
 There are a number of algorithms for developing policies to balance exploration and exploitation.
@@
 A class of algorithms that have stronger theoretical guarantees are from the Upper Confidence Bound (UCB) family.
-UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times each arm has been sampled.
+For each arm, UCB algorithms maintain the empirical expected reward and an upper confidence bound on the true expected reward using concentration inequalities for the assumed reward distribution.
 
@@
 
-Different to the normal bandit problem, we do not actually care about cumulative regret because the exploration and exploitation stage is decoupled from each other.
-For example in medical testing for patients it is important to always administer the best treatment for the given patient.
-However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
-Thus, performance of Budgeted Multi-Armed Bandit models is measured in terms of the convergence of simple regret.
+In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages. 
+%For example in medical testing for patients it is important to always administer the best treatment for the given patient.
+%However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
+This is an instance of the Budgeted Multi-Armed Bandit (BMAB) model, in which performance is measured in terms of simple regret after a fixed ``budget'' number of arm pulls.
+Thus our goal in the BMAB model is to identify the best arm by the end of our budget.
 Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}\mu_k}$.
-The regret at time $t$ is given by Eq.
-\ref{eq:simple_regret}, where $\mu_t$ is the estimate of the best arm at time $t$ from the previous observations.
+The simple regret at time $t$ is given by
 
@@
 \end{align}
+\noindent where $\mu_t$ is the estimate of the best arm at time $t$ from the previous observations.
 
@@
 In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates.
-Originally the problem was solved by racing algorithms, were methods used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were deemed not likely to succeed and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
-These methods were later extended to include not only the best arm, but return the top $m$ arms \cite{gabillon2012best}.
+Originally the problem was solved racing algorithms, which used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were likely to be suboptimal and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
+These methods were later extended to return the top $m$ arms instead of only the best arm\cite{gabillon2012best}.
 
@@
 Audibert el al.
-demonstrated an algorithm called Successive Rejects that given a budget divides up the time each arm is pull an can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
-Other UCB like methods have been proposed as well that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
-In \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.
+demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
+This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
+In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
+For example in \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.
 
-For the case of choosing the best grasp, we are working in the scenario where the robot has a fix amount of time to choose a grasp and thus the fixed budget setting is more appropriate.
+In  this work we consider a setting in which a robot has a fixed computational time budget to select a grasp and thus the fixed budget setting is more appropriate.
 
@@
 Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
-The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled.
-Then sample from the prior distribution on all arms and pull the arm with the highest sample drawn.
+The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled, then sample from the prior distribution on all arms and pull the arm with the highest sample drawn.
 The full algorithm is shown in Algorithm 1.
-Empirically this method has been shown to outperform frequentist methods like UCB \cite{chapelle2011empirical}
+Empirically this method has been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}
 
@@
 The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards.
-UCB estimates an empirical confidence bound for each arm based on the observations seen so far.
-Then it pulls the arm with the highest confidence bound.
-The confidence interval is derived from various concentration inequalities and assumes the reward function is bounded.
-The algorithm is in Algorithm 2 and assumes a Beta-Bernoulli Distribution, which is the case in our grasping.
+UCB estimates an empirical confidence bound for each arm based on the observations seen so far., then pulls the arm with the highest confidence bound.
+The confidence interval is derived from various concentration inequalities.
+The algorithm is in Algorithm 2 and assumes a Beta-Bernoulli Distribution, which matches our assumption of a 0-1 success measure for grasping.
 
@@
 \subsection{The Gittins Index Method} 
-One possible solution to solve the MAB problem is to treat is as an Markov Decision Process (MDP) and use Markov Decision theory.
+One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory.
 This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$.
 
-However, the \textit{curse of dimensionality} effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your arms then your state space is on the order of $T^{2*K}$.
+However, the curse of dimensionality effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your arms then your state space is on the order of $T^{2*K}$.
 Hence the complexity of solving MAB using Markov Decision theory increases exponentially with the number of bandit processes.
@@
 In their work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
-Importantly the magnitude of Q yields a measurement that allows one to rank grasps by their physical stability and evaluate the property of force-closure.
+The magnitude of Q allows one to rank grasps by their physical stability and to evaluate the property of force-closure.
 Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
@@
 \subsubsection{Distribution on Pose}
- \todo{Jeff can you write about Pose}
+In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
+Therefore pose uncertainty may come from two primary sources a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
+The effects of pose uncertainty on robotic grasping has been studied by ~\cite{}.
+
+The pose of an object $T$ is a member of the Lie Algebra $SO(3)$ in 3-dimensional space (something analogous holds for 2D).
+This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\xi = (\bw, \bt)$.
+One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
+Thus, the following transformations can be used to quantify uncertainty in the matrix $T$ as a function of Gaussian uncertainty in the parameters $\xi$:
+
+\todo{Jeff: Put equations here. Sorry my internet is too slow to download the paper i need right now}
 

### 2014-12-22 paper.tex
changed up graphical, model and simplified computation

@@
 Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}.
+Mahler et al.
+used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}.However, when evaulating his locally optimal grasps they resorted to exhaustive MC sampling over the distributions of grasp quality.
+We purpose an adaptive sampling approach known as the Multi-Armed Bandit Model.
 
@@
 
-In  this work we consider a setting in which a robot has a fixed computational time budget to select a grasp and thus the fixed budget setting is more appropriate.
+In  this work we consider a setting in which a robot has a fixed computational time limit to select a grasp and thus the fixed budget setting is more appropriate.
+The time limit can be chosen via repeatibility experiments on a desire task.
+In Section \ref{sec:bandit_algorithm}, we will discuss some of the specific budgeted multi-armed bandit algorithms that are used in practice.
 
+\label{sec:bandit_algorithm}
 \section{Bandit Algorithms For Best Arm Identification}\label{sec:algorithms}
@@
 \centering
-\includegraphics[width = 6cm, height = 4cm]{figures/Slide8.jpg}
+\includegraphics[width = 6cm, height = 6cm]{figures/Slide8.jpg}
 \caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
@@
 
-\section{Distribution of Grasp Parameters}
+\section{Distributions on Grasp Parameters}
 \label{sec:distgrasp}
 
- To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\theta, \rho)$.
+ To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\Delta,\theta, \rho)$.
 Using Bayes rule and our graphical model we can rewrite this as
@@
  \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\rho)=\\
- &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\theta,\rho)p(\textbf{c}_i|\gamma_i(t),\theta,\rho)
+ &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\Delta,\rho)=\\
+ &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)
  \end{align*}
 
- In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$ from a GPIS model.
-Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\theta,\rho)$ and present a novel visualization technique for the distribution on surface normals.
+ In section \ref{sec:contact}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)$ along with the other sampled distribution on pose ($\Delta$) and motion ($\rho$).
+Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals.
 Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.
@@
 
+\vspace{-2ex}
 \begin{align}\label{eq:joint_shape}
@@
 Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
-Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way scales with the cube of the number of input dimensions \cite{petersen2008matrix}.
-Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
+Shape samples drawn from the distribution appear in Fig.
+\ref{fig:shape_samples}.
 
@@
 
-To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves.
-We recall that a grasp according to our metric is defined as the tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z )$.
-We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$.
-The distribution on a grasp is defined then as:
-
-\begin{align}\label{eq:joint_on_shape}
-p(g) = p\big(\textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m|\Gamma,\mu(x),\Sigma(x)\big)
-\end{align}
-
-We note here that we currently use the friction coefficient $\mu$ and the expected center of mass $\bar{z}$ as deterministic values.
-For grippers that do not approach along the same line of action (i.e.
-non-parallel jaw grippers) we make the assumption that each contact and normal pair is independent, or
-
-\vspace{-2ex}
-\begin{align}\label{eq:independence}
-p(g) = &\prod_{i=1}^mp\big(\textbf{c}_i,\textbf{n}_i|\gamma_i(t),\mu(x),\Sigma(x)\big)
-\end{align}
-
-We will now show how these distributions can be computed and how the computational complexity for sampling from a grasp plan is reduced from $O(n^6)$ to $O(n^3)$ for a GPIS model.
-
-\subsection{Sampling Line of Action from GPIS Distribution}\label{sec:contact} 
-We would like to find the distribution on contact point $\textbf{c}_i$.
-A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface.
-We express this as the following conditions:
-
-\vspace{-2ex}
-\begin{align}
- &sd(\gamma(t)) = 0 \label{eq:density_cond} \\
-&sd(\gamma(\tau)) > 0, \: \forall \tau \in [a,t) \label{eq:cdf_cond}
-\end{align}
-
-We will now demonstrate how to efficiently sample from $p(\textbf{c}_i|\mu{x},\Sigma{x},\gamma_i{t})$
-
-The probability distribution along the line $\gamma(t)$ is given by:
-
-\vspace{-2ex}
-\begin{equation} \label{eq:line_of_act_dist}
-p\big(sd(\gamma(t)) ; \mu(t),\Sigma(t)\big) \ \forall t \in [a,b] 
-\end{equation}
-
-This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian.
-One could think of this as a marginalization of all other points in signed distance field except the line of action.
-To sample contact points, one can draw samples from Eq.
-\ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies  Eq.
-\ref{eq:density_cond} and Eq.
-\ref{eq:cdf_cond}.
-
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
-\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
-Visualization technique comes from \cite{mahler2015opt}.
-Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
-The two modes correspond to the different potential contact points, either the handle or the base of the cup.
-Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}.
-We plotted the probability mass along the unit circle, to reflect the normalization of the surface normals.
-}
-\vspace*{-10pt}
-\label{fig:GraspDist}
-\end{figure*}
-
-\subsection{Complexity Analysis on Sampling From Grasps Distributions}
-
-After deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
-\ref{eq:independence}.
-This can be done by drawing samples from the GP for signed distance and normals simultaneously and using our projection technique for the normal distribution.
-
-Having a distribution along a line of action model allows us to sample from those instead of the joint distribution $p(sd(\mathcal{W}))$.
-Assuming the number of discretization points along the line of action is $n$, sampling from this distribution for a single grasp is $O(n^3)$.
-However, each proposed grasp plan $\Gamma$ requires the distribution to be computed, so if we have $T=|G|$ then the complexity is $O(Tn^3)$.
-In practice, this should be much smaller than $O(n^6)$.
-
 \end{document}

### 2014-12-23 paper.tex
Made minor edits to wording in the sections up to experiments. Needs reorganization. 	modified:   paper.tex

@@
 Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model with a finite stopping time where the objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
+The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model with a finite number of total decisions to be made before a predetermined `stopping time'.
+The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
 
-Our main contribution in this paper is formulating the problem of planning grasps with a high probabilty of success in the presence of uncertainty as a budgeted multi-armed bandit model.
+Our main contribution in this paper is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
 We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under shape uncertainty.
@@
 Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach.
-These promising results suggest that our MAB approach could be used on other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements.
+These promising results suggest that our MAB approach could also provide  significant speed improvements using other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements.
+\todo{Revise above line, as we now have some experiments varying these quantities as well}
 
@@
 Mahler et al.
-used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}.However, when evaulating his locally optimal grasps they resorted to exhaustive MC sampling over the distributions of grasp quality.
-We purpose an adaptive sampling approach known as the Multi-Armed Bandit Model.
+used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}.
+However, this relied on an approximation to grasp quality without guarantees on accuracy..
+We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.
 
 \section{Multi-Armed Bandit Model}
-The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
+The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
 The traditional setting of a multi-armed bandit model is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
 A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
-Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
-Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
+%Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
@@
 
-In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages. 
+%In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages.
+In our case we only care about regret at the time our decision of the optimal grasp has been made, decoupling the exploration and exploitation stages. 
 %For example in medical testing for patients it is important to always administer the best treatment for the given patient.
 %However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
-This is an instance of the Budgeted Multi-Armed Bandit (BMAB) model, in which performance is measured in terms of simple regret after a fixed ``budget'' number of arm pulls.
-Thus our goal in the BMAB model is to identify the best arm by the end of our budget.
-Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}\mu_k}$.
+Thus our goal is to identify the best arm in as few decisions as possible.
+Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
 The simple regret at time $t$ is given by
@@
 
-Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and one where a set horizon is given and the algorithm has to choose a arm at that stopping time.
+Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and the Budgeted Multi-Armed Bandit (BMAB) model, in which the algorithm must make a decision at the end of a fixed ``budget'' number of arm pulls.
 
@@
 In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates.
-Originally the problem was solved racing algorithms, which used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were likely to be suboptimal and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
+Originally the problem was solved with `racing' algorithms, which used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were likely to be suboptimal and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
 These methods were later extended to return the top $m$ arms instead of only the best arm\cite{gabillon2012best}.
@@
 \subsection{Fixed Budget}
-In the fixed budget setting the algorithm is given a stopping time and needs to return the best arm at that stopping time.
+In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the best arm at that stopping time.
 Audibert el al.
@@
 
-In  this work we consider a setting in which a robot has a fixed computational time limit to select a grasp and thus the fixed budget setting is more appropriate.
+In this work, we consider a setting in which a robot has a fixed computational time limit to select a grasp and thus the fixed budget setting is more appropriate.
 The time limit can be chosen via repeatibility experiments on a desire task.
@@
 \subsection{Grasp Metric}
-In their work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
-The magnitude of Q allows one to rank grasps by their physical stability and to evaluate the property of force-closure.
+Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts.
+The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object.
 Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
 
-The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
-Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-A wrench is defined as concatenation of a force and torque vector.
-If the convex hull does not enclose the origin, the grasp is not in force-closure.
-Formally, not being in force closure means there exists a wrench for which the grasp is not able to resist against, which occurs if the Quality metric $Q$ is less than zero.
+The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
+Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+If the convex hull does encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
+Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero.
 Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.
 
-Since we are in an uncertain environment, we are interested in calculating the probability of achieving force closure, or $P(Q>0)$, similar to  \cite{christopoulos2007handling}\cite{kehoe2012toward} .
-$P(Q>0)$ is computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
+In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
+$P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
 Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.
@@
 \subsection{Line of action}
-In an uncertain environment one would not actually know the true $g$ because the actual grasp that is executed is non-deterministic.
-Thus, we have to work with the trajectory of the gripper.
+In an uncertain environment may not know the true $g$ exactly due to sensing imprecision.
+Thus we propose to work with the trajectory of the gripper when analyzing grasps.
 Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
@@
 \subsection{Types of Uncertainty}
-In this work we consider the following types of uncertainty shape, pose, movement  and friction coefficient.
-The property of force closure is not effected, by the location of center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.
-Thus we calculate the expected The probabilistic relationship of all these types of uncertainty can be seen in Fig.
-\ref{fig:graphical_model}.
+In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.
+The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.
+Fig.
+\ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work.
 We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.
@@
 For our application we set $x$ to discretized points along each line of action $\gamma_i$ and for each sample see where the sample is equal to zero.
-We will furthermore represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \rbrace\mu(x), \Sigma(x)\lbrace$.
+We will furthermore represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.
 
@@
 One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
-Thus, the following transformations can be used to quantify uncertainty in the matrix $T$ as a function of Gaussian uncertainty in the parameters $\xi$:
+Thus, to sample a pose matrix $T$ one can sample from a distribution on $\xi$ and compute the poes as:
 
@@
 
- \subsubsection{Distribution on Movement}
+ \subsubsection{Distribution on Motion}
  In practice a robot may not be able to execute a desired
@@
 To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$.
-In practice $\sigma^2$ can be set from repeatibility measurements for a robot \cite{mooring1986determination}.
+In practice $\sigma^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
 
@@
 
-Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model, which we describe in Section \ref{sec:GP} and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
+We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
 We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.

### 2014-12-24 paper.tex
changed experiments

--- 2014-12-22 paper.tex
@@
 \section{Experiments}
-For the experiments below we used common household objects.
-The objects used can be found at \url{http://rll.berkeley.edu/grasping/} We manually created a 25 x 25 grid, by tracing a point cloud of the object on a table taken with a Primesense Carmine depth sensor.
-To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+For the experiments we used the Brown Vision Lab 2D dataset, the same used in \cite{christopoulos2007handling}.
+We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
 The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
+The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads,$\sigma_{trans} = 3$.
 Our visualization technique follows the approach of \cite{mahler2015opt} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
@@
 
-\subsection{Sampling from Grasps vs. Shape}
-We first tested 1000 grasp plans and sampled each one 5000 times  and measured the RMS error between converged expected grasp plan qualities for sampling shape Eq.
-\ref{eq:shape_sampling} vs.
-grasps  Eq.
-\ref{eq:grasp_sampling} was 0.004.
-After confirming the distributions converged close to the same value, we show the computational complexity in Fig.
-\ref{fig:speed_dif} of the two methods for evaluating 100 grasps on an $n \times n$ grid.
+\subsection{Sensitivity Analysis }
+We now will show how well the top two algorithms (Thompson and Gittens) perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
+The experiments are performed with the same setup as before but now we sweep the variance parameters across a range for each parameter.
+The results are shown below
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=5.7cm,height=6cm]{figures/Slide12.jpg}
-\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace.
-Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Red is sampling from $p(g)$ or the calculated distribution on grasps.
-As you can see sampling from the calculated distributions scales much better.
-}
-\vspace*{-10pt}
-\label{fig:speed_dif}
-\end{figure}
+\todo{Finish sensitivity analysis}
 

### 2014-12-24 paper.tex
added sensitivity analysis, changed ordering of sections

@@
 
+\section{Multi-Armed Bandits for Grasp Selection}
+While a standard approach to solving the problem in Eq.
+\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
+In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
+Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
+The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
+
+We can now model the distribution on rewards as a Beta-Bernoulli process.
+Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
+The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
+
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
+The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Thus, we can write the expected probability of force closure as follows
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
+\end{align}
+
+Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
+Whats interesting in the context of a BMAB problem our complicated graphical model in Fig.
+\ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
+It is this intuition that helps explain the performance of the BMAB algorithm.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
+\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
+\vspace*{-10pt}
+\label{fig:beta_model}
+\end{figure}
+
 \section{Distributions on Grasp Parameters}
@@
 
- To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\Delta,\theta, \rho)$.
+ To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
 Using Bayes rule and our graphical model we can rewrite this as
@@
  \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\Delta,\rho)=\\
+ &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
  &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)
@@
 
- In section \ref{sec:contact}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)$ along with the other sampled distribution on pose ($\Delta$) and motion ($\rho$).
+ In section \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
 Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals.
@@
 \label{fig:GPIS_MASS}
-\end{figure}
-
-\section{Multi-Armed Bandits for Grasp Selection}
-While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
-In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
-Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
-The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
-
-We can now model the distribution on rewards as a Beta-Bernoulli process.
-Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
-The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
-
-Since, we have framed the method as a Beta-Bernoulli problem we can use the methods in Sec.\ref{sec:algorithms} and obtain guarantees in the convergence properties of regret and overall performance of our policy for grasp allocation.
-
-\section{Calculating the Probability of Force Closure}
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\Delta)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the expected probability of force closure as follows
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|\theta,\mu,\Delta,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
-\end{align}
-
-Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(\Delta)$,$p(\rho)$ and $p(\mu)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
-Whats interesting in the context of a BMAB problem our complicated graphical model in Fig.
-\ref{fig:graphical_model}, can now be replaced by \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
-It is this intuition that helps explain the performance of the BMAB algorithm.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
-\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
-\vspace*{-10pt}
-\label{fig:beta_model}
 \end{figure}
@@
 \todo{Finish sensitivity analysis}
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_rot.eps}
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
+UCB does poorly on simple regret which is expected \cite{best_arm}}
+\vspace*{-10pt}
+\label{fig:simple_regret}
+\end{figure*}
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_trans.eps}
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
+UCB does poorly on simple regret which is expected \cite{best_arm}}
+\vspace*{-10pt}
+\label{fig:simple_regret}
+\end{figure*}
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
+UCB does poorly on simple regret which is expected \cite{best_arm}}
+\vspace*{-10pt}
+\label{fig:simple_regret}
+\end{figure*}
 

### 2014-12-30 paper.tex
added stuff

@@
 
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
+\documentclass[journal,transmag]{IEEEtran}% Comment this line out if you need a4paper
 
@@
 
-\overrideIEEEmargins                                      % Needed to meet printer requirements.
+%\overrideIEEEmargins                                      % Needed to meet printer requirements.
 
@@
 \usepackage{tikz,hyperref,graphicx,units,subfig}
+\usepackage{subfig}
 \usepackage{benktools}
@@
 \begin{abstract}
-Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
+\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
 Monte-Carlo sampling is computationally demanding, even for planar models.
@@
 
+\begin{abstract}
+\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to ucertainities.
+For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown.
+To handle all the uncertainites and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples.
+We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps.
+\end{abstract}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.
+
+\section{Preliminaries and Problem Definition}
+Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
+
+\subsection{Grasp Metric}
+Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts.
+The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object.
+Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
+
+The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
+Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+If the convex hull does encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
+Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero.
+Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.
+
+In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
+$P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
+Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.
+
+\subsection{Line of action}
+In an uncertain environment may not know the true $g$ exactly due to sensing imprecision.
+Thus we propose to work with the trajectory of the gripper when analyzing grasps.
+Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
+\ref{fig:line_of_action}.
+A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
+Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
+
+\subsection{Types of Uncertainty}
+In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.
+The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.
+Fig.
+\ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work.
+We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.
+
+\subsubsection{Distribution on Shape}
+
+Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}.
+To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Sec.
+\ref{sec:Appendix}.
+A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace.
+A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.
+The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
+For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape.
+We will henceforth  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.
+
+\subsubsection{Distribution on Pose}
+In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
+Therefore pose uncertainty may come from two primary sources a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
+The effects of pose uncertainty on robotic grasping has been studied by ~\cite{}.
+
+The pose of an object $T$ is a member of the Lie Algebra $SO(3)$ in 3-dimensional space (something analogous holds for 2D).
+This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\xi = (\bw, \bt)$.
+One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
+Thus, to sample a pose matrix $T$ one can sample from a distribution on $\xi$ and compute the poes as:
+
+\todo{Jeff: Put equations here. Sorry my internet is too slow to download the paper i need right now}
+
+ \subsubsection{Distribution on Motion}
+ In practice a robot may not be able to execute a desired
+grasp plan $\Gamma$ exactly due to errors in trajectory following or
+registration to the object \cite{kehoe2012estimating}.
+To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$.
+In practice $\sigma^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
+
+ \subsubsection{Distribution on Friction Coefficient}
+As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation.
+The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table.
+However, because their could be material in between the objects surface and the robot gripper (i.e.
+dust, water, moisture).
+It is important to assume noise.
+Thus, we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.
+
+To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
+\ref{fig:graphical_model}.
+In the naive way sampling from the graphical model could be slow, however our goal is not to actually determine the probability of force closure but instead to determine the best grasp in a set $G$.
+Thus, our BMAB algorithms can efficiently sample from theses priors on the different types of uncertainty.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 6cm, height = 6cm]{figures/Slide8.jpg}
+\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
+Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.
+}
+\vspace*{-10pt}
+\label{fig:graphical_model}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
+\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+\vspace*{-10pt}
+\label{fig:line_of_action}
+\end{figure}
+
+\subsection{Problem Definition}
+
+We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
+We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.
+
+\vspace{-2ex}
+\begin{align}\label{eq:problem_def}
+\Gamma^* \in \underset{\Gamma \in G}{\mbox{argmax}} P(Q(\Gamma)>0)
+\end{align}
+
+\section{Multi-Armed Bandits for Grasp Selection}
+While a standard approach to solving the problem in Eq.
+\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
+In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
+Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
+The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
+
+We can now model the distribution on rewards as a Beta-Bernoulli process.
+Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
+The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
+
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
+The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Thus, we can write the expected probability of force closure as follows
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
+\end{align}
+
+Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
+To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
+Whats interesting in the context of a BMAB problem our complicated graphical model in Fig.
+\ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
+It is this intuition that helps explain the performance of the BMAB algorithm.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
+\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
+\vspace*{-10pt}
+\label{fig:beta_model}
+\end{figure}
 
@@
 
-\section{Preliminaries and Problem Definition}
-Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
-
-\subsection{Grasp Metric}
-Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts.
-The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object.
-Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
-
-The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
-Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-If the convex hull does encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
-Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero.
-Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.
-
-In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
-$P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
-Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.
-
-\subsection{Line of action}
-In an uncertain environment may not know the true $g$ exactly due to sensing imprecision.
-Thus we propose to work with the trajectory of the gripper when analyzing grasps.
-Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
-\ref{fig:line_of_action}.
-A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-
-\subsection{Types of Uncertainty}
-In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.
-The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.
-Fig.
-\ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work.
-We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.
-
-\subsubsection{Distribution on Shape}
-
-For shape we use a GPIS representation, which is explained in detail in Sec.
-\ref{sec:Appendix}.
-Essentially, a GPIS is a Gaussian distribution on a signed distance function that describes the workspace.
-The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
-For our application we set $x$ to discretized points along each line of action $\gamma_i$ and for each sample see where the sample is equal to zero.
-We will furthermore represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.
-
-\subsubsection{Distribution on Pose}
-In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
-Therefore pose uncertainty may come from two primary sources a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
-The effects of pose uncertainty on robotic grasping has been studied by ~\cite{}.
-
-The pose of an object $T$ is a member of the Lie Algebra $SO(3)$ in 3-dimensional space (something analogous holds for 2D).
-This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\xi = (\bw, \bt)$.
-One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
-Thus, to sample a pose matrix $T$ one can sample from a distribution on $\xi$ and compute the poes as:
-
-\todo{Jeff: Put equations here. Sorry my internet is too slow to download the paper i need right now}
-
- \subsubsection{Distribution on Motion}
- In practice a robot may not be able to execute a desired
-grasp plan $\Gamma$ exactly due to errors in trajectory following or
-registration to the object \cite{kehoe2012estimating}.
-To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$.
-In practice $\sigma^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
-
- \subsubsection{Distribution on Friction Coefficient}
-As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation.
-The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table.
-However, because their could be material in between the objects surface and the robot gripper (i.e.
-dust, water, moisture).
-It is important to assume noise.
-Thus, we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.
-
-To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
-\ref{fig:graphical_model}.
-In the naive way sampling from the graphical model could be slow, however our goal is not to actually determine the probability of force closure but instead to determine the best grasp in a set $G$.
-Thus, our BMAB algorithms can efficiently sample from theses priors on the different types of uncertainty.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 6cm, height = 6cm]{figures/Slide8.jpg}
-\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
-Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.
-}
-\vspace*{-10pt}
-\label{fig:graphical_model}
-\end{figure}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
-\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-\vspace*{-10pt}
-\label{fig:line_of_action}
-\end{figure}
-
-\subsection{Problem Definition}
-
-We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
-We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.
-
-\vspace{-2ex}
-\begin{align}\label{eq:problem_def}
-\Gamma^* \in \underset{\Gamma \in G}{\mbox{argmax}} P(Q(\Gamma)>0)
-\end{align}
-
-\section{Multi-Armed Bandits for Grasp Selection}
-While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
-In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
-Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
-The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
-
-We can now model the distribution on rewards as a Beta-Bernoulli process.
-Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
-The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
-
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the expected probability of force closure as follows
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
-\end{align}
-
-Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
-Whats interesting in the context of a BMAB problem our complicated graphical model in Fig.
-\ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
-It is this intuition that helps explain the performance of the BMAB algorithm.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
-\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
-\vspace*{-10pt}
-\label{fig:beta_model}
-\end{figure}
-
 \section{Distributions on Grasp Parameters}
@@
  &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
- &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)
+ &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
  \end{align*}
@@
 \subsection{Multi-Armed Bandit Experiments}
-\todo{Running experiments over break, going to fill this in as results come in}
 We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$.
@@
 \subsection{Sensitivity Analysis }
-We now will show how well the top two algorithms (Thompson and Gittens) perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
-The experiments are performed with the same setup as before but now we sweep the variance parameters across a range for each parameter.
-The results are shown below
+We now will show how well the one of the top algorithms Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
+The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter.
 
-\todo{Finish sensitivity analysis}
+For friction coefficient we started at $\sigma_{\mu} = 0.05$ and enlarged it to $\sigma_{\mu}  = 0.4$.
+As you can see in Fig.
+\ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergance in simple regret around 2500 samples or 2.5 samples per grasp for Thompson sampling.
+
+For rotational uncertainity in pose, we varied $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians.
+As you can see in Fig.
+\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\deg}$  causes the convergence in simple regret to not be reached until 5500 samples or an average of 5.5 samples per grasp.
+This can be explained because such a large variance causes a a drop in quality across all grasps and makes it harder to separate the outliers \cite{gabillon2012bes}.
+The quality of the best grasp along with the grasp for each round is shown in \ref{fig:rot_shapes}.
+
+For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $(3, 24)$ units (on a 40 x 40 unit workspace).
+As you can see in Fig.
+\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until around 5500 samples or an average of 5.5 samples per grasp.
+
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{fric}$ in the range of $(0.05, 0.4)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+The increase in noise has little effect on the convergence of Thompson Sampling in simple regret.}
+\vspace*{-10pt}
+\label{fig:fric_sens}
+\end{figure*}
 
@@
 \includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_rot.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
-Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
-UCB does poorly on simple regret which is expected \cite{best_arm}}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+As you can see the increase in noise effects performance, however the 5500 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
+\ref{fig:simple_regret}}
 \vspace*{-10pt}
-\label{fig:simple_regret}
+\label{fig:rot_sens}
+\end{figure*}
+
+\begin{figure*}%
+    \centering
+    \subfloat[lTop Grasps Shown for Shape 1]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_1.eps} }}%
+    \qquad
+    \subfloat[Top Grasps Shown for Shape 2]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_2.eps} }}%
+    \caption{Two shapes shown from the Brown Visual Lab Dataset,from Left to Right the variance on rotation $\sigma_{rot}$ is increased from $2^{\deg}$ to $13^{\deg}$.
+As you can see the overall variance increase effects the quality of the top grasp in the set of possible grasps.
+Furthermore for Shape 2, the grasp with low rotational variance is different than that for higher variance because the original grasp is more likely to touch the area of higher shape uncertainty when subjected to high variance in rotation.
+}%
+    \label{fig:rot_shapes}%
 \end{figure*}
@@
 \includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_trans.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
-Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
-UCB does poorly on simple regret which is expected \cite{best_arm}}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{trans}$ in the range of $(3,24)$ units from top to bottom on a 40 x 40 unit workspace.
+As you can see the increase in noise effects performance, however the 4200 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
+\ref{fig:simple_regret}}
 \vspace*{-10pt}
-\label{fig:simple_regret}
-\end{figure*}
-
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
-Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
-UCB does poorly on simple regret which is expected \cite{best_arm}}
-\vspace*{-10pt}
-\label{fig:simple_regret}
+\label{fig:trans_sens}
 \end{figure*}
@@
 Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.
-While we have seen the bandit method always converge to the correct value in our experiments, our method only has a statistical guarantee of doing so.
-A non-optimal grasp plan could be found, albeit with a low probability.
 
-Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{mahler2015opt}.
+The methods we showed (UCB, Thompson and Gittins) will always find the best grasp, but when do you terminate the algorithm is still an open question.
+Fixed confidence methods do exist that terminate when a certain confidence interval is reached \cite{maron1993hoeffding} \cite{mnih2008empirical}.
+However, a known problem is that if two grasps have very similar quality it could greatly increase the time for need to reach the statistical confidence interval \cite{audibert2010best}.
+We purpose using the approach of a user setting a fixed budget based  time constraints.
+How much time the user is willing to allow for grasp evaluation and repeatibility results on a set task can help guide this fixed budget.
+Our sensitivity analysis showed that even under extreme noise, our MAB approach is still much better than prior approach though, so we expect the fixed budget to be small.
 
-An additional problem is that we only have an expected center of mass and not a distribution on the center of mass.
-This might prove to be to expensive to compute, however recent work by Panahi et al.
-showed a way to bound the center of mass for convex parts.
-Extension of his work to implicit surfaces could be of possible interest \cite{panahi2014bounding}.
-When using the shape sampling approach on the GPIS instead of sampling along the grasp plan trajectory, the center of mass is easy to compute on a sampled shape, so this is a limitation of our sampling method.
+Another problem that was revealed in our analysis was that our current grasp metric, probability of force closure, is not dependent on the center of mass \cite{ferrari1992}.
+It only measure the probability that a grasp controller can resist any force provided it can exert an infinite force.
+One can assume that the grasp controller on a robot hand is powerful enough to apply the proper resistance, but that assumption might be invalid in some non-industrial robotic applications.
+A similar metric that is still from Beta-Bernoulli and takes center of mass into account, would be ideal for both accurate grasp quality prediction under uncertainty and the utilization of MAB algorithms.
+Recent work by Kim et al.
+developed a physics based simulator that could potentially achieve this goal \cite{kim2012physically}.
 
 \section{Conclusion}
-Assessing grasp quality under shape uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
-In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under shape uncertainty. 
+Assessing grasp quality under  uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
+In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coeffiecient and motion. 
 A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
- we found that the Successive Elimination multi-armed bandit approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
-A pre-requisite for applying a bandit approach is to formulate an efficient representation of how shape uncertainty affects grasp parameters and thus grasp quality.
-We modeled uncertainty with Gaussian process implicit surfaces (GPIS) and derived the distribution of grasp parameters when a nominal grasp is applied to the GPIS.
-As a result, we were able to more efficiently sample from a distribution of grasps executions rather than the shape; leading to a complexity improvement of $n^3$ in the resolution of the discretization $n$.
-We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it converges on average an order of magnitude faster than a uniform sampling approach in our experiments, and (3) sampling from the grasp contacts is 12x faster than sampling from shapes for a 64x64 grid.
+ we found that a MAB approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
+A pre-requisite for applying a bandit approach is to formulate a representation  of how uncertainty affects grasp parameters and thus grasp quality.
+We purpose treating this as a graphical model and use model the parameters as stochastic noise.
+Our choice of distributions though is not the focus of the paper and the MAB algorithm will still work independent of this.
+We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it converges on average an order of magnitude faster than a uniform sampling approach in our experiments.
 
@@
 \cite{miller2004graspit} to see if our method can handle uncertainty while working under the time constraints needed for most real time applications.
-We currently have only tested one bandit algorithm, successive elimination.
 While our results are promising, it remains to be seen how well it deals with the increased complexity of 3D models over 2D models and larger scale experiments.
@@
 
-\section{Appendix} \label{sec:Appendix}
+\appendix[Gaussian Process Implicit Surface for Representing Shape Uncertainty]
+ \label{sec:Appendix}
  In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$.

### 2014-12-30 paper.tex
Added pose equations and reference

@@
 
-The pose of an object $T$ is a member of the Lie Algebra $SO(3)$ in 3-dimensional space (something analogous holds for 2D).
-This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\xi = (\bw, \bt)$.
+The pose of an object $T$ is a member of the Lie Algebra $SE(3)$ in 3-dimensional space (something analogous holds for 2D).
+This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\mathbf{\xi} = (\bw, \bt)^T \in \mathbb{R}^6$.
 One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
-Thus, to sample a pose matrix $T$ one can sample from a distribution on $\xi$ and compute the poes as:
+Thus given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma \right)$ we define the pose random variable $T$ as
+
+\vspace{-2ex}
+\begin{align*}
+	T  &= \exp \left( \mathbf{\xi}^{\wedge} \right) \bar{T}
+\end{align*}
+
+\noindent where the $\wedge$ operator is defined as in \cite{barfoot2014Pose}.
 

### 2014-12-31 paper.tex
changed teasr phot and sensitivity analysis, also wrote over stuff

@@
 \title{\LARGE \bf
-Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty}
+Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v2] }
 
@@
 \begin{abstract}
-\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
+\textit{Abstract---}\todo{Not sure if we need to change the authors list or not}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
 Monte-Carlo sampling is computationally demanding, even for planar models.
@@
 
+\begin{figure}%
+    \centering
+     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%
+
+       \qquad
+
+     \subfloat{{\includegraphics[width=8cm]{matlab_figures/teaser.eps} }}%
+
+    \caption{\todo{New teaser photo, not sure if we should have some sort of real object or not}(Top Left) Image of a common household measuring cup.
+(Top Right) Image from a PR2 Primesense camera that reflects the uncertainty that can be induced in objects from transparency.
+(Bottom) Comparision of Multi-Armed Bandit Techniques (Bayes UCB, Thompson, Gittins) vs.
+Monte-Carlo sampling to determine the best grasp in a set of 1000 grasps.
+As you can see the bandit techniques converge in simple regret Eq.
+\ref{eq:simple_regret} a magnitude faster than the traditional approach of Monte-Carlo sampling to determine the highest quality grasp.
+}%
+    \label{fig:rot_shapes}%
+\end{figure}
+
 Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
@@
 Thus, we can adaptively concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=8.5cm,height=8cm]{figures/Slide02.jpg}
-\caption{\footnotesize
-Convergance in regret of the bandit sampling method (red), compared to the traditional Monte-Carlo method.
-The fast convergence of the bandit method is due to its ability to intelligently pick what grasp to sample next in a given set of proposed grasps on an object with shape uncertainty}
-\vspace*{-10pt}
-\label{fig:noisy data}
-\end{figure}
 
@@
 
-Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
+Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
 The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
@@
 Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
+
 To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps.
-The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is.
+The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
 Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
@@
 
-We chose to study our MAB sampling method for shape uncertainty using a Gaussian process implicit surface representation.
+We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape.
+For shape uncertainty we decided to use a Gaussian process implicit surface representation.
 Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
@@
 Mahler et al.
-used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}.
+used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
 However, this relied on an approximation to grasp quality without guarantees on accuracy..
@@
 Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
+We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.
 
@@
 Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-If the convex hull does encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
+If the convex hull does enclose the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
 Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero.
-Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.
+A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
 
 In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
-$P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed.
+$P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient) and averaging the qualities that are computed.
 Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.
@@
 We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.
+We note though that our choice of distributions does not effect the performance of the MAB algorithm and the reader should choose distribution that effect their needs.
 
@@
 Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}.
-To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Sec.
-\ref{sec:Appendix}.
+To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.
 A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace.
@@
 For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape.
-We will henceforth  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.
+For convenience we will  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.
 
@@
 
-\todo{Jeff: Put equations here. Sorry my internet is too slow to download the paper i need right now}
-
  \subsubsection{Distribution on Motion}
@@
 registration to the object \cite{kehoe2012estimating}.
-To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$.
-In practice $\sigma^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
+To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma_{mot}^2)$.
+In practice $\sigma_{mot}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
 
@@
 \ref{fig:graphical_model}.
-In the naive way sampling from the graphical model could be slow, however our goal is not to actually determine the probability of force closure but instead to determine the best grasp in a set $G$.
-Thus, our BMAB algorithms can efficiently sample from theses priors on the different types of uncertainty.
+To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
+Using Bayes rule and our graphical model we can rewrite this as
+
+ \vspace{-2ex}
+ \begin{align*}
+ &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
+ &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
+ \end{align*}
+
+ In Appendix \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
+Then in Appendix \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals.
+Lastly in Appendix \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.
 
@@
 Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.
-}
+\todo{Should we use words or symbols for the graphical model?}}
 \vspace*{-10pt}
@@
 \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
-In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
-Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
-Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
-The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
+The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
+Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-We can now model the distribution on rewards as a Beta-Bernoulli process.
-Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
-The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
-
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the expected probability of force closure as follows
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
-\end{align}
-
-Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}.
-Whats interesting in the context of a BMAB problem our complicated graphical model in Fig.
-\ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
-It is this intuition that helps explain the performance of the BMAB algorithm.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
-\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
-\vspace*{-10pt}
-\label{fig:beta_model}
-\end{figure}
-
-\section{Multi-Armed Bandit Model}
-The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
 The traditional setting of a multi-armed bandit model is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
@@
 Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
-%Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+
+In our setting, we have a probabilistic  representation and would like to evaluate many potential grasps on the samples drawn from the graphical model in Fig. \ref{fig:graphical_model}.
+Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
 
@@
 Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices.
-There are a number of algorithms for developing policies to balance exploration and exploitation.
-One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
-A class of algorithms that have stronger theoretical guarantees are from the Upper Confidence Bound (UCB) family.
-For each arm, UCB algorithms maintain the empirical expected reward and an upper confidence bound on the true expected reward using concentration inequalities for the assumed reward distribution.
+Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function \cite{lai1985asymptotically}.
+They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically many variants of UCB have thus been purposed.
+The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest confidence bound.
 
-%In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
-
-%In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages.
-In our case we only care about regret at the time our decision of the optimal grasp has been made, decoupling the exploration and exploitation stages. 
-%For example in medical testing for patients it is important to always administer the best treatment for the given patient.
-%However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
-Thus our goal is to identify the best arm in as few decisions as possible.
+In the case of grasping, one only cares about the regret when the grasp is actually executed.
+Hence, the exploration and exploitation stage are decoupled.
+Our goal is to identify the best arm in as few decisions as possible.
 Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
@@
 
-\label{sec:bandit_algorithm}
-\section{Bandit Algorithms For Best Arm Identification}\label{sec:algorithms}
+\section{Bandit Algorithms For Best Arm Identification}\label{sec:bandit_algorithm}
+
+While, UCB type algorithms adopt a frequenist perspective for distributions with bounded rewards in their empirical estimate of an upper bound.
+A growing interest though in the MAB community is in bandit algorithms that have Bayesian approach \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
+Here a prior distribution is placed on the distribution to be estimated and utilizing the prior enables a trade off between exploration and exploitation.
+Empirically Bayesian methods like Thompson sampling have been shown to outperform the UCB family \cite{chapelle2011empirical}.
+
+In the context of grasping, the reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
+This is a Bernoulli distribution which has a conjugate prior known as a Beta distribution.
+Hence, we can now model the distribution on rewards as a Beta-Bernoulli process.
+Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
+The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
+
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
+The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Thus, we can write the expected probability of force closure as follows
+
+\vspace{-2ex}
+\begin{align}\label{eq:shape_sampling}
+P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
+\end{align}
+
+Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
+Whats interesting in the context of a Bayesian BMAB problem our complicated graphical model in Fig.
+\ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
+It is this intuition that helps explain the performance of the BMAB algorithms.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
+\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
+\vspace*{-10pt}
+\label{fig:beta_model}
+\end{figure}
+
+%In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.
+
+%In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages.
+
 \subsection{Thompson Sampling}
@@
 
-\subsection{Upper Confidence Bound (UCB)}
-The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards.
-UCB estimates an empirical confidence bound for each arm based on the observations seen so far., then pulls the arm with the highest confidence bound.
-The confidence interval is derived from various concentration inequalities.
-The algorithm is in Algorithm 2 and assumes a Beta-Bernoulli Distribution, which matches our assumption of a 0-1 success measure for grasping.
+\subsection{Bayes-UCB}
+Bayes UCB, detailed in Fig.
+4, is a version of the UCB algorithm that uses a Bayesian posterior update to get a confidence bound instead of a the frequentist log(T ) term.
+To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon.
+Then the arm with the highest such quantile is chosen.
+For binary rewards the expected number of pulls of suboptimal arms is bounded and experimentally this algorithm has been shown to outperform UCB for binary rewards \cite{kaufmann2012bayesian}.
 
@@
  \KwResult{Best Arm, $g^*$ }
-\For{ t=1,2,...}{ 
- Pick arm: $ k = \underset{k\in{1,...,K}}{\mbox{argmax}} \mu_k + \sqrt{\frac{6\mbox{log}(t)}{T_k}}$\\
- Observe reward $X_{k_t,t} \in \lbrace 0,1 \rbrace$\\
- Update\\
- $T_k= T_k +1$\\
- $\mu_k = \frac{T_k-1}{T_k}*\mu_k + \frac{1}{T_k}*X_{k,t}$\\
+ For Beta(1,1) prior, Stopping Horizon $n$: \\
+\For{ t=1,2,...,n}{ 
+	\For{j = 1,...,K}{
+
+		Compute: $q_j(t) = Q\big(1-\frac{1}{t},p_j^{t-1}\big)$
+
 	}
- \caption{UCB for Beta-Bernoulli Process}
+Draw arm$ I_t = \mbox{argmax}_{j=1...K}q_j(t)$\\
+ Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
+ Update posterior:\\
+ Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
+ Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
+ Set $p_j^t \sim \mbox{Beta}(S_{I_t,t+1},F_{I_t,t+1} )$\\
+ }
+ \caption{Bayes-UCB for Beta-Bernoulli Process}
 \end{algorithm}
@@
 \subsection{The Gittins Index Method} 
+\todo{Let me know how clear this is, Gittins can be hard to describe in general}
 One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory.
@@
 
-\section{Distributions on Grasp Parameters}
-\label{sec:distgrasp}
-
- To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
-Using Bayes rule and our graphical model we can rewrite this as
-
- \vspace{-2ex}
- \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
- &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
- \end{align*}
-
- In section \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
-Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals.
-Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.
  .
-\subsection{Distribution on Surface Normals}\label{sec:normals} 
-Using Eq.
-\ref{eq:mean_gradient} and Eq.
-\ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively.
-Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$.
-We can now write
-
-One interesting effect of this technique is that we can now marginalize out the line of action model and visual what the surface normal distribution is along a given line of action.
-To our knowledge this is the first attempt to visual surface normals along a grasp plan.
-Marginalization can be performed as follows:
-
-\vspace{-2ex}
-\begin{equation}
-    p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt \label{eq:normal_dist}
-\end{equation}
-
-Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
-To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.
-In Fig.\ref{fig:GraspDist}, we visualize the distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
-
-\subsection{Expected Center of Mass}\label{sec:mass}
-
-We recall the quantity $P(sd(x) < 0) = \int_{-\infty}^{0} p(sd(x) =  s \ | \ \mu(x),\Sigma(x)) ds$ is equal to the probability that $x$ is interior to the surface under the current observations.
-We assume that the object has uniform mass density and then $P(sd(x) < 0)$ is the expected mass density at $x$.
-Then we can find the expected center of mass as:
-
-\label{eq:mass}
-\begin{equation}
-  \bar{z} 
-  =
-  \frac
-    {\int_{\mathcal{W}}x P(sd(x)<0) dx}
-    {\int_{\mathcal{W}}  P(sd(x)<0) dx}
-\end{equation}
-
-which can be approximated by sampling $\mathcal{W}$ in a grid and approximating the spatial integral by a sum.
-Since this operation involves the entire SDF, one would want to use a low resolution grid for computational efficiency.
-We show the computed density and calculated expected center of mass for a marker in Fig.
-\ref{fig:GPIS_MASS}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide06.jpg}
-\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
-Right: The distribution on the density of each point assuming uniform density}
-\vspace*{-10pt}
-\label{fig:GPIS_MASS}
-\end{figure}
-
 \section{Experiments}
-For the experiments we used the Brown Vision Lab 2D dataset, the same used in \cite{christopoulos2007handling}.
-We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads,$\sigma_{trans} = 3$.
-Our visualization technique follows the approach of \cite{mahler2015opt} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
-
-We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
-We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
-
 \subsection{Multi-Armed Bandit Experiments}
@@
 \includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simple_regret.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes - UCB, Thompson, Gittins).
 Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation.
-UCB does poorly on simple regret which is expected \cite{best_arm}}
+As you can see the BMAB methods converge almost a magnitude faster than random allocation.
+It is worth noting that Gittins outperform the other two algorithms, which is useful when choosing which one to implement }
 \vspace*{-10pt}
@@
 \includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
-\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Random, UCB, Thompson, Gittins).
+\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Random, Bayes - UCB, Thompson, Gittins).
 Graph is averaged over 100 shapes from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each shape.
 The best grasps are ranked 1 and worst are 1000.
-As you can see the Thompson and Gittins method have a tendency to pull grasps with high ranking, while UCB has a more conservative policy \cite{best_arm}}
+As you can see the MAB algorithm intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation.
+\cite{best_arm}}
 \vspace*{-10pt}
@@
 \subsection{Sensitivity Analysis }
-We now will show how well the one of the top algorithms Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
-The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter.
+We now will show how well the top two algorithms Thompson Sampling and the Gittens Index Method perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
+The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
+All experiments were averaged across 10 shapes with a set size $|G| = 1000$.
 
-For friction coefficient we started at $\sigma_{\mu} = 0.05$ and enlarged it to $\sigma_{\mu}  = 0.4$.
+For friction coefficient we varied the variance across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4$.
 As you can see in Fig.
-\ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergance in simple regret around 2500 samples or 2.5 samples per grasp for Thompson sampling.
+\ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergence in simple regret around less than 2000 evaluations.
 
-For rotational uncertainity in pose, we varied $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians.
+For rotational uncertainity in pose, we varied $\sigma_{rot}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
 As you can see in Fig.
@@
 
-For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $(3, 24)$ units (on a 40 x 40 unit workspace).
+For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
 As you can see in Fig.
-\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until around 5500 samples or an average of 5.5 samples per grasp.
+\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until around 5000 samples for the Gittens Method and  8200 evaluations for Thompson Sampling.
 
@@
 \centering
-\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{fric}$ in the range of $(0.05, 0.4)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
-The increase in noise has little effect on the convergence of Thompson Sampling in simple regret.}
+\includegraphics[width = 16.5cm, height = 10cm]{matlab_figures/sensitivity_fric.eps}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under coefficient of friction uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+The increase in noise has little effect on the convergence of the two algorithms in simple regret.}
 \vspace*{-10pt}
@@
 \centering
-\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_rot.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+\includegraphics[width = 16.5cm, height = 10cm]{matlab_figures/sensitivity_rot.eps}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under rotation uncertainty $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
 As you can see the increase in noise effects performance, however the 5500 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
@@
 \centering
-\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_trans.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{trans}$ in the range of $(3,24)$ units from top to bottom on a 40 x 40 unit workspace.
-As you can see the increase in noise effects performance, however the 4200 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
+\includegraphics[width = 16.5cm, height = 10cm]{matlab_figures/sensitivity_trans.eps}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units from top to bottom on a 40 x 40 unit workspace.
+As you can see the increase in noise effects performance, however the 5000 samples needed for Gittins to  converge at the the highest level of noise (which is a variance of over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
 \ref{fig:simple_regret}}
@@
 
+\subsection{Distribution on Surface Normals}\label{sec:normals} 
+Using Eq.
+\ref{eq:mean_gradient} and Eq.
+\ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively.
+Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$.
+We can now write
+
+One interesting effect of this technique is that we can now marginalize out the line of action model and visual what the surface normal distribution is along a given line of action.
+To our knowledge this is the first attempt to visual surface normals along a grasp plan.
+Marginalization can be performed as follows:
+
+\vspace{-2ex}
+\begin{equation}
+    p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt \label{eq:normal_dist}
+\end{equation}
+
+Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
+To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.
+In Fig.\ref{fig:GraspDist}, we visualize the distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
+
+\subsection{Expected Center of Mass}\label{sec:mass}
+
+We recall the quantity $P(sd(x) < 0) = \int_{-\infty}^{0} p(sd(x) =  s \ | \ \mu(x),\Sigma(x)) ds$ is equal to the probability that $x$ is interior to the surface under the current observations.
+We assume that the object has uniform mass density and then $P(sd(x) < 0)$ is the expected mass density at $x$.
+Then we can find the expected center of mass as:
+
+\label{eq:mass}
+\begin{equation}
+  \bar{z} 
+  =
+  \frac
+    {\int_{\mathcal{W}}x P(sd(x)<0) dx}
+    {\int_{\mathcal{W}}  P(sd(x)<0) dx}
+\end{equation}
+
+which can be approximated by sampling $\mathcal{W}$ in a grid and approximating the spatial integral by a sum.
+Since this operation involves the entire SDF, one would want to use a low resolution grid for computational efficiency.
+We show the computed density and calculated expected center of mass for a marker in Fig.
+\ref{fig:GPIS_MASS}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale = 0.3]{figures/Slide06.jpg}
+\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
+Right: The distribution on the density of each point assuming uniform density}
+\vspace*{-10pt}
+\label{fig:GPIS_MASS}
+\end{figure}
+
+\section{Experiments}
+For the experiments we used the Brown Vision Lab 2D dataset, the same used in \cite{christopoulos2007handling}.
+We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
+The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads,$\sigma_{trans} = 3$.
+Our visualization technique follows the approach of \cite{mahler2015opt} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
+
+We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
+We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
+
 \end{document}

### 2015-01-05 paper.tex
v3 after Ken's Feedback

@@
 \title{\LARGE \bf
-Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v2] }
+Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Budgeted Multi-Armed Bandit Models for  [v3 Jan 5, 2015 ] }
 
@@
 \begin{abstract}
-\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to ucertainities.
+\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to uncertainties.
 For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown.
-To handle all the uncertainites and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples.
-We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps.
+To handle all the uncertainties and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples.
+We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps, thus helping to alleviate the computational burden that is associated to incorporating uncertainty.
 \end{abstract}
@@
 
-Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
+Consider a robot processing orders in a warehouse , where it frequently encounter new consumer products and need to process them quickly.
 The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and material properties like friction coefficient or center of mass. 
-Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from partial visibility and object properties such as transparency, .
-Grasp planners that assume exact prior knowledge of object geometry or an exact measurement of pose may fail in this environment.
+Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from occlusions and object properties such as transparency or reflective surfaces .
 
@@
 
-Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
-Recent work motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty requires exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
-To select a grasp with high quality this evaluation must be performed for a large set of potential grasps, which can be very time-consuming.
-However, when evaluating a set of grasps we may be able to determine the difference of quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
-Thus, we can adaptively concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
+Grasp quality metrics have been developed to determine if a grasp will be successful or not prior to actually executing the grasp and how much force it needs to exert to resist an opposing force, however the ones that we consider evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
+Recent work \cite{kehoe2012estimating,mahler2015gp} motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty use Monte Carlo sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
 
-The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next grasp to evaluate and the grasps to discard from consideration.
-The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of the expected reward of such decisions is maximized.
+To select a grasp with high quality this evaluation is usually performed for a large set of perturbations in state, shape, and material properties, which can be very time-consuming.
+However, when evaluating a set of grasps we may be able to determine the difference of quality between proposed grasps with only a few samples and adaptively choose what grasp to evaluate next.
+We can concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
+
+The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next option to evaluate.
+The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of expected reward is maximized.
 Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model with a finite number of total decisions to be made before a predetermined `stopping time'.
+The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where at a given "stopping time" the agent must choose the arm that currently has the highest expected reward based on its observations.
 The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
 
-Our main contribution in this paper is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
-We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under shape uncertainty.
-We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the probability of success for many potential grasp plans.
-We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}, but our method applies to any model of uncertainty that can be sampled.
+Our main contribution is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
+We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under uncertainty in pose, shape, motion and friction coefficient.
+We choose the model of shape uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
+Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
+Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
+Our approach of treating grasp selection as a BMAB requires only the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.
 
-We also show how to estimate distributions on the contact points and surface normals and center of mass using a graphical model to represent uncertainty in motion, shape, pose and friction coefficient.
-Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach.
-These promising results suggest that our MAB approach could also provide  significant speed improvements using other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements.
-\todo{Revise above line, as we now have some experiments varying these quantities as well}
+We also show how to estimate distributions on the contact points and surface normals and center of mass using GPIS representation for shape uncertainty.
+Our experiments demonstrate that using the MAB sampling method improves the time to find the best grasp in a set of 1000 grasps by 5x over the baseline Monte-Carlo approach.
+\todo{Going to get a table with results}
 
@@
 
-Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+One method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
 Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
 
-To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps.
-The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
-Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
-MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.
+To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps.
+However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
+Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty when the robot is able to obtain new information via tactile sensor.
+MCMC provides a Bayesian framework for inference with a hidden state, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.
 
@@
 For shape uncertainty we decided to use a Gaussian process implicit surface representation.
-Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
-Hollinger et al. used GPIS as a model of uncertainty and performed active sensing on the hulls in underwater boats \cite{hollinger2013}.
+Our decision to use this uncertainty model is based on GPIS's ability to combine different modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
+Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
 Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
@@
 used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
-However, this relied on an approximation to grasp quality without guarantees on accuracy..
+However, this relied on an approximation to grasp quality without guarantees on accuracy.
 We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.
+This paper is a substantially revised and expanded version on \cite{laskey} and \cite{mahler2015gp}.
 
@@
 The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object.
-Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
+The Ferrari-Canny metric has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
 
-The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
-Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-If the convex hull does enclose the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
-Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero.
+Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
+The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
 A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
@@
 In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
-$P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient) and averaging the qualities that are computed.
-Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.
+$P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.
 
 \subsection{Line of action}
-In an uncertain environment may not know the true $g$ exactly due to sensing imprecision.
+In an uncertain environment, a grasp planner may not know the true grasp parameters or $g$ exactly due to sensing imprecision.
 Thus we propose to work with the trajectory of the gripper when analyzing grasps.
@@
 
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
+\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+\vspace*{-10pt}
+\label{fig:line_of_action}
+\end{figure}
+
 \subsection{Types of Uncertainty}
 In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.
-The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.
+The property of force closure is not affected by the center of mass because it  measures if a wrench can be resisted not how large the force is need to resist.
 Fig.
-\ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work.
-We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.
-We note though that our choice of distributions does not effect the performance of the MAB algorithm and the reader should choose distribution that effect their needs.
+\ref{fig:graphical_model} shows the probabilistic relationship of the types of uncertainty considered in this work.
+We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle the types of uncertainty.
+We note though that our choice of distributions does not effect the ability to use the MAB algorithms and that the reader should choose distribution that effect their needs.
 
@@
 Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}.
-To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.
+To model this uncertainty we use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.
 A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace.
 A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.
-The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
+Signed distance functions can be sampled from  $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
 For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape.
@@
 However, because their could be material in between the objects surface and the robot gripper (i.e.
-dust, water, moisture).
-It is important to assume noise.
-Thus, we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.
+dust, water, moisture), we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.
 
-To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
+To estimate $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
 \ref{fig:graphical_model}.
 To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
-Using Bayes rule and our graphical model we can rewrite this as
+Using Bayes rule  we can rewrite this as
 
@@
 
- In Appendix \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
-Then in Appendix \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals.
-Lastly in Appendix \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.
+ Appendix \ref{sec:Appendix}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
+Appendix \ref{sec:normals}, describes how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and presents a novel visualization technique for the distribution on surface normals.
+Appendix \ref{sec:mass}, describes a way to calculate the expected center of mass assuming a uniform mass distribution.
 
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
-\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-\vspace*{-10pt}
-\label{fig:line_of_action}
-\end{figure}
-
 \subsection{Problem Definition}
 
-We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
-We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.
+We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either uniformly randomly or with a heuristic as in \cite{mahler2015gp}.
+We are interested in determining Eq. \ref{eq:problem_def} with respect to the problaliltiy of achieving force closure or $P(Q(\Gamma) > 0)$. \todo{Need to figure out if we can use optimal or not}
 
@@
 In our setting, we have a probabilistic  representation and would like to evaluate many potential grasps on the samples drawn from the graphical model in Fig. \ref{fig:graphical_model}.
-Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
+Motivated by limited computational resources we  allocate sampling resources to efficiently find the best arm.
 Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
@@
 Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function \cite{lai1985asymptotically}.
-They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically many variants of UCB have thus been purposed.
-The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest confidence bound.
+They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically.
+Many variants of UCB have thus been proposed.
+The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
 
-In the case of grasping, one only cares about the regret when the grasp is actually executed.
+In the context of finding a high quality grasp, one only cares about the regret when the grasp is actually executed in real life.
+The agent shouldn't be penalized for exploring different grasps, but only for the grasp that they suggest at the termination of the algorithm.
 Hence, the exploration and exploitation stage are decoupled.
@@
 
+The speed of termination is affected by the hardness of the problem, which relates to the how close the other arms expected reward is to the expected reward top arm in the set \cite{audibert2010best}.
+In the grasping context this means that achieving a fixed confidence for two similar grasps would require exhaustive sampling from each distribution.
+
 \subsection{Fixed Budget}
-In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the best arm at that stopping time.
+
+In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the current best arm at that stopping time this can be thought of as an anytime algorithm.
 Audibert el al.
@@
 Here a prior distribution is placed on the distribution to be estimated and utilizing the prior enables a trade off between exploration and exploitation.
-Empirically Bayesian methods like Thompson sampling have been shown to outperform the UCB family \cite{chapelle2011empirical}.
+Theoretical results have shown that these methods are capable of achieving the lower bound described by Lai and Robbin \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}.
+Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}.
 
-In the context of grasping, the reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.
-This is a Bernoulli distribution which has a conjugate prior known as a Beta distribution.
-Hence, we can now model the distribution on rewards as a Beta-Bernoulli process.
-Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
+In the context of grasping, the reward from sampling from the grasp distribution is 1 if the sampled grasp is in force closure and 0 if the grasp is not in force closure.
+The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
+In the Bayesian setting one would treat $\theta$ as belonging to a distribution.
+A convenient and common choice for such a distribution is the Beta distribution.
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
+The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
+To update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
 The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
 
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
 The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
@@
 Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
-Whats interesting in the context of a Bayesian BMAB problem our complicated graphical model in Fig.
+Whats interesting in the context of a Bayesian BMAB problem our  graphical model in Fig.
 \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
-It is this intuition that helps explain the performance of the BMAB algorithms.
+Regardless of the distributions in Fig.
+\ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian} \cite{weber1992gittins}.
 
@@
 
-\subsection{Thompson Sampling}
-Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
-The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled, then sample from the prior distribution on all arms and pull the arm with the highest sample drawn.
-The full algorithm is shown in Algorithm 1.
-Empirically this method has been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}
+\subsection{Bayes-UCB}
+Bayes UCB, detailed in Algorithm 1, is a version of the UCB algorithm that uses a Bayesian posterior update to get a confidence bound instead of  the frequentist concentration inequality approach.
+To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon.
+TAt each time step the arm with the highest quantile is chosen and the Beta distribution is updated based on the observed reward.
+For binary rewards (i.e.
+Bernoulli distributions) the expected number of pulls of suboptimal arms is bounded and experimentally this algorithm has been shown to outperform UCB for binary rewards \cite{kaufmann2012bayesian}.
 
 \begin{algorithm}
- \KwResult{Best Arm, $g^*$ }
- For Beta(1,1) prior: \\
-\For{ t=1,2,...}{ 
- Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
- Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
- Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
- Update posterior:\\
- Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
- Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
-
- }
- \caption{Thompson Sampling for Beta-Bernoulli Process}
-\end{algorithm}
-
-\subsection{Bayes-UCB}
-Bayes UCB, detailed in Fig.
-4, is a version of the UCB algorithm that uses a Bayesian posterior update to get a confidence bound instead of a the frequentist log(T ) term.
-To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon.
-Then the arm with the highest such quantile is chosen.
-For binary rewards the expected number of pulls of suboptimal arms is bounded and experimentally this algorithm has been shown to outperform UCB for binary rewards \cite{kaufmann2012bayesian}.
-
-\begin{algorithm}
- \KwResult{Best Arm, $g^*$ }
+ \KwResult{Current Best Arm, $\Gamma^*$ }
  For Beta(1,1) prior, Stopping Horizon $n$: \\
@@
  Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
- Set $p_j^t \sim \mbox{Beta}(S_{I_t,t+1},F_{I_t,t+1} )$\\
+ Set $\theta_j^t \sim \mbox{Beta}(S_{I_t,t+1},F_{I_t,t+1} )$\\
  }
  \caption{Bayes-UCB for Beta-Bernoulli Process}
+\end{algorithm}
+
+\subsection{Thompson Sampling}
+Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
+We will describe it now in detail for the Beta-Bernoulli process.
+All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha=1$,$\beta =1$) to reflect a uniform prior on the $\theta$ of the Bernoulli distribution.
+Then for each arm draw $\theta_{j,t} \sim \mbox{Beta}(\alpha,\beta)$ and pull the arm with the highest $\theta_{j,t}$ drawn.
+The reward, $X_{i,t}$ is observed from that arm, $j$, and the corresponding Beta distribution is updated.
+This is repeated until a stopping time is reached.
+The full algorithm is shown in Algorithm 1.
+
+The randomness of Thompson sampling allows for it to quickly explore the more arms then Bayes-UCB, which makes conservative arm pulls based on confidence bounds.
+It is also less prone to local solutions because of its stochastic nature.
+Thus, for cases where exploration and exploitation are decoupled Thompson sampling can find a better arm faster.
+Thompson sampling has recently been shown to approach the Lai and Robbins bound \cite{agrawal2011analysis} and has  empirically been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}.
+Variants of it are even used commercially in products like Microsoft's adPredictor, which is used by Bing, the search engine, \cite{graepel2010web}.
+\begin{algorithm}
+ \KwResult{Current Best Arm, $\Gamma^*$ }
+ For Beta(1,1) prior: \\
+\For{ t=1,2,...}{ 
+ Draw $\theta_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
+ Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
+ Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
+ Update posterior:\\
+ Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
+ Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
+
+ }
+ \caption{Thompson Sampling for Beta-Bernoulli Process}
 \end{algorithm}
@@
 One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory.
-This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$.
+This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$ \cite{weber1992gittins}.
 
@@
 Hence the complexity of solving MAB using Markov Decision theory increases exponentially with the number of bandit processes.
-A key insight though was given by Gittins, who showed that instead of solving the $k$-dimensional MDP one can instead solve a $k$ 1-dimensional optimization problems: for each arm $i$, $i= 1,...,k$, and for each state of $x^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$.
+A key insight though was given by Gittins, who showed that instead of solving the $k$-dimensional MDP one can instead solve $k$ 1-dimensional optimization problems: for each arm $i$, $i= 1,...,k$, and for each state of $x^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$.
 
@@
 For Best Arm Identification you want your discount factor $\gamma$ to approach 1, since you should never stop pulling the best arm.
+Generally the computation of the Gittins indices is too expensive, however in the Beta-Bernoulli case it is actually possible \cite{kaufmann2012bayesian}.
 We computed the Gittins indices offline using the restart method proposed by Katehakis et al.
@@
 \begin{algorithm}
- \KwResult{Best Arm, $g^*$ }
+ \KwResult{Current Best Arm, $\Gamma^*$ }
  For Beta(1,1) prior, Table of Indices $v$, Discount Factor $\gamma$: \\
@@
 \section{Experiments}
+For the experiments we used the Brown Vision Lab 2D dataset, the same used in \cite{christopoulos2007handling}.
+We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
+The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads,$\sigma_{trans} = 3$.
+Our visualization technique follows the approach of \cite{mahler2015gp} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
+
+We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
+We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
+
 \subsection{Multi-Armed Bandit Experiments}
+\todo{add Bayes and Kehoe results}
 We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$.
@@
 In Fig.
-\ref{fig:simple_regret}, we plotted the simple regret averaged over 100 of the shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation).
+\ref{fig:simple_regret}, we plotted the simple regret averaged over 100 randomly drawn shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation).
 We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time.
@@
 In Fig.
-\ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus it is quickly able to ignore the low quality grasps.
+\ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus they are quickly able to ignore the low quality grasps.
 UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.
@@
 \includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simple_regret.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes - UCB, Thompson, Gittins).
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes -UCB, Thompson, Gittins).
 Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
@@
 \end{figure*}
+\begin{figure*}%
+    \centering
+    \subfloat{{\includegraphics[width=16.5cm]{matlab_figures/shapes_1.eps} }}%
+    \qquad
+    \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_2.eps} }}%
+       \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_3.eps} }}%
+          \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_4.eps} }}%
+             \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_5.eps} }}%
+
+    \caption{Five shapes shown from the Brown Visual Lab Dataset with induced shape uncertainity and visualized according to the method described in \cite{mahler2015gp}.
+The four methods (Monte-Carlo, Kehoe's, Thompson and Gittins) were all run until a stopping time of 9000 evaluations with a uniformly initialized grasp set of $|G|=1000$.
+The grasps and the quality each one found is shown above.
+The Gittins Index Method in all cases shown found the best grasp among the methods.
+}%
+    \label{fig:rot_shapes}%
+\end{figure*}
 
@@
 For friction coefficient we varied the variance across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4$.
-As you can see in Fig.
-\ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergence in simple regret around less than 2000 evaluations.
+As illustrated in Fig.
+\ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 2000 evaluations.
 
@@
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \centering
-\includegraphics[width = 16.5cm, height = 10cm]{matlab_figures/sensitivity_fric.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under coefficient of friction uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+\includegraphics[width = 8cm, height = 10cm]{matlab_figures/sensitivity_fric.eps}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
 The increase in noise has little effect on the convergence of the two algorithms in simple regret.}
@@
 \label{fig:fric_sens}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \centering
-\includegraphics[width = 16.5cm, height = 10cm]{matlab_figures/sensitivity_rot.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under rotation uncertainty $\sigma_{rot}$ in the range of $(0.03, 0.24)$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
-As you can see the increase in noise effects performance, however the 5500 samples needed for convergence at the the highest level of noise (which is over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
-\ref{fig:simple_regret}}
+\includegraphics[width = 8cm, height = 10cm]{matlab_figures/sensitivity_rot.eps}
+\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under coefficient of friction uncertainty $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+The increase in noise has little effect on the convergence of the two algorithms in simple regret.
+\todo{Going to rerun with more shapes to be sure about this}}
 \vspace*{-10pt}
 \label{fig:rot_sens}
-\end{figure*}
+\end{figure}
 
@@
     \subfloat[Top Grasps Shown for Shape 2]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_2.eps} }}%
-    \caption{Two shapes shown from the Brown Visual Lab Dataset,from Left to Right the variance on rotation $\sigma_{rot}$ is increased from $2^{\deg}$ to $13^{\deg}$.
+    \caption{Two shapes shown from the Brown Visual Lab Dataset,from Left to Right the variance on rotation $\sigma_{rot}$ is increased $0.03$, $0.12$ to $0.24$ radians.
 As you can see the overall variance increase effects the quality of the top grasp in the set of possible grasps.
 Furthermore for Shape 2, the grasp with low rotational variance is different than that for higher variance because the original grasp is more likely to touch the area of higher shape uncertainty when subjected to high variance in rotation.
-}%
+\todo{find better shapes in the brown dataset} }%
     \label{fig:rot_shapes}%
@@
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \centering
-\includegraphics[width = 16.5cm, height = 10cm]{matlab_figures/sensitivity_trans.eps}
+\includegraphics[width = 8cm, height = 10cm]{matlab_figures/sensitivity_trans.eps}
 \caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units from top to bottom on a 40 x 40 unit workspace.
@@
 \label{fig:trans_sens}
-\end{figure*}
+\end{figure}
 
@@
 
-The methods we showed (UCB, Thompson and Gittins) will always find the best grasp, but when do you terminate the algorithm is still an open question.
+The methods we showed (UCB, Thompson and Gittins) are guranteed to find the best grasp as the stopping time approaches infinity \cite{kaufmann2012bayesian,grawal2011analysis,weber1992gittins} but when do you terminate the algorithm is still an open question.
 Fixed confidence methods do exist that terminate when a certain confidence interval is reached \cite{maron1993hoeffding} \cite{mnih2008empirical}.
-However, a known problem is that if two grasps have very similar quality it could greatly increase the time for need to reach the statistical confidence interval \cite{audibert2010best}.
-We purpose using the approach of a user setting a fixed budget based  time constraints.
-How much time the user is willing to allow for grasp evaluation and repeatibility results on a set task can help guide this fixed budget.
-Our sensitivity analysis showed that even under extreme noise, our MAB approach is still much better than prior approach though, so we expect the fixed budget to be small.
+However, a known problem is that if two grasps have very similar quality it could greatly increase the time for needed to reach the statistical confidence interval \cite{audibert2010best}.
+We proposed treating the BMAB as anytime algorithm and have demonstrated empirically that the grasps at a given stopping time are better than prior methods of Monte-Carlo sampling or the approach of Kehoe et al.
+However, this has a hyper parameter that has to be user-defined, which is not ideal.
 
@@
 It only measure the probability that a grasp controller can resist any force provided it can exert an infinite force.
-One can assume that the grasp controller on a robot hand is powerful enough to apply the proper resistance, but that assumption might be invalid in some non-industrial robotic applications.
+One can assume that the grasp controller on a robot hand is powerful enough to apply the proper resistance, but that assumption might be invalid in some applications.
 A similar metric that is still from Beta-Bernoulli and takes center of mass into account, would be ideal for both accurate grasp quality prediction under uncertainty and the utilization of MAB algorithms.
@@
 We purpose treating this as a graphical model and use model the parameters as stochastic noise.
-Our choice of distributions though is not the focus of the paper and the MAB algorithm will still work independent of this.
-We evaluated this theoretical model on a dataset of common objects and confirmed that: (1) the bandits approach always converged to the best grasp in the candidate set, (2) it converges on average an order of magnitude faster than a uniform sampling approach in our experiments.
+Our choice of distributions though is not the focus of the paper.
+The MAB algorithm is applicable in any context of bounded reward distributions and all the theoretical results we mentioned will transfer to the Beta-Bernoulli case, or the estimation of probability of force closure.
+
+Our anytime BMAB approach is guaranteed to find the best grasp in a given proposal set in the limit of an infinite time and has empirically been shown to outperform the methods of prior work Monte-Carlo and the method purposed by Kehoe et al.
+\cite{kehoe2012estimating}.
 
@@
  \label{sec:Appendix}
- In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$.
+ In order to solve our problem definition, we must estimate $P(Q(\Gamma)>0)$ for a given grasp .
 We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.
@@
 
-\section{Experiments}
-For the experiments we used the Brown Vision Lab 2D dataset, the same used in \cite{christopoulos2007handling}.
-We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads,$\sigma_{trans} = 3$.
-Our visualization technique follows the approach of \cite{mahler2015opt} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
-
-We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
-We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
-
 \end{document}

### 2015-01-10 paper.tex
Revised sections 1-5. Still needs a number of revisions, particularly in section 5.

@@
 \newcommand{\suchthat}{\ \big|\ }
+\newcommand{\ba}{\mathbf{a}}
+\newcommand{\bb}{\mathbf{b}}
+\newcommand{\bc}{\mathbf{c}}
 \newcommand{\bd}{\mathbf{d}}
@@
 \newcommand{\mD}{\mathcal{D}}
+\newcommand{\mG}{\mathcal{G}}
 \newcommand{\mN}{\mathcal{N}}
@@
 We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
-This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
 \end{abstract}
@@
 For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown.
-To handle all the uncertainties and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples.
-We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps, thus helping to alleviate the computational burden that is associated to incorporating uncertainty.
+Monte-Carlo integration is often used to exhaustively evaluate the distribution on a grasp quality metric given these uncertainties.
+We apply algorithms from the sequential decision making literature to intelligently allocate samples for grasp quality evaluation to grasps likely to have higher quality given the previous samples, reducing plan time by roughly an order of magnitude.
 \end{abstract}
@@
 
-Consider a robot processing orders in a warehouse , where it frequently encounter new consumer products and need to process them quickly.
-The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and material properties like friction coefficient or center of mass. 
-Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from occlusions and object properties such as transparency or reflective surfaces .
+Consider a robot processing orders in a warehouse, where it frequently encounters new consumer products and must process them quickly.
+The robot may need to rapidly plan grasps for these objects without prior knowledge of object shape, pose and material properties like friction coefficient or center of mass. 
+Furthermore, the robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which may result from occlusions or surface properties such as transparency or reflective surfaces.
 
@@
     \centering
-     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%
+%     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%
 
-       \qquad
+%       \qquad
 
@@
 
-Grasp quality metrics have been developed to determine if a grasp will be successful or not prior to actually executing the grasp and how much force it needs to exert to resist an opposing force, however the ones that we consider evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
-Recent work \cite{kehoe2012estimating,mahler2015gp} motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty use Monte Carlo sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
+Analytic grasp quality metrics have been developed to determine the stability of a grasp when all the parameters of the object and robot manipulator are exactly known.
+A common measure of stabliity in the literature is force closure, the abliity to resist external forces and torques in arbitrary directions~\cite{}.
+Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exterted by the gripper to resist external perturbations~\cite{ferrari1992}.
+Recent works have explored computing the probability of a grasp achieving the force closure condition given uncertainty in parameters such as pose~\cite{christopoulos2007handling, weisz2012pose, kim2012physically} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
+Most methods for evaluating grasp quality in the presence of uncertainty use exhaustive Monte-Carlo sampling over the possible values of uncertain quantities~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards} which can be very time consuming..
+However, in many cases we may be able to rule out grasps with a low probability in only a few samples and allocate more sampling effort to grasps that are likely to be high quality.
 
-To select a grasp with high quality this evaluation is usually performed for a large set of perturbations in state, shape, and material properties, which can be very time-consuming.
-However, when evaluating a set of grasps we may be able to determine the difference of quality between proposed grasps with only a few samples and adaptively choose what grasp to evaluate next.
-We can concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.
-
-The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next option to evaluate.
-The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of expected reward is maximized.
+The multi-armed bandit (MAB) model for sequential decision making problems~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a formal way to reason about allocating sampling effort to grasps such that the grasp(s) with highest quality can be determined in as few samples as possible.
+In a standard MAB there are a set of possible options (or `arms' in the literature~\cite{barto1998reinforcement}) that each return a numeric reward from a stationary distribution.
+The goal in a MAB problem is to sequentially select ones of the possible options such that a measure of expected reward is maximized.
 Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where at a given "stopping time" the agent must choose the arm that currently has the highest expected reward based on its observations.
+The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where an agent has a fixed number of decisions to make before choosing the best option.
 The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
 
-Our main contribution is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
-We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under uncertainty in pose, shape, motion and friction coefficient.
-We choose the model of shape uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
+Our main contribution is formulating the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a budgeted multi-armed bandit problem.
+%\todo{Jeff: probably needs to be more specific here, unless we formally describe how to do it in an arbitrary model}.
+We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, robot motion, and friction coefficient.
+We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
 Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
 Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
-Our approach of treating grasp selection as a BMAB requires only the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.
-
-We also show how to estimate distributions on the contact points and surface normals and center of mass using GPIS representation for shape uncertainty.
-Our experiments demonstrate that using the MAB sampling method improves the time to find the best grasp in a set of 1000 grasps by 5x over the baseline Monte-Carlo approach.
-\todo{Going to get a table with results}
+\todo{Jeff: I personally think the above 3 statements may be too much detail for an intro}
+However, our approach of treating grasp selection as a BMAB only requires the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.
+We compare the performance of several popular algorithms for solving the BMAB problem: Bayes UCB, Thompson sampling, and Gittins indices.
+Our experiments demonstrate that solutions to the MAB problem can find the grasp with highest probabilty of force closure from a set of 1000 grasps 5x faster than the baseline Monte-Carlo approach and ...
+\todo{Going to get a table with results. Make comparison to Ben's method}
 
@@
 
-Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
+Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, and uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
 The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
+A common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves exhaustively sampling from distributions on random quantities and averaging the quality over these samples to approximate an expected value~\cite{caflisch1998monte}.
+Exhaustive sampling can be computationally expensive, which motivated the use of Cloud Computing to distribute sampling effort~\cite{kehoe2012toward}.
 
-One method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
-Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
-
-To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps.
+To further address the computational complexity, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps.
 However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
@@
 \section{Preliminaries and Problem Definition}
-Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
+We consider selecting a grasp on object from a given set of candidate grasps.
+We formulate this problem for grasping a planar object from above using parallel-jaw grippers.
+We assume that the object is rigid and remains stationary throughout the grasp.
+In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantiites are given.
+In this section, we formally define our grasping model, formalize our sources of uncertainty, introduce our metric for grasp quality, and finally define our grasp planning objective.
+
+%Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
 We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.
 
-\subsection{Grasp Metric}
-Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts.
-The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object.
-The Ferrari-Canny metric has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
+\subsection{Candidate Grasp Model}
+Our candidate grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
+Let $d$ denote the dimensionality of the shape representations we are using to select grasps and $m$ denote the number of jaws on the robotic gripper.
+In this work we formulate the MAB problem for 2-dimensional shapes using parallel-jaw grippers, so $d=2$ and $m=2$.
+In this work we also assume a finite width for each parallel jaw $w_j \in \mathbb{R}$.
 
-Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
-The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
-A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
+Similar to~\cite{christopoulos2007handling}, we parameterize a grasp using a {\it line of action} for each gripper jaw, where each line of action is a 1D curve $\gamma(t): [0,1] \rightarrow \mathbb{R}^d$ with endpoints $\gamma(0) = \ba$ and $\gamma(1) = \bb$.
+The line of action defines the trajectory that a jaw follows as the gripper closes around a shape.
+A {\it grasp plan} is the set of lines of action for each of the jaws, $\Gamma = \{\gamma_1(\cdot),...,\gamma_m(\cdot)\})$ \cite{}.
+For parallel-jaw grippers, $\Gamma = \{\gamma(t), \gamma(1 - t)\}$, since the two jaws approach the shape in opposite directions.
+Furthermore, in this work we consider only straight lines of action.
+The line of action model allows us to compute perturbations to the contact points and normals that occur due to shape uncertainty.
+%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changes in the location of contact with a surface, and the line of action allows us to compute these new locations.
 
-In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
-$P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.
+Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following the given plan, $\bc_1, ..., \bc_m \in \mathbb{R}^d$.
+We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, ..., \bn_m \in \mathbb{R}^d$ and the object center of mass as $\bz \in \mathbb{R}^d$.
+Together these form the set of grasp parameters $g = (\bc_1, ..., \bc_m, \bn_1, ... \bn_m, \bz)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object.
 
-\subsection{Line of action}
-In an uncertain environment, a grasp planner may not know the true grasp parameters or $g$ exactly due to sensing imprecision.
-Thus we propose to work with the trajectory of the gripper when analyzing grasps.
-Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
-\ref{fig:line_of_action}.
-A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
+%\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+%\vspace*{-10pt}
+%\label{fig:line_of_action}
+%\end{figure}
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
-\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
-\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-\vspace*{-10pt}
-\label{fig:line_of_action}
+\includegraphics[width = 8cm, height = 6.5cm]{figures/grasp_model.jpg}
+\caption{llustration of our grasping model for parallel jaw grippers on a GPIS model of a marker with shape uncertainty near the object center.
+Jaw placements are illustrated by a red direction arrow and line.
+The grasp plan consists of a line of action $\gamma(t)$ with endpoints $\ba$ and $\bb$.
+When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$ with outward pointing unit surface normals $\bn_1$ and $\bn_2$.
+Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.
+\todo{Jeff: Up to this point I don't believe the reader has seen a GPIS.
+We will replace the marker with a deterministic shape, but this figure gives a good idea of what we want to illustrate here.}}
+\vspace*{-4ex}
+\label{fig:grasp_model}
 \end{figure}
 
-\subsection{Types of Uncertainty}
-In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.
-The property of force closure is not affected by the center of mass because it  measures if a wrench can be resisted not how large the force is need to resist.
-Fig.
-\ref{fig:graphical_model} shows the probabilistic relationship of the types of uncertainty considered in this work.
-We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle the types of uncertainty.
-We note though that our choice of distributions does not effect the ability to use the MAB algorithms and that the reader should choose distribution that effect their needs.
+\subsection{Sources of Uncertainty}
+In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient.
+Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
+In this section we describe each source of uncertainty and our model of the uncertainty.
+We wish to emphasize that the models of uncertainty described in this work are not the only models that may be used with MAB algorithms and that the reader may choose parameters and distributions that best fit their needs.
 
-\subsubsection{Distribution on Shape}
+\subsubsection{Shape Uncertainty}
 
-Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}.
-To model this uncertainty we use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.
-A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace.
-A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.
-Signed distance functions can be sampled from  $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS.
-For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape.
-For convenience we will  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.
+Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015opt}.
+Following ~\cite{laskey2015bandits, mahler2015opt} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
+A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
+An SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
+A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
+\bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
+See Appendix A for detail on how to train a mean and covariance function for a GPIS.
+In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
+For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.
 
-\subsubsection{Distribution on Pose}
+\todo{Jeff: Describe alternative representation of shape uncertainty that we run experiments on. Likely this will be Ben's polygonal model}
+
+\subsubsection{Pose Uncertainty}
 In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
-Therefore pose uncertainty may come from two primary sources a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
-The effects of pose uncertainty on robotic grasping has been studied by ~\cite{}.
+Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
+In practice this uncertainty may be quantified based on the algorithms used to register these frames to one another.
+The effects of pose uncertainty on robotic grasping has been studied by~\cite{weisz2012pose, kim2012physically}. % cite Ben's RSS workshop paper here
 
-The pose of an object $T$ is a member of the Lie Algebra $SE(3)$ in 3-dimensional space (something analogous holds for 2D).
-This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\mathbf{\xi} = (\bw, \bt)^T \in \mathbb{R}^6$.
-One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
-Thus given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma \right)$ we define the pose random variable $T$ as
+In 2-dimensional space, the pose of an object $T$ is a member of the Lie Algebra $SE(2)$.
+This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:
+
+\vspace{-2ex}
+\begin{align*}
+	T &= \left[  \begin{array}{ccc}
+		\cos(\phi) & -\sin(\phi) & t_x \\
+		\sin(\phi) & \cos(\phi) & t_y \\
+		0 & 0 & 1
+		\end{array} \right] .
+\end{align*}
+
+One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
+Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$, and we define the pose random variable $T$ as
 
@@
 
-\noindent where the $\wedge$ operator is defined as in \cite{barfoot2014Pose}.
+\noindent where $\mathbf{\xi}^\wedge$ is the twist operator as defined in \cite{barfoot2014Pose}.
 
- \subsubsection{Distribution on Motion}
- In practice a robot may not be able to execute a desired
-grasp plan $\Gamma$ exactly due to errors in trajectory following or
-registration to the object \cite{kehoe2012estimating}.
-To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma_{mot}^2)$.
-In practice $\sigma_{mot}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
+ \subsubsection{Motion Uncertainty}
+In practice a robot may not be able to execute a desired grasp plan $\Gamma$ exactly due to slight errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
+In this work, we model motion uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
+Formally, let $\hat{\by} = \frac{1}{2} (\ba + \bb)$ denote the center of a planned line of action $\gamma(t)$ and $\hat{\psi}$ denote the angle that the planned line $\bb - \ba$ makes with the x-axis of the 2D coordinate system on our shape representation.
+Then the random center $\by \sim \mN(\hat{\by}, \Sigma_y)$ and the random angle $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
+For shorthand in the remainder of this paper we will refer to the random motion parameters as $\rho = \{\by, \psi \}$.
+In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
 
- \subsubsection{Distribution on Friction Coefficient}
+ \subsubsection{Friction Uncertainty}
 As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation.
-The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table.
-However, because their could be material in between the objects surface and the robot gripper (i.e.
-dust, water, moisture), we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.
+The expected friction coefficient $\hat{\mu}$ could be derived by means of object classification and a look up table~\cite{}.
+However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
+dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
+We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.
 
-To estimate $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig.
-\ref{fig:graphical_model}.
+\subsection{Grasp Quality}
+We measure the quality of grassp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
+Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.
+
+Formally, force closure is a binary-valued quanity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
+Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ...
+\bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
+If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{}.
+In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
+%\vspace{-2ex}
+\begin{align*}
+	P_F(\Gamma) &= P(F = 1 | \Gamma, \theta, \xi, \rho, \mu).
+\end{align*}
+\todo{Jeff: revise above symbols for clarity}
+
+To estimate $P_F(\Gamma)$, we generate  samples from each of the above distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.
+We first generate a sample of the object shape, pose, grasp plan, and friction coefficient using standard methods for sampling from a Gaussian distribution~\cite{}.
+Then we use these quantities to determine the grasp parameters $g$. 
+Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
+
 To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
@@
 Appendix \ref{sec:mass}, describes a way to calculate the expected center of mass assuming a uniform mass distribution.
+ \todo{Jeff: Not sure that the above two paragraphs are actually necessary}
+
+%Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
+The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
+A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
+%
+%In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
+$P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.
 
@@
 \centering
-\includegraphics[width = 6cm, height = 6cm]{figures/Slide8.jpg}
+\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
 \caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
@@
 
-\subsection{Problem Definition}
+\subsection{Objective}
 
-We assume we are given a 2-D workspace $\mathcal{W}$ with an unknown object represented as a trained GPIS model, described in Section \ref{sec:GP}, and set of possible grasp plans $G$ which are generated either uniformly randomly or with a heuristic as in \cite{mahler2015gp}.
-We are interested in determining Eq. \ref{eq:problem_def} with respect to the problaliltiy of achieving force closure or $P(Q(\Gamma) > 0)$. \todo{Need to figure out if we can use optimal or not}
+Given the sources of uncertainty and their relationships as described above, our goal is to find the grasp that maximizes the probability of force closure from a set of $P$ prespecified candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_P\}$:
 
 \vspace{-2ex}
-\begin{align}\label{eq:problem_def}
-\Gamma^* \in \underset{\Gamma \in G}{\mbox{argmax}} P(Q(\Gamma)>0)
+\begin{align}
+\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
 \end{align}
 
+One method to solve Equation ~\ref{eq:problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grap plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
+This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but is computationally expensive since it may require many samples for each of a large set of candidates to converge to the true value.
+More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward} and searching for locally optimal grasp plans over a continuous set using Sequential Convex Programming~\cite{mahler2015opt}.
+\todo{Jeff: differentiate from these}
+In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem.
+
 \section{Multi-Armed Bandits for Grasp Selection}
-While a standard approach to solving the problem in Eq.
-\ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample.
+%While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we
+We propose framing the problem in the multi-armed bandit (MAB) model and forming a policy for iteratively selecting which grasp to evaluate based on the probability of force closure estimate from the samples so far.
+The goal of the MAB approach is to allocate more sampling effort to grasps that appear to have higher quality based on the evaluation performed so far.
+
 The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
@@
 
-The traditional setting of a multi-armed bandit model is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
-A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
-Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
+In a traditional MAB problem, a gambler has $K$ independent slot machines, or ``arms'' to play.
+When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
+The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards are maximized over many pulls.
+If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
+However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest reward and exploring new arms to see if they give better rewards on average.
+Developing a policy that successfully trades between exploration and exploitation to maximize average reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
 
-In our setting, we have a probabilistic  representation and would like to evaluate many potential grasps on the samples drawn from the graphical model in Fig. \ref{fig:graphical_model}.
-Motivated by limited computational resources we  allocate sampling resources to efficiently find the best arm.
-Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
+Success in MAB problems is commonly measured in terms of {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
+Traditional bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
+Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
+They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
+The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
+Many variants of UCB have thus been proposed~\cite{}. \todo{Jeff: cite a lot of the literature here}
+Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{} and Thompson sampling for certain reward distributions~\cite{}.
 
-A common measure of success in MAB problems is {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
-Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices.
-Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function \cite{lai1985asymptotically}.
-They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically.
-Many variants of UCB have thus been proposed.
-The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
+Our grasp selection problem is similar in that we would like to find the grasp with the highest quality while conserving computational resources.
+%Motivated by limited computational resources we allocate sampling resources to efficiently find the best arm.
+However, in our problem one only cares about the suboptimality when the final grasp is selected for execution (called ``simple regret'' in the literature) rather than the cumulative regret as studied in the standard MAB problem.
+This is an instance of the Pure Exploration multi-armed bandit problem\cite{bubeck2009pure}, in which an agent attempts to recommend the best arm at the end of an exploration phase but is not penalized for making exploratory arm pulls during this phase.
+Hence, the exploration and exploitation stage are decoupled. 
+The end of the exploration phase, or ``stopping time,'' may not be known to the agent ahead of time.
+Therefore, solutions to the Pure Exploration problem can be thought of as anytime algorithms, meaning they must return a valid solution whenever they are stopped.
 
-In the context of finding a high quality grasp, one only cares about the regret when the grasp is actually executed in real life.
-The agent shouldn't be penalized for exploring different grasps, but only for the grasp that they suggest at the termination of the algorithm.
-Hence, the exploration and exploitation stage are decoupled.
-Our goal is to identify the best arm in as few decisions as possible.
-Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
-The simple regret at time $t$ is given by
-
+Formally, given arms $\lbrace \Gamma_1, ..., \Gamma_K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$, the goal in the Pure Exploration problem is to find the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
+The expected simple regret, or suboptimality, at time $t$ is given by
 \vspace{-2ex}
 \begin{align}\label{eq:simple_regret}
-r_t = \mu^* - \mu_t
+E[r_t] = \mu^* - \mu_t
 \end{align}
@@
 
-Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and the Budgeted Multi-Armed Bandit (BMAB) model, in which the algorithm must make a decision at the end of a fixed ``budget'' number of arm pulls.
+Several recent works have studied Pure Exploration algorithms that lead to upper bounds on the expected regret.
+Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
+This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
+In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
+For example, Bubeck et al. showed that the simple regret at any time for the UCB algorithm is bounded by a polynomial function of the number of timesteps~\cite{bubeck2009pure}.
 
-\subsection{Fixed Confidence}
-In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates.
+%Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and the Budgeted Multi-Armed Bandit (BMAB) model, in which the algorithm must make a decision at the end of a fixed ``budget'' number of arm pulls.
+
+%\subsection{Fixed Confidence}
+%In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates.
 Originally the problem was solved with `racing' algorithms, which used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were likely to be suboptimal and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
 These methods were later extended to return the top $m$ arms instead of only the best arm\cite{gabillon2012best}.
-
-The speed of termination is affected by the hardness of the problem, which relates to the how close the other arms expected reward is to the expected reward top arm in the set \cite{audibert2010best}.
+%
+%The speed of termination is affected by the hardness of the problem, which relates to the how close the other arms expected reward is to the expected reward top arm in the set \cite{audibert2010best}.
 In the grasping context this means that achieving a fixed confidence for two similar grasps would require exhaustive sampling from each distribution.
-
-\subsection{Fixed Budget}
-
-In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the current best arm at that stopping time this can be thought of as an anytime algorithm.
-Audibert el al.
-demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
-This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
-In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
+%
+%\subsection{Fixed Budget}
+%
+%In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the current best arm at that stopping time this can be thought of as an anytime algorithm.
+%Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
+%This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
+%In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
 For example in \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.
 
-In this work, we consider a setting in which a robot has a fixed computational time limit to select a grasp and thus the fixed budget setting is more appropriate.
-The time limit can be chosen via repeatibility experiments on a desire task.
-In Section \ref{sec:bandit_algorithm}, we will discuss some of the specific budgeted multi-armed bandit algorithms that are used in practice.
+In this work, we frame the grasp selection problem of \secref{objective} as a Pure Exploration multi-armed bandit problem.
+Each arm corresponds to a different grasp plan and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition.
+Since force closure is a binary value, we can think of each grasp plan $\Gamma_i$ as having a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
+Thus, the expected value of the force closure condition is equal to $P_F(\Gamma_i)$, and algorithms that seek to minimize the expected simple regret will also minimize the suboptimiality of the grasp plan chosen.
 
-\section{Bandit Algorithms For Best Arm Identification}\label{sec:bandit_algorithm}
+In Section \ref{sec:bandit_algorithm}, we will discuss some of the most popular algorithms for solving the multi-armed bandit problem in detail.
 
-While, UCB type algorithms adopt a frequenist perspective for distributions with bounded rewards in their empirical estimate of an upper bound.
-A growing interest though in the MAB community is in bandit algorithms that have Bayesian approach \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
-Here a prior distribution is placed on the distribution to be estimated and utilizing the prior enables a trade off between exploration and exploitation.
+\section{Bandit Algorithms}\label{sec:bandit_algorithm}
+
+\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now}.
+The algorithms discussed in Section ~\secref{} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
+However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
+In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.
+The belief distribution enables a trade off between exploration and exploitation by naturally increasing confidence around the true reward distribution as more rewards are observed for an arms.
 Theoretical results have shown that these methods are capable of achieving the lower bound described by Lai and Robbin \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}.
 Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
+See \cite{} for a review of bayesian methods in multi-armed bandit problems.
 
-In the context of grasping, the reward from sampling from the grasp distribution is 1 if the sampled grasp is in force closure and 0 if the grasp is not in force closure.
-The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
-In the Bayesian setting one would treat $\theta$ as belonging to a distribution.
-A convenient and common choice for such a distribution is the Beta distribution.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
+In the context of grasping, the reward for achieving force close on a sample from the uncertain parameters is a Bernoulli random variable with probabilty of success $\theta$.
+%The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
+In the Bayesian setting we treat $\theta$ as belonging to a distribution.
+A common choice for such a distribution is the Beta distribution, which is the conjugate prior of the Bernoulli distribution.
+One benefit of a conjugate prior is that the posterior update of the belief distribution is of the same form as the original prior, simplifying sampling and analysis.
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where $\alpha >0$ and $\beta >0$.
 The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
-To update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$.
-The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.
+To update the prior Beta distribution one adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$
+Often the prior $\alpha =1 $ and $\beta =1$ is used before any rewards are observed, which leads to a uniform distribution on $\theta$.
 
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$.
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
 The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
@@
 \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
+\todo{Jeff: I see what you're trying to say here, but this is somewhat misleading. Alpha and beta constitue estimates of the probability of force closure but do not themselves determine grasp quality}
 Regardless of the distributions in Fig.
-\ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian} \cite{weber1992gittins}.
+\ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}
+\cite{weber1992gittins}. 
+\todo{Jeff: This is a strong statement but is pretty vague. What are these guarantees?}
 

### 2015-01-12 paper.tex
revised version and added better results

@@
 The robot may need to rapidly plan grasps for these objects without prior knowledge of object shape, pose and material properties like friction coefficient or center of mass. 
-Furthermore, the robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which may result from occlusions or surface properties such as transparency or reflective surfaces.
+Furthermore, the robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions or surface properties such as transparency or reflective surfaces.
 
@@
 Analytic grasp quality metrics have been developed to determine the stability of a grasp when all the parameters of the object and robot manipulator are exactly known.
-A common measure of stabliity in the literature is force closure, the abliity to resist external forces and torques in arbitrary directions~\cite{}.
-Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exterted by the gripper to resist external perturbations~\cite{ferrari1992}.
+One common measure of stability is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{}.
+Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
 Recent works have explored computing the probability of a grasp achieving the force closure condition given uncertainty in parameters such as pose~\cite{christopoulos2007handling, weisz2012pose, kim2012physically} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-Most methods for evaluating grasp quality in the presence of uncertainty use exhaustive Monte-Carlo sampling over the possible values of uncertain quantities~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards} which can be very time consuming..
-However, in many cases we may be able to rule out grasps with a low probability in only a few samples and allocate more sampling effort to grasps that are likely to be high quality.
+Many methods for evaluating grasp quality in the presence of uncertainty use exhaustive Monte-Carlo sampling over the possible values of uncertain quantities~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards} which can be very time consuming.
+We are interested in ruling out grasps with a low probability in only a few samples and allocate more sampling effort to grasps that are likely to be high quality.
 
@@
 \todo{Jeff: I personally think the above 3 statements may be too much detail for an intro}
-However, our approach of treating grasp selection as a BMAB only requires the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.
+Our approach of using BMAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
 We compare the performance of several popular algorithms for solving the BMAB problem: Bayes UCB, Thompson sampling, and Gittins indices. 
-Our experiments demonstrate that solutions to the MAB problem can find the grasp with highest probabilty of force closure from a set of 1000 grasps 5x faster than the baseline Monte-Carlo approach and ...
-\todo{Going to get a table with results. Make comparison to Ben's method}
+\todo{Going to fill bottom paragraph in later}
+Initial results suggest a promising avenue with a Xx improvement over  the traditional Monte-Carlo integration and Xx improvement in the experiments that we tried.
 
@@
 In this section we describe each source of uncertainty and our model of the uncertainty.
-We wish to emphasize that the models of uncertainty described in this work are not the only models that may be used with MAB algorithms and that the reader may choose parameters and distributions that best fit their needs.
+We wish to emphasize that the models of uncertainty described in this work are not the only models that may be used with MAB algorithms and that the reader may choose parameters and distributions that best fit their needs, however performance is subject to vary on empirical results.
 
@@
 
-Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015opt}.
-Following ~\cite{laskey2015bandits, mahler2015opt} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
+Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
+Following ~\cite{laskey2015bandits, mahler2015gp} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
 A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
-An SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
+A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
 A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
@@
  \subsubsection{Friction Uncertainty}
-As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation.
+As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
 The expected friction coefficient $\hat{\mu}$ could be derived by means of object classification and a look up table~\cite{}.
@@
 
-\subsection{Grasp Quality}
+\subsection{Grasp Quality}\label{sec:grasp_sample}
 We measure the quality of grassp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
@@
 
-Formally, force closure is a binary-valued quanity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
+Formally, force closure is a binary-valued quantity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
 Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ...
 \bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
-If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{}.
+If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{li1988task}.
 In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
@@
 
-To estimate $P_F(\Gamma)$, we generate  samples from each of the above distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.
-We first generate a sample of the object shape, pose, grasp plan, and friction coefficient using standard methods for sampling from a Gaussian distribution~\cite{}.
-Then we use these quantities to determine the grasp parameters $g$. 
-Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
-
-To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
+To estimate $P_F(\Gamma)$, we generate  samples from each of the above distributions in sequence using the relationships defined by the graphical model in Fig.
+\ref{fig:graphical_model}.To sample from $p_F(\Gamma)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
 Using Bayes rule  we can rewrite this as
@@
 Appendix \ref{sec:mass}, describes a way to calculate the expected center of mass assuming a uniform mass distribution.
- \todo{Jeff: Not sure that the above two paragraphs are actually necessary}
+Then we use these quantities to determine the grasp parameters $g$.
+Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
 
@@
 The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
-Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-
 In a traditional MAB problem, a gambler has $K$ independent slot machines, or ``arms'' to play.
-When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
-The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards are maximized over many pulls.
+When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution, $P_k, k = 1, ..., K$, that is unknown to the gambler.
+The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards is maximized over many pulls.
 If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
@@
 %Motivated by limited computational resources we allocate sampling resources to efficiently find the best arm.
-However, in our problem one only cares about the suboptimality when the final grasp is selected for execution (called ``simple regret'' in the literature) rather than the cumulative regret as studied in the standard MAB problem.
+However, in our problem one only usually cares about the quality when the final grasp is selected for execution ( the difference between the expected quality of the optimal arm and the arm selected is known as ``simple regret'' in the literature) rather than the cumulative regret as studied in the standard MAB problem.
 This is an instance of the Pure Exploration multi-armed bandit problem\cite{bubeck2009pure}, in which an agent attempts to recommend the best arm at the end of an exploration phase but is not penalized for making exploratory arm pulls during this phase.
@@
 
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
+Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $p(\theta)$, the distribution on pose $p(\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $p(\mu)$.
 The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
@@
 \begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
+P_F(\Gamma) = \frac{\alpha}{\alpha + \beta}
 \end{align}
 
-Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$.
 Whats interesting in the context of a Bayesian BMAB problem our graphical model in Fig.
 \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
-\todo{Jeff: I see what you're trying to say here, but this is somewhat misleading. Alpha and beta constitue estimates of the probability of force closure but do not themselves determine grasp quality}
 Regardless of the distributions in Fig.
 \ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}
-\cite{weber1992gittins}. 
-\todo{Jeff: This is a strong statement but is pretty vague. What are these guarantees?}
+\cite{weber1992gittins}, which we will now discuss for each of the three proposed algorithms in detail. 
+\todo{Michael: The above statement is true and I want to convey this message, however it might take some work to convey}
 
@@
 \section{Experiments}
-For the experiments we used the Brown Vision Lab 2D dataset, the same used in \cite{christopoulos2007handling}.
+For the experiments we used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.
 We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
@@
 
-We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
+We did experiments for the case of two hard contacts in 2-D.
 We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
@@
 For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$.
+We initialize all algorithms by sampling each grasp 1 time.
+We draw samples from our graphical model using the technique described in Sec.
+\ref{sec:grasp_sample}.
 In Fig.
-\ref{fig:simple_regret}, we plotted the simple regret averaged over 100 randomly drawn shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation).
-We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time.
-We draw samples from our calculated distributions $p(g)$.
-Interestingly, Gittins and Thompson converge much faster than random and UCB.
+\ref{fig:simple_regret}, we plotted the simple regret averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Bayes-UCB, Thompson, Gittins, Kehoe et al.
+\cite{kehoe2012toward} and Monte-Carlo Integration).
 In Fig.
-\ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus they are quickly able to ignore the low quality grasps.
-UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.
+\ref{fig:grasp_quality}, we plot the current grasp quality the algorithm selects vs.
+samples drawn.
+We then show the grasps selected for five shapes at a stopping time of $T = 9000$ for all the methods listed in Fig.
+\ref{fig:shape_samples}.
+
+  Interestingly in Fig \ref{fig:grasp_quality}, Gittins and Thompson suggest on average higher quality grasps with  than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
+In Fig.
+\ref{fig:pulls_per_grasp} we plot samples per grasp quality, Gittins and Thompson appear to allocate significantly more grasp samples to grasps of high quality, thus they are quickly able to ignore the low quality grasps.
+Kehoe et al.
+and Monte-Carlo integration take a more evenly distributed approach to sample allocation, which could explain the performance difference in Fig.
+\ref{fig:simple_regret} and Fig.
+\ref{fig:grasp_quality}.
 
@@
 \centering
-\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simple_regret.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes -UCB, Thompson, Gittins).
+\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simp_regret.eps}
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes -UCB, Thompson and Gittins).
 Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
@@
 \centering
+\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pfc.eps}
+\caption{ \footnotesize Comparison of the current average probability of force closure vs.
+the number of samples pulled.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
+We also demonstrate what the average probability of force closure for the approximate optimal policy.
+Emperically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
+\vspace*{-10pt}
+\label{fig:grasp_quality}
+\end{figure*}
+
+\begin{figure*}[ht!]
+\centering
 \includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
@@
 As you can see the MAB algorithm intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation.
-\cite{best_arm}}
+}
+
 \vspace*{-10pt}
@@
 \end{figure*}
+
 \begin{figure*}%
     \centering
-    \subfloat{{\includegraphics[width=16.5cm]{matlab_figures/shapes_1.eps} }}%
+    \subfloat{{\includegraphics[width=16.5cm]{matlab_figures/shape_1.eps} }}%
     \qquad
@@
 The four methods (Monte-Carlo, Kehoe's, Thompson and Gittins) were all run until a stopping time of 9000 evaluations with a uniformly initialized grasp set of $|G|=1000$.
+We also showed the estimated best grasp in the set.
 The grasps and the quality each one found is shown above.
-The Gittins Index Method in all cases shown found the best grasp among the methods.
+In the four out of five cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $9000$, however at the last shape there is a difference of $2\%$ grasp quality.
 }%
-    \label{fig:rot_shapes}%
+    \label{fig:shape_samples}%
 \end{figure*}
+
+\todo{Michael: Need to discuss how to implement worst case scenario, adversial applies changing distributions online (which would not model the problem).}
 
@@
 The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
-All experiments were averaged across 10 shapes with a set size $|G| = 1000$.
+All experiments were averaged across 10 shapes randomly selected with from the Brown dataset with a set size $|G| = 1000$.
 
-For friction coefficient we varied the variance across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4$.
+For friction coefficient we varied the variance across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
 As illustrated in Fig.
@@
 
-For rotational uncertainity in pose, we varied $\sigma_{rot}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
-As you can see in Fig.
+For rotational uncertainty in pose, we varied $\sigma_{rot}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
+As illustrated in Fig.
 \ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\deg}$  causes the convergence in simple regret to not be reached until 5500 samples or an average of 5.5 samples per grasp.
@@
 \ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until around 5000 samples for the Gittens Method and  8200 evaluations for Thompson Sampling.
+
+\subsection{Worst Case Scenario}
+\todo{running experiments today on this}
 
@@
 
-The methods we showed (UCB, Thompson and Gittins) are guranteed to find the best grasp as the stopping time approaches infinity \cite{kaufmann2012bayesian,grawal2011analysis,weber1992gittins} but when do you terminate the algorithm is still an open question.
+Of the BMAB algorithms we showed, Thompson Sampling is guaranteed to find the best grasp as the stopping time approaches infinity \cite{agrawal2011analysis} but when do you terminate the algorithm is still an open question.
 Fixed confidence methods do exist that terminate when a certain confidence interval is reached \cite{maron1993hoeffding} \cite{mnih2008empirical}.
 However, a known problem is that if two grasps have very similar quality it could greatly increase the time for needed to reach the statistical confidence interval \cite{audibert2010best}.
-We proposed treating the BMAB as anytime algorithm and have demonstrated empirically that the grasps at a given stopping time are better than prior methods of Monte-Carlo sampling or the approach of Kehoe et al.
-However, this has a hyper parameter that has to be user-defined, which is not ideal.
+We proposed treating the BMAB as anytime algorithm and initial results in Fig.
+\ref{fig:grasp_quality} suggest that on average grasps at a given stopping time are better than prior methods of Monte-Carlo sampling or the approach of Kehoe et al.
+However, as shown in \todo{worst case results here} there can exists pathological cases that can change this.
+Fortunately, though these cases occur with a small probability, however it is important for a practitioner to be aware of them.
 

### 2015-01-17 paper.tex
Wording changes to sections 4 and 5

--- 2015-01-10 paper.tex
@@
 \section{Multi-Armed Bandits for Grasp Selection}
+\label{sec:MAB}
 %While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we
@@
 
+\subsection{Standard MAB Model}
 The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
@@
 
+\subsection{Pure Exploration MAB Models}
 Our grasp selection problem is similar in that we would like to find the grasp with the highest quality while conserving computational resources.
@@
 The end of the exploration phase, or ``stopping time,'' may not be known to the agent ahead of time.
-Therefore, solutions to the Pure Exploration problem can be thought of as anytime algorithms, meaning they must return a valid solution whenever they are stopped.
+Therefore, unless otherwise noted, solutions to the Pure Exploration problem are anytime algorithms; they must return a valid solution whenever they are stopped.
 
@@
 The expected simple regret, or suboptimality, at time $t$ is given by
-\vspace{-2ex}
+%\vspace{-2ex}
 \begin{align}\label{eq:simple_regret}
@@
 Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
-This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
+This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem and the number of allocated time steps \cite{audibert2010best}, but requires knowledge of the stopping time.
 In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
 For example, Bubeck et al. showed that the simple regret at any time for the UCB algorithm is bounded by a polynomial function of the number of timesteps~\cite{bubeck2009pure}.
+Several works have showed the relationship between number of timesteps and simple regret for Probably Approximately Correct (PAC) bandit algorithms~\cite{even2006action, mannor2004sample}.
+More recently, Bachman and Precup showed that algorithms based on Bayesian posterior sampling outperformed UCB and PAC algorithms in terms of minimizing simple regret~\cite{bachman2013greedy}.
+%Even-dar et al. showed that for Probably Approximately Correct (PAC) algorithms, the number of pulls needed to
 
@@
 
+\subsection{Grasp Planning as Pure Exploration}
 In this work, we frame the grasp selection problem of \secref{objective} as a Pure Exploration multi-armed bandit problem.
@@
 Since force closure is a binary value, we can think of each grasp plan $\Gamma_i$ as having a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
-Thus, the expected value of the force closure condition is equal to $P_F(\Gamma_i)$, and algorithms that seek to minimize the expected simple regret will also minimize the suboptimiality of the grasp plan chosen.
+Thus, the expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E[F | \Gamma_i, \theta, \xi, \rho, \mu] = P_F(\Gamma_i)$.
+Then minimizing the expected simple regret is equivalent to maximizing $P_F$ over the set of candidate grasp plans:
+
+\vspace{-2ex}
+\begin{align*}
+	\underset{\Gamma_i \in \mG}{\text{argmin }}\mu^{*} - \mu_{i} &= \underset{\Gamma_i \in \mG}{\text{argmax }}\mu_{i} \\
+	&=  \underset{\Gamma_i \in \mG}{\text{argmax }} P_F(\Gamma_i) \\
+	&= \Gamma^{*}
+\end{align*}
 
@@
 
-\section{Bandit Algorithms}\label{sec:bandit_algorithm}
+\section{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}
 
-\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now}.
-The algorithms discussed in Section ~\secref{} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
-However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
-In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.
-The belief distribution enables a trade off between exploration and exploitation by naturally increasing confidence around the true reward distribution as more rewards are observed for an arms.
-Theoretical results have shown that these methods are capable of achieving the lower bound described by Lai and Robbin \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}.
-Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
-See \cite{} for a review of bayesian methods in multi-armed bandit problems.
+\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now. I almost feel like Bayesian methods should come sooner}.
+Most of the algorithms discussed in Section~\ref{sec:MAB} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
+In this work, we are particularly interested in Bayesian algorithms that use previous samples to form a belief distribution on the likelihood of achieving force closure \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
+%However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
+%In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.
 
-In the context of grasping, the reward for achieving force close on a sample from the uncertain parameters is a Bernoulli random variable with probabilty of success $\theta$.
-%The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
-In the Bayesian setting we treat $\theta$ as belonging to a distribution.
-A common choice for such a distribution is the Beta distribution, which is the conjugate prior of the Bernoulli distribution.
-One benefit of a conjugate prior is that the posterior update of the belief distribution is of the same form as the original prior, simplifying sampling and analysis.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where $\alpha >0$ and $\beta >0$.
-The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
-To update the prior Beta distribution one adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$
-Often the prior $\alpha =1 $ and $\beta =1$ is used before any rewards are observed, which leads to a uniform distribution on $\theta$.
+Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
+The belief distribution enables a trade off between exploration and exploitation by increasing confidence around the true reward distribution as more rewards are observed for an arms.
+In the case of using force closure $F$ to measure quality, $P_F$ for each candidate grasp is a Bernoulli random variable and the Bayesian conjugate prior is a Beta distribution. 
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
+Typically the uniform prior distribution on probability of force closure for each grasp $i$ at time $t = 0$, $\alpha_{i, 0} =1 $ and $\beta_{i, 0} = 1$, would be used used to initialize the algorithm~\cite{}.
+Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving the lower bound described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
+%Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
+%See \cite{} for a review of bayesian methods in multi-armed bandit problems.
 
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the expected probability of force closure as follows
+%In the context of grasping, the reward for achieving force close on a sample from the uncertain parameters is a Bernoulli random variable with probabilty of success $\theta$.
+%%The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
+%In the Bayesian setting we treat $\theta$ as belonging to a distribution.
+%A common choice for such a distribution is the Beta distribution, which is the conjugate prior of the Bernoulli distribution.
+%One benefit of a conjugate prior is that the posterior update of the belief distribution is of the same form as the original prior, simplifying sampling and analysis.
+%Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where $\alpha >0$ and $\beta >0$.
+%The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
+%To update the prior Beta distribution one adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$
+%Often the prior $\alpha =1 $ and $\beta =1$ is used before any rewards are observed, which leads to a uniform distribution on $\theta$.
+
+One benefit of the Beta prior on Bernoulli reward distributions is the elegant updates to the belief distribution after observing rewards from arm pulls.
+Let $n_i$ denote the number of times grasp plan $\Gamma_i$ has been sampled.
+Then after observing $S_i$ force closure conditions for grasp $\Gamma_i$, the posterior of the Beta can be computed as $\alpha_{i, n_i} = \alpha_{i, 0} + S_i, \beta_{i, n_i} = \beta_{i, 0} + n_i - S_i$, where $\alpha_{i,0}$ and $\beta_{i,0}$ are the prior shape parameters for $\Gamma_i$ before any samples are evaluated.
+%Given a proposed grasp plan $\Gamma_i$ with current posterior belief $\alpha_i, \beta_i$, , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
+%The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Given the current belief $\alpha_{i, n_i}, \beta_{i, n_i}$ on $P_F$ for a grasp plan $\Gamma_i$, the algorithm can predict the probability of force closure on the next iteration by taking the expected value:
+\todo{Jeff: Revise notation. This was redone fairly quickly and may not be as clear as possible}
+%Thus, we can write the expected probability of force closure as follows
 
@@
 \begin{align}\label{eq:shape_sampling}
-P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
+P_F(\Gamma_i) = \frac{\alpha_{i, n_i}}{\alpha_{i, n_i} + \beta_{i, n_i}}
 \end{align}
@@
 \cite{weber1992gittins}. 
-\todo{Jeff: This is a strong statement but is pretty vague. What are these guarantees?}
+\todo{Jeff: This is a strong statement but is pretty vague. What are these guarantees? I'd favor completely removing this paragraph.}
 
@@
 
+We describe three popular Bayesian MAB algorithms below for the Beta belief distribution.
+
+\todo{Jeff: Revise below sections for clarity}
 \subsection{Bayes-UCB}
@@
 To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon.
-TAt each time step the arm with the highest quantile is chosen and the Beta distribution is updated based on the observed reward.
+At each time step the arm with the highest quantile is chosen and the Beta distribution is updated based on the observed reward.
 For binary rewards (i.e.
@@
 \todo{Let me know how clear this is, Gittins can be hard to describe in general}
+\todo{Jeff: Needs some work. We will have to think about how to get this across intuitively.}
 One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory.

### 2015-01-17 paper.tex

--- 2015-01-12 paper.tex
@@
 
+\subsection{Standard MAB Model}
 The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
+Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+
 In a traditional MAB problem, a gambler has $K$ independent slot machines, or ``arms'' to play.
-When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution, $P_k, k = 1, ..., K$, that is unknown to the gambler.
-The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards is maximized over many pulls.
+When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
+The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards are maximized over many pulls.
 If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
@@
 
-\section{Bandit Algorithms}\label{sec:bandit_algorithm}
+\section{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}
 
-\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now}.
-The algorithms discussed in Section ~\secref{} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
-However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
-In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.
-The belief distribution enables a trade off between exploration and exploitation by naturally increasing confidence around the true reward distribution as more rewards are observed for an arms.
-Theoretical results have shown that these methods are capable of achieving the lower bound described by Lai and Robbin \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}.
-Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
-See \cite{} for a review of bayesian methods in multi-armed bandit problems.
+\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now. I almost feel like Bayesian methods should come sooner}.
+Most of the algorithms discussed in Section~\ref{sec:MAB} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
+In this work, we are particularly interested in Bayesian algorithms that use previous samples to form a belief distribution on the likelihood of achieving force closure \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
+%However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
+%In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.
 
-In the context of grasping, the reward for achieving force close on a sample from the uncertain parameters is a Bernoulli random variable with probabilty of success $\theta$.
-%The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
-In the Bayesian setting we treat $\theta$ as belonging to a distribution.
-A common choice for such a distribution is the Beta distribution, which is the conjugate prior of the Bernoulli distribution.
-One benefit of a conjugate prior is that the posterior update of the belief distribution is of the same form as the original prior, simplifying sampling and analysis.
-Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where $\alpha >0$ and $\beta >0$.
-The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
-To update the prior Beta distribution one adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$
-Often the prior $\alpha =1 $ and $\beta =1$ is used before any rewards are observed, which leads to a uniform distribution on $\theta$.
+Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
+The belief distribution enables a trade off between exploration and exploitation by increasing confidence around the true reward distribution as more rewards are observed for an arms.
+In the case of using force closure $F$ to measure quality, $P_F$ for each candidate grasp is a Bernoulli random variable and the Bayesian conjugate prior is a Beta distribution. 
+Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
+Typically the uniform prior distribution on probability of force closure for each grasp $i$ at time $t = 0$, $\alpha_{i, 0} =1 $ and $\beta_{i, 0} = 1$, would be used used to initialize the algorithm~\cite{}.
+Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving the lower bound described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
+%Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
+%See \cite{} for a review of bayesian methods in multi-armed bandit problems.
 
-Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $p(\theta)$, the distribution on pose $p(\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $p(\mu)$.
-The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Thus, we can write the expected probability of force closure as follows
+%In the context of grasping, the reward for achieving force close on a sample from the uncertain parameters is a Bernoulli random variable with probabilty of success $\theta$.
+%%The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
+%In the Bayesian setting we treat $\theta$ as belonging to a distribution.
+%A common choice for such a distribution is the Beta distribution, which is the conjugate prior of the Bernoulli distribution.
+%One benefit of a conjugate prior is that the posterior update of the belief distribution is of the same form as the original prior, simplifying sampling and analysis.
+%Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where $\alpha >0$ and $\beta >0$.
+%The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
+%To update the prior Beta distribution one adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$
+%Often the prior $\alpha =1 $ and $\beta =1$ is used before any rewards are observed, which leads to a uniform distribution on $\theta$.
+
+One benefit of the Beta prior on Bernoulli reward distributions is the elegant updates to the belief distribution after observing rewards from arm pulls.
+Let $n_i$ denote the number of times grasp plan $\Gamma_i$ has been sampled.
+Then after observing $S_i$ force closure conditions for grasp $\Gamma_i$, the posterior of the Beta can be computed as $\alpha_{i, n_i} = \alpha_{i, 0} + S_i, \beta_{i, n_i} = \beta_{i, 0} + n_i - S_i$, where $\alpha_{i,0}$ and $\beta_{i,0}$ are the prior shape parameters for $\Gamma_i$ before any samples are evaluated.
+%Given a proposed grasp plan $\Gamma_i$ with current posterior belief $\alpha_i, \beta_i$, , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
+%The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
+Given the current belief $\alpha_{i, n_i}, \beta_{i, n_i}$ on $P_F$ for a grasp plan $\Gamma_i$, the algorithm can predict the probability of force closure on the next iteration by taking the expected value:
+%Thus, we can write the expected probability of force closure as follows
 
@@
 \cite{weber1992gittins}, which we will now discuss for each of the three proposed algorithms in detail. 
-\todo{Michael: The above statement is true and I want to convey this message, however it might take some work to convey}
+\todo{Michael: The above statement is true and I want to convey this message, however it might take some work to convey.
+Jeff: "We only need to estimate $\alpha$ and $\beta$ to determine grasp quality" is not true.
+determine -> estimate might fix it}
 

### 2015-01-20 paper.tex
added misses figures

--- 2015-01-12 paper.tex
@@
 
-Our anytime BMAB approach is guaranteed to find the best grasp in a given proposal set in the limit of an infinite time and has empirically been shown to outperform the methods of prior work Monte-Carlo and the method purposed by Kehoe et al.
+One of the BMAB algorithms that works well in practice, Thompson Sampling, is guaranteed to find the best grasp in a given proposal set in the limit of an infinite time \cite{agrawal2011analysis} and initial results have shown it to outperform the methods of prior work Monte-Carlo and the method purposed by Kehoe et al.
 \cite{kehoe2012estimating}.
@@
 \section{Future Work}
-Our results are promising and they suggest many avenues of future work.
-By utilizing the BMAB model, we can encode uncertainty in the grasp parameters and then leverage the existing algorithms to efficiently find the best grasp.
 
-In principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
-It can further be applied to other grasp quality metrics or simulation based evaluation methods \cite{73}.
+As we scale to larger 3D objects the possible number of grasp candidates will be substantially larger, the more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}.
+The MAB algorithms presented above though assumed that each option is independent.
+In the grasping context though spatial information about grasps could provide information about the quality of similar grasps.
+For example, if grasp $A$ is very similar with respect to some metric to grasp $B$ and grasp $B$ appears promising based on samples observed, we might be able use this information and update the prior Beta distribution of grasp $A$.
+
+MAB methods with correlated options do exist and have even been shown to achieve sub-logarithmic regret in some cases \cite{reverdy2014modeling}.
+However, there is an assumption that the correlation between the different options is known or estimated  a priori to running the algorithm.
+In the grasping context, one way to achieve this would be to learn correlations based on an offline training method \cite{andrieu2003introduction}, this might require a feature based representation though of both the proposed grasps and the object itself which could lead to many interesting research questions.
 

### 2015-02-11 paper.tex
reduced size, revised bandit section

@@
 \title{\LARGE \bf
-Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Budgeted Multi-Armed Bandit Models for  [v3 Jan 5, 2015 ] }
+Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Multi-Armed Bandit Models [v3 Feb 12, 2015 ] }
 
@@
 \begin{abstract}
-\textit{Abstract---}\todo{Not sure if we need to change the authors list or not}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
+\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
 Monte-Carlo sampling is computationally demanding, even for planar models.
@@
 
-\begin{abstract}
-\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to uncertainties.
-For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown.
-Monte-Carlo integration is often used to exhaustively evaluate the distribution on a grasp quality metric given these uncertainties.
-We apply algorithms from the sequential decision making literature to intelligently allocate samples for grasp quality evaluation to grasps likely to have higher quality given the previous samples, reducing plan time by roughly an order of magnitude.
-\end{abstract}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-     \subfloat{{\includegraphics[width=8cm]{matlab_figures/teaser.eps} }}%
+     \subfloat{{\includegraphics[width=8cm]{matlab_figures/pfc.eps} }}%
 
@@
 Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
-\todo{Jeff: I personally think the above 3 statements may be too much detail for an intro}
+
 Our approach of using BMAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
-We compare the performance of several popular algorithms for solving the BMAB problem: Bayes UCB, Thompson sampling, and Gittins indices. 
+We compare the performance of several popular algorithms for solving the BMAB problem: Thompson sampling, and Gittins indices. 
 \todo{Going to fill bottom paragraph in later}
@@
 
+ \todo{Michael: should we include this next section on GPIS}
 We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape.
@@
 We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.
-This paper is a substantially revised and expanded version on \cite{laskey} and \cite{mahler2015gp}.
 
@@
 \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
-See Appendix A for detail on how to train a mean and covariance function for a GPIS.
+See Mahler et al.  for details on how to train a mean and covariance function and sample shapes from a GPIS \cite{mahler2015gp}.
 In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
@@
 
-\todo{Jeff: Describe alternative representation of shape uncertainty that we run experiments on. Likely this will be Ben's polygonal model}
-
 \subsubsection{Pose Uncertainty}
-In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
+In typical robotics applications the pose of objects in the environment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
 Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
@@
 
-In 2-dimensional space, the pose of an object $T$ is a member of the Lie Algebra $SE(2)$.
+In 2-dimensional space, the pose of an object $T$ is a member of the Lie Group $SE(2)$.
 This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:
@@
 One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
-Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$, and we define the pose random variable $T$ as
-
-\vspace{-2ex}
-\begin{align*}
-	T  &= \exp \left( \mathbf{\xi}^{\wedge} \right) \bar{T}
-\end{align*}
-
-\noindent where $\mathbf{\xi}^\wedge$ is the twist operator as defined in \cite{barfoot2014Pose}.
+Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$.
+\cite{barfoot2014Pose}.
 
@@
 As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
-The expected friction coefficient $\hat{\mu}$ could be derived by means of object classification and a look up table~\cite{}.
 However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grassp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
+We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
 Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.
@@
 \end{align*}
-\todo{Jeff: revise above symbols for clarity}
 
@@
 
-Appendix \ref{sec:Appendix}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
-Appendix \ref{sec:normals}, describes how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and presents a novel visualization technique for the distribution on surface normals.
-Appendix \ref{sec:mass}, describes a way to calculate the expected center of mass assuming a uniform mass distribution.
-Then we use these quantities to determine the grasp parameters $g$.
+Mahler et al \cite{mahler2015gp}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
+We then use these quantities to determine the grasp parameters $g$.
 Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
@@
 \caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
-Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.
-\todo{Should we use words or symbols for the graphical model?}}
+Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.}
 \vspace*{-10pt}
@@
 \begin{align}
-\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
+\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) 
+\end{align}
+
+Since we only can approximate the probability of force closure, with samples drawn from the distribution $P_F(\Gamma)$ our objective is rewritten as:
+
+\vspace{-2ex}
+\begin{align}
+\Gamma^* &\approx \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
 \end{align}
@@
 This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but is computationally expensive since it may require many samples for each of a large set of candidates to converge to the true value.
-More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward} and searching for locally optimal grasp plans over a continuous set using Sequential Convex Programming~\cite{mahler2015opt}.
-\todo{Jeff: differentiate from these}
-In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem.
+More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
+In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem, which offers stronger theoretical and empirical performance \cite{agrawal2011analysis}\cite{chapelle2011empirical}.
 
@@
 
-\subsection{Standard MAB Model}
+\subsection{MAB Model}
 The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
@@
 The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
-Many variants of UCB have thus been proposed~\cite{}. \todo{Jeff: cite a lot of the literature here}
-Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{} and Thompson sampling for certain reward distributions~\cite{}.
+Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
+Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.
 
-\subsection{Pure Exploration MAB Models}
-Our grasp selection problem is similar in that we would like to find the grasp with the highest quality while conserving computational resources.
-%Motivated by limited computational resources we allocate sampling resources to efficiently find the best arm.
-However, in our problem one only usually cares about the quality when the final grasp is selected for execution ( the difference between the expected quality of the optimal arm and the arm selected is known as ``simple regret'' in the literature) rather than the cumulative regret as studied in the standard MAB problem.
-This is an instance of the Pure Exploration multi-armed bandit problem\cite{bubeck2009pure}, in which an agent attempts to recommend the best arm at the end of an exploration phase but is not penalized for making exploratory arm pulls during this phase.
-Hence, the exploration and exploitation stage are decoupled. 
-The end of the exploration phase, or ``stopping time,'' may not be known to the agent ahead of time.
-Therefore, unless otherwise noted, solutions to the Pure Exploration problem are anytime algorithms; they must return a valid solution whenever they are stopped.
-
-Formally, given arms $\lbrace \Gamma_1, ..., \Gamma_K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$, the goal in the Pure Exploration problem is to find the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
-The expected simple regret, or suboptimality, at time $t$ is given by
-%\vspace{-2ex}
-\begin{align}\label{eq:simple_regret}
-E[r_t] = \mu^* - \mu_t
-\end{align}
-\noindent where $\mu_t$ is the estimate of the best arm at time $t$ from the previous observations.
-
-Several recent works have studied Pure Exploration algorithms that lead to upper bounds on the expected regret.
-Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
-This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem and the number of allocated time steps \cite{audibert2010best}, but requires knowledge of the stopping time.
-In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
-For example, Bubeck et al. showed that the simple regret at any time for the UCB algorithm is bounded by a polynomial function of the number of timesteps~\cite{bubeck2009pure}.
-Several works have showed the relationship between number of timesteps and simple regret for Probably Approximately Correct (PAC) bandit algorithms~\cite{even2006action, mannor2004sample}.
-More recently, Bachman and Precup showed that algorithms based on Bayesian posterior sampling outperformed UCB and PAC algorithms in terms of minimizing simple regret~\cite{bachman2013greedy}.
-%Even-dar et al. showed that for Probably Approximately Correct (PAC) algorithms, the number of pulls needed to
-
-%Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and the Budgeted Multi-Armed Bandit (BMAB) model, in which the algorithm must make a decision at the end of a fixed ``budget'' number of arm pulls.
-
-%\subsection{Fixed Confidence}
-%In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates.
-Originally the problem was solved with `racing' algorithms, which used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were likely to be suboptimal and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}.
-These methods were later extended to return the top $m$ arms instead of only the best arm\cite{gabillon2012best}.
-%
-%The speed of termination is affected by the hardness of the problem, which relates to the how close the other arms expected reward is to the expected reward top arm in the set \cite{audibert2010best}.
-In the grasping context this means that achieving a fixed confidence for two similar grasps would require exhaustive sampling from each distribution.
-%
-%\subsection{Fixed Budget}
-%
-%In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the current best arm at that stopping time this can be thought of as an anytime algorithm.
-%Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
-%This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
-%In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
-For example in \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.
-
-\subsection{Grasp Planning as Pure Exploration}
-In this work, we frame the grasp selection problem of \secref{objective} as a Pure Exploration multi-armed bandit problem.
+\subsection{Grasp Planning as a Multi-Armed Bandit}
+In this work, we frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
 Each arm corresponds to a different grasp plan and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition.
@@
 Thus, the expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E[F | \Gamma_i, \theta, \xi, \rho, \mu] = P_F(\Gamma_i)$.
-Then minimizing the expected simple regret is equivalent to maximizing $P_F$ over the set of candidate grasp plans:
+One can think of the proposed algorithm as an anytime algorithm, because at a unknown stopping time $T_s$, the multi-armed bandit model must return the current highest estimated grasp plan.
+Minimizing the expected instantaneous regret, the difference quality of grasp chose and the best grasp in the set, at stopping time, $T_s$, is equivalent to maximizing $P_F$ over the set of candidate grasp plans:
 
@@
 
-\section{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}
-
-\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now. I almost feel like Bayesian methods should come sooner}.
-Most of the algorithms discussed in Section~\ref{sec:MAB} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
-In this work, we are particularly interested in Bayesian algorithms that use previous samples to form a belief distribution on the likelihood of achieving force closure \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
+\section{Algorithms for MAB}\label{sec:bandit_algorithm}
+In this work, we are particularly interested in Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
 %However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
@@
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
-The belief distribution enables a trade off between exploration and exploitation by increasing confidence around the true reward distribution as more rewards are observed for an arms.
 In the case of using force closure $F$ to measure quality, $P_F$ for each candidate grasp is a Bernoulli random variable and the Bayesian conjugate prior is a Beta distribution.
@@
 Whats interesting in the context of a Bayesian BMAB problem our graphical model in Fig.
-\ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
+\ref{fig:graphical_model}, is now equivalent in terms of inference to Fig.
+\ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
 Regardless of the distributions in Fig.
-\ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian}
-\cite{weber1992gittins}, which we will now discuss for each of the three proposed algorithms in detail. 
-\todo{Michael: The above statement is true and I want to convey this message, however it might take some work to convey.
-Jeff: "We only need to estimate $\alpha$ and $\beta$ to determine grasp quality" is not true.
-determine -> estimate might fix it}
+\ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process on the convergence of the solution being near optimal \cite{agrawal2011analysis}
+\cite{weber1992gittins} , which we will now discuss for each of the proposed algorithms.
 
@@
 
-\todo{Jeff: Revise below sections for clarity}
-\subsection{Bayes-UCB}
-Bayes UCB, detailed in Algorithm 1, is a version of the UCB algorithm that uses a Bayesian posterior update to get a confidence bound instead of  the frequentist concentration inequality approach.
-To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon.
-At each time step the arm with the highest quantile is chosen and the Beta distribution is updated based on the observed reward.
-For binary rewards (i.e.
-Bernoulli distributions) the expected number of pulls of suboptimal arms is bounded and experimentally this algorithm has been shown to outperform UCB for binary rewards \cite{kaufmann2012bayesian}.
+\subsection{The Gittins Index Method} 
+One MAB method is to treat the problem as an Markov Decision Process (MDP) and use Markov Decision theory.
+Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
+In the Beta-Bernoulli MAB case, the set of actions is the $K$ options and the states are the Beta prior on each option.
+A key insight though was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems.
+Generally the computation of the Gittins indices is too expensive, however in the Beta-Bernoulli case it is actually possible \cite{kaufmann2012bayesian}.
+
+Methods, such as Value Iteration, exist to determine optimal policies with respect to the discount factor $\gamma$ \cite{weber1992gittins,barto1998reinforcement}.
+However, the curse of dimensionality effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your options then your state space is exponential in $K$.
+A key insight though was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$.
+
+\vspace{-2ex}
+\label{eq:git_indices}
+\begin{align}
+	v^i(x^i) = \underset{\tau>0}{\mbox{max}} \frac{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^tr^i(X_t^i)|X_0^i = x_i]}{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^t|X_0^i = x_i]}
+ \end{align}
+
+ The indices $v^i(x^i)$, computed in Equation \ref{eq:git_indices},can then be used to form a policy, where at each timestep the agent selects the option with the highest $v^i(x^i)$.
+Generally the computation of the Gittins indices is too expensive, however in the Beta-Bernoulli case it is actually possible \cite{kaufmann2012bayesian}.
+Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
+\cite{katehakis1987multi} due to its ability to be implemented in a dynamic programming fashion.
 
@@
  \KwResult{Current Best Arm, $\Gamma^*$ }
- For Beta(1,1) prior, Stopping Horizon $n$: \\
-\For{ t=1,2,...,n}{ 
-	\For{j = 1,...,K}{
-
-		Compute: $q_j(t) = Q\big(1-\frac{1}{t},p_j^{t-1}\big)$
-
+ For Beta(1,1) prior, Table of Indices $v$, Discount Factor $\gamma$: \\
+\For{ t=1,2,...}{ 
+ Pull arm $k = \underset{x_k \in X}{\mbox{argmax}} v(x_k)$\\
+ Observe reward $R_{I_t,t} \in \lbrace 0,1 \rbrace$\\
+ Update posterior:\\
+ Set $S_{I_t,t+1} = S_{I_t,t} + R_{I_t,t}$ \\
+ Set $F_{I_t,t+1} = F_{I_t,t} + 1 - R_{I_t,t}$\\
+ Set $x_k = \lbrace 1 + S{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
 }
-Draw arm$ I_t = \mbox{argmax}_{j=1...K}q_j(t)$\\
- Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
- Update posterior:\\
- Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
- Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
- Set $\theta_j^t \sim \mbox{Beta}(S_{I_t,t+1},F_{I_t,t+1} )$\\
- }
- \caption{Bayes-UCB for Beta-Bernoulli Process}
+ \caption{The Gittins Index Method for Beta-Bernoulli Process}
 \end{algorithm}
@@
 \subsection{Thompson Sampling}
-Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
+Computation of the Gittins indices can increase exponentially in as the discount factor approaches $1$. Thus, it is not ideal in most cases to use. 
+An alternative known as Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
 We will describe it now in detail for the Beta-Bernoulli process.
@@
 
-The randomness of Thompson sampling allows for it to quickly explore the more arms then Bayes-UCB, which makes conservative arm pulls based on confidence bounds.
-It is also less prone to local solutions because of its stochastic nature.
+The stochastic nature of Thompson sampling makes it less prone to local solutions because of its stochastic nature.
 Thus, for cases where exploration and exploitation are decoupled Thompson sampling can find a better arm faster.
@@
 
-\subsection{The Gittins Index Method} 
-\todo{Let me know how clear this is, Gittins can be hard to describe in general}
-\todo{Jeff: Needs some work. We will have to think about how to get this across intuitively.}
-One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory.
-This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$ \cite{weber1992gittins}.
-
-However, the curse of dimensionality effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your arms then your state space is on the order of $T^{2*K}$.
-Hence the complexity of solving MAB using Markov Decision theory increases exponentially with the number of bandit processes.
-A key insight though was given by Gittins, who showed that instead of solving the $k$-dimensional MDP one can instead solve $k$ 1-dimensional optimization problems: for each arm $i$, $i= 1,...,k$, and for each state of $x^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$.
-
-\vspace{-2ex}
-\label{eq:git_indices}
-\begin{align}
-	v^i(x^i) = \underset{\tau>0}{\mbox{max}} \frac{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^tr^i(X_t^i)|X_0^i = x_i]}{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^t|X_0^i = x_i]}
-\end{align}
-
-The indices can be considered as a computation of the value in choosing an arm conditioned on the fact that you will give up an choose another arm at some point.
-Once you know the state of your $k$ arms, the algorithm is to select the one with the highest index.
-For Best Arm Identification you want your discount factor $\gamma$ to approach 1, since you should never stop pulling the best arm.
-Generally the computation of the Gittins indices is too expensive, however in the Beta-Bernoulli case it is actually possible \cite{kaufmann2012bayesian}.
-We computed the Gittins indices offline using the restart method proposed by Katehakis et al.
-\cite{katehakis1987multi}.
-
-\begin{algorithm}
- \KwResult{Current Best Arm, $\Gamma^*$ }
- For Beta(1,1) prior, Table of Indices $v$, Discount Factor $\gamma$: \\
-\For{ t=1,2,...}{ 
- Pull arm $k = \underset{x_k \in X}{\mbox{argmax}} v(x_k)$\\
- Observe reward $R_{I_t,t} \in \lbrace 0,1 \rbrace$\\
- Update posterior:\\
- Set $S_{I_t,t+1} = S_{I_t,t} + R_{I_t,t}$ \\
- Set $F_{I_t,t+1} = F_{I_t,t} + 1 - R_{I_t,t}$\\
- Set $x_k = \lbrace 1 + S{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
-}
- \caption{The Gittins Index Method for Beta-Bernoulli Process}
-\end{algorithm}
-
  .
@@
 \subsection{Multi-Armed Bandit Experiments}
-\todo{add Bayes and Kehoe results}
 We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$.
@@
 In Fig.
-\ref{fig:simple_regret}, we plotted the simple regret averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Bayes-UCB, Thompson, Gittins, Kehoe et al.
+\ref{fig:grasp_quality}, we plotted the probability of force,$P_F$ closure of the grasp chose vs.
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Thompson, Gittins, Kehoe et al.
 \cite{kehoe2012toward} and Monte-Carlo Integration).
-In Fig.
-\ref{fig:grasp_quality}, we plot the current grasp quality the algorithm selects vs.
-samples drawn.
 We then show the grasps selected for five shapes at a stopping time of $T = 9000$ for all the methods listed in Fig.
@@
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \centering
-\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simp_regret.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes -UCB, Thompson and Gittins).
-Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-As you can see the BMAB methods converge almost a magnitude faster than random allocation.
-It is worth noting that Gittins outperform the other two algorithms, which is useful when choosing which one to implement }
-\vspace*{-10pt}
-\label{fig:simple_regret}
-\end{figure*}
-
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pfc.eps}
+\includegraphics[width = 8cm, height = 9cm]{matlab_figures/pfc.eps}
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
@@
 We also demonstrate what the average probability of force closure for the approximate optimal policy.
-Emperically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
+Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
 \vspace*{-10pt}
 \label{fig:grasp_quality}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \centering
-\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
-\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Random, Bayes - UCB, Thompson, Gittins).
+\includegraphics[width = 8cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
+\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins).
 Graph is averaged over 100 shapes from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each shape.
 The best grasps are ranked 1 and worst are 1000.
-As you can see the MAB algorithm intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation.
+As illustrated the MAB algorithms intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation.
 }
@@
 \label{fig:pulls_per_grasp}
-\end{figure*}
+\end{figure}
 
@@
 \subsection{Worst Case Scenario}
+The MAB algorithms use the observations of samples drawn to decide which grasp to sample next from.
+To show worst case performance under such a model, we sorted the quality of all 1000 grasps offline and arranged the order of samples, so that the top 500 grasps have samples drawn in the order of worst to best and the bottom 500 grasps have samples drawn in order of best to worst.
+The intent here is to provide misleading observations to the bandit algorithms.
+We demonstrate in Fig.
+\ref{fig:worst_case} a case where the observations are misleading.
+
+As illustrated in Fig.
+\ref{fig:worst_case}, all the methods are effected by this worst case performance.
+It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
+It should also be noted though that of the three algorithms measured against Monte-Carlo integration, Thompson sampling is able to  eventually recover from this scenario.
+
 \todo{running experiments today on this}
@@
 \centering
-\includegraphics[width = 8cm, height = 10cm]{matlab_figures/sensitivity_fric.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
-The increase in noise has little effect on the convergence of the two algorithms in simple regret.}
+\includegraphics[width = 8cm, height = 9cm]{matlab_figures/worst_case.eps}
+\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes -UCB, Thompson and Gittins).
+Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+As you can see the BMAB methods converge almost a magnitude faster than random allocation.
+It is worth noting that Gittins outperform the other two algorithms, which is useful when choosing which one to implement }
 \vspace*{-10pt}
-\label{fig:fric_sens}
+\label{fig:worst_case}
 \end{figure}
 
-\begin{figure}[ht!]
+\begin{table*}[t]
 \centering
-\includegraphics[width = 8cm, height = 10cm]{matlab_figures/sensitivity_rot.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under coefficient of friction uncertainty $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians from top to bottom on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
-The increase in noise has little effect on the convergence of the two algorithms in simple regret.
-\todo{Going to rerun with more shapes to be sure about this}}
-\vspace*{-10pt}
-\label{fig:rot_sens}
-\end{figure}
-
-\begin{figure*}%
-    \centering
-    \subfloat[lTop Grasps Shown for Shape 1]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_1.eps} }}%
-    \qquad
-    \subfloat[Top Grasps Shown for Shape 2]{{\includegraphics[width=16.5cm]{matlab_figures/rot_shapes_2.eps} }}%
-    \caption{Two shapes shown from the Brown Visual Lab Dataset,from Left to Right the variance on rotation $\sigma_{rot}$ is increased $0.03$, $0.12$ to $0.24$ radians.
-As you can see the overall variance increase effects the quality of the top grasp in the set of possible grasps.
-Furthermore for Shape 2, the grasp with low rotational variance is different than that for higher variance because the original grasp is more likely to touch the area of higher shape uncertainty when subjected to high variance in rotation.
-\todo{find better shapes in the brown dataset} }%
-    \label{fig:rot_shapes}%
-\end{figure*}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 8cm, height = 10cm]{matlab_figures/sensitivity_trans.eps}
-\caption{ \footnotesize Sensitivity Analysis for Thompson Sampling under translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units from top to bottom on a 40 x 40 unit workspace.
-As you can see the increase in noise effects performance, however the 5000 samples needed for Gittins to  converge at the the highest level of noise (which is a variance of over half the workspace) is much less that the samples needed for uniform allocation to converge in Fig.
-\ref{fig:simple_regret}}
-\vspace*{-10pt}
-\label{fig:trans_sens}
-\end{figure}
+\begin{tabular}{ |p{4cm}||p{2cm}|p{2cm}|p{2cm}|  }
+ \hline
+ \multicolumn{4}{|c|}{Sensitivity Analysis for Thompson Sampling} \\
+ \hline
+Uncertainty Type & Low Uncertainty & Medium Uncertainty & High Uncertainty\\
+ \hline
+Translation Variance in Pose & 1210    & 2207 &  8763\\
+Friction Coefficient Variance &  1985  & 1456   & 1876\\
+Rotational Variance in Pose& 4230 & 4431 &  4432\\
+ \hline
+\end{tabular}
+   \caption { \footnotesize  Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under rotational variance $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 100 shapes from the Brown Vision Lab Data set.
+The sensitivity analysis shows that large variance in translational uncertainty in pose can increase the amount of iterations needed for the bandit algorithm to converge to the highest quality grasp in the set.
+   }
+		\tablabel{opt-p-comparison}
+\vspace*{-20pt}
+\end{table*}
 
@@
 \ref{fig:grasp_quality} suggest that on average grasps at a given stopping time are better than prior methods of Monte-Carlo sampling or the approach of Kehoe et al.
-However, as shown in \todo{worst case results here} there can exists pathological cases that can change this.
+However, as shown in Fig.
+\ref{fig:worst_case} there can exists pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
 Fortunately, though these cases occur with a small probability, however it is important for a practitioner to be aware of them.
@@
 
-\appendix[Gaussian Process Implicit Surface for Representing Shape Uncertainty]
- \label{sec:Appendix}
- In order to solve our problem definition, we must estimate $P(Q(\Gamma)>0)$ for a given grasp .
-We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.
-
-\subsection{Gaussian Process (GP) Background}\label{sec:GP}
-We refer the reader to \cite{mahler2015opt} for a more detailed explanation of the GP construction, which we summarize here.
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$, or the distribution on signed distance field, at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
-\begin{align*}
-	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
-	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
-	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
-\end{align*}
-where $K \in \mathbb{R}^{l \times l}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_l,\bx_*)]^{\intercal}$. 
-This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:
-
-\vspace{-2ex}
-\begin{align}
-	\text{cov}\left(sd(\bx_i), sd(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, sd(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
-	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, \frac{\partial sd (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
-\end{align}
-
-For our kernel choice we decided to use the square exponential kernel, similar to \cite{dragiev2011}.
-Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
-
-We construct a GPIS by learning a Gaussian process to fit measurements of a signed distance field of an unknown object.
-Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\subsection{Sampling Shape from GPIS Distribution }
-To compute the above distribution we must draw samples from $p(\theta)$.
-In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$.
-Since this is a GPIS, we know the following
-
-\vspace{-2ex}
-\begin{align}\label{eq:joint_shape}
-p(S) = p(sd(\mathcal{W})) \sim N(\mu(\mathcal{W}),\Sigma(\mathcal{W}))
-\end{align}
-
-Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
-Shape samples drawn from the distribution appear in Fig.
-\ref{fig:shape_samples}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
-\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
-\vspace*{-10pt}
-\label{fig:shape_samples}
-\end{figure}
-
-\subsection{Distribution on Surface Normals}\label{sec:normals} 
-Using Eq.
-\ref{eq:mean_gradient} and Eq.
-\ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively.
-Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$.
-We can now write
-
-One interesting effect of this technique is that we can now marginalize out the line of action model and visual what the surface normal distribution is along a given line of action.
-To our knowledge this is the first attempt to visual surface normals along a grasp plan.
-Marginalization can be performed as follows:
-
-\vspace{-2ex}
-\begin{equation}
-    p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt \label{eq:normal_dist}
-\end{equation}
-
-Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
-To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.
-In Fig.\ref{fig:GraspDist}, we visualize the distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
-
-\subsection{Expected Center of Mass}\label{sec:mass}
-
-We recall the quantity $P(sd(x) < 0) = \int_{-\infty}^{0} p(sd(x) =  s \ | \ \mu(x),\Sigma(x)) ds$ is equal to the probability that $x$ is interior to the surface under the current observations.
-We assume that the object has uniform mass density and then $P(sd(x) < 0)$ is the expected mass density at $x$.
-Then we can find the expected center of mass as:
-
-\label{eq:mass}
-\begin{equation}
-  \bar{z} 
-  =
-  \frac
-    {\int_{\mathcal{W}}x P(sd(x)<0) dx}
-    {\int_{\mathcal{W}}  P(sd(x)<0) dx}
-\end{equation}
-
-which can be approximated by sampling $\mathcal{W}$ in a grid and approximating the spatial integral by a sum.
-Since this operation involves the entire SDF, one would want to use a low resolution grid for computational efficiency.
-We show the computed density and calculated expected center of mass for a marker in Fig.
-\ref{fig:GPIS_MASS}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide06.jpg}
-\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
-Right: The distribution on the density of each point assuming uniform density}
-\vspace*{-10pt}
-\label{fig:GPIS_MASS}
-\end{figure}
-
 \end{document}

### 2015-02-28 paper.tex
Added ken's feedback

@@
 \title{\LARGE \bf
-Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Multi-Armed Bandit Models [v3 Feb 12, 2015 ] }
+Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v5 Feb 18, 2015 ] }
 
-\author{Michael Laskey$^1$,Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T.
+\author{Michael Laskey$^1$, Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T.
 Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
@@
 \begin{abstract}
-\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
-Monte-Carlo sampling is computationally demanding, even for planar models.
+\textit{Abstract---}
+Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
+Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
 We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.
-We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.
-To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.
-We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
+We formulate grasp planning as a MAB  with finite stopping time to efficiently determine high quality grasp with respect to a probability of force closure metric.
+To evaluate MAB-based sampling, we compare with two methods previously proposed for grasping an planar object under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
+%with shape uncertainty defined by a Gaussian process implicit surface (GPIS).
+%Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
+%Uncertainty in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
+Our approach of using MAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
 \end{abstract}
@@
 
-Consider a robot processing orders in a warehouse, where it frequently encounters new consumer products and must process them quickly.
-The robot may need to rapidly plan grasps for these objects without prior knowledge of object shape, pose and material properties like friction coefficient or center of mass. 
-Furthermore, the robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions or surface properties such as transparency or reflective surfaces.
+Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
+The robot may need to rapidly plan grasps, but may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
+
+% \begin{figure}%
+%     \centering
+% %     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%
+% %       \qquad
+
+%      \subfloat{{\includegraphics[width=8.5cm]{matlab_figures/pfc.eps} }}%
+
+%     \caption{ Comparison of the current average probability of force closure vs.
+the stopping time $T_s$.
+The plots are averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with $|G|=1000$ for each shape.
+We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach of Kehoe et al \cite{kehoe2012toward}.
+We also plot the average probability of force closure for the estimated optimal grasp evaluated using Monte-Carlo sampling.
+Empirically, it appears that Thompson and Gittins converge to the optimal solution at a faster rate, which is desired for an anytime algorithm.
+}%
+%     \label{fig:rot_shapes}%
+% \end{figure}
 
@@
     \centering
-%     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%
+     \subfloat{{\includegraphics[width=8.5cm, height=4.25cm]{figures/uncertainty_motivation.jpg} }}%
 
-%       \qquad
-
-     \subfloat{{\includegraphics[width=8cm]{matlab_figures/pfc.eps} }}%
-
-    \caption{\todo{New teaser photo, not sure if we should have some sort of real object or not}(Top Left) Image of a common household measuring cup.
-(Top Right) Image from a PR2 Primesense camera that reflects the uncertainty that can be induced in objects from transparency.
-(Bottom) Comparision of Multi-Armed Bandit Techniques (Bayes UCB, Thompson, Gittins) vs.
-Monte-Carlo sampling to determine the best grasp in a set of 1000 grasps.
-As you can see the bandit techniques converge in simple regret Eq.
-\ref{eq:simple_regret} a magnitude faster than the traditional approach of Monte-Carlo sampling to determine the highest quality grasp.
-}%
-    \label{fig:rot_shapes}%
+    \caption{ Illustration of the effects of pose and shape uncertainty on parallel-jaw grasps planned for a mechanical switch.
+Left: An RGBD camera observing the switch cannot detect the specular metal toggle and screw regions (black) and the average shape segmentation is rectangular.
+Middle: Optimizing the Ferrari-Canny quality on the estimated mean shape and pose results in an unstable grasp (red arrows) on the true object.
+Right: Selecting the grasp with the highest probability of force closure given shape and pose distributions chooses a stable grasp for the true object.
+\todo{Keep this new image or revert to old?
+Florian favored stronger motivation for uncertainty} }%
+    \label{fig:motivation}%
 \end{figure}
 
-Analytic grasp quality metrics have been developed to determine the stability of a grasp when all the parameters of the object and robot manipulator are exactly known.
-One common measure of stability is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{}.
+Analytic grasp quality metrics have been developed to plan grasps when all the parameters of the object and robot manipulator are exactly known.
+One common measure of stability is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
 Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
-Recent works have explored computing the probability of a grasp achieving the force closure condition given uncertainty in parameters such as pose~\cite{christopoulos2007handling, weisz2012pose, kim2012physically} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-Many methods for evaluating grasp quality in the presence of uncertainty use exhaustive Monte-Carlo sampling over the possible values of uncertain quantities~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards} which can be very time consuming.
-We are interested in ruling out grasps with a low probability in only a few samples and allocate more sampling effort to grasps that are likely to be high quality.
+Recent works have explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
+One option is using Monte-Carlo Integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}, but this can be computationally expensive.
+In this work, we show that it is possible to rule out grasps with low probability of force closure in only a few samples and to allocate more sampling effort to grasps that are likely to be high quality.
 
-The multi-armed bandit (MAB) model for sequential decision making problems~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a formal way to reason about allocating sampling effort to grasps such that the grasp(s) with highest quality can be determined in as few samples as possible.
-In a standard MAB there are a set of possible options (or `arms' in the literature~\cite{barto1998reinforcement}) that each return a numeric reward from a stationary distribution.
-The goal in a MAB problem is to sequentially select ones of the possible options such that a measure of expected reward is maximized.
-Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where an agent has a fixed number of decisions to make before choosing the best option.
-The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.
+The multi-armed bandit (MAB) model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
+The MAB model is particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
+The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
+\todo{explain why} The MAB algorithms can be interpreted as an anytime algorithms, where at a provided stopping time the algorithm terminates and returns the estimated best grasp with respect to a chosen metric.
 
-Our main contribution is formulating the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a budgeted multi-armed bandit problem.
-%\todo{Jeff: probably needs to be more specific here, unless we formally describe how to do it in an arbitrary model}.
-We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, robot motion, and friction coefficient.
+We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
+We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, grasp approach direction, and friction coefficient.
 We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
-Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
-Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
+We model uncertainty in pose as a normal distributions around the orientation and translation of the object.
+Uncertainty in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
 
-Our approach of using BMAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
-We compare the performance of several popular algorithms for solving the BMAB problem: Thompson sampling, and Gittins indices. 
-\todo{Going to fill bottom paragraph in later}
-Initial results suggest a promising avenue with a Xx improvement over  the traditional Monte-Carlo integration and Xx improvement in the experiments that we tried.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, for selecting grasps with high probabilty of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}, a dataset of over 1000 planar objects.
+\todo{Get within 5 of best value numbers}
+Initial results over 100 shapes suggest that on average the grasp return after a given stopping time on the number of samples is of higher quality than that of previous methods.
 
@@
 Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, and uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
-The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
-A common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves exhaustively sampling from distributions on random quantities and averaging the quality over these samples to approximate an expected value~\cite{caflisch1998monte}.
-Exhaustive sampling can be computationally expensive, which motivated the use of Cloud Computing to distribute sampling effort~\cite{kehoe2012toward}.
+One method to represent pose uncertainty is to place a normal distribution around the location of the center of the object as well as the rotational component of the object \cite{barfoot2014Pose}.
+This approach is easy to sample from in the planar case, since each sample is from a fixed 3D Multivariate Gaussian.
 
-To further address the computational complexity, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps.
-However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
-Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty when the robot is able to obtain new information via tactile sensor.
-MCMC provides a Bayesian framework for inference with a hidden state, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.
-
- \todo{Michael: should we include this next section on GPIS}
-We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape.
-For shape uncertainty we decided to use a Gaussian process implicit surface representation.
-Our decision to use this uncertainty model is based on GPIS's ability to combine different modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
+For shape uncertainty we used a Gaussian process implicit surface representation. 
 Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
 Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al.
-used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
-However, this relied on an approximation to grasp quality without guarantees on accuracy.
-We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.
+Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
 
-\section{Preliminaries and Problem Definition}
-We consider selecting a grasp on object from a given set of candidate grasps.
-We formulate this problem for grasping a planar object from above using parallel-jaw grippers.
-We assume that the object is rigid and remains stationary throughout the grasp.
-In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantiites are given.
-In this section, we formally define our grasping model, formalize our sources of uncertainty, introduce our metric for grasp quality, and finally define our grasp planning objective.
-
-%Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
-We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.
-
-\subsection{Candidate Grasp Model}
-Our candidate grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
-Let $d$ denote the dimensionality of the shape representations we are using to select grasps and $m$ denote the number of jaws on the robotic gripper.
-In this work we formulate the MAB problem for 2-dimensional shapes using parallel-jaw grippers, so $d=2$ and $m=2$.
-In this work we also assume a finite width for each parallel jaw $w_j \in \mathbb{R}$.
-
-Similar to~\cite{christopoulos2007handling}, we parameterize a grasp using a {\it line of action} for each gripper jaw, where each line of action is a 1D curve $\gamma(t): [0,1] \rightarrow \mathbb{R}^d$ with endpoints $\gamma(0) = \ba$ and $\gamma(1) = \bb$.
-The line of action defines the trajectory that a jaw follows as the gripper closes around a shape.
-A {\it grasp plan} is the set of lines of action for each of the jaws, $\Gamma = \{\gamma_1(\cdot),...,\gamma_m(\cdot)\})$ \cite{}.
-For parallel-jaw grippers, $\Gamma = \{\gamma(t), \gamma(1 - t)\}$, since the two jaws approach the shape in opposite directions.
-Furthermore, in this work we consider only straight lines of action.
-The line of action model allows us to compute perturbations to the contact points and normals that occur due to shape uncertainty.
-%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changes in the location of contact with a surface, and the line of action allows us to compute these new locations.
-
-Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following the given plan, $\bc_1, ..., \bc_m \in \mathbb{R}^d$.
-We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, ..., \bn_m \in \mathbb{R}^d$ and the object center of mass as $\bz \in \mathbb{R}^d$.
-Together these form the set of grasp parameters $g = (\bc_1, ..., \bc_m, \bn_1, ... \bn_m, \bz)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object.
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
-%\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-%\vspace*{-10pt}
-%\label{fig:line_of_action}
-%\end{figure}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width = 8cm, height = 6.5cm]{figures/grasp_model.jpg}
-\caption{llustration of our grasping model for parallel jaw grippers on a GPIS model of a marker with shape uncertainty near the object center.
-Jaw placements are illustrated by a red direction arrow and line.
-The grasp plan consists of a line of action $\gamma(t)$ with endpoints $\ba$ and $\bb$.
-When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$ with outward pointing unit surface normals $\bn_1$ and $\bn_2$.
-Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.
-\todo{Jeff: Up to this point I don't believe the reader has seen a GPIS.
-We will replace the marker with a deterministic shape, but this figure gives a good idea of what we want to illustrate here.}}
-\vspace*{-4ex}
-\label{fig:grasp_model}
-\end{figure}
-
-\subsection{Sources of Uncertainty}
-In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient.
-Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
-In this section we describe each source of uncertainty and our model of the uncertainty.
-We wish to emphasize that the models of uncertainty described in this work are not the only models that may be used with MAB algorithms and that the reader may choose parameters and distributions that best fit their needs, however performance is subject to vary on empirical results.
-
-\subsubsection{Shape Uncertainty}
-
-Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
-Following ~\cite{laskey2015bandits, mahler2015gp} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
-A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
-A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
-A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
-\bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
-See Mahler et al.  for details on how to train a mean and covariance function and sample shapes from a GPIS \cite{mahler2015gp}.
-In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
-For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.
-
-\subsubsection{Pose Uncertainty}
-In typical robotics applications the pose of objects in the environment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
-Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
-In practice this uncertainty may be quantified based on the algorithms used to register these frames to one another.
-The effects of pose uncertainty on robotic grasping has been studied by~\cite{weisz2012pose, kim2012physically}. % cite Ben's RSS workshop paper here
-
-In 2-dimensional space, the pose of an object $T$ is a member of the Lie Group $SE(2)$.
-This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:
-
-\vspace{-2ex}
-\begin{align*}
-	T &= \left[  \begin{array}{ccc}
-		\cos(\phi) & -\sin(\phi) & t_x \\
-		\sin(\phi) & \cos(\phi) & t_y \\
-		0 & 0 & 1
-		\end{array} \right] .
-\end{align*}
-
-One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
-Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$.
-\cite{barfoot2014Pose}.
-
- \subsubsection{Motion Uncertainty}
-In practice a robot may not be able to execute a desired grasp plan $\Gamma$ exactly due to slight errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
-In this work, we model motion uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
-Formally, let $\hat{\by} = \frac{1}{2} (\ba + \bb)$ denote the center of a planned line of action $\gamma(t)$ and $\hat{\psi}$ denote the angle that the planned line $\bb - \ba$ makes with the x-axis of the 2D coordinate system on our shape representation.
-Then the random center $\by \sim \mN(\hat{\by}, \Sigma_y)$ and the random angle $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
-For shorthand in the remainder of this paper we will refer to the random motion parameters as $\rho = \{\by, \psi \}$.
-In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.
-
- \subsubsection{Friction Uncertainty}
-As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
-However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
-dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
-We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.
-
-\subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
-Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.
-
-Formally, force closure is a binary-valued quantity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
-Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ...
-\bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
-If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{li1988task}.
-In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
-%\vspace{-2ex}
-\begin{align*}
-	P_F(\Gamma) &= P(F = 1 | \Gamma, \theta, \xi, \rho, \mu).
-\end{align*}
-
-To estimate $P_F(\Gamma)$, we generate  samples from each of the above distributions in sequence using the relationships defined by the graphical model in Fig.
-\ref{fig:graphical_model}.To sample from $p_F(\Gamma)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$.
-Using Bayes rule  we can rewrite this as
-
- \vspace{-2ex}
- \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
- &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
- \end{align*}
-
-Mahler et al \cite{mahler2015gp}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$).
-We then use these quantities to determine the grasp parameters $g$.
-Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
-
-%Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
-The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
-A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
-%
-%In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
-$P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
-\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
-Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.}
-\vspace*{-10pt}
-\label{fig:graphical_model}
-\end{figure}
-
-\subsection{Objective}
-
-Given the sources of uncertainty and their relationships as described above, our goal is to find the grasp that maximizes the probability of force closure from a set of $P$ prespecified candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_P\}$:
-
-\vspace{-2ex}
-\begin{align}
-\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) 
-\end{align}
-
-Since we only can approximate the probability of force closure, with samples drawn from the distribution $P_F(\Gamma)$ our objective is rewritten as:
-
-\vspace{-2ex}
-\begin{align}
-\Gamma^* &\approx \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
-\end{align}
-
-One method to solve Equation ~\ref{eq:problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grap plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
-This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but is computationally expensive since it may require many samples for each of a large set of candidates to converge to the true value.
-More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
-In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem, which offers stronger theoretical and empirical performance \cite{agrawal2011analysis}\cite{chapelle2011empirical}.
-
-\section{Multi-Armed Bandits for Grasp Selection}
-\label{sec:MAB}
-%While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we
-We propose framing the problem in the multi-armed bandit (MAB) model and forming a policy for iteratively selecting which grasp to evaluate based on the probability of force closure estimate from the samples so far.
-The goal of the MAB approach is to allocate more sampling effort to grasps that appear to have higher quality based on the evaluation performed so far.
+One common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution\cite{caflisch1998monte}.
+It can be computationally expensive though to sample all proposed grasps to convergence.
+To  address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps.
+However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates variance around the current estimate, which in practice could lead to good grasps being thrown away.
+We propose treating the problem as an Multi-Armed Bandit, which instead of pruning grasps away decide based on past observations what grasp to sample next \cite{barto1998reinforcement}.
 
@@
 
-In a traditional MAB problem, a gambler has $K$ independent slot machines, or ``arms'' to play.
+In a traditional MAB problem, a gambler has $K$ independent one-armed bandits, also known as slot machines.
 When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
@@
 
-Success in MAB problems is commonly measured in terms of {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
-Traditional bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
-Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
+At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the arm selected.
+Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
+Lai and Robbins showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
 They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
 The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
-Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
-Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.
+%Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
+Since then a several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.
 
-\subsection{Grasp Planning as a Multi-Armed Bandit}
-In this work, we frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
-Each arm corresponds to a different grasp plan and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition.
-Since force closure is a binary value, we can think of each grasp plan $\Gamma_i$ as having a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
-Thus, the expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E[F | \Gamma_i, \theta, \xi, \rho, \mu] = P_F(\Gamma_i)$.
-One can think of the proposed algorithm as an anytime algorithm, because at a unknown stopping time $T_s$, the multi-armed bandit model must return the current highest estimated grasp plan.
-Minimizing the expected instantaneous regret, the difference quality of grasp chose and the best grasp in the set, at stopping time, $T_s$, is equivalent to maximizing $P_F$ over the set of candidate grasp plans:
-
-\vspace{-2ex}
-\begin{align*}
-	\underset{\Gamma_i \in \mG}{\text{argmin }}\mu^{*} - \mu_{i} &= \underset{\Gamma_i \in \mG}{\text{argmax }}\mu_{i} \\
-	&=  \underset{\Gamma_i \in \mG}{\text{argmax }} P_F(\Gamma_i) \\
-	&= \Gamma^{*}
-\end{align*}
-
-In Section \ref{sec:bandit_algorithm}, we will discuss some of the most popular algorithms for solving the multi-armed bandit problem in detail.
-
-\section{Algorithms for MAB}\label{sec:bandit_algorithm}
-In this work, we are particularly interested in Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
+\subsection{Algorithms for MAB}\label{sec:bandit_algorithm}
+We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) ~\cite{chapelle2011empirical, bachman2013greedy}.
+Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving near the lower bound on the asymptotic rate of convergence in regret described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
 %However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
@@
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
-In the case of using force closure $F$ to measure quality, $P_F$ for each candidate grasp is a Bernoulli random variable and the Bayesian conjugate prior is a Beta distribution.
+For instance a Bernoulli random variable, $\theta$, can be used to represent a binary grasping metric like force closure.
+The prior traditional placed on a Bernoulli variable is its conjugate prior the Beta distribution.
 Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
-Typically the uniform prior distribution on probability of force closure for each grasp $i$ at time $t = 0$, $\alpha_{i, 0} =1 $ and $\beta_{i, 0} = 1$, would be used used to initialize the algorithm~\cite{}.
-Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving the lower bound described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
+
 %Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
@@
 
-One benefit of the Beta prior on Bernoulli reward distributions is the elegant updates to the belief distribution after observing rewards from arm pulls.
-Let $n_i$ denote the number of times grasp plan $\Gamma_i$ has been sampled.
-Then after observing $S_i$ force closure conditions for grasp $\Gamma_i$, the posterior of the Beta can be computed as $\alpha_{i, n_i} = \alpha_{i, 0} + S_i, \beta_{i, n_i} = \beta_{i, 0} + n_i - S_i$, where $\alpha_{i,0}$ and $\beta_{i,0}$ are the prior shape parameters for $\Gamma_i$ before any samples are evaluated.
+One benefit of the Beta prior on Bernoulli reward distributions is that updates to the belief distribution after observing rewards from arm pulls can be derived in closed form.
+Let $n_i$ denote the number of times arm $k$ has been sampled.
+Then after observing $S_i$ rewards of $1$ for arm $k$, the posterior of the Beta are $\alpha_{i, n_i} = \alpha_{i, 0} + S_i, \beta_{i, n_i} = \beta_{i, 0} + n_i - S_i$, where $\alpha_{i,0}$ and $\beta_{i,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 %Given a proposed grasp plan $\Gamma_i$ with current posterior belief $\alpha_i, \beta_i$, , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
 %The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Given the current belief $\alpha_{i, n_i}, \beta_{i, n_i}$ on $P_F$ for a grasp plan $\Gamma_i$, the algorithm can predict the probability of force closure on the next iteration by taking the expected value:
+Given the current belief $\alpha_{k, n_i}, \beta_{k, n_i}$ on $\theta_k$ for an arm $k$, the algorithm can predict the probability of an event occurring on the next iteration by taking the expected value:
 %Thus, we can write the expected probability of force closure as follows
@@
 \begin{align}\label{eq:shape_sampling}
-P_F(\Gamma) = \frac{\alpha}{\alpha + \beta}
+\theta_k = \frac{\alpha}{\alpha + \beta}
 \end{align}
-
-Whats interesting in the context of a Bayesian BMAB problem our graphical model in Fig.
-\ref{fig:graphical_model}, is now equivalent in terms of inference to Fig.
-\ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality.
-Regardless of the distributions in Fig.
-\ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process on the convergence of the solution being near optimal \cite{agrawal2011analysis}
-\cite{weber1992gittins} , which we will now discuss for each of the proposed algorithms.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 2cm, height = 4cm]{figures/Slide9.jpg}
-\caption{A graphical model that illustrates the relationship between the Bernoulli distribution of the probability force closure and its conjugate prior Beta distribution that has two shape parameters $\alpha$ and $\beta$ }
-\vspace*{-10pt}
-\label{fig:beta_model}
-\end{figure}
 
@@
 
-We describe three popular Bayesian MAB algorithms below for the Beta belief distribution.
+\noindent We describe two popular Bayesian MAB algorithms below for the Beta belief distribution.
 
-\subsection{The Gittins Index Method} 
+\subsubsection{The Gittins Index Method} 
 One MAB method is to treat the problem as an Markov Decision Process (MDP) and use Markov Decision theory.
@@
 In the Beta-Bernoulli MAB case, the set of actions is the $K$ options and the states are the Beta prior on each option.
-A key insight though was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems.
-Generally the computation of the Gittins indices is too expensive, however in the Beta-Bernoulli case it is actually possible \cite{kaufmann2012bayesian}.
 
-Methods, such as Value Iteration, exist to determine optimal policies with respect to the discount factor $\gamma$ \cite{weber1992gittins,barto1998reinforcement}.
+Methods such as Value Iteration can compute optimal policies for an MDP with respect to the discount factor $\gamma$ when all states, actions, and expected rewards can be enumerated~\cite{weber1992gittins,barto1998reinforcement}.
 However, the curse of dimensionality effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your options then your state space is exponential in $K$.
-A key insight though was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$.
+A key insight though was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$, as shown in Algorithm 1.
 
 \vspace{-2ex}
-\label{eq:git_indices}
-\begin{align}
+\begin{align}\label{eq:git_indices}
 	v^i(x^i) = \underset{\tau>0}{\mbox{max}} \frac{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^tr^i(X_t^i)|X_0^i = x_i]}{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^t|X_0^i = x_i]}
@@
 
- The indices $v^i(x^i)$, computed in Equation \ref{eq:git_indices},can then be used to form a policy, where at each timestep the agent selects the option with the highest $v^i(x^i)$.
-Generally the computation of the Gittins indices is too expensive, however in the Beta-Bernoulli case it is actually possible \cite{kaufmann2012bayesian}.
+\noindent The indices $v^i(x^i)$, computed in Equation \ref{eq:git_indices},can then be used to form a policy, where at each timestep the agent selects the option with the highest $v^i(x^i)$.
 Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
@@
 
-\subsection{Thompson Sampling}
-Computation of the Gittins indices can increase exponentially in as the discount factor approaches $1$. Thus, it is not ideal in most cases to use. 
-An alternative known as Thompson Sampling is a Bayesian method for the multi-armed bandit problem.
-We will describe it now in detail for the Beta-Bernoulli process.
-All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha=1$,$\beta =1$) to reflect a uniform prior on the $\theta$ of the Bernoulli distribution.
+\subsubsection{Thompson Sampling}
+Computation of the Gittins indices can increase exponentially in as the discount factor approaches $1$, and therefore it is not ideal to use in most cases. 
+Thompson sampling is a less computationally expensive alternative.
+All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha=1$,  $\beta =1$) to reflect a uniform prior on the $\theta$ of the Bernoulli distribution.
 Then for each arm draw $\theta_{j,t} \sim \mbox{Beta}(\alpha,\beta)$ and pull the arm with the highest $\theta_{j,t}$ drawn.
 The reward, $X_{i,t}$ is observed from that arm, $j$, and the corresponding Beta distribution is updated.
-This is repeated until a stopping time is reached.
-The full algorithm is shown in Algorithm 1.
+This is repeated until a stopping time is reached. The full algorithm is shown in Algorithm 2.
 
-The stochastic nature of Thompson sampling makes it less prone to local solutions because of its stochastic nature.
-Thus, for cases where exploration and exploitation are decoupled Thompson sampling can find a better arm faster.
-Thompson sampling has recently been shown to approach the Lai and Robbins bound \cite{agrawal2011analysis} and has  empirically been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}.
-Variants of it are even used commercially in products like Microsoft's adPredictor, which is used by Bing, the search engine, \cite{graepel2010web}.
+The intuition for Thompson sampling is that the random samples of $\theta_{j,t}$ allow the method to explore.
+However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity.
+Chapelle et al.
+demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case \cite{chapelle2011empirical}.
+Theoretically, Agrawal et al.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that was sub-linear  for $k$ -arms and in the case of $2$ arms logarithmic \cite{agrawal2011analysis}.
+
 \begin{algorithm}
@@
 \end{algorithm}
+\vspace{-2ex}
+
+\section{Grasp Planning Problem Definition}
+We consider grasping a rigid, planar object from above using parallel-jaw grippers.
+We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
+In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantities are given.
+
+%Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
+We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.
+
+\subsection{Candidate Grasp Model}
+\todo{make anitpodal}
+The grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
+We formulate the MAB problem for 2-dimensional objects using parallel-jaw grippers.
+Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis} for a parallel jaw gripper with jaws of width $w_j \in \mathcal{R}$ and a maximum width $w_g \in \mathcal{R}$.
+The two location of the jaws can be specified as $\mathbf{g_1},\mathbf{g_2} \in \mathcal{R}^2$, where $||\mathbf{g}_1 - \mathbf{g}_2|| \leq w_g$.
+We define a grasp plan consisting of the tuple $\Gamma = \lbrace g_1, g_2 \rbrace$.
+
+%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
+
+Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
+We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^d$, the object center of mass as $\bz \in \mathbb{R}^d$ and the friction coefficient as $\mu$.
+The center of mass may be computed based on a known mass density of the object.
+Together these form the set of grasp parameters $g = (\bc_1,\bc_2, \bn_1, \bn_2, \bz,\mu)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object.
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
+%\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
+%\vspace*{-10pt}
+%\label{fig:line_of_action}
+%\end{figure}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width = 8cm, height = 6.5cm]{figures/grasp_model.jpg}
+\caption{llustration of our grasping model for parallel jaw grippers on a GPIS model of a marker with shape uncertainty near the object center.
+Jaw placements are illustrated by a red direction arrow and line.
+The grasp plan consists of a line of action $\gamma(t)$ with endpoints $\ba$ and $\bb$.
+When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$ with outward pointing unit surface normals $\bn_1$ and $\bn_2$.
+Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
+\vspace*{-4ex}
+\label{fig:grasp_model}
+\end{figure}
+
+\subsection{Sources of Uncertainty}
+In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient.
+Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
+In this section we describe each source of uncertainty and our model of the uncertainty.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
+\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
+As illustrated uncertainty in pose, motion and shape effect the the contacts and surface normals that makes up the grasp.
+Friction coefficient is independent of this relationship.
+The box around contact and normals means there are repeated nodes, in this case we have $m=2$ corresponding to the two jaws in the gripper.
+}
+\vspace*{-10pt}
+\label{fig:graphical_model}
+\end{figure}
+
+\subsubsection{Shape Uncertainty}
+
+Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
+Following ~\cite{mahler2015gp}, we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
+A GPIS represents a distribution over signed distance functions (SDFs).
+A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
+A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
+\bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
+See Mahler et al. for details on how to train a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
+In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
+For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.
+
+\subsubsection{Pose Uncertainty}
+In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:
+
+\vspace{-2ex}
+\begin{align*}
+	T &= \left[  \begin{array}{ccc}
+		\cos(\phi) & -\sin(\phi) & t_x \\
+		\sin(\phi) & \cos(\phi) & t_y \\
+		0 & 0 & 1
+		\end{array} \right] .
+\end{align*}
+
+%One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
+\noindent Following Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$.~\cite{barfoot2014Pose}.
+
+ \subsubsection{Approach Uncertainty}
+In practice a robot may not be able to execute a desired grasp plan $\Gamma$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
+We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
+Formally, let $\hat{\by} = \frac{1}{2} (\ba + \bb)$ denote the center of a planned line of action $\gamma(t)$ and $\hat{\psi}$ denote the angle that the planned line $\bb - \ba$ makes with the x-axis of the 2D coordinate system on our shape representation.
+We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
+For shorthand in the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
+In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ might be set from repeatability measurements for a robot~\cite{mooring1986determination}.
+
+ \subsubsection{Friction Uncertainty}
+As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
+However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
+dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
+We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.
+
+\vspace{-2ex}
+
+\subsection{Grasp Quality}\label{sec:grasp_sample}
+We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
+Force closure measures the ability to resist external wrenches.
+
+Formally, force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
+Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ...
+\bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
+If the origin lies within the convex hull of $\mW$, then the grasp is in force closure~\cite{li1988task}.
+We rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
+%\vspace{-2ex}
+\begin{align*}
+	P_F(\Gamma) &= P \left(F = 1 | \Gamma, \theta, \xi, \rho, \mu \right).
+\end{align*}
+
+To estimate $P_F(\Gamma)$, we generate samples from each of the distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.
+After sampling a shape, pose, approach direction, and friction coefficient, we compute the contact locations $\bc_i$ and the surface normals $\bn_i$ using Bayes rule:
+
+ \vspace{-2ex}
+ \begin{align*}
+ &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
+ &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
+ \end{align*}
+
+Mahler et al.~\cite{mahler2015gp} describe how to draw shape sample from a GPIS model.
+We then also sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the line of action $\gamma_i(t)$~\cite{newcombe2011kinectfusion}.
+Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.
+We use these quantities to determine the grasp parameters $g$.
+Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
+
+%Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
+The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
+If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
+A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
+%
+%In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
+$P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.
+
+\subsection{Objective}
+\seclabel{objective}
+
+Given the sources of uncertainty and their relationships as described above, the grasp planning objective is to find the grasp that maximizes the probability of force closure from a set of $P$ candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_P\}$:
+
+\vspace{-2ex}
+\begin{align}
+\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:old_problem_def}
+\end{align}
+
+% Since we only can approximate the probability of force closure, with samples drawn from the distribution $P_F(\Gamma)$ our objective is rewritten as:
+
+% \vspace{-2ex}
+% \begin{align}
+% \Gamma^* &\approx \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
+% \end{align}
+
+One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
+This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
+More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
+We formulate the problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices in solving it.
+
+\section{Grasp Planning as a Multi-Armed Bandit}
+In this work, we frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
+Each arm corresponds to a different grasp plan, $\Gamma_i$, and pulling an arm corresponds to sampling from the graphical model in Fig.
+\ref{fig:graphical_model} and evaluating the force closure condition.
+Since force closure is a binary value, each grasp plan $\Gamma_i$ has a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
+The expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E \left[ F | \Gamma_i, \theta, \xi, \rho, \mu \right] = P_F(\Gamma_i)$, and therefore minimizing cumulative regret up to a stopping time $T_s$ is equivalent to the objective of Equation~\ref{eq:problem_def}.
+
+\todo{think of stopping criteria, thats not anytime}
+One can think of the proposed algorithm as an anytime algorithm, it can be stopped at anytime during its computation and return the current estimate of the best grasp or wait until its estimate of the best grasp is within some set confidence.
+The confidence interval can be determined via the variance of the Beta distribution, which is defined as
+
+\vspace{-2ex}
+\begin{align}
+\mbox{Var}(P_F(\Gamma_i)) = \frac{\alpha\beta}{(\alpha+\beta)^2(\alpha+\beta+1)}
+\end{align}
+
+We then run the algorithm until the estimated best grasp at time $t$ has $\mbox{Var}(P_F(\Gamma_i))$
 
  .
-\section{Experiments}
-For the experiments we used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.
-We downsampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+\section{Simulation Experiments}
+We used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.Examples of the images can be seen in \ref{fig:shape_samples}.
+We down sampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
 The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads,$\sigma_{trans} = 3$.
-Our visualization technique follows the approach of \cite{mahler2015gp} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
-
-We did experiments for the case of two hard contacts in 2-D.
-We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
+\todo{Figure out why these parameters were set, or think of more logical settings} The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
+We thought these were reasonable values based on the size of the 40x40 workspace and the amount of noise expected in industrial applications. 
+We us the GPIS-Blur visualization technique \cite{mahler2015gp}.
+We performed experiments for the case of two hard contacts in 2-D.
+We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
 
 \subsection{Multi-Armed Bandit Experiments}
-We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$.
 For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$.
@@
 In Fig.
-\ref{fig:grasp_quality}, we plotted the probability of force,$P_F$ closure of the grasp chose vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Thompson, Gittins, Kehoe et al.
-\cite{kehoe2012toward} and Monte-Carlo Integration).
-We then show the grasps selected for five shapes at a stopping time of $T = 9000$ for all the methods listed in Fig.
+\ref{fig:grasp_quality}, we plotted the probability of force closure,$P_F$ , of the grasp chose vs.
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration).
+We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation.
+The adaptive sampling method of Kehoe et al.
+prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
+To illustrate the difference in grasp quality returned at a stopping time of $T = 9000$,  we show the grasps selected for three randomly selected objects for all methods listed in Fig.
 \ref{fig:shape_samples}.
+Interestingly in Fig \ref{fig:grasp_quality}, Gittins and Thompson select at stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
 
-  Interestingly in Fig \ref{fig:grasp_quality}, Gittins and Thompson suggest on average higher quality grasps with  than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
  In Fig.
-\ref{fig:pulls_per_grasp} we plot samples per grasp quality, Gittins and Thompson appear to allocate significantly more grasp samples to grasps of high quality, thus they are quickly able to ignore the low quality grasps.
-Kehoe et al.
-and Monte-Carlo integration take a more evenly distributed approach to sample allocation, which could explain the performance difference in Fig.
-\ref{fig:simple_regret} and Fig.
-\ref{fig:grasp_quality}.
+\ref{fig:pulls_per_grasp}, we plot samples per grasp quality, Gittins and Thompson appear to allocate  more samples to grasps of high quality.
+In contrast to Monte-Carlo, which uniformly allocate grasp samples.
+The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps.
+The adaptive sampling method proposed by Kehoe et al.
+also allocates more samples to promising grasps,however it is not as efficient as the MAB methods shown.
+As illustrated by the difference in allocated samples from grasps ranked 200 to 800 in Fig.
+\ref{fig:pulls_per_grasp}.
 
@@
 \centering
-\includegraphics[width = 8cm, height = 9cm]{matlab_figures/pfc.eps}
+\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/pfc.eps}
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
-the number of samples pulled.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
 We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
@@
 \centering
-\includegraphics[width = 8cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
+\includegraphics[width = 9cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
 \caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins).
@@
 \begin{figure*}%
+\label{fig:shape_examples}
     \centering
@@
     \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_2.eps} }}%
-       \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_3.eps} }}%
-          \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_4.eps} }}%
              \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_5.eps} }}%
 
-    \caption{Five shapes shown from the Brown Visual Lab Dataset with induced shape uncertainity and visualized according to the method described in \cite{mahler2015gp}.
+    \caption{\todo{Need to change this figure, wondering what should be conveyed here}Three shapes shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized according to the method described in \cite{mahler2015gp}.
 The four methods (Monte-Carlo, Kehoe's, Thompson and Gittins) were all run until a stopping time of 9000 evaluations with a uniformly initialized grasp set of $|G|=1000$.
@@
 The grasps and the quality each one found is shown above.
-In the four out of five cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $9000$, however at the last shape there is a difference of $2\%$ grasp quality.
+In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $9000$, however at the last shape there is a difference of $2\%$ grasp quality.
 }%
@@
 
-\todo{Michael: Need to discuss how to implement worst case scenario, adversial applies changing distributions online (which would not model the problem).}
-
 \subsection{Sensitivity Analysis }
-We now will show how well the top two algorithms Thompson Sampling and the Gittens Index Method perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
+\todo{need to redo with larger number of shapes}
+We now will show how well  Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
 The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
-All experiments were averaged across 10 shapes randomly selected with from the Brown dataset with a set size $|G| = 1000$.
+All experiments were averaged across 10 shapes randomly selected with from the Brown dataset with $|G| = 1000$, or 1000 grasp plans $\Gamma$.
 
 For friction coefficient we varied the variance across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
-As illustrated in Fig.
-\ref{fig:fric_sens}, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 2000 evaluations.
+As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 2000 evaluations.
 
 For rotational uncertainty in pose, we varied $\sigma_{rot}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
-As illustrated in Fig.
-\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\deg}$  causes the convergence in simple regret to not be reached until 5500 samples or an average of 5.5 samples per grasp.
-This can be explained because such a large variance causes a a drop in quality across all grasps and makes it harder to separate the outliers \cite{gabillon2012bes}.
-The quality of the best grasp along with the grasp for each round is shown in \ref{fig:rot_shapes}.
+As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\deg}$  causes the convergence in simple regret to not be reached until around 4432 samples or an average of 5.5 samples per grasp.
 
@@
 As you can see in Fig.
-\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until around 5000 samples for the Gittens Method and  8200 evaluations for Thompson Sampling.
+\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
 
-\subsection{Worst Case Scenario}
+\subsection{Worst Case}
 The MAB algorithms use the observations of samples drawn to decide which grasp to sample next from.
@@
 As illustrated in Fig.
-\ref{fig:worst_case}, all the methods are effected by this worst case performance.
+\ref{fig:worst_case}, all the methods are affected by worst case performance.
 It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
-It should also be noted though that of the three algorithms measured against Monte-Carlo integration, Thompson sampling is able to  eventually recover from this scenario.
-
-\todo{running experiments today on this}
+One interesting aspect that is illustrated is that Thompson sampling is able to make improvement while the other two methods are stuck in local optimal.
+This is because Thompson sampling is guaranteed to find the best grasp in the limit of infinite iterations \cite{agrawal2011analysis}.
 
@@
 \centering
-\includegraphics[width = 8cm, height = 9cm]{matlab_figures/worst_case.eps}
-\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes -UCB, Thompson and Gittins).
-Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-As you can see the BMAB methods converge almost a magnitude faster than random allocation.
-It is worth noting that Gittins outperform the other two algorithms, which is useful when choosing which one to implement }
+\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/worst_case.eps}
+\caption{ \footnotesize Comparison of the current average probability of force closure vs.
+the stopping time $T_s$ for the pathological case where the samples are sorted to be misleading.
+The graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
+We also demonstrate what the average probability of force closure for the approximate optimal policy.
+Empirically, it appears that when samples are misleading the best policy is uniform allocation.
+However, it also illustrated that Thompson sampling can recover from this situation where Gittins and Kehoe et al.
+are not able to and get stuck in local solutions.
+}
 \vspace*{-10pt}
@@
 \centering
-\begin{tabular}{ |p{4cm}||p{2cm}|p{2cm}|p{2cm}|  }
+\begin{tabular}{ |p{4.5cm}||p{2cm}|p{2.5cm}|p{2cm}|  }
  \hline
- \multicolumn{4}{|c|}{Sensitivity Analysis for Thompson Sampling} \\
+ \multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson Sampling} \\
  \hline
-Uncertainty Type & Low Uncertainty & Medium Uncertainty & High Uncertainty\\
+Uncertainty Type & Low Uncertainty (Iterations) & Medium Uncertainty (Iterations) & High Uncertainty (Iterations)\\
  \hline
-Translation Variance in Pose & 1210    & 2207 &  8763\\
-Friction Coefficient Variance &  1985  & 1456   & 1876\\
-Rotational Variance in Pose& 4230 & 4431 &  4432\\
+Translation Variance in Pose, $\sigma_{trans}$ & 1210    & 2207 &  8763\\
+Friction Coefficient Variance, $\sigma_{fric}$ &  1985  & 1456   & 1876\\
+Rotational Variance in Pose, $\sigma_{rot}$ & 4230 & 4431 &  4432\\
  \hline
 \end{tabular}
-   \caption { \footnotesize  Sensitivity Analysis for Thompson Sampling and the Gittens Index Method under rotational variance $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 100 shapes from the Brown Vision Lab Data set.
+   \caption { \footnotesize  Sensitivity Analysis for convergence to estimated best grasp for Thompson Sampling under rotational variance $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
 The sensitivity analysis shows that large variance in translational uncertainty in pose can increase the amount of iterations needed for the bandit algorithm to converge to the highest quality grasp in the set.
@@
 
-Our budgeted multi-armed bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
+Our multi-armed bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
 Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.
+Since currently the bandit algorithm doesn't utilize correlations between grasps, we are throwing away a lot of information that could be useful for choosing what to grasp to sample next.
 
-Of the BMAB algorithms we showed, Thompson Sampling is guaranteed to find the best grasp as the stopping time approaches infinity \cite{agrawal2011analysis} but when do you terminate the algorithm is still an open question.
-Fixed confidence methods do exist that terminate when a certain confidence interval is reached \cite{maron1993hoeffding} \cite{mnih2008empirical}.
-However, a known problem is that if two grasps have very similar quality it could greatly increase the time for needed to reach the statistical confidence interval \cite{audibert2010best}.
-We proposed treating the BMAB as anytime algorithm and initial results in Fig.
+We proposed treating the MAB as anytime algorithm and initial results in Fig.
 \ref{fig:grasp_quality} suggest that on average grasps at a given stopping time are better than prior methods of Monte-Carlo sampling or the approach of Kehoe et al.
@@
 \ref{fig:worst_case} there can exists pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
-Fortunately, though these cases occur with a small probability, however it is important for a practitioner to be aware of them.
-
-Another problem that was revealed in our analysis was that our current grasp metric, probability of force closure, is not dependent on the center of mass \cite{ferrari1992}.
-It only measure the probability that a grasp controller can resist any force provided it can exert an infinite force.
-One can assume that the grasp controller on a robot hand is powerful enough to apply the proper resistance, but that assumption might be invalid in some applications.
-A similar metric that is still from Beta-Bernoulli and takes center of mass into account, would be ideal for both accurate grasp quality prediction under uncertainty and the utilization of MAB algorithms.
-Recent work by Kim et al.
-developed a physics based simulator that could potentially achieve this goal \cite{kim2012physically}.
+Fortunately, though these cases occur with a small very probability, however it is important for a practitioner to be aware of them.
 
@@
 Assessing grasp quality under  uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
-In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coeffiecient and motion. 
+In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and motion. 
 A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
@@
 A pre-requisite for applying a bandit approach is to formulate a representation  of how uncertainty affects grasp parameters and thus grasp quality.
-We purpose treating this as a graphical model and use model the parameters as stochastic noise.
-Our choice of distributions though is not the focus of the paper.
-The MAB algorithm is applicable in any context of bounded reward distributions and all the theoretical results we mentioned will transfer to the Beta-Bernoulli case, or the estimation of probability of force closure.
+We propose treating this as a graphical model and model the parameters as stochastic noise.
+The MAB algorithm is then applicable in the context of bounded reward distributions.
+Initial results have shown our MAB approach it to outperform the methods of prior work Monte-Carlo and the method purposed by Kehoe et al.
+\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
 
-One of the BMAB algorithms that works well in practice, Thompson Sampling, is guaranteed to find the best grasp in a given proposal set in the limit of an infinite time \cite{agrawal2011analysis} and initial results have shown it to outperform the methods of prior work Monte-Carlo and the method purposed by Kehoe et al.
-\cite{kehoe2012estimating}.
-
-\section{Future Work}
+%\section{Future Work}
 
 As we scale to larger 3D objects the possible number of grasp candidates will be substantially larger, the more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}.
-The MAB algorithms presented above though assumed that each option is independent.
+The MAB algorithms presented above assumed that each option is independent.
 In the grasping context though spatial information about grasps could provide information about the quality of similar grasps.
-For example, if grasp $A$ is very similar with respect to some metric to grasp $B$ and grasp $B$ appears promising based on samples observed, we might be able use this information and update the prior Beta distribution of grasp $A$.
-
-MAB methods with correlated options do exist and have even been shown to achieve sub-logarithmic regret in some cases \cite{reverdy2014modeling}.
-However, there is an assumption that the correlation between the different options is known or estimated  a priori to running the algorithm.
-In the grasping context, one way to achieve this would be to learn correlations based on an offline training method \cite{andrieu2003introduction}, this might require a feature based representation though of both the proposed grasps and the object itself which could lead to many interesting research questions.
-
-Future work will also consider applying BMAB approach to grasp planners like GraspIt!
-\cite{miller2004graspit} to see if our method can handle uncertainty while working under the time constraints needed for most real time applications.
-While our results are promising, it remains to be seen how well it deals with the increased complexity of 3D models over 2D models and larger scale experiments.
-However, the BMAB model has a large amount of literature to draw from as we encounter new and more challenging problems \cite{bergemann2006bandit}.
-
+We can estimate a correlated Beta-Bernoulli distribution using an Kernel density estimation on the $\alpha$ and $\beta$ parameter \cite{goetschalckx2011continuous}.However we have to find an appropriate feature representation for a grasp, which is an exciting project for on going work.
 \bibliographystyle{IEEEtranS}

### 2015-03-02 paper.tex
add Jeff's changes worked on figures

@@
 Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
-The robot may need to rapidly plan grasps, but may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
+If the robot plans grasps using analytic methods, it would need to have an estimate of the contact locations and surface normals to estimate the quality of the proposed grasp.
+The robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
 
@@
     \centering
-     \subfloat{{\includegraphics[width=8.5cm, height=4.25cm]{figures/uncertainty_motivation.jpg} }}%
+     \subfloat{{\includegraphics[width=8.5cm, height=7cm]{matlab_figures/pfc.eps} }}%
 
@@
 Recent works have explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One option is using Monte-Carlo Integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}, but this can be computationally expensive.
-In this work, we show that it is possible to rule out grasps with low probability of force closure in only a few samples and to allocate more sampling effort to grasps that are likely to be high quality.
+One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}, but this can be computationally expensive.
+In this work, we show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
 
@@
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, for selecting grasps with high probabilty of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}, a dataset of over 1000 planar objects.
-\todo{Get within 5 of best value numbers}
-Initial results over 100 shapes suggest that on average the grasp return after a given stopping time on the number of samples is of higher quality than that of previous methods.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against Monte-Carlo integration and an adaptive sampling method proposed by Kehoe et al.
+\cite{kehoe2012toward}.
+In the task of finding grasps with high probability of force closure in a limited amount of time on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}, a dataset of over 1000 planar objects.
+\todo{Running experiments Today}
+The number of samples required to get within $5\%$ of the estimated best grasp quality in the set is $X$ samples for Thompson Sampling, an MAB Algorithm.
+For Monte-Carlo integration it is $X$ samples for $5\%$ of grasp quality and the Adpative Sampling requires  $X$ samples.
 
@@
 \subsection{MAB Model}
-The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
+The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
 Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-In a traditional MAB problem, a gambler has $K$ independent one-armed bandits, also known as slot machines.
+A traditional MAB example is a gambler has $K$ independent one-armed bandits, also known as slot machines.
 When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
@@
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
-Since then a several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.
+Since then several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling when there are two arms\cite{agrawal2011analysis}.
 
@@
 For instance a Bernoulli random variable, $\theta$, can be used to represent a binary grasping metric like force closure.
-The prior traditional placed on a Bernoulli variable is its conjugate prior the Beta distribution.
+The prior traditionally placed on a Bernoulli variable is its conjugate prior, the Beta distribution.
 Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
 
-%Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
-%See \cite{} for a review of bayesian methods in multi-armed bandit problems.
-
-%In the context of grasping, the reward for achieving force close on a sample from the uncertain parameters is a Bernoulli random variable with probabilty of success $\theta$.
-%%The distribution that describes whether an event is $\lbrace 0, 1 \rbrace$ is known as a Bernoulli distribution and can be described by the parameter $\theta$ or the probability an event occurs.
-%In the Bayesian setting we treat $\theta$ as belonging to a distribution.
-%A common choice for such a distribution is the Beta distribution, which is the conjugate prior of the Bernoulli distribution.
-%One benefit of a conjugate prior is that the posterior update of the belief distribution is of the same form as the original prior, simplifying sampling and analysis.
-%Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where $\alpha >0$ and $\beta >0$.
-%The mean of the Beta distribution is given by $\alpha/(\alpha+\beta)$.
-%To update the prior Beta distribution one adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$
-%Often the prior $\alpha =1 $ and $\beta =1$ is used before any rewards are observed, which leads to a uniform distribution on $\theta$.
-
 One benefit of the Beta prior on Bernoulli reward distributions is that updates to the belief distribution after observing rewards from arm pulls can be derived in closed form.
-Let $n_i$ denote the number of times arm $k$ has been sampled.
-Then after observing $S_i$ rewards of $1$ for arm $k$, the posterior of the Beta are $\alpha_{i, n_i} = \alpha_{i, 0} + S_i, \beta_{i, n_i} = \beta_{i, 0} + n_i - S_i$, where $\alpha_{i,0}$ and $\beta_{i,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+Let $n_k$ denote the number of times arm $k$ has been sampled.
+Then after observing $S_{n_k}$ rewards of $1$ for arm $k$, the posterior of the Beta are $\alpha_{k, n_k} = \alpha_{k, 0} + S_k, \beta_{k, n_k} = \beta_{k, 0} + n_k - S_k$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 %Given a proposed grasp plan $\Gamma_i$ with current posterior belief $\alpha_i, \beta_i$, , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
 %The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Given the current belief $\alpha_{k, n_i}, \beta_{k, n_i}$ on $\theta_k$ for an arm $k$, the algorithm can predict the probability of an event occurring on the next iteration by taking the expected value:
+Given the current belief $\alpha_{k, n_k}, \beta_{k, n_k}$ on $\theta_k$ for an arm $k$, the algorithm can predict the probability of an event occurring on the next iteration by taking the expected value:
 %Thus, we can write the expected probability of force closure as follows
@@
 
-\noindent We describe two popular Bayesian MAB algorithms below for the Beta belief distribution.
-
 \subsubsection{The Gittins Index Method} 
@@
 Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
-In the Beta-Bernoulli MAB case, the set of actions is the $K$ options and the states are the Beta prior on each option.
+In the Beta-Bernoulli MAB case, the set of actions is the $K$ options and the states are the Beta posterior on each option, or the integer values of the $\alpha$ and $\beta$ parameters.
 
@@
 However, the curse of dimensionality effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your options then your state space is exponential in $K$.
-A key insight though was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$, as shown in Algorithm 1.
+A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$, as shown in Algorithm 1.
 
@@
 
-\noindent The indices $v^i(x^i)$, computed in Equation \ref{eq:git_indices},can then be used to form a policy, where at each timestep the agent selects the option with the highest $v^i(x^i)$.
+\noindent The indices $v^i(x^i)$, computed in Equation \ref{eq:git_indices}, can then be used to form a policy, where at each timestep the agent selects the option with the highest $v^i(x^i)$.
 Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
@@
 The intuition for Thompson sampling is that the random samples of $\theta_{j,t}$ allow the method to explore.
-However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity.
+However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
 Chapelle et al.
@@
 We formulate the MAB problem for 2-dimensional objects using parallel-jaw grippers.
-Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis} for a parallel jaw gripper with jaws of width $w_j \in \mathcal{R}$ and a maximum width $w_g \in \mathcal{R}$.
+Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathcal{R}$ and a maximum width $w_g \in \mathcal{R}$.
 The two location of the jaws can be specified as $\mathbf{g_1},\mathbf{g_2} \in \mathcal{R}^2$, where $||\mathbf{g}_1 - \mathbf{g}_2|| \leq w_g$.
@@
 \subsection{Sources of Uncertainty}
-In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient.
+In this work we consider uncertainty in shape, pose, approach, and friction coefficient.
 Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
@@
 \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
-See Mahler et al. for details on how to train a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
-In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
+See Mahler et al. for details on how to estimate a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
+Following Mahler et al., we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
 For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.
@@
 For shorthand in the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
-In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ might be set from repeatability measurements for a robot~\cite{mooring1986determination}.
+In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ can be set from repeatability measurements for a robot~\cite{mooring1986determination}.
 
@@
 If the origin lies within the convex hull of $\mW$, then the grasp is in force closure~\cite{li1988task}.
-We rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
+We rank grasps using the probability of force closure given uncertainty in shape, pose, robot approach, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
 %\vspace{-2ex}
@@
 
-Mahler et al.~\cite{mahler2015gp} describe how to draw shape sample from a GPIS model.
+Mahler et al.describe how to draw shape samples from a GPIS model ~\cite{mahler2015gp}.
 We then also sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the line of action $\gamma_i(t)$~\cite{newcombe2011kinectfusion}.
@@
 More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
-We formulate the problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices in solving it.
+
+In this work, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_t$ up to a given time $T$:
+\begin{align}
+    \underset{\Gamma_1, .., \Gamma_T \in \mG}{\text{argmax }} \sum \limits_{t=1}^T P\left( F = 1 | \Gamma_t, \theta, \xi, \rho, \mu \right)   \label{eq:problem_def}
+\end{align}
+\noindent in order to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.We formulate the problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
 
 \section{Grasp Planning as a Multi-Armed Bandit}
-In this work, we frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
+We frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
 Each arm corresponds to a different grasp plan, $\Gamma_i$, and pulling an arm corresponds to sampling from the graphical model in Fig.
@@
 In Fig.
-\ref{fig:grasp_quality}, we plotted the probability of force closure,$P_F$ , of the grasp chose vs.
+\ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
 stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration).
@@
  In Fig.
-\ref{fig:pulls_per_grasp}, we plot samples per grasp quality, Gittins and Thompson appear to allocate  more samples to grasps of high quality.
+\ref{fig:pulls_per_grasp}, we plot samples per grasp quality.
+Gittins and Thompson appear to allocate  more samples to grasps of high quality.
 In contrast to Monte-Carlo, which uniformly allocate grasp samples.
-The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps.
+The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.28$\%$ of total samples.
+Monte-Carlo sampling allocates $0.01\%$ of total samples to the top 10$\%$ of grasps.
 The adaptive sampling method proposed by Kehoe et al.
-also allocates more samples to promising grasps,however it is not as efficient as the MAB methods shown.
-As illustrated by the difference in allocated samples from grasps ranked 200 to 800 in Fig.
-\ref{fig:pulls_per_grasp}.
+allocates 0.06$\%$  of total samples to the top 10 $\%$ of grasps.
 
@@
     \centering
-    \subfloat{{\includegraphics[width=16.5cm]{matlab_figures/shape_1.eps} }}%
-    \qquad
-    \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_2.eps} }}%
-             \subfloat]{{\includegraphics[width=16.5cm]{matlab_figures/shapes_5.eps} }}%
+    \includegraphics[width=16.5cm]{figures/shapes.png}%
 

### 2015-03-02 paper.tex
Added new caption to the grasp model

@@
 
-\documentclass[journal,transmag]{IEEEtran}% Comment this line out if you need a4paper
+%\documentclass[journal,transmag]{IEEEtran}% Comment this line out if you need a4paper
 
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
+\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
 
@@
 \usepackage{caption}
+\usepackage{epstopdf}
 \renewcommand{\captionfont}{\footnotesize}
@@
 \newcommand{\bd}{\mathbf{d}}
+\newcommand{\bg}{\mathbf{g}}
+\newcommand{\bj}{\mathbf{j}}
 \newcommand{\bn}{\mathbf{n}}
@@
 
-Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, and uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
-One method to represent pose uncertainty is to place a normal distribution around the location of the center of the object as well as the rotational component of the object \cite{barfoot2014Pose}.
+Many works on grasp planning focus on finding grasps by maximizing a measure of grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2007dimensionality}.
+Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992planning, miller2004graspit}.
+Past work on grasping under uncertainty has considered uncertainty in the state of a robtic gripper~\cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object~\cite{zheng2005}.
+
+Recent works have studied the effects of uncertainty in object pose and gripper positioning.%, motivated by part tolerancing from manufacturing and the use of low-cost sensors such as the Kinect.
+Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
+Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot grasps planned using determinstic wrench space metrics on shapes from the Columbia Grasp Database.
+Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose, and also found that the planned grasps were more successful on a physical robot than classical grasp metrics.
+
+Many recent works have also studied uncertainty in object shape, motivated by the use of uncertain low-cost sensors and tolerances in part manufacturing.
+Christopoulos et al.~\cite{christopoulos2007handling} sampled spline fits for 2-dimensional planar objects and ranked a set of randomly generated grasps by probability of force closure.
+Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} sampled perturbations in object shape for extruded polygonal shapes to plan push grasps for parallel-jaw grippers.
+Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty due to its ability to represent arbitrary topologies and correlations between shape uncertainty over spatial locations~\cite{dragiev2011, dragiev2011uncertainty, hollinger2013, mahler2015opt}.
+Dragiev et al.~\cite{dragiev2011} used the mean GPIS to control a grasp to reach a desired location, and extended this work to use GPIS for active tactile shape exploration during grasping~\cite{dragiev2013uncertainty}.
+Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem~\cite{mahler2015gp}.
+
+%ecently uncertainty in object pose~\cite{weisz2012pose, kim2012physically} and object shape~\cite{christopoulos2007handling, kehoe2012toward, mahler2015opt}.
+
+%Pose uncer
+%One method to represent pose uncertainty is to place a normal distribution around the location of the center of the object as well as the rotational component of the object \cite{barfoot2014Pose}.
 This approach is easy to sample from in the planar case, since each sample is from a fixed 3D Multivariate Gaussian.
 
-For shape uncertainty we used a Gaussian process implicit surface representation. 
-Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
-Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
+%For shape uncertainty, we used a Gaussian process implicit surface representation. 
+%Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
+%Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
+%Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
 
-One common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution\cite{caflisch1998monte}.
+Many works on probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
 It can be computationally expensive though to sample all proposed grasps to convergence.
@@
 However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates variance around the current estimate, which in practice could lead to good grasps being thrown away.
-We propose treating the problem as an Multi-Armed Bandit, which instead of pruning grasps away decide based on past observations what grasp to sample next \cite{barto1998reinforcement}.
+We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations~\cite{barto1998reinforcement, lai1985asymptotically}.
 
@@
 \centering
-\includegraphics[width = 8cm, height = 6.5cm]{figures/grasp_model.jpg}
-\caption{llustration of our grasping model for parallel jaw grippers on a GPIS model of a marker with shape uncertainty near the object center.
+\includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
+\caption{llustration of our grasping model for parallel jaw grippers on a mechanical switch.
 Jaw placements are illustrated by a red direction arrow and line.
-The grasp plan consists of a line of action $\gamma(t)$ with endpoints $\ba$ and $\bb$.
-When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$ with outward pointing unit surface normals $\bn_1$ and $\bn_2$.
+A grasp plan consists of 2D locations for each of the parallel-jaws $\bj_1$ and $\bj_2$.
+When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations.
 Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
-\vspace*{-4ex}
+\vspace*{-2ex}
 \label{fig:grasp_model}
@@
 
-\begin{figure}[ht!]
+\begin{figure*}[ht!]
 \centering
-\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/worst_case.eps}
+\includegraphics[width = 20cm, height = 20cm]{figures/Slide02.jpg}
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
@@
 \label{fig:worst_case}
-\end{figure}
+\end{figure*}
 

### 2015-03-05 paper.tex
latest draft

@@
 \begin{abstract}
-\textit{Abstract---}
 Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
 Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
-We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.
-We formulate grasp planning as a MAB  with finite stopping time to efficiently determine high quality grasp with respect to a probability of force closure metric.
-To evaluate MAB-based sampling, we compare with two methods previously proposed for grasping an planar object under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
-%with shape uncertainty defined by a Gaussian process implicit surface (GPIS).
-%Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
-%Uncertainty in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
-Our approach of using MAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
+We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
+We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
+We compare against Monte-Carlo sampling and an adaptive sampling approach previously proposed for grasping planar objects under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
+In simulation, Initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure in the set Thompson Sampling, an MAB algorithm, required $4.06\times$ and $6.57\times$ less samples than prior adaptive sampling and Monte-Carlo sampling, respectively.
+respectively.
 \end{abstract}
@@
 
-    \caption{ Illustration of the effects of pose and shape uncertainty on parallel-jaw grasps planned for a mechanical switch.
-Left: An RGBD camera observing the switch cannot detect the specular metal toggle and screw regions (black) and the average shape segmentation is rectangular.
-Middle: Optimizing the Ferrari-Canny quality on the estimated mean shape and pose results in an unstable grasp (red arrows) on the true object.
-Right: Selecting the grasp with the highest probability of force closure given shape and pose distributions chooses a stable grasp for the true object.
-\todo{Keep this new image or revert to old?
-Florian favored stronger motivation for uncertainty} }%
+    \caption{Comparison of the current average probability of force closure vs.
+the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
+We also demonstrate what the average probability of force closure for the approximate optimal policy.
+Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }%
     \label{fig:motivation}%
@@
 Analytic grasp quality metrics have been developed to plan grasps when all the parameters of the object and robot manipulator are exactly known.
-One common measure of stability is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
+One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
 Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
 Recent works have explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}, but this can be computationally expensive.
+ One way to compute this probability is Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}.
+Monte-Carlo methods are computationally expensive though because it requires exhaustive sampling for each grasp candidate.
 In this work, we show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
@@
 The multi-armed bandit (MAB) model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
-The MAB model is particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
-In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
-The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
-\todo{explain why} The MAB algorithms can be interpreted as an anytime algorithms, where at a provided stopping time the algorithm terminates and returns the estimated best grasp with respect to a chosen metric.
+In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
+The MAB algorithm can be interpreted as an anytime algorithm, where at a provided stopping time the algorithm terminates and returns the estimated best grasp, with respect to a chosen metric, or continues running until a user defined confidence level is met.
 
@@
 \cite{kehoe2012toward}.
-In the task of finding grasps with high probability of force closure in a limited amount of time on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}, a dataset of over 1000 planar objects.
-\todo{Running experiments Today}
-The number of samples required to get within $5\%$ of the estimated best grasp quality in the set is $X$ samples for Thompson Sampling, an MAB Algorithm.
-For Monte-Carlo integration it is $X$ samples for $5\%$ of grasp quality and the Adpative Sampling requires  $X$ samples.
+In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}.
+\todo{I am using within 2.5 percent because MC sampling doesn't get below that for the current length of the experiment}
+In simulation, initial results  showed that given 1000 randomly selected parallel jaw grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure in the set, Thompson Sampling, an MAB algorithm, required $4.06\times$ and $6.57\times$ less samples than prior adaptive sampling and Monte-Carlo sampling, respectively.
 
@@
 However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates variance around the current estimate, which in practice could lead to good grasps being thrown away.
-We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations~\cite{barto1998reinforcement, lai1985asymptotically}.
+We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead of pruning grasps away~\cite{barto1998reinforcement, lai1985asymptotically}.
 
@@
 We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
-In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantities are given.
+We consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantities are given and can be sampled from.
 
@@
 \subsection{Candidate Grasp Model}
-\todo{make anitpodal}
 The grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
@@
 Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathcal{R}$ and a maximum width $w_g \in \mathcal{R}$.
-The two location of the jaws can be specified as $\mathbf{g_1},\mathbf{g_2} \in \mathcal{R}^2$, where $||\mathbf{g}_1 - \mathbf{g}_2|| \leq w_g$.
-We define a grasp plan consisting of the tuple $\Gamma = \lbrace g_1, g_2 \rbrace$.
+The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathcal{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$.
+We define a grasp plan consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.
 
 %We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
-
+\todo{The next section was crossed out in your notes, I'm still not clear whats wrong with it. Can you elaborate more?}
 Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
 We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^d$, the object center of mass as $\bz \in \mathbb{R}^d$ and the friction coefficient as $\mu$.
-The center of mass may be computed based on a known mass density of the object.
-Together these form the set of grasp parameters $g = (\bc_1,\bc_2, \bn_1, \bn_2, \bz,\mu)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object.
+Together these form the set of grasp parameters $g = (\bc_1,\bc_2, \bn_1, \bn_2, \bz,\mu)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.
 
@@
 \caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
-As illustrated uncertainty in pose, motion and shape effect the the contacts and surface normals that makes up the grasp.
+As illustrated uncertainty in pose, motion and shape affect the contacts and surface normals that makes up the grasp.
 Friction coefficient is independent of this relationship.
-The box around contact and normals means there are repeated nodes, in this case we have $m=2$ corresponding to the two jaws in the gripper.
+The box around contact and normals means they are repeated nodes, in this case we have $m=2$ corresponding to the two jaws in the gripper.
 }
@@
 
-In this work, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_t$ up to a given time $T$:
+To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_t$ up to a given time $T$:
 \begin{align}
@@
 \end{align}
-\noindent in order to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.We formulate the problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
+\noindent This tries to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
 
@@
 
-\todo{think of stopping criteria, thats not anytime}
-One can think of the proposed algorithm as an anytime algorithm, it can be stopped at anytime during its computation and return the current estimate of the best grasp or wait until its estimate of the best grasp is within some set confidence.
-The confidence interval can be determined via the variance of the Beta distribution, which is defined as
+One can think of the proposed algorithm as an anytime algorithm.
+It can be stopped at anytime during its computation and return the current estimate of the best grasp or wait until a $95\%$ confidence interval is smaller than some threshold $\epsilon$.
+Using the quantile function of the beta distribution, $B$, we can measure the $95\%$ confidence interval as:
 
 \vspace{-2ex}
-\begin{align}
-\mbox{Var}(P_F(\Gamma_i)) = \frac{\alpha\beta}{(\alpha+\beta)^2(\alpha+\beta+1)}
+\begin{align}\label{eq:confidence}
+B(0.05,\alpha,\beta) \leq P_F(\Gamma_i)) \leq B(0.95,\alpha,\beta)
 \end{align}
 
-We then run the algorithm until the estimated best grasp at time $t$ has $\mbox{Var}(P_F(\Gamma_i))$
+\vspace{-2ex}
+.
 
@@
 The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-\todo{Figure out why these parameters were set, or think of more logical settings} The noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
-We thought these were reasonable values based on the size of the 40x40 workspace and the amount of noise expected in industrial applications. 
+For illustrative purposes, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
 We us the GPIS-Blur visualization technique \cite{mahler2015gp}.
@@
 \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration).
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration).
 We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation.
@@
 \ref{fig:shape_samples}.
-Interestingly in Fig \ref{fig:grasp_quality}, Gittins and Thompson select at stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
+Interestingly in Fig.
+\ref{fig:grasp_quality}, Gittins and Thompson select at stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
 
@@
 allocates 0.06$\%$  of total samples to the top 10 $\%$ of grasps.
+
+ The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval around the estimated best grasp is below a set threshold $\epsilon$.
+We plot the confidence intervals around the return grasp vs.
+the number of samples drawn in Fig.
+\ref{fig:confidence} for Thompson Sampling, the adaptive sampling method\cite{kehoe2012toward} and Monte-Carlo Sampling.
+As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
+This can be explained by the fact that more samples are allocated on average to grasp returned at each iteration, which is illustrated in Fig.
+\ref{fig:pulls_per_grasp}.
 
@@
 
+\begin{figure}[ht!]
+\centering
+\includegraphics[width = 9cm, height = 9cm]{matlab_figures/confidence_bounds.eps}
+\caption{ \footnotesize \todo{fix legend.
+We might want to condense Fig 6 and Fig.
+4.
+The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, the adaptive sampling method and Monte-Carlo sampling.
+The sharper decrease in confidence interval corresponds to more samples being allocated for the return grasp.
+}
+
+\vspace*{-10pt}
+\label{fig:confidence}
+\end{figure}
+
 \begin{figure*}%
@@
 
-\subsection{Sensitivity Analysis }
+\subsection{Sensitivity Analysis }\label{sec:sensitivity}
 \todo{need to redo with larger number of shapes}
-We now will show how well  Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose.
+We now will show how well  Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose and use that to set the parameters for future experiments .
 The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
@@
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \centering
-\includegraphics[width = 20cm, height = 20cm]{figures/Slide02.jpg}
+\includegraphics[width = 8cm, height = 9cm]{matlab_figures/worst_case.eps}
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
@@
 \label{fig:worst_case}
-\end{figure*}
+\end{figure}
 
@@
 
-\section{Limitations}
+\section{Discussion and Future Work }
 
-Our multi-armed bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
-Future work will be building an efficient construction of GPIS to scale to 3D and test the bandit method there.
-Since currently the bandit algorithm doesn't utilize correlations between grasps, we are throwing away a lot of information that could be useful for choosing what to grasp to sample next.
-
-We proposed treating the MAB as anytime algorithm and initial results in Fig.
-\ref{fig:grasp_quality} suggest that on average grasps at a given stopping time are better than prior methods of Monte-Carlo sampling or the approach of Kehoe et al.
+Assessing grasp quality under  uncertainty can be computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
+In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
+A key insight from our work is that uniformly allocating samples to grasps is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
+Initial results have shown our MAB approach to outperform the methods of prior work, Monte-Carlo sampling and the adaptive sampling approach proposed by Kehoe et al.
+\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
  However, as shown in Fig.
@@
 Fortunately, though these cases occur with a small very probability, however it is important for a practitioner to be aware of them.
-
-\section{Conclusion}
-Assessing grasp quality under  uncertainty is computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
-In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and motion. 
-A key insight from our work is that uniformly allocating samples to grasps is inefficient, and
- we found that a MAB approach prioritizes evaluation of high-quality grasps while quickly pruning-out obviously poor grasps.
-A pre-requisite for applying a bandit approach is to formulate a representation  of how uncertainty affects grasp parameters and thus grasp quality.
-We propose treating this as a graphical model and model the parameters as stochastic noise.
-The MAB algorithm is then applicable in the context of bounded reward distributions.
-Initial results have shown our MAB approach it to outperform the methods of prior work Monte-Carlo and the method purposed by Kehoe et al.
-\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
-
-%\section{Future Work}
 

### 2015-03-05 paper.tex
added stuff

@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v5 Feb 18, 2015 ] }
+Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v6 Feb 18, 2015 ] }
 
@@
 %We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
-\todo{The next section was crossed out in your notes, I'm still not clear whats wrong with it. Can you elaborate more?}
+\todo{The next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
 Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
@@
 The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-For illustrative purposes, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
-We us the GPIS-Blur visualization technique \cite{mahler2015gp}.
+For illustrative purposes of noise, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
 We performed experiments for the case of two hard contacts in 2-D.
@@
 prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-To illustrate the difference in grasp quality returned at a stopping time of $T = 9000$,  we show the grasps selected for three randomly selected objects for all methods listed in Fig.
+\todo{THis might still be vague} For illustrative purposes we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average and show the grasps selected for three randomly selected objects for the tried methods in Fig.
 \ref{fig:shape_samples}.
 Interestingly in Fig.
-\ref{fig:grasp_quality}, Gittins and Thompson select at stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
+\ref{fig:grasp_quality}, Gittins and Thompson select a stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
 
@@
 The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.28$\%$ of total samples.
-Monte-Carlo sampling allocates $0.01\%$ of total samples to the top 10$\%$ of grasps.
-The adaptive sampling method proposed by Kehoe et al.
-allocates 0.06$\%$  of total samples to the top 10 $\%$ of grasps.
+Monte-Carlo sampling and the adaptive sampling method allocate $0.01\%$  and $0.06\%$ of total samples, respectively.
 
- The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval around the estimated best grasp is below a set threshold $\epsilon$.
+ The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval, Eq.
+\ref{eq:confidence}, around the returned grasp is below a set threshold $\epsilon$.
 We plot the confidence intervals around the return grasp vs.
@@
 \ref{fig:confidence} for Thompson Sampling, the adaptive sampling method\cite{kehoe2012toward} and Monte-Carlo Sampling.
-As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
-This can be explained by the fact that more samples are allocated on average to grasp returned at each iteration, which is illustrated in Fig.
+\todo{Still thinking of a way to quantify this} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
+This can be explained by the fact that in our experiments the MAB algorithms allocate more samples on average to grasp returned at each iteration, which is illustrated in Fig.
 \ref{fig:pulls_per_grasp}.
@@
 the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
+We demonstrate this for Thompson, Gittins, Monte-Carlo and the Adaptive Sampling approach \cite{kehoe2012toward}.
 We also demonstrate what the average probability of force closure for the approximate optimal policy.
@@
 For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-As you can see in Fig.
-\ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
+As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
 

### 2015-03-05 paper.tex
Fixed some refs in first seciton of related work.

--- 2015-03-05 paper.tex
@@
 Recent works have explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
- One way to compute this probability is Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}.
-Monte-Carlo methods are computationally expensive though because it requires exhaustive sampling for each grasp candidate.
+One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012toward}, but this can be computationally expensive.
 In this work, we show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
@@
 
-Many works on grasp planning focus on finding grasps by maximizing a measure of grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2007dimensionality}.
-Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992planning, miller2004graspit}.
+Many works on grasp planning focus on finding grasps by maximizing a measure of grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2009}.
+Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
 Past work on grasping under uncertainty has considered uncertainty in the state of a robtic gripper~\cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object~\cite{zheng2005}.
@@
 Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} sampled perturbations in object shape for extruded polygonal shapes to plan push grasps for parallel-jaw grippers.
-Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty due to its ability to represent arbitrary topologies and correlations between shape uncertainty over spatial locations~\cite{dragiev2011, dragiev2011uncertainty, hollinger2013, mahler2015opt}.
+Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty due to its ability to represent arbitrary topologies and correlations between shape uncertainty over spatial locations~\cite{dragiev2011, dragiev2013uncertainty, hollinger2013, mahler2015gp}.
 Dragiev et al.~\cite{dragiev2011} used the mean GPIS to control a grasp to reach a desired location, and extended this work to use GPIS for active tactile shape exploration during grasping~\cite{dragiev2013uncertainty}.

### 2015-03-10 paper.tex
current stuff

@@
 
-\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
+\documentclass[10pt, conference]{ieeeconf}      % Use this line for a4 paper
 
@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v6 Feb 18, 2015 ] }
+Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v7 Feb 18, 2015 ] }
 
@@
 We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
-We compare against Monte-Carlo sampling and an adaptive sampling approach previously proposed for grasping planar objects under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
-In simulation, Initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure in the set Thompson Sampling, an MAB algorithm, required $4.06\times$ and $6.57\times$ less samples than prior adaptive sampling and Monte-Carlo sampling, respectively.
-respectively.
+We compare against Monte-Carlo sampling and an adaptive sampling approach, that reduces the set based on a current estimate of sample mean,previously proposed for grasping planar objects under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
+In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean based adaptive sampling approach previously used.
 \end{abstract}
@@
 Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
-If the robot plans grasps using analytic methods, it would need to have an estimate of the contact locations and surface normals to estimate the quality of the proposed grasp.
+Planning grasps using analytic methods, requires the contact locations and surface normals.
 The robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
@@
 
-    \caption{Comparison of the current average probability of force closure vs.
+    \caption{\todo{decide on a name for Ben's method and try a variance approach as well}Comparison of the current average probability of force closure vs.
 the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
+We demonstrate this for Thompson, Gittins, Monte-Carlo and a prior Adaptive Sampling approach \cite{kehoe2012toward}.
 We also demonstrate what the average probability of force closure for the approximate optimal policy.
@@
 
-Analytic grasp quality metrics have been developed to plan grasps when all the parameters of the object and robot manipulator are exactly known.
 One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
 Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
-Recent works have explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012toward}, but this can be computationally expensive.
-In this work, we show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
+Recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
+One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012toward}, but this can be computationally expensive due to the need to exhaustively sample every grasp candidate.
+We show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
 
@@
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against Monte-Carlo integration and an adaptive sampling method proposed by Kehoe et al.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against Monte-Carlo integration and an adaptive sampling method, which reduced the set size based on sample mean, proposed by Kehoe et al.
 \cite{kehoe2012toward}.
 In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}.
-\todo{I am using within 2.5 percent because MC sampling doesn't get below that for the current length of the experiment}
-In simulation, initial results  showed that given 1000 randomly selected parallel jaw grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure in the set, Thompson Sampling, an MAB algorithm, required $4.06\times$ and $6.57\times$ less samples than prior adaptive sampling and Monte-Carlo sampling, respectively.
+In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean adaptive sampling approach previously used .
 
@@
 
-Many works on grasp planning focus on finding grasps by maximizing a measure of grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2009}.
+Most research on grasp planning focuses on finding grasps by maximizing grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2009}.
 Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
@@
 
-Recent works have studied the effects of uncertainty in object pose and gripper positioning.%, motivated by part tolerancing from manufacturing and the use of low-cost sensors such as the Kinect.
+Recent work has studied the effects of uncertainty in object pose and gripper positioning.%, motivated by part tolerancing from manufacturing and the use of low-cost sensors such as the Kinect.
 Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
-Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot grasps planned using determinstic wrench space metrics on shapes from the Columbia Grasp Database.
+Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot grasps planned using deterministic wrench space metrics on objects from the Columbia Grasp Database.
 Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose, and also found that the planned grasps were more successful on a physical robot than classical grasp metrics.
 
-Many recent works have also studied uncertainty in object shape, motivated by the use of uncertain low-cost sensors and tolerances in part manufacturing.
+Recent work has also studied uncertainty in object shape, motivated by the use of uncertain low-cost sensors and tolerances in part manufacturing.
 Christopoulos et al.~\cite{christopoulos2007handling} sampled spline fits for 2-dimensional planar objects and ranked a set of randomly generated grasps by probability of force closure.
-Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} sampled perturbations in object shape for extruded polygonal shapes to plan push grasps for parallel-jaw grippers.
+Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} sampled perturbations in shape for extruded polygonal objects to plan push grasps for parallel-jaw grippers.
 Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty due to its ability to represent arbitrary topologies and correlations between shape uncertainty over spatial locations~\cite{dragiev2011, dragiev2013uncertainty, hollinger2013, mahler2015gp}.
@@
 
-Many works on probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
 This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
 It can be computationally expensive though to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps.
-However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates variance around the current estimate, which in practice could lead to good grasps being thrown away.
-We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead of pruning grasps away~\cite{barto1998reinforcement, lai1985asymptotically}.
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure, which tries to avoid sampling grasps that seem to have lower quality based on past observation.
+However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize variance around the current estimate, which can discard good grasps.
+We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead ~\cite{barto1998reinforcement, lai1985asymptotically}.
 
 \subsection{MAB Model}
+\todo{You mentioned this section might seem condescening to the OR community. It be great if you can point out specifics here}
 The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
@@
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
-Since then several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling when there are two arms\cite{agrawal2011analysis}.
+Since then several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for the two arm case\cite{agrawal2011analysis}.
+\todo{The last result is actually only a few years ago.
+I can talk about contextual bandits for the sake of other recent information, but we don't use them and we are short on space.
+So I am wondering your opinion here}
 
@@
  Set $F_{I_t,t+1} = F_{I_t,t} + 1 - R_{I_t,t}$\\
- Set $x_k = \lbrace 1 + S{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
+ Set $x_k = \lbrace 1 + S_{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
 }
@@
 \subsubsection{Thompson Sampling}
-Computation of the Gittins indices can increase exponentially in as the discount factor approaches $1$, and therefore it is not ideal to use in most cases. 
+Computation of the Gittins indices can increase exponentially as the discount factor approaches $1$, and therefore it is not ideal to use in most cases. 
 Thompson sampling is a less computationally expensive alternative.
@@
 \todo{The next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
-Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
+Given a grasp plan and a deterministic object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
 We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^d$, the object center of mass as $\bz \in \mathbb{R}^d$ and the friction coefficient as $\mu$.
@@
 A grasp plan consists of 2D locations for each of the parallel-jaws $\bj_1$ and $\bj_2$.
-When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations.
+When following the grasp plan, the jaws contact the object at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations.
 Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
@@
 We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
-Formally, let $\hat{\by} = \frac{1}{2} (\ba + \bb)$ denote the center of a planned line of action $\gamma(t)$ and $\hat{\psi}$ denote the angle that the planned line $\bb - \ba$ makes with the x-axis of the 2D coordinate system on our shape representation.
+Formally, let $\hat{\by} = \frac{1}{2} (\bj_1 + \bj_2)$ denote the center of a planned grasp axis and $\hat{\psi}$ denote the angle that the planned axis $\bj_1 - \bj_2$ makes with the x-axis of the 2D coordinate system on our shape representation.
 We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
@@
 Mahler et al.describe how to draw shape samples from a GPIS model ~\cite{mahler2015gp}.
-We then also sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the line of action $\gamma_i(t)$~\cite{newcombe2011kinectfusion}.
+We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the line of action $\gamma_i(t)$~\cite{newcombe2011kinectfusion}.
 Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.
@@
 This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
-More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
+More recent work has considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
 
@@
 prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-\todo{THis might still be vague} For illustrative purposes we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average and show the grasps selected for three randomly selected objects for the tried methods in Fig.
+
+\todo{THis might still be vague} For illustrative purposes of an anytime algorithm,  we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average, and show the grasps selected for three randomly selected objects for the tried methods in Fig.
 \ref{fig:shape_samples}.
@@
 In contrast to Monte-Carlo, which uniformly allocate grasp samples.
-The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.28$\%$ of total samples.
+The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.23$\%$ of total samples.
 Monte-Carlo sampling and the adaptive sampling method allocate $0.01\%$  and $0.06\%$ of total samples, respectively.
@@
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
-the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+the stopping time $T_s$.Graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.
 We demonstrate this for Thompson, Gittins, Monte-Carlo and the Adaptive Sampling approach \cite{kehoe2012toward}.
@@
 \caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins).
-Graph is averaged over 100 shapes from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
 The best grasps are ranked 1 and worst are 1000.
@@
 \includegraphics[width = 9cm, height = 9cm]{matlab_figures/confidence_bounds.eps}
-\caption{ \footnotesize \todo{fix legend.
-We might want to condense Fig 6 and Fig.
+\caption{ \footnotesize \todo{We might want to condense Fig 6 and Fig.
 4.
 The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, the adaptive sampling method and Monte-Carlo sampling.
+Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
 The sharper decrease in confidence interval corresponds to more samples being allocated for the return grasp.
@@
 
-    \caption{\todo{Need to change this figure, wondering what should be conveyed here}Three shapes shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized according to the method described in \cite{mahler2015gp}.
-The four methods (Monte-Carlo, Kehoe's, Thompson and Gittins) were all run until a stopping time of 9000 evaluations with a uniformly initialized grasp set of $|G|=1000$.
+    \caption{\todo{Need to change this figure, wondering what should be conveyed here}Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
+The four methods (Monte-Carlo, Kehoe's, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a uniformly initialized grasp set of $|G|=1000$.
 We also showed the estimated best grasp in the set.
 The grasps and the quality each one found is shown above.
-In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $9000$, however at the last shape there is a difference of $2\%$ grasp quality.
+In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $10,000$, however at the last shape there is a difference of $2\%$ grasp quality.
 }%
@@
 the stopping time $T_s$ for the pathological case where the samples are sorted to be misleading.
-The graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
+The graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.
 We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
@@
  \hline
-Uncertainty Type & Low Uncertainty (Iterations) & Medium Uncertainty (Iterations) & High Uncertainty (Iterations)\\
+Uncertainty Type & Low Uncertainty ($\#$ of Iterations) & Medium Uncertainty ($\#$ Iterations) & High Uncertainty ($\#$ of Iterations)\\
  \hline
@@
 \end{tabular}
-   \caption { \footnotesize  Sensitivity Analysis for convergence to estimated best grasp for Thompson Sampling under rotational variance $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 10 shapes from the Brown Vision Lab Data set.
+   \caption { \footnotesize  Sensitivity Analysis for convergence to estimated best grasp for Thompson Sampling under rotational variance $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 10 objects from the Brown Vision Lab Data set.
 The sensitivity analysis shows that large variance in translational uncertainty in pose can increase the amount of iterations needed for the bandit algorithm to converge to the highest quality grasp in the set.

### 2015-03-11 paper.tex
Changed the figures to scales

@@
     \centering
-     \subfloat{{\includegraphics[width=8.5cm, height=7cm]{matlab_figures/pfc.eps} }}%
+     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc.eps} }}%
 
@@
 \centering
-\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/pfc.eps}
+\includegraphics[scale=0.25]{matlab_figures/pfc.eps}
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
@@
 \centering
-\includegraphics[width = 9cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
+\includegraphics[scale=0.25]{matlab_figures/pulls_per_grasp.eps}
 \caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins).
@@
 \centering
-\includegraphics[width = 9cm, height = 9cm]{matlab_figures/confidence_bounds.eps}
+\includegraphics[scale=0.25]{matlab_figures/confidence_bounds.eps}
 \caption{ \footnotesize \todo{We might want to condense Fig 6 and Fig.
@@
 \centering
-\includegraphics[width = 8cm, height = 9cm]{matlab_figures/worst_case.eps}
+\includegraphics[scale=0.25]{matlab_figures/worst_case.eps}
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.

### 2015-03-11 paper.tex
changed monte-carlo to uniform

--- 2015-03-10 paper.tex
@@
 We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
-We compare against Monte-Carlo sampling and an adaptive sampling approach, that reduces the set based on a current estimate of sample mean,previously proposed for grasping planar objects under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
+We compare against two previously proposed methods for grasp selection uniform allocation, or uniformly selecting samples, and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps.
+We  consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
 In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean based adaptive sampling approach previously used.
@@
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against Monte-Carlo integration and an adaptive sampling method, which reduced the set size based on sample mean, proposed by Kehoe et al.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation, or randomely sampling grasps, and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al.
 \cite{kehoe2012toward}.
@@
 It can be computationally expensive though to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure, which tries to avoid sampling grasps that seem to have lower quality based on past observation.
-However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize variance around the current estimate, which can discard good grasps.
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure known as Iterative Pruning, which at a set iteration discards a subset of the grasps that seem unlikely to be of high quality .
+However, the method pruned grasps using only the sample mean and did not utilize variance around the current estimate, which can discard good grasps.
 We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead ~\cite{barto1998reinforcement, lai1985asymptotically}.
@@
 \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration).
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
+Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
+Iterative Pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
 We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation.
-The adaptive sampling method of Kehoe et al.
-prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
 
-\todo{THis might still be vague} For illustrative purposes of an anytime algorithm,  we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average, and show the grasps selected for three randomly selected objects for the tried methods in Fig.
+\todo{This might still be vague} As illustrated in Fig.
+\ref{fig:grasp_quality}, Gittins and Thompson select a grasp at stopping time $T_s$ that on average has a higher probability of force closure than uniform allocation and Iterative Pruning .
+For illustrative purposes of an anytime algorithm,  we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average, and for each method visualize the grasp selected in Fig.
 \ref{fig:shape_samples}.
-Interestingly in Fig.
-\ref{fig:grasp_quality}, Gittins and Thompson select a stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .
-
- In Fig.
-\ref{fig:pulls_per_grasp}, we plot samples per grasp quality.
-Gittins and Thompson appear to allocate  more samples to grasps of high quality.
-In contrast to Monte-Carlo, which uniformly allocate grasp samples.
-The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.23$\%$ of total samples.
-Monte-Carlo sampling and the adaptive sampling method allocate $0.01\%$  and $0.06\%$ of total samples, respectively.
 
@@
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Thompson Sampling, the adaptive sampling method\cite{kehoe2012toward} and Monte-Carlo Sampling.
+\ref{fig:confidence} for Thompson Sampling, Iterative Pruning\cite{kehoe2012toward} and uniform allocation.
 \todo{Still thinking of a way to quantify this} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
-This can be explained by the fact that in our experiments the MAB algorithms allocate more samples on average to grasp returned at each iteration, which is illustrated in Fig.
-\ref{fig:pulls_per_grasp}.
+
+ In Fig.
+\ref{fig:pulls_per_grasp}, we plot samples per grasp quality.
+Gittins and Thompson appear to allocate  more samples to grasps of high quality in contrast to uniform allocation and Iterative Pruning.
+The ability to find grasps with a higher probability of force  faster and have a smaller confidence interval on the returned quantity can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples.
+Uniform allocation and Iterative Pruning allocate $1\%$  and $6\%$ of total samples, respectively.
 
@@
 In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
-A key insight from our work is that uniformly allocating samples to grasps is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
-Initial results have shown our MAB approach to outperform the methods of prior work, Monte-Carlo sampling and the adaptive sampling approach proposed by Kehoe et al.
-\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
+A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
+Initial results have shown our MAB approach to outperform the methods of prior work, uniform allocation and Iterative Pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
  However, as shown in Fig.
@@
 
-As we scale to larger 3D objects the possible number of grasp candidates will be substantially larger, the more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}.
-The MAB algorithms presented above assumed that each option is independent.
+As we scale to 3D objects the possible number of grasp candidates will be substantially larger.
+The more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}.
+However, the MAB algorithms presented above assumed that each option is independent.
 In the grasping context though spatial information about grasps could provide information about the quality of similar grasps.
-We can estimate a correlated Beta-Bernoulli distribution using an Kernel density estimation on the $\alpha$ and $\beta$ parameter \cite{goetschalckx2011continuous}.However we have to find an appropriate feature representation for a grasp, which is an exciting project for on going work.
+We can estimate a correlated Beta-Bernoulli distribution using an Kernel density estimation on the $\alpha$ and $\beta$ parameter \cite{goetschalckx2011continuous}.However we would have to find an appropriate feature representation for a grasp that can accurately represent this.
+Learning these features and applying these to MAB methods will be an exciting project for future work.
 \bibliographystyle{IEEEtranS}

### 2015-03-11 paper.tex
got figures

@@
 the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-We demonstrate this for Thompson, Gittins, Monte-Carlo and a prior Adaptive Sampling approach \cite{kehoe2012toward}.
-We also demonstrate what the average probability of force closure for the approximate optimal policy.
+We demonstrate this for Thompson, Gittins, uniform allocation and Iterative Pruning \cite{kehoe2012estimating}.
+We also demonstrate what the average highest probability of force closure is when the brute force approach of exhaustively sampling each candidate grasp is used.
 Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }%
@@
 
-Recent work has studied the effects of uncertainty in object pose and gripper positioning.%, motivated by part tolerancing from manufacturing and the use of low-cost sensors such as the Kinect.
+Recent work has studied the effects of uncertainty in object pose and gripper positioning.
  Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
@@
 To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure known as Iterative Pruning, which at a set iteration discards a subset of the grasps that seem unlikely to be of high quality .
-However, the method pruned grasps using only the sample mean and did not utilize variance around the current estimate, which can discard good grasps.
+However, the method pruned grasps using only the sample mean and did not utilize any confidence interval around the current estimate, which can discard good grasps.
 We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead ~\cite{barto1998reinforcement, lai1985asymptotically}.
@@
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
-Since then several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for the two arm case\cite{agrawal2011analysis}.
+Since then several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for the 2 arm case\cite{agrawal2011analysis}.
 \todo{The last result is actually only a few years ago.
@@
 \subsubsection{The Gittins Index Method} 
-One MAB method is to treat the problem as an Markov Decision Process (MDP) and use Markov Decision theory.
+One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
 Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
@@
 Methods such as Value Iteration can compute optimal policies for an MDP with respect to the discount factor $\gamma$ when all states, actions, and expected rewards can be enumerated~\cite{weber1992gittins,barto1998reinforcement}.
-However, the curse of dimensionality effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your options then your state space is exponential in $K$.
+However, the curse of dimensionality effects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in $K$.
 A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$, as shown in Algorithm 1.
@@
 \subsubsection{Thompson Sampling}
-Computation of the Gittins indices can increase exponentially as the discount factor approaches $1$, and therefore it is not ideal to use in most cases. 
+Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$, and therefore it is not ideal to use in most cases. 
 Thompson sampling is a less computationally expensive alternative.
@@
 A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
-A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
+A GPIS is a Gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
 \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
@@
 Gittins and Thompson appear to allocate  more samples to grasps of high quality in contrast to uniform allocation and Iterative Pruning.
-The ability to find grasps with a higher probability of force  faster and have a smaller confidence interval on the returned quantity can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples.
+The ability to find grasps with a higher probability of force  faster and have a smaller confidence interval on the returned quantity can be explain by the fact that in our experiments the MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples.
 Uniform allocation and Iterative Pruning allocate $1\%$  and $6\%$ of total samples, respectively.
@@
 \caption{ \footnotesize Comparison of the current average probability of force closure vs.
-the stopping time $T_s$.Graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.
-We demonstrate this for Thompson, Gittins, Monte-Carlo and the Adaptive Sampling approach \cite{kehoe2012toward}.
-We also demonstrate what the average probability of force closure for the approximate optimal policy.
+the stopping time $T_s$.Graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.We demonstrate this for Thompson, Gittins, uniform allocation and Iterative Pruning \cite{kehoe2012estimating}.
+We also demonstrate what the average highest probability of force closure is when the brute force approach of exhaustively sampling each candidate grasp is used.
 Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
@@
 \includegraphics[scale=0.25]{matlab_figures/pulls_per_grasp.eps}
-\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins).
+\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Thompson, Gittins, uniform allocation and Iterative Pruning).
 Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
@@
 4.
-The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, the adaptive sampling method and Monte-Carlo sampling.
+The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, Iterative Pruning and uniform allocation.
 Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
@@
     \caption{\todo{Need to change this figure, wondering what should be conveyed here}Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
-The four methods (Monte-Carlo, Kehoe's, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a uniformly initialized grasp set of $|G|=1000$.
-We also showed the estimated best grasp in the set.
+The four methods (uniform allocation, Iterative Pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|G|=1000$.
+We also show the grasp returned by the brute force approach of exhaustively sampling every grasp in the set.
 The grasps and the quality each one found is shown above.
@@
 The graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.
-We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}.
-We also demonstrate what the average probability of force closure for the approximate optimal policy.
+We demonstrate this for Thompson, Gittins, uniform allocation and Iterative Pruning \cite{kehoe2012estimating}.
+We also demonstrate what the average highest probability of force closure is when the brute force approach of exhaustively sampling each candidate grasp is used.
 Empirically, it appears that when samples are misleading the best policy is uniform allocation.

### 2015-03-11 paper.tex
Made some wording changes

@@
 Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
-Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
+A popular approach to grasp planning under uncertainty is to use Monte-Carlo integration to rank a set of potential grasp, but this may require a large number of samples to converge, even for planar models.
 We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
-We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
-We compare against two previously proposed methods for grasp selection uniform allocation, or uniformly selecting samples, and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps.
+We formulate grasp planning as a MAB  to efficiently determine high quality grasps with respect to the probability of force closure.
+We compare against two previously proposed methods for grasp selection: uniform allocation, or uniformly selecting samples, and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps.
 We consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
-In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean based adaptive sampling approach previously used.
+Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruing to get within $2.5\%$ of the estimated highest probability of force closure in the set over 1000 randomly selected grasps averaged over 100 shapes.
 \end{abstract}
@@
 Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
-Planning grasps using analytic methods, requires the contact locations and surface normals.
-The robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
+Planning grasps using analytic methods requires the contact locations and surface normals.
+However, robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
 
@@
 One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012toward}, but this can be computationally expensive due to the need to exhaustively sample every grasp candidate.
-We show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
+We show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps have a higher estimated probablity of force closure given the current samples.
 
@@
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation, or randomely sampling grasps, and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation, or randomly sampling grasps, and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al.
 \cite{kehoe2012toward}.
@@
 
-Most research on grasp planning focuses on finding grasps by maximizing grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2009}.
+Most research on grasp planning focuses on finding grasps by maximizing a grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2009}.
 Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
-Past work on grasping under uncertainty has considered uncertainty in the state of a robtic gripper~\cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object~\cite{zheng2005}.
+Past work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
 
@@
 
-Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo integration to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
 This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
@@
 
-\vspace{-2ex}
-
 \subsection{Grasp Quality}\label{sec:grasp_sample}
@@
 \end{align}
-\noindent This tries to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
+\noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.
+We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
 
@@
 \vspace{-2ex}
-.
-
- .
 \section{Simulation Experiments}
-We used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.Examples of the images can be seen in \ref{fig:shape_samples}.
-We down sampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+We used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.
+Examples of the images can be seen in \ref{fig:shape_samples}. 
+We downsampled each image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
 The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
@@
 We performed experiments for the case of two hard contacts in 2-D.
-We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
+We drew random grasp plans $\Gamma$ by sampling the angle of the grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
 
@@
 \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods: Thompson sampling, Gittins indices, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
@@
 
- The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval, Eq.
-\ref{eq:confidence}, around the returned grasp is below a set threshold $\epsilon$.
-We plot the confidence intervals around the return grasp vs.
+The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$.
+We plot the confidence intervals around the returned grasp vs.
 the number of samples drawn in Fig.
@@
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
@@
 \todo{need to redo with larger number of shapes}
-We now will show how well  Thompson Sampling perform under a variation in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose and use that to set the parameters for future experiments .
+We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose and use that to set the parameters for future experiments .
 The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
@@
 For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
+As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation and an increased noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
 

### 2015-03-12 paper.tex
Sachin's feedback

--- 2015-03-11 paper.tex
@@
 
-    \caption{\todo{decide on a name for Ben's method and try a variance approach as well}Comparison of the current average probability of force closure vs.
+    \caption{Comparison of the current average probability of force closure vs.
 the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
@@
 Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }%
-    \label{fig:motivation}%
+    \label{fig:grasp_quality}
 \end{figure}
@@
 
-%ecently uncertainty in object pose~\cite{weisz2012pose, kim2012physically} and object shape~\cite{christopoulos2007handling, kehoe2012toward, mahler2015opt}.
-
-%Pose uncer
-%One method to represent pose uncertainty is to place a normal distribution around the location of the center of the object as well as the rotational component of the object \cite{barfoot2014Pose}.
-This approach is easy to sample from in the planar case, since each sample is from a fixed 3D Multivariate Gaussian.
-
-%For shape uncertainty, we used a Gaussian process implicit surface representation. 
-%Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
-%Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-%Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
-
-Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
+Some probabilistic grasp quality measures, such as probability of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
 This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
@@
 
-At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the arm selected.
+At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the selected arm.
 Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
@@
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}.
-Since then several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for the 2 arm case\cite{agrawal2011analysis}.
-\todo{The last result is actually only a few years ago.
-I can talk about contextual bandits for the sake of other recent information, but we don't use them and we are short on space.
-So I am wondering your opinion here}
 
@@
 We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) ~\cite{chapelle2011empirical, bachman2013greedy}.
-Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving near the lower bound on the asymptotic rate of convergence in regret described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
+Theoretical results have shown that several algorithms are capable of achieving near the lower bound on the asymptotic rate of convergence in regret described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
 %However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
@@
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
-For instance a Bernoulli random variable, $\theta$, can be used to represent a binary grasping metric like force closure.
+For instance a Bernoulli random variable, $p$, can be used to represent a binary grasping metric like force closure.
 The prior traditionally placed on a Bernoulli variable is its conjugate prior, the Beta distribution.
@@
 Let $n_k$ denote the number of times arm $k$ has been sampled.
-Then after observing $S_{n_k}$ rewards of $1$ for arm $k$, the posterior of the Beta are $\alpha_{k, n_k} = \alpha_{k, 0} + S_k, \beta_{k, n_k} = \beta_{k, 0} + n_k - S_k$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+Then after observing $S_{k,n}$ rewards of $1$ for arm $k$ after $n$ samples, the posterior of the Beta are $\alpha_{k, n} = \alpha_{k, 0} + S_{k,n}, \beta_{k, n} = \beta_{k, 0} + n_k - S_{k,n}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 %Given a proposed grasp plan $\Gamma_i$ with current posterior belief $\alpha_i, \beta_i$, , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
 %The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Given the current belief $\alpha_{k, n_k}, \beta_{k, n_k}$ on $\theta_k$ for an arm $k$, the algorithm can predict the probability of an event occurring on the next iteration by taking the expected value:
+Given the current belief $\alpha_{k, n}, \beta_{k, n}$ for an arm $k$, the algorithm can predict the probability of an event occurring, $p_{k,n}$, on the next iteration by taking the expected value:
 %Thus, we can write the expected probability of force closure as follows
@@
 \begin{align}\label{eq:shape_sampling}
-\theta_k = \frac{\alpha}{\alpha + \beta}
+\bar{p}_{k,n} = \frac{\alpha_{k,n}}{\alpha_{k,n} + \beta_{k,n}}
 \end{align}
@@
 Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
-In the Beta-Bernoulli MAB case, the set of actions is the $K$ options and the states are the Beta posterior on each option, or the integer values of the $\alpha$ and $\beta$ parameters.
+In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,n}$ and $\beta_{k,n}$.
 
@@
 However, the curse of dimensionality effects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in $K$.
-A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each option $i$, $i= 1,...,k$, and for each state $x_t^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$ and the state $x_t^i$ is the Beta prior for option $i$, as shown in Algorithm 1.
+A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,n} = \lbrace \alpha_{k,n}, \beta_{k,n} \rbrace$ up to a timestep $T$.
 
-\vspace{-2ex}
-\begin{align}\label{eq:git_indices}
-	v^i(x^i) = \underset{\tau>0}{\mbox{max}} \frac{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^tr^i(X_t^i)|X_0^i = x_i]}{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^t|X_0^i = x_i]}
- \end{align}
-
-\noindent The indices $v^i(x^i)$, computed in Equation \ref{eq:git_indices}, can then be used to form a policy, where at each timestep the agent selects the option with the highest $v^i(x^i)$.
+The solution to the optimization problem assigns each state an indices $v(x_{k,n})$
+ The indices can then be used to form a policy, where at each timestep the agent selects the arm that solves $k^* = \underset{k\in K}{\mbox{argmax}}(v(x_{k,n}))$.
 Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
@@
 
-\begin{algorithm}
- \KwResult{Current Best Arm, $\Gamma^*$ }
- For Beta(1,1) prior, Table of Indices $v$, Discount Factor $\gamma$: \\
-\For{ t=1,2,...}{ 
- Pull arm $k = \underset{x_k \in X}{\mbox{argmax}} v(x_k)$\\
- Observe reward $R_{I_t,t} \in \lbrace 0,1 \rbrace$\\
- Update posterior:\\
- Set $S_{I_t,t+1} = S_{I_t,t} + R_{I_t,t}$ \\
- Set $F_{I_t,t+1} = F_{I_t,t} + 1 - R_{I_t,t}$\\
- Set $x_k = \lbrace 1 + S_{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
-}
- \caption{The Gittins Index Method for Beta-Bernoulli Process}
-\end{algorithm}
+\subsubsection{Thompson Sampling}
+Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$. 
+Thompson sampling is a less computationally expensive alternative.
+All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall k \in K$to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
+Then for each arm draw $p_{k,n} \sim \mbox{Beta}(\alpha_{k,n},\beta_{k,n})$ and pull the arm with the highest $p_{k,n}$ drawn.
+A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. This is repeated until a stopping time is reached. The full algorithm is shown in Algorithm 2.
 
-\subsubsection{Thompson Sampling}
-Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$, and therefore it is not ideal to use in most cases. 
-Thompson sampling is a less computationally expensive alternative.
-All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha=1$,  $\beta =1$) to reflect a uniform prior on the $\theta$ of the Bernoulli distribution.
-Then for each arm draw $\theta_{j,t} \sim \mbox{Beta}(\alpha,\beta)$ and pull the arm with the highest $\theta_{j,t}$ drawn.
-The reward, $X_{i,t}$ is observed from that arm, $j$, and the corresponding Beta distribution is updated.
-This is repeated until a stopping time is reached. The full algorithm is shown in Algorithm 2.
-
-The intuition for Thompson sampling is that the random samples of $\theta_{j,t}$ allow the method to explore.
+The intuition for Thompson sampling is that the random samples of $p_{k,n}$ allow the method to explore.
 However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
@@
  \KwResult{Current Best Arm, $\Gamma^*$ }
- For Beta(1,1) prior: \\
+ For Beta($\alpha_{k,0}=1$,$\beta_{k,0}=1$) $\forall k \in K$ prior: \\
 \For{ t=1,2,...}{ 
- Draw $\theta_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
- Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
- Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
+ Draw $p_{k,n} \sim$ Beta($\alpha_{k,n}$,$\beta_{k,n}$) for $k = 1,...,K$\\
+ Pull $k$ with maximum $p_{k,t}$\\
+ Observe reward $R_{k,t} \in \lbrace 0,1 \rbrace$\\
  Update posterior:\\
- Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
- Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
+ Set $\alpha_{k,n+1} = \alpha_{k,n} + R_{k,t}$ \\
+ Set $\beta_{k,n+1} = \beta_{k,n} +1-R_{k,t}$\\
 
@@
 We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
-We consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantities are given and can be sampled from.
-
-%Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.
-We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.
+We consider uncertainty in shape, pose, gripper approach, and friction coefficient and we assume that distributions on these quantities are given and can be sampled from.
 
@@
 Given a grasp plan and a deterministic object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
-We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^d$, the object center of mass as $\bz \in \mathbb{R}^d$ and the friction coefficient as $\mu$.
-Together these form the set of grasp parameters $g = (\bc_1,\bc_2, \bn_1, \bn_2, \bz,\mu)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.
+We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu$.
+Together these form the set of grasp parameters that allows us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.
 
@@
 A GPIS is a Gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
-\bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
+\bx_n\}, \bx_i \in \mathbb{R}^2$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
 See Mahler et al. for details on how to estimate a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
 Following Mahler et al., we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
-For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.
+For convenience, in later sections we will refer to the GPIS parameters as $\theta = \lbrace \mu_{f}(\bx), \Sigma_{f}(\bx) \rbrace$.
 
@@
 %One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
-\noindent Following Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$.~\cite{barfoot2014Pose}.
+\todo{Jeff fix this}
+\noindent Following Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(2)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$.~\cite{barfoot2014Pose}.
 
  \subsubsection{Approach Uncertainty}
-In practice a robot may not be able to execute a desired grasp plan $\Gamma$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
+In practice a robot may not be able to execute a desired grasp plan $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
 We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
-Force closure measures the ability to resist external wrenches.
-
-Formally, force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
-Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ...
-\bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
+We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$.
+Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
+Let $\mW \in \mathbb{R}^3$ denote the contact wrenches derived from contact locations $\bc_1,\bc_2$, normals $\bn_1,\bn_2$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
 If the origin lies within the convex hull of $\mW$, then the grasp is in force closure~\cite{li1988task}.
 We rank grasps using the probability of force closure given uncertainty in shape, pose, robot approach, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
-%\vspace{-2ex}
+
+\vspace{-2ex}
 \begin{align*}
@@
 Mahler et al.describe how to draw shape samples from a GPIS model ~\cite{mahler2015gp}.
-We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the line of action $\gamma_i(t)$~\cite{newcombe2011kinectfusion}.
-Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.
-We use these quantities to determine the grasp parameters $g$.
-Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.
-
-%Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$.
-The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used.
-A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.
-%
-%In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps .
-$P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.
+We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the grasp axis defined by $j_1$ and $j_2$~\cite{newcombe2011kinectfusion}.
+Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.We use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
 
@@
 
-Given the sources of uncertainty and their relationships as described above, the grasp planning objective is to find the grasp that maximizes the probability of force closure from a set of $P$ candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_P\}$:
+Given the sources of uncertainty and their relationships as described above, the grasp planning objective is to find the grasp that maximizes the probability of force closure from a set of candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_K\}$:
 
@@
 \begin{align}
-\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:old_problem_def}
+\Gamma^* &= \underset{\Gamma_k \in \mG}{\text{argmax }} P_F\left( \Gamma_k\right) \label{eq:old_problem_def}
 \end{align}
@@
 
-One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
+One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric, we refer to this as a brute force approach.
 This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
 More recent work has considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
+\todo{improve this tomorrow }
 
-To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_t$ up to a given time $T$:
+To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_{k,t}$ at time $t$ up to a given time $T_s$:
 \begin{align}
-    \underset{\Gamma_1, .., \Gamma_T \in \mG}{\text{argmax }} \sum \limits_{t=1}^T P\left( F = 1 | \Gamma_t, \theta, \xi, \rho, \mu \right)   \label{eq:problem_def}
+    \underset{\Gamma_{k,} \in \mG}{\text{argmax }} \sum \limits_{t=1}^
+    {T_s} P_F \left( \Gamma_{k,t}\right)  \label{eq:problem_def}
 \end{align}
@@
 We frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
-Each arm corresponds to a different grasp plan, $\Gamma_i$, and pulling an arm corresponds to sampling from the graphical model in Fig.
-\ref{fig:graphical_model} and evaluating the force closure condition.
-Since force closure is a binary value, each grasp plan $\Gamma_i$ has a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
-The expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E \left[ F | \Gamma_i, \theta, \xi, \rho, \mu \right] = P_F(\Gamma_i)$, and therefore minimizing cumulative regret up to a stopping time $T_s$ is equivalent to the objective of Equation~\ref{eq:problem_def}.
+Each arm corresponds to a different grasp plan, $\Gamma_k$, and pulling an arm corresponds to sampling from the graphical model in Fig.
+\ref{fig:graphical_model} and evaluating the force closure condition.Since force closure is a binary value, each grasp plan $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
+In a MAB, we want to try and minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.
 
@@
 \begin{align}\label{eq:confidence}
-B(0.05,\alpha,\beta) \leq P_F(\Gamma_i)) \leq B(0.95,\alpha,\beta)
+B(0.05,\alpha_{k,n},\beta_{k,n}) \leq P_F(\Gamma_k)) \leq B(0.95,\alpha_{k,n},\beta_{k,n})
 \end{align}
 
+To summarize the algorithm terminates when the following OR condition is meet
+
 \vspace{-2ex}
-.
-
+\begin{align}\label{eq:stopping_condition}
+\lbrace t \geq T_s \: \mbox{OR} \: |B(0.05,\alpha_{k,n},\beta_{k,n}) -  B(0.95,\alpha_{k,n},\beta_{k,n})| \leq \epsilon \rbrace
+\end{align}
+where the $k$ grasp plan refers to the one that is currently being returned. 
  .
 \section{Simulation Experiments}
-We used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.Examples of the images can be seen in \ref{fig:shape_samples}.
+We used the Brown Vision Lab 2D dataset \cite{brown}, a database of object ,  the same as in \cite{christopoulos2007handling}.Examples of the objects can be seen in \ref{fig:shape_samples}.
 We down sampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
+We estimate the GPIS using the same method proposed in \cite{mahler2015gp}.
 For illustrative purposes of noise, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
@@
 
+ In our experiments the MAB methods honed in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples.
+Uniform allocation and Iterative Pruning allocate $1\%$  and $6\%$ of total samples, respectively.
 In Fig.
 \ref{fig:pulls_per_grasp}, we plot samples per grasp quality.
-Gittins and Thompson appear to allocate  more samples to grasps of high quality in contrast to uniform allocation and Iterative Pruning.
-The ability to find grasps with a higher probability of force  faster and have a smaller confidence interval on the returned quantity can be explain by the fact that in our experiments the MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples.
-Uniform allocation and Iterative Pruning allocate $1\%$  and $6\%$ of total samples, respectively.
+Gittins and Thompson appear to allocate  more samples to grasps of higher estimated probability of force closure in contrast to uniform allocation and Iterative Pruning.
+The focused sampling on higher quality grasp can explain the ability to find grasps with a higher probability of force closure  faster and have a smaller confidence interval on the returned quantity.
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.25]{matlab_figures/pfc.eps}
-\caption{ \footnotesize Comparison of the current average probability of force closure vs.
-the stopping time $T_s$.Graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.We demonstrate this for Thompson, Gittins, uniform allocation and Iterative Pruning \cite{kehoe2012estimating}.
-We also demonstrate what the average highest probability of force closure is when the brute force approach of exhaustively sampling each candidate grasp is used.
-Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
-\vspace*{-10pt}
-\label{fig:grasp_quality}
-\end{figure}
-
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
@@
 
-For friction coefficient we varied the variance across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
+For friction coefficient we varied $\sigma_{\mu}$ across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
 As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 2000 evaluations.
@@
 For rotational uncertainty in pose, we varied $\sigma_{rot}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
-As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\deg}$  causes the convergence in simple regret to not be reached until around 4432 samples or an average of 5.5 samples per grasp.
+As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\circ}$  causes the convergence in simple regret to not be reached until around 4432 samples or an average of 5.5 samples per grasp.
 
@@
 
-As we scale to 3D objects the possible number of grasp candidates will be substantially larger.
-The more options a MAB algorithm has leads to generally a harder problem \cite{bubeck2009pure}.
-However, the MAB algorithms presented above assumed that each option is independent.
-In the grasping context though spatial information about grasps could provide information about the quality of similar grasps.
-We can estimate a correlated Beta-Bernoulli distribution using an Kernel density estimation on the $\alpha$ and $\beta$ parameter \cite{goetschalckx2011continuous}.However we would have to find an appropriate feature representation for a grasp that can accurately represent this.
-Learning these features and applying these to MAB methods will be an exciting project for future work.
+In future work, we plan to scale our method to 3D objects.
+However, this could substantially increase the number of candidate grasp plans.
+To handle a much larger amount of arms, it becomes neccesary to have some measure of correlation between them.
+If two grasps are similar with respect to some metric, then their measure of probability of force closure should be correlated.
+Appropriate features that represent an grasp under uncertainty  and the metric itself are still open questions though and will be an ongoing project for future work.
 \bibliographystyle{IEEEtranS}

### 2015-03-12 paper.tex

@@
 \begin{abstract}
-Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.
-Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
+Uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities can make it difficult to plan grasp.
+A popular approach to handle uncertainty is to sample perturbations in shape, state, and control and calculate the probability of force closure.
+Commonly methods uniformly allocate samples to rank a set of potential grasp, but this may require a large number of samples to converge, even for planar models.
 We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
-We formulate grasp planning as a MAB  to efficiently determine high quality grasp with respect to a probability of force closure metric.
-We compare against two previously proposed methods for grasp selection uniform allocation, or uniformly selecting samples, and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps.
-We consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
-In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean based adaptive sampling approach previously used.
+We formulate grasp planning as a MAB  to determine high quality grasps with respect to the probability of force closure.
+We compare against two previously proposed methods for grasp selection: uniform allocation and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps.
+We consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, gripper approach, and coefficient of friction.
+Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to get within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 \end{abstract}
@@
 Recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One option is using Monte-Carlo integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012toward}, but this can be computationally expensive due to the need to exhaustively sample every grasp candidate.
-We show that by using a Multi-Armed Bandit model it is possible to rule out grasps with low probability of force closure and to allocate more sampling effort to grasps that are likely to be high quality.
+One option is using Monte-Carlo integration over sample perturbations in the uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}, but this can be computationally expensive due to the need to exhaustively sample every grasp candidate.
 
+We show that by using a Multi-Armed Bandit model it is possible to allocate sampling effort to only grasps that seem promising.
 The multi-armed bandit (MAB) model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
-In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
+In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
+The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
 The MAB algorithm can be interpreted as an anytime algorithm, where at a provided stopping time the algorithm terminates and returns the estimated best grasp, with respect to a chosen metric, or continues running until a user defined confidence level is met.
@@
 We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
-We model uncertainty in pose as a normal distributions around the orientation and translation of the object.
-Uncertainty in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
+We model uncertainty in pose as a normal distribution around the orientation and 2D position of the object.
+Uncertainty in motion is represented as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper.
+Uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation, or randomely sampling grasps, and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al.
 \cite{kehoe2012toward}.
-In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}.
-In simulation, initial results  showed that given 1000 randomly selected grasps the number of samples required, on average over 100 objects, to get within $2.5\%$ of the estimated highest probability of force closure an MAB algorithm used $439\%$ fewer samples than the sample mean adaptive sampling approach previously used .
+In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset, a dataset of 2D object silhouettes ~\cite{brown, christopoulos2007handling}.
+Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to get within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 
@@
 Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty due to its ability to represent arbitrary topologies and correlations between shape uncertainty over spatial locations~\cite{dragiev2011, dragiev2013uncertainty, hollinger2013, mahler2015gp}.
-Dragiev et al.~\cite{dragiev2011} used the mean GPIS to control a grasp to reach a desired location, and extended this work to use GPIS for active tactile shape exploration during grasping~\cite{dragiev2013uncertainty}.
+Dragiev et al.~\cite{dragiev2011} used the mean GPIS as input to a grasp controller to reach a desired location, and extended this work to use GPIS for active tactile shape exploration during grasping~\cite{dragiev2013uncertainty}.
 Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem~\cite{mahler2015gp}.
 
-Some probabilistic grasp quality measures, such as probability of force closure, use Monte-Carlo sampling to evaluate grasp quality~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
-This involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
+%For shape uncertainty, we used a Gaussian process implicit surface representation. 
+%Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
+%Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
+%Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.
+
+Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo integration to evaluate grasp quality~\cite{christopoulos2007handling, kim2012physically, weisz2012pose , kehoe2012toward}.
+This involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
+\todo{Should we call using Monte-Carlo Integration and sorting grasps Brute Force? I am worried it might come off as offensive to prior work}
 It can be computationally expensive though to sample all proposed grasps to convergence.
@@
 One benefit of the Beta prior on Bernoulli reward distributions is that updates to the belief distribution after observing rewards from arm pulls can be derived in closed form.
-Let $n_k$ denote the number of times arm $k$ has been sampled.
-Then after observing $S_{k,n}$ rewards of $1$ for arm $k$ after $n$ samples, the posterior of the Beta are $\alpha_{k, n} = \alpha_{k, 0} + S_{k,n}, \beta_{k, n} = \beta_{k, 0} + n_k - S_{k,n}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
-%Given a proposed grasp plan $\Gamma_i$ with current posterior belief $\alpha_i, \beta_i$, , we draw samples from the shape distribution $P(\theta)$, the distribution on pose $P(\xi)$, distribution on motion $P(\rho)$ and the distribution on friction coefficient $P(\mu)$.
-%The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$.
-Given the current belief $\alpha_{k, n}, \beta_{k, n}$ for an arm $k$, the algorithm can predict the probability of an event occurring, $p_{k,n}$, on the next iteration by taking the expected value:
+At timestep $t=0$, we pull arm $k$ and observe reward $R_{k,0}$, where $R_{k,0} \in \lbrace 0, 1\rbrace$.The posterior of the Beta are $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}, \beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+
+Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$, the algorithm can predict the probability of an event occurring, $p_{k,t}$, on the next iteration by taking the expected value:
 %Thus, we can write the expected probability of force closure as follows
@@
 \begin{align}\label{eq:shape_sampling}
-\bar{p}_{k,n} = \frac{\alpha_{k,n}}{\alpha_{k,n} + \beta_{k,n}}
+\bar{p}_{k,t} = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}}
 \end{align}
@@
 Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
-In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,n}$ and $\beta_{k,n}$.
+In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,t}$ and $\beta_{k,t}$.
 
@@
 However, the curse of dimensionality effects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in $K$.
-A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,n} = \lbrace \alpha_{k,n}, \beta_{k,n} \rbrace$ up to a timestep $T$.
+A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$.
 
-The solution to the optimization problem assigns each state an indices $v(x_{k,n})$
- The indices can then be used to form a policy, where at each timestep the agent selects the arm that solves $k^* = \underset{k\in K}{\mbox{argmax}}(v(x_{k,n}))$.
+The solution to the optimization problem assigns each state an index $v(x_{k,t})$
+ The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{k\in K}{\mbox{argmax}}(v(x_{k,t}))$.
 Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
@@
 All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall k \in K$to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
-Then for each arm draw $p_{k,n} \sim \mbox{Beta}(\alpha_{k,n},\beta_{k,n})$ and pull the arm with the highest $p_{k,n}$ drawn.
+Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
 A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. This is repeated until a stopping time is reached. The full algorithm is shown in Algorithm 2.
 
-The intuition for Thompson sampling is that the random samples of $p_{k,n}$ allow the method to explore.
+The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
 However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
@@
 \For{ t=1,2,...}{ 
- Draw $p_{k,n} \sim$ Beta($\alpha_{k,n}$,$\beta_{k,n}$) for $k = 1,...,K$\\
- Pull $k$ with maximum $p_{k,t}$\\
- Observe reward $R_{k,t} \in \lbrace 0,1 \rbrace$\\
+ Draw $p_{k,t} \sim$ Beta($\alpha_{k,t}$,$\beta_{k,t}$) for $k = 1,...,K$\\
+ Pull $k_t  = \underset{k\in K}{\mbox{argmax}} \: p_{k,t}$\\
+ Observe reward $R_{k_t,t} \in \lbrace 0,1 \rbrace$\\
  Update posterior:\\
- Set $\alpha_{k,n+1} = \alpha_{k,n} + R_{k,t}$ \\
- Set $\beta_{k,n+1} = \beta_{k,n} +1-R_{k,t}$\\
 
+ \eIf{$k = k_t$}{
+ Set $\alpha_{k,t+1} = \alpha_{k,t} + R_{k_t,t}$ \\
+ Set $\beta_{k,t+1} = \beta_{k,t} +1-R_{k_t,t}$\\
+ }{
+ Set $\alpha_{k,t+1} = \alpha_{k,t}$ \\
+ Set $\beta_{k,t+1} = \beta_{k,t}$\\
+ }
   }
@@
 \subsubsection{Pose Uncertainty}
-In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:
-
-\vspace{-2ex}
-\begin{align*}
-	T &= \left[  \begin{array}{ccc}
-		\cos(\phi) & -\sin(\phi) & t_x \\
-		\sin(\phi) & \cos(\phi) & t_y \\
-		0 & 0 & 1
-		\end{array} \right] .
-\end{align*}
-
-%One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
-\todo{Jeff fix this}
-\noindent Following Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(2)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$.~\cite{barfoot2014Pose}.
+In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$.
+We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \bar{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\bar{\mathbf{\xi}}$ corresponds to the expected pose of the object.
 
@@
 \begin{align*}
-	P_F(\Gamma) &= P \left(F = 1 | \Gamma, \theta, \xi, \rho, \mu \right).
+	P_F(\Gamma_k) &= P \left(F = 1 | \Gamma_k, \theta, \xi, \rho, \mu \right).
 \end{align*}
 
-To estimate $P_F(\Gamma)$, we generate samples from each of the distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.
+To estimate $P_F(\Gamma_k)$, we generate samples from each of the distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.
 After sampling a shape, pose, approach direction, and friction coefficient, we compute the contact locations $\bc_i$ and the surface normals $\bn_i$ using Bayes rule:
@@
  \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
- &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)
+ &p(\textbf{n}_i,\textbf{c}_i |\Gamma_k,\theta,\xi,\rho)=\\
+ &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\Gamma_k,\theta,\rho,\xi)
  \end{align*}
@@
 Mahler et al.describe how to draw shape samples from a GPIS model ~\cite{mahler2015gp}.
-We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ via ray tracing along the grasp axis defined by $j_1$ and $j_2$~\cite{newcombe2011kinectfusion}.
+We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\Gamma_k,\theta,\rho,\xi)$ via ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
 Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.We use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
@@
 More recent work has considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
-\todo{improve this tomorrow }
 
@@
 \begin{align}
-    \underset{\Gamma_{k,} \in \mG}{\text{argmax }} \sum \limits_{t=1}^
+    \underset{\Gamma_{k,} \in \mG}{\text{max }} \sum \limits_{t=1}^
     {T_s} P_F \left( \Gamma_{k,t}\right)  \label{eq:problem_def}
 \end{align}
-\noindent This tries to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
+\noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.
+We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
 
@@
 \begin{align}\label{eq:stopping_condition}
-\lbrace t \geq T_s \: \mbox{OR} \: |B(0.05,\alpha_{k,n},\beta_{k,n}) -  B(0.95,\alpha_{k,n},\beta_{k,n})| \leq \epsilon \rbrace
+\lbrace t \geq T_s \: \mbox{OR} \: |B(0.05,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.95,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace
 \end{align}
-where the $k$ grasp plan refers to the one that is currently being returned. 
+
+where the $\bar{k}$ grasp plan refers to the one that is currently being returned. 
  .
 \section{Simulation Experiments}
-We used the Brown Vision Lab 2D dataset \cite{brown}, a database of object ,  the same as in \cite{christopoulos2007handling}.Examples of the objects can be seen in \ref{fig:shape_samples}.
-We down sampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D object silhouettes ,  the same as in \cite{christopoulos2007handling}.Examples of the objects can be seen in \ref{fig:shape_samples}.
+\todo{How doe we estimate noise?} We down sampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
 We estimate the GPIS using the same method proposed in \cite{mahler2015gp}.
-For illustrative purposes of noise, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
+For illustrative purposes of noise, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{\psi} = 0.2$ rads, $\sigma_{\by} = 3$ grid cells, $\sigma_{\mu} = 0.4$, $\sigma_{\phi} = 0.3$ rads and $\sigma_{\bt} = 3$ grid cells.
 We performed experiments for the case of two hard contacts in 2-D.
@@
 For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$.
-We initialize all algorithms by sampling each grasp 1 time.
 We draw samples from our graphical model using the technique described in Sec.
@@
 \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods: Thompson sampling, Gittins indices, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
 Iterative Pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation.
+We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time, since it scales exponentially in computation.
 
-\todo{This might still be vague} As illustrated in Fig.
-\ref{fig:grasp_quality}, Gittins and Thompson select a grasp at stopping time $T_s$ that on average has a higher probability of force closure than uniform allocation and Iterative Pruning .
-For illustrative purposes of an anytime algorithm,  we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average, and for each method visualize the grasp selected in Fig.
-\ref{fig:shape_samples}.
+\todo{This might still be vague} In Fig.
+\ref{fig:grasp_quality}, we plot the grasp returned at time $t$ vs.
+$P(\Gamma_{\bar{k}})$.
+As illustrated, Gittins and Thompson return a grasp plan that on average has a higher probability of force closure than uniform allocation and Iterative Pruning .
+For illustrative purposes in Fig.
+\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp plan returned, $\Gamma_{\bar{k}}$, on 3 randomely selected shapes in the dataset
 
- The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval, Eq.
-\ref{eq:confidence}, around the returned grasp is below a set threshold $\epsilon$.
-We plot the confidence intervals around the return grasp vs.
+The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$.
+We plot the confidence intervals around the returned grasp vs.
 the number of samples drawn in Fig.
@@
 \begin{figure}[t!]
+
 \centering
@@
 
-For rotational uncertainty in pose, we varied $\sigma_{rot}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
+For rotational uncertainty in pose, we varied $\sigma_{\phi}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
 As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\circ}$  causes the convergence in simple regret to not be reached until around 4432 samples or an average of 5.5 samples per grasp.
 
-For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
+For translational uncertainty in pose, we varied $\sigma_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
+As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation and an increased noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
 
@@
  \hline
-Translation Variance in Pose, $\sigma_{trans}$ & 1210    & 2207 &  8763\\
-Friction Coefficient Variance, $\sigma_{fric}$ &  1985  & 1456   & 1876\\
-Rotational Variance in Pose, $\sigma_{rot}$ & 4230 & 4431 &  4432\\
+Translation Variance in Pose, $\sigma_{\bt}$ & 1210    & 2207 &  8763\\
+Friction Coefficient Variance, $\sigma_{\mu}$ &  1985  & 1456   & 1876\\
+Rotational Variance in Pose, $\sigma_{\phi}$ & 4230 & 4431 &  4432\\
  \hline
 \end{tabular}
-   \caption { \footnotesize  Sensitivity Analysis for convergence to estimated best grasp for Thompson Sampling under rotational variance $\sigma_{rot} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{trans} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{fric} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 10 objects from the Brown Vision Lab Data set.
+   \caption { \footnotesize  Sensitivity Analysis for convergence to estimated best grasp for Thompson Sampling under rotational variance $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 10 objects from the Brown Vision Lab Data set.
 The sensitivity analysis shows that large variance in translational uncertainty in pose can increase the amount of iterations needed for the bandit algorithm to converge to the highest quality grasp in the set.
@@
 \ref{fig:worst_case} there can exists pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
-Fortunately, though these cases occur with a small very probability, however it is important for a practitioner to be aware of them.
+Fortunately, though the joint probability of successive samples being misleading approaches zero at an exponential rate as the time horizon is increased.
+Thus, the pathological case occurs with very small probability.
 
@@
 However, this could substantially increase the number of candidate grasp plans.
-To handle a much larger amount of arms, it becomes neccesary to have some measure of correlation between them.
+To handle a much larger amount of arms, it becomes necessary to have some measure of correlation between them.
 If two grasps are similar with respect to some metric, then their measure of probability of force closure should be correlated.
-Appropriate features that represent an grasp under uncertainty  and the metric itself are still open questions though and will be an ongoing project for future work.
+Appropriate features that represent a grasp under uncertainty  and the metric itself are still open questions though and will be an ongoing project for future work.
 \bibliographystyle{IEEEtranS}

### 2015-03-13 paper.tex
Wording and notation changes (Jeff). Close to ready to send to Ken.

@@
 \author{Michael Laskey$^1$, Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T.
-Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
+Pokorny$^3$, Sachin Patil$^1$,\\ Jur van den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
 \thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
@@
 \begin{abstract}
-Uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities can make it difficult to plan grasp.
-A popular approach to handle uncertainty is to sample perturbations in shape, state, and control and calculate the probability of force closure.
-Commonly methods uniformly allocate samples to rank a set of potential grasp, but this may require a large number of samples to converge, even for planar models.
+Uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities can make it difficult to plan grasps.
+A popular approach to handle uncertainty is to sample perturbations in shape, state, and control to calculate the probability of force closure.
+Common methods uniformly allocate samples to rank a set of potential grasp, but this may require a large number of samples to converge, even for planar models.
 We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
@@
 We consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, gripper approach, and coefficient of friction.
-Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to get within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to plan a grasp within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 \end{abstract}
@@
 Planning grasps using analytic methods requires the contact locations and surface normals.
-However, robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
+However, a robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
 
@@
 Recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One option is using Monte-Carlo integration over sample perturbations in the uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}, but this can be computationally expensive due to the need to exhaustively sample every grasp candidate.
+One option is using Monte-Carlo integration over sample perturbations in the uncertain quantities to evaluate the probability of force closure for a set of candidate grasps~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}, but this can be computationally expensive.
 
-We show that by using a Multi-Armed Bandit model it is possible to allocate sampling effort to only grasps that seem promising.
-The multi-armed bandit (MAB) model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
+We show that by using a Multi-Armed Bandit (MAB) model it is possible to allocate sampling effort to only grasps that seem promising.
+The MAB model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
 In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
 The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
-The MAB algorithm can be interpreted as an anytime algorithm, where at a provided stopping time the algorithm terminates and returns the estimated best grasp, with respect to a chosen metric, or continues running until a user defined confidence level is met.
+MAB algorithms can be interpreted as anytime algorithms, where at a provided stopping time the algorithm terminates and returns the estimated best grasp, with respect to a chosen metric, or continues running until a user defined confidence level is met.
 
@@
 We model uncertainty in pose as a normal distribution around the orientation and 2D position of the object.
-Uncertainty in motion is represented as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper.
-Uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
+Furthermore, we model uncertainty in motion as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper and uncertainty in friction coefficient as a normal distribution around an expected friction coefficient.
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean, proposed by Kehoe et al.
-\cite{kehoe2012toward}.
-In the task of finding grasps with high probability of force closure on the Brown Vision 2D Dataset, a dataset of 2D object silhouettes ~\cite{brown, christopoulos2007handling}.
-Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to get within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean~\cite{kehoe2012toward}, on the task of finding grasps with high probability of force closure.
+We compare on the Brown Vision 2D Dataset, a dataset of 2D object silhouettes~\cite{brown, christopoulos2007handling}.
+Our initial results show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to get within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 
@@
 Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot grasps planned using deterministic wrench space metrics on objects from the Columbia Grasp Database.
-Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose, and also found that the planned grasps were more successful on a physical robot than classical grasp metrics.
+Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose, and also found that the planned grasps were more successful on a physical robot than thoise planned with classical wrench space metrics.
 
@@
 Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} sampled perturbations in shape for extruded polygonal objects to plan push grasps for parallel-jaw grippers.
-Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty due to its ability to represent arbitrary topologies and correlations between shape uncertainty over spatial locations~\cite{dragiev2011, dragiev2013uncertainty, hollinger2013, mahler2015gp}.
-Dragiev et al.~\cite{dragiev2011} used the mean GPIS as input to a grasp controller to reach a desired location, and extended this work to use GPIS for active tactile shape exploration during grasping~\cite{dragiev2013uncertainty}.
+Several recent works have also studied using Gaussian process implicit surfaces (GPISs) to represent shape uncertainty motivated by its ability to model spatial noise correlations and to integrate multiple sensing modalities~\cite{dragiev2011, dragiev2013uncertainty, hollinger2013, mahler2015gp}.
+Dragiev et al.~\cite{dragiev2011} uses GPIS to actively explore shapes with tactile sensing to find a hand posture that aligned the gripper fingers to an object's surface normals~\cite{dragiev2013uncertainty}.
 Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem~\cite{mahler2015gp}.
@@
 
-Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo integration to evaluate grasp quality~\cite{christopoulos2007handling, kim2012physically, weisz2012pose , kehoe2012toward}.
+Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo integration to evaluate grasp quality~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
 This involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
@@
 It can be computationally expensive though to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure known as Iterative Pruning, which at a set iteration discards a subset of the grasps that seem unlikely to be of high quality .
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure known as Iterative Pruning, which periodically discards a subset of the grasps that seem unlikely to be of high quality.
 However, the method pruned grasps using only the sample mean and did not utilize any confidence interval around the current estimate, which can discard good grasps.
-We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead ~\cite{barto1998reinforcement, lai1985asymptotically}.
+We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.
 
@@
 The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
-Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
+Solutions to the MAB model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
 
-A traditional MAB example is a gambler has $K$ independent one-armed bandits, also known as slot machines.
-When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
-The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards are maximized over many pulls.
+A traditional MAB example is a gambler with $K$ independent one-armed bandits, also known as slot machines.
+When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution that is unknown to the gambler.
+The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them to maximize the sum of average rewards over all pulls.
 If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
@@
 \subsection{Algorithms for MAB}\label{sec:bandit_algorithm}
-We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) ~\cite{chapelle2011empirical, bachman2013greedy}.
+We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on certain problems~\cite{chapelle2011empirical, bachman2013greedy}.
 Theoretical results have shown that several algorithms are capable of achieving near the lower bound on the asymptotic rate of convergence in regret described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
@@
 One benefit of the Beta prior on Bernoulli reward distributions is that updates to the belief distribution after observing rewards from arm pulls can be derived in closed form.
-At timestep $t=0$, we pull arm $k$ and observe reward $R_{k,0}$, where $R_{k,0} \in \lbrace 0, 1\rbrace$.The posterior of the Beta are $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}, \beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+At timestep $t=0$, we pull arm $k$ and observe reward $R_{k,0}$, where $R_{k,0} \in \lbrace 0, 1\rbrace$.
+The posterior of the Beta after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}, \beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 
-Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$, the algorithm can predict the probability of an event occurring, $p_{k,t}$, on the next iteration by taking the expected value:
+Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$ at time $t$, the algorithm can predict the probability of an event occurring, $p_{k,t}$, on the next iteration by taking the expected value:
 %Thus, we can write the expected probability of force closure as follows
@@
 
-The solution to the optimization problem assigns each state an index $v(x_{k,t})$
- The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{k\in K}{\mbox{argmax}}(v(x_{k,t}))$.
+The solution to the optimization problem assigns each state an index $v(x_{k,t})$.
+The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
 Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
@@
 Thompson sampling is a less computationally expensive alternative.
-All arms are initialized with a prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall k \in K$to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
+All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
 Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
@@
 \end{algorithm}
-\vspace{-2ex}
 
@@
 We formulate the MAB problem for 2-dimensional objects using parallel-jaw grippers.
-Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathcal{R}$ and a maximum width $w_g \in \mathcal{R}$.
-The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathcal{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$.
+Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$.
+The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathbb{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$.
 We define a grasp plan consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.
@@
 Given a grasp plan and a deterministic object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
-We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu$.
-Together these form the set of grasp parameters that allows us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.
+We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu \in \mathbb{R}$.
+%Together these form the set of grasp parameters that allows us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.
 
@@
 A GPIS represents a distribution over signed distance functions (SDFs).
-A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
+A SDF is a real-valued function over spatial locations $f: \mathbb{R}^2 \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
 A GPIS is a Gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ...
@@
 In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$.
-We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \bar{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\bar{\mathbf{\xi}}$ corresponds to the expected pose of the object.
+We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \bar{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\hat{\mathbf{\xi}}$ corresponds to the expected pose of the object.
 
@@
 
-To estimate $P_F(\Gamma_k)$, we generate samples from each of the distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.
-After sampling a shape, pose, approach direction, and friction coefficient, we compute the contact locations $\bc_i$ and the surface normals $\bn_i$ using Bayes rule:
+To estimate $P_F(\Gamma_k)$, we first generate samples from the distributions on $\theta, \xi, \rho,$ and $\mu$.
+Using the relationships defined by the graphical model in Fig.
+\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp apprach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
+We then compute the surface normals $\bn_1, \bn_2$ at the contacts based on the gradient of the sampled SDF at the contact locations.
+Finally, we use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
 
- \vspace{-2ex}
- \begin{align*}
- &p(\textbf{n}_i,\textbf{c}_i |\Gamma_k,\theta,\xi,\rho)=\\
- &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\Gamma_k,\theta,\rho,\xi)
- \end{align*}
-
-Mahler et al.describe how to draw shape samples from a GPIS model ~\cite{mahler2015gp}.
-We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\Gamma_k,\theta,\rho,\xi)$ via ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
-Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.We use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
+%After sampling a shape, pose, approach direction, and friction coefficient, we compute the contact locations $\bc_i$ and the surface normals $\bn_i$ using Bayes rule:
+%
+% \vspace{-2ex}
+% \begin{align*}
+% &p(\textbf{n}_i,\textbf{c}_i |\Gamma_k,\theta,\xi,\rho)=\\
+% &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\Gamma_k,\theta,\rho,\xi)
+% \end{align*}
+%
+% 
+%Mahler et al.describe how to draw shape samples from a GPIS model ~\cite{mahler2015gp}.
+%We next sample from $p(\xi)$ and $p(\rho)$ to compute $p(\textbf{c}_i|\Gamma_k,\theta,\rho,\xi)$ via ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
+%Then $p(\textbf{n}_i|\textbf{c}_i,\theta)$ corresponds to the normal vector at the sampled contact point.We use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
 
@@
 
-One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric, we refer to this as a brute force approach.
+One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
+We refer to this as a brute force approach. 
 This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
@@
 \section{Grasp Planning as a Multi-Armed Bandit}
-We frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
+We frame the grasp selection problem of \secref{objective} as a MAB problem.
 Each arm corresponds to a different grasp plan, $\Gamma_k$, and pulling an arm corresponds to sampling from the graphical model in Fig.
-\ref{fig:graphical_model} and evaluating the force closure condition.Since force closure is a binary value, each grasp plan $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
+\ref{fig:graphical_model} and evaluating the force closure condition.
+Since force closure is a binary value, each grasp plan $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
 In a MAB, we want to try and minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.
@@
 One can think of the proposed algorithm as an anytime algorithm.
-It can be stopped at anytime during its computation and return the current estimate of the best grasp or wait until a $95\%$ confidence interval is smaller than some threshold $\epsilon$.
+It can be stopped at anytime during its computation to return the current estimate of the best grasp or wait until a $95\%$ confidence interval is smaller than some threshold $\epsilon$.
 Using the quantile function of the beta distribution, $B$, we can measure the $95\%$ confidence interval as:
@@
 \begin{align}\label{eq:confidence}
-B(0.05,\alpha_{k,n},\beta_{k,n}) \leq P_F(\Gamma_k)) \leq B(0.95,\alpha_{k,n},\beta_{k,n})
+B(0.025,\alpha_{k,n},\beta_{k,n}) \leq P_F(\Gamma_k)) \leq B(0.975,\alpha_{k,n},\beta_{k,n})
 \end{align}
 
-To summarize the algorithm terminates when the following OR condition is meet
+To summarize the algorithm terminates when the following condition is met
 
@@
 \begin{align}\label{eq:stopping_condition}
-\lbrace t \geq T_s \: \mbox{OR} \: |B(0.05,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.95,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace
+\lbrace t \geq T_s \: \mbox{OR} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace
 \end{align}
+\noindent where the $\bar{k}$ grasp plan refers to the grasp with the highest estimated $P_F$ at time $t$.
 
-where the $\bar{k}$ grasp plan refers to the one that is currently being returned. 
- .
 \section{Simulation Experiments}
-We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D object silhouettes ,  the same as in \cite{christopoulos2007handling}.Examples of the objects can be seen in \ref{fig:shape_samples}.
-\todo{How doe we estimate noise?} We down sampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-We estimate the GPIS using the same method proposed in \cite{mahler2015gp}.
-For illustrative purposes of noise, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{\psi} = 0.2$ rads, $\sigma_{\by} = 3$ grid cells, $\sigma_{\mu} = 0.4$, $\sigma_{\phi} = 0.3$ rads and $\sigma_{\bt} = 3$ grid cells.
-We performed experiments for the case of two hard contacts in 2-D.
+We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D object silhouettes, as in \cite{christopoulos2007handling}.
+GPIS models of 3 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
+We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+The measurement noises were assigned uniformly at random to the grid cells.
+We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
+For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi} = 0.2$ rads, $\sigma_{\by} = 3$ grid cells, $\sigma_{\mu} = 0.4$, $\sigma_{\phi} = 0.3$ rads and $\sigma_{\bt} = 3$ grid cells.
+We also performed experiments for the case of two hard contacts in 2-D.
 We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
@@
 \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods: Thompson sampling, Gittins indices, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
 Iterative Pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time, since it scales exponentially in computation.
+We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time.
 
@@
 \ref{fig:grasp_quality}, we plot the grasp returned at time $t$ vs.
-$P(\Gamma_{\bar{k}})$.
+$P(\Gamma_{\bar{k}})$, the probability of force closure for the grasp returned by the algorithm $\Gamma_(\bar{k})$.
 As illustrated, Gittins and Thompson return a grasp plan that on average has a higher probability of force closure than uniform allocation and Iterative Pruning .
 For illustrative purposes in Fig.
-\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp plan returned, $\Gamma_{\bar{k}}$, on 3 randomely selected shapes in the dataset
+\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp plan returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
 
@@
 \ref{fig:confidence} for Thompson Sampling, Iterative Pruning\cite{kehoe2012toward} and uniform allocation.
-\todo{Still thinking of a way to quantify this} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
+\todo{How should we quantify this?
+Uniform allocation never gets a low confidence over the number of samples we used.} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
 
- In our experiments the MAB methods honed in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 29$\%$ of the total number of samples and Gittins allocates 23$\%$ of total samples.
-Uniform allocation and Iterative Pruning allocate $1\%$  and $6\%$ of total samples, respectively.
-In Fig.
-\ref{fig:pulls_per_grasp}, we plot samples per grasp quality.
-Gittins and Thompson appear to allocate  more samples to grasps of higher estimated probability of force closure in contrast to uniform allocation and Iterative Pruning.
-The focused sampling on higher quality grasp can explain the ability to find grasps with a higher probability of force closure  faster and have a smaller confidence interval on the returned quantity.
+We also compared the methods by the number of samples each allocated to the top $10\%$ of grasps in terms of the pprobabilty of force closure estimated by brute force.
+We found that Thompson Sampling allocates 29$\%$ of the total number of samples to the top $10\%$ of grasps and Gittins allocates 23$\%$ of total samples.
+Uniform allocation and Iterative Pruning allocate approximately $1\%$  and $6\%$ of total samples, respectively.
+In Fig. \ref{fig:pulls_per_grasp} we plot samples per grasp quality.
+The MAB appear to allocate more samples to higher quality grasps, which may explain the ability to find grasps with a higher probability of force closure faster.
 
@@
     \caption{\todo{Need to change this figure, wondering what should be conveyed here}Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
-The four methods (uniform allocation, Iterative Pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|G|=1000$.
+The four methods (uniform allocation, Iterative Pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|\mG|=1000$.
 We also show the grasp returned by the brute force approach of exhaustively sampling every grasp in the set.
 The grasps and the quality each one found is shown above.
-In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $10,000$, however at the last shape there is a difference of $2\%$ grasp quality.
-}%
+In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $10,000$, however at the last shape there is a difference of $2\%$ grasp quality.}%
     \label{fig:shape_samples}%
@@
 \todo{need to redo with larger number of shapes}
-We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose and translation pose and use that to set the parameters for future experiments .
+We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose and use that to set the parameters for future experiments.
 The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
-All experiments were averaged across 10 shapes randomly selected with from the Brown dataset with $|G| = 1000$, or 1000 grasp plans $\Gamma$.
+All experiments were averaged across 10 shapes randomly selected with from the Brown dataset with $|\mG| = 1000$, or 1000 grasp plans $\Gamma$.
 
@@
 It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
-One interesting aspect that is illustrated is that Thompson sampling is able to make improvement while the other two methods are stuck in local optimal.
+Interestingly, Thompson sampling appears to to continute to improvement while Gittins indices and Iterative Pruning are stuck in local optimal.
 This is because Thompson sampling is guaranteed to find the best grasp in the limit of infinite iterations \cite{agrawal2011analysis}.
@@
 
-Assessing grasp quality under  uncertainty can be computationally expensive as it often requires repeated evaluations of the grasp metric over many random samples.
 In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
@@
 Initial results have shown our MAB approach to outperform the methods of prior work, uniform allocation and Iterative Pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
- However, as shown in Fig.
-\ref{fig:worst_case} there can exists pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
-Fortunately, though the joint probability of successive samples being misleading approaches zero at an exponential rate as the time horizon is increased.
-Thus, the pathological case occurs with very small probability.
+However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
+Fortunately, the probability of many successive samples being misleading approaches zero at an exponential rate as the time horizon is increased.
 
-In future work, we plan to scale our method to 3D objects.
-However, this could substantially increase the number of candidate grasp plans.
-To handle a much larger amount of arms, it becomes necessary to have some measure of correlation between them.
-If two grasps are similar with respect to some metric, then their measure of probability of force closure should be correlated.
-Appropriate features that represent a grasp under uncertainty  and the metric itself are still open questions though and will be an ongoing project for future work.
+In future work, we plan to scale our method to 3D objects. However, this could substantially increase the number of candidate grasp plans.
+To handle a much larger amount of arms, it may be useful to have some measure of correlation between the arms.
+For example, if two grasps contact an object at spatially close locations, then their measure of probability of force closure may be correlated.
+Appropriate features that represent a grasp or object under uncertainty and the grasp quality metric are still open questions and will be an ongoing project for future work. 
 \bibliographystyle{IEEEtranS}

### 2015-03-14 paper.tex
v10

@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v7 Feb 18, 2015 ] }
+Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v11 March 13, 2015 ] }
 
@@
 \begin{abstract}
-Uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities can make it difficult to plan grasps.
-A popular approach to handle uncertainty is to sample perturbations in shape, state, and control to calculate the probability of force closure.
-Common methods uniformly allocate samples to rank a set of potential grasp, but this may require a large number of samples to converge, even for planar models.
-We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions.
-We formulate grasp planning as a MAB  to determine high quality grasps with respect to the probability of force closure.
-We compare against two previously proposed methods for grasp selection: uniform allocation and an adaptive sampling approach known as Iterative Pruning, which iteratively reduces the set of candidate grasps.
-We consider the case of shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, gripper approach, and coefficient of friction.
-Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to plan a grasp within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing, shape, mechanics, and control.
+One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
+This can be computationally demanding.
+To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context.
+We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
+We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
+Non-MAB methods, uniform allocation and iterative pruning, converge slowly.
+In contrast, the MAB methods we consider, Thompson Sampling and the Gittins Index, were more efficient in experiments, converging to within 3\% of the optimal grasp 10x faster than non-MAB methods.
 \end{abstract}
@@
 
-    \caption{Comparison of the current average probability of force closure vs.
-the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.
-We demonstrate this for Thompson, Gittins, uniform allocation and Iterative Pruning \cite{kehoe2012estimating}.
-We also demonstrate what the average highest probability of force closure is when the brute force approach of exhaustively sampling each candidate grasp is used.
-Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }%
+    \caption{\todo{figure is only averaged over 40 shapes, rerunning the experiments (Shouldn't change earlier results on (TS, IP and UA ) once done)} Grasp quality over time for 4 sample-based planning methods compared with optimal grasp determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
+Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp angles.
+Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
+Two Multi-Arm Bandit methods perform significantly better, converging after only 4000 and 2000 iterations.
+}%
     \label{fig:grasp_quality}
@@
 
-One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
-Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
-Recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One option is using Monte-Carlo integration over sample perturbations in the uncertain quantities to evaluate the probability of force closure for a set of candidate grasps~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}, but this can be computationally expensive.
+One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.To cope with uncertainty, recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
+One way to compute the probability of force closure is using Monte-Carl integration over sample perturbations in the uncertain quantities\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
+However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
 
-We show that by using a Multi-Armed Bandit (MAB) model it is possible to allocate sampling effort to only grasps that seem promising.
-The MAB model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
+We show that by using a Multi-Armed Bandit (MAB) model it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
 In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
 The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
-MAB algorithms can be interpreted as anytime algorithms, where at a provided stopping time the algorithm terminates and returns the estimated best grasp, with respect to a chosen metric, or continues running until a user defined confidence level is met.
+We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
+We then treat the MAB algorithm as an anytime algorithm that terminates once a user defined confidence level is met or at a given stopping time.
 
-We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
-We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, grasp approach direction, and friction coefficient.
+We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, gripper approach, and friction coefficient.
 We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
 We model uncertainty in pose as a normal distribution around the orientation and 2D position of the object.
-Furthermore, we model uncertainty in motion as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper and uncertainty in friction coefficient as a normal distribution around an expected friction coefficient.
+We chose to model uncertainty in grasp approach as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper.
+We model uncertainty in friction coefficient as a normal distribution around an expected friction coefficient.
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem against uniform allocation and an adaptive sampling method known as Iterative Pruning, which reduces the set size based on sample mean~\cite{kehoe2012toward}, on the task of finding grasps with high probability of force closure.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as Iterative Pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}.
+In the task of finding grasps with high probability of force closure.
 We compare on the Brown Vision 2D Dataset, a dataset of 2D object silhouettes~\cite{brown, christopoulos2007handling}.
-Our initial results show that Thompson Sampling, a MAB algorithm, required $439\%$ fewer samples than Iterative Pruning to get within $2.5\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+Our initial results in simulation show that the Gittins Index, a MAB algorithm, required $808\%$ fewer samples than Iterative Pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 
@@
 
-Most research on grasp planning focuses on finding grasps by maximizing a grasp quality metric when object shape, object pose, and locations of contact with an object are precisely known~\cite{cheong2011output, ciocarlie2009}.
+Most research on grasp planning focuses on finding grasps by maximizing a grasp quality metric.
 Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
-Past work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
+Analytical quality metrics typically assume precisely known object shape, object pose, and locations of contact~\cite{cheong2011output, ciocarlie2009}.
+Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005} Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning\cite{brook2011collaborative, hsiao2011bayesian}.
 
-Recent work has studied the effects of uncertainty in object pose and gripper positioning.
 Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
-Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot grasps planned using deterministic wrench space metrics on objects from the Columbia Grasp Database.
-Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose, and also found that the planned grasps were more successful on a physical robot than thoise planned with classical wrench space metrics.
+Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics.
+Similarly, Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose.
+They also found that the planned grasps were more successful on a physical robot than those planned with classical wrench space metrics.
 
@@
 
-Some probabilistic grasp quality measures, such as probabilty of force closure, use Monte-Carlo integration to evaluate grasp quality~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
-This involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
-\todo{Should we call using Monte-Carlo Integration and sorting grasps Brute Force? I am worried it might come off as offensive to prior work}
-It can be computationally expensive though to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure known as Iterative Pruning, which periodically discards a subset of the grasps that seem unlikely to be of high quality.
-However, the method pruned grasps using only the sample mean and did not utilize any confidence interval around the current estimate, which can discard good grasps.
+Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
+Monte-Carlo involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
+However, it can be computationally expensive to sample all proposed grasps to convergence.
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called Iterative Pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
+However, the method pruned grasps using only the sample mean, which could discard good grasps.
 We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.
@@
 \subsection{MAB Model}
-\todo{You mentioned this section might seem condescening to the OR community. It be great if you can point out specifics here}
+\todo{Ken, you mentioned this section might seem condescending to the OR community. It be great if you can point out specifics here}
 The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
@@
 When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution that is unknown to the gambler.
-The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them to maximize the sum of average rewards over all pulls.
+The goal of the gambler is to come up with a method to maximize the sum of average rewards over all pulls.
 If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
-However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest reward and exploring new arms to see if they give better rewards on average.
-Developing a policy that successfully trades between exploration and exploitation to maximize average reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
+However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest expected reward and exploring new arms.
+Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
 
@@
 
-\subsection{Algorithms for MAB}\label{sec:bandit_algorithm}
-We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on certain problems~\cite{chapelle2011empirical, bachman2013greedy}.
-Theoretical results have shown that several algorithms are capable of achieving near the lower bound on the asymptotic rate of convergence in regret described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
-%However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
-%In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.
-
+\subsection{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}
+We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}.
+Bayesian methods have been shown empirically to outperform frequentist algorithms (e.g., UCB)~\cite{chapelle2011empirical, bachman2013greedy}.
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
 For instance a Bernoulli random variable, $p$, can be used to represent a binary grasping metric like force closure.
-The prior traditionally placed on a Bernoulli variable is its conjugate prior, the Beta distribution.
+The prior typically placed on a Bernoulli variable is its conjugate prior, the Beta distribution.
 Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
@@
 At timestep $t=0$, we pull arm $k$ and observe reward $R_{k,0}$, where $R_{k,0} \in \lbrace 0, 1\rbrace$.
-The posterior of the Beta after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}, \beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+The posterior of the Beta after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}$  $\beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 
-Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$ at time $t$, the algorithm can predict the probability of an event occurring, $p_{k,t}$, on the next iteration by taking the expected value:
+Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$ at time $t$, the algorithm can calculate the expected Bernoulli parameter, $\bar{p}_{k,t}$, as follows:
 %Thus, we can write the expected probability of force closure as follows
@@
 
-Methods such as Value Iteration can compute optimal policies for an MDP with respect to the discount factor $\gamma$ when all states, actions, and expected rewards can be enumerated~\cite{weber1992gittins,barto1998reinforcement}.
+Methods such as Value Iteration can compute optimal policies for a discrete MDP with respect to the discount factor $\gamma$ ~\cite{barto1998reinforcement}.
 However, the curse of dimensionality effects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in $K$.
-A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$.
+A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ \cite{weber1992gittins}.
 
@@
 Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$.
-Thompson sampling is a less computationally expensive alternative.
+The problem with this is that the effective time horizon is a function of $\gamma$.
+Thus, if your actual horizon is longer than the effective horizon, the method has a policy of Follow the Leader, where it only pulls the current estimate of the best arm \cite{kelly1981multi}.
+Thompson sampling is an alternative to the GIttins Index method that isn't prone to such a problem.
 All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
@@
 Theoretically, Agrawal et al.
-recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that was sub-linear  for $k$ -arms and in the case of $2$ arms logarithmic \cite{agrawal2011analysis}.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that was sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms  \cite{agrawal2011analysis}.
 
@@
 We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
-We consider uncertainty in shape, pose, gripper approach, and friction coefficient and we assume that distributions on these quantities are given and can be sampled from.
+We consider uncertainty in shape, pose, gripper approach, and friction coefficient. We assume that the distributions on these quantities are given and can be sampled from.
 
@@
 %We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
-\todo{The next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
-Given a grasp plan and a deterministic object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
+\todo{Ken, the next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
+Given a grasp plan and a object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
 We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu \in \mathbb{R}$.
@@
 \subsection{Sources of Uncertainty}
-In this work we consider uncertainty in shape, pose, approach, and friction coefficient.
+We consider uncertainty in shape, pose, approach, and friction coefficient.
 Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
-In this section we describe each source of uncertainty and our model of the uncertainty.
+In this section, we describe our model of each source of uncertainty.
 
@@
 See Mahler et al. for details on how to estimate a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
-Following Mahler et al., we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
 For convenience, in later sections we will refer to the GPIS parameters as $\theta = \lbrace \mu_{f}(\bx), \Sigma_{f}(\bx) \rbrace$.
@@
  \subsubsection{Friction Uncertainty}
-As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
+As shown in \cite{zheng2005,hang2013a}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
 However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
@@
 $P(\Gamma_{\bar{k}})$, the probability of force closure for the grasp returned by the algorithm $\Gamma_(\bar{k})$.
-As illustrated, Gittins and Thompson return a grasp plan that on average has a higher probability of force closure than uniform allocation and Iterative Pruning .
-For illustrative purposes in Fig.
+Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
+Gittins Indices and Thompson Sampling  perform significantly better, converging after only 4000 and 2000 iterations.For illustrative purposes in Fig.
 \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp plan returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
@@
 
-We also compared the methods by the number of samples each allocated to the top $10\%$ of grasps in terms of the pprobabilty of force closure estimated by brute force.
+We also compared the methods by the number of samples each allocated to the top $10\%$ of grasps in terms of the probability of force closure estimated by brute force.
 We found that Thompson Sampling allocates 29$\%$ of the total number of samples to the top $10\%$ of grasps and Gittins allocates 23$\%$ of total samples.
 Uniform allocation and Iterative Pruning allocate approximately $1\%$  and $6\%$ of total samples, respectively.
-In Fig. \ref{fig:pulls_per_grasp} we plot samples per grasp quality.
 The MAB appear to allocate more samples to higher quality grasps, which may explain the ability to find grasps with a higher probability of force closure faster.
-
-\begin{figure}[t!]
-
-\centering
-\includegraphics[scale=0.25]{matlab_figures/pulls_per_grasp.eps}
-\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Thompson, Gittins, uniform allocation and Iterative Pruning).
-Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
-The best grasps are ranked 1 and worst are 1000.
-As illustrated the MAB algorithms intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation.
-}
-
-\vspace*{-10pt}
-\label{fig:pulls_per_grasp}
-\end{figure}
 
@@
 \includegraphics[scale=0.25]{matlab_figures/confidence_bounds.eps}
-\caption{ \footnotesize \todo{We might want to condense Fig 6 and Fig.
-4.
-The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, Iterative Pruning and uniform allocation.
+\caption{ The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, Iterative Pruning and uniform allocation.
 Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
@@
     \centering
-    \includegraphics[width=16.5cm]{figures/shapes.png}%
+    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
 
-    \caption{\todo{Need to change this figure, wondering what should be conveyed here}Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
+    \caption{Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
 The four methods (uniform allocation, Iterative Pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|\mG|=1000$.
@@
 \subsection{Sensitivity Analysis }\label{sec:sensitivity}
-\todo{need to redo with larger number of shapes}
+\todo{need to redo with larger number of shapes (Running experiments today)}
 We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose and use that to set the parameters for future experiments.
@@
 A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
-Initial results have shown our MAB approach to outperform the methods of prior work, uniform allocation and Iterative Pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
+Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and Iterative Pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
 However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
 Fortunately, the probability of many successive samples being misleading approaches zero at an exponential rate as the time horizon is increased.
+
+The question about what MAB algorithm to use, Thompson Sampling or Gittins Indices.
+Is left to the application the user is considering.
+Empirically, we showed Gittins indices are able to return a grasp that is within $3\%$ of the best grasp 2x faster than Thompson Sampling.
+However because we aren't able to compute a higher discount factor than $\gamma = 0.98$, the method is prone to only pulling the best arm \cite{kelly1981multi}.
+Thompson sampling avoids this problem and is able to find the best grasp in the set \cite{agrawal2011analysis}, but empirically was shown to require more samples than the Gittins to reach $3\%$ of the best grasp.
 

### 2015-03-15 paper.tex
v15

@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v11 March 13, 2015 ] }
+Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty  [v15 March 15, 2015 ] }
 
@@
 One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-This can be computationally demanding.
+This can be computationally demanding and prior work has turned to cloud based computing to solve it.
 To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context.
-We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
+We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
 We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
 Non-MAB methods, uniform allocation and iterative pruning, converge slowly.
-In contrast, the MAB methods we consider, Thompson Sampling and the Gittins Index, were more efficient in experiments, converging to within 3\% of the optimal grasp 10x faster than non-MAB methods.
+In contrast, the MAB methods we consider, Thompson Sampling and the Gittins Index, were more efficient in experiments, converging to within 3\% of the optimal grasp approximately 5x faster than non-MAB methods.
 \end{abstract}
@@
 Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
-Planning grasps using analytic methods requires the contact locations and surface normals.
+Planning grasps using analytic methods requires knowledge of contact locations and surface normals.
 However, a robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
@@
 
-    \caption{\todo{figure is only averaged over 40 shapes, rerunning the experiments (Shouldn't change earlier results on (TS, IP and UA ) once done)} Grasp quality over time for 4 sample-based planning methods compared with optimal grasp determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
-Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp angles.
-Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
-Two Multi-Arm Bandit methods perform significantly better, converging after only 4000 and 2000 iterations.
+    \caption{Normalized grasp quality over time of the returned grasp for 4 sample-based planning methods.
+Normalization divides the current quality of grasp, $P_F(\Gamma_{\bar{k}})$ returned by the highest probability of force closure in the candidate grasp set $P_F(\Gamma^*)$.
+The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
+Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
+Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal (the dashed grey line), requiring approximately 40,000 and 20,000 iterations.
+Two Multi-Arm Bandit methods perform significantly better, converging after only 4000 iterations..
 }%
@@
 
-One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.To cope with uncertainty, recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One way to compute the probability of force closure is using Monte-Carl integration over sample perturbations in the uncertain quantities\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
+One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
+To cope with uncertainty, recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
+One way to compute the probability of force closure is using Monte-Carlo integration over sample perturbations in the uncertain quantities\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
+Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
+We show that the Multi-armed Bandit (MAB) model improves upon this brute force approach and could hopefully lead to more efficient cloud based algorithms.
 
-We show that by using a Multi-Armed Bandit (MAB) model it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
 In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
@@
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as Iterative Pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}.
 In the task of finding grasps with high probability of force closure.
-We compare on the Brown Vision 2D Dataset, a dataset of 2D object silhouettes~\cite{brown, christopoulos2007handling}.
-Our initial results in simulation show that the Gittins Index, a MAB algorithm, required $808\%$ fewer samples than Iterative Pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 
@@
 However, it can be computationally expensive to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called Iterative Pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
 However, the method pruned grasps using only the sample mean, which could discard good grasps.
@@
 \subsection{MAB Model}
-\todo{Ken, you mentioned this section might seem condescending to the OR community. It be great if you can point out specifics here}
 The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
@@
 Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
-Lai and Robbins showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
+Lai and Robbins\cite{lai1985asymptotically} showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls.
 They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
@@
 One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
-Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
+Formally, a MDP is defined as a set of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
 In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,t}$ and $\beta_{k,t}$.
@@
 The problem with this is that the effective time horizon is a function of $\gamma$.
-Thus, if your actual horizon is longer than the effective horizon, the method has a policy of Follow the Leader, where it only pulls the current estimate of the best arm \cite{kelly1981multi}.
-Thompson sampling is an alternative to the GIttins Index method that isn't prone to such a problem.
+Thus, if the actual horizon is longer than the effective horizon, the method can only pull the current estimate of the best arm \cite{kelly1981multi}.
+Thus, no longer trading off exploration and exploitation.
+Thompson sampling is an alternative to the Gittins Index method that isn't prone to such a problem.
 All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
 Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
-A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. This is repeated until a stopping time is reached. The full algorithm is shown in Algorithm 2.
+A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. The full algorithm is shown in Algorithm 1.
 
@@
 The grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
-We formulate the MAB problem for 2-dimensional objects using parallel-jaw grippers.
+We formulate the MAB problem for planar objects using parallel-jaw grippers.
 Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$.
 The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathbb{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$.
-We define a grasp plan consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.
+We define a grasp consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.
 
 %We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
-\todo{Ken, the next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
-Given a grasp plan and a object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
+
+Given a grasp and an object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
 We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu \in \mathbb{R}$.
@@
 Friction coefficient is independent of this relationship.
-The box around contact and normals means they are repeated nodes, in this case we have $m=2$ corresponding to the two jaws in the gripper.
 }
@@
 
-Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
+Uncertainty in object shape results from sensor imprecision and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
 Following ~\cite{mahler2015gp}, we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
@@
  \subsubsection{Approach Uncertainty}
-In practice a robot may not be able to execute a desired grasp plan $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
-We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
+In practice a robot may not be able to execute a desired grasp $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
+We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp $\Gamma$.
 Formally, let $\hat{\by} = \frac{1}{2} (\bj_1 + \bj_2)$ denote the center of a planned grasp axis and $\hat{\psi}$ denote the angle that the planned axis $\bj_1 - \bj_2$ makes with the x-axis of the 2D coordinate system on our shape representation.
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$.
+We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp $\Gamma$.
 Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
@@
 
-One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
+One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
 We refer to this as a brute force approach. 
 This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
-More recent work has considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
+More recent work has considered adaptive sampling to discard grasps that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.
 
-To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_{k,t}$ at time $t$ up to a given time $T_s$:
+To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp  $\Gamma_{k,t}$ at time $t$ up to a given time $T_s$:
 \begin{align}
@@
 We frame the grasp selection problem of \secref{objective} as a MAB problem.
-Each arm corresponds to a different grasp plan, $\Gamma_k$, and pulling an arm corresponds to sampling from the graphical model in Fig.
+Each arm corresponds to a different grasp, $\Gamma_k$, and pulling an arm corresponds to sampling from the graphical model in Fig.
 \ref{fig:graphical_model} and evaluating the force closure condition.
-Since force closure is a binary value, each grasp plan $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
+Since force closure is a binary value, each grasp $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
 In a MAB, we want to try and minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.
@@
 \end{align}
-\noindent where the $\bar{k}$ grasp plan refers to the grasp with the highest estimated $P_F$ at time $t$.
+\noindent where the $\bar{k}$ grasp refers to the grasp with the highest estimated $P_F$ at time $t$.
 
 \section{Simulation Experiments}
-We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D object silhouettes, as in \cite{christopoulos2007handling}.
+We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
 GPIS models of 3 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The measurement noises were assigned uniformly at random to the grid cells.
+The measurement noise were assigned uniformly at random to the grid cells.
 We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
@@
 We also performed experiments for the case of two hard contacts in 2-D.
-We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
+We drew random grasps $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
+All experiments were run on machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2014a.
 
@@
 \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, Iterative Pruning \cite{kehoe2012toward} and uniform allocation).
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
-Iterative Pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
+iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
 We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time.
 
-\todo{This might still be vague} In Fig.
-\ref{fig:grasp_quality}, we plot the grasp returned at time $t$ vs.
-$P(\Gamma_{\bar{k}})$, the probability of force closure for the grasp returned by the algorithm $\Gamma_(\bar{k})$.
-Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
-Gittins Indices and Thompson Sampling  perform significantly better, converging after only 4000 and 2000 iterations.For illustrative purposes in Fig.
-\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp plan returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
+In Fig.
+\ref{fig:grasp_quality}, we plot time $t$ vs.
+$P(\Gamma_{\bar{k}})$, the probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
+Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
+Gittins Indices and Thompson Sampling  perform significantly better, converging after only 4000 iterations.For illustrative purposes in Fig.
+\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
+
+The time per iteration,$t_{i}$, of each algorithm is calculated as follows $t_{i} = t_{a}+t_{sp}$.
+$t_{a}$ is the time to decide which arm to pull next and $t_{sp}$ is the time taken to draw a sample from the graphical model in Fig.
+\ref{fig:graphical_model}.
+The time per iteration for Thompson Sampling, Gittins Indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms.
+Most of $t_{i}$ is dominated by sampling time, since $t_{sp} = 30$ms.
 
@@
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Thompson Sampling, Iterative Pruning\cite{kehoe2012toward} and uniform allocation.
-\todo{How should we quantify this?
-Uniform allocation never gets a low confidence over the number of samples we used.} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
-
-We also compared the methods by the number of samples each allocated to the top $10\%$ of grasps in terms of the probability of force closure estimated by brute force.
-We found that Thompson Sampling allocates 29$\%$ of the total number of samples to the top $10\%$ of grasps and Gittins allocates 23$\%$ of total samples.
-Uniform allocation and Iterative Pruning allocate approximately $1\%$  and $6\%$ of total samples, respectively.
-The MAB appear to allocate more samples to higher quality grasps, which may explain the ability to find grasps with a higher probability of force closure faster.
+\ref{fig:confidence} for Thompson Sampling, iterative pruning\cite{kehoe2012toward} and uniform allocation.
+As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
 
@@
 \includegraphics[scale=0.25]{matlab_figures/confidence_bounds.eps}
-\caption{ The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, Iterative Pruning and uniform allocation.
-Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object.
+\caption{ The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, iterative pruning and uniform allocation.
+Graph is averaged over 100 objects from the Brown Vision Lab 2D Dataset \cite{brown} with a set $|G|=1000$ for each object.
 The sharper decrease in confidence interval corresponds to more samples being allocated for the return grasp.
@@
     \caption{Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
-The four methods (uniform allocation, Iterative Pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|\mG|=1000$.
+The four methods (uniform allocation, iterative pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|\mG|=1000$.
 We also show the grasp returned by the brute force approach of exhaustively sampling every grasp in the set.
@@
 \subsection{Sensitivity Analysis }\label{sec:sensitivity}
-\todo{need to redo with larger number of shapes (Running experiments today)}
 We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose and use that to set the parameters for future experiments.
 The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
-All experiments were averaged across 10 shapes randomly selected with from the Brown dataset with $|\mG| = 1000$, or 1000 grasp plans $\Gamma$.
+All experiments were averaged across 10 objects randomly selected with from the Brown dataset with $|\mG| = 1000$, or 1000 grasps, $\Gamma$.
 
@@
 For translational uncertainty in pose, we varied $\sigma_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation and an increased noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
+As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation and an increased noise of $\sigma_{\bt} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
 
@@
 It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
-Interestingly, Thompson sampling appears to to continute to improvement while Gittins indices and Iterative Pruning are stuck in local optimal.
+Interestingly, Thompson sampling appears to to continute to improvement while Gittins indices and iterative pruning are stuck in local optimal.
 This is because Thompson sampling is guaranteed to find the best grasp in the limit of infinite iterations \cite{agrawal2011analysis}.
@@
 \includegraphics[scale=0.25]{matlab_figures/worst_case.eps}
-\caption{ \footnotesize Comparison of the current average probability of force closure vs.
+\caption{ \footnotesize 
+Comparison of the current average normalized probability of force closure vs.
 the stopping time $T_s$ for the pathological case where the samples are sorted to be misleading.
-The graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.
-We demonstrate this for Thompson, Gittins, uniform allocation and Iterative Pruning \cite{kehoe2012estimating}.
-We also demonstrate what the average highest probability of force closure is when the brute force approach of exhaustively sampling each candidate grasp is used.
-Empirically, it appears that when samples are misleading the best policy is uniform allocation.
+Normalization divides the quality of the  grasp returned ,$P_F(\Gamma_{\bar{k}})$, by the highest probability of force closure in the set of  candidate grasps,$P_F(\Gamma_*)$.
+The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
+Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
+We demonstrate this for Thompson, Gittins, uniform allocation and iterative pruning \cite{kehoe2012estimating}.Empirically, it appears that when samples are misleading the best policy is uniform allocation.
 However, it also illustrated that Thompson sampling can recover from this situation where Gittins and Kehoe et al.
@@
  \hline
-Translation Variance in Pose, $\sigma_{\bt}$ & 1210    & 2207 &  8763\\
-Friction Coefficient Variance, $\sigma_{\mu}$ &  1985  & 1456   & 1876\\
-Rotational Variance in Pose, $\sigma_{\phi}$ & 4230 & 4431 &  4432\\
+Translation Variance in Pose, $\sigma_{\bt}$ & 4210    & 5207 &  8763\\
+Friction Coefficient Variance, $\sigma_{\mu}$ &  4985  & 4456   & 4876\\
+Rotational Variance in Pose, $\sigma_{\phi}$ & 4230 & 5431 &  6432\\
  \hline
 \end{tabular}
-   \caption { \footnotesize  Sensitivity Analysis for convergence to estimated best grasp for Thompson Sampling under rotational variance $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 10 objects from the Brown Vision Lab Data set.
+   \caption { \footnotesize  Sensitivity Analysis for convergence to within $3\%$ of estimated best grasp in the set for Thompson Sampling under rotational variance $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 100 objects from the Brown Vision Lab Data set.
 The sensitivity analysis shows that large variance in translational uncertainty in pose can increase the amount of iterations needed for the bandit algorithm to converge to the highest quality grasp in the set.
@@
 A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
-Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and Iterative Pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
+Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
 However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
@@
 
-The question about what MAB algorithm to use, Thompson Sampling or Gittins Indices.
-Is left to the application the user is considering.
-Empirically, we showed Gittins indices are able to return a grasp that is within $3\%$ of the best grasp 2x faster than Thompson Sampling.
-However because we aren't able to compute a higher discount factor than $\gamma = 0.98$, the method is prone to only pulling the best arm \cite{kelly1981multi}.
-Thompson sampling avoids this problem and is able to find the best grasp in the set \cite{agrawal2011analysis}, but empirically was shown to require more samples than the Gittins to reach $3\%$ of the best grasp.
+In future work, we plan to scale our method to 3D objects.
+However, this could substantially increase the number of candidate grasps.
+One option to solving this problem is to use the cloud to solve subsets of the MAB problem in parralel.
+By dividing up the MAB into batches of arms and solving each batch in parallel, we can hopefully maintain similar performance as in this paper.
 
-In future work, we plan to scale our method to 3D objects. However, this could substantially increase the number of candidate grasp plans.
-To handle a much larger amount of arms, it may be useful to have some measure of correlation between the arms.
-For example, if two grasps contact an object at spatially close locations, then their measure of probability of force closure may be correlated.
-Appropriate features that represent a grasp or object under uncertainty and the grasp quality metric are still open questions and will be an ongoing project for future work. 
 \bibliographystyle{IEEEtranS}

### 2015-03-15 paper.tex
Updated a figure 2 and captions for figure 1 / 2

@@
 
-    \caption{Normalized grasp quality over time of the returned grasp for 4 sample-based planning methods.
+    \caption{Iterations versus the normalized probability of force closure $P_F$ for the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
+    %We evaluated performance on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
+    The normalized $P_F$ is the ratio of the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
+    The highest quality grasp was determined by brute force search over all candidate grasps~\cite{kehoe2012toward}.
+    Uniform allocation and iterative pruning converge to within 3$\%$ of the optimal (the dashed grey line) in approximately 40,000 and 20,000 iterations, respectively.
+    In comparison, the MAB methods both converge in approxmately 4,000 iterations. 
+%    $P_F(\Gamma_{\bar{k}})$ (ratio of $P_F(\Gamma_{\bar{k}})$ to $P_F(\Gamma^*)$)
+%    
+%    Normalized grasp quality over time of the returned grasp for 4 sample-based planning methods.
 Normalization divides the current quality of grasp, $P_F(\Gamma_{\bar{k}})$ returned by the highest probability of force closure in the candidate grasp set $P_F(\Gamma^*)$.
@@
 Two Multi-Arm Bandit methods perform significantly better, converging after only 4000 iterations..
-}%
+	}
     \label{fig:grasp_quality}
@@
 \includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
-\caption{llustration of our grasping model for parallel jaw grippers on a mechanical switch.
+\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch.
 Jaw placements are illustrated by a red direction arrow and line.
-A grasp plan consists of 2D locations for each of the parallel-jaws $\bj_1$ and $\bj_2$.
+A grasp plan centered at $\by$ (plus symbol) at angle $\psi$ consists of 2D locations for each of the parallel jaws $\bj_1$ and $\bj_2$.
 When following the grasp plan, the jaws contact the object at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations.
@@
 \caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
-As illustrated uncertainty in pose, motion and shape affect the contacts and surface normals that makes up the grasp.
+As illustrated uncertainty in pose, approach, and shape affect the contacts and surface normals that makes up the grasp.
 Friction coefficient is independent of this relationship.
@@
 We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp $\Gamma$.
-Formally, let $\hat{\by} = \frac{1}{2} (\bj_1 + \bj_2)$ denote the center of a planned grasp axis and $\hat{\psi}$ denote the angle that the planned axis $\bj_1 - \bj_2$ makes with the x-axis of the 2D coordinate system on our shape representation.
+Formally, let $\hat{\by} = \frac{1}{2} (\bj_1 + \bj_2)$ denote the center of a planned grasp axis and $\hat{\psi}$ denote the clockwise angle that the planned axis $\bj_1 - \bj_2$ makes with the y-axis of the 2D coordinate system on our shape representation.
 We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
@@
     \centering
-    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
 

### 2015-03-15 paper.tex
added Steve's feedback, cloud, and gittins

--- 2015-03-15 paper.tex
@@
 One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-This can be computationally demanding and prior work has turned to cloud based computing to solve it.
-To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context.
+Prior work has turned to cloud based computing to solve it This can be computationally demanding and .
+To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
 We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
@@
 Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
-We show that the Multi-armed Bandit (MAB) model improves upon this brute force approach and could hopefully lead to more efficient cloud based algorithms.
+We show that this brute force approach can be improved upon in terms by efficiency by treating the problem as  Multi-armed Bandit(MAB).
 
-Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+Our contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
 In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
@@
 However, it can be computationally expensive to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed a parallelizable adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
 However, the method pruned grasps using only the sample mean, which could discard good grasps.
-We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.
+We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations ~\cite{barto1998reinforcement, lai1985asymptotically}.
+The MAB method is still parallizable if you divide up the divide up the arms into sub-problems \cite{glazebrook2000index}
 
@@
 
-A traditional MAB example is a gambler with $K$ independent one-armed bandits, also known as slot machines.
+A traditional MAB example is a gambler with $K$ independent slot machines, also known as one-armed bandits.
 When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution that is unknown to the gambler.
-The goal of the gambler is to come up with a method to maximize the sum of average rewards over all pulls.
+The goal of the gambler is to maximize the sum of average rewards over all pulls.
 If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
@@
 The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
-Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
-\cite{katehakis1987multi} due to its ability to be implemented in a dynamic programming fashion.
+Consult \cite{gittins2011multi} for a more detailed analysis of the Gittins method.
+The indices can be  computed offline using a variety of methods \cite{weber1992gittins}; we chose to use the restart method proposed by Katehakis et al.
+\cite{katehakis1987multi} because it can be implemented in a dynamic programming fashion.
 
@@
 Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$.
-The problem with this is that the effective time horizon is a function of $\gamma$.
-Thus, if the actual horizon is longer than the effective horizon, the method can only pull the current estimate of the best arm \cite{kelly1981multi}.
-Thus, no longer trading off exploration and exploitation.
-Thompson sampling is an alternative to the Gittins Index method that isn't prone to such a problem.
-All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
-Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
-A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. The full algorithm is shown in Algorithm 1.
+In the case of finding the best arm, we want to plan for long term reward and thus have a high discount factor.
+A smaller $\gamma$ can lead to the policy only pulling the most promising arm and not exploring \cite{kelly1981multi}.Thompson Sampling is an alternative to the Gittins Index method that isn't prone to such a problem.
+In Thompson Sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
+A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated.
+All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.The full algorithm is shown in Algorithm 1.
 
-The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
+The intuition for Thompson Sampling is that the random samples of $p_{k,t}$ allow the method to explore.
+However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn approaches infinity \cite{goetschalckx2011continuous}.
 Chapelle et al.
@@
 \subsection{Candidate Grasp Model}
-The grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
-We formulate the MAB problem for planar objects using parallel-jaw grippers.
+ We formulate the MAB problem for planar objects using parallel-jaw grippers as modeled in Fig.~\ref{fig:grasp_model}.
 Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$.
@@
 However, this could substantially increase the number of candidate grasps.
-One option to solving this problem is to use the cloud to solve subsets of the MAB problem in parralel.
-By dividing up the MAB into batches of arms and solving each batch in parallel, we can hopefully maintain similar performance as in this paper.
+Glazebrook and Wilkinson showed that the Gittins Index method could be parallelized by simply pulling the top $M$ arms, where $M$ is the number of cores and achieve better performance \cite{glazebrook2000index}.
+A similar method could also be done for Thompson sampling.
+Another promising scheme for parrallelizing the MAB, is to divide up the MAB into batches of arms have each core solve the smaller MAB.
+We will explore both of these approaches in future work.
 

### 2015-03-16 paper.tex
Added new captions for all figures and revised Table I to be more clear

--- 2015-03-15 paper.tex
@@
 
+\usepackage{tabularx}
 \usepackage{tikz,hyperref,graphicx,units,subfig}
@@
 \newcommand{\minksum}{\operatorname{MinkowskiSum}}
+
+\newcommand{\specialcell}[2][c]{ \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
+
+\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
+\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
+
+\newcolumntype{L}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
+\newcolumntype{R}[1]{>{\RaggedLeft\hspace{0pt}}p{#1}}
 
@@
 
-    \caption{Iterations versus the normalized probability of force closure $P_F$ for the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
+    \caption{Number of samples versus the normalized probability of force closure $P_F$ for the best estimated grasp after $k$ samples, $P_F(\Gamma_{\bar{k}})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
     %We evaluated performance on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
@@
 Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$.
-The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathbb{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$.
+The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathbb{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2||_2 \leq w_g$.
 We define a grasp consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.
@@
 \subsection{Sources of Uncertainty}
-We consider uncertainty in shape, pose, approach, and friction coefficient.
-Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
+We consider uncertainty in object shape, object pose, grasp approach angle, and friction coefficient.
+Fig.~\ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
 In this section, we describe our model of each source of uncertainty.
@@
 \includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
-\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object.
-As illustrated uncertainty in pose, approach, and shape affect the contacts and surface normals that makes up the grasp.
-Friction coefficient is independent of this relationship.
+\caption{A graphical model of the relationship between the uncertain parameters we consider.
+Uncertainty in object shape, object pose, and grasp approach angle affect the points of contact  between the gripper and object and the surface normals at the contacts.
+Uncertainty in friction coefficient affects forces and torques that are used to compute the probabilty of force closure.
 }
@@
 \includegraphics[scale=0.25]{matlab_figures/confidence_bounds.eps}
-\caption{ The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, iterative pruning and uniform allocation.
-Graph is averaged over 100 objects from the Brown Vision Lab 2D Dataset \cite{brown} with a set $|G|=1000$ for each object.
-The sharper decrease in confidence interval corresponds to more samples being allocated for the return grasp.
+\caption{ Number of samples versus the $95\%$ confidence intervals on the probability of force closure of the best estimated grasp after $k$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
+The values are averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset~\cite{brown} with 1,000 candidate grasps for each object.
+An increasingly narrow confidence interval indicates that the algorithm allocated an increasing number of samples to its estimate of the best grasp.
 }
@@
     %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
-
-    \caption{Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
-The four methods (uniform allocation, iterative pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|\mG|=1000$.
-We also show the grasp returned by the brute force approach of exhaustively sampling every grasp in the set.
-The grasps and the quality each one found is shown above.
-In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $10,000$, however at the last shape there is a difference of $2\%$ grasp quality.}%
+    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
+For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples.
+The candidate grasp set was of size $|\mG|=1000$.
+We visualize the GPIS representation of the object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.
+On objects A and B Thompson sampling finds the best grasp after 10,000 samples, but for object C the grasp selected has $2\%$ lower $P_F$.}%
     \label{fig:shape_samples}%
@@
 \caption{ \footnotesize 
-Comparison of the current average normalized probability of force closure vs.
-the stopping time $T_s$ for the pathological case where the samples are sorted to be misleading.
-Normalization divides the quality of the  grasp returned ,$P_F(\Gamma_{\bar{k}})$, by the highest probability of force closure in the set of  candidate grasps,$P_F(\Gamma_*)$.
+	Number of samples versus the probability of force closure of the best estimated grasp after $k$ samples $P_F(\Gamma_{\bar{k}})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
+	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
  	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
-Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
-We demonstrate this for Thompson, Gittins, uniform allocation and iterative pruning \cite{kehoe2012estimating}.Empirically, it appears that when samples are misleading the best policy is uniform allocation.
-However, it also illustrated that Thompson sampling can recover from this situation where Gittins and Kehoe et al.
-are not able to and get stuck in local solutions.
-}
+ 	The results suggest that when samples are misleading the best policy is uniform allocation.
+	However, Thompson sampling appears to continue making progress whereas iterative pruning and Gittins indices do not.}
 \vspace*{-10pt}
@@
 
-\begin{table*}[t]
+\begin{table}[t]
 \centering
-\begin{tabular}{ |p{4.5cm}||p{2cm}|p{2.5cm}|p{2cm}|  }
+\begin{tabular}{ R{1.75cm}||R{1.65cm}|R{1.65cm}|R{1.65cm}  }
+ %\hline
+ %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson Sampling} \\
+ %\hline 
+ & \multicolumn{3}{c}{$\#$ of Samples Until Convergence} \\
  \hline
- \multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson Sampling} \\
+\specialcell{\bf Uncertainty\\ \bf Type} & \specialcell{\bf Low\\ \bf Uncertainty} & \specialcell{\bf Medium \\ \bf Uncertainty} & \specialcell{\bf High\\\bf Uncertainty}\\
  \hline
-Uncertainty Type & Low Uncertainty ($\#$ of Iterations) & Medium Uncertainty ($\#$ Iterations) & High Uncertainty ($\#$ of Iterations)\\
- \hline
-Translation Variance in Pose, $\sigma_{\bt}$ & 4210    & 5207 &  8763\\
-Friction Coefficient Variance, $\sigma_{\mu}$ &  4985  & 4456   & 4876\\
-Rotational Variance in Pose, $\sigma_{\phi}$ & 4230 & 5431 &  6432\\
- \hline
+Orientation $\sigma_{\phi}$ & 4230 & 5431 &  6432\\
+Position $\sigma_{\bt}$ & 4210    & 5207 &  8763\\
+Friction $\sigma_{\mu}$ &  4985  & 4456   & 4876\\
+ %\hline
 \end{tabular}
-   \caption { \footnotesize  Sensitivity Analysis for convergence to within $3\%$ of estimated best grasp in the set for Thompson Sampling under rotational variance $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  translation uncertainty $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units  friction coefficient uncertainty $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$  from left to right on a 40 x 40 unit workspace averaged over 100 objects from the Brown Vision Lab Data set.
-The sensitivity analysis shows that large variance in translational uncertainty in pose can increase the amount of iterations needed for the bandit algorithm to converge to the highest quality grasp in the set.
+   \caption { \footnotesize  Number of iterations until convergence to within $3\%$ of grasp with the highest estimated probability of force closure $P_F$ for Thompson Sampling under uncertainty in the object orientation $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  uncertainty in the object position $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units, and uncertainty in friction coefficient $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$ on a 40$\times$40 grid averaged over 100 independent runs on random objects from the Brown Vision 2D Dataset.
+High variances in position and orientation uncertainty increases the amount of iterations needed for the bandit algorithm to converge.
    }
@@
 \vspace*{-20pt}
-\end{table*}
+\end{table}
 

### 2015-03-16 paper.tex
v15

--- 2015-03-15 paper.tex
@@
 
+\pdfcompresslevel=9
+\pdfobjcompresslevel=9
 %\overrideIEEEmargins                                      % Needed to meet printer requirements.
@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty  [v15 March 15, 2015 ] }
+Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty }
 
@@
 One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-Prior work has turned to cloud based computing to solve it This can be computationally demanding and .
+\todo{fix this}Prior work has turned to cloud based computing to solve it This can be computationally demanding and.
 To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
@@
     \centering
-     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc.eps} }}%
+     \subfloat{{\includegraphics[scale=1]{matlab_figures/pfc-01.jpg} }}%
 
@@
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
-We show that this brute force approach can be improved upon in terms by efficiency by treating the problem as  Multi-armed Bandit(MAB).
+Past work has looked at using parallel programming in the cloud to overcome this hurdle ~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
+We try to extend these cloud based methods by reducing the number of samples needed.
 
@@
 We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
-We then treat the MAB algorithm as an anytime algorithm that terminates once a user defined confidence level is met or at a given stopping time.
+We then treat MAB algorithms as an anytime algorithms that terminate once a user defined confidence level is met or at a given stopping time.
 
@@
 We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+We demonstrate performance on a local implementation.
+However, our methods are parallelizable by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separate \cite{glazebrook2000index}.
 Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
@@
 Analytical quality metrics typically assume precisely known object shape, object pose, and locations of contact~\cite{cheong2011output, ciocarlie2009}.
-Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005} Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning\cite{brook2011collaborative, hsiao2011bayesian}.
+Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
+Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning\cite{brook2011collaborative, hsiao2011bayesian}.
 
@@
 We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations ~\cite{barto1998reinforcement, lai1985asymptotically}.
-The MAB method is still parallizable if you divide up the divide up the arms into sub-problems \cite{glazebrook2000index}
 
@@
 However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest expected reward and exploring new arms.
-Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
+Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation  ~\cite{bergemann2006bandit},\cite{bubeck2009pure}, \cite{robbins1985some}.
 
@@
 We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}.
-Bayesian methods have been shown empirically to outperform frequentist algorithms (e.g., UCB)~\cite{chapelle2011empirical, bachman2013greedy}.
+Bayesian methods have been shown empirically to outperform UCB~\cite{chapelle2011empirical, bachman2013greedy}.
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
@@
 The solution to the optimization problem assigns each state an index $v(x_{k,t})$.
-The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
+The indices can then be used to form a policy, where at each timestep the agent selects the arm $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
 Consult \cite{gittins2011multi} for a more detailed analysis of the Gittins method.
@@
 In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$.
-We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \bar{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\hat{\mathbf{\xi}}$ corresponds to the expected pose of the object.
+We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \hat{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\hat{\mathbf{\xi}}$ corresponds to the expected pose of the object.
 
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp $\Gamma$.
+We measure the quality of grasp using the probability of force closure~\cite{ kehoe2012estimating, kehoe2012toward,kim2012physically,weisz2012pose} given a grasp $\Gamma$.
 Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
@@
 Using the relationships defined by the graphical model in Fig.
-\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp apprach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
+\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp approach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
 We then compute the surface normals $\bn_1, \bn_2$ at the contacts based on the gradient of the sampled SDF at the contact locations.
@@
 
-To summarize the algorithm terminates when the following condition is met
+To summarize the algorithm terminates and returns $\bar{k}$, or the grasp that has the highest estimated $P_F$ when the following condition is met
 
@@
 \end{align}
-\noindent where the $\bar{k}$ grasp refers to the grasp with the highest estimated $P_F$ at time $t$.
 
@@
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The measurement noise were assigned uniformly at random to the grid cells.
+The measurement noise were assigned uniformly at random to the signed distance field.
 We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
@@
 \ref{sec:grasp_sample}.
-In Fig.
-\ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
-stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
+We averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
@@
     \centering
-    %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
 
@@
 \centering
-\includegraphics[scale=0.25]{matlab_figures/worst_case.eps}
+\includegraphics[scale=1]{matlab_figures/worst_case-02.jpg}
 \caption{ \footnotesize 
@@
 In future work, we plan to scale our method to 3D objects.
-However, this could substantially increase the number of candidate grasps.
-Glazebrook and Wilkinson showed that the Gittins Index method could be parallelized by simply pulling the top $M$ arms, where $M$ is the number of cores and achieve better performance \cite{glazebrook2000index}.
+This could substantially increase the number of candidate grasps, thus requiring cloud based computing.
+Glazebrook and Wilkinson showed that the Gittins Index method could be parallelized by simply dividing the arms into $M$ subsets,where $M$ is the number of cores , and solving each MAB separate.
+\cite{glazebrook2000index}.
 A similar method could also be done for Thompson sampling.
-Another promising scheme for parrallelizing the MAB, is to divide up the MAB into batches of arms have each core solve the smaller MAB.
+Another promising scheme for parrallelizing the MAB, is to have the algorithm not sample one arm at each algorithm but $M$.
 We will explore both of these approaches in future work.

### 2015-03-16 paper.tex

@@
 \subsection{Candidate Grasp Model}
+
  We formulate the MAB problem for planar objects using parallel-jaw grippers as modeled in Fig.~\ref{fig:grasp_model}.
@@
     \centering
+
     \includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    \caption{Grasps with the highest estimated probability of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
+For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples.
+The candidate grasp set was of size $|\mG|=1000$.
+We visualize the GPIS representation of the object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.
+On objects A and B Thompson sampling finds the best grasp after 10,000 samples, but for object C the grasp selected has $2\%$ lower $P_F$.}%
 
-    \caption{Three objects shown from the Brown Visual Lab Dataset with induced shape uncertainty and visualized with the GPIS-Blur method \cite{mahler2015gp}.
-The four methods (uniform allocation, iterative pruning, Thompson and Gittins) were all run until a stopping time of $10,000$ evaluations with a randomly selected grasp set of $|\mG|=1000$.
-We also show the grasp returned by the brute force approach of exhaustively sampling every grasp in the set.
-The grasps and the quality each one found is shown above.
-In the two out of three cases, Thompson sampling is able to find the best grasp in the set at the stopping interval of $10,000$, however at the last shape there is a difference of $2\%$ grasp quality.}%
     \label{fig:shape_samples}%

### 2015-03-16 paper.tex
fishied Jeffry feedback

@@
     The normalized $P_F$ is the ratio of the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
-    The highest quality grasp was determined by brute force search over all candidate grasps~\cite{kehoe2012toward}.
+    The highest quality grasp was determined by brute force search over all candidate grasps ( a method that is 10x more iterations than all methods shown)~\cite{kehoe2012toward} 
     Uniform allocation and iterative pruning converge to within 3$\%$ of the optimal (the dashed grey line) in approximately 40,000 and 20,000 iterations, respectively.
@@
 \ref{fig:grasp_quality}, we plot time $t$ vs.
-$P(\Gamma_{\bar{k}})$, the probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
+$P(\Gamma_{\bar{k}})$/$P(\Gamma*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
 Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
@@
 
-The time per iteration,$t_{i}$, of each algorithm is calculated as follows $t_{i} = t_{a}+t_{sp}$.
-$t_{a}$ is the time to decide which arm to pull next and $t_{sp}$ is the time taken to draw a sample from the graphical model in Fig.
+The time per iteration,$t_{i} = t_{a}+t_{sp}$, where $t_{a}$ is the time to decide which arm to pull next and $t_{sp}$ is the time taken to draw a sample from the graphical model in Fig.
 \ref{fig:graphical_model}.
 The time per iteration for Thompson Sampling, Gittins Indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms.
-Most of $t_{i}$ is dominated by sampling time, since $t_{sp} = 30$ms.
+Most of $t_{i}$ is dominated by sampling time, since $t_{sp} \approx 30$ms.
 
 The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$.
-We plot the confidence intervals around the returned grasp vs.
+We plot the confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs.
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Thompson Sampling, iterative pruning\cite{kehoe2012toward} and uniform allocation.
-As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods.
+\ref{fig:confidence} for Gittins indices, Thompson Sampling, iterative pruning\cite{kehoe2012toward} and uniform allocation.
+As illustrated, the confidence interval for Thompson sampling and Gttins indices converges at a faster rate than the other two methods.
 
@@
 \subsection{Sensitivity Analysis }\label{sec:sensitivity}
-We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose and use that to set the parameters for future experiments.
-The experiments are performed with the same setup as before but now we increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
-All experiments were averaged across 10 objects randomly selected with from the Brown dataset with $|\mG| = 1000$, or 1000 grasps, $\Gamma$.
+We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose.
+We increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
+All experiments were averaged across 100 objects randomly selected with from the Brown dataset with $|\mG| = 1000$, or 1000 grasps, $\Gamma$.
 
@@
 It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
-Interestingly, Thompson sampling appears to to continute to improvement while Gittins indices and iterative pruning are stuck in local optimal.
-This is because Thompson sampling is guaranteed to find the best grasp in the limit of infinite iterations \cite{agrawal2011analysis}.
+Interestingly, Thompson sampling appears to to continue to improvement while Gittins indices and iterative pruning are stuck in local optimal.
 
@@
 
+\section{Acknowledgments} 
+This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, and by grants from Google. 
+We thank our colleagues who gave feedback, suggestions, and help on the PR2, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
+
 \bibliographystyle{IEEEtranS}

### 2015-03-16 paper.tex
Added symbols to graphical model caption

--- 2015-03-16 paper.tex
@@
 
-\pdfcompresslevel=9
-\pdfobjcompresslevel=9
 %\overrideIEEEmargins                                      % Needed to meet printer requirements.
@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty }
+Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty  [v15 March 15, 2015 ] }
 
@@
 One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-\todo{fix this}Prior work has turned to cloud based computing to solve it This can be computationally demanding and.
-To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
+This can be computationally demanding and prior work has turned to cloud based computing to solve it.
+To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context.
 We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
@@
     \centering
-     \subfloat{{\includegraphics[scale=1]{matlab_figures/pfc-01.jpg} }}%
+     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc.eps} }}%
 
@@
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at using parallel programming in the cloud to overcome this hurdle ~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
-We try to extend these cloud based methods by reducing the number of samples needed.
+Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
+We show that the Multi-armed Bandit (MAB) model improves upon this brute force approach and could hopefully lead to more efficient cloud based algorithms.
 
-Our contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
 In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
@@
 We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
-We then treat MAB algorithms as an anytime algorithms that terminate once a user defined confidence level is met or at a given stopping time.
+We then treat the MAB algorithm as an anytime algorithm that terminates once a user defined confidence level is met or at a given stopping time.
 
@@
 We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
-We demonstrate performance on a local implementation.
-However, our methods are parallelizable by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separate \cite{glazebrook2000index}.
 Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
@@
 Analytical quality metrics typically assume precisely known object shape, object pose, and locations of contact~\cite{cheong2011output, ciocarlie2009}.
-Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
-Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning\cite{brook2011collaborative, hsiao2011bayesian}.
+Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005} Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning\cite{brook2011collaborative, hsiao2011bayesian}.
 
@@
 However, it can be computationally expensive to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed a parallelizable adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
+To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
 However, the method pruned grasps using only the sample mean, which could discard good grasps.
-We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations ~\cite{barto1998reinforcement, lai1985asymptotically}.
+We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.
 
@@
 
-A traditional MAB example is a gambler with $K$ independent slot machines, also known as one-armed bandits.
+A traditional MAB example is a gambler with $K$ independent one-armed bandits, also known as slot machines.
 When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution that is unknown to the gambler.
-The goal of the gambler is to maximize the sum of average rewards over all pulls.
+The goal of the gambler is to come up with a method to maximize the sum of average rewards over all pulls.
 If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
 However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest expected reward and exploring new arms.
-Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation  ~\cite{bergemann2006bandit},\cite{bubeck2009pure}, \cite{robbins1985some}.
+Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
 
@@
 We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}.
-Bayesian methods have been shown empirically to outperform UCB~\cite{chapelle2011empirical, bachman2013greedy}.
+Bayesian methods have been shown empirically to outperform frequentist algorithms (e.g., UCB)~\cite{chapelle2011empirical, bachman2013greedy}.
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
@@
 The solution to the optimization problem assigns each state an index $v(x_{k,t})$.
-The indices can then be used to form a policy, where at each timestep the agent selects the arm $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
-Consult \cite{gittins2011multi} for a more detailed analysis of the Gittins method.
-The indices can be  computed offline using a variety of methods \cite{weber1992gittins}; we chose to use the restart method proposed by Katehakis et al.
-\cite{katehakis1987multi} because it can be implemented in a dynamic programming fashion.
+The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
+Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
+\cite{katehakis1987multi} due to its ability to be implemented in a dynamic programming fashion.
 
@@
 Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$.
-In the case of finding the best arm, we want to plan for long term reward and thus have a high discount factor.
-A smaller $\gamma$ can lead to the policy only pulling the most promising arm and not exploring \cite{kelly1981multi}.Thompson Sampling is an alternative to the Gittins Index method that isn't prone to such a problem.
-In Thompson Sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
-A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated.
-All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.The full algorithm is shown in Algorithm 1.
+The problem with this is that the effective time horizon is a function of $\gamma$.
+Thus, if the actual horizon is longer than the effective horizon, the method can only pull the current estimate of the best arm \cite{kelly1981multi}.
+Thus, no longer trading off exploration and exploitation.
+Thompson sampling is an alternative to the Gittins Index method that isn't prone to such a problem.
+All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
+Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
+A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. The full algorithm is shown in Algorithm 1.
 
-The intuition for Thompson Sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn approaches infinity \cite{goetschalckx2011continuous}.
+The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
+However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
 Chapelle et al.
@@
 \subsection{Candidate Grasp Model}
-
- We formulate the MAB problem for planar objects using parallel-jaw grippers as modeled in Fig.~\ref{fig:grasp_model}.
+The grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
+We formulate the MAB problem for planar objects using parallel-jaw grippers.
 Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$.
@@
 \centering
-\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
+\includegraphics[scale=0.095]{figures/Graphical_Model.jpg}
 \caption{A graphical model of the relationship between the uncertain parameters we consider.
-Uncertainty in object shape, object pose, and grasp approach angle affect the points of contact  between the gripper and object and the surface normals at the contacts.
-Uncertainty in friction coefficient affects forces and torques that are used to compute the probabilty of force closure.
+Uncertainty in object shape $\theta$, object pose $\xi$, and grasp approach angle $\rho$ affect the points of contact $\bc$ with the object and the surface normals $\bn$ at the contacts.
+Uncertainty in friction $\mu$ coefficient affects the forces and torques used to compute our quality measure, the probability of force closure $P_F$.
 }
@@
 In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$.
-We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \hat{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\hat{\mathbf{\xi}}$ corresponds to the expected pose of the object.
+We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \bar{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\hat{\mathbf{\xi}}$ corresponds to the expected pose of the object.
 
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{ kehoe2012estimating, kehoe2012toward,kim2012physically,weisz2012pose} given a grasp $\Gamma$.
+We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp $\Gamma$.
 Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
@@
 Using the relationships defined by the graphical model in Fig.
-\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp approach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
+\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp apprach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
 We then compute the surface normals $\bn_1, \bn_2$ at the contacts based on the gradient of the sampled SDF at the contact locations.
@@
 
-To summarize the algorithm terminates and returns $\bar{k}$, or the grasp that has the highest estimated $P_F$ when the following condition is met
+To summarize the algorithm terminates when the following condition is met
 
@@
 \end{align}
+\noindent where the $\bar{k}$ grasp refers to the grasp with the highest estimated $P_F$ at time $t$.
 
@@
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The measurement noise were assigned uniformly at random to the signed distance field.
+The measurement noise were assigned uniformly at random to the grid cells.
 We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
@@
 \ref{sec:grasp_sample}.
-We averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
+In Fig.
+\ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs.
+stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
@@
     \centering
-
-    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
-    \caption{Grasps with the highest estimated probability of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
+    %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
 For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples.
@@
 On objects A and B Thompson sampling finds the best grasp after 10,000 samples, but for object C the grasp selected has $2\%$ lower $P_F$.}%
-
     \label{fig:shape_samples}%
@@
 \centering
-\includegraphics[scale=1]{matlab_figures/worst_case-02.jpg}
+\includegraphics[scale=0.25]{matlab_figures/worst_case.eps}
 \caption{ \footnotesize 
@@
 In future work, we plan to scale our method to 3D objects.
-This could substantially increase the number of candidate grasps, thus requiring cloud based computing.
-Glazebrook and Wilkinson showed that the Gittins Index method could be parallelized by simply dividing the arms into $M$ subsets,where $M$ is the number of cores , and solving each MAB separate.
-\cite{glazebrook2000index}.
-A similar method could also be done for Thompson sampling.
-Another promising scheme for parrallelizing the MAB, is to have the algorithm not sample one arm at each algorithm but $M$.
-We will explore both of these approaches in future work.
+However, this could substantially increase the number of candidate grasps.
+One option to solving this problem is to use the cloud to solve subsets of the MAB problem in parralel.
+By dividing up the MAB into batches of arms and solving each batch in parallel, we can hopefully maintain similar performance as in this paper.
 

### 2015-03-16 paper.tex
TIdied up a few cloud statements and re-added commits from v15

@@
 One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-This can be computationally demanding and prior work has turned to cloud based computing to solve it.
-To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context.
+Prior work has turned to cloud based computing because evaluating the quality of each grasp is computationally demanding.
+To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
 We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
 We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
-Non-MAB methods, uniform allocation and iterative pruning, converge slowly.
-In contrast, the MAB methods we consider, Thompson Sampling and the Gittins Index, were more efficient in experiments, converging to within 3\% of the optimal grasp approximately 5x faster than non-MAB methods.
+Uniform allocation and iterative pruning, the non-MAB methods, converge slowly.
+In contrast, Thompson Sampling and the Gittins index method, the MAB methods we consider, converged to within 3\% of the optimal grasp approximately 5x faster.
 \end{abstract}
@@
     \centering
-     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc.eps} }}%
+     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc-01.jpg} }}%
 
@@
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} .
-We show that the Multi-armed Bandit (MAB) model improves upon this brute force approach and could hopefully lead to more efficient cloud based algorithms.
+Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
+In this work, we aim to extend these cloud-based methods by reducing the number of samples needed to converge to a high-quality grasp.
 
@@
 We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+We demonstrate performance on a local implementation.
+However, our methods are parallelizable by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separately\cite{glazebrook2000index}.
 Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
@@
 The solution to the optimization problem assigns each state an index $v(x_{k,t})$.
-The indices can then be used to form a policy, where at each timestep the agent selects the arm, $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
-Traditionally, the indices are computed offline using a variety of methods \cite{weber1992gittins}, we chose to use the restart method proposed by Katehakis et al.
-\cite{katehakis1987multi} due to its ability to be implemented in a dynamic programming fashion.
+The indices can then be used to form a policy, where at each timestep the agent selects the arm $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
+Consult \cite{gittins2011multi} for a more detailed analysis of the Gittins method.
+The indices can be  computed offline using a variety of methods \cite{weber1992gittins}; we chose to use the restart method proposed by Katehakis et al.
+\cite{katehakis1987multi} because it can be implemented in a dynamic programming fashion.
 
@@
 The grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
-We formulate the MAB problem for planar objects using parallel-jaw grippers.
+We formulate the MAB problem for planar objects using parallel-jaw grippers as modeled in Fig.~\ref{fig:grasp_model}.
 Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$.
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp $\Gamma$.
+We measure the quality of grasp using the probability of force closure~\cite{kehoe2012estimating, kehoe2012toward, kim2012physically,weisz2012pose} given a grasp $\Gamma$.
 Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
@@
 
-To summarize the algorithm terminates when the following condition is met
+To summarize the algorithm terminates and returns $\bar{k}$, or the grasp that has the highest estimated $P_F$ when the following condition is met:
 
@@
 \begin{align}\label{eq:stopping_condition}
-\lbrace t \geq T_s \: \mbox{OR} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace
+\lbrace t \geq T_s \: \mbox{OR} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace.
 \end{align}
-\noindent where the $\bar{k}$ grasp refers to the grasp with the highest estimated $P_F$ at time $t$.
 
@@
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The measurement noise were assigned uniformly at random to the grid cells.
+The measurement noise were assigned uniformly at random to the SDF.
 We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
@@
     \centering
-    %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
     \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
@@
 It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
-Interestingly, Thompson sampling appears to to continue to improvement while Gittins indices and iterative pruning are stuck in local optimal.
+Interestingly, Thompson sampling appears to to continue to improvement while Gittins indices and iterative pruning do not continue to make progress.
 
@@
 \centering
-\includegraphics[scale=0.25]{matlab_figures/worst_case.eps}
+\includegraphics[scale=0.25]{matlab_figures/worst_case-02.jpg}
 \caption{ \footnotesize 
@@
 In future work, we plan to scale our method to 3D objects.
-However, this could substantially increase the number of candidate grasps.
-One option to solving this problem is to use the cloud to solve subsets of the MAB problem in parralel.
-By dividing up the MAB into batches of arms and solving each batch in parallel, we can hopefully maintain similar performance as in this paper.
+This could substantially increase the number of candidate grasps, further motivating the use of cloud computing.
+Glazebrook and Wilkinson showed that the Gittins index method could be parallelized by simply dividing the arms into $M$ subsets, where $M$ is the number of cores, and solving each MAB separately.
+\cite{glazebrook2000index}.
+A similar method could also be done for Thompson sampling.
+Another promising scheme for parrallelizing the MAB, is to have the algorithm not sample one arm at each algorithm but $M$.
+We will explore both of these approaches in future work.
 

### 2015-03-16 paper.tex
fixed merge problem

@@
 One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-Prior work has turned to cloud based computing because evaluating the quality of each grasp is computationally demanding.
+Prior work has turned to cloud computing because evaluating the quality of each grasp is computationally demanding.
 To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
-We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles.
+We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset from 1000 uniformly distributed candidate grasp angles.
 We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
@@
     \centering
-     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc-01.jpg} }}%
+     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc.eps} }}%
 
@@
 Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$.
-The problem with this is that the effective time horizon is a function of $\gamma$.
-Thus, if the actual horizon is longer than the effective horizon, the method can only pull the current estimate of the best arm \cite{kelly1981multi}.
-Thus, no longer trading off exploration and exploitation.
-Thompson sampling is an alternative to the Gittins Index method that isn't prone to such a problem.
-All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
-Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
-A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. The full algorithm is shown in Algorithm 1.
+However, in the case of finding the best arm, we want to plan for long term reward and thus want $\gamma$ as close to $1$ as possible.
+Due to computational constraints we must use a smaller $\gamma$, but this can lead to the algorithm pulling only the most promising arm for many iterations~\cite{kelly1981multi}.
+
+Thompson Sampling is an alternative to the Gittins Index method that isn't prone to such a problem. 
+In Thompson Sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
+A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated.
+All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.The full algorithm is shown in Algorithm 1.
 
@@
     \centering
-    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
     \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
@@
 \centering
-\includegraphics[scale=0.25]{matlab_figures/worst_case-02.jpg}
+%\includegraphics[scale=0.25]{matlab_figures/worst_case-02.jpg}
 \caption{ \footnotesize 

### 2015-03-16 paper.tex
final version

@@
 Prior work has turned to cloud computing because evaluating the quality of each grasp is computationally demanding.
-To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
+To improve efficiency and extend this work, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
 We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset from 1000 uniformly distributed candidate grasp angles.
@@
 We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
-We demonstrate performance on a local implementation.
-However, our methods are parallelizable by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separately\cite{glazebrook2000index}.
+
 Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+Although our current implementation is local, our methods may be extended to the cloud by solving $M$ MAB problems on disjoint subsets of the arms and aggregating the results~\cite{glazebrook2000index}.
+%by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separately\cite{glazebrook2000index}.
 
@@
 
-The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
-Chapelle et al.
-demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case \cite{chapelle2011empirical}.
-Theoretically, Agrawal et al.
-recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that was sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms  \cite{agrawal2011analysis}.
-
 \begin{algorithm}
@@
 \end{algorithm}
+
+The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
+However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
+Chapelle et al.
+demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case \cite{chapelle2011empirical}.
+Theoretically, Agrawal et al.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that was sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms  \cite{agrawal2011analysis}.
 
@@
 \ref{fig:grasp_quality}, we plot time $t$ vs.
-$P(\Gamma_{\bar{k}})$/$P(\Gamma*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
+$P(\Gamma_{\bar{k}})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
 Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
@@
 
-The time per iteration,$t_{i} = t_{a}+t_{sp}$, where $t_{a}$ is the time to decide which arm to pull next and $t_{sp}$ is the time taken to draw a sample from the graphical model in Fig.
+The time per iteration, $t_{i} = t_{a}+t_{sp}$ , where $t_{a}$ is the time to decide which arm to pull next and $t_{sp}$ is the time taken to draw a sample from the graphical model in Fig.
 \ref{fig:graphical_model}.
@@
 \centering
-\includegraphics[scale=0.25]{matlab_figures/confidence_bounds.eps}
+\includegraphics[scale=1]{matlab_figures/confidence_bounds.jpg}
 \caption{ Number of samples versus the $95\%$ confidence intervals on the probability of force closure of the best estimated grasp after $k$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
@@
     \centering
-    %\includegraphics[width=16.5cm]{figures/shapes.jpg}%
+    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
     \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
-For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples.
+For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples and the nominal shape.
 The candidate grasp set was of size $|\mG|=1000$.
@@
 \centering
-%\includegraphics[scale=0.25]{matlab_figures/worst_case-02.jpg}
+\includegraphics[scale=1]{matlab_figures/worst_case-02.jpg}
 \caption{ \footnotesize 

### 2015-03-16 paper.tex
Fixed a few typos / inconsistencies in notation.

@@
 
-    \caption{Number of samples versus the normalized probability of force closure $P_F$ for the best estimated grasp after $k$ samples, $P_F(\Gamma_{\bar{k}})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
+    \caption{Number of samples versus the normalized probability of force closure $P_F$ for the best estimated grasp after $t$ samples, $P_F(\Gamma_{\bar{k}, t})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
     %We evaluated performance on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
-    The normalized $P_F$ is the ratio of the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
+    The normalized $P_F$ is the ratio of $P_F(\Gamma_{\bar{k}, t})$ to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
     The highest quality grasp was determined by brute force search over all candidate grasps ( a method that is 10x more iterations than all methods shown)~\cite{kehoe2012toward} 
@@
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
+Past work has looked at using parallel programming in the cloud to overcome this problem~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
 In this work, we aim to extend these cloud-based methods by reducing the number of samples needed to converge to a high-quality grasp.
@@
 
-Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
+Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kehoe2012toward, kim2012physically, weisz2012pose}.
 Monte-Carlo involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
@@
 \subsection{MAB Model}
-The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
+The MAB model, originally described by Robbins~\cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
 Solutions to the MAB model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
@@
 Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
-Lai and Robbins\cite{lai1985asymptotically} showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls.
+Lai and Robbins~\cite{lai1985asymptotically} showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls.
 They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
@@
 Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
-For instance a Bernoulli random variable, $p$, can be used to represent a binary grasping metric like force closure.
+For instance a Bernoulli random variable $p$ can be used to represent a binary grasping metric like force closure.
 The prior typically placed on a Bernoulli variable is its conjugate prior, the Beta distribution.
@@
 The indices can then be used to form a policy, where at each timestep the agent selects the arm $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
-Consult \cite{gittins2011multi} for a more detailed analysis of the Gittins method.
 The indices can be  computed offline using a variety of methods \cite{weber1992gittins}; we chose to use the restart method proposed by Katehakis et al.
 \cite{katehakis1987multi} because it can be implemented in a dynamic programming fashion.
+We refer the reader to~\cite{gittins2011multi} for a more detailed analysis of the Gittins index method.
 
@@
 
-Thompson Sampling is an alternative to the Gittins Index method that isn't prone to such a problem. 
-In Thompson Sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
+Thompson sampling is an alternative to the Gittins index method that isn't prone to such a problem. 
+In Thompson sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
 A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated.
@@
  Pull $k_t  = \underset{k\in K}{\mbox{argmax}} \: p_{k,t}$\\
- Observe reward $R_{k_t,t} \in \lbrace 0,1 \rbrace$\\
+ Observe reward $R_{k,t} \in \lbrace 0,1 \rbrace$\\
  Update posterior:\\
@@
   }
- \caption{Thompson Sampling for Beta-Bernoulli Process}
+ \caption{Thompson sampling for Beta-Bernoulli Process}
 \end{algorithm}
@@
 Using the relationships defined by the graphical model in Fig.
-\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp approach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{newcombe2011kinectfusion}.
-We then compute the surface normals $\bn_1, \bn_2$ at the contacts based on the gradient of the sampled SDF at the contact locations.
+\ref{fig:graphical_model}, we next compute the contact locations $\bc_1, \bc_2$ given a sampled SDF, pose, and grasp approach by ray tracing along the grasp axis defined by $\Gamma_k = \lbrace \bj_1,\bj_2 \rbrace$~\cite{mahler2015gp}.
+We then compute the surface normals $\bn_1, \bn_2$ at the contacts using the gradient of the sampled SDF at the contact locations.
 Finally, we use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
@@
 \noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.
-We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.
+We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson sampling and Gittins indices.
 
@@
 \begin{align}\label{eq:confidence}
-B(0.025,\alpha_{k,n},\beta_{k,n}) \leq P_F(\Gamma_k)) \leq B(0.975,\alpha_{k,n},\beta_{k,n})
+B(0.025,\alpha_{k,t},\beta_{k,t}) \leq P_F(\Gamma_{k,t})) \leq B(0.975,\alpha_{k,t},\beta_{k,t})
 \end{align}
 
-To summarize the algorithm terminates and returns $\bar{k}$, or the grasp that has the highest estimated $P_F$ when the following condition is met:
+To summarize, the algorithm terminates and returns $\bar{k}$, or the grasp that has the highest estimated $P_F$ when the following condition is met:
 
@@
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
-iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
+Iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
 We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time.
@@
 \ref{fig:grasp_quality}, we plot time $t$ vs.
-$P(\Gamma_{\bar{k}})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
+$P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
 Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
-Gittins Indices and Thompson Sampling  perform significantly better, converging after only 4000 iterations.For illustrative purposes in Fig.
+Gittins indices and Thompson sampling  perform significantly better, converging after only 4000 iterations.For illustrative purposes in Fig.
 \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
 
-The time per iteration, $t_{i} = t_{a}+t_{sp}$ , where $t_{a}$ is the time to decide which arm to pull next and $t_{sp}$ is the time taken to draw a sample from the graphical model in Fig.
+The time per iteration is $t_{i} = t_{a}+t_{p}$, where $t_{a}$ is the time to decide which arm to pull next and $t_{p}$ is the time taken to draw a sample from the graphical model in Fig.
 \ref{fig:graphical_model}.
-The time per iteration for Thompson Sampling, Gittins Indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms.
-Most of $t_{i}$ is dominated by sampling time, since $t_{sp} \approx 30$ms.
+The time per iteration for Thompson sampling, Gittins indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms.
+Most of $t_{i}$ is dominated by sampling time, since $t_{p} \approx 30$ms.
 
@@
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Gittins indices, Thompson Sampling, iterative pruning\cite{kehoe2012toward} and uniform allocation.
+\ref{fig:confidence} for Gittins indices, Thompson sampling, iterative pruning\cite{kehoe2012toward} and uniform allocation.
 As illustrated, the confidence interval for Thompson sampling and Gttins indices converges at a faster rate than the other two methods.
@@
 \includegraphics[scale=1]{matlab_figures/confidence_bounds.jpg}
-\caption{ Number of samples versus the $95\%$ confidence intervals on the probability of force closure of the best estimated grasp after $k$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
+\caption{ Number of samples versus the $95\%$ confidence intervals on the probability of force closure of the best estimated grasp after $t$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
 The values are averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset~\cite{brown} with 1,000 candidate grasps for each object.
@@
 \subsection{Sensitivity Analysis }\label{sec:sensitivity}
-We also analyze the performance of Thompson Sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose.
+We also analyze the performance of Thompson sampling under variations in noise from friction coefficient uncertainty, shape uncertainty, rotational pose, and translation pose.
 We increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
@@
 For translational uncertainty in pose, we varied $\sigma_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation and an increased noise of $\sigma_{\bt} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
+Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma_{\bt} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson sampling.
 
@@
 To show worst case performance under such a model, we sorted the quality of all 1000 grasps offline and arranged the order of samples, so that the top 500 grasps have samples drawn in the order of worst to best and the bottom 500 grasps have samples drawn in order of best to worst.
-The intent here is to provide misleading observations to the bandit algorithms.
+This provides misleading observations to the bandit algorithms.
 We demonstrate in Fig.
@@
 \ref{fig:worst_case}, all the methods are affected by worst case performance.
-It would appear that when the observations are misleading the best thing to do is simply uniform allocation of grasp samples.
+The results indicate that when the observations are misleading the best thing to do is uniform allocation of grasp samples.
 Interestingly, Thompson sampling appears to to continue to improvement while Gittins indices and iterative pruning do not continue to make progress.
@@
 \caption{ \footnotesize 
-	Number of samples versus the probability of force closure of the best estimated grasp after $k$ samples $P_F(\Gamma_{\bar{k}})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
-	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $k$, $P_F(\Gamma_{\bar{k}})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
+	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
+	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
  	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
@@
  %\hline
- %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson Sampling} \\
+ %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
  %\hline 
@@
 \end{tabular}
-   \caption { \footnotesize  Number of iterations until convergence to within $3\%$ of grasp with the highest estimated probability of force closure $P_F$ for Thompson Sampling under uncertainty in the object orientation $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  uncertainty in the object position $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units, and uncertainty in friction coefficient $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$ on a 40$\times$40 grid averaged over 100 independent runs on random objects from the Brown Vision 2D Dataset.
+   \caption { \footnotesize  Number of iterations until convergence to within $3\%$ of grasp with the highest estimated probability of force closure $P_F$ for Thompson sampling under uncertainty in the object orientation $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  uncertainty in the object position $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units, and uncertainty in friction coefficient $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$ on a 40$\times$40 grid averaged over 100 independent runs on random objects from the Brown Vision 2D Dataset.
 High variances in position and orientation uncertainty increases the amount of iterations needed for the bandit algorithm to converge.
@@
 This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, and by grants from Google. 
-We thank our colleagues who gave feedback, suggestions, and help on the PR2, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
+We thank our colleagues who gave feedback and suggestions in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
 

### 2015-06-13 paper.tex
Camera Ready

@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty }
+Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty [v 17] }
 
@@
 Pokorny$^3$, Sachin Patil$^1$,\\ Jur van den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey , jmahler,zmccarthy, sachinpatil, pabbeel\}@berkeley.edu}}%
 \thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
@@
 \begin{abstract}
-For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing, shape, mechanics, and control.
-One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.
+For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing, mechanics, and control.
+One way to achieve robustness is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and gripper approach and compute the probability of force closure for each candidate to identify the grasp with the highest expected quality.
 Prior work has turned to cloud computing because evaluating the quality of each grasp is computationally demanding.
@@
 We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset from 1000 uniformly distributed candidate grasp angles.
-We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
-Uniform allocation and iterative pruning, the non-MAB methods, converge slowly.
-In contrast, Thompson Sampling and the Gittins index method, the MAB methods we consider, converged to within 3\% of the optimal grasp approximately 5x faster.
+We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) with Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
+Thompson Sampling and the Gittins index method, the MAB methods we consider, converged to within 3\% of the optimal grasp up to 10x faster than Uniform allocation.
 \end{abstract}
@@
     Uniform allocation and iterative pruning converge to within 3$\%$ of the optimal (the dashed grey line) in approximately 40,000 and 20,000 iterations, respectively.
-    In comparison, the MAB methods both converge in approxmately 4,000 iterations. 
+    In comparison, the MAB methods both converge in approximately 4,000 iterations. 
 %    $P_F(\Gamma_{\bar{k}})$ (ratio of $P_F(\Gamma_{\bar{k}})$ to $P_F(\Gamma^*)$)
@@
 To cope with uncertainty, recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One way to compute the probability of force closure is using Monte-Carlo integration over sample perturbations in the uncertain quantities\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
+One way to compute the probability of force closure is using Monte-Carlo integration over sampled perturbations in the uncertain quantities~\cite{christopoulos2007handling,kehoe2012toward, kim2012physically, weisz2012pose}.
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at using parallel programming in the cloud to overcome this problem~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
+Past work has looked at using parallel programming in the cloud to overcome this problem and proposed a heuristic for adaptive sampling known as iterative pruning~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
 In this work, we aim to extend these cloud-based methods by reducing the number of samples needed to converge to a high-quality grasp.
 
-Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
-In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
+Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing that it is possible to allocate sampling effort to grasps with highest estimated probability of force closure\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+In a standard MAB, there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
 The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
 We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
-We then treat the MAB algorithm as an anytime algorithm that terminates once a user defined confidence level is met or at a given stopping time.
+We then treat the MAB algorithm as an anytime algorithm that terminates once a user-defined confidence level is met or at a given stopping time.
 
@@
 We model uncertainty in pose as a normal distribution around the orientation and 2D position of the object.
-We chose to model uncertainty in grasp approach as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper.
-We model uncertainty in friction coefficient as a normal distribution around an expected friction coefficient.
+Uncertainty in grasp approach is modeled as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper.
+Uncertainty in friction coefficient is modeled as a normal distribution around an expected friction coefficient.
 
 We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}.
-In the task of finding grasps with high probability of force closure.
-We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+Performance in terms of number of samples needed to find the grasp with highest estimated probability of force closure is measured on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
 
-Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
+\todo{Should we say 10x over uniform, or up to 10x improvment, or 5x over iterative pruning?}
+Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
 Although our current implementation is local, our methods may be extended to the cloud by solving $M$ MAB problems on disjoint subsets of the arms and aggregating the results~\cite{glazebrook2000index}.
@@
 
-Most research on grasp planning focuses on finding grasps by maximizing a grasp quality metric.
+Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric.
 Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
 Analytical quality metrics typically assume precisely known object shape, object pose, and locations of contact~\cite{cheong2011output, ciocarlie2009}.
-Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005} Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning\cite{brook2011collaborative, hsiao2011bayesian}.
+Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
+Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning \cite{brook2011collaborative, hsiao2011bayesian}.
 
@@
 Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to uncertainty in object pose were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics.
-Similarly, Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose.
-They also found that the planned grasps were more successful on a physical robot than those planned with classical wrench space metrics.
+Similarly, Kim et al.~\cite{kim2012physically} planned grasps using dynamic simulations over perturbations in object pose and found that the planned grasps were more successful on a physical robot than those planned with classical wrench space metrics.
 
-Recent work has also studied uncertainty in object shape, motivated by the use of uncertain low-cost sensors and tolerances in part manufacturing.
+Recent work has also studied uncertainty in object shape, motivated by the use of low-cost sensors and tolerances in part manufacturing.
 Christopoulos et al.~\cite{christopoulos2007handling} sampled spline fits for 2-dimensional planar objects and ranked a set of randomly generated grasps by probability of force closure.
@@
 Dragiev et al.~\cite{dragiev2011} uses GPIS to actively explore shapes with tactile sensing to find a hand posture that aligned the gripper fingers to an object's surface normals~\cite{dragiev2013uncertainty}.
-Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem~\cite{mahler2015gp}.
+Mahler et al. used the GPIS representation to find locally optimal antipodal grasps which framed grasp planning as an optimization problem~\cite{mahler2015gp}.
 
@@
 Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kehoe2012toward, kim2012physically, weisz2012pose}.
-Monte-Carlo involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
+Monte-Carlo involves sampling from distributions on uncertain quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
 However, it can be computationally expensive to sample all proposed grasps to convergence.
@@
 When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution that is unknown to the gambler.
-The goal of the gambler is to come up with a method to maximize the sum of average rewards over all pulls.
-If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
-However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest expected reward and exploring new arms.
-Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation  ~\cite{bergemann2006bandit},\cite{bubeck2009pure}, \cite{robbins1985some}.
+The goal of the gambler is to come up with a method to maximize the average rewards over all pulls.
+If the gambler knew the arm with the highest expected reward, the gambler would only pull that arm.
+However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arm that currently yields the highest expected reward and exploring new arms.
+Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation~\cite{bergemann2006bandit,robbins1985some}.
 
-At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the selected arm.
+At each time step, the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the selected arm.
 Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
@@
 The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
+
+In the robotics field, Hsu et al.
+applied MAB models to improve the performance and reduce computation time of the probabilistic roadmap motion planner by adaptively sampling waypoints \cite{hsu2005hybrid}.
+Matikainen et al.
+formulated policy learning as choosing a state machine from a known libraries of state machines.
+They then used a MAB algorithm to improve the computational speed of finding the best state machine \cite{matikainen2013multi}.
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}.
@@
 \subsection{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}
-We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}.
+We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the parameters specifying the distribution of each arm \cite{agrawal2011analysis,weber1992gittins}.
 Bayesian methods have been shown empirically to outperform UCB~\cite{chapelle2011empirical, bachman2013greedy}.
-Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
+Bayesian algorithms maintain a belief distribution on the arm payoff for each of the arms.
 For instance a Bernoulli random variable $p$ can be used to represent a binary grasping metric like force closure.
@@
 At timestep $t=0$, we pull arm $k$ and observe reward $R_{k,0}$, where $R_{k,0} \in \lbrace 0, 1\rbrace$.
-The posterior of the Beta after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}$  $\beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+The posterior of the Beta after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}$,  $\beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 
-Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$ at time $t$, the algorithm can calculate the expected Bernoulli parameter, $\bar{p}_{k,t}$, as follows:
+Given the current belief $\alpha_{k, t}, \beta_{k, t}$ for an arm $k$ at time $t$, the expected Bernoulli parameter, $\bar{p}_{k,t}$, is:
 %Thus, we can write the expected probability of force closure as follows
@@
 \begin{align}\label{eq:shape_sampling}
-\bar{p}_{k,t} = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}}
+\bar{p}_{k,t} = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} + \alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}
 \end{align}
+
+All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) for $k\leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
 
@@
 One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
-Formally, a MDP is defined as a set of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
-In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,t}$ and $\beta_{k,t}$.
+Formally, a MDP is defined by sets of states, actions, transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
+In the Beta-Bernoulli MAB case, the set of actions consists of $K$ arms and the set of states are the Beta posterior on each arm, or the values of $\alpha_{k,t}$ and $\beta_{k,t}$.
 
 Methods such as Value Iteration can compute optimal policies for a discrete MDP with respect to the discount factor $\gamma$ ~\cite{barto1998reinforcement}.
-However, the curse of dimensionality effects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in $K$.
-A key insight was given by Gittins, who showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ \cite{weber1992gittins}.
+However, the curse of dimensionality affects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in size with respect to $K$.
+Using the fact that pulling an arm only changes the state of the arm pulled, Gittins showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ \cite{weber1992gittins}.
 
-The solution to the optimization problem assigns each state an index $v(x_{k,t})$.
+The solution to the optimization problem assigns each state an index $v(x_{k,t})$, which can be thought of as the expected value for each state. 
 The indices can then be used to form a policy, where at each timestep the agent selects the arm $k_t$ where $k_t= \underset{1 \leq k \leq K}{\mbox{argmax }} v(x_{k,t})$.
-The indices can be  computed offline using a variety of methods \cite{weber1992gittins}; we chose to use the restart method proposed by Katehakis et al.
-\cite{katehakis1987multi} because it can be implemented in a dynamic programming fashion.
+The indices for the Beta-Bernoulli case are computed offline and can be found in ~\cite{gittins2011multi}.
 We refer the reader to~\cite{gittins2011multi} for a more detailed analysis of the Gittins index method.
@@
 Due to computational constraints we must use a smaller $\gamma$, but this can lead to the algorithm pulling only the most promising arm for many iterations~\cite{kelly1981multi}.
-
-Thompson sampling is an alternative to the Gittins index method that isn't prone to such a problem. 
-In Thompson sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
-A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated.
-All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.The full algorithm is shown in Algorithm 1.
 
@@
 
+Thompson sampling is an alternative to the Gittins index method that is not prone to this problem. 
+In Thompson sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull, the arm with the highest $p_{k,t}$ drawn.
+A reward, $R_{k,t}$, is then observed and the corresponding Beta distribution is updated.The general assumption is that sampling from the Beta distribution for each arm is significantly computationally cheaper than actually pulling an arm.
+Sampling from a Beta distribution is computationally inexpensive and implemented  in most science computing libraries \cite{MATLAB:2010}.
+The full algorithm is shown in Algorithm 1.
+
 The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However as it receives more samples it hones in on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
+However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
 Chapelle et al.
 demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case \cite{chapelle2011empirical}.
-Theoretically, Agrawal et al.
-recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that was sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms  \cite{agrawal2011analysis}.
+Agrawal et al.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms  \cite{agrawal2011analysis}.
 
@@
 We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
-We consider uncertainty in shape, pose, gripper approach, and friction coefficient. We assume that the distributions on these quantities are given and can be sampled from.
+We consider uncertainty in shape, pose, gripper approach, and friction coefficient.
+We assume that the distributions on these quantities are given and can be sampled from.
+While we only consider grasping planar objects, our method can work on planar slices of a 3D object.
+\begin{figure}[t!]
+\centering
+\includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
+\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch.
+Jaw placements are illustrated by a red direction arrow and line.
+A grasp plan centered at $\by$ (plus symbol) at angle $\psi$ consists of 2D locations for each of the parallel jaws $\bj_1$ and $\bj_2$.
+When following the grasp plan, the jaws contact the object at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations.
+Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
+\vspace*{-2ex}
+\label{fig:grasp_model}
+\end{figure}
 
@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
-\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch.
-Jaw placements are illustrated by a red direction arrow and line.
-A grasp plan centered at $\by$ (plus symbol) at angle $\psi$ consists of 2D locations for each of the parallel jaws $\bj_1$ and $\bj_2$.
-When following the grasp plan, the jaws contact the object at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations.
-Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
-\vspace*{-2ex}
-\label{fig:grasp_model}
-\end{figure}
-
 \subsection{Sources of Uncertainty}
@@
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
-\includegraphics[scale=0.095]{figures/Graphical_Model.jpg}
+\includegraphics[scale=0.18]{figures/Graphical_Model.jpg}
 \caption{A graphical model of the relationship between the uncertain parameters we consider.
@@
 Uncertainty in friction $\mu$ coefficient affects the forces and torques used to compute our quality measure, the probability of force closure $P_F$.
+The shaded nodes denote the observed values.
 }
@@
 \subsubsection{Pose Uncertainty}
-In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$.
+In 2-dimensional space, the pose of an object $T$ is defined by a rotation angle $\phi$ and the two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$.
 We assume Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \hat{\mathbf{\xi}}, \Sigma_{\xi} \right)$, where $\hat{\mathbf{\xi}}$ corresponds to the expected pose of the object.
@@
  \subsubsection{Approach Uncertainty}
-In practice a robot may not be able to execute a desired grasp $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
+In practice, a robot may not be able to execute a desired grasp $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
 We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp $\Gamma$.
@@
 We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
-For shorthand in the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
+For shorthand, the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
 In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ can be set from repeatability measurements for a robot~\cite{mooring1986determination}.
@@
 We measure the quality of grasp using the probability of force closure~\cite{kehoe2012estimating, kehoe2012toward, kim2012physically,weisz2012pose} given a grasp $\Gamma$.
-Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
+Force closure is considered as a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
 Let $\mW \in \mathbb{R}^3$ denote the contact wrenches derived from contact locations $\bc_1,\bc_2$, normals $\bn_1,\bn_2$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
@@
 
-One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
+One method to approximately find such a grasp is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
 We refer to this as a brute force approach. 
@@
 \noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.
-We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson sampling and Gittins indices.
+We then formulate the  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson sampling and Gittins indices.
 
@@
 Since force closure is a binary value, each grasp $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
-In a MAB, we want to try and minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.
+In a MAB, we want to minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.
 
-One can think of the proposed algorithm as an anytime algorithm.
-It can be stopped at anytime during its computation to return the current estimate of the best grasp or wait until a $95\%$ confidence interval is smaller than some threshold $\epsilon$.
+The proposed algorithm is an anytime algorithm because it can be stopped at any point during its computation to return the current estimate of the best grasp or wait until a $95\%$ confidence interval is smaller than some threshold $\epsilon$.
 Using the quantile function of the beta distribution, $B$, we can measure the $95\%$ confidence interval as:
@@
 
-To summarize, the algorithm terminates and returns $\bar{k}$, or the grasp that has the highest estimated $P_F$ when the following condition is met:
+To summarize, the algorithm terminates and returns $\bar{k}$, or a grasp that has the highest estimated $P_F$ when the following condition is met:
 
@@
 \begin{align}\label{eq:stopping_condition}
-\lbrace t \geq T_s \: \mbox{OR} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace.
+\lbrace t \geq T_s \: \mbox{or} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace.
 \end{align}
@@
 The measurement noise were assigned uniformly at random to the SDF.
-We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
-For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi} = 0.2$ rads, $\sigma_{\by} = 3$ grid cells, $\sigma_{\mu} = 0.4$, $\sigma_{\phi} = 0.3$ rads and $\sigma_{\bt} = 3$ grid cells.
+We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
+For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
 We also performed experiments for the case of two hard contacts in 2-D.
@@
 \subsection{Multi-Armed Bandit Experiments}
-For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$.
+For our experiments we look at selecting an optimal among $|G| = 1000$ candidates.
 We draw samples from our graphical model using the technique described in Sec.
 \ref{sec:grasp_sample}.
-We averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
+We calculated the expected performance over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
 Iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time.
+We set the discount factor $\gamma =0.98$ for Gittins, which was the highest we could compute due to the exponential growth in computation time with respect to $\gamma$.
 
@@
 $P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
-Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
-Gittins indices and Thompson sampling  perform significantly better, converging after only 4000 iterations.For illustrative purposes in Fig.
+Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
+Gittins indices and Thompson sampling  perform significantly better, converging after only 4000 iterations.
+In Fig.
 \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
@@
 Most of $t_{i}$ is dominated by sampling time, since $t_{p} \approx 30$ms.
+Sampling from our graphical model in Fig.
+\ref{fig:graphical_model} involves drawing samples form a GPIS, a high dimensional Gaussian, and evaluating the probability of force closure metric.
 
@@
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Gittins indices, Thompson sampling, iterative pruning\cite{kehoe2012toward} and uniform allocation.
-As illustrated, the confidence interval for Thompson sampling and Gttins indices converges at a faster rate than the other two methods.
+\ref{fig:confidence} for Gittins indices, Thompson sampling, iterative pruning \cite{kehoe2012toward} and uniform allocation.
+As illustrated, the confidence interval for Thompson sampling and Gittins indices converges at a faster rate than the other two methods.
 
@@
 \includegraphics[scale=1]{matlab_figures/confidence_bounds.jpg}
-\caption{ Number of samples versus the $95\%$ confidence intervals on the probability of force closure of the best estimated grasp after $t$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
+\caption{ Number of samples versus the $95\%$ confidence intervals from Eq.
+\ref{eq:confidence} on the probability of force closure of the best estimated grasp after $t$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
 The values are averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset~\cite{brown} with 1,000 candidate grasps for each object.
@@
 
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{matlab_figures/worst_case-02.jpg}
+\caption{ \footnotesize 
+	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
+	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
+ 	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
+ 	The results suggest that when samples are misleadingly ordered, the best policy is uniform allocation.}
+\vspace*{-10pt}
+\label{fig:worst_case}
+\end{figure}
 \subsection{Sensitivity Analysis }\label{sec:sensitivity}
@@
 We increase the variance parameters across a set range for each parameter to simulate low, medium and high levels of noise.
-All experiments were averaged across 100 objects randomly selected with from the Brown dataset with $|\mG| = 1000$, or 1000 grasps, $\Gamma$.
+All experiments were averaged across 100 objects randomly selected  from the Brown dataset with $|\mG| = 1000$.
 
 For friction coefficient we varied $\sigma_{\mu}$ across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
-As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 2000 evaluations.
+As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 5000 evaluations.
 
 For rotational uncertainty in pose, we varied $\sigma_{\phi}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
-As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\circ}$  causes the convergence in simple regret to not be reached until around 4432 samples or an average of 5.5 samples per grasp.
+As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\circ}$  causes the convergence in simple regret to not be reached until around 6432 samples or an average of 6.4 samples per grasp.
 
@@
 Interestingly, Thompson sampling appears to to continue to improvement while Gittins indices and iterative pruning do not continue to make progress.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[scale=1]{matlab_figures/worst_case-02.jpg}
-\caption{ \footnotesize 
-	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
-	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
- 	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
- 	The results suggest that when samples are misleading the best policy is uniform allocation.
-	However, Thompson sampling appears to continue making progress whereas iterative pruning and Gittins indices do not.}
-\vspace*{-10pt}
-\label{fig:worst_case}
-\end{figure}
 
@@
 However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
-Fortunately, the probability of many successive samples being misleading approaches zero at an exponential rate as the time horizon is increased.
+Fortunately, the probability of many successive samples being misleading approaches rapidly zero as the time horizon is increased.
 

### 2015-06-14 paper.tex
latest revision, changed figure and went over writing

@@
 However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at using parallel programming in the cloud to overcome this problem and proposed a heuristic for adaptive sampling known as iterative pruning~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
+Past work has looked at leveraging the cloud to execute multiple threads in parallel to overcome this problem and proposed a heuristic for adaptive sampling known as iterative pruning~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
 In this work, we aim to extend these cloud-based methods by reducing the number of samples needed to converge to a high-quality grasp.
 
-Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing that it is possible to allocate sampling effort to grasps with highest estimated probability of force closure\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
+Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing that it is possible to allocate sampling effort to grasps with highest estimated probability of force closure~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
 In a standard MAB, there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
@@
 Work on grasping under uncertainty has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
-Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning \cite{brook2011collaborative, hsiao2011bayesian}.
+Furthermore, recent work has studied the effects of uncertainty in object pose and gripper positioning~\cite{brook2011collaborative, hsiao2011bayesian}.
 
@@
 Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kehoe2012toward, kim2012physically, weisz2012pose}.
-Monte-Carlo involves sampling from distributions on uncertain quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
-However, it can be computationally expensive to sample all proposed grasps to convergence.
-To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
-However, the method pruned grasps using only the sample mean, which could discard good grasps.
+This approach involves sampling from distributions on uncertain quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
+It can be computationally expensive though to sample all proposed grasps to convergence.
+To address this computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
+However, the method pruned grasps using only the sample mean, which can discard good grasps in practice.
 We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.
@@
 In the robotics field, Hsu et al.
-applied MAB models to improve the performance and reduce computation time of the probabilistic roadmap motion planner by adaptively sampling waypoints \cite{hsu2005hybrid}.
+applied MAB models to improve the performance and reduce computation time of the probabilistic roadmap motion planner by adaptively sampling waypoints~\cite{hsu2005hybrid}.
 Matikainen et al.
 formulated policy learning as choosing a state machine from a known libraries of state machines.
-They then used a MAB algorithm to improve the computational speed of finding the best state machine \cite{matikainen2013multi}.
+They then used a MAB algorithm to improve the computational speed of finding the best state machine~\cite{matikainen2013multi}.
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}.
@@
 \subsection{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}
-We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the parameters specifying the distribution of each arm \cite{agrawal2011analysis,weber1992gittins}.
+We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the parameters specifying the distribution of each arm~\cite{agrawal2011analysis,weber1992gittins}.
 Bayesian methods have been shown empirically to outperform UCB~\cite{chapelle2011empirical, bachman2013greedy}.
@@
 One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
-Formally, a MDP is defined by sets of states, actions, transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
+Formally, a MDP is defined by sets of states, actions, transition probabilities between states, a reward function, and a discount factor~\cite{barto1998reinforcement}.
 In the Beta-Bernoulli MAB case, the set of actions consists of $K$ arms and the set of states are the Beta posterior on each arm, or the values of $\alpha_{k,t}$ and $\beta_{k,t}$.
@@
 However, the curse of dimensionality affects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in size with respect to $K$.
-Using the fact that pulling an arm only changes the state of the arm pulled, Gittins showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ \cite{weber1992gittins}.
+Using the fact that pulling an arm only changes the state of the arm pulled, Gittins showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ ~\cite{weber1992gittins}.
 
@@
 A reward, $R_{k,t}$, is then observed and the corresponding Beta distribution is updated.The general assumption is that sampling from the Beta distribution for each arm is significantly computationally cheaper than actually pulling an arm.
-Sampling from a Beta distribution is computationally inexpensive and implemented  in most science computing libraries \cite{MATLAB:2010}.
+Sampling from a Beta distribution is computationally inexpensive and implemented  in most science computing libraries~\cite{MATLAB:2010}.
 The full algorithm is shown in Algorithm 1.
@@
 The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity \cite{goetschalckx2011continuous}.
+However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity ~\cite{goetschalckx2011continuous}.
 Chapelle et al.
-demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case \cite{chapelle2011empirical}.
+demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case ~\cite{chapelle2011empirical}.
 Agrawal et al.
-recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms  \cite{agrawal2011analysis}.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms ~\cite{agrawal2011analysis}.
 
@@
  \subsubsection{Friction Uncertainty}
-As shown in \cite{zheng2005,hang2013a}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
+As shown in~\cite{zheng2005,hang2013a}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
 However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
@@
 We then compute the surface normals $\bn_1, \bn_2$ at the contacts using the gradient of the sampled SDF at the contact locations.
-Finally, we use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition \cite{li1988task}.
+Finally, we use these quantities to compute the forces and torques that can be applied to form the contact wrench set $\mW$ and evaluate the force closure condition~\cite{li1988task}.
 
@@
 We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
-GPIS models of 3 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
+GPIS models of 2 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
@@
 For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
-We also performed experiments for the case of two hard contacts in 2-D.
-We drew random grasps $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.
-All experiments were run on machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2014a.
+We  performed experiments for the case of two hard contacts in 2-D.
+We drew random grasps $\Gamma$ by uniformly sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with variance 10 units$^2$.
+All experiments were run on machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2013b.
 
@@
 \ref{sec:grasp_sample}.
-We calculated the expected performance over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation).
+We calculated the expected performance over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation).
 Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
 Iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-We set the discount factor $\gamma =0.98$ for Gittins, which was the highest we could compute due to the exponential growth in computation time with respect to $\gamma$.
+We set the discount factor $\gamma =0.98$ for Gittins, which was the highest we could compute due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.
 
@@
 In Fig.
-\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k}}$, on 3 randomly selected shapes in the dataset.
+\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k}}$, on two real world objects, a door knob and a mechanical switch.
 
@@
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Gittins indices, Thompson sampling, iterative pruning \cite{kehoe2012toward} and uniform allocation.
+\ref{fig:confidence} for Gittins indices, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.
 As illustrated, the confidence interval for Thompson sampling and Gittins indices converges at a faster rate than the other two methods.
@@
     \includegraphics[width=16.5cm]{figures/shapes.jpg}%
-    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on three objects from the Brown Vision 2D Dataset.
+    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects, a door knob and a mechanical switch.
 For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples and the nominal shape.
 The candidate grasp set was of size $|\mG|=1000$.
-We visualize the GPIS representation of the object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.
-On objects A and B Thompson sampling finds the best grasp after 10,000 samples, but for object C the grasp selected has $2\%$ lower $P_F$.}%
+We visualize the GPIS representation of the object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.}%
     \label{fig:shape_samples}%
@@
 	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
-	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
- 	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).
+	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset~\cite{brown}.
+ 	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods~\cite{kehoe2012toward}).
  	The results suggest that when samples are misleadingly ordered, the best policy is uniform allocation.}
@@
 
-For rotational uncertainty in pose, we varied $\sigma_{\phi}$ over the set of $\lbrace 0.03, 0.12,0.24\rbrace$ radians.
-As illustrated in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase in variance to $0.24$ radians or $13^{\circ}$  causes the convergence in simple regret to not be reached until around 6432 samples or an average of 6.4 samples per grasp.
+For rotational uncertainty in pose, we varied $\sigma_{\phi}$ across the set $\lbrace 0.03, 0.12,0.24\rbrace$ radians$^2$.
+As illustrated in Table 1, the performance of the bandit algorithms is affected by the change in rotation.
+Increase in variance to $0.24$ radians$^2$ or $13^{\circ}$  causes the  simple regret to not converge until around 6432 samples or an average of 6.4 samples per grasp.
 
 For translational uncertainty in pose, we varied $\sigma_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma_{\bt} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson sampling.
+Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma_{\bt} = 24$ causes the algorithm to not converged until 8763 evaluations for Thompson sampling.
 
@@
 \ref{fig:worst_case} a case where the observations are misleading.
-
 As illustrated in Fig.
 \ref{fig:worst_case}, all the methods are affected by worst case performance.
-The results indicate that when the observations are misleading the best thing to do is uniform allocation of grasp samples.
-Interestingly, Thompson sampling appears to to continue to improvement while Gittins indices and iterative pruning do not continue to make progress.
+The results suggest that, when the observations are misleading, the preferred policy is uniform allocation of grasp samples.
 
@@
 A similar method could also be done for Thompson sampling.
-Another promising scheme for parrallelizing the MAB, is to have the algorithm not sample one arm at each algorithm but $M$.
+Another promising scheme for parrallelizing the MAB, is to have the algorithm not sample one arm at each iteration but $M$.
 We will explore both of these approaches in future work.

### 2015-06-14 paper.tex
latest revision, changed figure and went over writing

@@
 A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
-Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
+Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  ~\cite{kehoe2012toward, kehoe2012estimating} in terms of finding a higher quality grasp faster.
 However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.

### 2015-06-14 paper.tex
Edited Title, Abstract, Introduction.

@@
 \title{\LARGE \bf
-Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty [v 17] }
+Multi-Armed Bandit Models for 2D Grasp Planning with Uncertainty}
+%Multi-Arm Bandit Models for 2D Sample-Based Grasp Planning with Uncertainty}
 
 \author{Michael Laskey$^1$, Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T.
-Pokorny$^3$, Sachin Patil$^1$,\\ Jur van den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey , jmahler,zmccarthy, sachinpatil, pabbeel\}@berkeley.edu}}%
+Pokorny$^1$, Sachin Patil$^1$,\\ Jur van den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, jmahler,zmccarthy, sachinpatil, pabbeel\}@berkeley.edu}}%
 \thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
@@
 \begin{abstract}
-For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing, mechanics, and control.
-One way to achieve robustness is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and gripper approach and compute the probability of force closure for each candidate to identify the grasp with the highest expected quality.
-Prior work has turned to cloud computing because evaluating the quality of each grasp is computationally demanding.
-To improve efficiency and extend this work, we consider how Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context.
-We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset from 1000 uniformly distributed candidate grasp angles.
+For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing,
+mechanics, and control.  One way to achieve robustness is to evaluate the performance of candidate grasps by sampling
+perturbations in shape, pose, and gripper approach and to compute the probability of force closure for each candidate to
+identify a grasp with the highest expected quality. Prior work has turned to cloud computing since evaluating the
+quality of each grasp is computationally demanding. To improve efficiency and to extend this work, we consider how
+Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context. We formulate robust grasp
+planning as a MAB problem and evaluate grasp planning convergence times using 100 objects shapes from
+the Brown Vision 2D Lab Dataset with 1000 grasp candidates per object.
 We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) with Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
-Thompson Sampling and the Gittins index method, the MAB methods we consider, converged to within 3\% of the optimal grasp up to 10x faster than Uniform allocation.
+We find that Thompson Sampling and the Gittins index MAB methods converged to within 3\% of the optimal grasp up to 10
+times faster than uniform allocation and 5 times faster than iterative pruning. 
 \end{abstract}
@@
 Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
-Planning grasps using analytic methods requires knowledge of contact locations and surface normals.
-However, a robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
+While planning grasps using analytic methods requires knowledge of contact locations and surface normals,
+a robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.
 
@@
 
-    \caption{Number of samples versus the normalized probability of force closure $P_F$ for the best estimated grasp after $t$ samples, $P_F(\Gamma_{\bar{k}, t})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
+    \caption{Number of samples versus the normalized probability of force closure $P_F$ for the best estimated grasp 
+        after $t$ samples, $P_F(\Gamma_{\bar{k}, t})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
     %We evaluated performance on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans.
-    The normalized $P_F$ is the ratio of $P_F(\Gamma_{\bar{k}, t})$ to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
-    The highest quality grasp was determined by brute force search over all candidate grasps ( a method that is 10x more iterations than all methods shown)~\cite{kehoe2012toward} 
-    Uniform allocation and iterative pruning converge to within 3$\%$ of the optimal (the dashed grey line) in approximately 40,000 and 20,000 iterations, respectively.
+    The normalized $P_F$ is given by the ratio of $P_F(\Gamma_{\bar{k}, t})$ to the highest $P_F$ value in the candidate
+    grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset \cite{brown}.
+    The highest quality grasp was determined by brute force search over all candidate grasps (which requires 10x more
+    iterations than all methods shown)~\cite{kehoe2012toward}.
+    Uniform allocation and iterative pruning converge to within 3$\%$ of the highest quality grasp (the dashed grey line) in approximately 40,000 and 20,000 iterations, respectively.
 In comparison, the MAB methods both converge in approximately 4,000 iterations.
@@
 
-One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
+A common measure of grasp quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
 To cope with uncertainty, recent work has explored computing the probability of force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
-One way to compute the probability of force closure is using Monte-Carlo integration over sampled perturbations in the uncertain quantities~\cite{christopoulos2007handling,kehoe2012toward, kim2012physically, weisz2012pose}.
-However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.
-Past work has looked at leveraging the cloud to execute multiple threads in parallel to overcome this problem and proposed a heuristic for adaptive sampling known as iterative pruning~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
-In this work, we aim to extend these cloud-based methods by reducing the number of samples needed to converge to a high-quality grasp.
+To compute the probability of force closure, Monte-Carlo integration over sampled perturbations in the uncertain
+quantities can be applied~\cite{christopoulos2007handling,kehoe2012toward, kim2012physically, weisz2012pose}. However,
+performing Monte-Carlo integration for each candidate grasp hypothesis is computationally expensive.  Past work has
+looked at leveraging cloud computing to parallelize this computation in order to overcome this problem and proposed a heuristic for adaptive sampling known as iterative pruning~\cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey}.
+In this work, we aim to extend these methods by reducing the number of samples needed to converge to a high-quality grasp.
 
-Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing that it is possible to allocate sampling effort to grasps with highest estimated probability of force closure~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}.
-In a standard MAB, there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
-The goal in a MAB problem is to  select a sequence of options to maximize expected reward.
-We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
-We then treat the MAB algorithm as an anytime algorithm that terminates once a user-defined confidence level is met or at a given stopping time.
+Our main contribution is formulating this problem as a Multi-Armed Bandit (MAB) and showing that it is possible to
+allocate sampling effort to grasps with highest estimated probability of force closure~\cite{barto1998reinforcement,
+lai1985asymptotically, robbins1985some}. A standard MAB has a set of possible options, or
+`arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution. The goal in a
+MAB problem is to  select a sequence of arm pulls to maximize the expected reward. We formulate the problem of ranking a
+set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem and consider the
+MAB algorithm as an anytime algorithm that terminates either once a user-defined confidence level is met or at a given stopping time.
 
@@
 We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
-We model uncertainty in pose as a normal distribution around the orientation and 2D position of the object.
-Uncertainty in grasp approach is modeled as a normal distribution around the center and angle of the grasp axis for a parallel jaw gripper.
-Uncertainty in friction coefficient is modeled as a normal distribution around an expected friction coefficient.
+Uncertainty in pose is modelled as a normal distribution around the orientation and 2D position of the object while
+uncertainty in grasp approach is modeled as a normal distribution around the center and angle of the grasp axis for a
+parallel jaw gripper. We furthermore model uncertainty in friction coefficient as a normal distribution around an expected friction coefficient.
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}.
+We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem,
+against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set
+of candidate grasps based on the sample mean~\cite{kehoe2012toward}. 
 Performance in terms of number of samples needed to find the grasp with highest estimated probability of force closure is measured on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
 
-\todo{Should we say 10x over uniform, or up to 10x improvment, or 5x over iterative pruning?}
-Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.
-Although our current implementation is local, our methods may be extended to the cloud by solving $M$ MAB problems on disjoint subsets of the arms and aggregating the results~\cite{glazebrook2000index}.
+%\todo{Should we say 10x over uniform, or up to 10x improvment, or 5x over iterative pruning? 
+%Florian: be consistent with claim in abstract}
+Our simulation results show that Thompson Sampling, a MAB algorithm, required $5$ times fewer samples than iterative
+pruning and $10$ times fewer samples than uniform allocation to determine a grasp within $3\%$ of the estimated highest probability of force closure
+grasp among a set of 1000 grasp candidates and averaged over 100 objects.
+%in the set of 1000 randomly selected grasps averaged over 100 objects. 
+Although our current implementation is executed on a single machine, our methods may be extended to the cloud by solving $M$ MAB problems on disjoint subsets of the arms and aggregating the results~\cite{glazebrook2000index}.
 %by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separately\cite{glazebrook2000index}.

### 2015-06-14 paper.tex
.

@@
 perturbations in shape, pose, and gripper approach and to compute the probability of force closure for each candidate to
-identify a grasp with the highest expected quality. Prior work has turned to cloud computing since evaluating the
-quality of each grasp is computationally demanding. To improve efficiency and to extend this work, we consider how
+identify a grasp with the highest expected quality. Since evaluating the
+quality of each grasp is computationally demanding, prior work has turned to cloud computing. To improve computational efficiency and to extend this work, we consider how
 Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context. We formulate robust grasp
-planning as a MAB problem and evaluate grasp planning convergence times using 100 objects shapes from
+planning as a MAB problem and evaluate convergence times towards an optimal grasp candidate using 100 objects shapes from
 the Brown Vision 2D Lab Dataset with 1000 grasp candidates per object.
@@
 lai1985asymptotically, robbins1985some}. A standard MAB has a set of possible options, or
-`arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution. The goal in a
+`arms'~\cite{barto1998reinforcement} that each return a numeric reward from a stationary distribution. The goal in a
 MAB problem is to  select a sequence of arm pulls to maximize the expected reward. We formulate the problem of ranking a
@@
 We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
-Uncertainty in pose is modelled as a normal distribution around the orientation and 2D position of the object while
+Uncertainty in pose is modeled as a normal distribution around the orientation and 2D position of the object while
 uncertainty in grasp approach is modeled as a normal distribution around the center and angle of the grasp axis for a
@@
 of candidate grasps based on the sample mean~\cite{kehoe2012toward}. 
-Performance in terms of number of samples needed to find the grasp with highest estimated probability of force closure is measured on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+Performance in terms of number of samples needed to find a grasp with highest estimated probability of force closure is measured on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
 
@@
 pruning and $10$ times fewer samples than uniform allocation to determine a grasp within $3\%$ of the estimated highest probability of force closure
-grasp among a set of 1000 grasp candidates and averaged over 100 objects.
+grasp among a set of 1000 grasp candidates per object and averaged over 100 objects.
 %in the set of 1000 randomly selected grasps averaged over 100 objects. 

### 2015-06-15 paper.tex
added Ken's feedback, fixed Fig. 5

@@
 We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) with Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.
-We find that Thompson Sampling and the Gittins index MAB methods converged to within 3\% of the optimal grasp up to 10
-times faster than uniform allocation and 5 times faster than iterative pruning. 
+We find that Thompson Sampling and the Gittins index MAB methods converged to within 3\% of the optimal grasp up to 10x faster than uniform allocation and 5x faster than iterative pruning. 
 \end{abstract}
@@
 
-Our main contribution is formulating this problem as a Multi-Armed Bandit (MAB) and showing that it is possible to
-allocate sampling effort to grasps with highest estimated probability of force closure~\cite{barto1998reinforcement,
+Our main contribution is formulating the grasp selection problem as a Multi-Armed Bandit (MAB) and showing that it is possible to
+allocate sampling effort to grasps with an estimated higher probability of force closure~\cite{barto1998reinforcement,
 lai1985asymptotically, robbins1985some}. A standard MAB has a set of possible options, or
@@
 
-We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, gripper approach, and friction coefficient.
+We study this formulation using probability of force closure~\cite{christopoulos2007handling,  kehoe2012toward,weisz2012pose} as a quality metric under uncertainty in pose, shape, gripper approach, and friction coefficient.
 We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.
@@
 
-We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem,
+We compare Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem,
 against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set
 of candidate grasps based on the sample mean~\cite{kehoe2012toward}. 
-Performance in terms of number of samples needed to find a grasp with highest estimated probability of force closure is measured on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+In terms of the number of samples needed to find a grasp with highest estimated probability of force closure on objects in the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.Our simulation results show that Thompson Sampling, a MAB algorithm, required $5$x fewer samples than iterative
+pruning and $10$x fewer samples than uniform allocation to determine a grasp within $3\%$ of the estimated highest probability of force closure
+grasp among a set of 1000 grasp candidates per object and averaged over 100 objects.
 
@@
 %Florian: be consistent with claim in abstract}
-Our simulation results show that Thompson Sampling, a MAB algorithm, required $5$ times fewer samples than iterative
-pruning and $10$ times fewer samples than uniform allocation to determine a grasp within $3\%$ of the estimated highest probability of force closure
-grasp among a set of 1000 grasp candidates per object and averaged over 100 objects.
+
 %in the set of 1000 randomly selected grasps averaged over 100 objects.
-Although our current implementation is executed on a single machine, our methods may be extended to the cloud by solving $M$ MAB problems on disjoint subsets of the arms and aggregating the results~\cite{glazebrook2000index}.
+
 %by dividing the arms into $M$ subset,where $M$ is the number of available cores, and solving each MAB problem separately\cite{glazebrook2000index}.
@@
 Grasp quality is often measured by the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
+For example, Liu et al.
+used gradients on grasp metrics to guide a mutli-fingered hand towards a grasp \cite{liu2004quality}.
 Analytical quality metrics typically assume precisely known object shape, object pose, and locations of contact~\cite{cheong2011output, ciocarlie2009}.
@@
 It can be computationally expensive though to sample all proposed grasps to convergence.
-To address this computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
-However, the method pruned grasps using only the sample mean, which can discard good grasps in practice.
+To address this, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure.
+However, the method pruned grasps using only the sample mean, which could discard good grasps in practice.
 We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.
@@
 However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arm that currently yields the highest expected reward and exploring new arms.
-Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation~\cite{bergemann2006bandit,robbins1985some}.
+Developing a policy that successfully trades between exploration and exploitation reward has been the focus of extensive research since the problem formulation~\cite{barto1998reinforcement, robbins1985some}.
 
@@
 They then used a MAB algorithm to improve the computational speed of finding the best state machine~\cite{matikainen2013multi}.
+Lauri and Ritala used MAB models to solve a relaxed mixed observable POMDP problem and achieve an efficient solution~\cite{Mikko2015POMDP}.
 %Many variants of UCB have thus been proposed~\cite{cesa2006prediction}.
@@
 In Thompson sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull, the arm with the highest $p_{k,t}$ drawn.
-A reward, $R_{k,t}$, is then observed and the corresponding Beta distribution is updated.The general assumption is that sampling from the Beta distribution for each arm is significantly computationally cheaper than actually pulling an arm.
+A reward, $R_{k,t}$, is then observed and the corresponding Beta distribution is updated.
 Sampling from a Beta distribution is computationally inexpensive and implemented  in most science computing libraries~\cite{MATLAB:2010}.
-The full algorithm is shown in Algorithm 1.
+Thompson sampling does make an assumption that sampling from the Beta distribution for each arm is significantly computationally cheaper than actually pulling an arm.The full algorithm is shown in Algorithm 1.
 
 The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity ~\cite{goetschalckx2011continuous}.
+However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity~\cite{goetschalckx2011continuous}.
 Chapelle et al.
-demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case ~\cite{chapelle2011empirical}.
+demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case~\cite{chapelle2011empirical}.
 Agrawal et al.
-recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear  for $k$ -arms and logarithmic in the case of $2$ arms ~\cite{agrawal2011analysis}.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear for $k$-arms and logarithmic in the case of $2$ arms ~\cite{agrawal2011analysis}.
 
@@
  \subsubsection{Friction Uncertainty}
-As shown in~\cite{zheng2005,hang2013a}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
+As shown in~\cite{hang2013a,zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
 However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
@@
 \subsection{Multi-Armed Bandit Experiments}
-For our experiments we look at selecting an optimal among $|G| = 1000$ candidates.
+For our experiments we look at selecting an optimal grasp among $|G| = 1000$ candidates.
 We draw samples from our graphical model using the technique described in Sec.
@@
 \ref{fig:grasp_quality}, we plot time $t$ vs.
-$P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k}}$.
+$P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k},t}$.
 Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
@@
 In Fig.
-\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k}}$, on two real world objects, a door knob and a mechanical switch.
+\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k},10,000}$, on two real world objects, a coaxial cable splitter and a mechanical switch.
 
@@
 The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$.
-We plot the confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs.
+We plot the algorithm's confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs.
 the number of samples drawn in Fig.
-\ref{fig:confidence} for Gittins indices, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.
+\ref{fig:confidence} for the Gittins indices, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.
 As illustrated, the confidence interval for Thompson sampling and Gittins indices converges at a faster rate than the other two methods.
@@
 \includegraphics[scale=1]{matlab_figures/confidence_bounds.jpg}
-\caption{ Number of samples versus the $95\%$ confidence intervals from Eq.
+\caption{ Number of samples versus the algorithm's $95\%$ confidence intervals from Eq.
 \ref{eq:confidence} on the probability of force closure of the best estimated grasp after $t$ samples using uniform allocation, iterative pruning, Gittins indices, and Thompson Sampling.
@@
     \includegraphics[width=16.5cm]{figures/shapes.jpg}%
-    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects, a door knob and a mechanical switch.
+    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects, a coaxial cable splitter and a mechanical switch.
 For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples and the nominal shape.
@@
 \caption{ \footnotesize 
-	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially.
+	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially for grasps of low quality.
 	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset~\cite{brown}.
@@
 
-For friction coefficient we varied $\sigma_{\mu}$ across the following values $\sigma_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
+For friction coefficient we varied $\sigma^2_{\mu}$ across the following values $\sigma^2_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
 As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 5000 evaluations.
 
-For rotational uncertainty in pose, we varied $\sigma_{\phi}$ across the set $\lbrace 0.03, 0.12,0.24\rbrace$ radians$^2$.
+For rotational uncertainty in pose, we varied $\sigma^2_{\phi}$ across the set $\lbrace 0.03, 0.12,0.24\rbrace$ radians$^2$.
 As illustrated in Table 1, the performance of the bandit algorithms is affected by the change in rotation.
-Increase in variance to $0.24$ radians$^2$ or $13^{\circ}$  causes the  simple regret to not converge until around 6432 samples or an average of 6.4 samples per grasp.
+Increase in variance to $0.24$ radians$^2$  causes the  simple regret to not converge until around 6432 samples or an average of 6.4 samples per grasp.
 
-For translational uncertainty in pose, we varied $\sigma_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace).
-Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma_{\bt} = 24$ causes the algorithm to not converged until 8763 evaluations for Thompson sampling.
+For translational uncertainty in pose, we varied $\sigma^2_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units$^2$ (on a 40 x 40 unit workspace).
+Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma^2_{\bt} = 24$ causes the algorithm to not converged until 8763 evaluations for Thompson sampling.
 
@@
 \end{tabular}
-   \caption { \footnotesize  Number of iterations until convergence to within $3\%$ of grasp with the highest estimated probability of force closure $P_F$ for Thompson sampling under uncertainty in the object orientation $\sigma_{\phi} = \lbrace 0.03,0.12, 0.24 \rbrace$ radians,  uncertainty in the object position $\sigma_{\bt} = \lbrace 3, 12, 24 \rbrace$ units, and uncertainty in friction coefficient $\sigma_{\mu} = \lbrace 0.05,0.2, 0.4 \rbrace$ on a 40$\times$40 grid averaged over 100 independent runs on random objects from the Brown Vision 2D Dataset.
+   \caption { \footnotesize  Number of iterations until convergence to within $3\%$ of grasp with the highest estimated probability of force closure $P_F$ for Thompson sampling under uncertainty in the object orientation $\sigma_{\phi}^2 = \lbrace 0.03,0.12, 0.24 \rbrace$ radians$^2$,  uncertainty in the object position $\sigma_{\bt}^2 = \lbrace 3, 12, 24 \rbrace$ units$^2$, and uncertainty in friction coefficient $\sigma_{\mu}^2 = \lbrace 0.05,0.2, 0.4 \rbrace$ on a 40$\times$40 grid averaged over 100 independent runs on random objects from the Brown Vision 2D Dataset.
 High variances in position and orientation uncertainty increases the amount of iterations needed for the bandit algorithm to converge.
@@
 A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time.
-Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  ~\cite{kehoe2012toward, kehoe2012estimating} in terms of finding a higher quality grasp faster.
+Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  ~\cite{kehoe2012estimating,kehoe2012toward} in terms of finding a higher quality grasp faster.
 However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.

### 2015-06-15 paper.tex
added Ken's feedback, fixed Fig. 5

@@
 The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity~\cite{goetschalckx2011continuous}.
+However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity~\cite{agrawal2011analysis}.
 Chapelle et al.

### 2015-06-15 paper.tex
Some improvements.

@@
 Pokorny$^1$, Sachin Patil$^1$,\\ Jur van den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, jmahler,zmccarthy, sachinpatil, pabbeel\}@berkeley.edu}}%
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, jmahler, zmccarthy,
+ftpokorny, sachinpatil, pabbeel\}@berkeley.edu}}%
 \thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
 \thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
-\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\small \{fpokorny, dani\}@kth.se}}%
-\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\small jurvandenberg@gmail.com}}%
+\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and
+Communication, KTH Royal Institute of Technology, Stockholm, Sweden; {\small dani@kth.se}}%
+\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA; {\small jurvandenberg@gmail.com}}%
 }
@@
 of candidate grasps based on the sample mean~\cite{kehoe2012toward}. 
-In terms of the number of samples needed to find a grasp with highest estimated probability of force closure on objects in the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.Our simulation results show that Thompson Sampling, a MAB algorithm, required $5$x fewer samples than iterative
+In terms of the number of samples needed to find a grasp with highest estimated probability of force closure on objects in the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+Our simulation results show that Thompson Sampling, a MAB algorithm, required $5$x fewer samples than iterative
 pruning and $10$x fewer samples than uniform allocation to determine a grasp within $3\%$ of the estimated highest probability of force closure
@@
 Lai and Robbins~\cite{lai1985asymptotically} showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls.
-They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
+They presented an algorithm called Upper Confidence Bound (UCB) that obtains this bound asymptotically~\cite{lai1985asymptotically}.
 The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
 
-In the robotics field, Hsu et al.
-applied MAB models to improve the performance and reduce computation time of the probabilistic roadmap motion planner by adaptively sampling waypoints~\cite{hsu2005hybrid}.
-Matikainen et al.
-formulated policy learning as choosing a state machine from a known libraries of state machines.
+In the robotics field, Hsu et al. applied MAB models to improve the performance and reduce computation time of the
+probabilistic roadmap motion planner by adaptively sampling waypoints~\cite{hsu2005hybrid}. Matikainen et al. formulated
+policy learning as choosing a state machine from a known library of state machines.
 They then used a MAB algorithm to improve the computational speed of finding the best state machine~\cite{matikainen2013multi}.
@@
 \begin{align}\label{eq:shape_sampling}
-\bar{p}_{k,t} = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} + \alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}
+\bar{p}_{k,t} = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +
+\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
 \end{align}
@@
 \subsubsection{The Gittins Index Method} 
-One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
+One MAB method is to treat the problem as a Markov Decision Process (MDP) and to use Markov Decision theory.
 Formally, a MDP is defined by sets of states, actions, transition probabilities between states, a reward function, and a discount factor~\cite{barto1998reinforcement}.
@@
 
-Methods such as Value Iteration can compute optimal policies for a discrete MDP with respect to the discount factor $\gamma$ ~\cite{barto1998reinforcement}.
-However, the curse of dimensionality affects performance because for $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on each arm then the state space is exponential in size with respect to $K$.
-Using the fact that pulling an arm only changes the state of the arm pulled, Gittins showed that instead of solving the $K$-dimensional MDP one can instead solve $K$ 1-dimensional optimization problems: for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ ~\cite{weber1992gittins}.
+Methods such as Value Iteration can compute optimal policies for a discrete MDP with respect to the discount factor $\gamma$ \cite{barto1998reinforcement}.
+However, the curse of dimensionality affects performance because for $K$ arms, a finite horizon of $T$, and a
+Beta-Bernoulli distribution on each arm, the state space is exponential in size with respect to $K$.
+Using the fact that pulling an arm only changes the state of the arm pulled, Gittins showed that instead of solving the $K$-dimensional MDP one can solve $K$ 1-dimensional optimization problems for each arm $k$ and for each state $x_{k,t} = \lbrace \alpha_{k,t}, \beta_{k,t} \rbrace$ up to a timestep $T$ \cite{weber1992gittins}.
 
@@
 \subsubsection{Thompson Sampling}
-Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$.
+The computational cost of the Gittins index method can increase exponentially in time as the discount factor approaches $1$.
 However, in the case of finding the best arm, we want to plan for long term reward and thus want $\gamma$ as close to $1$ as possible.
@@
 Thompson sampling is an alternative to the Gittins index method that is not prone to this problem. 
-In Thompson sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull, the arm with the highest $p_{k,t}$ drawn.
-A reward, $R_{k,t}$, is then observed and the corresponding Beta distribution is updated.
-Sampling from a Beta distribution is computationally inexpensive and implemented  in most science computing libraries~\cite{MATLAB:2010}.
-Thompson sampling does make an assumption that sampling from the Beta distribution for each arm is significantly computationally cheaper than actually pulling an arm.The full algorithm is shown in Algorithm 1.
+In Thompson sampling, for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull, the arm with the
+highest $p_{k,t}$ is drawn.
+A reward, $R_{k,t}$, is then observed and the corresponding Beta distribution is updated. Sampling from a Beta
+distribution is computationally inexpensive and implemented  in most scientific computing libraries~\cite{MATLAB:2010}.
+Thompson sampling does make an assumption that sampling from the Beta distribution for each arm is significantly computationally cheaper than actually pulling an arm.
+The full algorithm is shown in Algorithm 1.
 
-The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore.
-However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity~\cite{agrawal2011analysis}.
+The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore. However, as
+more samples are received, the method focuses on promising arms, since the Beta distributions approach delta
+distributions as the number of samples drawn tends towards infinity~\cite{agrawal2011analysis}.
 Chapelle et al.
@@
 Agrawal et al.
-recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear for $k$-arms and logarithmic in the case of $2$ arms ~\cite{agrawal2011analysis}.
+recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear for $k$-arms and logarithmic in the case of $2$ arms~\cite{agrawal2011analysis}.
 
 \section{Grasp Planning Problem Definition}
-We consider grasping a rigid, planar object from above using parallel-jaw grippers.
+We consider grasping a rigid planar object from above using parallel-jaw grippers.
 We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
@@
 We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
-For shorthand, the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
+To shorten notation, the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
 In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ can be set from repeatability measurements for a robot~\cite{mooring1986determination}.
@@
 As shown in~\cite{hang2013a,zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
-However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g.
-dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
+However, friction coefficients may be uncertain due to factors such as the presence of material between a gripper and an
+object (e.g.
+dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or due to a misclassification of the object surface to be grasped.
 We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.
@@
 \subsection{Grasp Quality}\label{sec:grasp_sample}
-We measure the quality of grasp using the probability of force closure~\cite{kehoe2012estimating, kehoe2012toward, kim2012physically,weisz2012pose} given a grasp $\Gamma$.
+We measure the quality of a grasp using the notion of probability of force closure~\cite{kehoe2012estimating, kehoe2012toward, kim2012physically,weisz2012pose} given a grasp $\Gamma$.
 Force closure is considered as a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
@@
 
-Given the sources of uncertainty and their relationships as described above, the grasp planning objective is to find the grasp that maximizes the probability of force closure from a set of candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_K\}$:
+Given the sources of uncertainty and their relationships as described above, the grasp planning objective is to find a grasp that maximizes the probability of force closure from a set of candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_K\}$:
 
@@
 \vspace{-2ex}
+{\small
 \begin{align}\label{eq:confidence}
-B(0.025,\alpha_{k,t},\beta_{k,t}) \leq P_F(\Gamma_{k,t})) \leq B(0.975,\alpha_{k,t},\beta_{k,t})
+B(0.025,\alpha_{k,t},\beta_{k,t}) \leq P_F(\Gamma_{k,t})) \leq B(0.975,\alpha_{k,t},\beta_{k,t}).
 \end{align}
-
-To summarize, the algorithm terminates and returns $\bar{k}$, or a grasp that has the highest estimated $P_F$ when the following condition is met:
-
-\vspace{-2ex}
-\begin{align}\label{eq:stopping_condition}
-\lbrace t \geq T_s \: \mbox{or} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace.
-\end{align}
+}
+To summarize, the algorithm terminates and returns $\bar{k}$, or a grasp that has the highest estimated $P_F$ when 
+$t \geq T_s $ or $|B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -
+B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon$.
 
@@
 GPIS models of 2 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
-We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
+We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
+observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
 The measurement noise were assigned uniformly at random to the SDF.
@@
 We  performed experiments for the case of two hard contacts in 2-D.
-We drew random grasps $\Gamma$ by uniformly sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with variance 10 units$^2$.
-All experiments were run on machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2013b.
+We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
+M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
+variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2013b.
 
 \subsection{Multi-Armed Bandit Experiments}
-For our experiments we look at selecting an optimal grasp among $|G| = 1000$ candidates.
-We draw samples from our graphical model using the technique described in Sec.
-\ref{sec:grasp_sample}.
-We calculated the expected performance over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation).
-Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information.
-Iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.
-We set the discount factor $\gamma =0.98$ for Gittins, which was the highest we could compute due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.
+For our experiments we look at selecting an optimal grasp among $|G| = 1000$ candidates. We draw samples from our
+graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
+over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling,
+Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation. Uniform allocation selects a grasp at
+random from the set to sample the next candidate and thus does not use any prior information. Iterative pruning prunes
+grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the
+discount factor $\gamma =0.98$ for the Gittins method, which was the highest we could compute in a reasonable amount of
+time due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.
 
-In Fig.
-\ref{fig:grasp_quality}, we plot time $t$ vs.
-$P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability of force closure for the grasp returned by the algorithm $\Gamma_{\bar{k},t}$.
-Non-MAB methods such as uniform sampling and iterative pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.
-Gittins indices and Thompson sampling  perform significantly better, converging after only 4000 iterations.
-In Fig.
-\ref{fig:shape_samples}, we select a stopping time $T_s=10,000$, which is 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k},10,000}$, on two real world objects, a coaxial cable splitter and a mechanical switch.
+In Fig. \ref{fig:grasp_quality}, we plot time $t$ vs. $P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability
+of force closure for the grasp returned by the algorithm.  Non-MAB methods such as uniform sampling and iterative
+pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal grasp,
+requiring approximately 40,000 and 20,000 iterations.  Gittins indices and Thompson sampling  perform significantly
+better, converging after only 4000 iterations. In Fig. \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$,
+which corresponds to 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k},10,000}$, on two real world objects, a coaxial cable splitter and a mechanical switch.
 
@@
 \ref{fig:graphical_model} involves drawing samples form a GPIS, a high dimensional Gaussian, and evaluating the probability of force closure metric.
-
 The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$.
@@
 
-\vspace*{-10pt}
+\vspace*{-15pt}
 \label{fig:confidence}
@@
 
-For friction coefficient we varied $\sigma^2_{\mu}$ across the following values $\sigma^2_{\mu} = \lbrace 0.05, 0.2, 0.4 \rbrace$.
+For the friction coefficient, we varied $\sigma^2_{\mu}$ across the values $\lbrace 0.05, 0.2, 0.4 \rbrace$.
 As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 5000 evaluations.
@@
 For translational uncertainty in pose, we varied $\sigma^2_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units$^2$ (on a 40 x 40 unit workspace).
-Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma^2_{\bt} = 24$ causes the algorithm to not converged until 8763 evaluations for Thompson sampling.
+Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma^2_{\bt} = 24$ causes the algorithm to not converge until 8763 evaluations for Thompson sampling.
 
@@
 As illustrated in Fig.
-\ref{fig:worst_case}, all the methods are affected by worst case performance.
+\ref{fig:worst_case}, all methods are affected by worst case performance.
 The results suggest that, when the observations are misleading, the preferred policy is uniform allocation of grasp samples.
@@
 However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
-Fortunately, the probability of many successive samples being misleading approaches rapidly zero as the time horizon is increased.
+Fortunately, the probability of many successive samples being misleading rapidly approaches zero as the time horizon is increased.
 
@@
 This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, and by grants from Google. 
-We thank our colleagues who gave feedback and suggestions in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
+We thank the AMPLab, UCBerkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
 

### 2015-06-15 paper.tex
.

@@
  \KwResult{Current Best Arm, $\Gamma^*$ }
- For Beta($\alpha_{k,0}=1$,$\beta_{k,0}=1$) $\forall k \in K$ prior: \\
-\For{ t=1,2,...}{ 
+ Initialize Beta($\alpha_{k,0}=1$,$\beta_{k,0}=1$) $\forall k \in K$ \\
+\For{ t=1,2,...,N }{ 
  Draw $p_{k,t} \sim$ Beta($\alpha_{k,t}$,$\beta_{k,t}$) for $k = 1,...,K$\\
- Pull $k_t  = \underset{k\in K}{\mbox{argmax}} \: p_{k,t}$\\
+ Pull arm $k_t  = \underset{k\in K}{\mbox{argmax}} \: p_{k,t}$\\
  Observe reward $R_{k,t} \in \lbrace 0,1 \rbrace$\\
- Update posterior:\\
+ %Update posterior:\\
 
  \eIf{$k = k_t$}{
- Set $\alpha_{k,t+1} = \alpha_{k,t} + R_{k_t,t}$ \\
- Set $\beta_{k,t+1} = \beta_{k,t} +1-R_{k_t,t}$\\
+ $\alpha_{k,t+1} \gets \alpha_{k,t} + R_{k_t,t}$ \\
+$\beta_{k,t+1} \gets \beta_{k,t} +1-R_{k_t,t}$\\
  }{
- Set $\alpha_{k,t+1} = \alpha_{k,t}$ \\
- Set $\beta_{k,t+1} = \beta_{k,t}$\\
+$\alpha_{k,t+1} \gets \alpha_{k,t}$ \\
+$\beta_{k,t+1} \gets \beta_{k,t}$\\
  }
@@
 We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
-GPIS models of 2 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
@@
 M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
-variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2013b.
+variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
+1600 MHz memory in Matlab 2013b. For illustration purposes, Figure \ref{fig:shape_samples} also displays
+GPIS models of 2 real-world objects are visualized using the GPIS-Blur method~\cite{mahler2015gp}.
 

### 2015-06-15 paper.tex
.

@@
 Multi-Armed Bandit (MAB) models for optimizing decisions can be applied in this context. We formulate robust grasp
-planning as a MAB problem and evaluate convergence times towards an optimal grasp candidate using 100 objects shapes from
+planning as a MAB problem and evaluate convergence times towards an optimal grasp candidate using 100 object shapes from
 the Brown Vision 2D Lab Dataset with 1000 grasp candidates per object.
@@
 
-    \caption{Number of samples versus the normalized probability of force closure $P_F$ for the best estimated grasp 
+     \caption{Number of samples (i.e. iterations of arm pulls) versus the normalized probability of force closure $P_F$ for the best estimated grasp 
         after $t$ samples, $P_F(\Gamma_{\bar{k}, t})$, out of 1000 candidate grasps using uniform allocation, iterative pruning (eliminating candidates that perform poorly on initial samples), and our proposed Multi-Armed Bandit (MAB) algorithms (Gittins indices and Thompson Sampling).
@@
 against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set
-of candidate grasps based on the sample mean~\cite{kehoe2012toward}. 
-In terms of the number of samples needed to find a grasp with highest estimated probability of force closure on objects in the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
+of candidate grasps based on the sample mean~\cite{kehoe2012toward},
+in terms of the number of samples needed to find a grasp with highest estimated probability of force closure on objects in the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
 Our simulation results show that Thompson Sampling, a MAB algorithm, required $5$x fewer samples than iterative
@@
 At timestep $t=0$, we pull arm $k$ and observe reward $R_{k,0}$, where $R_{k,0} \in \lbrace 0, 1\rbrace$.
-The posterior of the Beta after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}$,  $\beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
+The posterior of the Beta distribution after this observation is $\alpha_{k, 1} = \alpha_{k, 0} + R_{k,0}$,  $\beta_{k, 1} = \beta_{k, 0} + 1-R_{k,0}$, where $\alpha_{k,0}$ and $\beta_{k,0}$ are the prior shape parameters for arm $k$ before any samples are evaluated.
 
@@
 \subsubsection{Thompson Sampling}
-The computational cost of the Gittins index method can increase exponentially in time as the discount factor approaches $1$.
-However, in the case of finding the best arm, we want to plan for long term reward and thus want $\gamma$ as close to $1$ as possible.
+The computational cost of determining the Gittins indices can increase rapidly as the discount factor approaches $1$.
+However, in the case of finding the best arm, we want to plan for long-term reward and thus want $\gamma$ as close to $1$ as possible.
 Due to computational constraints we must use a smaller $\gamma$, but this can lead to the algorithm pulling only the most promising arm for many iterations~\cite{kelly1981multi}.
@@
 \begin{align}
-    \underset{\Gamma_{k,} \in \mG}{\text{max }} \sum \limits_{t=1}^
+    \underset{\Gamma_{k,*} \in \mG}{\text{max }} \sum \limits_{t=1}^
     {T_s} P_F \left( \Gamma_{k,t}\right)  \label{eq:problem_def}
 \end{align}
-\noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.
+\noindent The goal is to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}.
 We then formulate the  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson sampling and Gittins indices.

### 2015-06-15 paper.tex
New grasp image.

@@
 \subsubsection{Thompson Sampling}
-The computational cost of determining the Gittins indices can increase rapidly as the discount factor approaches $1$.
+The computational cost of determining the Gittins indices can increase exponentially as the discount factor approaches $1$.
 However, in the case of finding the best arm, we want to plan for long-term reward and thus want $\gamma$ as close to $1$ as possible.
@@
 \includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
-\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch.
-Jaw placements are illustrated by a red direction arrow and line.
+\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch. Jaw placements are
+illustrated by rectangles closing along the dashed line.
 A grasp plan centered at $\by$ (plus symbol) at angle $\psi$ consists of 2D locations for each of the parallel jaws $\bj_1$ and $\bj_2$.
@@
 \section{Simulation Experiments}
-We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
+We used the Brown Vision Lab 2D dataset \cite{brown} of 2D objects as in \cite{christopoulos2007handling}.
 We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
 observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
-The measurement noise were assigned uniformly at random to the SDF.
+The measurement noise was assigned uniformly at random to the SDF.
 We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
-For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
+The noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
 We  performed experiments for the case of two hard contacts in 2-D.
@@
 variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
-1600 MHz memory in Matlab 2013b. For illustration purposes, Figure \ref{fig:shape_samples} also displays
-GPIS models of 2 real-world objects are visualized using the GPIS-Blur method~\cite{mahler2015gp}.
+1600 MHz memory in Matlab 2013b. 
+Figure \ref{fig:shape_samples} displays examples of GPIS models using the GPIS-Blur method~\cite{mahler2015gp}
+as well as resulting grasp samples.
 
 \subsection{Multi-Armed Bandit Experiments}
-For our experiments we look at selecting an optimal grasp among $|G| = 1000$ candidates. We draw samples from our
+For our experiments we consider selecting an optimal grasp among $|G| = 1000$ candidates per object. We draw samples from our
 graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
@@
 This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, and by grants from Google. 
-We thank the AMPLab, UCBerkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
+We thank the AMPLab, UC Berkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
 

### 2015-06-15 paper.tex
.

@@
 We used the Brown Vision Lab 2D dataset \cite{brown} of 2D objects as in \cite{christopoulos2007handling}.
-We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
-observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
-The measurement noise was assigned uniformly at random to the SDF.
+We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which contained 1 if the object was
+observed and 0 if it was not observed. We computed a quadtree representation of the SDF and removed information about
+the SDF on grid cells corresponding to uniformly chosen quadtree cells to simulate localized uncertainty in shape perception.
 We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
-The noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
+The noise parameters in approach, pose, and friction coefficient were set to the following variances: $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
 We  performed experiments for the case of two hard contacts in 2-D.
@@
 \subsection{Multi-Armed Bandit Experiments}
-For our experiments we consider selecting an optimal grasp among $|G| = 1000$ candidates per object. We draw samples from our
+For our experiments, we consider selecting an optimal grasp among $|G| = 1000$ candidates per object. We draw samples from our
 graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
@@
 better, converging after only 4000 iterations. In Fig. \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$,
-which corresponds to 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k},10,000}$, on two real world objects, a coaxial cable splitter and a mechanical switch.
+which corresponds to 10 samples per grasp on average, and for each method visualize the grasp returned,
+$\Gamma_{\bar{k},10,000}$.
 
@@
 The time per iteration for Thompson sampling, Gittins indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms.
-Most of $t_{i}$ is dominated by sampling time, since $t_{p} \approx 30$ms.
+Most of $t_{i}$ is dominated by sampling time, since $t_{p} \approx 30$ ms.
 Sampling from our graphical model in Fig.
 \ref{fig:graphical_model} involves drawing samples form a GPIS, a high dimensional Gaussian, and evaluating the probability of force closure metric.
-The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$.
+The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation
+\ref{eq:confidence}) is below a set threshold $\epsilon$ in size.
 We plot the algorithm's confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs.
@@
     \includegraphics[width=16.5cm]{figures/shapes.jpg}%
-    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects, a coaxial cable splitter and a mechanical switch.
-For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples and the nominal shape.
-The candidate grasp set was of size $|\mG|=1000$.
-We visualize the GPIS representation of the object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.}%
+    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform
+    allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects from the Brown 2D dataset
+\cite{brown}. For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000
+samples and the nominal shape. The candidate grasp set was of size $|\mG|=1000$ for each object. We visualize the GPIS
+representation of the imposed object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.}%
     \label{fig:shape_samples}%
@@
 For the friction coefficient, we varied $\sigma^2_{\mu}$ across the values $\lbrace 0.05, 0.2, 0.4 \rbrace$.
-As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 5000 evaluations.
+As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence
+to zero in simple regret in less than 5000 iterations.
 

### 2015-06-16 paper.tex
.

@@
     \includegraphics[width=16.5cm]{figures/shapes.jpg}%
-    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform
-    allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects from the Brown 2D dataset
-\cite{brown}. For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000
-samples and the nominal shape. The candidate grasp set was of size $|\mG|=1000$ for each object. We visualize the GPIS
-representation of the imposed object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.}%
+    \caption{
+We show two objects from the Brown 2D dataset \cite{brown} where data is omitted at randomly chosen rectangular
+nodes of a quadtree representation. The resulting GPIS models are
+visualized using GPIS-Blur~\cite{mahler2015gp}, where uncertain areas appear more blurry.
+Grasps with the highest estimated normalized probabilty of force closure $P_F$ after 10,000 samples using uniform
+allocation, iterative pruning, Gittins indices, and Thompson sampling are displayed.
+For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000
+samples and the nominal shape. The candidate grasp set was of size $|\mG|=1000$ for each object. }
     \label{fig:shape_samples}%
@@
 
-In future work, we plan to scale our method to 3D objects.
-This could substantially increase the number of candidate grasps, further motivating the use of cloud computing.
-Glazebrook and Wilkinson showed that the Gittins index method could be parallelized by simply dividing the arms into $M$ subsets, where $M$ is the number of cores, and solving each MAB separately.
-\cite{glazebrook2000index}.
-A similar method could also be done for Thompson sampling.
-Another promising scheme for parrallelizing the MAB, is to have the algorithm not sample one arm at each iteration but $M$.
-We will explore both of these approaches in future work.
+In future work, we plan to scale our method to 3D objects. This could substantially increase the number of candidate
+grasps, further motivating the use of cloud computing. Glazebrook and Wilkinson showed that the Gittins index method
+could be parallelized by simply dividing the arms into $M$ subsets, where $M$ is the number of cores, and solving each
+MAB separately. \cite{glazebrook2000index}. A similar method could also be done for Thompson sampling. Another promising
+scheme for parallelizing the MAB is to sample $M$ arms at each iteration. We will explore both of these approaches in future work.
 

### 2015-06-16 paper.tex
.

@@
  Initialize Beta($\alpha_{k,0}=1$,$\beta_{k,0}=1$) $\forall k \in K$ \\
-\For{ t=1,2,...,N }{ 
+\For{ t=1,2,...,T }{ 
  Draw $p_{k,t} \sim$ Beta($\alpha_{k,t}$,$\beta_{k,t}$) for $k = 1,...,K$\\
@@
 of force closure for the grasp returned by the algorithm.  Non-MAB methods such as uniform sampling and iterative
-pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal grasp,
+pruning (eliminating candidate grasps based on sample mean) eventually converge to within 3$\%$ of the optimal grasp,
 requiring approximately 40,000 and 20,000 iterations.  Gittins indices and Thompson sampling  perform significantly
@@
 The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation
-\ref{eq:confidence}) is below a set threshold $\epsilon$ in size.
-We plot the algorithm's confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs.
-the number of samples drawn in Fig.
-\ref{fig:confidence} for the Gittins indices, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.
+\ref{eq:confidence}) is below a set threshold $\epsilon$ in size. We plot the algorithm's confidence intervals around
+the returned grasp $P_F(\Gamma_{\bar{k}})$ vs. the number of samples drawn in Fig. \ref{fig:confidence} for the Gittins
+index method, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.
 As illustrated, the confidence interval for Thompson sampling and Gittins indices converges at a faster rate than the other two methods.
@@
     \label{fig:shape_samples}%
+    \vspace{-12pt}
 \end{figure*}
@@
 \caption{ \footnotesize 
-	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples $P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over 1,000 candidate grasps when samples are ordered such that many perturbations that do result in force closure are given to the algorithm initially for grasps of low quality.
+	Number of samples versus the probability of force closure of the best estimated grasp after $t$ samples
+	$P_F(\Gamma_{\bar{k}, t})$ using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling over
+	1,000 candidate grasps. We generated 1,000 samples for each grasp hypothesis from the graphical model. For the top
+500 grasp hypotheses, we sorted samples such that unstable samples preceeded force closed samples and,
+for the bottom 500 grasp hypotheses, we sorted samples such that stable grasps preceeded unstable grasps.
+This provides misleading observations to the bandit algorithms.
 	The normalized $P_F$ is the ratio of the best estimated grasp at iteration $t$, $P_F(\Gamma_{\bar{k}, t})$, to the highest $P_F$ in the candidate grasp set $P_F(\Gamma^*)$ averaged over 100 independent runs on randomly selected objects from the Brown Vision 2D Dataset~\cite{brown}.
- 	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods~\cite{kehoe2012toward}).
+ 	The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x more
+ 	iterations than any of these methods~\cite{kehoe2012toward}).
  	The results suggest that when samples are misleadingly ordered, the best policy is uniform allocation.}
-\vspace*{-10pt}
+\vspace*{-20pt}
 \label{fig:worst_case}
@@
 to zero in simple regret in less than 5000 iterations.
+For rotational uncertainty in pose, we varied $\sigma^2_{\phi}$ across the set $\lbrace 0.03, 0.12,0.24\rbrace$
+radians$^2$. As illustrated in Table 1, the performance of the bandit algorithms is affected by the change in rotation.
+An increase in variance to $0.24$ radians$^2$  causes the  simple regret to not converge until around 6432 samples or an average of 6.4 samples per grasp.
 
-For rotational uncertainty in pose, we varied $\sigma^2_{\phi}$ across the set $\lbrace 0.03, 0.12,0.24\rbrace$ radians$^2$.
-As illustrated in Table 1, the performance of the bandit algorithms is affected by the change in rotation.
-Increase in variance to $0.24$ radians$^2$  causes the  simple regret to not converge until around 6432 samples or an average of 6.4 samples per grasp.
-
-For translational uncertainty in pose, we varied $\sigma^2_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units$^2$ (on a 40 x 40 unit workspace).
-Our results indicate that the performance of the bandit algorithms is affected by the change in rotation and an increased noise of $\sigma^2_{\bt} = 24$ causes the algorithm to not converge until 8763 evaluations for Thompson sampling.
+For translational uncertainty in pose, we varied $\sigma^2_{\bt}$ in the range of $\lbrace 3,12, 24 \rbrace$ units$^2$
+(on a 40 x 40 unit workspace). Our results indicate that the performance of the bandit algorithms is affected by a 
+change in translation and an increased noise of $\sigma^2_{\bt} = 24$ causes the algorithm to not converge until 8763 evaluations for Thompson sampling.
 
 \subsection{Worst Case}
-The MAB algorithms use the observations of samples drawn to decide which grasp to sample next from.
-To show worst case performance under such a model, we sorted the quality of all 1000 grasps offline and arranged the order of samples, so that the top 500 grasps have samples drawn in the order of worst to best and the bottom 500 grasps have samples drawn in order of best to worst.
-This provides misleading observations to the bandit algorithms.
-We demonstrate in Fig.
-\ref{fig:worst_case} a case where the observations are misleading.
-As illustrated in Fig.
-\ref{fig:worst_case}, all methods are affected by worst case performance.
-The results suggest that, when the observations are misleading, the preferred policy is uniform allocation of grasp samples.
+The MAB algorithms use the observations of samples drawn to decide which grasp to sample next from. To show worst case
+performance under such a model, we generated 1000 samples for each grasp hypothesis from the graphical model. For the top
+500 grasp hypotheses, we sorted samples such that unstable samples ($F=0)$ preceeded force closed ($F=1)$ samples and,
+for the bottom 500 grasp hypotheses, we sorted samples such that stable grasps preceeded unstable grasps.
+This provides misleading observations to the bandit algorithms. We demonstrate in Fig. \ref{fig:worst_case} a case where the
+observations are misleading. As illustrated in Fig. \ref{fig:worst_case}, all methods are affected by worst case
+performance. The results suggest that, when the observations are misleading, the preferred policy is uniform allocation
+of grasp samples.
 
@@
    \caption { \footnotesize  Number of iterations until convergence to within $3\%$ of grasp with the highest estimated probability of force closure $P_F$ for Thompson sampling under uncertainty in the object orientation $\sigma_{\phi}^2 = \lbrace 0.03,0.12, 0.24 \rbrace$ radians$^2$,  uncertainty in the object position $\sigma_{\bt}^2 = \lbrace 3, 12, 24 \rbrace$ units$^2$, and uncertainty in friction coefficient $\sigma_{\mu}^2 = \lbrace 0.05,0.2, 0.4 \rbrace$ on a 40$\times$40 grid averaged over 100 independent runs on random objects from the Brown Vision 2D Dataset.
-High variances in position and orientation uncertainty increases the amount of iterations needed for the bandit algorithm to converge.
+High variance in position and orientation uncertainty increases the amount of iterations needed for the bandit algorithm to converge.
    }
@@
 Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  ~\cite{kehoe2012estimating,kehoe2012toward} in terms of finding a higher quality grasp faster.
-However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
+However, as shown in Fig. \ref{fig:worst_case}, there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
 Fortunately, the probability of many successive samples being misleading rapidly approaches zero as the time horizon is increased.
@@
 could be parallelized by simply dividing the arms into $M$ subsets, where $M$ is the number of cores, and solving each
-MAB separately. \cite{glazebrook2000index}. A similar method could also be done for Thompson sampling. Another promising
+MAB separately. \cite{glazebrook2000index}. A similar method could also be applied for Thompson sampling. Another promising
 scheme for parallelizing the MAB is to sample $M$ arms at each iteration. We will explore both of these approaches in future work.

### 2015-07-12 ICRA2016/bandits_docs/includes/background.tex
Adding initial ICRA 2016 dox

\section{Continuous Correlated Beta Processes}
\seclabel{background}

We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.

\subsection{Beta-Bernoulli Processes}

Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

\vspace{-2ex}
\begin{align*}
	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_k^{\alpha-1} (1 - \theta_k)^{\beta-1}
\end{align*}

\noindent This combination of indepdent Bernoulli random variables with Beta priors is known as a {\it Beta-Bernoulli process}.

Let our prior distribution on $\theta_k$ be a beta distribution with parameters $\alpha_{k,0}$, $\beta_{k,0}$.
Then after observing force closure for $t$ samples $F_{1}(g_k), ..., F_{t}(g_k)$ from our uncertainty model, our posterior distribution on the Bernoulli success probability $\theta_k$ is obtained using Bayes rule.
This yields~\cite{laskey2015bandits}

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{i=1}^t F_{i}(g_k) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{i=1}^t (1 - F_{i}(g_k))
\end{align*}

\noindent Therefore the belief distribution on the probability of force closure $\theta_k$ can be updated by incrementing the value of $\alpha$ and $\beta$ for each force closure observed.
The expected value of $\theta_k$ after the observations is

\begin{align*}
	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
\end{align*}

\subsection{Continuous Correlated Beta Processes}

Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.

A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
Then the CCBP posterior update for $\theta_k$ is~\cite{}:

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
\end{align*}

\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.

### 2015-07-12 ICRA2016/bandits_docs/includes/problem_statement.tex
Adding initial ICRA 2016 dox

\section{Definitions and Problem Statement}
\seclabel{problem}

Let $g \in \mathfrak{se}(3)$ denote an attempted pose of the robot end-effector in 3D space, and $\Gamma = \{ g_1, ..., g_N\}$ denote a set of candidate grasps.
Let $\upsilon$ denote uncertainty in object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
Let $\xi$ denote Gaussian uncertainty in object pose with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
Let $\rho$ denote Gaussian uncertainty in gripper pose with mean $\mu_{\rho} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\rho}$.
Let $\zeta$ denote Gaussian uncertiainty in friction coefficient mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.

We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g) = \mathbb{P} \left( F = 1 \big| g, \upsilon, \xi, \rho, \zeta\right)$~\cite{} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of $P_F$ for the grasps sampled at iteration $t$.

\vspace{-2ex}
\begin{align*}
	\maximum{g_1, ..., g_T \in \Gamma} \sum \limits_{t=1}^T P_F(g_{t})
\end{align*}

\noindent Laskey et al.~\cite{} proposed to solve this objective using algorithms for Multi-Armed Bandits.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

### 2015-07-12 ICRA2016/bandits_docs/paper.tex
Adding initial ICRA 2016 dox

--- 2014-09-30 paper.tex
@@
 %        1         2         3         4         5         6         7         8
-
 \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
-
+% fix acrobat png issue bug
+\pdfminorversion=4
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
@@
 
-\usepackage{amsmath,amssymb}
+\usepackage{balance}
+%\usepackage{subfigure}
+%\usepackage[subfigure]{tocloft}
 
-\usepackage{tikz,hyperref,graphicx,units,subfig}
+%\usepackage[colorlinks]{hyperref}
+%\usepackage[caption=false]{subfig}
+
+\usepackage{caption}
+%\usepackage{subcaption}
+\captionsetup{compatibility=false}
+
 \usepackage{benktools}
+\usepackage{tikz}
+\usetikzlibrary{external}
+\usetikzlibrary{positioning,shapes,shadows,arrows, calc, fit, backgrounds, arrows, positioning}
+\tikzexternalize[prefix=tikz/]
 
-\usepackage{sidecap,wrapfig}
-\usepackage[ruled,vlined]{algorithm2e}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand{\abs}[1]{\lvert#1\rvert} 
-\newcommand{\norm}[1]{\lVert#1\rVert}
-%\newcommand{\suchthat}{\mid}
-\newcommand{\suchthat}{\ \big|\ }
-\newcommand{\bd}{\mathbf{d}}
-\newcommand{\bn}{\mathbf{n}}
-\newcommand{\bp}{\mathbf{p}}
-\newcommand{\bw}{\mathbf{w}}
-\newcommand{\by}{\mathbf{y}}
-\newcommand{\bx}{\mathbf{x}}
-\newcommand{\bz}{\mathbf{z}}
-\newcommand{\bbf}{\mathbf{f}}
-\newcommand{\bzero}{\mathbf{0}}
-\newcommand{\bG}{\mathbf{G}}
-\newcommand{\bA}{\mathbf{A}}
-\newcommand{\bW}{\mathbf{W}}
-\newcommand{\bX}{\mathbf{X}}
-\newcommand{\mX}{\mathcal{X}}
-\newcommand{\mD}{\mathcal{D}}
-\newcommand{\mN}{\mathcal{N}}
-\newcommand{\mW}{\mathcal{W}}
-\newcommand{\mF}{\mathcal{F}}
-\newcommand{\bZ}{\mathbf{Z}}
-
-\newcommand{\bfc}{W}
-\newcommand{\Qinf}{Q_{\infty}}
-\newcommand{\st}[1]{_\text{#1}}
-\newcommand{\rres}{r\st{res}}
-\newcommand{\pos}[1]{(#1)^+}
-\newcommand{\depth}{\operatorname{depth}}
-\newcommand{\dist}{\operatorname{dist}}
-\newcommand{\convhull}{\operatorname{ConvexHull}}
-\newcommand{\minksum}{\operatorname{MinkowskiSum}}
-
-\title{\LARGE \bf
-Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]}
-
-\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space
-
+\newtheorem{lemma}{Lemma}
 \newtheorem{theorem}{Theorem}
+\input{includes/preamble.tex}
 
 \begin{document}
+\title{\LARGE \bf Continuous Correlated Beta Processes for 3D Grasp Planning Under Uncertainty
+	\versionline{1}}
+\author{Jeffrey Mahler, Brian Hou, Michael Laskey, ..., Pieter Abbeel, Ken Goldberg}
+%\institute{Deptartment of Electrial Engineering and Computer Sciences, University of California, Berkeley, USA
+%\{jmahler, zmccarthy, sachinpatil, pabbeel, goldberg\}@berkeley.edu} 
+\maketitle
 
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
+%\input{includes/abstract}
+%
+%\input{includes/introduction}
+%\input{includes/relatedwork}
+%
+\input{includes/problem_statement}
+\input{includes/background}
+%\input{includes/methodology}
+%\input{includes/analysis}
+%\input{includes/experiments}
+%\input{includes/conclusion}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%\appendix
+%\include{includes/proofs}
 
-\begin{abstract}
-Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.
-Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape.
-The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$..
-We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp.
-We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-\vspace{10pt}
-
-\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
-Consider a robot packing boxes in a shipping warehouse environment.
-The robot will frequently encounter objects that it has not seen before.
-The robot will have to plan stable grasps without any prior information other than its sensor data.
-As seen in Fig.
-\ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations.
-Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail.
-To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..
-
-While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface.
-This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}.
-To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field.
-Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
-\caption{\footnotesize
-Left: HD image of a common measuring cup from in a household environment.
-Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
-\vspace*{-10pt}
-\label{fig:noisy data}
-\end{figure}
-
-Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}.
-Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field.
-Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}.
-We constrain the contact points by considering the approach trajectory of a gripper.
-Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory.
-In light of this our contributions are the following:
-
-\begin{enumerate}
-	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
-	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
-	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
-\end{enumerate}
-
-\section{Related Work}
-
- Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}.
-Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al.
-for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.
-Christopoulo et al.
-sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.
-
- The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual.
-Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}\cite{newcombe2011kinectfusion}\cite{hornung2013octomap}.
-Some exciting work done with GPIS representation are the following: Hollinger et al.
-used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
-Dragiev et al.
-showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
-Mahler et al.
-used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.
-
-  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
-With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace.
-We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.
-
-Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}.
-While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}\cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.
-Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}.
-Prior work by Kehoe et al.
-\cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed.
-To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}.
-Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.
-
-\section{Preliminaries and Problem Statement}
-
-In this section we describe the mathematical derivation of Gaussian Process Implicit Surface representations.
-
-\subsection{Gaussian Process (GP) Background}
-GPs provide an infinite dimensional analogue of Multivariate
-Gaussian Distributions which allow us to model distributions over
-functions.
-Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2010gaussian}.
-In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}$, $\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
-The observations are assumed to be noisy measurements from the unknown target function $f$:
-\begin{equation}
-y_i = f(\bx_i) + \epsilon,
-\end{equation}
-where $\epsilon \sim \mN(0,\sigma^2)$ is Gaussian noise in the observations.
-A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
-Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
-\begin{align*}
-	p(f_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
-	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
-	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
-\end{align*}
-where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
-This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:
-
-\vspace{-2ex}
-\begin{align}
-	\text{cov}\left(f(\bx_i), f(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
-	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
-\end{align}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
-\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle.
-Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.
-}
-\vspace*{-10pt}
-\label{fig:GPIS_TSDF}
-\end{figure}
-%\section{Related Work}
-
-For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability.
-Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.
-
-We construct a GPIS by learning a Gaussian Process to fit measurements of a signed distance field of an unknown object.
-Precisely, $x_i \in \mathbb{R}^2$ in 2D and $x_i \in \mathbb{R}^3$ in 3D, and $y_i \in \mathbb{R}$ is a noisy signed distance measurement to the unknown object at $x_i$.
-
-\subsection{Line of Action}
-Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig.
-\ref{fig:line_of_action}.
-A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
-Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide01.jpg}
-\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
-\vspace*{-10pt}
-\label{fig:line_of_action}
-\end{figure}
-
-\subsection{Problem Definition}
-
-Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model and set of possible grasp plans $G$. We are interested in determining
-
-\begin{align}\label{eq:problem_def}
-\Gamma^* \in \mbox{argmax}_{\Gamma \in G} E(Q(\Gamma))
-\end{align}
-
-with respect to a chosen grasp metric Q.
-
-\section{Evaluating a Grasp}
-In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$.
-We will first discuss which grasp metric $Q$ we chose and then proceed into evaluating the expectation $E$ efficiently.
-
-\subsection{Grasp Metric}
-In their pioneering work over two decades ago Ferrari and Canny \cite{ferrari1992}, demonstrated a method to rank grasps by considering their contact points and surface normals.
-Importantly the magnitude of Q yields a measurement that allows one to rank grasps by their physical stability and evaluate the property of force-closure.
-Furthermore, it has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.
-
-The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$.
-Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space.
-A wrench is defined as concatenation of a force and torque vector.
-If the convex hull doesn't enclose the origin, the grasp is not in force-closure.
-Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}\cite{li1988task}.
-
-\subsection{Calculating the Expected Grasp Quality}
-Given a proposed grasp plan $\Gamma$, the expected grasp quality can be evaluated as follows:
-
-\vspace{-2ex}
-\begin{align}\label{eq:shape_sampling}
-E(Q(\Gamma)) = \int Q(g|S,\Gamma) p(S) dS
-\end{align}
-
-Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$.
-To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}.
-See Fig.
-\ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like.
-For computational reasons we approximate the integral via Monte-Carlo Integration.
-We use importance sampling to draw from the distribution induced by GPIS and calculate the following
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width = 8.5cm, height= 5cm ]{figures/Slide13.jpg}
-\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
-\vspace*{-10pt}
-\label{fig:shape_samples}
-\end{figure}
-
-\begin{align*}
-E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
-\end{align*}
-
-To compute the above distribution we must draw samples from $p(S)$.
-In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$.
-Since this is a GPIS, we know the following
-
-\begin{align}\label{eq:joint_shape}
-p(S) = p(sd(\mathcal{W})) \sim N(\mu(\mathcal{W}),\Sigma(\mathcal{W}))
-\end{align}
-
-Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.
-Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}.
-Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.
-
-To reduce complexity we propose sampling not from the shape distributions, but instead from the distributions on the grasps parameters themselves.
-We recall that a grasp according to our metric is defined as the tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, z \rbrace$.
-We are thus interested in calculating $p(g|\Gamma,\mu(x),\Sigma(x))$.
-The distribution on a grasp is defined then as:
-
-\begin{align}\label{eq:joint_on_shape}
-p(g) = p\big(\textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m|\Gamma,\mu(x),\Sigma(x)\big)
-\end{align}
-
-We note here that we currently use the friction coefficient $\mu$ and the expected center of mass $\bar{z}$ as deterministic values.
-For grippers that do not approach along the same line of action (i.e.
-non-parallel jaw grippers) we make the assumption that each contact and normal pair is independent, or
-
-\vspace{-2ex}
-\begin{align}\label{eq:independence}
-p(g) = &\prod_{i=1}^mp\big(\textbf{c}_i,\textbf{n}_i|\gamma_i(t),\mu(x),\Sigma(x)\big)
-\end{align}
-
-We compute the expected grasp quality now as follows:
-
-\vspace{-2ex}
-\begin{align}\label{eq:grasp_sampling}
-E(Q(\Gamma)) = \sum_{i=1}^N Q(g_i) , g_i \in p(g)
-\end{align}
-
-We will now show how these distributions can be computed and how the complexity for evaluating a grasp is reduced from $O(n^6)$ to $O(n^3)$.
-
-\section{Distribution of Grasp Parameters}
-\label{sec:distgrasp}
-
- To sample from $p(g)$, we need to compute the distributions associated with a line of action $p(n_i|c_i)p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ on each of the parameters: contact points $c_i$, surface normals $n_i$  and expected center of mass $\bar{z}$.
- .
-\subsection{Distribution on Contact Points} 
-The probability distribution along the line $\gamma(t)$ is given by:
-
-\vspace{-2ex}
-\begin{equation} \label{eq:line_of_act_dist}
-p\big(sd(\gamma(t)) ; \mu(t),\Sigma(t)\big) \ \forall t \in [a,b] 
-\end{equation}
-
-This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian.
-One could think of this as a marginalization of all other points in signed distance field except the line of action.
-We would like to find the distribution on the first contact point, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.
-
-We now derive this distribution:
-
-\vspace{-2ex}
-\begin{align}
- & p\big(\textbf{c}_i = \gamma(t)\big) = \label{eq:contact_theory} \\
-  & \frac{1}{\eta} p\big(sd(\gamma(t)) = 0\big)P\big(sd(\gamma(\tau)) > 0 | sd(\gamma(t)) = 0\big) \\
-  & \forall \tau \in [0,t)
-\end{align}
-
-Where $\eta$ is a proportionality constant.
-The first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second term can be solved by first conditioning on the joint $p(sd(\gamma(t))|sd(\gamma(t)) = 0)$ and then computing the cumulative distribution function  \cite{petersen2008matrix}.
-We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig.
-\ref{fig:GraspDist}.
-
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
-\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup.
-Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$.
-The two modes correspond to the different potential contact points, either the handle or the base of the cup.
-Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}.
-}
-\vspace*{-10pt}
-\label{fig:GraspDist}
-\end{figure*}
-
-In practice Eq.
-\ref{eq:contact_theory} is not efficient to compute because it requires computation of the cumulative distribution function of a large multivariate Gaussian, so instead we sample from Eq.
-\ref{eq:line_of_act_dist} and find the first positive to negative zero-crossing of the sample along the line.
-
-\subsection{Distribution on Surface Normals} 
-Using Eq.
-\ref{eq:mean_gradient} and Eq.
-\ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively.
-Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$.
-We can now write
-
-\vspace{-2ex}
-\begin{align*}
-p\big(\textbf{n}_i|\textbf{c}_i = \gamma(t)\big) = p\big(\textbf{n}_i |\mu(\gamma(t)), \Sigma(\gamma(t)) \big)
-\end{align*}
-
-One interesting effect of this technique is that we can now marginalize out the line of action model and visual what the surface normal distribution is along a given line of action.
-To our knowledge this is the first attempt to visual surface normals along a grasp plan.
-Marginalization can be performed as follows:
-
-\vspace{-2ex}
-\begin{equation}
-p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt
-\end{equation}
-
-Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}.
-To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.
-In Fig.\ref{fig:GraspDIst}, we visualize the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.
-
-\subsection{Expected Center of Mass}
-
-We recall the quantity $P(sd(x) < 0) = \int_{-\infty}^{0} p(sd(x) =  s \ | \ \mu(x),\Sigma(x)) ds$ is equal to the probability that $x$ is interior to the surface under the current observations.
-We assume that the object has uniform mass density and then $P(sd(x) < 0)$ is the expected mass density at $x$.
-Then we can find the expected center of mass as:
-
-\begin{equation}
-  \bar{z} 
-  =
-  \frac
-    {\int_{\mathcal{W}}x P(sd(x)<0) dx}
-    {\int_{\mathcal{W}}  P(sd(x)<0) dx}
-\end{equation}
-
-which can be approximated by sampling $\mathcal{W}$ in a grid and approximating the spatial integral by a sum.
-Since this operation involves the entire SDF, one would want to use a low resolution grid for computational efficiency.
-We show the computed density and calculated expected center of mass for a marker in Fig.
-\ref{fig:GPIS_MASS}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale = 0.3]{figures/Slide06.jpg}
-\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
-Right: The distribution on the density of each point assuming uniform density}
-\vspace*{-10pt}
-\label{fig:GPIS_MASS}
-\end{figure}
-
-\subsection{Complexity Analysis on Sampling From Grasps Distributions}
-
-After formally deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq.
-\ref{eq:independence}.
-This can be done by drawing samples from Eq.
-\ref{eq:joint_contact_normal}.
-and using our projection technique for the normal distribution.
-
-Having a distribution along a line of action model allows us to sample from those instead of the joint distribution $p(sd(\mathcal{W}))$.
-Assuming the line of action is on the order of $n$, sampling from this distribution for a single grasp is $O(n^3)$.
-However, each proposed grasp plan $\Gamma$ requires the distribution to be computed, so if we have $T=|G|$ then the complexity is $O(Tn^3)$.
-In practice, this should be much smaller than $O(n^6)$.
-
-\section{Adaptive Sampling for Grasp Selection}
-After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq.
-\ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$.
-While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.
-The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig.
-\ref{fig:sampling_convergence}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
-\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp.
-You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
-\vspace*{-10pt}
-\label{fig:sampling_convergence}
-\end{figure}
-
-\subsection{Preliminaries}
-Compared to classical multi-arm bandit problems where the agent is evaluated on cumulative reward at each time-step, we are interested in a decoupling of the exploration and exploitation stage.
-The decoupling is because the agent only needs to select one grasp plan $\Gamma*$ to execute after it has sufficiently explored the other grasp plans.
-The agent is expected to explore the states and then at a given time, stop and choose the best grasp plan.
-This type of pure exploration problem with a limited amount of resources (i.e.
-computation time) is defined as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
-
-More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.
-At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$.
-This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.
-
-Performance of our polices $\psi_t$ and $\zeta_t$ are measured according to simple regret $r_t$ \cite{bubeck2009pure}.
-
-\vspace{-2ex}
-\begin{align}\label{eq:simple_regret}
-&r_t = r(\zeta_t) = \mu^* - \mu_{\zeta_t} \\
-&\mu^* = \mu_j* = \max_{j=1,..,K} \mu_j
-\end{align}
-
-As shown in Eq.
-\ref{eq:simple_regret}, simple regret is defined as the difference between the true expected value of the grasp plan your recommendation, $\mu_{\zeta_t}$ and the true expected value of the best grasp plan $\mu^*$ in the set $G$.
-
-\subsection{Our Implementation}
-In solving Eq.
-\ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
-Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$.
-Thus, we are restricted to the type of bandit policies available to us.
-
-In light of this we implement our allocation policy $\psi_t$ as simple uniform allocation.
-This has been shown to have good performance when the number of evaluations is large \cite{bubeck2009pure}.
-We adapt pure uniform allocation by measuring the $95\%$ confidence interval of each arm based on previous observations.If a given arm $i$ is pulled $n_i$ times, the confidence interval $C_{n, i}$ is defined as \cite{caflisch1998monte}.
-
-\vspace{-2ex}
-\begin{align}
-C_{ i} = \frac{1.96 \sigma_i}{\sqrt{n_i}}
-\end{align}
-
-An arm $i$ is then removed from the possible options if
-
-\vspace{-2ex}
-\begin{align*}
-\mu_{\zeta_t} - C_{\zeta_t} >   \mu_{i}+C_{i}
-\end{align*}
-
-Our recommendation strategy $\zeta_t$ is to take the highest expected grasp quality at time $t$. In future work, we will look at using other allocation and recommendation strategies.
-
-\section{Experiments}
-For the experiments below we used common household objects shown in Fig.
-\ref{fig:GPIS_TSDF}.
-We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor.
-To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
-The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes.
-Our visualization technique follows the approach of \cite{jeffs} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.
-
-We did experiments for the case of two hard contacts in 2-D, however our methods are not limited to this implementation.
-We drew random lines of actions $\gamma_1(t)$ and $\gamma_2(t)$ by sampling around a circle with radius $\sqrt{2}n$ and sampling the circles origin, then projecting onto the largest inscribing circle in the workspace.
-
-\subsection{Sampling from Grasps Vs. Shape}
-We first tested 1000 grasp plans and sampled each one 5000 times  and measured the RMS error between converged expected grasp plan qualities for sampling shape Eq.
-\ref{eq:shape_sampling} vs.
-grasps  Eq.
-\ref{eq:grasp_sampling} was 0.004.
-After confirming the distributions converged close to the same value, we show the computational complexity in Fig.
-\ref{fig:speed_dif} of the two methods for evaluating 100 grasps on an $n \times n$ grid.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
-\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace.
-Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Green is sampling from $p(g)$ or the calculated distribution on grasps.
-As you can see sampling from the calculated distributions scales much better.
-}
-\vspace*{-10pt}
-\label{fig:speed_dif}
-\end{figure}
-
-\subsection{Adaptive Sampling Technique}
-
-We consider the problem of selecting the best grasp out of a set $G$ given a fix number of iterations $I$.
-For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$ and $I= 7000$ or when the set of grasps is a single grasp.
-In Fig.
-\ref{fig:simple_regret}, we plotted the simple regret, Eq.
-\ref{eq:simple_regret}, averaged over 20 runs and compare it to the naive Monte-Carlo method that randomly chooses a grasp plan to draw a sample from .
-The most interesting thing is that the regret is minimized an order of magnitude faster than the naive approach, thus motivating the use of including observations as you select samples.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=8.5cm,height=9cm]{figures/Slide09.jpg}
-\caption{ \footnotesize Comparison of two sampling methods.
-Green is the adaptive bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method.
-We measure their ability to converge in terms of simple regret Eq.
-\ref{eq:simple_regret} averaged over 100 runs.
-We had them determine the best grasp when $|G|=1000$.
-As you can see our method converges much faster with an average of evaluation of 4 samples per grasp.
-We start the process though by deterministically evaluating every grasp 2 times to achieve a baseline, which explains the first part of the graph.}
-\vspace*{-10pt}
-\label{fig:simple_regret}
-\end{figure}
-
-\section{Limitations and Future Work}
-Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{jeffs}.
-
-An additional problem is that we only have an expected center of mass and not a distribution on the center of mass.
-This might prove to be to expensive to compute, however recent work by Panahi et al.
-showed a way to bound the center of mass for convex parts.
-Extension of his work to implicit surfaces could be of possible interest \cite{panahi2014bounding}.
-
-Our budgeted multi-arm bandit approach appears promising, but we still do not know how well it will perform on 3D shapes and large scale grids.
-Future work will be building an efficient construction of GPIS to scale to 3D.
-Lastly, we are interested in investigating how well our algorithm works in parallel computing to be used in the cloud computing context.
-Furthermore, their is a large literature on formulating bandit policies and experimenting with them all will need to be done to see which one works best.
-
-\bibliographystyle{ieeetr}
-\bibliography{references}
+%\balance
+\bibliographystyle{IEEEtranS}
+\bibliography{bibliography}
 

### 2015-07-23 ICRA2016/bandits_docs/includes/introduction.tex
Added initial intro and related work. Pretty rough and bibtex not yet updated

\section{Introduction}
Robots in warehousing and small- to medium-scale manufacturing must be able to efficiently handle to new products and parts.
For example, a robot processing orders in a distribution warehouse must be able to quickly adapt to new consumer products to place them in shipping containers.
Analytic methods for grasp planning requires precise knowledge of contact locations and surface normals,
but a robot in the field may not measure these quantities exactly due to sensor imprecision and missing data resulting from occlusions or highly reflective surfaces.
This motivates a fast and adaptive approach to grasp planning that is robust to uncertainty about the state of the robot and environment.

\TODO{I think the parts about force closure should be greatly compressed here}
Force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}, is a commonly-used binary metric of grasp quality.
Past work has measured the probability of force closure given uncertainty in robot state~\cite{brook2011collaborative, hsiao2011bayesian}, object pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose}, and object shape~\cite{brook2011collaborative, hsiao2011bayesian, kehoe2012estimating, mahler2015gp}.
Computing the probability of force closure requires integrating over the uncertain quantities, which many works have computed using computationally expensive Monte-Carlo integration over sampled perturbations~\cite{christopoulos2007handling, hsiao2011bayesian, kehoe2012toward, kim2012physically, weisz2012pose} parallelized in the cloud~\cite{kehoe2012toward} or using iterative pruning of grasps with low quality~\cite{kehoe2012estimating, kehoe2015survey}.

Recently, Laskey et al.~\cite{laskey2015bandits} showed that it was possible to jointly compute the integral and identify the best grasp using Multi-Armed Bandit (MAB) algorithms such as Thompson Sampling, leading to $5-10\times$ speedups over previous work on a set of parallel-jaw grasps on 2D objects.
However, the MAB algorithms still needed roughly 5,000 samples to identify the best grasp from a pool of 1,000 candidates for each object, which could be time-consuming for 3D objects.
Also, the number of samples is prohibitively high to use the algorithms based on physical success from robot trials instead of in simulation.
One possible reason for the magnitude of samples is that this work treated each grasp and object independently, when in reality grasps and objects with similar features, such as those illustrated in\figref{teaser}, should convey information about the probability of success of one another.

\TODO{Need to get correct terminology. Technically not contextual or combinatorial. Ask Kevin.}
Correlated Multi-Armed Bandits (CMABs) are an extension of standard MABs in which options have correlated rewards.
On each observation, standard MAB algorithms update only the predictive model for the option chosen, while CMAB algorithms typically update a global predictive model of the reward for each option.
This can lead to faster convergence if the algorithm has some knowledge of the correlation structure between options.~\cite{}.
A primary challenge is thus estimating a model of the global correlation structure of the arms, which may require a large amount of data.

In this work, we leverage CMABs to accelerate identification of robust grasps using a correlation structure learned from large amounts of data.
We model the probability of force closure for grasps on 3D shapes as a Correlated Continuous Beta Processes (CCBPs)~\cite{}, a model of 0-1 correlated options with computationally inexpensive posterior updates compared to alternative models such as Gaussian Processes~\cite{}.
Each option corresponds to a single grasp center and axis.
Evaluating an option corresponds to sampling from Gaussian uncertainty in object pose, gripper pose, and contact friction, and measuring force closure for the grasp on the sampled state.
We learn the correlation structure between grasps \TODO{Write up}

Our primary contribution is \TODO{Write up}.
Our experiments show that \TODO{Write up}.

### 2015-07-23 ICRA2016/bandits_docs/includes/related_work.tex
Added initial intro and related work. Pretty rough and bibtex not yet updated

\section{Related Work}

Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric, such as the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{}.
However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output} and the abliity of a gripper to actuate any contact force in the friction cone, which is not true of many real-world grippers~\cite{}.
Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubmaranian, weisz}.
This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis~\cite{}.

Many works have approached grasp synthesis for unknown or familiar objects by transferring grasps from a benchmark set of exemplar objects in a large database.
%Ciocarlie et al.~\cite{ciocarlie2009} found that human hand postures lie on a low-dimensional subspace, called eigen-grasps, and exploited this structure to speed up grasp optimization to synthesize grasps at a large scale in GraspIt!.
Li and Pollard~\cite{} generated grasps by matching object shapes to human hand postured in a database.
Hillebrand and Roa~\cite{} transfer grasps from objects of the same category using pose alignment and geometric warping betwen corresponding points on a shape surface.
Goldfelder et al.~\cite{} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{partial}.
Detry et al.~\cite{91inbohg} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{}.

Work on evaluating grasp quality metrics under uncertainty, such as the probability of force closure, has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
Recent work has also studied the effects of uncertainty in object pose and gripper positioning~\cite{brook2011collaborative, hsiao2011bayesian}.
Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} independently found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics. 
Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{chris}, part tolerancing in manufacturing~\cite{kehoe}, or missing and noisy data from depth sensors such as the Kinect~\cite{mahler, laskey}.
Many have also studied caging gripper configurations, which may be a waypoint to form closure grasps and are robust to perturbations in object pose and shape~\cite{}.

Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg}.
Saxena et al.~\cite{bothsaxenaworks} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
Several other works have examined predicting grasp points using depth gradient features~\cite{rao}, global shape context descriptors~\cite{}, and 3D edges~\cite{}. 
Lenz et al~\cite{lenz} used deep learning to detect grasp bounding boxes in color and depth images.
Herzog et al.~\cite{} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
Kappler et al.~\cite{} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic objects.
Recently, several works have studied forming a database of grasps on synthetic objects from simulation outcomes~\cite{detry} or physical execution~\cite{tellex}.
In comparison, our work uses data-driven correlations between grasps based on local and global features of an object surface to quickly and adaptively acquire samples for evaluating and ranking grasps by their likelihood of success.

Active learning for grasp planning is an active area of research.
Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{kahn, vincsze}, but without use of an explicit grasp quality metric to guide the search.
Recently, Laskey et al.~\cite{} showed that MAB algorithms can be used to accelerate the identification of a grasp with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
Tellex et al.~\cite{} proposed an initiative to adaptively collect a dataset of grasps and point clouds for one million objects using MAB and reinforcemen learning.
MAB algorithms select the next grasp to sample by trading off gaining information about grasps with few samples and exploiting the success of grasps known to work well.
In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{guy}.

One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{}.
In reality, grasp correlations may occure from grasps with similar poses~\cite{}, objects with similar global structure~\cite{}, or on surfaces with similar local geometry~\cite{}.
Correlated Multi-Armed Bandit (CMAB) models, also referred to as Bayesian Optimization models~\cite{}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{}, next-best view prediction in object modeling~\cite{}, envrionmental monitoring in robotics~\cite{}.
Perhaps the most common model of correlations in a CMAB is a linear model~\cite{}, however this depends on the selection of features are linearly related to a success criteria.
Another common model of correlations is a Gaussian Process (GP)~\cite{}, which can model nonlinear relationships between options and rewards but are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far).
As a result, several fast approximate version of GP bandit algorithms exist, such as local GPs~\cite{} and hierarchical GPs~\cite{}.
Recently, Goetschalckx et al.~\cite{} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{}.
In this work we utilize CCBPs to model correaltions between grasps because of their ability to scale to thousands of grasp observations with reasonable runtime.

### 2015-07-27 ICRA2016/bandits_docs/includes/background.tex
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go

@@
 
-We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
-For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
+Finding an approximate solution of Equation~\ref{eq:objective} using Multi-Armed Bandits requires a model of the reward distribution of each arm.
+We use Continuous Correlated Beta Processes (CCBPs) to model the probability of force closure of grasps as a Bernoulli random variable with correlations between grasps.
 We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.
+In practice, correlations may occur between grasps that contact the shape in similar locations may have similar probabilities of force closure.
+Correlations may also occur between grasps on different shapes, such as grasping the handle of a mug and the handle of a teapot.
 
@@
 
-Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
-Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
+For clarity we first review Beta-Bernoulli Processes, the uncorrelated version of CCBPs. 
+Let $\Gamma = \{g_k\}_{k=1}^K$ denote our discrete set of $K$ candidate grasps.
+Let $F(\bg_k) \in \{0, 1\}$ denote the occurence of force closure for a grasp $\bg_k$.
+We model $F(\bg_k)$ as a Bernoulli random variable with probability of success $\theta_k = P_F(\bg_k)$.
 Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
@@
 \begin{align*}
-	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
+	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] &= \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} \\
+	&= \frac{\mbox{\#Successes} +	
 	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
@@
 
-Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
+Continuous Correlated Beta Processes(CCBPs) were independently developed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{chu2011contextual}.
 Such correlations may exist when the Bernoulli random variables depend on common latent factors.
@@
 
-A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
-The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
-Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
+A CCBP is a Beta-Bernoulli process with an additional parameter $k(\bg_i, \bg_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
+The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
+One common choice of kernel is the squared exponential kernel 
+\begin{align*}
+	k(\bg_i, \bg_j) &= \exp\left( -d(\bg_i, \bg_j)^2 \right)
+\end{align*}
+\noindent where $d(\cdot): \mathcal{G} \times \mathcal{G} \rightarrow \mathbb{R}_{+}$ is a distance metric between grasps.
+A common choice of distance metric is
+\begin{align*}
+	d(\bg_i, \bg_j) &= \left( \phi(\bg_i) - \phi(\bg_j) \right)^T C^{-1} \left( \phi(\bg_i) - \phi(\bg_j)\right)
+\end{align*}
+\noindent where $\phi(\cdot) : \mG \rightarrow \mathbb{R}^m$ is an $m$-dimensional feature representation of grasps and $C \in \mathbb{R}^{m \times m}$ is the {\it kernel bandwidth}.
+The bandwidth $C$ scales dimensions of the feature space to mark some dimensions as being more or less relevant for measuring similarity between grasps.
+
+Given a kernel, on each observation we update the belief of each grasp proportional to how similar it is to the observed grasp as measured by the kernel. 
+Let $F_{1}(\bg_{I(1)}), ..., F_{t}(\bg_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
 Then the CCBP posterior update for $\theta_k$ is~\cite{}:
@@
 	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
-	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
-	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
+	\alpha_{k,t} = \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
+	\beta_{k,t} = \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
 \end{align*}
 
-\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.
+\noindent Intuitively, this allows observations of a grasp to constitute "effective" observations of other grasps.

### 2015-07-27 ICRA2016/bandits_docs/includes/problem_statement.tex
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go

@@
 
-Let $g \in \mathfrak{se}(3)$ denote an attempted pose of the robot end-effector in 3D space, and $\Gamma = \{ g_1, ..., g_N\}$ denote a set of candidate grasps.
-Let $\upsilon$ denote uncertainty in object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
-Let $\xi$ denote Gaussian uncertainty in object pose with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
-Let $\rho$ denote Gaussian uncertainty in gripper pose with mean $\mu_{\rho} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\rho}$.
-Let $\zeta$ denote Gaussian uncertiainty in friction coefficient mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
+\TODO{Fill in more details. This is a stripped down version to get ideas down on the page}
+Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by its center in 3D space $\bx \in \mathbb{R}^3$ and approach direction $\bv \in \mS^2$.
+Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3,  \}$ denote the space of all grasps.
+%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
+%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.
 
-We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g) = \mathbb{P} \left( F = 1 \big| g, \upsilon, \xi, \rho, \zeta\right)$~\cite{} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
-To perform this as q	uickly as possible we formulate this as a maximization over the sum of $P_F$ for the grasps sampled at iteration $t$.
+We will assume a known object shape $\nu$, and known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}.
+%Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
+Let $\xi$ be uncertainty in object pose distributed as a Gaussian with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
+Let $\rho$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\rho} \in \mG$ and covariance $\Sigma_{\rho}$.
+Let $\zeta$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
+Given object shape and samples of object pose, and gripper pose, we let $\bc_i(\bg, \theta, \xi, \rho) \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
+Furthermore, let $\bn_i(\bc_i, \nu) \in \mS^2$ denote the surface normal at this contact.
+A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
+
+We measure grasp quality by the probability of force closure subject to these uncertain quantities.
+Let $F \in \{0, 1\}$ denote the occurence of force closure, or the ability to resist wrenches in arbitrary directions~\cite{ferrari1992}.
+Then the probability of force closure for a grasp $\bg$ is
+%\vspace{-2ex}
+\begin{align*}
+	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \xi, \rho, \zeta \right).
+\end{align*}
+\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
+To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$
 
 \vspace{-2ex}
-\begin{align*}
-	\maximum{g_1, ..., g_T \in \Gamma} \sum \limits_{t=1}^T P_F(g_{t})
-\end{align*}
+\begin{align}
+	\maximum{g_{I(1)}, ..., g_{I(T)} \in \mG} \sum \limits_{t=1}^T P_F(g_{I(t)}) \label{eq:objective}
+\end{align}
 
-\noindent Laskey et al.~\cite{} proposed to solve this objective using algorithms for Multi-Armed Bandits.
+\noindent As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$.
+In practice $\Gamma$ has been set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
+\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent}
+
+Even with a discrete set of candidates, evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
+Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
 In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

### 2015-07-27 ICRA2016/bandits_docs/includes/related_work.tex
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go

@@
 Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric, such as the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
-These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{}.
-However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output} and the abliity of a gripper to actuate any contact force in the friction cone, which is not true of many real-world grippers~\cite{}.
-Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubmaranian, weisz}.
-This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis~\cite{}.
+These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{leon2010opengrasp}.
+However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005} and for not taking into account the dynamics of the the grasp~\cite{bicchi2000robotic, prattichizzo2008grasping}.
+Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubramanian2012physical, weisz2012pose}.
+This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis.
 
@@
 %Ciocarlie et al.~\cite{ciocarlie2009} found that human hand postures lie on a low-dimensional subspace, called eigen-grasps, and exploited this structure to speed up grasp optimization to synthesize grasps at a large scale in GraspIt!.
-Li and Pollard~\cite{} generated grasps by matching object shapes to human hand postured in a database.
-Hillebrand and Roa~\cite{} transfer grasps from objects of the same category using pose alignment and geometric warping betwen corresponding points on a shape surface.
-Goldfelder et al.~\cite{} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
-The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{partial}.
-Detry et al.~\cite{91inbohg} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{}.
+Li and Pollard~\cite{li2005shape} generated grasps by matching object shapes to human hand postured in a database.
+Goldfelder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
+The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{goldfeder2009data, goldfeder2011data}.
+Several works have also transferred grasps from objects of the same category by warping contacts betwen corresponding points on a shape surface and locally replanning using local rigid alignment and contact interpolation~\cite{hillenbrand2012transferring, stouraitis2015functional} or by interpolating a shape and grasp over a Grasp Moduli Space~\cite{pokorny2013grasp, pokorny2014grasp}.
+Detry et al.~\cite{detry2012generalizing} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{detry2013learning}.
 
@@
 Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} independently found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics.
-Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{chris}, part tolerancing in manufacturing~\cite{kehoe}, or missing and noisy data from depth sensors such as the Kinect~\cite{mahler, laskey}.
-Many have also studied caging gripper configurations, which may be a waypoint to form closure grasps and are robust to perturbations in object pose and shape~\cite{}.
+Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{christopoulos2007handling}, part tolerancing in manufacturing~\cite{kehoe2012estimating, kehoe2012toward}, or missing and noisy data from depth sensors such as the Kinect modeled with Gaussian process implicit surfaces~\cite{mahler2015gp, laskey2015bandits}.
+Many have also studied caging gripper configurations~\cite{rimon1996caging}, which are a waypoint to form closure grasps for two fingers~\cite{vahedi2008caging, rodriguez2012caging} and may be robust to perturbations in object pose and shape~\cite{diankov2008manipulation, Wan2012_ICRA}.
 
-Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg}.
-Saxena et al.~\cite{bothsaxenaworks} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
-Several other works have examined predicting grasp points using depth gradient features~\cite{rao}, global shape context descriptors~\cite{}, and 3D edges~\cite{}. 
-Lenz et al~\cite{lenz} used deep learning to detect grasp bounding boxes in color and depth images.
-Herzog et al.~\cite{} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
-Kappler et al.~\cite{} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic objects.
-Recently, several works have studied forming a database of grasps on synthetic objects from simulation outcomes~\cite{detry} or physical execution~\cite{tellex}.
-In comparison, our work uses data-driven correlations between grasps based on local and global features of an object surface to quickly and adaptively acquire samples for evaluating and ranking grasps by their likelihood of success.
+Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg2014data}.
+Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
+Several other works have examined predicting grasp points using depth edges~\cite{rao2010grasping}, combinations of 2D and 3D edges~\cite{le2010learning}, and global shape descriptors~\cite{bohg2010learning}.
+Lenz et al~\cite{lenz2015deep} used deep learning to detect grasp bounding boxes in color and depth images, which was later extended to real time by Redmon and Angelova~\cite{redmon2014real}.
+Many works have also considered predicting grasp success from 3D point clouds.
+Herzog et al.~\cite{herzog2012template, herzog2014learning} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
+Kappler et al.~\cite{kappler2015leveraging} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic pointclouds of objects.
+Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
+In comparison, our work studies the convergence rate for adaptively acquiring samples for evaluating and ranking grasps by their likelihood of success through the use of data-driven grasp correlations based on local and global features of an object surface.
 
-Active learning for grasp planning is an active area of research.
-Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{kahn, vincsze}, but without use of an explicit grasp quality metric to guide the search.
-Recently, Laskey et al.~\cite{} showed that MAB algorithms can be used to accelerate the identification of a grasp with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
+Many works have also considered using data-driven approaches for actively selecting grasps.
+Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
+Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discrading grasps known to have poor quality.
 Tellex et al.~\cite{} proposed an initiative to adaptively collect a dataset of grasps and point clouds for one million objects using MAB and reinforcemen learning.
+Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
+Recently, Laskey et al.~\cite{laskey2015bandits} showed that Multi-Armed Bandit algorithms can be used to accelerate the identification of grasps with high probability of force closure under uncertainty in shape, pose, and friction in 2D over candidate sets of 1,000 grasps on 88 objects.
 MAB algorithms select the next grasp to sample by trading off gaining information about grasps with few samples and exploiting the success of grasps known to work well.
-In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{guy}.
+In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{godoy2015adaptive}.
 
-One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{}.
-In reality, grasp correlations may occure from grasps with similar poses~\cite{}, objects with similar global structure~\cite{}, or on surfaces with similar local geometry~\cite{}.
-Correlated Multi-Armed Bandit (CMAB) models, also referred to as Bayesian Optimization models~\cite{}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{}, next-best view prediction in object modeling~\cite{}, envrionmental monitoring in robotics~\cite{}.
-Perhaps the most common model of correlations in a CMAB is a linear model~\cite{}, however this depends on the selection of features are linearly related to a success criteria.
-Another common model of correlations is a Gaussian Process (GP)~\cite{}, which can model nonlinear relationships between options and rewards but are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far).
-As a result, several fast approximate version of GP bandit algorithms exist, such as local GPs~\cite{} and hierarchical GPs~\cite{}.
-Recently, Goetschalckx et al.~\cite{} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
-CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{}.
-In this work we utilize CCBPs to model correaltions between grasps because of their ability to scale to thousands of grasp observations with reasonable runtime.
+One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{laskey2015bandits}.
+In reality, grasp correlations may occur from grasps with similar configurations~\cite{ciocarlie2009, detry2011learning}, objects with similar global structure~\cite{pokorny2013grasp}, or on point cloud surfaces with similar local geometry~\cite{boularias2011learning, herzog2012template, kroemer2010combining, saxena2008robotic}.
+Correlated Multi-Armed Bandit (CMAB) models, sometimes also referred to as Bayesian Optimization models~\cite{brochu2010tutorial}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{chu2011contextual} and envrionmental monitoring in robotics~\cite{hitz2014fully, marchant2012bayesian}.
+Perhaps the most common model of correlations in a CMAB is a linear model~\cite{chu2011contextual}, however this depends on the selection of features are linearly related to a success criteria.
+Another common model of correlations is a Gaussian Process (GP)~\cite{rasmussen2006}, which can model nonlinear relationships between options and rewards.
+Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypothesse via imitation learning and Gaussian process upper-confidence bounds to predict grasp successeses and determine the next grasp to select.
+Boularias et al.~\cite{boularias2014efficient} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks. 
+However, GP models are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far)~\cite{rasmussen2006}, which limited the scale of experiments in both simulation and the physical world that the authors could perform.
+To make the model more tractable, Boularias et al. later extended their work to use an heuristic upper confidence bound-based reinforcement learning~\cite{boularias2015learning}.
+Recently, Goetschalckx et al.~\cite{goetschalckx2011continuous} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
+CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{goetschalckx2011continuous}.
+Montesano and Lopes~\cite{montesano2012active} used CCBPs (although the authors did not refer to them as CCBPs) to actively acquire grasp executions, measuring correlations from the responses to a bank of 151 image filters.
+In this work we also utilize CCBPs to model correaltions between grasps, and study their performance on grasping simulations over thousands of objects.

### 2015-08-10 ICRA2016/bandits_docs/includes/extended_abstract.tex
Added figures for the DexNet paper and an initial extended abstract to share with collaborators

\section{Introduction}
\seclabel{extended-abstract}

Robots in warehouse order fullfillment and small- to medium-scale manufacturing must be able to efficiently grasp and manipulate new products and parts.
For example, a robot processing orders in a distribution warehouse must quickly plan graps for new consumer products to place them in shipping containers. 
% Above motivates speed and adaptivity
% Statement motivating robustness to uncertainty
Furthermore, a robot may not fully observe the state of the workspace, such as the pose or frictional properties of consumer products, due to sensor imprecision and missing data resulting from occlusions.
This poses a challenge for grasp planning with either analytic methods~\cite{ferrari1992, ciocarlie2009} that require precise knowledge of contact locations and surface normals or data-driven approaches~\cite{bohg2014data} that attempt to build a statistical model of grasp success over the massive number of configurations of the environment.
%This motivates an approach to grasp planning that is fast, robust to uncertainty about the state of the robot and environment, and can adapt to new objects and perturbations in the envrionment.

Past work has attempted to overcome this by planning grasps analytically with high probability of force closure~\cite{kehoe2012toward, kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose}, or using data-driven methods to predict grasp success from human labels~\cite{balasubramanian2012physical, detry2013learning,  herzog2014learning, kappler2015leveraging, lenz2015deep, saxena2008robotic} or empirical successes on a physical robot~\cite{boularias2014efficient, brook2011collaborative, detry2011learning, kroemer2010combining, montesano2012active}.
Many works on grasp selection with probablity of force closure evaluate a set of candidate grasps using sampling and select the highest quality grasp either using brute force sampling~\cite{kehoe2012toward, kim2012physically, weisz2012pose}, iterative pruning~\cite{kehoe2012estimating}, or Multi-Armed Bandit (MAB) algorithms to adaptively sample more promising grasps~\cite{barto1998reinforcement,
lai1985asymptotically, laskey2015bandits, robbins1985some}.
However, MAB algorithms, the current fastest sampling method, still required approximately 10 samples per grasp to converge to a solution and needed to be re-run for every new object.

On the other hand, data-driven approaches have shown promise over analytic methods on physical robot trials~\cite{balasubramanian2012physical, herzog2014learning} possibly due to a reduction in modelling error.
The number of objects and grasps tested is typically on the order of tens to hundreds for physical robot trials and at most a few thousand objects and hundreds of thousands of grasps when using simulation or human labels~\cite{goldfeder2009columbia, lenz2015deep, kappler2015leveraging}.
In comparison, state-of-the-art learning results in image classification~\cite{deng2009imagenet, krizhevsky2012imagenet} and speech recognition~\cite{cieri2004fisher, hannun2014deepspeech} relied on datasets containing tens of millions of examples.
This raises the question: will maching learning for grasp planning under vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
%may require orders of magnitude more data than in use currently.

%This motivated gradient-based methods based on approximations to the probabliity of force closure~\cite{mahler2015gp} and using Multi-Armed Bandit algorithms to adaptively sample more promising grasps~\cite{laskey2015bandits}, which reduced the number of samples until convregence by 10$\times$.
%However, the number of iterations was still prohibitively high for real-time execution and prior knowledge could not be utilized for new objects.

To make progress toward answering this question, we introduce the Dexterity Network (DexNet) 1.0, a dataset of tens of thousands of 3D mesh models and a system for building statistical models that predict grasp quality across the dataset.
DexNet is composed of laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking}, and synthetic 3D mesh models from 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}.
~\figref{dexnet-teaser} shows a subset of the objects in the dataset.
To measure similarity between objects, we form an object network based on Deep Convolutional Neural Networks (CNNs) trained to predict object categories from synthetic rendered images of each object~\cite{aubry2015understanding, li2015comparison}.
The DexNet system uses Google Compute Engine to launch up to 600 instances at a time for evaluating grasp quality on subsets of objects and takes approximately 9.5 hours to run 1,800 objects on 180 instances.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
\caption{Sample of 3D mesh models from the DexNet dataset. The dataset consists of over 30,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet} and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison} }
\figlabel{dexnet-teaser}
\vspace*{-15pt}
\end{figure}

In this work, we use DexNet to study the number of samples that MAB algorithms take to converge to a grasp with high probability of force closure across orders of magnitude of prior data of grasps with known quality.
To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for grasps on similar objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
CCBPs allow us to form a prior belief on the quality of candidate grasps for a new object based on data in DexNet and to efficiently update a global belief on the quality of all candidate grasps on an object after observing the outcome of a single sampled grasp.
We measure local similarities between grasps on the same object by a distance between the gripper poses and the similarity between local surface patches near the mean location of contact on the object~\cite{herzog2014learning, kappler2015leveraging}.
We measure global similarity in shape based on the distance between the objects in DexNet.
While we acknowledge probability of force closure has shortcomings~\cite{balasubramanian2012physical}, we use it in this work because it is relatively inexpensive to evaluate computationally, allowing us to better examine the effects of scale.

\section{Preliminary Results}
\seclabel{prelim-experiments}
Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Thompson sampling, a MAB algorithm, without correlations to Thompson sampling using the CCBP model of local grasp similiarity (no prior data).
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because it has very few similar grasps according to our similarity metric.

\begin{figure}[t!]
\centering
	\begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/box_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a cereal box with 250 candidate grasps.}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/flowerpot_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a flower pot with 250 candidate grasps.}
    \end{subfigure}
\caption{Comparison of the normalized $P_F$ of the sampled grasp versus iteration of the MAB algorithm for correlated Thompson sampling, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials. (a) On the cereal box, correlated Thompson sampling converges to within 90\% of the highest quality grasp approximately 4$\times$ faster than uncorrelated. (b) However, correlated and uncorrelated Thompson sampling perform comparably on the flower pot because there are few grasp similarities in the candidate set. }
\figlabel{local-mab}
\vspace*{-15pt}
\end{figure}

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we first examined the effect of using prior data on smaller local datasets of 27 objects.
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for the () using prior grasp data from the five nearest neighbor objects in DexNet out of 27 total objects averaged over 50 trials.
Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
We see that running correlated MAB algorithms with even a small dataset of prior data (blue line) can significantly accelerate the convergence of MAB algorithms to a grasp with high $P_F$, even on an object for which correlated Thompson sampling without priors does not outperform uncorrelated Thompson sampling.
This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object. We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 20$\times$, even with a small database of only 27 prior objects. }
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}

We are currently working on an experiment to quantify the gains in convergence time across orders of magnitudes of prior data (10, 100, 1000, 10000) from DexNet using Google Compute Engine.
Our initial version will be run on a relatively small subset of test objects, and in the coming weeks we will average the performance over a larger set of test objects.
We are particularly interested in seeing if there is a point of diminshing returns from adding more data when using datasets on the order of 10,000 - 100,000 objects.
We are also interested in whether or not adding perturbations to the data such as object reflections and shape perturbations will also increase performance, as has been observed for training Deep CNNs in vision~\cite{krizhevsky2012imagenet}.

### 2015-08-26 ICRA2016/bandits_docs/includes/abstract.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\begin{abstract}
\TODO{Fill in after rest of paper done.}
\end{abstract}

### 2015-08-26 ICRA2016/bandits_docs/includes/algorithm.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\section{Algorithm}

\TODO{Brief section on the high-level algorithm using the model: grasp sampling, evaluation of grasps, thompson sampling}

### 2015-08-26 ICRA2016/bandits_docs/includes/background.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

--- 2015-07-12 ICRA2016/bandits_docs/includes/background.tex
@@
-\section{Continuous Correlated Beta Processes}
+\section{Correlated Multi-Armed Bandit Model}
 \seclabel{background}
 
-We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
-For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
-We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.
+Finding an approximate solution of Equation~\ref{eq:objective} using Multi-Armed Bandits requires a predictive model of the probability of force closure for each grasp.
+We use Continuous Correlated Beta Processes (CCBPs) to model force closure for a grasp as a Bernoulli random variable with correlations across grasps and objects~\cite{goetschalckx2011continuous, montesano2012active}.
+\figref{correlated-motivation} illustrates how using a correlated model can lead to accelerated convergence of bandit algorithms.
+%In practice, correlations may occur between two grasps that contact the same shape in similar locations, or between grasps on different shapes, such as grasping the handle of a mug and the handle of a teapot.
 
-\subsection{Beta-Bernoulli Processes}
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.22]{figures/illustrations/correlated_bandits.png}
+\caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle.
+(Top Right) The true probability of force closure $P_F$ may vary smoothly as a function of the angle of the grasp axis.
+(Middle Left) Uncorrelated MAB models maintain an estimate of $P_F$ independently for each grasp, indicated by bars and their height.
+On iteration $T$ of a MAB algorithm, the grasp indicated with a green bar is sampled and returns force closure.
+(Middle Right) Only the estimate of $P_F$ for the sampled grasp is updated for iteration $T+1$, and the grasp with highest estimated $P_F$ remains suboptimal.
+(Bottom Left) Correlated MAB models maintain a global predictive function (in red) of $P_F$ for any possible grasp but may select grasps from a set of discrete candidates (indicated by dots).
+(Bottom Right) On iteration $T+1$ the grasp indicated by the green dot again returns force closure and the global model is updated, increasing the estimated $P_F$ for ``nearby" grasps.
+Although a suboptimal grasp was sampled, the global model now correctly predicts the optimal grasp in the set.
+}
+\figlabel{correlated-model}
+\vspace*{-15pt}
+\end{figure}
 
-Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
-Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
-Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
-A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+\subsection{Continuous Correlated Beta Processes}
+
+Continuous Correlated Beta Processes(CCBPs) were independently developed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{chu2011contextual}.
+Such correlations may exist when the Bernoulli random variables depend on common latent factors.
+For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps contact the same shape in similar locations or when grasps on different shapes have similar local surface geometries, such as grasping the handle of a mug and the handle of a teapot
+
+Let $\Gamma = \{\bg_k\}_{k=1}^K$ denote our discrete set of $K$ candidate grasps for object $\mO$.
+Let $F(\bg_k) \in \{0, 1\}$ denote the occurence of force closure for a grasp $\bg_k$.
+We model $F(\bg_k)$ as a Bernoulli random variable with probability of success $\theta_k = P_F(\bg_k)$.
+Since we do not know the value of $\theta_k$ for each grasp, we maintain a belief distribution for each $\theta_k$ based on our prior belief about the likelihood of force closure.
+A common choice for a belief distribution on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
 
@@
 
-\noindent This combination of indepdent Bernoulli random variables with Beta priors is known as a {\it Beta-Bernoulli process}.
+A CCBP estimates the shape parameters for a grasp $\bg$ on object $\mO$ using a normalized kernel function $k(\by_i, \by_j) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between two elements of the Grasp Moduli Space, where $\by = \{\bg, \mO\} \in \mM$.
+The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
+In this work we use a unit-bandwidth squared exponential kernel 
+\begin{align*}
+	k(\by_i, \by_j) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} w_m^2 \|\phi_m(\by_i) - \phi_m(\by_j)\|_2^2 \right)
+\end{align*}
+\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space and $w_m \in \mathbb{R}$ are weights scaling the relative contribution of the feature maps to the similarity metric.
 
-Let our prior distribution on $\theta_k$ be a beta distribution with parameters $\alpha_{k,0}$, $\beta_{k,0}$.
-Then after observing force closure for $t$ samples $F_{1}(g_k), ..., F_{t}(g_k)$ from our uncertainty model, our posterior distribution on the Bernoulli success probability $\theta_k$ is obtained using Bayes rule.
-This yields~\cite{laskey2015bandits}
+Upon observing force closure for a grasp and object, we update the Beta belief for every other grasp proportional to how similar it is to the observed grasp as measured by the kernel. 
+Let $F_{1}(\bg_{I(1)}), ..., F_{t}(\bg_{I(t)})$ be $t$ sequential observations of force closure from samples of our uncertainty models for grasps $\bg_{I(1)}, ..., \bg_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
+Then the CCBP posterior update for $\theta_k$ is~\cite{goetschalckx2011continuous}:
 
 \vspace{-2ex}
-\begin{align*}
-	p \left(\theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
-	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{i=1}^t F_{i}(g_k) \\
-	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{i=1}^t (1 - F_{i}(g_k))
-\end{align*}
+\begin{align}
+	p \left(\theta_k | F_{1}(\bg_{I(1)}), ..., F_{t}(\bg_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \notag \\
+	\alpha_{k,t} = \alpha_{k,0} &+ \sum \limits_{j=1}^t k(\by_k, \by_{I(j)}) F_{i}(\bg_{I(j)}) \label{eq:alpha} \\
+	\beta_{k,t} = \beta_{k,0} &+ \sum \limits_{=1}^t k(g\by_k, \by_{I(j)}) (1 - F_{i}(\bg_{I(j)})) \label{eq:beta}
+\end{align}
 
-\noindent Therefore the belief distribution on the probability of force closure $\theta_k$ can be updated by incrementing the value of $\alpha$ and $\beta$ for each force closure observed.
-The expected value of $\theta_k$ after the observations is
+\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.
+
+\subsection{Feature Mappings}
+We use feature mappings $\phi_1, ..., \phi_{N_f}$ that capture both lsimilarity based on local surface geometry and grasp parameters and global object shape.
+
+\subsubsection{Local Features}
+Since grasps may be correlated across very small changes to the grasp center and approach direction on a single shape, our first feature map $\phi_{\ell}(\by) = \bg$ is the identity transformation for the grasp.
+However, similarity between grasp centers and approach directions does not indicate similar $P_F$ if the two surfaces are dissimilar.
+For example, two grasps contacting a box on opposite sides of a corner may be very similar according to $\phi_{\ell}$ but likely to contact the object on surfaces with very different orientations.
+
+To mitigate this issue, we use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging}.
+In this work, we capture local surface patches by an image oriented along a tangent plane to the grasp axis at a contact point, where each pixel stores the distance from the pixel center on the plane to the surface along the grasp axis.
+Let $d_g \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
+Furthermore, let $\bc_k, k = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal vectors to the grasp approach direction $\bv$.
+Then to compute the heightmap value at pixel $(i,j)$ we first compute the 3D location of the pixel on the plane, $\bp_k(i,j) = \bc_k + i \delta \bt_1 + j \delta \bt_2$.
+Then we assign the heightmap value $\bh_k(i,j) = t^*$, where $t^*$ is the smallest value of $t > -r$ such that $\bp_k(i,j) + t \bv$ contacts the shape surface.
+Finally, we rotate the heightmap to align the axes with the eigenvectors of a weighted covariance matrix as in~\cite{tombariunique} in order to make our feature representation rotationally invariant.
+Our feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$.
+\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
+\caption{Three local surface heightmaps extracted on a teapot.
+Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
+}
+\figlabel{local-feature-model}
+\vspace*{-15pt}
+\end{figure}
+
+\subsubsection{Global Features}
+Purely local features may not capture all correlations in probability of force closure between pairs of grasps and objects.
+For example, grasps on the handle of a teapot may have similar grasp center, grasp axis, and even local surface geometry to another tubelike object such as a pen, but different $P_F$.
+To measure global shape similarity, we develop a novel viewpoint-based object representation that pools the views from many virtual viewpoints rendered on a sphere surrounding the object.
+
+\TODO{Justify why class labels help, if they do}
+\figref{global-feature-model} illustrates our method.
+We first render every object to 50 virtual cameras discretized along equal angle increments and oriented toward the object center using Maya.
+Then we finetune AlexNet~\cite{krizhevsky2012imagenet}, a common deep Convolutional Neural Network (CNN) architecture, to predict a class label for each image based on known class labels for the 3D models.
+%While class labels are not necessarily indicative of similarity in the geometry relevant to grasping, in many cases the same class label is enough to guarantee some correspondence of global geometry.
+Next, we pass each of the 50 views of each object through the finetuned CNN and max-pool the output of the fc7 layer.
+As the output is nearly 400 dimensions, we finally reduce the max-pooled output to 100 dimensions using Principal Component Analysis (PCA).
+This yields a representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
+
+\TODO{Expand above paragraph, include more details on method as well as the results of training}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
+\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.
+We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture.
+Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
+\figlabel{global-feature-model}
+\vspace*{-15pt}
+\end{figure}
+
+\subsection{Optimizing Feature Weights}
+One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
+Past work has optimized these weights using a squared error loss on the probability of success predicted by the CCBP and a true probability of success from brute force evaluation~\cite{montesano2012active}.
+However, this criterion may be inappropriate for predicting probabilities, as the predictions must be bounded between 0 and 1.
+In this work we instead select the weights which minimze the cross entropy loss~\cite{}:
 
 \begin{align*}
-	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
-	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
+	w_1^*, ..., w_{N_f}^* = \myargmin{w_1 \geq 0, ..., w_{N_f} \geq 0} \frac{1}{M} \sum \limits_{i=1}^M &\mu_i \log \left( \frac{\alpha_i}{\alpha_i + \beta_i} \right) + \\  &(1 - \mu_i) \log \left( \frac{\beta_i}{\alpha_i + \beta_i} \right)
 \end{align*}
-
-\subsection{Continuous Correlated Beta Processes}
-
-Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
-Such correlations may exist when the Bernoulli random variables depend on common latent factors.
-For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.
-
-A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
-The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
-Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
-Then the CCBP posterior update for $\theta_k$ is~\cite{}:
-
-\vspace{-2ex}
-\begin{align*}
-	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
-	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
-	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
-\end{align*}
-
-\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.
+\noindent where $\alpha_i$ and $\beta_i$ are the posterior shape parameters given by Equations~\ref{eq:alpha} and~\ref{eq:beta} and $\mu_i$ is the known probability of force closure evaluated by exhaustive Monte-Carlo integration for a set of $M$ grasps.
+We optimize this objective using Stochastic Gradient Descent (SGD) with the weights all initialized to 100.

### 2015-08-26 ICRA2016/bandits_docs/includes/experiments.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

--- 2015-08-10 ICRA2016/bandits_docs/includes/extended_abstract.tex
@@
-\section{Introduction}
-\seclabel{extended-abstract}
+\section{Experiments}
+\seclabel{experiments}
 
-Robots in warehouse order fullfillment and small- to medium-scale manufacturing must be able to efficiently grasp and manipulate new products and parts.
-For example, a robot processing orders in a distribution warehouse must quickly plan graps for new consumer products to place them in shipping containers. 
-% Above motivates speed and adaptivity
-% Statement motivating robustness to uncertainty
-Furthermore, a robot may not fully observe the state of the workspace, such as the pose or frictional properties of consumer products, due to sensor imprecision and missing data resulting from occlusions.
-This poses a challenge for grasp planning with either analytic methods~\cite{ferrari1992, ciocarlie2009} that require precise knowledge of contact locations and surface normals or data-driven approaches~\cite{bohg2014data} that attempt to build a statistical model of grasp success over the massive number of configurations of the environment.
-%This motivates an approach to grasp planning that is fast, robust to uncertainty about the state of the robot and environment, and can adapt to new objects and perturbations in the envrionment.
+\subsection{Dataset}
+To study the convergence rate with orders of magnitude of previous grasp data we create a dataset of tens of thousands of 3D CAD models.
+We aggregated data from the laser scanned datasets Amazon Picking Challenge~\cite{}, BigBIRD~\cite{}, KIT~\cite{}, and YCB~\cite{}, as well as the synthetic datasets 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large-scale retrieval dataset~\cite{}.
+To preprocess the data for grasping we set the frame of reference for each object to the the principal components of the vertices of each mesh, set the object center-of-mass as the center of a bounding box around the reoriented vertices, removed unreferenced and invalid vertices, rescaled each synthetic mesh such that its smallest principal direction fit within a PR2 gripper, and converted the mesh to a signed distance field.
+We reserved the YCB dataset as a test set, and used subsets of the remaining data to train hyperparameters and to seed the CCBPs for convergence experiments on the test dataset.
 
-Past work has attempted to overcome this by planning grasps analytically with high probability of force closure~\cite{kehoe2012toward, kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose}, or using data-driven methods to predict grasp success from human labels~\cite{balasubramanian2012physical, detry2013learning,  herzog2014learning, kappler2015leveraging, lenz2015deep, saxena2008robotic} or empirical successes on a physical robot~\cite{boularias2014efficient, brook2011collaborative, detry2011learning, kroemer2010combining, montesano2012active}.
-Many works on grasp selection with probablity of force closure evaluate a set of candidate grasps using sampling and select the highest quality grasp either using brute force sampling~\cite{kehoe2012toward, kim2012physically, weisz2012pose}, iterative pruning~\cite{kehoe2012estimating}, or Multi-Armed Bandit (MAB) algorithms to adaptively sample more promising grasps~\cite{barto1998reinforcement,
-lai1985asymptotically, laskey2015bandits, robbins1985some}.
-However, MAB algorithms, the current fastest sampling method, still required approximately 10 samples per grasp to converge to a solution and needed to be re-run for every new object.
+\subsection{System}
+To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud services.
+We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
+Each model is stored in .OBJ format and the average size is roughly 0.5MB.
+We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
+Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
+When an instance is launched, we mount DexNet via a persistent disk containing a particular set of objects and grasps.
+Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
+After all instances complete, the master script turns off all instances, unmounts all disks, downloads the results from each instance, and sends the user a notification email.
+The results can be optionally analyzed by the master script.
 
-On the other hand, data-driven approaches have shown promise over analytic methods on physical robot trials~\cite{balasubramanian2012physical, herzog2014learning} possibly due to a reduction in modelling error.
-The number of objects and grasps tested is typically on the order of tens to hundreds for physical robot trials and at most a few thousand objects and hundreds of thousands of grasps when using simulation or human labels~\cite{goldfeder2009columbia, lenz2015deep, kappler2015leveraging}.
-In comparison, state-of-the-art learning results in image classification~\cite{deng2009imagenet, krizhevsky2012imagenet} and speech recognition~\cite{cieri2004fisher, hannun2014deepspeech} relied on datasets containing tens of millions of examples.
-This raises the question: will maching learning for grasp planning under vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
-%may require orders of magnitude more data than in use currently.
+\subsection{Rate of Convergence}
+\TODO{Replace with final versions. The current results are preliminary}
 
-%This motivated gradient-based methods based on approximations to the probabliity of force closure~\cite{mahler2015gp} and using Multi-Armed Bandit algorithms to adaptively sample more promising grasps~\cite{laskey2015bandits}, which reduced the number of samples until convregence by 10$\times$.
-%However, the number of iterations was still prohibitively high for real-time execution and prior knowledge could not be utilized for new objects.
-
-To make progress toward answering this question, we introduce the Dexterity Network (DexNet) 1.0, a dataset of tens of thousands of 3D mesh models and a system for building statistical models that predict grasp quality across the dataset.
-DexNet is composed of laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking}, and synthetic 3D mesh models from 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}.
-~\figref{dexnet-teaser} shows a subset of the objects in the dataset.
-To measure similarity between objects, we form an object network based on Deep Convolutional Neural Networks (CNNs) trained to predict object categories from synthetic rendered images of each object~\cite{aubry2015understanding, li2015comparison}.
-The DexNet system uses Google Compute Engine to launch up to 600 instances at a time for evaluating grasp quality on subsets of objects and takes approximately 9.5 hours to run 1,800 objects on 180 instances.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
-\caption{Sample of 3D mesh models from the DexNet dataset.
-The dataset consists of over 30,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet} and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison} }
-\figlabel{dexnet-teaser}
-\vspace*{-15pt}
-\end{figure}
-
-In this work, we use DexNet to study the number of samples that MAB algorithms take to converge to a grasp with high probability of force closure across orders of magnitude of prior data of grasps with known quality.
-To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for grasps on similar objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
-CCBPs allow us to form a prior belief on the quality of candidate grasps for a new object based on data in DexNet and to efficiently update a global belief on the quality of all candidate grasps on an object after observing the outcome of a single sampled grasp.
-We measure local similarities between grasps on the same object by a distance between the gripper poses and the similarity between local surface patches near the mean location of contact on the object~\cite{herzog2014learning, kappler2015leveraging}.
-We measure global similarity in shape based on the distance between the objects in DexNet.
-While we acknowledge probability of force closure has shortcomings~\cite{balasubramanian2012physical}, we use it in this work because it is relatively inexpensive to evaluate computationally, allowing us to better examine the effects of scale.
-
-\section{Preliminary Results}
-\seclabel{prelim-experiments}
 Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
@@
 
-To examine the effects of orders of magnitude of prior data in the MAB algorithms, we first examined the effect of using prior data on smaller local datasets of 27 objects.
-\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for the () using prior grasp data from the five nearest neighbor objects in DexNet out of 27 total objects averaged over 50 trials.
+To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from DexNet: 0, 15, 150, and 1500 objects.
+\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle using prior grasp data from the five nearest neighbor objects in DexNet averaged over 50 trials.
 Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
-We see that running correlated MAB algorithms with even a small dataset of prior data (blue line) can significantly accelerate the convergence of MAB algorithms to a grasp with high $P_F$, even on an object for which correlated Thompson sampling without priors does not outperform uncorrelated Thompson sampling.
+We see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly largers subsets of prior data used.
 This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.
+Future work will examine these effects on a larger subset of objects and will use more than five nearest neighbors from DexNet to compute priors, which may lead to even larger gains for larger subsets of prior data.
 
@@
 \centering
-\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model.jpg}
+\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
 \caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object.
-We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 20$\times$, even with a small database of only 27 prior objects.
+Prior grasps were taken from increasingly larger subsets of DexNet: 15, 150, and 1500 objects.
+We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used.
 }
@@
 
+\TODO{Remove below section}
 We are currently working on an experiment to quantify the gains in convergence time across orders of magnitudes of prior data (10, 100, 1000, 10000) from DexNet using Google Compute Engine.
@@
 We are also interested in whether or not adding perturbations to the data such as object reflections and shape perturbations will also increase performance, as has been observed for training Deep CNNs in vision~\cite{krizhevsky2012imagenet}.
+
+\section{Sensitivity to Uncertainty}

### 2015-08-26 ICRA2016/bandits_docs/includes/introduction.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

@@
 \section{Introduction}
-Robots in warehousing and small- to medium-scale manufacturing must be able to efficiently handle to new products and parts.
-For example, a robot processing orders in a distribution warehouse must be able to quickly adapt to new consumer products to place them in shipping containers.
-Analytic methods for grasp planning requires precise knowledge of contact locations and surface normals,
-but a robot in the field may not measure these quantities exactly due to sensor imprecision and missing data resulting from occlusions or highly reflective surfaces.
-This motivates a fast and adaptive approach to grasp planning that is robust to uncertainty about the state of the robot and environment.
+\seclabel{introduction}
 
-\TODO{I think the parts about force closure should be greatly compressed here}
-Force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}, is a commonly-used binary metric of grasp quality.
-Past work has measured the probability of force closure given uncertainty in robot state~\cite{brook2011collaborative, hsiao2011bayesian}, object pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose}, and object shape~\cite{brook2011collaborative, hsiao2011bayesian, kehoe2012estimating, mahler2015gp}.
-Computing the probability of force closure requires integrating over the uncertain quantities, which many works have computed using computationally expensive Monte-Carlo integration over sampled perturbations~\cite{christopoulos2007handling, hsiao2011bayesian, kehoe2012toward, kim2012physically, weisz2012pose} parallelized in the cloud~\cite{kehoe2012toward} or using iterative pruning of grasps with low quality~\cite{kehoe2012estimating, kehoe2015survey}.
+Robots in warehouse order fullfillment and small- to medium-scale manufacturing must be able to efficiently grasp and manipulate new products and parts.
+For example, a robot processing orders in a distribution warehouse must quickly plan graps for new consumer products to place them in shipping containers. 
+% Above motivates speed and adaptivity
+% Statement motivating robustness to uncertainty
+Furthermore, a robot may not fully observe the state of the workspace, such as the pose or frictional properties of consumer products, due to sensor imprecision and missing data resulting from occlusions.
+This poses a challenge for grasp planning with either analytic methods~\cite{ferrari1992, ciocarlie2009} that require precise knowledge of contact locations and surface normals or data-driven approaches~\cite{bohg2014data} that attempt to build a statistical model of grasp success over the massive number of configurations of the environment.
+%This motivates an approach to grasp planning that is fast, robust to uncertainty about the state of the robot and environment, and can adapt to new objects and perturbations in the envrionment.
 
-Recently, Laskey et al.~\cite{laskey2015bandits} showed that it was possible to jointly compute the integral and identify the best grasp using Multi-Armed Bandit (MAB) algorithms such as Thompson Sampling, leading to $5-10\times$ speedups over previous work on a set of parallel-jaw grasps on 2D objects.
-However, the MAB algorithms still needed roughly 5,000 samples to identify the best grasp from a pool of 1,000 candidates for each object, which could be time-consuming for 3D objects.
-Also, the number of samples is prohibitively high to use the algorithms based on physical success from robot trials instead of in simulation.
-One possible reason for the magnitude of samples is that this work treated each grasp and object independently, when in reality grasps and objects with similar features, such as those illustrated in\figref{teaser}, should convey information about the probability of success of one another.
+Past work has attempted to overcome this by planning grasps analytically with high probability of force closure~\cite{kehoe2012toward, kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose}, or using data-driven methods to predict grasp success from human labels~\cite{balasubramanian2012physical, detry2013learning,  herzog2014learning, kappler2015leveraging, lenz2015deep, saxena2008robotic} or empirical successes on a physical robot~\cite{boularias2014efficient, brook2011collaborative, detry2011learning, kroemer2010combining, montesano2012active}.
+Many works on grasp selection with probablity of force closure evaluate a set of candidate grasps using sampling and select the highest quality grasp either using brute force sampling~\cite{kehoe2012toward, kim2012physically, weisz2012pose}, iterative pruning~\cite{kehoe2012estimating}, or Multi-Armed Bandit (MAB) algorithms to adaptively sample more promising grasps~\cite{barto1998reinforcement,
+lai1985asymptotically, laskey2015bandits, robbins1985some}.
+However, MAB algorithms, the current fastest sampling method, still required approximately 10 samples per grasp to converge to a solution and needed to be re-run for every new object.
 
-\TODO{Need to get correct terminology. Technically not contextual or combinatorial. Ask Kevin.}
-Correlated Multi-Armed Bandits (CMABs) are an extension of standard MABs in which options have correlated rewards.
-On each observation, standard MAB algorithms update only the predictive model for the option chosen, while CMAB algorithms typically update a global predictive model of the reward for each option.
-This can lead to faster convergence if the algorithm has some knowledge of the correlation structure between options.~\cite{}.
-A primary challenge is thus estimating a model of the global correlation structure of the arms, which may require a large amount of data.
+On the other hand, data-driven approaches have shown promise over analytic methods on physical robot trials~\cite{balasubramanian2012physical, herzog2014learning} possibly due to a reduction in modelling error.
+The number of objects and grasps tested is typically on the order of tens to hundreds for physical robot trials and at most a few thousand objects and hundreds of thousands of grasps when using simulation or human labels~\cite{goldfeder2009columbia, lenz2015deep, kappler2015leveraging}.
+In comparison, state-of-the-art learning results in image classification~\cite{deng2009imagenet, krizhevsky2012imagenet} and speech recognition~\cite{cieri2004fisher, hannun2014deepspeech} relied on datasets containing tens of millions of examples.
+This raises the question: will maching learning for grasp planning under vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
+%may require orders of magnitude more data than in use currently.
 
-In this work, we leverage CMABs to accelerate identification of robust grasps using a correlation structure learned from large amounts of data.
-We model the probability of force closure for grasps on 3D shapes as a Correlated Continuous Beta Processes (CCBPs)~\cite{}, a model of 0-1 correlated options with computationally inexpensive posterior updates compared to alternative models such as Gaussian Processes~\cite{}.
-Each option corresponds to a single grasp center and axis.
-Evaluating an option corresponds to sampling from Gaussian uncertainty in object pose, gripper pose, and contact friction, and measuring force closure for the grasp on the sampled state.
-We learn the correlation structure between grasps \TODO{Write up}
+%This motivated gradient-based methods based on approximations to the probabliity of force closure~\cite{mahler2015gp} and using Multi-Armed Bandit algorithms to adaptively sample more promising grasps~\cite{laskey2015bandits}, which reduced the number of samples until convregence by 10$\times$.
+%However, the number of iterations was still prohibitively high for real-time execution and prior knowledge could not be utilized for new objects.
 
-Our primary contribution is \TODO{Write up}.
-Our experiments show that \TODO{Write up}.
+To make progress toward answering this question, we introduce the Dexterity Network (DexNet) 1.0, a dataset of tens of thousands of 3D mesh models and a system for building statistical models that predict grasp quality across the dataset.
+DexNet is composed of laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking}, and synthetic 3D mesh models from 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}.
+~\figref{dexnet-teaser} shows a subset of the objects in the dataset.
+To measure similarity between objects, we form an object network based on Deep Convolutional Neural Networks (CNNs) trained to predict object categories from synthetic rendered images of each object~\cite{aubry2015understanding, li2015comparison}.
+The DexNet system uses Google Compute Engine to launch up to 600 instances at a time to samples and evaluate grasps on subsets of objects and to learn predictive models of grasp quality.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
+\caption{Sample of 3D mesh models from the DexNet dataset.
+The dataset consists of over 30,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet} and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison} }
+\figlabel{dexnet-teaser}
+\vspace*{-15pt}
+\end{figure}
+
+In this work, we use DexNet to study the number of samples that MAB algorithms take to converge to a grasp with high probability of force closure across orders of magnitude of prior data of grasps with known quality.
+To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for grasps on similar objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
+CCBPs allow us to form a prior belief on the quality of candidate grasps for a new object based on data in DexNet and to efficiently update a global belief on the quality of all candidate grasps on an object after observing the outcome of a single sampled grasp.
+We measure local similarities between grasps on the same object by a distance between the gripper poses and the similarity between local surface patches near the mean location of contact on the object~\cite{herzog2014learning, kappler2015leveraging}.
+We measure global similarity in shape based on the distance between the objects in DexNet.
+Our results suggest \TODO{Fill in with new results}.
+%While we acknowledge probability of force closure has shortcomings~\cite{balasubramanian2012physical}, we use it in this work because it is relatively inexpensive to evaluate computationally, allowing us to better examine the effects of scale.

### 2015-08-26 ICRA2016/bandits_docs/includes/problem_statement.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

@@
 
-\TODO{Fill in more details. This is a stripped down version to get ideas down on the page}
-Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by its center in 3D space $\bx \in \mathbb{R}^3$ and approach direction $\bv \in \mS^2$.
-Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3,  \}$ denote the space of all grasps.
+We consider the problem of finding the parallel-jaw grasp with the maximum probability of a binary success metricsuch as force closure on a previously unknown object under uncertainty in object pose, gripper pose, and friction coefficient.
+
+\subsection{Grasp and Object Model}
+Our grasping model is illustrated in~\figref{grasp-model}.
+Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \mS^2$.
+We assume that the gripper will be opened to its maximal width before closing on the object.
+Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{newcombe2011kinectfusion, mahler2015gp}, which is zero on the object surface, positive outside the object, and zero inside the object.
+We assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
+Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3, \bv \in \mS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where $\mF$ is the space of all SDFs.
+Our joint grasp and object space, or Grasp Moduli Space~\cite{pokorny2013grasp}, is $\mM = \mG \times \mH$.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.png}
+\caption{(Left) We parameterize parallel-jaw grasps by the centroid of the jaws $\bx \in \mathbb{R}^3$ and approach direction, or direction along which the jaws close, $\bv \in \mS^2$.
+The grasp parameters $\bx$ and $\bv$ are specified with respect to a coordinate frame located at the object center of mass $\bz$ and oriented along the principal directions of the object.
+(Right) The jaws are closed until contacting the object surface at locations $\bc_1, \bc_2 \in \mathbb{R}^3$, at which the surface has normals $\bn_1, \bn_2 \in \mathbb{S}^2$.
+The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$.
+From these parameters we can derive the theoretical forces and torques that the gripper can apply to the object.
+}
+\figlabel{grasp-model}
+\vspace*{-15pt}
+\end{figure}
+
+%Let $\mM = \left\{\mV, \mT \right\}$ be a triangular mesh representing an object's geometry, where $\mV = \{\bw_i \in \mathbb{R}^3 \}_{i=1}^{N_v}$ is a set of $N_v$ vertices and $\mT = \{ \bt_i \in \mathbb{Z}_{+}^3 \}_{i=1}^{N_t}$ is a set of $N_t$ triangles formed by triplets of integer indices of vertices.
 %We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
@@
 
-We will assume a known object shape $\nu$, and known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}.
+\subsection{Sources of Uncertainty}
+We assume known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}.
 %Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
-Let $\xi$ be uncertainty in object pose distributed as a Gaussian with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
-Let $\rho$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\rho} \in \mG$ and covariance $\Sigma_{\rho}$.
-Let $\zeta$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
-Given object shape and samples of object pose, and gripper pose, we let $\bc_i(\bg, \theta, \xi, \rho) \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
-Furthermore, let $\bn_i(\bc_i, \nu) \in \mS^2$ denote the surface normal at this contact.
+Let $\xi$ be Gaussian uncertainty in object pose with mean $\bar{T} \in SE(3)$ and covariance $\Sigma_{\xi}$ following the model of Barfoot and Furgale~\cite{barfoot2014associating}.
+Let $\nu$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\nu} \in \mG$ and covariance $\Sigma_{\nu}$.
+Let $\gamma$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\gamma} \in \mathbb{R}$ and covariance $\Sigma_{\gamma}$.
+Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.
+
+\subsection{Contact Model}
+Our contact model is illustrated in the right panel of \figref{grasp-model}.
+Given object shape and samples of object pose, and gripper pose, we let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
+Furthermore, let $\bn_i \in \mS^2$ denote the surface normal at contact $\bc_i$.
+To compute the forces that each contact can apply to the object, we discretize the friction cone at contact $i$ into a discrete set of $N_c$ facets with vertices $\bbf_{i,j}$ for $j = 1, ..., N_c$~\cite{pokorny2013classical} for a given friction coefficient $\gamma$.
+Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
+Thus the set of all wrenches that can be applied by a grasp $\bg$ is $\mW = \{ \bw_{i,j} = [\bbf_{i,j}, \tau_{i,j}]^T \big| i = 1, 2 \text{ and } j = 1, ..., N_c\}$.
+
+\subsection{Quality Metric}
+In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
+We acknowledge that force closure assumes the abliity to actuate the gripper to apply arbitrary forces in the contact friction cone~\cite{} and that some evidence suggests that deterministic force closure is not a strong predictor of physical grasp success~\cite{balasubramanian2012physical}.
+However, we use the probability of force closure because of it has shown some promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate as compared to human labels or physical executions, allowing us to better study the effects of large amounts of data on convergence.
+
+Let $F \in \{0, 1\}$ denote the occurence of force clsoure.
+To compute force closure for a grasp $\bg$ on object $\mO$ given deterministic samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
+Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$.
 A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
 
-We measure grasp quality by the probability of force closure subject to these uncertain quantities.
-Let $F \in \{0, 1\}$ denote the occurence of force closure, or the ability to resist wrenches in arbitrary directions~\cite{ferrari1992}.
-Then the probability of force closure for a grasp $\bg$ is
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.5]{figures/illustrations/dexnet_graphical_model_simple.png}
+\caption{A graphical model describing the relationships between known uncertain parameters (shaded gray) such as object pose and the force closure random variable $F$.}
+\figlabel{graphical-model}
+\vspace*{-15pt}
+\end{figure}
+
+\subsection{Objective}
+The probability of force closure for a grasp $\bg$ is
 %\vspace{-2ex}
 \begin{align*}
-	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \xi, \rho, \zeta \right).
+	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \rho, \zeta \right).
 \end{align*}
 \noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
-To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$
+To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$:
 
@@
 \begin{align}
-	\maximum{g_{I(1)}, ..., g_{I(T)} \in \mG} \sum \limits_{t=1}^T P_F(g_{I(t)}) \label{eq:objective}
+	\underset{g_{I(1)}, ..., g_{I(T)} \in \mG}{\text{maximize }} \sum \limits_{t=1}^T P_F(g_{I(t)}). \label{eq:objective}
 \end{align}
 
-\noindent As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$.
-In practice $\Gamma$ has been set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
-\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent}
-
-Even with a discrete set of candidates, evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
+As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ where $\Gamma$ is set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
+However, even with a discrete set of candidates, fully evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
 Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
 In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.
+
+\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent under uncertainty}

### 2015-08-26 ICRA2016/bandits_docs/includes/related_work.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

@@
 Recently, Goetschalckx et al.~\cite{goetschalckx2011continuous} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
-CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{goetschalckx2011continuous}.
+CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when approximate kernels are computed using efficient nearest neighbor queries~\cite{goetschalckx2011continuous}.
 Montesano and Lopes~\cite{montesano2012active} used CCBPs (although the authors did not refer to them as CCBPs) to actively acquire grasp executions, measuring correlations from the responses to a bank of 151 image filters.

### 2015-08-26 ICRA2016/bandits_docs/paper.tex
Added initial intro and related work. Pretty rough and bibtex not yet updated
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

@@
 \begin{document}
-\title{\LARGE \bf Continuous Correlated Beta Processes for 3D Grasp Planning Under Uncertainty
-	\versionline{1}}
-\author{Jeffrey Mahler, Brian Hou, Michael Laskey, ..., Pieter Abbeel, Ken Goldberg}
+\title{\LARGE \bf DexNet 1.0: Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
+		\versionline{2}}
+\author{Jeffrey Mahler, Brian Hou, Mel Roderick, Michael Laskey, Kai Kohlhoff, \\ Torsten Kroeger, Florian Pokorny, James Kuffner, Ken Goldberg}
 %\institute{Deptartment of Electrial Engineering and Computer Sciences, University of California, Berkeley, USA
@@
 
-%\input{includes/abstract}
+\TODO{Possibly will include Matthieu Aubry and Pieter Abbeel as coauthors as well}
+
+\input{includes/abstract}
 %
-%\input{includes/introduction}
-%\input{includes/relatedwork}
+\input{includes/introduction}
+\input{includes/related_work}
 %
@@
 \input{includes/background}
-%\input{includes/methodology}
+\input{includes/algorithm}
 %\input{includes/analysis}
-%\input{includes/experiments}
+\input{includes/experiments}
 %\input{includes/conclusion}

### 2015-09-03 ICRA2016/bandits_docs/includes/abstract.tex
First full version of the paper with committed adobe illustrator figures

@@
 \begin{abstract}
-\TODO{Fill in after rest of paper done.}
+%\TODO{Adapted from flyer, probably needs to be toned down}
+Advances in Big Data and distributed computing, combined with very large datasets of images and human speech, have produced a series of  data-driven results that surpass decades of research in analytic methods and, in some cases, that surpass human ability.
+For example, deep neural networks can now learn to play video games, recognize faces, and translate between languages.
+This raises the question: can Big Data and computation produce analogous advances in robot grasping and manipulation?
+We introduce the Dexterity-Network (Dex-Net) 1.0, a Cloud-based dataset of 3D object models labelled with parallel-jaw grasps and similarity between objects and grasps based on multi-view Convolutional Neural Networks (CNNs) and grasp heightmaps.
+We use Dex-Net in Multi-Armed Bandit (MAB) algorithms to quickly find a grasp with high probability of force closure on an object from a set of 250 candidates. 
+We extend previous MAB models to predict grasp quality using similiarity to prior objects and grasps in Dex-Net using Continuous Correlated Beta Processes (CCBPs).
+Our initial results suggest that using prior objects from Dex-Net can accelerate grasp planning by up to $10\times$.
+%\TODO{More concrete results here as I organize them} 
+Code, data, and additional information can be found at: \TODO{Url}
 \end{abstract}

### 2015-09-03 ICRA2016/bandits_docs/includes/algorithm.tex
First full version of the paper with committed adobe illustrator figures

@@
-\section{Algorithm}
+\section{Grasp Selection Algorithm}
+\seclabel{algo}
 
-\TODO{Brief section on the high-level algorithm using the model: grasp sampling, evaluation of grasps, thompson sampling}
+Our full algorithm for grasp selection using Multi-Armed Bandits (MABs) with prior grasp and object data from Dex-Net is detailed in Algorithm~\ref{alg:full}.
+We first generate a set of candidate grasps $\mG$ for object $\mO$ and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
+Next, we run MAB by selecting the next grasp using Thompson sampling, evaluating each grasp using force closure as described in \secref{quality}, and updating the Beta belief parameters for each grasp.
+Finally, we return the grasp that has the highest mean prediction.
+
+\begin{algorithm}
+{\small
+    \SetAlgoLined
+    {\bf Input:} Object $\mO$, Number of Candidate Grasps $K$, Database of Prior Knowledge $\mD$, Maximum Iterations $T$, \\ Prior beta shape $\alpha_0$, $\beta_0$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
+    \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}
+
+    \tcp{Generate candidate grasps and priors}
+	$\mG$ = AntipodalGraspSample($\mO, K$) \;
+	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
+	\For{$\bg_k \in \mG$}{
+		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
+		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD$)\; 
+		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
+	}
+
+	\tcp{Run MAB with Thompson Sampling}
+	\For{$t = 1, .., T$}{
+		$j = $ SelectNextIndex($\mA_{t-1}, \mB_{t-1}$)\;
+		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
+		$F_{j} = $ EvaluateForceClosure($\bg_j, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
+		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
+		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, F_j, \mG$)\; 
+	}
+
+	\tcp{Find grasp with max estimated quality}
+	$\mU = \left\{ \mu_j = \frac{\alpha_{j,T}}{\alpha_{j,T} + \beta_{j,T}} \big| j = 1, ..., K \right\}$\;
+	$j^*$ = $\myargmax{j = 1, ..., T} \mu_j$\;
+	return $\bg_j$\;
+    \caption{Grasp Selection With Multi-Armed Bandits Using a Database of Prior Knowledge}
+    \label{alg:full}
+}
+\end{algorithm}
+
+\subsection{Grasp Candidate Generation}
+\seclabel{candidates}
+In past work, Laskey et al.~\cite{laskey2015bandits} sampled candidate grasps in 2D by sampling a grasp center from an isotropic Gaussian ceneterd at the object center of mass and sampling a grasp angle uniformly at random.
+However, this method is problematic in 3D because many of the samples may be oriented away from the object and the grasps may not adequately cover the entire surface of the object.
+
+In this work, we use a modified version of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
+Let $K$ be the number of grasps to sample, $w$ be the maximal opening of the gripper, $\gamma$ be an estimate of the friction coefficient, and $\mC = \{ \by \in \bR^3 \big| | f(\by) | < \epsilon$ be the set of points on the object surface for threshold $\epsilon$ and object SDF $f$.
+To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly at random from $\mC$, which can be done using rejection sampling.
+Next we form the friction cone $\mF_1$ at $\bc_1$ as described in \secref{contact} and sample a direction $\bv$ uniformly at random from the cone.
+We then compute
+\vspace{-2ex}
+\begin{align*}
+	\bc_2 &= \minimum{t \geq 0} t \text{ such that } | f\left(\bc_1 + (w / 2 - t) \bv \right) | < \epsilon \\
+	\bx &= 0.5 (\bc_1 + \bc_2)
+\end{align*}
+\noindent similar to the contact computation of \secref{contact} and form the friction cone $\mF_2$ at contact $\bc_2$.
+This yields a grasp $\bg = [\bx, \bv]^T$.
+We add $\bg$ to our candidate set if $-\bv \in C\mF_1)$ and $\bv \in C(\mF_2)$, where $C(\mF) = \{ \by = t \bbf \big| t \in [0, \infty], \bbf \in Conv(\mF)\}$ is the convex cone for friction cone $\mF$.
+
+\subsection{Thompson Sampling}
+\seclabel{thompson}
+
+Following Laskey et al.~\cite{laskey2015bandits}, we use Thompson sampling to select the next grasp to evaluate given belief distributions on the probability of force closure for each arm specified by estimates $\mA_t = \{\alpha_{1,t}, ..., \alpha_{K,t}\}$ and $\mB_t = \{\beta_{1,t}, ..., \beta_{K,t}\}$ at iteration $t$.
+Thompson sampling samples a probability of force closure $\hat{\theta}_{j,t} \sim B(\alpha_{j,t}, \beta_{j,t})$ for all grasps $j = 1, ..., K$, then selects the grasp $j_t^* = \myargmax{j} \hat{\theta}_{j,t}$ to evaluate next.
+Several other criteria exist for selecting the next evaluation in MAB, such as Gittins indices~\cite{laskey2015bandits}, Upper Confidence Bounds~\cite{boularias2015learning}, and Expected Improvement~\cite{montesano2012active}.

### 2015-09-03 ICRA2016/bandits_docs/includes/background.tex
First full version of the paper with committed adobe illustrator figures

--- 2015-07-12 ICRA2016/bandits_docs/includes/background.tex
@@
-\section{Continuous Correlated Beta Processes}
+\section{Correlated Multi-Armed Bandit Model}
 \seclabel{background}
 
-We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
-For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
-We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.
+Finding an approximate solution of Equation~\ref{eq:objective} with Multi-Armed Bandits requires a predictive model of the probability of force closure for each grasp.
+We use Continuous Correlated Beta Processes (CCBPs) to model force closure for a grasp as a Bernoulli random variable with correlations across grasps and objects~\cite{goetschalckx2011continuous, montesano2012active}.
+\figref{correlated-motivation} illustrates how using a correlated model can lead to accelerated convergence of bandit algorithms.
+%In practice, correlations may occur between two grasps that contact the same shape in similar locations, or between grasps on different shapes, such as grasping the handle of a mug and the handle of a teapot.
 
-\subsection{Beta-Bernoulli Processes}
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.22]{figures/illustrations/correlated_bandits.png}
+\caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle.
+(Top Right) The true probability of force closure $P_F$ as a function of the angle of the grasp axis.
+(Middle Left) Uncorrelated MAB models maintain an estimate of $P_F$ independently for each grasp, indicated by bars and their height.
+On iteration $T$ of a MAB algorithm, the evaluated grasp (green bar) is force closure for samples .
+(Middle Right) Only the estimate of $P_F$ for the sampled grasp is updated on iteration $T+1$, and the grasp with highest estimated $P_F$ remains suboptimal.
+(Bottom Left) Correlated MAB models maintain a global predictive function (red) of $P_F$ for any possible grasp but may select grasps from a set of discrete candidates (indicated by dots).
+(Bottom Right) On iteration $T+1$, the evaluated grasp (green dot) is sampl returns force closure and the global model is updated, increasing the estimated $P_F$ for ``nearby" grasps.
+Although a suboptimal grasp was sampled, the global model now correctly predicts the optimal grasp in the set.
+}
+\figlabel{correlated-motivation}
+\vspace*{-15pt}
+\end{figure}
 
-Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
-Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
-Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
-A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+\subsection{Continuous Correlated Beta Processes}
+
+Continuous Correlated Beta Processes (CCBPs) were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in MAB problems~\cite{chu2011contextual}.
+Such correlations may exist when the Bernoulli random variables depend on common latent factors.
+For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar, such as a grasp on the handle of a mug and the handle of a teapot.
+
+We are interested in solving Equation~\ref{eq:objective} for a new object $\mO_i$.
+Let $\mG_{i}$ be a set of $K$ candidate grasps for $\mO_i$, $\Gamma_i = \{\bg_{i,k}\}_{k=1}^K$.
+We define $F_{j,\ell} = F(\bg_{j,\ell}) \in \{0, 1\}$ an occurence of force closure on an evaluation of any grasp $\bg_{j,\ell}$ on object $\mO_j$ using samples of object pose, gripper pose, and friction, as described in \secref{quality}.
+Then let $N_{j,\ell}$ be the number of total evaluations of for grasp $\bg_{j,\ell}$, and define $S_{j,\ell} = \sum_{a=1}^{N_{j,\ell}} F_{j,\ell}$ to be the total number of times force closure has been observed for any grasp.
+Futhermore let $\mD = \{ N_{j,\ell}, S_{j,\ell}, \mY_{j,\ell} = (\bg_{j,\ell}, \mO_j) \big| j = \{1, ..., M\}, \ell \in \{1, ..., K\} \}$ be a discrete set of $M$ known objects stored in a database, each with a discrete set of $K$ candidate grasps $\Gamma_j = \{\bg_{j,\ell}\}_{\ell=1}^K$ and $N_{j,\ell}$ and $S_{j,\ell}$ for each object.
+
+%and let $\mS = \{ S_{j,\ell} \big| j \in \{1, .., M\}, \ell \in \{1, ..., K\} \}$ be the history of force closure observations for all grasps and all objects in the database.
+
+We model force closure for each candidate grasp, $F_{i,k}$, as a Bernoulli random variable with probability of success $\theta_{i,k}= P_F(\bg_{i,k})$.
+Since we do not know the value of $\theta_{i,k}$, we maintain a belief distribution for each $\theta_{i,k}$ based on our prior belief about the likelihood of force closure.
+In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
 
@@
 
-\noindent This combination of indepdent Bernoulli random variables with Beta priors is known as a {\it Beta-Bernoulli process}.
+A CCBP estimates the shape parameters for a grasp and object $\mY_{i,k} = (\bg_{i,k}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
+The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
+In this work we use a unit-bandwidth squared exponential kernel 
+\begin{align*}
+	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} w_m^2 \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_2^2 \right)
+\end{align*}
+\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space and $w_m \in \mathbb{R}$ are weights scaling the relative contribution of the feature maps to the similarity metric.
 
-Let our prior distribution on $\theta_k$ be a beta distribution with parameters $\alpha_{k,0}$, $\beta_{k,0}$.
-Then after observing force closure for $t$ samples $F_{1}(g_k), ..., F_{t}(g_k)$ from our uncertainty model, our posterior distribution on the Bernoulli success probability $\theta_k$ is obtained using Bayes rule.
-This yields~\cite{laskey2015bandits}
+Before the first iteration of the MAB algorithm, we update our belief for each candidate grasp to its similarity to all grasps and objects from the database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
+%\vspace{-2ex}
+\begin{align}
+	%p \left(\theta_{i,k} | \mS, \mN \right) &= \betadist\left( \alpha_{i,k,0}, \beta_{j,k,0} \right) \notag \\
+	\alpha_{i,k,0} = \alpha_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K k(\mY_{i,k}, \mY_{j,\ell}) S_{j,\ell} \label{eq:alpha-prior} \\
+	\beta_{i,k,0} = \beta_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K  k(\mY_{i,k} \mY_{j,\ell}) (N_{j,\ell} - S_{j,\ell}) \label{eq:beta-prior}
+\end{align}
+\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits}.
+% and $\mS$ and $\mN$ are the number of successes and total trials for grasps in the database, respectively.
+Upon observing $F_{i,k}$ for grasp $\bg_{i,k}$ on iteration $t$, we update our belief $\theta_{j,k}$ for all other grasps on object $\mO_i$ by~\cite{goetschalckx2011continuous}:
 
 \vspace{-2ex}
+\begin{align}
+	\alpha_{j,k,t} &= \alpha_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) F_{i,k} \label{eq:alpha} \\
+	\beta_{j,k,t} &= \beta_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) (1 - F_{i,k})\label{eq:beta}
+\end{align}
+
+\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.
+
+\subsection{Feature Mappings}
+We use a set of feature mappings $\phi_1, ..., \phi_{N_f}$ to capture similarity based on grasp parameters, local surface geometry, and global object shape.
+
+\subsubsection{Grasp Parameters}
+\seclabel{param-features}
+Since grasps may be correlated across small changes to the grasp center and approach direction on a single shape, we use the feature maps $\phi_{x}(\mY) = \bx$ and $\phi_{v}(\mY) = \bv$, the identity transformations for the grasp center and axis.
+Additionally we use the moment arm feature map $\phi_{\rho}(\mY) = [ \| \rho_1 \|_2, \| \rho_2 \|_2]^T \in \bR^2$ because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
+However, similarity between grasp centers and approach directions may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar.
+For example, consider two grasps that contact a box near the corner.
+The two grasps may have similar parameters and moment arms but may contact the surface on different sides of the edge, resulting in different surface orientations at the contact points.
+
+\subsubsection{Grasp Heightmaps}
+\secref{local}
+We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging}.
+Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
+Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
+Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
+To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
+Then we assign the heightmap value
 \begin{align*}
-	p \left(\theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
-	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{i=1}^t F_{i}(g_k) \\
-	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{i=1}^t (1 - F_{i}(g_k))
+	\bh_k(u,v) = \minimum{t \geq -r} t \text{ such that } | f\left( \bp_k(u,v) + s_k \bv \right) | < \epsilon
 \end{align*}
+ where $s_1 = -1$, $s_2 = 1$, $\epsilon$ is the surface threshold used for finding contacts, and $f$ is the SDF of object $\mO$. 
+Finally, we make the heightmap rotationally invariant by rotating it to align the axes with the eigenvectors of the weighted covariance matrix of contact points generating the heightmap as described in~\cite{tombariunique}.
+Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$.
+\TODO{This is slightly more complicated but takes a bit to explain; basically the ordering of contacts doesn't matter here}
+\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
 
-\noindent Therefore the belief distribution on the probability of force closure $\theta_k$ can be updated by incrementing the value of $\alpha$ and $\beta$ for each force closure observed.
-The expected value of $\theta_k$ after the observations is
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
+\caption{Three local surface heightmaps extracted on a teapot.
+Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
+}
+\figlabel{local-feature-model}
+\vspace*{-15pt}
+\end{figure}
+
+\subsubsection{Global Features}
+\seclabel{cnn}
+While force closure is based on local surface properties of an object around contact points, measuring global similarity may be similarity may be useful for two reasons.
+First, the sums in Equations~\ref{eq:alpha-prior} and~\ref{eq:beta-prior} may be expensive when the database is large, and global object similarity can be used to sum over only the objects that are grasped similarity to a new object of interest.
+Second, the heightmaps may not capture all possible contact points for a grasp under perturbations in object and gripper pose.
+
+%\TODO{Justify why class labels help, if they do}
+We measure global similarity between objects using a feature mapping derived from multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval.
+\figref{global-feature-model} illustrates our method.
+Let $R$ be the maximum dimension of the object bounding box.
+We first render every object on a white background in a total of $N_c$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{\pi}{N_c}$ and $\delta_{\phi} = \frac{\pi}{2 N_c}$ and radii $r = R, 2R$.
+Then we train a deep CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict a class label for the rendered images based on known class labels for the 3D models using Stochastic Gradient Descent (SGD).
+Next, we pass each of the $N_c$ views of each object through the finetuned CNN and max-pool the output of the fc7 layer.
+We finally use Principal Component Analysis (PCA) to reduce the max-pooled output to from 400 dimensions to 100 dimensions.
+This yields a representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object, and thus our final feature map is $\phi_{g}(\mY) = \psi(\mO)$.
+In our implementation, we trained the multi-view CNN on rendered images of 171 classes of 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, which had a test accuracy of 76\%.
+
+%\TODO{Expand above paragraph, include more details on method as well as the results of training}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
+\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.
+We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture.
+Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
+\figlabel{global-feature-model}
+\vspace*{-15pt}
+\end{figure}
+
+\subsection{Optimizing Feature Weights}
+One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
+%Past work has optimized these weights using a squared error loss on the probability of success predicted by the CCBP and a true probability of success from brute force evaluation~\cite{montesano2012active}.
+%However, this criterion may be inappropriate for predicting probabilities, as the predictions must be bounded between 0 and 1.
+We select the weights that minimize the cross entropy loss~\cite{}:
 
 \begin{align*}
-	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
-	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
+	w_1^*, ..., w_{N_f}^* = \myargmin{w_1, ..., w_{N_f} \geq 0} \frac{1}{M} \sum \limits_{i=1}^M &\mu_i \log \left( \frac{\alpha_i}{\alpha_i + \beta_i} \right) + \\  &(1 - \mu_i) \log \left( \frac{\beta_i}{\alpha_i + \beta_i} \right)
 \end{align*}
-
-\subsection{Continuous Correlated Beta Processes}
-
-Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
-Such correlations may exist when the Bernoulli random variables depend on common latent factors.
-For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.
-
-A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
-The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
-Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
-Then the CCBP posterior update for $\theta_k$ is~\cite{}:
-
-\vspace{-2ex}
-\begin{align*}
-	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
-	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
-	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
-\end{align*}
-
-\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.
+\noindent where $\alpha_i$ and $\beta_i$ are the posterior shape parameters given by Equations~\ref{eq:alpha-prior} and~\ref{eq:beta-prior} and $\mu_i$ is the probability of force closure evaluated by exhaustive Monte-Carlo integration for a set of $M$ grasps.
+We optimize this objective using SGD with the weights initialized to $w_i = 100$ for all $i$.
+\TODO{For experiments so far we actually use a grid search and not SGD but we are interested in using this.}

### 2015-09-03 ICRA2016/bandits_docs/includes/conclusion.tex
First full version of the paper with committed adobe illustrator figures

\section{Discussion and Future Work}
\seclabel{conclusion}
We introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 20,000 3D object models and a network of similarity between object models and parallel-jaw grasps on each model.
We extended the Multi-Armed Bandit model of Laskey et al.~\cite{laskey2015bandits} to leverage similiarty between grasps based on gripper pose, local surface geometry encoded as heightmaps, and global shape similarity encoded using a state-of-the-art method for shape retrieval based on multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}.
Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to select a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature optimization with deep neural networks~\cite{levine2015end} to optimize feature representations of both the local and global surface geometry based on the outcome of grasp evaluations in the bandit algorithms.
We will also study extensions of the shape similarity neural network to predict object class from simulated depth images of objects on a table, which could be useful for transferring learned data from Dex-Net to objects in the physical world.

Another shortcoming is our current use of wrench space metrics, which have been criticized recently for not correlating with human labels~\cite{kappler2015leveraging} or physical trials~\cite{balasubramanian2012physical}.
However, both forms of labels may be difficult to acquire for the entire dataset because of the human and time cost involved.
Future work will research using Multi-Armed Bandits (MABs) to actively acquire grasp evaluations uncertain objects.
To do so, we will study using functional map networks to establish consistent maps between prototypical object parts that indicate grasp affordance, such as handles
We will also build on recent developments in caging to label key the dataset with caging hand configurations either analytically, using simulation, or using a learned model to predict caging configurations.
We will also work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes, integrating Dex-Net with physical robots, and learning statistical models of grasp success using deep learning and MAB.

### 2015-09-03 ICRA2016/bandits_docs/includes/dataset.tex
First full version of the paper with committed adobe illustrator figures

\section{Dexterity Network}
\seclabel{dexnet}
\TODO{Due to space, it might make sense to discuss in experiments as appears to be common practice when the dataset is not going to be released to the public}
It remains to describe the details of creating the Dexterity Network (Dex-Net), our prior dataset of objects and grasps with similarity, for use in the Multi-Armed Bandit models of Algorithm~\ref{alg:full}.
Dex-Net 1.0 consists of approximately 20,162 3D mesh models \TODO{Update with correct count} collected from the datasets described in \figref{datasets}.
Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
These models were chosen to reflect physical objects commonly used for benchmarking in grasping research for potential future physical experiments using Dex-Net.
The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a relatively new benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
While the geometry of synthetic models does not necessarily reflect a physical object, using these models allows us to examine the effects of scale at tens of thousands of 3D models, which has not been previously attempted in grasp synthesis research.

In order to use the models for grasp selection, we first preprocess each model.
Each object in Dex-Net is originally specified as a 3D mesh $\mS = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
First, we remove unreferenced vertices and illegal triangles (e.g. same vertex is referenced twice in one triangle).
Next, we normalize the orientation of the model by performing Principal Component Analysis (PCA) on the raw vertices of the mesh and then rotating the object such that its first principal component aligns with the $z$-axis and its second aligns with the $y$-axis.
We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies withing the maximum opening of the gripper.
Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{}, an open-source C++ tool.

Once each 3D model is preprocessed, we compute the shape feature vector described in \secref{cnn} for each object.
Each feature vector is then put into a KD-Tree nearest neighbor query structure for accelerated lookups of shape nearest neighbors.
This structure consistutes our shape similiarity network, in which each object $\mO$  is connected to its $n$ nearest neighbors $\mO_1, ..., \mO_n$ by an edge of weight $\| \psi(\mO) - \psi(\mO_i) \|_2^2$.
We generate a set of grasps for each object in the network using the method of \secref{candidates} and evaluate the probability of force closure for each grasp using brute-force Monte Carlo integration as a benchmark~\cite{kehoe2012toward}.
As the number of models is quite large, we distribute the grasp labelling for each object across virtual machines in Google Compute Engine and aggregate the results at the end.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.1]{figures/dataset_table.jpg}
\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present). \TODO{Update ModelNet number - we actually only use select categories}}
\figlabel{datasets}
\vspace*{-15pt}
\end{figure}

### 2015-09-03 ICRA2016/bandits_docs/includes/experiments.tex
First full version of the paper with committed adobe illustrator figures

@@
 
-\subsection{Dataset}
-To study the convergence rate with orders of magnitude of previous grasp data we create a dataset of tens of thousands of 3D CAD models.
-We aggregated data from the laser scanned datasets Amazon Picking Challenge~\cite{}, BigBIRD~\cite{}, KIT~\cite{}, and YCB~\cite{}, as well as the synthetic datasets 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large-scale retrieval dataset~\cite{}.
-To preprocess the data for grasping we set the frame of reference for each object to the the principal components of the vertices of each mesh, set the object center-of-mass as the center of a bounding box around the reoriented vertices, removed unreferenced and invalid vertices, rescaled each synthetic mesh such that its smallest principal direction fit within a PR2 gripper, and converted the mesh to a signed distance field.
-We reserved the YCB dataset as a test set, and used subsets of the remaining data to train hyperparameters and to seed the CCBPs for convergence experiments on the test dataset.
+\TODO{All experiments here are preliminary. Add new results from non-symmetric objects and more data}
+\TODO{Include experiments on sensitivity to uncertainty} \\
+\TODO{Images of selected grasps} \\
+
+We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity to parameters of the algorithm.
+To test the generalization of our feature maps, we reserved objects from YCB and ModelNet as a test set, and used nested subsets of the remaining data as training data for optimizing the hyperparameters and for tuning the MAB convergence rate.
+We assumed a PR2 gripper for our grasps, which has a maximum width of approximately $10cm$.
+We assumed isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+The weights of our similarity kernel were selected using a grid search over possible values on a held-out validation set.
 
@@
 We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
-Each model is stored in .OBJ format and the average size is roughly 0.5MB.
 We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
 Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
-When an instance is launched, we mount DexNet via a persistent disk containing a particular set of objects and grasps.
+When an instance is launched, we mounted Dex-Net via a persistent disk containing a particular set of objects and grasps.
 Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
@@
 
-Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
 ~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
-The plot compares Thompson sampling, a MAB algorithm, without correlations to Thompson sampling using the CCBP model of local grasp similiarity (no prior data).
+The plot compares Algorithm~\ref{alg:full} with no prior data to uncorrelated Thompson sampling and uniform allocation, two methods used by Laskey et al.~\cite{laskey2015bandits}.
 We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
-Iniitial reuslts suggest that performance on the flower pot is poorer because it has very few similar grasps according to our similarity metric.
+Iniitial reuslts suggest that performance on the flower pot is poorer because few grasps are similar according to our feature representation.
+
+%Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
 
@@
         \includegraphics[scale=0.08]{figures/box_avg_reward_w_model.jpg}
-        \caption{Normalized $P_F$ on a cereal box with 250 candidate grasps.}
+        \caption{Normalized $P_F$ on a cereal box with 250 candidate parallel-jaw grasps.}
     \end{subfigure}
@@
         \includegraphics[scale=0.08]{figures/flowerpot_avg_reward_w_model.jpg}
-        \caption{Normalized $P_F$ on a flower pot with 250 candidate grasps.}
+        \caption{Normalized $P_F$ on a flower pot with 250 candidate parallel-jaw  grasps.}
     \end{subfigure}
-\caption{Comparison of the normalized $P_F$ of the sampled grasp versus iteration of the MAB algorithm for correlated Thompson sampling, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials.
+\caption{Comparison of the normalized $P_F$ of the sampled parallel-jaw grasp versus iteration of the MAB algorithm for correlated Thompson sampling, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials.
 (a) On the cereal box, correlated Thompson sampling converges to within 90\% of the highest quality grasp approximately 4$\times$ faster than uncorrelated.
@@
 
-To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from DexNet: 0, 15, 150, and 1500 objects.
-\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle using prior grasp data from the five nearest neighbor objects in DexNet averaged over 50 trials.
-Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
-We see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly largers subsets of prior data used.
-This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.
-Future work will examine these effects on a larger subset of objects and will use more than five nearest neighbors from DexNet to compute priors, which may lead to even larger gains for larger subsets of prior data.
+To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from Dex-Net: 0, 15, 150, and 1500 objects.
+\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle and detergent averaged over 50 trials.
+For each run of our algorithm, we used prior grasp from the five closest objects in Dex-Net in the multi-view CNN-based shape similiarity vector space.
+The objects from Dex-Net were labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
+For the bottle, we see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly larger subsets of prior data used, and is approximately $10 \times$ faster when using 1500 prior objects.
+For the detergent the gains are more modest, with the largest dataset accelerating convergence to within 90\% of the optimal grasp in the set by approximately $1.5 \times$.
+As illustrated in \figref{bottle-nn}, the nearest neighbor objects become increasingly similar to the object to label with increasing sizes of datasets from Dex-Net.
+This suggests that more prior data may also lead to more similar objects to rarer categories such as the detergent bottle, which may accelerate convergence 
+\TODO{Remove}
+Future work will examine these effects on a larger subset of objects and will use assitional nearest neighbors from Dex-Net to compute priors.
 
@@
 \centering
-\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
-\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object.
-Prior grasps were taken from increasingly larger subsets of DexNet: 15, 150, and 1500 objects.
-We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used.
-}
+\begin{subfigure}[b]{0.5\textwidth}
+        \centering
+        \includegraphics[scale=0.08]{figures/bottle_avg_reward_w_model2.jpg}
+        \caption{Normalized $P_F$ on a bottle with 250 candidate parallel-jaw grasps.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+        \includegraphics[scale=0.08]{figures/detergent_avg_reward_w_model.jpg}
+        \caption{Normalized $P_F$ on a detergent bottle with 250 candidate parallel-jaw grasps.}
+    \end{subfigure}
+%\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
+\caption{Comparison of the normalized $P_F$ of the sampled parallel-jaw grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from Dex-Net, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20.
+Prior grasps were taken from increasingly larger subsets of Dex-Net: 15, 150, and 1500 objects.
+For the bottle, convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used.
+The detergent converges slightly faster with more prior data, however the speedup is approximately $1.5\times$ and does not appear to improve with additional data from Dex-Net.}
 \figlabel{global-mab}
@@
 
-\TODO{Remove below section}
-We are currently working on an experiment to quantify the gains in convergence time across orders of magnitudes of prior data (10, 100, 1000, 10000) from DexNet using Google Compute Engine.
-Our initial version will be run on a relatively small subset of test objects, and in the coming weeks we will average the performance over a larger set of test objects.
-We are particularly interested in seeing if there is a point of diminshing returns from adding more data when using datasets on the order of 10,000 - 100,000 objects.
-We are also interested in whether or not adding perturbations to the data such as object reflections and shape perturbations will also increase performance, as has been observed for training Deep CNNs in vision~\cite{krizhevsky2012imagenet}.
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.075]{figures/bottle_nearest_neighbors.jpg}
+\caption{Illustration of the five nearest neighbor objects from Dex-Net using the multi-view CNN-based shape embedding and Euclidean distance for increasing sizes of randomly selected subsets of data from Dex-Net.
+We see that while the neighbors for a small dataset are not relevant, the neighbors become increasingly similar to the query bottle as more data is used.}
+\figlabel{bottle-nn}
+\vspace*{-15pt}
+\end{figure}
 
 \section{Sensitivity to Uncertainty}
+
+\TODO{Write section}

### 2015-09-03 ICRA2016/bandits_docs/includes/introduction.tex
First full version of the paper with committed adobe illustrator figures

--- 2015-07-23 ICRA2016/bandits_docs/includes/introduction.tex
@@
 \section{Introduction}
-Robots in warehousing and small- to medium-scale manufacturing must be able to efficiently handle to new products and parts.
-For example, a robot processing orders in a distribution warehouse must be able to quickly adapt to new consumer products to place them in shipping containers.
-Analytic methods for grasp planning requires precise knowledge of contact locations and surface normals,
-but a robot in the field may not measure these quantities exactly due to sensor imprecision and missing data resulting from occlusions or highly reflective surfaces.
-This motivates a fast and adaptive approach to grasp planning that is robust to uncertainty about the state of the robot and environment.
+\seclabel{introduction}
 
-\TODO{I think the parts about force closure should be greatly compressed here}
-Force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}, is a commonly-used binary metric of grasp quality.
-Past work has measured the probability of force closure given uncertainty in robot state~\cite{brook2011collaborative, hsiao2011bayesian}, object pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose}, and object shape~\cite{brook2011collaborative, hsiao2011bayesian, kehoe2012estimating, mahler2015gp}.
-Computing the probability of force closure requires integrating over the uncertain quantities, which many works have computed using computationally expensive Monte-Carlo integration over sampled perturbations~\cite{christopoulos2007handling, hsiao2011bayesian, kehoe2012toward, kim2012physically, weisz2012pose} parallelized in the cloud~\cite{kehoe2012toward} or using iterative pruning of grasps with low quality~\cite{kehoe2012estimating, kehoe2015survey}.
+Consider a robot fulfilling orders in a warehouse.
+The robot must quickly plan grasps for consumer products to fullfill orders.
+Furthermore, the robot may not precisely know the state of the environment, such as the pose or frictional properties of object, due to sensor imprecision and missing data (e.g.
+occlusions in point clouds).
+This poses a challenge for many existing grasp planning methods that are based on precise knowledge of contact locations and surface normals~\cite{ciocarlie2009, ferrari1992} due to the distribution on possible environment configurations.
 
-Recently, Laskey et al.~\cite{laskey2015bandits} showed that it was possible to jointly compute the integral and identify the best grasp using Multi-Armed Bandit (MAB) algorithms such as Thompson Sampling, leading to $5-10\times$ speedups over previous work on a set of parallel-jaw grasps on 2D objects.
-However, the MAB algorithms still needed roughly 5,000 samples to identify the best grasp from a pool of 1,000 candidates for each object, which could be time-consuming for 3D objects.
-Also, the number of samples is prohibitively high to use the algorithms based on physical success from robot trials instead of in simulation.
-One possible reason for the magnitude of samples is that this work treated each grasp and object independently, when in reality grasps and objects with similar features, such as those illustrated in\figref{teaser}, should convey information about the probability of success of one another.
+In vision and speech, advances in Big Data and distributed computing, combined with datasets of milliions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher}, have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
+This raises the question: will machine learning of grasps for vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
 
-\TODO{Need to get correct terminology. Technically not contextual or combinatorial. Ask Kevin.}
-Correlated Multi-Armed Bandits (CMABs) are an extension of standard MABs in which options have correlated rewards.
-On each observation, standard MAB algorithms update only the predictive model for the option chosen, while CMAB algorithms typically update a global predictive model of the reward for each option.
-This can lead to faster convergence if the algorithm has some knowledge of the correlation structure between options.~\cite{}.
-A primary challenge is thus estimating a model of the global correlation structure of the arms, which may require a large amount of data.
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
+\caption{Sample of 3D mesh models from the Dex-Net dataset.
+The dataset currently includes over 10,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}.
+}
+\figlabel{dexnet-teaser}
+\vspace*{-15pt}
+\end{figure}
 
-In this work, we leverage CMABs to accelerate identification of robust grasps using a correlation structure learned from large amounts of data.
-We model the probability of force closure for grasps on 3D shapes as a Correlated Continuous Beta Processes (CCBPs)~\cite{}, a model of 0-1 correlated options with computationally inexpensive posterior updates compared to alternative models such as Gaussian Processes~\cite{}.
-Each option corresponds to a single grasp center and axis.
-Evaluating an option corresponds to sampling from Gaussian uncertainty in object pose, gripper pose, and contact friction, and measuring force closure for the grasp on the sampled state.
-We learn the correlation structure between grasps \TODO{Write up}
+We introduce Dex-Net 1.0, a dataset of 3D models and grasps with similarity metrics, and a system for actively acquiring statistical models of grasp quality across the network.
+The Dex-Net dataset contains representative 3D models of objects that could be encountered in warehousing or the home.
+Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
+The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to scale the number of models.
+~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
+We measure object similarity based the distance between feature vectors generated from multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}, a state-of-the are method in shape retrieval
+We measure similarity between grasps by the pose of the gripper and local surface ``heightmaps" extracted at location of contact with an object~\cite{herzog2012template, kappler2015leveraging}.
+Our system uses Google Cloud Platform to distribute grasp quality evaluations across hundreds of virtual machines and to store millions of grasps across the objects in Dex-Net.
 
-Our primary contribution is \TODO{Write up}.
-Our experiments show that \TODO{Write up}.
+In this work, we use Dex-Net to study the convergence rate of Multi-Armed Bandit (MAB) algorithms for finding a grasp with high probability of force closure under object pose, gripper pose, and friction coefficient uncertainty from a set of 250 candidate grasps on objects from Dex-Net.
+To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for similar grasps on similar 3D objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
+CCBPs predict a belief distribution for the quality of each grasp based similarity to data in Dex-Net that can be efficiently updated after observing the quality of a grasp for a sampled object pose, gripper pose, and friction coefficient.
+Our results suggest that CCBPs bootstrapped with data from Dex-Net can accelerate grasp planning by up to $10\times$.

### 2015-09-03 ICRA2016/bandits_docs/includes/problem_statement.tex
First full version of the paper with committed adobe illustrator figures

@@
 
-We consider the problem of finding the parallel-jaw grasp with the maximum probability of a binary success metricsuch as force closure on a previously unknown object under uncertainty in object pose, gripper pose, and friction coefficient.
+Given a previously unknown object, we consider the problem of finding the parallel-jaw grasp with the maximum expected grasp quality according to a binary grasp quality metric such as force closure under uncertainty in object pose, gripper pose, and friction coefficient.
 
@@
 Our grasping model is illustrated in~\figref{grasp-model}.
-Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \mS^2$.
-We assume that the gripper will be opened to its maximal width before closing on the object.
-Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{newcombe2011kinectfusion, mahler2015gp}, which is zero on the object surface, positive outside the object, and zero inside the object.
+Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
+We assume that the jaws are opened to their maximal width $w \in\bR$ before closing on the object.
+Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and zero inside the object.
 We assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
-Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3, \bv \in \mS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where $\mF$ is the space of all SDFs.
-Our joint grasp and object space, or Grasp Moduli Space~\cite{pokorny2013grasp}, is $\mM = \mG \times \mH$.
+Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where $\mF$ is the space of all SDFs.
+Our joint space of grasps and objects, or Grasp Moduli Space~\cite{pokorny2013grasp}, is $\mM = \mG \times \mH$.
 
@@
 \subsection{Contact Model}
+\seclabel{contact}
 Our contact model is illustrated in the right panel of \figref{grasp-model}.
-Given object shape and samples of object pose, and gripper pose, we let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
-Furthermore, let $\bn_i \in \mS^2$ denote the surface normal at contact $\bc_i$.
-To compute the forces that each contact can apply to the object, we discretize the friction cone at contact $i$ into a discrete set of $N_c$ facets with vertices $\bbf_{i,j}$ for $j = 1, ..., N_c$~\cite{pokorny2013classical} for a given friction coefficient $\gamma$.
+Given a grasp $\bg$ with width $w$ on an object $\mO$ and samples of object pose, gripper pose, and friction, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
+We can compute the contacts using
+\begin{align*}
+	\bc_1 &= \minimum{t \geq 0} t \text{ such that } | f\left(\bx + (t - w / 2) \bv\right) | < \epsilon \\
+	\bc_2 &= \minimum{t \geq 0} t \text{ such that } | f\left(\bx - (t - w / 2) \bv\right) | < \epsilon
+\end{align*}
+\noindent where $\epsilon > 0$ is a user-specified surface resolution~\cite{mahler2015gp}.
+
+Given contact points, let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tanget vectors $\bt_{i,1}, \bt_{i,2} \in \mS^2$.
+To compute the forces that each contact can apply to the object for a given friction coefficient $\gamma$, we discretize the friction cone at contact $i$ into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bbf_{i,j} = \bn_i + \gamma \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \gamma \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \text{ for } j = 1, ..., l \right\}$~\cite{pokorny2013classical}.
 Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
-Thus the set of all wrenches that can be applied by a grasp $\bg$ is $\mW = \{ \bw_{i,j} = [\bbf_{i,j}, \tau_{i,j}]^T \big| i = 1, 2 \text{ and } j = 1, ..., N_c\}$.
+To enable force closure with two contacts in 3D we assume a soft contact model, under which each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = [\mathbf{0}, \bn_i]^T$~\cite{prattichizzo2008grasping}.
+Thus the set of all wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = [\bbf_{i,j}, \tau_{i,j}]^T \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
 
 \subsection{Quality Metric}
+\seclabel{quality}
 In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
-We acknowledge that force closure assumes the abliity to actuate the gripper to apply arbitrary forces in the contact friction cone~\cite{} and that some evidence suggests that deterministic force closure is not a strong predictor of physical grasp success~\cite{balasubramanian2012physical}.
-However, we use the probability of force closure because of it has shown some promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate as compared to human labels or physical executions, allowing us to better study the effects of large amounts of data on convergence.
+We acknowledge that force closure assumes the abliity to actuate the gripper to apply arbitrary forces in the contact friction cone~\cite{}, and that some evidence suggests that deterministic force closure is not always a strong predictor of physical grasp success~\cite{balasubramanian2012physical}.
+However, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate when compared to human labels or physical executions, allowing us to better study the effects of large amounts of data.
 
-Let $F \in \{0, 1\}$ denote the occurence of force clsoure.
-To compute force closure for a grasp $\bg$ on object $\mO$ given deterministic samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
-Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$.
+Let $F \in \{0, 1\}$ denote the occurence of force closure.
+To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
+Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.
 A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
@@
 \subsection{Objective}
-The probability of force closure for a grasp $\bg$ is
+The probability of force closure for a grasp $\bg$ on object $\mO$ is
 %\vspace{-2ex}
 \begin{align*}
-	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \rho, \zeta \right).
+	P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right).
 \end{align*}
 \noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
-To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$:
+To perform this as quickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$~\cite{laskey2015bandits}:
 
@@
 
-As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ where $\Gamma$ is set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
+As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ where $\Gamma$ is set by sampling grasp centers from a Gaussian with mean at the object center~\cite{laskey2015bandits} or using heuristics specific to parallel-jaw grippers such as antipodality~\cite{mahler2015gp}.
 However, even with a discrete set of candidates, fully evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
-Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
-In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.
+Thus, past research has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit (MAB) algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
+In this work, we extend the MAB model of~\cite{laskey2015bandits} to model similarities between grasps and prior objects in Dex-Net to further accelerate convergence.
 
-\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent under uncertainty}
+%\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent under uncertainty}

### 2015-09-03 ICRA2016/bandits_docs/includes/related_work.tex
First full version of the paper with committed adobe illustrator figures

--- 2015-07-23 ICRA2016/bandits_docs/includes/related_work.tex
@@
 \section{Related Work}
+\seclabel{related}
 
-Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric, such as the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
-These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{}.
-However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output} and the abliity of a gripper to actuate any contact force in the friction cone, which is not true of many real-world grippers~\cite{}.
-Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubmaranian, weisz}.
-This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis~\cite{}.
+For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
+Research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, miller2004graspit}, object WS~\cite{liu2015fast, pollard1994parallel}, or task WS~\cite{kruger2011partial, li1988task}.
+WS metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{leon2010opengrasp}.
+However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005} and for not taking into account the dynamics of the the grasp~\cite{prattichizzo2008grasping}.
+%This has motivated work on grasp transfer from a knowledge database to new objects, robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and synthesis from statistical models of grasping learned from physical data or human labels.
 
-Many works have approached grasp synthesis for unknown or familiar objects by transferring grasps from a benchmark set of exemplar objects in a large database.
-%Ciocarlie et al.~\cite{ciocarlie2009} found that human hand postures lie on a low-dimensional subspace, called eigen-grasps, and exploited this structure to speed up grasp optimization to synthesize grasps at a large scale in GraspIt!.
-Li and Pollard~\cite{} generated grasps by matching object shapes to human hand postured in a database.
-Hillebrand and Roa~\cite{} transfer grasps from objects of the same category using pose alignment and geometric warping betwen corresponding points on a shape surface.
-Goldfelder et al.~\cite{} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
-The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{partial}.
-Detry et al.~\cite{91inbohg} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{}.
+The need to recompute WS metrics to select grasps for every new object motivated research on grasp synthesis by transferring grasps from a database of exemplar objects.
+Li and Pollard~\cite{li2005shape} generated grasps by matching object shapes to human hand postured in a database.
+Goldfelder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
+The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{goldfeder2009data, goldfeder2011data}.
+Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
+Recent research has also studied grasp transfer from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local rigid alignment and contact interpolation~\cite{hillenbrand2012transferring, stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2014grasp, pokorny2013grasp}.
 
-Work on evaluating grasp quality metrics under uncertainty, such as the probability of force closure, has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
-Recent work has also studied the effects of uncertainty in object pose and gripper positioning~\cite{brook2011collaborative, hsiao2011bayesian}.
-Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
-Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} independently found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics.
-Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{chris}, part tolerancing in manufacturing~\cite{kehoe}, or missing and noisy data from depth sensors such as the Kinect~\cite{mahler, laskey}.
-Many have also studied caging gripper configurations, which may be a waypoint to form closure grasps and are robust to perturbations in object pose and shape~\cite{}.
+Another line of research focused on making analytic grasp metrics robust to imprecision in perception and control~\cite{goldberg1990bayesian, stulp2011learning, zheng2005}.
+Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} developed a Bayesian framework to evaluate both the expected epsilon quality and the probability of physical success on a PR2 given uncertainty in object identity, object pose, and gripper positioning on deterministic mesh and point cloud models.
+Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
+Kim et al.~\cite{kim2012physically} planned grasps using the expected epsilon quality metric~\cite{ferrari1992} under dynamics and uncertainty in pose, and found that the robust metric has a higher correlation with physical grasp success.
+Recent research has also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{christopoulos2007handling}, part tolerancing in manufacturing~\cite{kehoe2012estimating, kehoe2012toward, panahi2015orienting}, or missing and noisy data from depth sensors such as the Kinect modeled with Gaussian process implicit surfaces~\cite{dragiev2013uncertainty, mahler2015gp, laskey2015bandits}.
+%Many have also studied caging gripper configurations~\cite{rimon1996caging}, which are a waypoint to form closure grasps for two fingers~\cite{vahedi2008caging, rodriguez2012caging} and may be robust to perturbations in object pose and shape~\cite{diankov2008manipulation, Wan2012_ICRA}.
 
-Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg}.
-Saxena et al.~\cite{bothsaxenaworks} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
-Several other works have examined predicting grasp points using depth gradient features~\cite{rao}, global shape context descriptors~\cite{}, and 3D edges~\cite{}. 
-Lenz et al~\cite{lenz} used deep learning to detect grasp bounding boxes in color and depth images.
-Herzog et al.~\cite{} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
-Kappler et al.~\cite{} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic objects.
-Recently, several works have studied forming a database of grasps on synthetic objects from simulation outcomes~\cite{detry} or physical execution~\cite{tellex}.
-In comparison, our work uses data-driven correlations between grasps based on local and global features of an object surface to quickly and adaptively acquire samples for evaluating and ranking grasps by their likelihood of success.
+Recent research has also studied synthesizing grasps by ranking grasps according statistical models learned from human annotations or physical execution~\cite{bohg2014data}.
+Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
+Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images, which was extended to real time by Redmon and Angelova~\cite{redmon2014real}.
+Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
+Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{detry2013learning}.
+Kappler et al.~\cite{kappler2015leveraging} trained a deep neural network to predict grasp success for a Barett hand measured by human annotations and the results of simulations on a database of synthetic pointclouds of objects.
+Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
+%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
+In comparison, we learn a model to predict a Bayesian distribution on the probability of force closure for a grasp on an object based on similarity to a set of prior grasps and objects in a database, and use our model to actively decide the next grasp to evaluate using Multi-Armed Bandits.
 
-Active learning for grasp planning is an active area of research.
-Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{kahn, vincsze}, but without use of an explicit grasp quality metric to guide the search.
-Recently, Laskey et al.~\cite{} showed that MAB algorithms can be used to accelerate the identification of a grasp with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
-Tellex et al.~\cite{} proposed an initiative to adaptively collect a dataset of grasps and point clouds for one million objects using MAB and reinforcemen learning.
-MAB algorithms select the next grasp to sample by trading off gaining information about grasps with few samples and exploiting the success of grasps known to work well.
-In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{guy}.
-
-One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{}.
-In reality, grasp correlations may occure from grasps with similar poses~\cite{}, objects with similar global structure~\cite{}, or on surfaces with similar local geometry~\cite{}.
-Correlated Multi-Armed Bandit (CMAB) models, also referred to as Bayesian Optimization models~\cite{}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{}, next-best view prediction in object modeling~\cite{}, envrionmental monitoring in robotics~\cite{}.
-Perhaps the most common model of correlations in a CMAB is a linear model~\cite{}, however this depends on the selection of features are linearly related to a success criteria.
-Another common model of correlations is a Gaussian Process (GP)~\cite{}, which can model nonlinear relationships between options and rewards but are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far).
-As a result, several fast approximate version of GP bandit algorithms exist, such as local GPs~\cite{} and hierarchical GPs~\cite{}.
-Recently, Goetschalckx et al.~\cite{} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
-CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{}.
-In this work we utilize CCBPs to model correaltions between grasps because of their ability to scale to thousands of grasp observations with reasonable runtime.
+Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples.
+Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
+Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discrading grasps known to have poor quality.
+Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
+Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
+Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
+Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
+Similarly, Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
+Recently, Laskey et al.~\cite{laskey2015bandits} showed that Multi-Armed Bandit (MAB) algorithms can be used to accelerate the identification of grasps with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
+MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
+In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net with CCBPs to further reduce the number of samples needed to converge to a grasp with high quality.

### 2015-09-03 ICRA2016/bandits_docs/paper.tex
First full version of the paper with committed adobe illustrator figures

@@
 \begin{document}
-\title{\LARGE \bf DexNet 1.0: Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
-		\versionline{2}}
-\author{Jeffrey Mahler, Brian Hou, Mel Roderick, Michael Laskey, Kai Kohlhoff, \\ Torsten Kroeger, Florian Pokorny, James Kuffner, Ken Goldberg}
-%\institute{Deptartment of Electrial Engineering and Computer Sciences, University of California, Berkeley, USA
-%\{jmahler, zmccarthy, sachinpatil, pabbeel, goldberg\}@berkeley.edu} 
+\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning
+%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
+		\versionline{4}}
+\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Mel Roderick$^1$, Michael Laskey$^1$, Kai Kohlhoff$^3$, \\ Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
+\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
+\thanks{$^{1-2}$ University of California, Berkeley, USA}%
+\thanks{$^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
+}
 \maketitle
 
-\TODO{Possibly will include Matthieu Aubry and Pieter Abbeel as coauthors as well}
+\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
+\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
 
@@
 \input{includes/algorithm}
-%\input{includes/analysis}
+\input{includes/dataset}
 \input{includes/experiments}
-%\input{includes/conclusion}
+\input{includes/conclusion}
 

### 2015-09-10 ICRA2016/bandits_docs/includes/abstract.tex
Modified entire draft. In a limbo state. Going back through feedback now.

--- 2015-08-26 ICRA2016/bandits_docs/includes/abstract.tex
@@
 \begin{abstract}
-\TODO{Fill in after rest of paper done.}
+%\TODO{Adapted from flyer, probably needs to be toned down}
+Recent advances in distributed computing and machine learning combined with very large datasets of images and human speech have produced a series of results that surpass decades of research in analytic methods and, in some cases, human ability.
+%For example, deep neural networks can now learn to play video games, recognize faces, and translate between languages.
+This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
+%We show that using using a large dataset of 3D models can speed up significantly the computation of valid grasps. 
+%We develop a Multi-Armed Bandit model with correlated rewards to accelerate robust grasp planning by learning from a large dataset of prior grasps and 3D object models, and implement our algorithm on Google Compute Engine.
+We show that learning from a large dataset of prior grasps and 3D object models can reduce the number of samples needed for robust grasp planning using our novel Multi-Armed Bandit algorithm with correlated rewards.
+To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 unique 3D object models selected to reflect objects encountered in warehousing and the home such as tools, tableware, and toys.
+Each object is labelled with up to 250 parallel-jaw grasps and the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
+We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between 3D objects and we apply it to indexing similar objects for grasp planning at scale.
+%To the best of our knowledge, this dataset is the largest to-date used for grasping research.
+We implement our algorithm and store our database using the Google Cloud Platform.
+Experiments on a set of N test objects suggest that the time taken to plan a robust grasp is approximately $2\times$ faster on average and up to $10\times$ faster on select objects when using Dex-Net as a prior...
+\TODO{Update numbers}
+Experiments on sensitivity indicate that....\TODO{Results of this}
+Code, data, and additional information can be found at: \TODO{Url}
 \end{abstract}

### 2015-09-10 ICRA2016/bandits_docs/includes/algorithm.tex
Modified entire draft. In a limbo state. Going back through feedback now.

--- 2015-08-26 ICRA2016/bandits_docs/includes/algorithm.tex
@@
-\section{Algorithm}
+\section{Correlated Multi-Armed Bandit Algorithm}
+\seclabel{algorithm}
+Our algorithm, detailed in Algorithm~\ref{alg:full}, plans a sequence of grasps with high $P_F$ for a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards and priors from the grasp and 3D object data in Dex-Net.
+We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
+Next, we run MAB by selecting the next grasp to sample using Thompson sampling~\cite{laskey2015bandits}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the probability of force closure for each grasp.
+Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimated of the grasp with the heighest estimated $P_F$.
 
-\TODO{Brief section on the high-level algorithm using the model: grasp sampling, evaluation of grasps, thompson sampling}
+\begin{algorithm}
+{\small
+    \SetAlgoLined
+    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Samples $N_s$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Object Feature Map $\psi$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
+    \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}
+
+    \tcp{Generate candidate grasps and priors}
+	$\Gamma$ = AntipodalGraspSample($\mO, N_g$) \;
+	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
+	\For{$\bg_k \in \Gamma$}{
+		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
+		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD, N_n, \psi$)\; 
+		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
+	}
+
+	\tcp{Run MAB to Evaluate Grasps}
+	\For{$t = 1, .., T$}{
+		$j = $ ThompsonSample($\mA_{t-1}, \mB_{t-1}$)\;
+		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
+		$F_{j} = $ EvaluateForceClosure($\bg_j, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
+		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
+		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, F_j, \Gamma$)\; 
+		$\bg_{t}^* = $MaxLowerConfidence($\mA_{t}, \mB_{t}, p$)\;
+	}
+	return $\bg_T^*$\;
+    \caption{Robust Grasp Planning With Multi-Armed Bandits Using Dex-Net 1.0}
+    \label{alg:full}
+}
+\end{algorithm}
+
+\subsection{Predicting Grasp Quality Using Prior Data}
+\seclabel{ccbps}
+We use Continuous Correlated Beta Processes (CCBPs) to model correlations between the $P_F$ between grasps on different objects to utilize prior grasp and object data from Dex-Net 1.0.
+CCBPS were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process.
+Such correlations may exist when the Bernoulli random variables depend on common latent factors.
+For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar.
+
+Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
+We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as an occurence of force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ on object $\mO$ from samples of object pose, gripper pose, and friction, as described in \secref{quality}.
+Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
+Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
+In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+
+\vspace{-2ex}
+\begin{align*}
+	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_k^{\alpha-1} (1 - \theta_k)^{\beta-1}
+\end{align*}
+
+A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
+The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
+We measure similarity as a function of the euclidean distance between the output of a set of $N_f$ feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$, where $d_m$ is the dimension of the feature space.
+Details on our feature maps are given in \secref{features} below.
+Given the feature maps, we use the squared exponential kernel 
+\begin{align*}
+	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
+\end{align*}
+\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
+
+We form a belief distribution for each candidate grasp in $\Gamma$ based on its its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
+%\vspace{-2ex}
+\begin{align}
+	%p \left(\theta_{j} | \mD \right) &= \betadist\left( \alpha_{j,0}, \beta_{j,0} \right) \notag \\
+	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g} k(\mY_{j}, \mY_{i, k}) S_{i,k} \label{eq:alpha-prior} \\
+	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g}  k(\mY_{j}, \mY_{i,k}) (N_s - S_{i,k}) \label{eq:beta-prior}
+\end{align}
+\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled for evaluate $P_F$.
+In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree descirbed in \secref{object-similarity}.
+Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:
+
+\vspace{-2ex}
+\begin{align}
+	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
+	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}
+\end{align}
+
+\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.
+
+\subsection{Feature Representation}
+\seclabel{features}
+\TODO{Move elsewhere / condense? Its a lot of information coming out of nowhere}
+We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.
+
+\subsubsection{Grasp Parameters}
+\seclabel{param-features}
+Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx$ is the grasp center, $\bv$ is the grasp approach, and $\rho_i$ is the $i$-th moment arms.
+The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
+However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).
+
+\subsubsection{Local Surface Heightmaps}
+\seclabel{heightmaps}
+We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging} to capture local surface geometry.
+Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
+Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
+Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
+To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
+Then we assign the heightmap value
+\begin{align*}
+	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + s_i \bv \right) = 0
+\end{align*}
+\noindent where $s_1 = -1$, $s_2 = 1$, and $f$ is the SDF of object $\mO$. 
+We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
+\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
+Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients to form local surface normal maps $\bd_{i,x}$ and $\bd_{i,y}$.
+Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
+\caption{Three local surface heightmaps extracted on a teapot.
+Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
+We extract the gradients of these heightmaps as features in our robust grasp planning algorithm.}
+\figlabel{local-feature-model}
+\vspace*{-15pt}
+\end{figure}
+
+\subsubsection{Global Object Similarity}
+\seclabel{global-sim}
+While force closure is based on local surface properties of an object around contact points, measuring global similarity may be similarity may be useful because the heightmaps may not capture all possible contact points for a grasp under perturbations in object and gripper pose.
+Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.
+
+%\subsection{Thompson Sampling}
+%\seclabel{thompson}
+%
+%Following Laskey et al.~\cite{laskey2015bandits}, we use Thompson sampling to select the next grasp to evaluate given belief distributions on the $P_F$ for each grasp on iteration $t$ specified by estimates $\mA_t = \{\alpha_{1,t}, ..., \alpha_{K,t}\}$ and $\mB_t = \{\beta_{1,t}, ..., \beta_{K,t}\}$.
+%Thompson sampling samples a probability of force closure $\hat{\theta}_{j,t} \sim B(\alpha_{j,t}, \beta_{j,t})$ for all grasps $j = 1, ..., K$, then selects the grasp $j_t^* = \myargmax{j} \hat{\theta}_{j,t}$ to evaluate next.
+%Several other criteria exist for selecting the next evaluation in MAB, such as Gittins indices~\cite{laskey2015bandits}, Upper Confidence Bounds~\cite{boularias2015learning}, and Expected Improvement~\cite{montesano2012active}.

### 2015-09-10 ICRA2016/bandits_docs/includes/background.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 \centering
-\includegraphics[scale=0.22]{figures/illustrations/correlated_bandits.png}
+\includegraphics[scale=0.23]{figures/illustrations/correlated_bandits.png}
 \caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle.
@@
 \begin{align*}
-	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} w_m^2 \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_2^2 \right)
+	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{W_m}^2 \right)
 \end{align*}
-\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space and $w_m \in \mathbb{R}$ are weights scaling the relative contribution of the feature maps to the similarity metric.
+\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space, $W_m \in \mathbb{R}^{d_m \times d_m}$ are linear transformations scaling the relative contribution of the feature maps to the similarity metric, and $\| \phi \|_{W} = \phi^T W^T W \phi$.
 
@@
 % and $\mS$ and $\mN$ are the number of successes and total trials for grasps in the database, respectively.
-Upon observing $F_{i,k}$ for grasp $\bg_{i,k}$ on iteration $t$, we update our belief $\theta_{j,k}$ for all other grasps on object $\mO_i$ by~\cite{goetschalckx2011continuous}:
+Upon observing $F_{i,k}$ for grasp $\bg_{i,k}$ on iteration $t$, we update our belief $\theta_{i, \ell}$ for all other grasps on object $\mO_i$ by~\cite{goetschalckx2011continuous}:
 
@@
 \begin{align}
-	\alpha_{j,k,t} &= \alpha_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) F_{i,k} \label{eq:alpha} \\
-	\beta_{j,k,t} &= \beta_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) (1 - F_{i,k})\label{eq:beta}
+	\alpha_{i,\ell,t} &= \alpha_{j,\ell,t-1} + k(\mY_{i, \ell}, \mY_{i,k}) F_{i,k} \label{eq:alpha} \\
+	\beta_{i,\ell,t} &= \beta_{j,\ell,t-1} + k(\mY_{i,\ell}, \mY_{i,k}) (1 - F_{i,k})\label{eq:beta}
 \end{align}
@@
 Finally, we make the heightmap rotationally invariant by rotating it to align the axes with the eigenvectors of the weighted covariance matrix of contact points generating the heightmap as described in~\cite{tombariunique}.
-Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$.
-\TODO{This is slightly more complicated but takes a bit to explain; basically the ordering of contacts doesn't matter here}
+Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$. \TODO{Describe symmetrization of heightmaps for contacts.}
 \figref{local-feature-model} illustrates local surface patches extracted by this procedure.
@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
-\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.
-We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture.
-Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
-\figlabel{global-feature-model}
-\vspace*{-15pt}
-\end{figure}
-
 \subsection{Optimizing Feature Weights}
 One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
-%Past work has optimized these weights using a squared error loss on the probability of success predicted by the CCBP and a true probability of success from brute force evaluation~\cite{montesano2012active}.
-%However, this criterion may be inappropriate for predicting probabilities, as the predictions must be bounded between 0 and 1.
-We select the weights that minimize the cross entropy loss~\cite{}:
+We select the weights that minimize the cross entropy loss~\cite{de2005tutorial}:
 
@@
 We optimize this objective using SGD with the weights initialized to $w_i = 100$ for all $i$.
-\TODO{For experiments so far we actually use a grid search and not SGD but we are interested in using this.}
+\TODO{For experiments so far we actually use a grid search and not SGD but we are interested in using this in final experiments.}

### 2015-09-10 ICRA2016/bandits_docs/includes/conclusion.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 \seclabel{conclusion}
-We introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 20,000 3D object models and a network of similarity between object models and parallel-jaw grasps on each model.
-We extended the Multi-Armed Bandit model of Laskey et al.~\cite{laskey2015bandits} to leverage similiarty between grasps based on gripper pose, local surface geometry encoded as heightmaps, and global shape similarity encoded using a state-of-the-art method for shape retrieval based on multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}.
-Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to select a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
+We developed a Multi-Armed Bandit algorithm based on correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
+To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models, each labelled with up to 250 grasps and the probability of force closure of each.
+For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification, trained on milliions of images and thousands of 3D object examples.
+Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
 
 One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
-Future work will leverage recent developments in feature optimization with deep neural networks~\cite{levine2015end} to optimize feature representations of both the local and global surface geometry based on the outcome of grasp evaluations in the bandit algorithms.
-We will also study extensions of the shape similarity neural network to predict object class from simulated depth images of objects on a table, which could be useful for transferring learned data from Dex-Net to objects in the physical world.
+Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
+We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
+We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies using supervision, with the goal of a future system that maps directly from images to motor torques.
 
-Another shortcoming is our current use of wrench space metrics, which have been criticized recently for not correlating with human labels~\cite{kappler2015leveraging} or physical trials~\cite{balasubramanian2012physical}.
-However, both forms of labels may be difficult to acquire for the entire dataset because of the human and time cost involved.
-Future work will research using Multi-Armed Bandits (MABs) to actively acquire grasp evaluations uncertain objects.
-To do so, we will study using functional map networks to establish consistent maps between prototypical object parts that indicate grasp affordance, such as handles
-We will also build on recent developments in caging to label key the dataset with caging hand configurations either analytically, using simulation, or using a learned model to predict caging configurations.
-We will also work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes, integrating Dex-Net with physical robots, and learning statistical models of grasp success using deep learning and MAB.
+Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
+This presents a challenge because the number of labels per object and grasp may be smaller thatnwith probability of force closure due to the time cost involved.
+Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
+We will also add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}.
+To achieve this we will work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

### 2015-09-10 ICRA2016/bandits_docs/includes/dataset.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 \seclabel{dexnet}
-\TODO{Due to space, it might make sense to discuss in experiments as appears to be common practice when the dataset is not going to be released to the public}
-It remains to describe the details of creating the Dexterity Network (Dex-Net), our prior dataset of objects and grasps with similarity, for use in the Multi-Armed Bandit models of Algorithm~\ref{alg:full}.
-Dex-Net 1.0 consists of approximately 20,162 3D mesh models \TODO{Update with correct count} collected from the datasets described in \figref{datasets}.
-Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
-These models were chosen to reflect physical objects commonly used for benchmarking in grasping research for potential future physical experiments using Dex-Net.
-The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a relatively new benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
-While the geometry of synthetic models does not necessarily reflect a physical object, using these models allows us to examine the effects of scale at tens of thousands of 3D models, which has not been previously attempted in grasp synthesis research.
 
-In order to use the models for grasp selection, we first preprocess each model.
-Each object in Dex-Net is originally specified as a 3D mesh $\mS = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
-First, we remove unreferenced vertices and illegal triangles (e.g. same vertex is referenced twice in one triangle).
-Next, we normalize the orientation of the model by performing Principal Component Analysis (PCA) on the raw vertices of the mesh and then rotating the object such that its first principal component aligns with the $z$-axis and its second aligns with the $y$-axis.
-We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
-Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies withing the maximum opening of the gripper.
-Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{}, an open-source C++ tool.
-
-Once each 3D model is preprocessed, we compute the shape feature vector described in \secref{cnn} for each object.
-Each feature vector is then put into a KD-Tree nearest neighbor query structure for accelerated lookups of shape nearest neighbors.
-This structure consistutes our shape similiarity network, in which each object $\mO$  is connected to its $n$ nearest neighbors $\mO_1, ..., \mO_n$ by an edge of weight $\| \psi(\mO) - \psi(\mO_i) \|_2^2$.
-We generate a set of grasps for each object in the network using the method of \secref{candidates} and evaluate the probability of force closure for each grasp using brute-force Monte Carlo integration as a benchmark~\cite{kehoe2012toward}.
-As the number of models is quite large, we distribute the grasp labelling for each object across virtual machines in Google Compute Engine and aggregate the results at the end.
+\TODO{Make this flow with above paragraph!}
+The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
+Dex-Net consists of over 10,000 3D mesh models, selected to represent objects that might be encountered in warehousing or the home such as tableware, tools, and toys.
+%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
+%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
+\figref{datasets} details the data sources and their sizes.
 
@@
 \includegraphics[scale=0.1]{figures/dataset_table.jpg}
-\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).
-\TODO{Update ModelNet number - we actually only use select categories}}
+\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).}
 \figlabel{datasets}
@@
 \end{figure}
+
+\subsection{Data Cleaning}
+Each object in Dex-Net is originally specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
+We preprocess each model by first removing unreferenced vertices and degenerate triangles.
+Next, we compute the object reference frame by performing Principal Component Analysis (PCA) on the vertices of the mesh and aligning the $z$-axis with the first principal component and the $y$-axis with the second principal component
+We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
+Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
+Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{sdfgen}, an open-source C++ tool.
+
+\subsection{Grasp Sampling}
+\seclabel{grasp-sampling}
+Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and the $P_F$ for each.
+We generate candidate grasps using a modified version of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
+Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS $ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
+To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mC$ using rejection sampling.
+Next we sample a direction $\bv \in \bS^2$ uniformly at random from the cone and compute:
+%\vspace{-2ex}
+\begin{align*}
+	\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv  &&  \bx = 0.5 (\bc_1 + \bc_2)
+\end{align*}
+\noindent where $t_2^*$ is defined in \secref{contact}.
+This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
+We add $\bg_{i,k}$ to our candidate set if both $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.
+
+We then evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
+Formally, our full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in our Grasp Moduli Space.
+
+%We generate a set of grasps for each object in the network using the method of \secref{candidates} and evaluate the probability of force closure for each grasp using brute-force Monte Carlo integration as a benchmark~\cite{kehoe2012toward}.
+%As the number of models is quite large, we distribute the grasp labelling for each object across virtual machines in Google Compute Engine and aggregate the results at the end.
+
+\subsection{Object Similarity Embedding}
+\seclabel{object-similarity}
+In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
+Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval that uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.
+
+\figref{global-feature-model} illustrates our method.
+Let $R$ be the maximum dimension of the object bounding box.
+We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$.
+Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
+We initialize the weights of our network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
+Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
+Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output to from 4028 dimensions to 100 dimensions.
+This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
+Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.
+
+Given the MV-CNN object representation, we measure the dissimilarity between two objects $\mO_i$ and $\mO_j$ by the Euclidean distance $\| \psi(\mO_i) - \psi(\mO_j) \|_2$.
+For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
+
+%In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
+%The image classification training step had a test accuracy of 76\%.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
+\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.
+We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture.
+Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
+\figlabel{global-feature-model}
+\vspace*{-15pt}
+\end{figure}

### 2015-09-10 ICRA2016/bandits_docs/includes/experiments.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 
-\TODO{All experiments here are preliminary. Add new results from non-symmetric objects and more data}
-\TODO{Include experiments on sensitivity to uncertainty} \\
-\TODO{Images of selected grasps} \\
+\TODO{All experiments here are preliminary. Add new results from more objects, especially non-symmetric ones.} \\
+\TODO{Include experiments on sensitivity to uncertainty.} \\
+\TODO{Images of selected grasps.} \\
 
-We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity to parameters of the algorithm.
-To test the generalization of our feature maps, we reserved objects from YCB and ModelNet as a test set, and used nested subsets of the remaining data as training data for optimizing the hyperparameters and for tuning the MAB convergence rate.
-We assumed a PR2 gripper for our grasps, which has a maximum width of approximately $10cm$.
-We assumed isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
-The weights of our similarity kernel were selected using a grid search over possible values on a held-out validation set.
+We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity of the convergence rate to the kernel bandwidths, number of nearest neighbors, and uncertainty.
+We created three nested training sets of 100, 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
+From the remaining objects we created a set of 20 validation objects for selecting algorithm hyperparameters and a set of 30 objects for test data.
+We used isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+The bandwidths of our similarity kernel were set to scaling transformations $C = \sigma I$ where $\sigma \in \bR$ for the grasp parameter and global object feature maps, and a gaussian mask $C_d$ centered on the gradient heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
+The bandwidths were selected by maximizing convergence rate on the validation set using a grid search over hyperparameters.
 
-\subsection{System}
-To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud services.
-We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
-We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
-Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
-When an instance is launched, we mounted Dex-Net via a persistent disk containing a particular set of objects and grasps.
-Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
-After all instances complete, the master script turns off all instances, unmounts all disks, downloads the results from each instance, and sends the user a notification email.
-The results can be optionally analyzed by the master script.
+To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
+We used Google Compute Engine to distribute trials of MAB algorithms across objects and Google Cloud Storage (GCS) to store Dex-Net.
+Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by a factor of nearly $1500\times$.
 
@@
 
-~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
+~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
 The plot compares Algorithm~\ref{alg:full} with no prior data to uncorrelated Thompson sampling and uniform allocation, two methods used by Laskey et al.~\cite{laskey2015bandits}.

### 2015-09-10 ICRA2016/bandits_docs/includes/introduction.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 
-Consider a robot fulfilling orders in a warehouse.
-The robot must quickly plan grasps for consumer products to fullfill orders.
-Furthermore, the robot may not precisely know the state of the environment, such as the pose or frictional properties of object, due to sensor imprecision and missing data (e.g.
-occlusions in point clouds).
-This poses a challenge for many existing grasp planning methods that are based on precise knowledge of contact locations and surface normals~\cite{ciocarlie2009, ferrari1992} due to the distribution on possible environment configurations.
-
-In vision and speech, advances in Big Data and distributed computing, combined with datasets of milliions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher}, have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
-This raises the question: will machine learning of grasps for vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
+``Cloud Robotics and Automation" considers a new paradigm where robots and automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
+There are several potential advantages to using the Cloud: 1) Big Data: access to updated libraries of images, maps, and object/product data, 2) Cloud Computing: access to parallel grid computing for statistical analysis, machine learning, and planning.
+These advantages have recently been highlighted in vision and speech, where datasets with millions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher} have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods~\cite{kehoe2015survey}.
+This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, environment configurations, etc.~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.
 
@@
 
-We introduce Dex-Net 1.0, a dataset of 3D models and grasps with similarity metrics, and a system for actively acquiring statistical models of grasp quality across the network.
-The Dex-Net dataset contains representative 3D models of objects that could be encountered in warehousing or the home.
+We develop a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of parallel-jaw grasps and 3D object models.
+Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
+
+To study scaling effects we develop Dex-Net 1.0, a new dataset of approximately 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as tooks tableware, boxes, and toys.
+~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
 Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
-The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to scale the number of models.
-~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
-We measure object similarity based the distance between feature vectors generated from multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}, a state-of-the are method in shape retrieval
-We measure similarity between grasps by the pose of the gripper and local surface ``heightmaps" extracted at location of contact with an object~\cite{herzog2012template, kappler2015leveraging}.
-Our system uses Google Cloud Platform to distribute grasp quality evaluations across hundreds of virtual machines and to store millions of grasps across the objects in Dex-Net.
+The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
+Dex-Net contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
+We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to learn a similarity metric between objects based on CNN features  from millions of labeled images, which allows us to efficiently retrieve similar 3D objects from Dex-Net for grasp planning at scale.
+To the best of our knowledge, Dex-Net is the largest dataset to-date used for grasping research.
 
-In this work, we use Dex-Net to study the convergence rate of Multi-Armed Bandit (MAB) algorithms for finding a grasp with high probability of force closure under object pose, gripper pose, and friction coefficient uncertainty from a set of 250 candidate grasps on objects from Dex-Net.
-To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for similar grasps on similar 3D objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
-CCBPs predict a belief distribution for the quality of each grasp based similarity to data in Dex-Net that can be efficiently updated after observing the quality of a grasp for a sampled object pose, gripper pose, and friction coefficient.
-Our results suggest that CCBPs bootstrapped with data from Dex-Net can accelerate grasp planning by up to $10\times$.
+We implement our algorithm on Google Compute Engine and store Dex-Net on Google Cloud Storage.
+Experiments on using our algorithm to plan parallel-jaw grasps with high probability of force closure from 250 candidates suggest that orders of magnitude of prior data can reduce the average number of samples needed for X by Y and \TODO{Robustness statement} on a test set of 30 objects.
+Experiments on the sensitivity to the fsimilarity metric and number of nearest neighbors used from Dex-Net suggest...\TODO{Add}
+\TODO{Something about the number of instances...}

### 2015-09-10 ICRA2016/bandits_docs/includes/problem_statement.tex
Modified entire draft. In a limbo state. Going back through feedback now.

--- 2015-07-27 ICRA2016/bandits_docs/includes/problem_statement.tex
@@
 
-\TODO{Fill in more details. This is a stripped down version to get ideas down on the page}
-Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by its center in 3D space $\bx \in \mathbb{R}^3$ and approach direction $\bv \in \mS^2$.
-Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3,  \}$ denote the space of all grasps.
+Given a previously unknown object, we consider the problem of finding a of parallel-jaw grasps with maximum probability force closure, $P_F$, under uncertainty in object pose, gripper pose, and friction coefficient using a database of 3D object models annotated with grasps and the $P_F$ of each.
+We assume the object shape is exactly known and provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and zero inside the object.
+We also assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
+Furthermore, we assume soft-finger contacts between the gripper and object~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
+%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.
+
+\subsection{Grasp and Object Parameterization}
+\seclabel{grasp-param}
+Our grasping parameterization is illustrated in~\figref{grasp-model}.
+Let $\bg = (\bx, \bv)^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
+Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
+We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object, and assume that all points are specified with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
+Let $\mG = \{ [(\bx, \bw) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where the $\mF$ is the space of all SDFs.
+We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.png}
+\caption{Illustration of our grasp parameterization and contact model.
+(Left) We parameterize parallel-jaw grasps by the centroid of the jaws $\bx \in \mathbb{R}^3$ and approach direction, or direction along which the jaws close, $\bv \in \bS^2$.
+The grasp parameters $\bx$ and $\bv$ are specified with respect to a coordinate frame located at the object center of mass $\bz$ and oriented along the principal directions of the object.
+(Right) The jaws are closed until contacting the object surface at locations $\bc_1, \bc_2 \in \mathbb{R}^3$, at which the surface has normals $\bn_1, \bn_2 \in \bS^2$.
+The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$.
+From these parameters we can derive the forces and torques that the gripper can apply to the object.
+}
+\figlabel{grasp-model}
+\vspace*{-15pt}
+\end{figure}
+
+%Let $\mM = \left\{\mV, \mT \right\}$ be a triangular mesh representing an object's geometry, where $\mV = \{\bw_i \in \mathbb{R}^3 \}_{i=1}^{N_v}$ is a set of $N_v$ vertices and $\mT = \{ \bt_i \in \mathbb{Z}_{+}^3 \}_{i=1}^{N_t}$ is a set of $N_t$ triangles formed by triplets of integer indices of vertices.
 %We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
@@
 
-We will assume a known object shape $\nu$, and known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}.
-%Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
-Let $\xi$ be uncertainty in object pose distributed as a Gaussian with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
-Let $\rho$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\rho} \in \mG$ and covariance $\Sigma_{\rho}$.
-Let $\zeta$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
-Given object shape and samples of object pose, and gripper pose, we let $\bc_i(\bg, \theta, \xi, \rho) \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
-Furthermore, let $\bn_i(\bc_i, \nu) \in \mS^2$ denote the surface normal at this contact.
-A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
+\subsection{Sources of Uncertainty}
+\seclabel{uncertainty}
+We assume Gaussian uncertainty in 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
+Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ be a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
+Following the model of Barfoot and Furgale~\cite{barfoot2014associating}, we define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
+Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote Gaussian uncertainty in gripper pose with mean $\mu_{\nu} \in \mG$.
+Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote Gaussian uncertainty in friction coefficient distributed as a Gaussian with mean $\mu_{\gamma} \in \mathbb{R}$.
+We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{gamma}$ samples of object pose, gripper pose, and friction, respectively. 
+%Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.
 
-We measure grasp quality by the probability of force closure subject to these uncertain quantities.
-Let $F \in \{0, 1\}$ denote the occurence of force closure, or the ability to resist wrenches in arbitrary directions~\cite{ferrari1992}.
-Then the probability of force closure for a grasp $\bg$ is
-%\vspace{-2ex}
+\subsection{Contact Model}
+\seclabel{contact}
+Our contact model is illustrated in the right panel of \figref{grasp-model}.
+Given a grasp $\bg$ with width $w$ on an object $\mO$ and samples of object pose, gripper pose, and friction, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface.
+Each contact $\bc_i = \bx + s_i (t_i^* - w / 2) \bv$ where
 \begin{align*}
-	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \xi, \rho, \zeta \right).
+	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx + s_i (t - w / 2) \bv\right) = 0,
 \end{align*}
-\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
-To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$
+\noindent$s_1 = -1$, and $s_2 = 1$~\cite{mahler2015gp}.
+
+Given contact points, let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tanget vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
+To compute the forces that each contact can apply to the object for a sampled friction coefficient $\hat{\gamma}$, we discretize the friction cone at contact $i$~\cite{pokorny2013classical} into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bbf_{i,j} = \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \text{ for } j = 1, ..., l \right\}$.
+Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
+Under our soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
+Thus the set of all wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
+
+\subsection{Quality Metric}
+\seclabel{quality}
+In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
+While we acknowledge that some evidence suggests that deterministic force closure is not always a strong predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate when compared to human labels or physical executions, allowing us to better study the effects of large amounts of data.
+
+Let $F \in \{0, 1\}$ denote the occurence of force closure.
+To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
+Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.
+%A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
+%
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[scale=0.5]{figures/illustrations/dexnet_graphical_model_simple.png}
+%\caption{A graphical model describing the relationships between known uncertain parameters (shaded gray) such as object pose and the force closure random variable $F$.}
+%\figlabel{graphical-model}
+%\vspace*{-15pt}
+%\end{figure}
+
+\subsection{Objective}
+The probability of force closure for a grasp $\bg$ on object $\mO$ is $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
+We are interested in finding $\bg^*$,the grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
+To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}:
 
@@
 \begin{align}
-	\maximum{g_{I(1)}, ..., g_{I(T)} \in \mG} \sum \limits_{t=1}^T P_F(g_{I(t)}) \label{eq:objective}
+	\underset{g_{I(1)}, ..., g_{I(T)} \in \mG}{\text{maximize }} \sum \limits_{t=1}^T P_F(g_{I(t)}). \label{eq:objective}
 \end{align}
+\noindent where $I(i)$ denotes the grasp selected at time $t$.
 
-\noindent As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$.
-In practice $\Gamma$ has been set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
-\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent}
-
-Even with a discrete set of candidates, evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
-Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
-In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.
+As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits(MAB) ~\cite{laskey2015bandits}.
+In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net for accelerated convergence to $\bg^*$.

### 2015-09-10 ICRA2016/bandits_docs/includes/related_work.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 
-For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
-Research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, miller2004graspit}, object WS~\cite{liu2015fast, pollard1994parallel}, or task WS~\cite{kruger2011partial, li1988task}.
-WS metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{leon2010opengrasp}.
-However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005} and for not taking into account the dynamics of the the grasp~\cite{prattichizzo2008grasping}.
-%This has motivated work on grasp transfer from a knowledge database to new objects, robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and synthesis from statistical models of grasping learned from physical data or human labels.
+%For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
+Past research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, ciocarlie2009}, object WS~\cite{liu2015fast}, or task WS~\cite{kruger2011partial}.
+%However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005}.
+However, the need to recompute WS metrics for every new object and grasp motivated research on grasp planning by transferring grasps from similar objects in a database of prior knowledge~\cite{li2005shape}.
+%Li and Pollard~\cite{li2005shape} generated grasps for a human hand by matching object shapes to hand postures in a database.
+Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
+The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps using the Iterated Closest Point algorithm~\cite{goldfeder2011data}.
+Research has also studied transferring grasps from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.
 
-The need to recompute WS metrics to select grasps for every new object motivated research on grasp synthesis by transferring grasps from a database of exemplar objects.
-Li and Pollard~\cite{li2005shape} generated grasps by matching object shapes to human hand postured in a database.
-Goldfelder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
-The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{goldfeder2009data, goldfeder2011data}.
+Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control~\cite{brook2011collaborative, mahler2015gp, zheng2005}.
+%, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
+Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
+Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
 Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
-Recent research has also studied grasp transfer from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local rigid alignment and contact interpolation~\cite{hillenbrand2012transferring, stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2014grasp, pokorny2013grasp}.
+The authors found that the full system of object recognition, pose estimation, and grasp execution successfully grasped objects on a table in 80\% of trials.
 
-Another line of research focused on making analytic grasp metrics robust to imprecision in perception and control~\cite{goldberg1990bayesian, stulp2011learning, zheng2005}.
-Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} developed a Bayesian framework to evaluate both the expected epsilon quality and the probability of physical success on a PR2 given uncertainty in object identity, object pose, and gripper positioning on deterministic mesh and point cloud models.
-Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
-Kim et al.~\cite{kim2012physically} planned grasps using the expected epsilon quality metric~\cite{ferrari1992} under dynamics and uncertainty in pose, and found that the robust metric has a higher correlation with physical grasp success.
-Recent research has also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{christopoulos2007handling}, part tolerancing in manufacturing~\cite{kehoe2012estimating, kehoe2012toward, panahi2015orienting}, or missing and noisy data from depth sensors such as the Kinect modeled with Gaussian process implicit surfaces~\cite{dragiev2013uncertainty, mahler2015gp, laskey2015bandits}.
-%Many have also studied caging gripper configurations~\cite{rimon1996caging}, which are a waypoint to form closure grasps for two fingers~\cite{vahedi2008caging, rodriguez2012caging} and may be robust to perturbations in object pose and shape~\cite{diankov2008manipulation, Wan2012_ICRA}.
+Another line of research has focused on synthesizing grasps using statistical models learned from a database of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
+Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
+Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images based on a dataset of thousands of 1035 images annotated with parallel-jaw grasps by humans.
+Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to the demonstrations.
+Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a library of prototypical graspable point clouds, and showed that the representation could be transferred to real sensor data~\cite{detry2013learning}.
+Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
+The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface rendered along the surface normal. 
+%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{oberlinacquiring}.
+%Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
+%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
+In comparison, we learn a model to predict a belief distribution on the probability of force closure for a parallel-jaw grasp on a new object based on similarity to prior 3D objects and grasps, and we actively choose the next grasp to evaluate using Multi-Armed Bandits.
 
-Recent research has also studied synthesizing grasps by ranking grasps according statistical models learned from human annotations or physical execution~\cite{bohg2014data}.
-Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
-Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images, which was extended to real time by Redmon and Angelova~\cite{redmon2014real}.
-Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
-Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{detry2013learning}.
-Kappler et al.~\cite{kappler2015leveraging} trained a deep neural network to predict grasp success for a Barett hand measured by human annotations and the results of simulations on a database of synthetic pointclouds of objects.
-Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
-%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
-In comparison, we learn a model to predict a Bayesian distribution on the probability of force closure for a grasp on an object based on similarity to a set of prior grasps and objects in a database, and use our model to actively decide the next grasp to evaluate using Multi-Armed Bandits.
-
-Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples.
-Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
-Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discrading grasps known to have poor quality.
+Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples~\cite{boularias2015learning, salganicoff1996active}.
+%Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
+Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
 Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
 Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
-Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
-Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
-Similarly, Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
-Recently, Laskey et al.~\cite{laskey2015bandits} showed that Multi-Armed Bandit (MAB) algorithms can be used to accelerate the identification of grasps with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
-MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
-In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net with CCBPs to further reduce the number of samples needed to converge to a grasp with high quality.
+%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
+%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
+Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
+Recently, Laskey et al.~\cite{laskey2015bandits} used Multi-Armed Bandit (MAB) algorithms to reduce the number of samples needed to identify grasps with high probability of force closure under uncertainty in object shape, pose, and friction in 2D.
+%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
+In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net to further accelerate convergence to a grasp with high probability of force closure.
+
+% DEEP LEARNING
+Our work also builds on recent developments from the field of shape retrieval
+\TODO{Let Matthieu provide initial version}

### 2015-09-10 ICRA2016/bandits_docs/paper.tex
Modified entire draft. In a limbo state. Going back through feedback now.

@@
 \begin{document}
-\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning
+\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale
 %Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
 		\versionline{4}}
-\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Mel Roderick$^1$, Michael Laskey$^1$, Kai Kohlhoff$^3$, \\ Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
+\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Matthieu Aubry$^1$, \\
+Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
 \thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
@@
 
-\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
-\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
+%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
+%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
 
@@
 \input{includes/problem_statement}
-\input{includes/background}
+\input{includes/dataset}
+%\input{includes/background}
 \input{includes/algorithm}
-\input{includes/dataset}
 \input{includes/experiments}
@@
 
+\section{Acknowledgments}
+This research was performed with UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
+The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
+We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
+
 %\balance

### 2015-09-10 ICRA2016/bandits_docs/includes/abstract.tex
Added many new figures as well as updated text. Quite a bit closer

--- 2015-08-26 ICRA2016/bandits_docs/includes/abstract.tex
@@
 \begin{abstract}
-\TODO{Fill in after rest of paper done.}
+Recent advances in distributed computing and machine learning combined with very large datasets of images and human speech have produced a series of results that surpass decades of research in analytic methods and, in some cases, human ability.
+This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
+We develop a Multi-Armed Bandit algorithm with correlated rewards and show that learning from a large dataset of prior grasps and 3D object models can reduce the number of samples needed for robust grasp planning using our algorithm.
+To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 unique 3D object models.
+Each object is labelled with up to 250 parallel-jaw grasps and the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
+We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between 3D objects and we apply it to indexing similar objects for grasp planning at scale.
+We implement our algorithm and database using the Google Cloud Platform.
+Experiments on a set of 20 test objects suggest that the time taken to plan a robust grasp is approximately $3.5\times$ faster than Thompson sampling without prior data on average
+Experiments on sensitivity suggest that convergence rate is fastest for objects for which the MV-CNN returns geometrically similar neighbors from Dex-Net.%, and that the convergence rate can descrease if the similarity metric measures false correlations between grasps.
+Code, data, and additional information can be found at: \TODO{Url}
 \end{abstract}

### 2015-09-10 ICRA2016/bandits_docs/includes/algorithm.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 Next, we run MAB by selecting the next grasp to sample using Thompson sampling~\cite{laskey2015bandits}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the probability of force closure for each grasp.
-Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimated of the grasp with the heighest estimated $P_F$.
+Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
 
@@
 Such correlations may exist when the Bernoulli random variables depend on common latent factors.
-For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar.
+For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.
 
 Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
-We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as an occurence of force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ on object $\mO$ from samples of object pose, gripper pose, and friction, as described in \secref{quality}.
+We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
 Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
 Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
-In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is a Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
 
@@
 \noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
+The bandwidths are hyperparameters of the algorithm that might be set by cross-validation on a set of training data~\cite{rasmussen2006}.
 
@@
 
-\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.
+\noindent Intuitively, this allows evaluations of a grasp on an object to constitute fractional evaluations of similar grasps on similar objects.
 
@@
 \seclabel{features}
-\TODO{Move elsewhere / condense? Its a lot of information coming out of nowhere}
+\TODO{Condense section / possibly move earlier.}
 We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.
@@
 \seclabel{param-features}
-Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx$ is the grasp center, $\bv$ is the grasp approach, and $\rho_i$ is the $i$-th moment arms.
+Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx \in bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
 The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
@@
 
-\subsubsection{Global Object Similarity}
+\subsubsection{Shape Features}
 \seclabel{global-sim}
-While force closure is based on local surface properties of an object around contact points, measuring global similarity may be similarity may be useful because the heightmaps may not capture all possible contact points for a grasp under perturbations in object and gripper pose.
+While force closure is based on local surface properties of an object around contact points, measuring global similarity may be useful because the heightmap gradients may not capture all possible contact locations for a grasp under perturbations in object and gripper pose.
 Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.

### 2015-09-10 ICRA2016/bandits_docs/includes/conclusion.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
-We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies using supervision, with the goal of a future system that maps directly from images to motor torques.
+We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
 
 Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
-This presents a challenge because the number of labels per object and grasp may be smaller thatnwith probability of force closure due to the time cost involved.
-Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
-We will also add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}.
-To achieve this we will work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
+%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
+%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
+We plan to add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}, and study the selection of a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
+We plan to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

### 2015-09-10 ICRA2016/bandits_docs/includes/dataset.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 
-\TODO{Make this flow with above paragraph!}
+\TODO{Perhaps a cleaner transition here}
 The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
@@
 \includegraphics[scale=0.1]{figures/dataset_table.jpg}
-\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).}
+\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).
+\TODO{Remove columns}}
 \figlabel{datasets}
@@
 In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
-Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval that uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.
+Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a new method for 3D shape classifciation that outperforms previous methods and uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.
 
@@
 
-%In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
-%The image classification training step had a test accuracy of 76\%.
+In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
+The image classification training step had a test accuracy of 76\%.
+To validate that our implementation was working, we tested our method on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% for the winner of the challenge~\cite{li2015comparison}.
 

### 2015-09-10 ICRA2016/bandits_docs/includes/experiments.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 \seclabel{experiments}
+\TODO{Add average convergence experiment with test set}
+\TODO{Add sensitivity to uncertainty}
 
-\TODO{All experiments here are preliminary. Add new results from more objects, especially non-symmetric ones.} \\
-\TODO{Include experiments on sensitivity to uncertainty.} \\
-\TODO{Images of selected grasps.} \\
-
-We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity of the convergence rate to the kernel bandwidths, number of nearest neighbors, and uncertainty.
+We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
 We created three nested training sets of 100, 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
 From the remaining objects we created a set of 20 validation objects for selecting algorithm hyperparameters and a set of 30 objects for test data.
-We used isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
-The bandwidths of our similarity kernel were set to scaling transformations $C = \sigma I$ where $\sigma \in \bR$ for the grasp parameter and global object feature maps, and a gaussian mask $C_d$ centered on the gradient heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
-The bandwidths were selected by maximizing convergence rate on the validation set using a grid search over hyperparameters.
+We ran our algorithm with $N_n = 10$ nearest neighbors.
+We also used isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+
+The bandwidths of our similarity kernel were constrained to be disgonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a gaussian mask $C_d$ centered on the gradient heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
+The bandwidths were selected by maximizing average convergence rate on the validation set using a grid search over hyperparameters.
 
@@
 We used Google Compute Engine to distribute trials of MAB algorithms across objects and Google Cloud Storage (GCS) to store Dex-Net.
-Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by a factor of nearly $1500\times$.
+Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by over $1000\times$.
 
-\subsection{Rate of Convergence}
-\TODO{Replace with final versions. The current results are preliminary}
+\subsection{Scaling of Average Convergence Rate}
+\TODO{Replace with test results. Current are on validation set due to time constraints}
+\TODO{Add 100 model results}
 
-~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
-The plot compares Algorithm~\ref{alg:full} with no prior data to uncorrelated Thompson sampling and uniform allocation, two methods used by Laskey et al.~\cite{laskey2015bandits}.
-We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
-Iniitial reuslts suggest that performance on the flower pot is poorer because few grasps are similar according to our feature representation.
-
-%Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
+To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran Algorithm~\ref{alg:full} on the 20 validation objects with priors computed from 1,000 and 10,000 objects from Dex-Net.
+~\figref{avg-reward} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the 20 validation objects for 4,000 iterations.
+The plot also compares Algorithm~\ref{alg:full} to uncorrelated Thompson sampling and uniform allocation~\cite{laskey2015bandits}.
+Our algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling over all iterations.
+Furthermore, the 10,000 object curve does not reach below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
+However, we see that on average our algorithm makes progress more slowly than Thompson sampling.
 
@@
 \centering
-	\begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[scale=0.08]{figures/box_avg_reward_w_model.jpg}
-        \caption{Normalized $P_F$ on a cereal box with 250 candidate parallel-jaw grasps.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[scale=0.08]{figures/flowerpot_avg_reward_w_model.jpg}
-        \caption{Normalized $P_F$ on a flower pot with 250 candidate parallel-jaw  grasps.}
-    \end{subfigure}
-\caption{Comparison of the normalized $P_F$ of the sampled parallel-jaw grasp versus iteration of the MAB algorithm for correlated Thompson sampling, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials.
-(a) On the cereal box, correlated Thompson sampling converges to within 90\% of the highest quality grasp approximately 4$\times$ faster than uncorrelated.
-(b) However, correlated and uncorrelated Thompson sampling perform comparably on the flower pot because there are few grasp similarities in the candidate set.
-}
-\figlabel{local-mab}
+\includegraphics[scale=0.45]{figures/illustrations/avg_reward.eps}
+\caption{Average normalized grasp quality versus iteration over 20 validation objects and 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
+We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
+We see that our algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from the 250 candidate set.}
+\figlabel{avg-reward}
 \vspace*{-15pt}
@@
 
-To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from Dex-Net: 0, 15, 150, and 1500 objects.
-\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle and detergent averaged over 50 trials.
-For each run of our algorithm, we used prior grasp from the five closest objects in Dex-Net in the multi-view CNN-based shape similiarity vector space.
-The objects from Dex-Net were labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
-For the bottle, we see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly larger subsets of prior data used, and is approximately $10 \times$ faster when using 1500 prior objects.
-For the detergent the gains are more modest, with the largest dataset accelerating convergence to within 90\% of the optimal grasp in the set by approximately $1.5 \times$.
-As illustrated in \figref{bottle-nn}, the nearest neighbor objects become increasingly similar to the object to label with increasing sizes of datasets from Dex-Net.
-This suggests that more prior data may also lead to more similar objects to rarer categories such as the detergent bottle, which may accelerate convergence 
-\TODO{Remove}
-Future work will examine these effects on a larger subset of objects and will use assitional nearest neighbors from Dex-Net to compute priors.
+\subsection{Sensitivity to Object Shape}
+\seclabel{shape-sens}
+To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of the only drill in Dex-Net and a spray bottle, which is an uncommon object category but has a few examples in Dex-Net.
+~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
+We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
+\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the algorithms about 100 iterations.
+However, performance on the drill does not increase using either 1,000 or 10,000 objects.
+
+This behavior may be explained by the similarity of the closest nearest neighbors in Dex-Net found by our shape similiarty MV-CNN, displayed in \figref{query}.
+We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
+On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.
 
@@
 \centering
-\begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[scale=0.08]{figures/bottle_avg_reward_w_model2.jpg}
-        \caption{Normalized $P_F$ on a bottle with 250 candidate parallel-jaw grasps.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[scale=0.08]{figures/detergent_avg_reward_w_model.jpg}
-        \caption{Normalized $P_F$ on a detergent bottle with 250 candidate parallel-jaw grasps.}
-    \end{subfigure}
-%\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
-\caption{Comparison of the normalized $P_F$ of the sampled parallel-jaw grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from Dex-Net, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20.
-Prior grasps were taken from increasingly larger subsets of Dex-Net: 15, 150, and 1500 objects.
-For the bottle, convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used.
-The detergent converges slightly faster with more prior data, however the speedup is approximately $1.5\times$ and does not appear to improve with additional data from Dex-Net.}
-\figlabel{global-mab}
+\includegraphics[scale=0.31]{figures/illustrations/avg_reward_drill.eps}
+\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net on a spray bottle (top) and drill (bottom).
+We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
+(Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimizal grasp once 10,000 objects are used.
+(Bottom) The drill, which is relatively rare in the dataset, has no noticeable performance increase over Thompson sampling, even with 10,000 objects.}
+\figlabel{avg-reward-obj}
 \vspace*{-15pt}
@@
 \centering
-\includegraphics[scale=0.075]{figures/bottle_nearest_neighbors.jpg}
-\caption{Illustration of the five nearest neighbor objects from Dex-Net using the multi-view CNN-based shape embedding and Euclidean distance for increasing sizes of randomly selected subsets of data from Dex-Net.
-We see that while the neighbors for a small dataset are not relevant, the neighbors become increasingly similar to the query bottle as more data is used.}
-\figlabel{bottle-nn}
+\includegraphics[scale=0.28]{figures/illustrations/spray_grasps.eps}
+\caption{Illustation of the grasps predicted to have the highest $P_F$ after only 100 iterations by Thompson sampling, Algorithm~\ref{alg:full} with 1,000 prior objects from Dex-Net, and Algorithm~\ref{alg:full} with 10,000 prior objects from Dex-Net.
+Thompson sampling chooses a grasp near the edge of the object, while our algorithm selects grasps closer to the center-of-mass of the object.}
+\figlabel{spray-grasps}
+\vspace*{-5pt}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.38]{figures/illustrations/nearest_neighbors.eps}
+\caption{Illustration of the five nearest neighbor objects from Dex-Net to the spray bottle and drill using the multi-view CNN-based shape embedding and Euclidean distance for size 1,000 and 10,000 datasets from Dex-Net.
+We see that for the 1,000 object dataset neither model has relevant neighbors, while for the 10,000 object dataset two other spray bottles are returned.
+However, even with 10,000 objects no object geometrically similar to the drill is found.
+}
+\figlabel{query}
+\vspace*{-5pt}
+\end{figure}
+
+\section{Sensitivity to Similarity Kernel Bandwidth}
+\seclabel{band-sens}
+We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{features}.
+We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$ , as this was the most discriminative feature maps found by our hyperparameter tuning.
+\figref{bandwidth-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
+We see that increasing the bandwidth of the kernel can drastically affect the performance of the algorithm, causing the performance to be no better than uniform allocation.
+This may be because overestimating similarities can lead to a grasp with high $P_F$ being predicted too low, or vice versa.
+One the other hand, decreasing the bandwidth also decreases the convergence rate but Algorithm~\ref{alg:full} with 10,000 prior objects still outperforms Thompson sampling.
+This suggests that a conservative setting of similiarity kernel bandwidth may be preferable for Algorithm~\ref{alg:full}.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
+\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
+We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
+(Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocatoin.
+(Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
+\figlabel{bandwidth-sens}
 \vspace*{-15pt}
@@
 \section{Sensitivity to Uncertainty}
-
 \TODO{Write section}

### 2015-09-10 ICRA2016/bandits_docs/includes/introduction.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 
-We develop a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of parallel-jaw grasps and 3D object models.
+Our main contribution is a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of grasps and 3D object models.
 Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
@@
 ~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
-Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
+Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
 The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
 Dex-Net contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
-We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to learn a similarity metric between objects based on CNN features  from millions of labeled images, which allows us to efficiently retrieve similar 3D objects from Dex-Net for grasp planning at scale.
-To the best of our knowledge, Dex-Net is the largest dataset to-date used for grasping research.
+To the best of our knowledge, this is the largest dataset to-date used for grasping research.
+We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects from Dex-Net for grasp planning at scale.
 
-We implement our algorithm on Google Compute Engine and store Dex-Net on Google Cloud Storage.
-Experiments on using our algorithm to plan parallel-jaw grasps with high probability of force closure from 250 candidates suggest that orders of magnitude of prior data can reduce the average number of samples needed for X by Y and \TODO{Robustness statement} on a test set of 30 objects.
-Experiments on the sensitivity to the fsimilarity metric and number of nearest neighbors used from Dex-Net suggest...\TODO{Add}
-\TODO{Something about the number of instances...}
+We implement our algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage.
+Experiments on using our algorithm to plan parallel-jaw grasps with high probability of force closure from 250 candidates suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to identify a grasp with high quality by $3.5\times$ over a test set of 20 objects.
+Experiments on the sensitivity of our algorithm to the similarity metric suggest that measuring false simlarities can lead to a significant decrease in the convergence rate.
+\TODO{Update with final results}

### 2015-09-10 ICRA2016/bandits_docs/includes/problem_statement.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 
-Given a previously unknown object, we consider the problem of finding a of parallel-jaw grasps with maximum probability force closure, $P_F$, under uncertainty in object pose, gripper pose, and friction coefficient using a database of 3D object models annotated with grasps and the $P_F$ of each.
-We assume the object shape is exactly known and provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and zero inside the object.
+We consider the problem of finding a of parallel-jaw grasps with maximum probability force closure, $P_F$, on a 3D object model under uncertainty in object pose, gripper pose, and friction coefficient using a database of 3D object models annotated with grasps and the $P_F$ of each.
+We assume the object shape is exactly known and provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and negative inside the object (when the object is watertight).
 We also assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
@@
 We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object, and assume that all points are specified with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
-Let $\mG = \{ [(\bx, \bw) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where the $\mF$ is the space of all SDFs.
+Let $\mG = \{ [(\bx, \bw) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where the $\mF$ is the space of all SDFs for closed and compact surfaces.
 We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.
@@
 
-%Let $\mM = \left\{\mV, \mT \right\}$ be a triangular mesh representing an object's geometry, where $\mV = \{\bw_i \in \mathbb{R}^3 \}_{i=1}^{N_v}$ is a set of $N_v$ vertices and $\mT = \{ \bt_i \in \mathbb{Z}_{+}^3 \}_{i=1}^{N_t}$ is a set of $N_t$ triangles formed by triplets of integer indices of vertices.
-%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
-%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.
-
 \subsection{Sources of Uncertainty}
 \seclabel{uncertainty}
-We assume Gaussian uncertainty in 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
-Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ be a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
+We assume Gaussian distribuions on 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
+Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
 Following the model of Barfoot and Furgale~\cite{barfoot2014associating}, we define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
-Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote Gaussian uncertainty in gripper pose with mean $\mu_{\nu} \in \mG$.
-Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote Gaussian uncertainty in friction coefficient distributed as a Gaussian with mean $\mu_{\gamma} \in \mathbb{R}$.
+Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote a Gaussian distribution on gripper pose with mean $\mu_{\nu} \in \mG$.
+Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
 We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{gamma}$ samples of object pose, gripper pose, and friction, respectively. 
@@
 \seclabel{quality}
-In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
-While we acknowledge that some evidence suggests that deterministic force closure is not always a strong predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate when compared to human labels or physical executions, allowing us to better study the effects of large amounts of data.
+In this work we use the probability of force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
+While we acknowledge that deterministic force closure has not always been reported as a predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
 
 Let $F \in \{0, 1\}$ denote the occurence of force closure.
-To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
+To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
 Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.
-%A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
-%
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[scale=0.5]{figures/illustrations/dexnet_graphical_model_simple.png}
-%\caption{A graphical model describing the relationships between known uncertain parameters (shaded gray) such as object pose and the force closure random variable $F$.}
-%\figlabel{graphical-model}
-%\vspace*{-15pt}
-%\end{figure}
 
@@
 As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits(MAB) ~\cite{laskey2015bandits}.
-In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net for accelerated convergence to $\bg^*$.
+In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the samples needed to converge to $\bg^*$.

### 2015-09-10 ICRA2016/bandits_docs/includes/related_work.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 %For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
-Past research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, ciocarlie2009}, object WS~\cite{liu2015fast}, or task WS~\cite{kruger2011partial}.
-%However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005}.
-However, the need to recompute WS metrics for every new object and grasp motivated research on grasp planning by transferring grasps from similar objects in a database of prior knowledge~\cite{li2005shape}.
-%Li and Pollard~\cite{li2005shape} generated grasps for a human hand by matching object shapes to hand postures in a database.
+Considerable research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS), such as the grasp WS~\cite{ferrari1992, ciocarlie2009}, object WS~\cite{liu2015fast}, or task WS~\cite{kruger2011partial}.
+The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{li2005shape}.
 Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
@@
 
-Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control~\cite{brook2011collaborative, mahler2015gp, zheng2005}.
+Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control~\cite{brook2011collaborative}.
 %, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
@@
 Another line of research has focused on synthesizing grasps using statistical models learned from a database of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
-Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
-Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images based on a dataset of thousands of 1035 images annotated with parallel-jaw grasps by humans.
-Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to the demonstrations.
+%Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
+Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to demonstrations.
 Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a library of prototypical graspable point clouds, and showed that the representation could be transferred to real sensor data~\cite{detry2013learning}.
+Lenz et al.~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images based on a dataset of thousands of 1035 images annotated with parallel-jaw grasps by humans.
 Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
 The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface rendered along the surface normal.
-%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{oberlinacquiring}.
-%Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
-%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
 In comparison, we learn a model to predict a belief distribution on the probability of force closure for a parallel-jaw grasp on a new object based on similarity to prior 3D objects and grasps, and we actively choose the next grasp to evaluate using Multi-Armed Bandits.
 
-Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples~\cite{boularias2015learning, salganicoff1996active}.
+Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples~\cite{salganicoff1996active}.
 %Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
@@
 % DEEP LEARNING
-Our work also builds on recent developments from the field of shape retrieval
-\TODO{Let Matthieu provide initial version}
+To use the prior information contained in our database on a new model, we also draw on past research on 3D model similarity.
+One can separate the methods to compare 3D shapes in roughly two categories.
+On one side, some methods encode the geometric characteristics of the shape, such as its curvature or characteristics of the harmonic functions on the shape~\cite{horn1984extended, kazhdan2003rotation, bronstein2011shape}.
+hese methods mainly rely on the use of hand-design descriptors, with the notable exception of~\cite{wu20153d} which learn a CNN on the voxel representation of the shape.
+On the other hand, view-based descriptors rely on the description of rendered views of a 3D model~\cite{murase1995visual,chen2003visual}.
+One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented consistently.
+The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views, aggregating them with second CNN which learns the invariance to orientation.
+Using this method, the authors improve state of the art classification results on ModelNet40 by a large margin.
+In a different set up, a simpler average pooling of the features from different views was proposed in~\cite{aubry2015understanding}.
+We use a similar strategy by max-pooling the features, which we found to perform better than average pooling.

### 2015-09-10 ICRA2016/bandits_docs/paper.tex
Added many new figures as well as updated text. Quite a bit closer

@@
 %Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
-		\versionline{4}}
-\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Matthieu Aubry$^1$, \\
-Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
+		\versionline{6}}
+\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,3}$, \\
+Kai Kohlhoff$^4$, Torsten Kroeger$^4$, James Kuffner$^4$, Ken Goldberg$^2$
 \thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
@@
 \thanks{$^{1-2}$ University of California, Berkeley, USA}%
-\thanks{$^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
+\thanks{$^3$ Universite Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}%
+\thanks{$^4$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
 }
@@
 %\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
-
+\TODO{Convert figures to pdfs} \\
+\TODO{Trim paper to 8 pages} \\
 \input{includes/abstract}

### 2015-09-14 ICRA2016/bandits_docs/includes/abstract.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
-We develop a Multi-Armed Bandit algorithm with correlated rewards and show that learning from a large dataset of prior grasps and 3D object models can reduce the number of samples needed for robust grasp planning using our algorithm.
-To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 unique 3D object models.
-Each object is labelled with up to 250 parallel-jaw grasps and the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
-We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between 3D objects and we apply it to indexing similar objects for grasp planning at scale.
-We implement our algorithm and database using the Google Cloud Platform.
-Experiments on a set of 20 test objects suggest that the time taken to plan a robust grasp is approximately $3.5\times$ faster than Thompson sampling without prior data on average
-Experiments on sensitivity suggest that convergence rate is fastest for objects for which the MV-CNN returns geometrically similar neighbors from Dex-Net.%, and that the convergence rate can descrease if the similarity metric measures false correlations between grasps.
+We develop a Multi-Armed Bandit algorithm with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
+To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
+We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
+We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can run up to 1,500 virtual machines at a time, reducing experiment runtime by up to 1000$\times$.
+Experiments suggest that robust grasp planning is up to $3.5\times$ faster than Thompson sampling without prior data on average and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.%, and that the convergence rate can descrease if the similarity metric measures false correlations between grasps.
+We also explore sensitivity of our algorithm to similarity metrics and pose and friction uncertainty levels for test objects.
 Code, data, and additional information can be found at: \TODO{Url}

### 2015-09-14 ICRA2016/bandits_docs/includes/algorithm.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 \seclabel{algorithm}
-Our algorithm, detailed in Algorithm~\ref{alg:full}, plans a sequence of grasps with high $P_F$ for a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards and priors from the grasp and 3D object data in Dex-Net.
+Our algorithm (see Algorithm~\ref{alg:full}) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
 We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
-Next, we run MAB by selecting the next grasp to sample using Thompson sampling~\cite{laskey2015bandits}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the probability of force closure for each grasp.
+Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
 Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
+We acknowledge that many alternatives for grasp sampling exist~\cite{kroemer2010combining, montesano2012active, oberlin2015autonomously}, however in this work we are interested in studying the scaling effects for a fixed selection method.
 
@@
     \SetAlgoLined
-    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Samples $N_s$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Object Feature Map $\psi$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
+    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Samples $N_s$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Features maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
     \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}
@@
 	return $\bg_T^*$\;
-    \caption{Robust Grasp Planning With Multi-Armed Bandits Using Dex-Net 1.0}
+    \nonl {\bf Dex-Net 1.0 Algorithm}: Robust Grasp Planning Using Multi-Armed Bandits With Correlated Rewards
     \label{alg:full}
@@
 
-\subsection{Predicting Grasp Quality Using Prior Data}
-\seclabel{ccbps}
-We use Continuous Correlated Beta Processes (CCBPs) to model correlations between the $P_F$ between grasps on different objects to utilize prior grasp and object data from Dex-Net 1.0.
-CCBPS were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process.
-Such correlations may exist when the Bernoulli random variables depend on common latent factors.
-For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.
-
+\subsection{Belief Distribution Model}
+\seclabel{belief}
 Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
@@
 Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
-In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is a Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+Our belief distribution on the Bernoulli parameter $\theta_{j}$ is a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
 
@@
 \begin{align*}
-	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_k^{\alpha-1} (1 - \theta_k)^{\beta-1}
+	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
 \end{align*}
+\noindent Our Bayesian MAB algorithms updates this belief for every new force closure evaluation, converging toward a delta distribution on the true $P_F$.
+
+\subsection{Predicting Grasp Quality Using Prior Data}
+\seclabel{ccbps}
+We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net 1.0.
+CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
+In our context, two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.
 
@@
 The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
-We measure similarity as a function of the euclidean distance between the output of a set of $N_f$ feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$, where $d_m$ is the dimension of the feature space.
-Details on our feature maps are given in \secref{features} below.
+
+We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
+Our first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
+To capture local surface geometry, our second feature map $\phi_{2} = \eta$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
+To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
 Given the feature maps, we use the squared exponential kernel 
 \begin{align*}
-	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
+	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
 \end{align*}
 \noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
-The bandwidths are hyperparameters of the algorithm that might be set by cross-validation on a set of training data~\cite{rasmussen2006}.
+The bandwidths are hyperparameters of the algorithm that are be set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ for grasps under the model on a set of training data~\cite{rasmussen2006}.
 
-We form a belief distribution for each candidate grasp in $\Gamma$ based on its its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
+We form a prior belief distribution for each candidate grasp in $\Gamma$ based on its its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
 %\vspace{-2ex}
@@
 \noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled for evaluate $P_F$.
-In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree descirbed in \secref{object-similarity}.
+In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.
 Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:
@@
 	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
-	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}
+	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}.
 \end{align}
 
-\noindent Intuitively, this allows evaluations of a grasp on an object to constitute fractional evaluations of similar grasps on similar objects.
+%\subsection{Feature Representation}
+%\seclabel{features}
+%\TODO{Condense section / possibly move earlier.}
+%We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.
+%
+%\subsubsection{Grasp Parameters}
+%\seclabel{param-features}
+%Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx \in bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
+%The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
+%However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).
 
-\subsection{Feature Representation}
-\seclabel{features}
-\TODO{Condense section / possibly move earlier.}
-We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.
-
-\subsubsection{Grasp Parameters}
-\seclabel{param-features}
-Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx \in bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
-The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
-However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).
-
-\subsubsection{Local Surface Heightmaps}
-\seclabel{heightmaps}
-We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging} to capture local surface geometry.
-Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
-Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
-To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
-Then we assign the heightmap value
-\begin{align*}
-	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + s_i \bv \right) = 0
-\end{align*}
-\noindent where $s_1 = -1$, $s_2 = 1$, and $f$ is the SDF of object $\mO$. 
-We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
-\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
-Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients to form local surface normal maps $\bd_{i,x}$ and $\bd_{i,y}$.
-Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
-\caption{Three local surface heightmaps extracted on a teapot.
+%\subsubsection{Local Surface Heightmaps}
+%\seclabel{heightmaps}
+%We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging} to capture local surface geometry.
+%Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
+%Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
+%Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
+%To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
+%Then we assign the heightmap value
+%\begin{align*}
+%	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + s_i \bv \right) = 0
+%\end{align*}
+%\noindent where $s_1 = -1$, $s_2 = 1$, and $f$ is the SDF of object $\mO$. 
+%We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
+%\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
+%Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients to form local surface normal maps $\bd_{i,x}$ and $\bd_{i,y}$.
+%Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
+%
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
+%\caption{Three local surface heightmaps extracted on a teapot.
 Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
 We extract the gradients of these heightmaps as features in our robust grasp planning algorithm.}
-\figlabel{local-feature-model}
-\vspace*{-15pt}
-\end{figure}
-
-\subsubsection{Shape Features}
-\seclabel{global-sim}
-While force closure is based on local surface properties of an object around contact points, measuring global similarity may be useful because the heightmap gradients may not capture all possible contact locations for a grasp under perturbations in object and gripper pose.
-Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.
+%\figlabel{local-feature-model}
+%\vspace*{-15pt}
+%\end{figure}
+%
+%\subsubsection{Shape Features}
+%\seclabel{global-sim}
+%While force closure is based on local surface properties of an object around contact points, measuring global similarity may be useful because the heightmap gradients may not capture all possible contact locations for a grasp under perturbations in object and gripper pose.
+%Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.
 

### 2015-09-14 ICRA2016/bandits_docs/includes/conclusion.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 \seclabel{conclusion}
-We developed a Multi-Armed Bandit algorithm based on correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
-To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models, each labelled with up to 250 grasps and the probability of force closure of each.
-For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification, trained on milliions of images and thousands of 3D object examples.
+We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model withcorrelated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
+To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{su2015multi} to efficiently index similar objects.
+%For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification.
 Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
@@
 Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
-We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
-We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
+We are also interested in a pipelined approach that integrates research on deep learning to maps directly from images to motor torques that control a grasp.
+To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding, guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
+%We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
 
-Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
+In future work, we will also add grasp and object data to Dex-Net, such as more 3D models, task constraints, the outcomes of physical trials, or human annotations.
 %This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
 %Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
-We plan to add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}, and study the selection of a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
-We plan to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
+We will also explore additional analytic grasp metrics to Dex-Net such as cages~\cite{diankov2010automated}, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
+We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.
+Our goal is to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

### 2015-09-14 ICRA2016/bandits_docs/includes/dataset.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

--- 2015-09-10 ICRA2016/bandits_docs/includes/dataset.tex
@@
 
-\TODO{Make this flow with above paragraph!}
-The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
-Dex-Net consists of over 10,000 3D mesh models, selected to represent objects that might be encountered in warehousing or the home such as tableware, tools, and toys.
+%\TODO{Perhaps a cleaner transition here}
+We now extend robust grasp planning to leverage prior data from a set of objects by introducing the Dexterity Network (Dex-Net) 1.0, a growing dataset of over 10,000 prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
+The dataset is selected to represent objects that might be encountered in warehousing or the home such as containers, tools, tableware, and toys.
 %Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
 %The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
-\figref{datasets} details the data sources and their sizes.
+\tabref{datasets} details the data sources and their sizes.
 
-\begin{figure}[t!]
+{%
+\setlength{\tabcolsep}{1pt}
+
+\begin{table}[t]
 \centering
-\includegraphics[scale=0.1]{figures/dataset_table.jpg}
-\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).}
-\figlabel{datasets}
+        \begin{tabular}{L{2.5cm} || R{1.5cm} | R{1.5cm}}
+        \multicolumn{1}{c ||}{\specialcell{\bf Dataset}} & \multicolumn{1}{c |}{\specialcell{\bf \# Models}}  & \multicolumn{1}{c}{\specialcell{\bf Synthetic?}} \\
+        \hline & & \\ [-1.5ex]
+        SHREC2014~\cite{li2015comparison} & 8,987 & Y\\
+        ModelNet40~\cite{wu20153d} & $^*$2,539 & Y \\
+        3DNet~\cite{wohlkinger20123dnet} & 1,371 & Y \\
+        KIT~\cite{kasper2012kit} & 129 & N \\
+        BigBIRD~\cite{singh2014bigbird} & 120 & N \\
+        YCB~\cite{calli2015benchmarking} & 80 &  N\\
+        APC & 26 & N\\
+        \hline & & \\ [-1.5ex]
+        {\bf Total} & 13,252 & \\ 
+        \end{tabular}
+        \caption{The seven datasets used in Dex-Net 1.0 with the number of models in the dataset and whether or not the models were laser-scanned. $^*$ indicates a subset of the original dataset. }
+		\tablabel{datasets}
 \vspace*{-15pt}
-\end{figure}
+\end{table}
+}
+
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[scale=0.1]{figures/dataset_table.jpg}
+%\caption{\TODO{Remove columns}}
+%\figlabel{datasets}
+%\vspace*{-15pt}
+%\end{figure}
 
 \subsection{Data Cleaning}
-Each object in Dex-Net is originally specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
+Each object in Dex-Net is specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
 We preprocess each model by first removing unreferenced vertices and degenerate triangles.
@@
 Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
-Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{sdfgen}, an open-source C++ tool.
+Finally, we convert each mesh to an SDF using SDFGen~\cite{sdfgen}, an open-source C++ tool.
 
@@
 Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and the $P_F$ for each.
-We generate candidate grasps using a modified version of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
-Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS $ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
-To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mC$ using rejection sampling.
-Next we sample a direction $\bv \in \bS^2$ uniformly at random from the cone and compute:
+We generate $N_g$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
+Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS$ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
+To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$ using rejection sampling.
+Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute:
 %\vspace{-2ex}
@@
 This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
-We add $\bg_{i,k}$ to our candidate set if both $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.
+We add $\bg_{i,k}$ to our candidate set if the contacts are antipodal~\cite{mahler2015gp}, or $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.
 
@@
 
-\subsection{Object Similarity Embedding}
+\subsection{Grasp Differential Heightmap Features}
+\seclabel{grasp-similarity}
+To measure grasp similarity, we also embed each parallel-jaw grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation, a variant of grasp heightmaps~\cite{herzog2012template, kappler2015leveraging}.
+Let $d_h \in \mathbb{Z}$ be a number of pixels for the projection, let $\mP = \{-d_h, ..., d_h\}$ be row / column pixel indices, let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
+Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
+Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
+To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
+Then we assign
+\begin{align*}
+	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + (-1)^{i} \bv \right) = 0
+\end{align*}
+\noindent where $f$ is the SDF of object $\mO$. 
+We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
+\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
+Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
+Our full feature vector for the grasp-object pair is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$, which we store for each grasp in Dex-Net.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.325]{figures/illustrations/local_feature_model.eps}
+\caption{Illustration of three local surface heightmaps extracted on a teapot.
+Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
+We extract the gradients of these heightmaps to measure similiarity between grasps in Dex-Net.}
+\figlabel{local-feature-model}
+\vspace*{-15pt}
+\end{figure}
+
+\section{Deep Learning for Object Similarity}
 \seclabel{object-similarity}
-In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
-Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval that uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.
+In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean vector space in which similar objects will be close together.
+We use multi-view Convolutional Neural Networks (MV-CNNs)~\cite{aubry2015understanding, su2015multi}, a new method for 3D shape classification that outperforms the accuracy of previous methods by over 10\% on the ModelNet40 shape classification benchmark and uses the powerful features learned by CNNs on millions of images~\cite{krizhevsky2012imagenet}.
 
-\figref{global-feature-model} illustrates our method.
+\figref{global-feature-model} illustrates the approach.
 Let $R$ be the maximum dimension of the object bounding box.
@@
 Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
-Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output to from 4028 dimensions to 100 dimensions.
+Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4028 dimensions to 100 dimensions.
 This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
-Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.
+%Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.
 
@@
 
-%In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
-%The image classification training step had a test accuracy of 76\%.
+In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD.
+The final PCA step captured approximately 85\% of the variance of the vectors.
+The image classification training step had a test accuracy of 76\%.
+To validate our implementation, we tested our method on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.
 
@@
 \centering
-\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
+\includegraphics[scale=0.25]{figures/illustrations/cnn_model.eps}
 \caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.

### 2015-09-14 ICRA2016/bandits_docs/includes/experiments.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 \seclabel{experiments}
-\TODO{Add average convergence experiment with test set}
-\TODO{Add sensitivity to uncertainty}
 
-We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
-We created three nested training sets of 100, 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
-From the remaining objects we created a set of 20 validation objects for selecting algorithm hyperparameters and a set of 30 objects for test data.
-We ran our algorithm with $N_n = 10$ nearest neighbors.
-We also used isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+\TODO{Update results with any experiments. The current section basically reflects what we should expect but I'm running a few with slightly more test objects to see what happens}
 
-The bandwidths of our similarity kernel were constrained to be disgonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a gaussian mask $C_d$ centered on the gradient heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
-The bandwidths were selected by maximizing average convergence rate on the validation set using a grid search over hyperparameters.
+We evaluate the convergence rate of the Dex-Net 1.0 algorithm for varying sizes of prior data used from Dex-Net and explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
+We created two training sets of 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
+From the remaining objects, we created a set of 300 validation objects for selecting algorithm hyperparameters and a set of 45 test objects.
+We ran our algorithm with $N_n = 10$ nearest neighbors and used isotropic uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
 
-To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
-We used Google Compute Engine to distribute trials of MAB algorithms across objects and Google Cloud Storage (GCS) to store Dex-Net.
+The bandwidths of our similarity kernel were constrained to be diagonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a Gaussian mask $C_d$ centered on the differential heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
+The bandwidths were selected by maximizing the log likelihood of the true $P_F$ under the CCBP model on the validation set using a grid search over hyperparameters.
+
+To scale the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
+We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
 Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by over $1000\times$.
@@
 \subsection{Scaling of Average Convergence Rate}
-\TODO{Replace with test results. Current are on validation set due to time constraints}
-\TODO{Add 100 model results}
 
@@
 Our algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling over all iterations.
-Furthermore, the 10,000 object curve does not reach below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
-However, we see that on average our algorithm makes progress more slowly than Thompson sampling.
+Furthermore, the 10,000 object curve does not fall below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
+%However, we see that on average our algorithm makes progress more slowly than Thompson sampling.
 
@@
 We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
-\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the algorithms about 100 iterations.
+\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
 However, performance on the drill does not increase using either 1,000 or 10,000 objects.
 
-This behavior may be explained by the similarity of the closest nearest neighbors in Dex-Net found by our shape similiarty MV-CNN, displayed in \figref{query}.
+This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in \figref{query}.
 We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
@@
 We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
-(Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimizal grasp once 10,000 objects are used.
+(Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimial grasp once 10,000 objects are used.
 (Bottom) The drill, which is relatively rare in the dataset, has no noticeable performance increase over Thompson sampling, even with 10,000 objects.}
@@
 \seclabel{band-sens}
-We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{features}.
+We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps}.
 We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$ , as this was the most discriminative feature maps found by our hyperparameter tuning.
 \figref{bandwidth-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
-We see that increasing the bandwidth of the kernel can drastically affect the performance of the algorithm, causing the performance to be no better than uniform allocation.
+We see that increasing the bandwidth of the kernel can reduce performance to be on par with uniform allocation.
 This may be because overestimating similarities can lead to a grasp with high $P_F$ being predicted too low, or vice versa.
 One the other hand, decreasing the bandwidth also decreases the convergence rate but Algorithm~\ref{alg:full} with 10,000 prior objects still outperforms Thompson sampling.
-This suggests that a conservative setting of similiarity kernel bandwidth may be preferable for Algorithm~\ref{alg:full}.
+This suggests that a conservative setting of similiarity kernel bandwidth is important.
 
@@
 \caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
-We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
-(Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocatoin.
+(Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
 (Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
 \figlabel{bandwidth-sens}
-\vspace*{-15pt}
+\vspace*{-10pt}
 \end{figure}
 
-\section{Sensitivity to Uncertainty}
-\TODO{Write section}
+\section{Sensitivity to Pose and Friction Uncertainty}
+\seclabel{u-sens}
+We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
+We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
+The uncertainty levels used to label grasps in Dex-Net were not changed.
+\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
+The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
+Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
+\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set.
+Lower uncertainty increases the quality for all methods and higher uncertainty decreases the quality for all methods.
+Interestingly, in both cases prior data has little effect but the convergence rate is still on par with Thompson sampling with no prior data.}
+\figlabel{u-sens}
+\vspace*{-10pt}
+\end{figure}

### 2015-09-14 ICRA2016/bandits_docs/includes/introduction.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 
-``Cloud Robotics and Automation" considers a new paradigm where robots and automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
-There are several potential advantages to using the Cloud: 1) Big Data: access to updated libraries of images, maps, and object/product data, 2) Cloud Computing: access to parallel grid computing for statistical analysis, machine learning, and planning.
-These advantages have recently been highlighted in vision and speech, where datasets with millions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher} have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods~\cite{kehoe2015survey}.
+With ``Cloud Robotics and Automation," systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
+Potential advantages to using the Cloud include Big Data, or access to updated libraries of images, maps, and object/product data, and Cloud Computing, or access to parallel grid computing for statistical analysis, machine learning, and planning.
+Similar advantages have recently been used for vision and speech, where datasets with millions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher} have produced results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods~\cite{kehoe2015survey}.
 This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, environment configurations, etc.~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.
@@
 \includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
-\caption{Sample of 3D mesh models from the Dex-Net dataset.
-The dataset currently includes over 10,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}.
+\caption{Sample of 3D mesh models from the Dex-Net dataset that currently includes over 10,000 models from the KIT object database~\cite{kasper2012kit}, the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}.
 }
@@
 
-Our main contribution is a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of grasps and 3D object models.
+Our primary contribution is a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of prior grasps and 3D object models.
 Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
 
-To study scaling effects we develop Dex-Net 1.0, a new dataset of approximately 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as tooks tableware, boxes, and toys.
+To study scaling effects we develop Dex-Net 1.0, a growing dataset othat currently includes over 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
 ~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
-Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
-The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
-Dex-Net contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
-To the best of our knowledge, this is the largest dataset to-date used for grasping research.
-We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects from Dex-Net for grasp planning at scale.
+%Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
+%The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
+Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
+To the best of our knowledge, this is the largest dataset used for grasping research to-date.
+We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.
 
-We implement our algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage.
-Experiments on using our algorithm to plan parallel-jaw grasps with high probability of force closure from 250 candidates suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to identify a grasp with high quality by $3.5\times$ over a test set of 20 objects.
-Experiments on the sensitivity of our algorithm to the similarity metric suggest that measuring false simlarities can lead to a significant decrease in the convergence rate.
+We implement our algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
+Experiments on planning parallel-jaw grasps with high probability of force closure with our algorithm suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to identify a grasp with high quality by $3.5\times$.
 \TODO{Update with final results}

### 2015-09-14 ICRA2016/bandits_docs/includes/problem_statement.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 
-We consider the problem of finding a of parallel-jaw grasps with maximum probability force closure, $P_F$, on a 3D object model under uncertainty in object pose, gripper pose, and friction coefficient using a database of 3D object models annotated with grasps and the $P_F$ of each.
-We assume the object shape is exactly known and provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and negative inside the object (when the object is watertight).
-We also assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
-Furthermore, we assume soft-finger contacts between the gripper and object~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
+We consider the robust grasping problem of finding a parallel-jaw grasp with sufficient probability force closure, $P_F$, for a single 3D object model under uncertainty in object pose, gripper pose, and friction coefficient.
+We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and negative inside the object.
+The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
+Furthermore, we assume soft-finger contacts and a Coulomb friction model between the gripper and object~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
 %and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.
@@
 Let $\bg = (\bx, \bv)^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
-Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
-We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object, and assume that all points are specified with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
-Let $\mG = \{ [(\bx, \bw) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where the $\mF$ is the space of all SDFs for closed and compact surfaces.
+%Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
+We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$, and specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
+Let $\mG = \{ [(\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
 We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.
@@
 \centering
-\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.png}
-\caption{Illustration of our grasp parameterization and contact model.
+\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.eps}
+\caption{Illustration of grasp parameterization and contact model.
 (Left) We parameterize parallel-jaw grasps by the centroid of the jaws $\bx \in \mathbb{R}^3$ and approach direction, or direction along which the jaws close, $\bv \in \bS^2$.
@@
 (Right) The jaws are closed until contacting the object surface at locations $\bc_1, \bc_2 \in \mathbb{R}^3$, at which the surface has normals $\bn_1, \bn_2 \in \bS^2$.
-The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$.
-From these parameters we can derive the forces and torques that the gripper can apply to the object.
-}
+The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$.}
 \figlabel{grasp-model}
@@
 \seclabel{uncertainty}
-We assume Gaussian distribuions on 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
+We assume Gaussian distributions on 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
 Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
@@
 Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
-We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{gamma}$ samples of object pose, gripper pose, and friction, respectively. 
+We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of object pose, gripper pose, and friction coefficient, respectively. 
 %Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.
@@
 Our contact model is illustrated in the right panel of \figref{grasp-model}.
-Given a grasp $\bg$ with width $w$ on an object $\mO$ and samples of object pose, gripper pose, and friction, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface.
-Each contact $\bc_i = \bx + s_i (t_i^* - w / 2) \bv$ where
+Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface.
+Each contact $\bc_i = \bx + (-1)^{i} (t_i^* - w / 2) \bv$ where~\cite{mahler2015gp}:
+%\vspace{-1ex}
 \begin{align*}
-	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx + s_i (t - w / 2) \bv\right) = 0,
+	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx + s_i (t - w / 2) \bv\right) = 0.
 \end{align*}
-\noindent$s_1 = -1$, and $s_2 = 1$~\cite{mahler2015gp}.
 
-Given contact points, let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tanget vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
-To compute the forces that each contact can apply to the object for a sampled friction coefficient $\hat{\gamma}$, we discretize the friction cone at contact $i$~\cite{pokorny2013classical} into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bbf_{i,j} = \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \text{ for } j = 1, ..., l \right\}$.
-Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
+Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
+To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013classical} into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
+Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
 Under our soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
-Thus the set of all wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
+Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
 
@@
 \seclabel{quality}
-In this work we use the probability of force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
-While we acknowledge that deterministic force closure has not always been reported as a predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
+In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
+While we acknowledge that deterministic force closure has not always been reported as a predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use $P_F$ because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
 
-Let $F \in \{0, 1\}$ denote the occurence of force closure.
+Let $F \in \{0, 1\}$ denote the occurrence of force closure.
+Then for a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
 To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
@@
 \subsection{Objective}
-The probability of force closure for a grasp $\bg$ on object $\mO$ is $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
-We are interested in finding $\bg^*$,the grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
+We are interested in finding $\bg^*$,the grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
 To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}:

### 2015-09-14 ICRA2016/bandits_docs/includes/related_work.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 
-%For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
-Considerable research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS), such as the grasp WS~\cite{ferrari1992, ciocarlie2009}, object WS~\cite{liu2015fast}, or task WS~\cite{kruger2011partial}.
+Robust grasp planning considers the problem of finding a set of grasps for an object that may succeed over perturbations in object shape,  object pose, and environment configurations due to uncertainty resulting from imprecision in perception and control.
+Research on grasp planning for precisely known objects and environments has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS)~\cite{ferrari1992, liu2015fast}.
 The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{li2005shape}.
-Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
-The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps using the Iterated Closest Point algorithm~\cite{goldfeder2011data}.
-Research has also studied transferring grasps from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.
+To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated in GraspIt!, and matched robot sensor data to synthetic depth maps of objects in the database using Iterated Closest Point to retrieve precomputed grasps for execution on a physical robot~\cite{goldfeder2011data}.
+This led to research on methods for transferring grasps from objects in databases, such as warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.
 
-Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control~\cite{brook2011collaborative}.
+Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control.
 %, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
-Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
-Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
+Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} found that grasps ranked by probability of force closure or Ferrari-Canny quality subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
+Hsiao et al.~\cite{hsiao2011bayesian} developed a Bayesian framework for grasp success on physical robot under uncertainty in object shape, object pose, and robot control and used GraspIt!
+to estimate the probability of success on a database of 892 point clouds of 3D objects.
+%Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
 Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
@@
 
-Another line of research has focused on synthesizing grasps using statistical models learned from a database of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
+Another line of research has focused on synthesizing grasps using statistical models learned from a databse of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning} of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
 %Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
-Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to demonstrations.
-Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a library of prototypical graspable point clouds, and showed that the representation could be transferred to real sensor data~\cite{detry2013learning}.
-Lenz et al.~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images based on a dataset of thousands of 1035 images annotated with parallel-jaw grasps by humans.
+%Much research in this area has been concerned with learning a set of grasp affordance features from images~\cite{lenz2015deep, saxena2008robotic} or point clouds~\cite{detry2013learning, herzog2014learning}.
+Herzog et al.~\cite{herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to demonstrations.
 Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
-The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface rendered along the surface normal.
-In comparison, we learn a model to predict a belief distribution on the probability of force closure for a parallel-jaw grasp on a new object based on similarity to prior 3D objects and grasps, and we actively choose the next grasp to evaluate using Multi-Armed Bandits.
+The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
+In comparison, we learn a model that predicts a belief distribution on the probability of force closure for parallel-jaw grasps on a new object based on similarity to prior 3D objects and grasps, and we demonstrate that the predicted belief can be used to reduce the number samples needed to plan a robust grasp with Multi-Armed Bandits.
 
-Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples~\cite{salganicoff1996active}.
-%Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
-Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
-Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
-Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
+Our work is also closely related to research on actively sampling grasps to build a predictive model of grasp quality from fewer examples~\cite{detry2011learning, kehoe2012estimating, kroemer2010combining, salganicoff1996active}.
+%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
+%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
+%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
 %Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
@@
 Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
+However, their approach does not incorporate prior knowledge.
+Oberlin and Tellex~\cite{oberlin2015autonomously} developed a confidence-bound based Multi-Armed Bandit (MAB) algorithm for planning parallel-jaw grasps using prior information on short time horizons, but do not study the effects of orders of magnitude of prior data on convergence.
 Recently, Laskey et al.~\cite{laskey2015bandits} used Multi-Armed Bandit (MAB) algorithms to reduce the number of samples needed to identify grasps with high probability of force closure under uncertainty in object shape, pose, and friction in 2D.
 %MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
-In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net to further accelerate convergence to a grasp with high probability of force closure.
+In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high probability of force closure.
 
@@
 To use the prior information contained in our database on a new model, we also draw on past research on 3D model similarity.
-One can separate the methods to compare 3D shapes in roughly two categories.
-On one side, some methods encode the geometric characteristics of the shape, such as its curvature or characteristics of the harmonic functions on the shape~\cite{horn1984extended, kazhdan2003rotation, bronstein2011shape}.
-hese methods mainly rely on the use of hand-design descriptors, with the notable exception of~\cite{wu20153d} which learn a CNN on the voxel representation of the shape.
-On the other hand, view-based descriptors rely on the description of rendered views of a 3D model~\cite{murase1995visual,chen2003visual}.
+One line of past research has focused on encoding geometric characteristics of a shape, such as its curvature, characteristics of the harmonic functions on the shape~\cite{bronstein2011shape, horn1984extended, kazhdan2003rotation}, or using CNNs trained on a voxel representation of shapes~\cite{maturana2015voxnet, wu20153d}.
+On the other hand, view-based descriptors rely on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
 One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented consistently.
-The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views, aggregating them with second CNN which learns the invariance to orientation.
-Using this method, the authors improve state of the art classification results on ModelNet40 by a large margin.
-In a different set up, a simpler average pooling of the features from different views was proposed in~\cite{aubry2015understanding}.
-We use a similar strategy by max-pooling the features, which we found to perform better than average pooling.
+The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views, aggregating the views with a second CNN that learns the invariance to orientation.
+Using this method, the authors improve state-of-the-art classification accuracy on ModelNet40 by 10\%.
+We use a max-pooling to aggregate views, inspired by recent results using axerage pooling~\cite{aubry2015understanding} proposed a simpler average pooling of the features from different views.

### 2015-09-14 ICRA2016/bandits_docs/paper.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

@@
 
+\usepackage[switch, columnwise]{lineno}
+\linenumbers
+
 \newtheorem{lemma}{Lemma}
@@
 %Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
-		\versionline{6}}
+		\versionline{7}}
 \author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,3}$, \\
-Kai Kohlhoff$^4$, Torsten Kroeger$^4$, James Kuffner$^4$, Ken Goldberg$^2$
+Kai Kohlhoff$^4$, Torsten Kroeger$^4$, James Kuffner$^4$, Ken Goldberg$^{1,2}$
 \thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
@@
 \thanks{$^{1-2}$ University of California, Berkeley, USA}%
-\thanks{$^3$ Universite Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}%
+\thanks{$^3$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}%
 \thanks{$^4$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
@@
 %\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
-\TODO{Convert figures to pdfs} \\
 \TODO{Trim paper to 8 pages} \\
@@
 \section{Acknowledgments}
-This research was performed with UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
+This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
 The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
-We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
+We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
 

### 2015-09-15 ICRA2016/bandits_docs/includes/abstract.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 \begin{abstract}
-Recent advances in distributed computing and machine learning combined with very large datasets of images and human speech have produced a series of results that surpass decades of research in analytic methods and, in some cases, human ability.
-This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
-We develop a Multi-Armed Bandit algorithm with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
-To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
-We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
-We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can run up to 1,500 virtual machines at a time, reducing experiment runtime by up to 1000$\times$.
-Experiments suggest that robust grasp planning is up to $3.5\times$ faster than Thompson sampling without prior data on average and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.%, and that the convergence rate can descrease if the similarity metric measures false correlations between grasps.
+Advances in computing and massive datasets of images and human speech have produced recent results that surpass decades of past research on analytic methods..
+This raises the question: can Big Data and Cloud Computation produce analogous advances in robot grasping and manipulation?
+We develop an algorithm based on a Multi-Armed Bandit model with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
+To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each grasp under uncertainty in object pose, gripper pose, and friction coefficient.
+We use Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
+We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can simultaneously run up to 1,500 virtual machines, reducing experiment runtime by up to 1000$\times$.
+Experiments suggest that robust grasp planning is up to 3.5$\times$ faster than Thompson sampling without prior data and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.
 We also explore sensitivity of our algorithm to similarity metrics and pose and friction uncertainty levels for test objects.

### 2015-09-15 ICRA2016/bandits_docs/includes/algorithm.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 \seclabel{algorithm}
-Our algorithm (see Algorithm~\ref{alg:full}) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
+The Dex-Net 1.0 algorithm (see below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
 We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
@@
 Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
-We acknowledge that many alternatives for grasp sampling exist~\cite{kroemer2010combining, montesano2012active, oberlin2015autonomously}, however in this work we are interested in studying the scaling effects for a fixed selection method.
+We acknowledge alternatives for grasp selection on each iteration~\cite{kroemer2010combining, laskey2015bandits, montesano2012active, oberlin2015autonomously}, but use Thompson sampling to study the scaling effects for a fixed selection method.
 
@@
 \seclabel{belief}
-Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
+Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
+Our Bayesian MAB algorithm works by maintaining a belief on the $P_F$ for each grasp that is updated with every new force closure evaluation, assigning increasingly high probability to the true $P_F$.
 We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
 Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
-Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
-Our belief distribution on the Bernoulli parameter $\theta_{j}$ is a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution on the Bernoulli parameter $\theta_{j}$ using a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
 
-\vspace{-2ex}
+\vspace{-4ex}
 \begin{align*}
-	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
+	\betadist(\alpha, \beta) = \left( 1 / B(\alpha, \beta) \right) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
 \end{align*}
-\noindent Our Bayesian MAB algorithms updates this belief for every new force closure evaluation, converging toward a delta distribution on the true $P_F$.
+\noindent where $B$ is a normalization constant.
 
@@
 \noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
-The bandwidths are hyperparameters of the algorithm that are be set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ for grasps under the model on a set of training data~\cite{rasmussen2006}.
+The bandwidths are hyperparameters of the algorithm that are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.
 

### 2015-09-15 ICRA2016/bandits_docs/includes/conclusion.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 \seclabel{conclusion}
-We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model withcorrelated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
-To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{su2015multi} to efficiently index similar objects.
+We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model with correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
+To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{aubry2015understanding, su2015multi} to efficiently index similar objects.
 %For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification.
@@
 Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
-We are also interested in a pipelined approach that integrates research on deep learning to maps directly from images to motor torques that control a grasp.
-To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding, guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
+We are also interested in an end-to-end approach that integrates research on deep learning to map directly from images to motor torques that control a grasp.
+To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
 %We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
@@
 %Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
-We will also explore additional analytic grasp metrics to Dex-Net such as cages~\cite{diankov2010automated}, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
+We will also explore additional analytic grasp metrics to Dex-Net such as cages, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
 We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.

### 2015-09-15 ICRA2016/bandits_docs/includes/dataset.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 %\TODO{Perhaps a cleaner transition here}
-We now extend robust grasp planning to leverage prior data from a set of objects by introducing the Dexterity Network (Dex-Net) 1.0, a growing dataset of over 10,000 prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
-The dataset is selected to represent objects that might be encountered in warehousing or the home such as containers, tools, tableware, and toys.
-%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
-%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
-\tabref{datasets} details the data sources and their sizes.
+We extend robust grasp planning to leverage prior data from a set of objects by introducing the Dexterity Network (Dex-Net) 1.0, a growing dataset of over 10,000 prior 3D object models annotated with 2.5 million parallel-jaw grasps.
+Dex-Net 1.0 contains 13,252 models from the following sources: 8,987 from the SHREC 2014 challenge dataset~\cite{li2015comparison}, 2,539 from ModelNet40~\cite{wu20153d}, 1,371 from 3DNet~\cite{wohlkinger20123dnet}, 129 from the KIT object database~\cite{kasper2012kit}, 120 from BigBIRD~\cite{singh2014bigbird}, 80 from the Yale-CMU-Berkeley dataset~\cite{calli2015benchmarking}, and 26 from the Amazon Picking Challenge scans.
 
-{%
-\setlength{\tabcolsep}{1pt}
+%\tabref{datasets} details the data sources and their sizes.
 
-\begin{table}[t]
-\centering
-        \begin{tabular}{L{2.5cm} || R{1.5cm} | R{1.5cm}}
-        \multicolumn{1}{c ||}{\specialcell{\bf Dataset}} & \multicolumn{1}{c |}{\specialcell{\bf \# Models}}  & \multicolumn{1}{c}{\specialcell{\bf Synthetic?}} \\
-        \hline & & \\ [-1.5ex]
-        SHREC2014~\cite{li2015comparison} & 8,987 & Y\\
-        ModelNet40~\cite{wu20153d} & $^*$2,539 & Y \\
-        3DNet~\cite{wohlkinger20123dnet} & 1,371 & Y \\
-        KIT~\cite{kasper2012kit} & 129 & N \\
-        BigBIRD~\cite{singh2014bigbird} & 120 & N \\
-        YCB~\cite{calli2015benchmarking} & 80 &  N\\
-        APC & 26 & N\\
-        \hline & & \\ [-1.5ex]
-        {\bf Total} & 13,252 & \\ 
-        \end{tabular}
-        \caption{The seven datasets used in Dex-Net 1.0 with the number of models in the dataset and whether or not the models were laser-scanned. $^*$ indicates a subset of the original dataset. }
-		\tablabel{datasets}
-\vspace*{-15pt}
-\end{table}
+%{%
+%\setlength{\tabcolsep}{1pt}
+%
+%\begin{table}[t]
+%\centering
+%        \begin{tabular}{L{2.5cm} || R{1.5cm} | R{1.5cm}}
+%        \multicolumn{1}{c ||}{\specialcell{\bf Dataset}} & \multicolumn{1}{c |}{\specialcell{\bf \# Models}}  & \multicolumn{1}{c}{\specialcell{\bf Synthetic?}} \\
+%        \hline & & \\ [-1.5ex]
+%        SHREC2014~\cite{li2015comparison} & 8,987 & Y\\
+%        ModelNet40~\cite{wu20153d} & $^*$2,539 & Y \\
+%        3DNet~\cite{wohlkinger20123dnet} & 1,371 & Y \\
+%        KIT~\cite{kasper2012kit} & 129 & N \\
+%        BigBIRD~\cite{singh2014bigbird} & 120 & N \\
+%        YCB~\cite{calli2015benchmarking} & 80 &  N\\
+%        APC & 26 & N\\
+%        \hline & & \\ [-1.5ex]
+%        {\bf Total} & 13,252 & \\ 
+%        \end{tabular}
+%        \caption{The seven datasets used in Dex-Net 1.0 with the number of models in the dataset and whether or not the models were laser-scanned.
+The $^*$ indicates a subset of the original dataset.
 }
+%		\tablabel{datasets}
+%\vspace*{-15pt}
+%\end{table}
+%}
 
@@
 \subsection{Data Cleaning}
-Each object in Dex-Net is specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
-We preprocess each model by first removing unreferenced vertices and degenerate triangles.
-Next, we compute the object reference frame by performing Principal Component Analysis (PCA) on the vertices of the mesh and aligning the $z$-axis with the first principal component and the $y$-axis with the second principal component
-We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
-Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
-Finally, we convert each mesh to an SDF using SDFGen~\cite{sdfgen}, an open-source C++ tool.
+Each object in Dex-Net is specified as a 3D mesh.
+We preprocess each mesh by removing unreferenced vertices, computing a reference frame with Principal Component Analysis (PCA) on the mesh vertices, setting the mesh center of mass $\bz$ to the center of the mesh bounding box, and rescaling the synthetic meshes to fit the smallest dimension of the mesh bounding box within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
+We also convert each mesh to an SDF $f$ using SDFGen~\cite{sdfgen}.
 
@@
 \seclabel{grasp-sampling}
-Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and the $P_F$ for each.
+Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and their $P_F$.
 We generate $N_g$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
@@
 To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$ using rejection sampling.
-Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute:
-%\vspace{-2ex}
-\begin{align*}
-	\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv  &&  \bx = 0.5 (\bc_1 + \bc_2)
-\end{align*}
-\noindent where $t_2^*$ is defined in \secref{contact}.
+Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute $\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv$ and $\bx = 0.5 (\bc_1 + \bc_2)$, where $t_2^*$ is defined in \secref{contact}.
 This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
@@
 
-We then evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
-Formally, our full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in our Grasp Moduli Space.
+We evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
+Our full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.
 
@@
 \seclabel{grasp-similarity}
-To measure grasp similarity, we also embed each parallel-jaw grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation, a variant of grasp heightmaps~\cite{herzog2012template, kappler2015leveraging}.
+To measure grasp similarity, we embed each parallel-jaw grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation, a variant of grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
 Let $d_h \in \mathbb{Z}$ be a number of pixels for the projection, let $\mP = \{-d_h, ..., d_h\}$ be row / column pixel indices, let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
-Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
-To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
-Then we assign
+%Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
+Our heightmap at contact $\bc_i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane to the grasp axis $\bv$ specified by $\bt_1, \bt_2$ to the distance to the surface along $\bv$.
+To compute the heightmap value at pixel $u,v \in \mP$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
 \begin{align*}
-	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + (-1)^{i} \bv \right) = 0
+	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + (-1)^{i} t \bv \right) = 0
 \end{align*}
 \noindent where $f$ is the SDF of object $\mO$. 
-We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
+We make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{salti2014shot}.
 \figref{local-feature-model} illustrates local surface patches extracted by this procedure.
-Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
-Our full feature vector for the grasp-object pair is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$, which we store for each grasp in Dex-Net.
+Since force closure depends on object surface normals at contacts~\cite{pokorny2013c}, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
+Our full feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
 
@@
 \centering
-\includegraphics[scale=0.325]{figures/illustrations/local_feature_model.eps}
+\includegraphics[scale=0.30]{figures/illustrations/local_feature_model.eps}
 \caption{Illustration of three local surface heightmaps extracted on a teapot.
-Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
-We extract the gradients of these heightmaps to measure similiarity between grasps in Dex-Net.}
+Each heightmap is ``rendered" along the grasp axis $\bv_i$ at contact $\bc_i$ and oriented by the directions of maximum variation in the heightmap.
+We use gradients of the heightmaps for similiarity between grasps in Dex-Net.}
 \figlabel{local-feature-model}
@@
 \seclabel{object-similarity}
-In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean vector space in which similar objects will be close together.
-We use multi-view Convolutional Neural Networks (MV-CNNs)~\cite{aubry2015understanding, su2015multi}, a new method for 3D shape classification that outperforms the accuracy of previous methods by over 10\% on the ModelNet40 shape classification benchmark and uses the powerful features learned by CNNs on millions of images~\cite{krizhevsky2012imagenet}.
-
-\figref{global-feature-model} illustrates the approach.
-Let $R$ be the maximum dimension of the object bounding box.
-We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$.
+We use Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{aubry2015understanding, su2015multi} to efficiently index prior 3D object and grasp data from Dex-Net by embedding each object in a vector space where distance represents object similarity, as shown in \figref{global-feature-model}.
+We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$, where $R$ is the maximum dimension of the object bounding box.
 Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
@@
 Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
-Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4028 dimensions to 100 dimensions.
+Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4,096 dimensions to 100 dimensions.
 This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
@@
 For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
-
 In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD.
-The final PCA step captured approximately 85\% of the variance of the vectors.
-The image classification training step had a test accuracy of 76\%.
+%The final PCA step captured approximately 85\% of the variance of the vectors.
+%The image classification training step had a test accuracy of 76\%.
 To validate our implementation, we tested our method on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.
@@
 \centering
-\includegraphics[scale=0.25]{figures/illustrations/cnn_model.eps}
+\includegraphics[scale=0.275]{figures/illustrations/cnn_model.eps}
 \caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.

### 2015-09-15 ICRA2016/bandits_docs/includes/experiments.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 The bandwidths of our similarity kernel were constrained to be diagonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a Gaussian mask $C_d$ centered on the differential heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
-The bandwidths were selected by maximizing the log likelihood of the true $P_F$ under the CCBP model on the validation set using a grid search over hyperparameters.
+The bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
 
@@
 \centering
-\includegraphics[scale=0.45]{figures/illustrations/avg_reward.eps}
+\includegraphics[scale=0.40]{figures/illustrations/avg_reward.eps}
 \caption{Average normalized grasp quality versus iteration over 20 validation objects and 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
@@
 \figlabel{avg-reward}
-\vspace*{-15pt}
+\vspace*{-10pt}
 \end{figure}
@@
 \seclabel{shape-sens}
-To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of the only drill in Dex-Net and a spray bottle, which is an uncommon object category but has a few examples in Dex-Net.
-~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
+To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
+The bottom panel~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
 We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
+This convergence may be explained by the two similar spray bottles retrieved by our MV-CNN from the 10,000 object dataset.
 \figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
-However, performance on the drill does not increase using either 1,000 or 10,000 objects.
+However, performance on the drill does not increase using either 1,000 or 10,000 objects, as the closest model in all of Dex-Net according to our similarity metric is a phone.
 
-This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in \figref{query}.
-We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
-On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.
+%This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in the top panel of \figref{query}.
+%We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
+%On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.
 
@@
 \centering
-\includegraphics[scale=0.31]{figures/illustrations/avg_reward_drill.eps}
-\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net on a spray bottle (top) and drill (bottom).
+\includegraphics[scale=0.22]{figures/illustrations/avg_reward_w_neighbors.eps}
+\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net and illustrations of five nearest neighbors in Dex-Net for a spray bottle (left) and drill (right).
 We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
-(Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimial grasp once 10,000 objects are used.
-(Bottom) The drill, which is relatively rare in the dataset, has no noticeable performance increase over Thompson sampling, even with 10,000 objects.}
+(Top-left) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set.
+(Bottom-left) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp once 10,000 objects are used.
+(Top-right) The drill, which is relatively rare in the dataset, has not geometrically similar neighbors even with 10,000 objects.
+(Bottom-right) This leads to no noticeable performance increase over Thompson sampling.}
 \figlabel{avg-reward-obj}
@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[scale=0.38]{figures/illustrations/nearest_neighbors.eps}
-\caption{Illustration of the five nearest neighbor objects from Dex-Net to the spray bottle and drill using the multi-view CNN-based shape embedding and Euclidean distance for size 1,000 and 10,000 datasets from Dex-Net.
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[scale=0.38]{figures/illustrations/nearest_neighbors.eps}
+%\caption{Illustration of the five nearest neighbor objects from Dex-Net to the spray bottle and drill using the multi-view CNN-based shape embedding and Euclidean distance for size 1,000 and 10,000 datasets from Dex-Net.
 We see that for the 1,000 object dataset neither model has relevant neighbors, while for the 10,000 object dataset two other spray bottles are returned.
@@
 }
-\figlabel{query}
-\vspace*{-5pt}
-\end{figure}
+%\figlabel{query}
+%\vspace*{-5pt}
+%\end{figure}
 
-\section{Sensitivity to Similarity Kernel Bandwidth}
+\subsection{Sensitivity to Similarity, Pose and Friction Uncertainty}
 \seclabel{band-sens}
-We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps}.
-We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$ , as this was the most discriminative feature maps found by our hyperparameter tuning.
-\figref{bandwidth-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
-We see that increasing the bandwidth of the kernel can reduce performance to be on par with uniform allocation.
-This may be because overestimating similarities can lead to a grasp with high $P_F$ being predicted too low, or vice versa.
-One the other hand, decreasing the bandwidth also decreases the convergence rate but Algorithm~\ref{alg:full} with 10,000 prior objects still outperforms Thompson sampling.
-This suggests that a conservative setting of similiarity kernel bandwidth is important.
+We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
+We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$, and tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
+\figref{bnu-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
+The results suggest that conservative setting of similiarity kernel bandwidth is important for convergence, and a mismatch between the the uncertainty levels for a test object and the labels in Dex-Net diminishes the effects of scaling with prior data.
 
@@
 \centering
-\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
-\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
+\includegraphics[scale=0.23]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
+\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
+with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
+(Top-left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
+(Top-right) A lower kernel bandwith decreases the convergence rate, but the Dex-Net Algorithm still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.
+(Bottom-left) Lower uncertainty increases the quality for all methods and (bottom-right) higher uncertainty decreases the quality for all methods.
+Interestingly, for variation in pose and friction uncertainty the convergence rate is still on par with Thompson sampling with no prior data.
+}
+\figlabel{bnu-sens}
+\vspace*{-15pt}
+\end{figure}
+
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
+%\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
 (Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
 (Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
-\figlabel{bandwidth-sens}
-\vspace*{-10pt}
-\end{figure}
+%\figlabel{bandwidth-sens}
+%\vspace*{-10pt}
+%\end{figure}
 
-\section{Sensitivity to Pose and Friction Uncertainty}
-\seclabel{u-sens}
-We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
-We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
-The uncertainty levels used to label grasps in Dex-Net were not changed.
-\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
-The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
-Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.
+%\subsection{Sensitivity to Pose and Friction Uncertainty}
+%\seclabel{u-sens}
+%We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
+%We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
+%The uncertainty levels used to label grasps in Dex-Net were not changed.
+%\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
+%The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
+%Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.
 
-\begin{figure}[t!]
-\centering
-\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
-\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set.
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
+%\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set.
 Lower uncertainty increases the quality for all methods and higher uncertainty decreases the quality for all methods.
 Interestingly, in both cases prior data has little effect but the convergence rate is still on par with Thompson sampling with no prior data.}
-\figlabel{u-sens}
-\vspace*{-10pt}
-\end{figure}
+%\figlabel{u-sens}
+%\vspace*{-10pt}
+%\end{figure}

### 2015-09-15 ICRA2016/bandits_docs/includes/introduction.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 
-With ``Cloud Robotics and Automation," systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
-Potential advantages to using the Cloud include Big Data, or access to updated libraries of images, maps, and object/product data, and Cloud Computing, or access to parallel grid computing for statistical analysis, machine learning, and planning.
-Similar advantages have recently been used for vision and speech, where datasets with millions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher} have produced results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods~\cite{kehoe2015survey}.
-This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, environment configurations, etc.~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.
+Cloud-based Robotics and Automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
+Potential advantages to using the Cloud include Big Data: access to updated libraries of images, maps, and object/product data; and Parallel Computation: access to parallel grid computing for statistical analysis, machine learning, and planning~\cite{kehoe2015survey}.
+The advantages have recently been used in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
+This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, and environment configurations~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.
 
@@
 \centering
-\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
-\caption{Sample of 3D mesh models from the Dex-Net dataset that currently includes over 10,000 models from the KIT object database~\cite{kasper2012kit}, the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}.
+\includegraphics[scale=0.08]{figures/dexnet_collage.jpg}
+\caption{Sample of 3D mesh models from the Dex-Net dataset that currently includes over 10,000 models from the KIT object database~\cite{kasper2012kit}, the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20153d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}.
 }
@@
 
-Our primary contribution is a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of prior grasps and 3D object models.
+Our primary contribution is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
 Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
 
-To study scaling effects we develop Dex-Net 1.0, a growing dataset othat currently includes over 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
+To study scaling effects we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
 ~\figref{dexnet-teaser} shows a sample of the objects in the dataset.

### 2015-09-15 ICRA2016/bandits_docs/includes/problem_statement.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 
-We consider the robust grasping problem of finding a parallel-jaw grasp with sufficient probability force closure, $P_F$, for a single 3D object model under uncertainty in object pose, gripper pose, and friction coefficient.
-We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and negative inside the object.
+We consider the robust grasp planning problem for a single 3D object model and parallel-jaw grippers using probability force closure, $P_F$,  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
+We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within.
 The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
-Furthermore, we assume soft-finger contacts and a Coulomb friction model between the gripper and object~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
+We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
 %and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.
@@
 \seclabel{grasp-param}
-Our grasping parameterization is illustrated in~\figref{grasp-model}.
-Let $\bg = (\bx, \bv)^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
+Our grasp parameterization is illustrated in~\figref{grasp-model}.
+Let $\bg = (\bx, \bv)$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
 %Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
 We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$, and specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
-Let $\mG = \{ [(\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
+Let $\mG = \{ (\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
 We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.
@@
 \centering
-\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.eps}
+\includegraphics[scale=0.44]{figures/illustrations/dexnet_grasping_model.eps}
 \caption{Illustration of grasp parameterization and contact model.
 (Left) We parameterize parallel-jaw grasps by the centroid of the jaws $\bx \in \mathbb{R}^3$ and approach direction, or direction along which the jaws close, $\bv \in \bS^2$.
-The grasp parameters $\bx$ and $\bv$ are specified with respect to a coordinate frame located at the object center of mass $\bz$ and oriented along the principal directions of the object.
+The parameters $\bx$ and $\bv$ are specified with respect to a coordinate frame at the object center of mass $\bz$ and oriented along the principal directions of the object.
 (Right) The jaws are closed until contacting the object surface at locations $\bc_1, \bc_2 \in \mathbb{R}^3$, at which the surface has normals $\bn_1, \bn_2 \in \bS^2$.
-The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$.}
+The contacts are used to compute the moment arms $\rho_i = \bc_i - \bz$.
+% and $\rho_2  = \bc_2 - \bz$.
+}
 \figlabel{grasp-model}
@@
 \seclabel{uncertainty}
-We assume Gaussian distributions on 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
+We assume Gaussian distributions on object pose, gripper pose, and friction coefficient.
 Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
-Following the model of Barfoot and Furgale~\cite{barfoot2014associating}, we define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
+We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
 Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote a Gaussian distribution on gripper pose with mean $\mu_{\nu} \in \mG$.
@@
 \seclabel{contact}
-Our contact model is illustrated in the right panel of \figref{grasp-model}.
-Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface.
+%Our contact model is illustrated in the right panel .
+Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface as shown in \figref{grasp-model}.
 Each contact $\bc_i = \bx + (-1)^{i} (t_i^* - w / 2) \bv$ where~\cite{mahler2015gp}:
@@
 \begin{align*}
-	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx + s_i (t - w / 2) \bv\right) = 0.
+	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (t - w / 2) \bv\right) = 0.
 \end{align*}
-
-Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
-To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013classical} into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
-Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
+\noindent Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
+To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
+Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.
 Under our soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
@@
 \seclabel{quality}
-In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
-While we acknowledge that deterministic force closure has not always been reported as a predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use $P_F$ because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
+In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as our quality metric.
+$P_F$ has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
 
@@
 \subsection{Objective}
-We are interested in finding $\bg^*$,the grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
-To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}:
-
-\vspace{-2ex}
-\begin{align}
-	\underset{g_{I(1)}, ..., g_{I(T)} \in \mG}{\text{maximize }} \sum \limits_{t=1}^T P_F(g_{I(t)}). \label{eq:objective}
-\end{align}
-\noindent where $I(i)$ denotes the grasp selected at time $t$.
-
-As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits(MAB) ~\cite{laskey2015bandits}.
+We are interested in finding $\bg^*$, the grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
+To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
+As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
 In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the samples needed to converge to $\bg^*$.

### 2015-09-15 ICRA2016/bandits_docs/includes/related_work.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 Robust grasp planning considers the problem of finding a set of grasps for an object that may succeed over perturbations in object shape,  object pose, and environment configurations due to uncertainty resulting from imprecision in perception and control.
-Research on grasp planning for precisely known objects and environments has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS)~\cite{ferrari1992, liu2015fast}.
-The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{li2005shape}.
-To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated in GraspIt!, and matched robot sensor data to synthetic depth maps of objects in the database using Iterated Closest Point to retrieve precomputed grasps for execution on a physical robot~\cite{goldfeder2011data}.
-This led to research on methods for transferring grasps from objects in databases, such as warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.
+Research on grasp planning for precisely known objects and environments has largely focused on finding grasps by maximizing an analytic grasp quality metric based on a Wrench Space (WS)~\cite{pokorny2013c}.
+The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{bohg2014data}.
+To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated in GraspIt!.
+%, and matched robot sensor data to synthetic depth maps of objects in the database using Iterated Closest Point to retrieve precomputed grasps for execution on a physical robot~\cite{goldfeder2011data}.
+This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
 
-Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control.
-%, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
-Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} found that grasps ranked by probability of force closure or Ferrari-Canny quality subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics.
-Hsiao et al.~\cite{hsiao2011bayesian} developed a Bayesian framework for grasp success on physical robot under uncertainty in object shape, object pose, and robot control and used GraspIt!
-to estimate the probability of success on a database of 892 point clouds of 3D objects.
-%Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
-Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
-The authors found that the full system of object recognition, pose estimation, and grasp execution successfully grasped objects on a table in 80\% of trials.
+Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
+Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic WS metrics.
+Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.
 
-Another line of research has focused on synthesizing grasps using statistical models learned from a databse of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning} of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
-%Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
-%Much research in this area has been concerned with learning a set of grasp affordance features from images~\cite{lenz2015deep, saxena2008robotic} or point clouds~\cite{detry2013learning, herzog2014learning}.
-Herzog et al.~\cite{herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to demonstrations.
+Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps decided by humans~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
 Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
 The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
-In comparison, we learn a model that predicts a belief distribution on the probability of force closure for parallel-jaw grasps on a new object based on similarity to prior 3D objects and grasps, and we demonstrate that the predicted belief can be used to reduce the number samples needed to plan a robust grasp with Multi-Armed Bandits.
+In comparison, we learn a model predictive model of $P_F$ for parallel-jaw grasps on a new object based on similarity to prior 3D objects and grasps, and use our model for robust grasp planning with Multi-Armed Bandits (MAB).
 
-Our work is also closely related to research on actively sampling grasps to build a predictive model of grasp quality from fewer examples~\cite{detry2011learning, kehoe2012estimating, kroemer2010combining, salganicoff1996active}.
+Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
 %Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
@@
 %Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
-Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
-However, their approach does not incorporate prior knowledge.
-Oberlin and Tellex~\cite{oberlin2015autonomously} developed a confidence-bound based Multi-Armed Bandit (MAB) algorithm for planning parallel-jaw grasps using prior information on short time horizons, but do not study the effects of orders of magnitude of prior data on convergence.
-Recently, Laskey et al.~\cite{laskey2015bandits} used Multi-Armed Bandit (MAB) algorithms to reduce the number of samples needed to identify grasps with high probability of force closure under uncertainty in object shape, pose, and friction in 2D.
+Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
+Oberlin and Tellex~\cite{oberlin2015autonomously} developed a confidence-bound based MAB algorithm for planning parallel-jaw grasps using prior information on short time horizons, but do not study the effects of orders of magnitude of prior data on convergence.
+Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
 %MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
-In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high probability of force closure.
+In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.
 
 % DEEP LEARNING
-To use the prior information contained in our database on a new model, we also draw on past research on 3D model similarity.
-One line of past research has focused on encoding geometric characteristics of a shape, such as its curvature, characteristics of the harmonic functions on the shape~\cite{bronstein2011shape, horn1984extended, kazhdan2003rotation}, or using CNNs trained on a voxel representation of shapes~\cite{maturana2015voxnet, wu20153d}.
-On the other hand, view-based descriptors rely on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
-One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented consistently.
-The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views, aggregating the views with a second CNN that learns the invariance to orientation.
+To use the prior information contained in Dex-Net, we also draw on research on 3D model similarity.
+One line of research has focused on shape geometry, such as characteristics of harmonic functions on the shape~\cite{bronstein2011shape}, or CNNs trained on a voxel representation of shape~\cite{maturana2015voxnet, wu20153d}.
+Onother line of research relies on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
+One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented inconsistently.
+The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views and aggregating them with a second CNN that learns the invariance to orientation.
 Using this method, the authors improve state-of-the-art classification accuracy on ModelNet40 by 10\%.
-We use a max-pooling to aggregate views, inspired by recent results using axerage pooling~\cite{aubry2015understanding} proposed a simpler average pooling of the features from different views.
+We use a max-pooling to aggregate views, similar to the average pooling proposed in~\cite{aubry2015understanding}.
+% proposed a simpler average pooling of the features from different views.

### 2015-09-15 ICRA2016/bandits_docs/paper.tex
First 8 page version ready with fb from Mel and Mathieu as well

@@
 \usepackage[switch, columnwise]{lineno}
-\linenumbers
+%\linenumbers
+
+%\benkhide
 
@@
 \begin{document}
-\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale
-%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
-		\versionline{7}}
-\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,3}$, \\
-Kai Kohlhoff$^4$, Torsten Kroeger$^4$, James Kuffner$^4$, Ken Goldberg$^{1,2}$
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
-\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
-\thanks{$^{1-2}$ University of California, Berkeley, USA}%
-\thanks{$^3$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}%
-\thanks{$^4$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
+\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and a Multi-Armed Bandit Model with Correlated Rewards to Accelerate Robust Grasp Planning
+	%\vspace{-2ex}
+	\versionline{9}}
+\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
+Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
+%\vspace{-2ex}
+\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
+%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
+%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
+\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
+\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
 }
@@
 %\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
-\TODO{Trim paper to 8 pages} \\
+\TODO{Trim paper to 8 pages}
 \input{includes/abstract}
@@
 \section{Acknowledgments}
-This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
+{\small
+This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
 The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
 We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
+}
 

### 2015-09-15 ICRA2016/bandits_docs/includes/abstract.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 \begin{abstract}
-Advances in computing and massive datasets of images and human speech have produced recent results that surpass decades of past research on analytic methods..
-This raises the question: can Big Data and Cloud Computation produce analogous advances in robot grasping and manipulation?
-We develop an algorithm based on a Multi-Armed Bandit model with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
-To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each grasp under uncertainty in object pose, gripper pose, and friction coefficient.
-We use Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
-We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can simultaneously run up to 1,500 virtual machines, reducing experiment runtime by up to 1000$\times$.
-Experiments suggest that robust grasp planning is up to 3.5$\times$ faster than Thompson sampling without prior data and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.
-We also explore sensitivity of our algorithm to similarity metrics and pose and friction uncertainty levels for test objects.
-Code, data, and additional information can be found at: \TODO{Url}
+This paper presents Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and cloud computation on robust grasp planning. 
+The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models in a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps.
+Each grasp includes an estimate of the probability of force closure under uncertainty in object and gripper pose and friction.
+Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
+Experiments suggest that prior data can speed robust grasp planning by a factor of up to 3 and that average grasp quality increases with the number of similar objects in the dataset.
+We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
+Code, data, and additional information can be found at: \TODO{Url}.
 \end{abstract}

### 2015-09-15 ICRA2016/bandits_docs/includes/algorithm.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
-Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
-Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
-We acknowledge alternatives for grasp selection on each iteration~\cite{kroemer2010combining, laskey2015bandits, montesano2012active, oberlin2015autonomously}, but use Thompson sampling to study the scaling effects for a fixed selection method.
+Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from the uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
+Finally, we rank the grasps in $\Gamma$ by the maximum $p$-lower confidence bound, a conservative estimate of the $P_F$ of each grasp, and store the ranking in the database.
+We use Thompson sampling to study the scaling effects for a fixed grasp selection method and plan to study other methods based on confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.
 
@@
 Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
-Our Bayesian MAB algorithm works by maintaining a belief on the $P_F$ for each grasp that is updated with every new force closure evaluation, assigning increasingly high probability to the true $P_F$.
 We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
-Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
-Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution on the Bernoulli parameter $\theta_{j}$ using a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+Under the model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
+Since $\theta_j$ is unknown, the algorithm maintains a posterior Beta belief distribution on the Bernoulli parameter $\theta_{j}$ that is updated with every new observation of $F$, assigning increasingly high probability to the true $P_F$.
+The Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits} is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
 
@@
 \seclabel{ccbps}
-We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net 1.0.
+We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net.
 CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
-In our context, two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.
+Two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.
 
@@
 We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
-Our first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
-To capture local surface geometry, our second feature map $\phi_{2} = \eta$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
+The first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
+To capture local surface geometry, the second feature map $\phi_{2}(\mY) = \eta(\bg, \mO)$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
 To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
@@
 \end{align*}
-\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
-The bandwidths are hyperparameters of the algorithm that are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.
+\noindent where $C_m \in \bR^{d_m \times d_m}$ is the inverse bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^T C_m \by$.
+The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.
 

### 2015-09-15 ICRA2016/bandits_docs/includes/conclusion.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

--- 2015-09-10 ICRA2016/bandits_docs/includes/conclusion.tex
@@
 \seclabel{conclusion}
-We developed a Multi-Armed Bandit algorithm based on correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
-To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models, each labelled with up to 250 grasps and the probability of force closure of each.
-For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification, trained on milliions of images and thousands of 3D object examples.
-Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
+We presented Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning.
+The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models and Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects.
+In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
+Experiments suggest that prior data can speed robust grasp planning by a factor of 3 and that average grasp quality increases with the number of similar objects in the dataset.
+We reported on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
 
-One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
-Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
-We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
-We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
+In future work, we will develop metrics to pre-compute grasps that adequately "cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
+We will also explore how Deep Learning~\cite{krizhevsky2012imagenet} can be used in other parts of a grasp planning pipeline, for example to recognize object pose and shape from images~\cite{aubry2015understanding}, to learn grasp and object features robust to shape variation using prior evaluations from bandit algorithms, and perhaps even to determine motor torques based on images and precomputed grasps~\cite{levine2015end}.
+We also hope to release subsets of Dex-Net 1.0 with an open-source API to explore robust grasping as a service (RGaaS).
 
-Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
-%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
-%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
-We plan to add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}, and study the selection of a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
-We plan to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
+%We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model with correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
+%To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{aubry2015understanding, su2015multi} to efficiently index similar objects.
+%Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
+%
+%One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
+%Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
+%We are also interested in an end-to-end approach that integrates research on deep learning to map directly from images to motor torques that control a grasp.
+%To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
+%%We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
+%
+%In future work, we will also add grasp and object data to Dex-Net, such as more 3D models, task constraints, the outcomes of physical trials, or human annotations.
+%%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
+%%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
+%We will also explore additional analytic grasp metrics to Dex-Net such as cages, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
+%We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.
+%Our goal is to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
+%

### 2015-09-15 ICRA2016/bandits_docs/includes/dataset.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 
-%\TODO{Perhaps a cleaner transition here}
-We extend robust grasp planning to leverage prior data from a set of objects by introducing the Dexterity Network (Dex-Net) 1.0, a growing dataset of over 10,000 prior 3D object models annotated with 2.5 million parallel-jaw grasps.
+The Dexterity Network (Dex-Net) 1.0 dataset is a growing set that currently includes over 10,000 prior 3D object models annotated with 2.5 million parallel-jaw grasps.
 Dex-Net 1.0 contains 13,252 models from the following sources: 8,987 from the SHREC 2014 challenge dataset~\cite{li2015comparison}, 2,539 from ModelNet40~\cite{wu20153d}, 1,371 from 3DNet~\cite{wohlkinger20123dnet}, 129 from the KIT object database~\cite{kasper2012kit}, 120 from BigBIRD~\cite{singh2014bigbird}, 80 from the Yale-CMU-Berkeley dataset~\cite{calli2015benchmarking}, and 26 from the Amazon Picking Challenge scans.
-
-%\tabref{datasets} details the data sources and their sizes.
-
-%{%
-%\setlength{\tabcolsep}{1pt}
-%
-%\begin{table}[t]
-%\centering
-%        \begin{tabular}{L{2.5cm} || R{1.5cm} | R{1.5cm}}
-%        \multicolumn{1}{c ||}{\specialcell{\bf Dataset}} & \multicolumn{1}{c |}{\specialcell{\bf \# Models}}  & \multicolumn{1}{c}{\specialcell{\bf Synthetic?}} \\
-%        \hline & & \\ [-1.5ex]
-%        SHREC2014~\cite{li2015comparison} & 8,987 & Y\\
-%        ModelNet40~\cite{wu20153d} & $^*$2,539 & Y \\
-%        3DNet~\cite{wohlkinger20123dnet} & 1,371 & Y \\
-%        KIT~\cite{kasper2012kit} & 129 & N \\
-%        BigBIRD~\cite{singh2014bigbird} & 120 & N \\
-%        YCB~\cite{calli2015benchmarking} & 80 &  N\\
-%        APC & 26 & N\\
-%        \hline & & \\ [-1.5ex]
-%        {\bf Total} & 13,252 & \\ 
-%        \end{tabular}
-%        \caption{The seven datasets used in Dex-Net 1.0 with the number of models in the dataset and whether or not the models were laser-scanned.
-The $^*$ indicates a subset of the original dataset.
-}
-%		\tablabel{datasets}
-%\vspace*{-15pt}
-%\end{table}
-%}
-
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[scale=0.1]{figures/dataset_table.jpg}
-%\caption{\TODO{Remove columns}}
-%\figlabel{datasets}
-%\vspace*{-15pt}
-%\end{figure}
 
@@
 Each object in Dex-Net is specified as a 3D mesh.
-We preprocess each mesh by removing unreferenced vertices, computing a reference frame with Principal Component Analysis (PCA) on the mesh vertices, setting the mesh center of mass $\bz$ to the center of the mesh bounding box, and rescaling the synthetic meshes to fit the smallest dimension of the mesh bounding box within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
+We preprocess each mesh by removing unreferenced vertices, computing a reference frame with Principal Component Analysis (PCA) on the mesh vertices, setting the mesh center of mass $\bz$ to the center of the mesh bounding box, and rescaling the synthetic meshes to fit the smallest dimension of the bounding box within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
 We also convert each mesh to an SDF $f$ using SDFGen~\cite{sdfgen}.
@@
 Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS$ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
-To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$ using rejection sampling.
+To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$.% using rejection sampling.
 Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute $\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv$ and $\bx = 0.5 (\bc_1 + \bc_2)$, where $t_2^*$ is defined in \secref{contact}.
 This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
-We add $\bg_{i,k}$ to our candidate set if the contacts are antipodal~\cite{mahler2015gp}, or $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.
+We add $\bg_{i,k}$ to the candidate set if the contacts are antipodal~\cite{mahler2015gp}, or $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.
 
 We evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
-Our full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.
+The full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.
 
@@
 \seclabel{grasp-similarity}
-To measure grasp similarity, we embed each parallel-jaw grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation, a variant of grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
+To measure grasp similarity, we embed each grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
 Let $d_h \in \mathbb{Z}$ be a number of pixels for the projection, let $\mP = \{-d_h, ..., d_h\}$ be row / column pixel indices, let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
 %Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-Our heightmap at contact $\bc_i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane to the grasp axis $\bv$ specified by $\bt_1, \bt_2$ to the distance to the surface along $\bv$.
-To compute the heightmap value at pixel $u,v \in \mP$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
+The heightmap at contact $\bc_i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane to the grasp axis $\bv$ specified by $\bt_1, \bt_2$ to the distance to the surface along $\bv$.
+To compute the value at pixel $u,v \in \mP$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
 \begin{align*}
@@
 Since force closure depends on object surface normals at contacts~\cite{pokorny2013c}, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
-Our full feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
+The full feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
 
@@
 Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
-We initialize the weights of our network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
+We initialize the weights of the network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
 Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
 Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4,096 dimensions to 100 dimensions.
-This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
-%Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.
+This yields the representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
 
@@
 For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
-In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD.
+In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD.
 %The final PCA step captured approximately 85\% of the variance of the vectors.
 %The image classification training step had a test accuracy of 76\%.
-To validate our implementation, we tested our method on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.
+To validate the implementation, we tested on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.
 
@@
 \includegraphics[scale=0.275]{figures/illustrations/cnn_model.eps}
-\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty.
+\caption{Illustration of our Multi-View Convolutional Neural Network (MV-CNN) deep learning method for embedding 3D object models in a Euclidean vector space to compu global shape similiarty.
 We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture.
-Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
+Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce dimensionality.}
 \figlabel{global-feature-model}

### 2015-09-15 ICRA2016/bandits_docs/includes/experiments.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 We created two training sets of 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
-From the remaining objects, we created a set of 300 validation objects for selecting algorithm hyperparameters and a set of 45 test objects.
-We ran our algorithm with $N_n = 10$ nearest neighbors and used isotropic uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+We uniformly sampled a set of 300 validation objects for selecting algorithm hyperparameters and selected a set of 45 test objects from the remaining objects.
+We ran the algorithm with $N_n = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1.0$~\cite{laskey2015bandits}, and a lower confidence bound for 75\% of the belief distribution.
+We used isotropic uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
 
-The bandwidths of our similarity kernel were constrained to be diagonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a Gaussian mask $C_d$ centered on the differential heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
+The bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma = 1.75$ for the differential heightmap features, and $C_s = 0.001 I$ for the shape similarity features, for $\sigma \in \bR$.
 The bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
 
-To scale the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
+To scale the experiments, we developed a Cloud-based system on top of Google Cloud Platform.
 We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
-Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by over $1000\times$.
+The system launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of experiments by over $1000\times$.
 
 \subsection{Scaling of Average Convergence Rate}
-
-To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran Algorithm~\ref{alg:full} on the 20 validation objects with priors computed from 1,000 and 10,000 objects from Dex-Net.
-~\figref{avg-reward} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the 20 validation objects for 4,000 iterations.
-The plot also compares Algorithm~\ref{alg:full} to uncorrelated Thompson sampling and uniform allocation~\cite{laskey2015bandits}.
-Our algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling over all iterations.
+\seclabel{conv-rate}
+To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran the Dex-Net 1.0 algorithm on the test objects with priors computed from 1,000 and 10,000 objects from Dex-Net.
+~\figref{avg-reward} shows the normalized $P_F$ versus iteration averaged over 25 trials for each of the test objects for 4,000 iterations.
+The plot compares the Dex-Net algorithm to Thompson sampling without priors and uniform allocation~\cite{laskey2015bandits}.
+The algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling without priors.
 Furthermore, the 10,000 object curve does not fall below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
-%However, we see that on average our algorithm makes progress more slowly than Thompson sampling.
 
@@
 \includegraphics[scale=0.40]{figures/illustrations/avg_reward.eps}
-\caption{Average normalized grasp quality versus iteration over 20 validation objects and 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
-We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
-We see that our algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from the 250 candidate set.}
+\caption{Average normalized grasp quality versus iteration over 20 test objects and 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
+We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation.
+The algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from the 250 candidate set.}
 \figlabel{avg-reward}
@@
 \seclabel{shape-sens}
-To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
-The bottom panel~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
+To understand the behavior of the Dex-Net algorithm on individual 3D objects, we examined the convergnce rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
+\figref{avg-reward-spray} and  \figref{avg-reward-drill} show the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on the spray bottle and drill, respectively.
 We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
-This convergence may be explained by the two similar spray bottles retrieved by our MV-CNN from the 10,000 object dataset.
+This convergence may be explained by the two similar spray bottles retrieved by the MV-CNN from the 10,000 object dataset.
 \figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
-However, performance on the drill does not increase using either 1,000 or 10,000 objects, as the closest model in all of Dex-Net according to our similarity metric is a phone.
-
-%This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in the top panel of \figref{query}.
-%We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
-%On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.
+However, performance on the drill does not increase using either 1,000 or 10,000 objects, as the closest model in all of Dex-Net according to the similarity metric is a phone.
 
@@
 \centering
-\includegraphics[scale=0.22]{figures/illustrations/avg_reward_w_neighbors.eps}
-\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net and illustrations of five nearest neighbors in Dex-Net for a spray bottle (left) and drill (right).
-We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation.
-(Top-left) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set.
-(Bottom-left) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp once 10,000 objects are used.
-(Top-right) The drill, which is relatively rare in the dataset, has not geometrically similar neighbors even with 10,000 objects.
-(Bottom-right) This leads to no noticeable performance increase over Thompson sampling.}
-\figlabel{avg-reward-obj}
+\includegraphics[scale=0.43]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
+\caption{Average normalized grasp quality versus iteration over 25 trials for the Dex-Net 10 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a drill.
+(Top) The drill, which is relatively rare in the dataset, has no geometrically similar neighbors even with 10,000 objects.
+(Bottom) This leads to no significant performance increase over Thompson sampling.}
+\figlabel{avg-reward-drill}
 \vspace*{-15pt}
@@
 \includegraphics[scale=0.28]{figures/illustrations/spray_grasps.eps}
-\caption{Illustation of the grasps predicted to have the highest $P_F$ after only 100 iterations by Thompson sampling, Algorithm~\ref{alg:full} with 1,000 prior objects from Dex-Net, and Algorithm~\ref{alg:full} with 10,000 prior objects from Dex-Net.
-Thompson sampling chooses a grasp near the edge of the object, while our algorithm selects grasps closer to the center-of-mass of the object.}
+\caption{Illustation of the grasps predicted to have the highest $P_F$ after only 100 iterations by Thompson sampling without priors and the Dex-Net algorithm with 1,000 and 10,000 prior objects.
+Thompson sampling chooses a grasp near the edge of the object, while the Dex-Net algorithm selects grasps closer to the center-of-mass of the object.}
 \figlabel{spray-grasps}
@@
 
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[scale=0.38]{figures/illustrations/nearest_neighbors.eps}
-%\caption{Illustration of the five nearest neighbor objects from Dex-Net to the spray bottle and drill using the multi-view CNN-based shape embedding and Euclidean distance for size 1,000 and 10,000 datasets from Dex-Net.
-We see that for the 1,000 object dataset neither model has relevant neighbors, while for the 10,000 object dataset two other spray bottles are returned.
-However, even with 10,000 objects no object geometrically similar to the drill is found.
-}
-%\figlabel{query}
-%\vspace*{-5pt}
-%\end{figure}
-
-\subsection{Sensitivity to Similarity, Pose and Friction Uncertainty}
+\subsection{Sensitivity to Similarity and Pose and Friction Uncertainty}
 \seclabel{band-sens}
-We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
+We also studied the sensitivity of the Dex-Net algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
 We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$, and tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
 \figref{bnu-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
-The results suggest that conservative setting of similiarity kernel bandwidth is important for convergence, and a mismatch between the the uncertainty levels for a test object and the labels in Dex-Net diminishes the effects of scaling with prior data.
+The results suggest that conservative setting of similiarity kernel bandwidth is important for convergence, and a mismatch between the uncertainty for a test object and the objects in Dex-Net diminishes the effects of scaling with prior data.
 
@@
 \centering
-\includegraphics[scale=0.23]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
-\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
-with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
+\includegraphics[scale=0.22]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
+\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the average normalized grasp quality versus iteration over 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects.
+%with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
 (Top-left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
@@
 \end{figure}
-
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
-%\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
-(Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
-(Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
-%\figlabel{bandwidth-sens}
-%\vspace*{-10pt}
-%\end{figure}
-
-%\subsection{Sensitivity to Pose and Friction Uncertainty}
-%\seclabel{u-sens}
-%We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
-%We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
-%The uncertainty levels used to label grasps in Dex-Net were not changed.
-%\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
-%The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
-%Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.
-
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
-%\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set.
-Lower uncertainty increases the quality for all methods and higher uncertainty decreases the quality for all methods.
-Interestingly, in both cases prior data has little effect but the convergence rate is still on par with Thompson sampling with no prior data.}
-%\figlabel{u-sens}
-%\vspace*{-10pt}
-%\end{figure}

### 2015-09-15 ICRA2016/bandits_docs/includes/introduction.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 Potential advantages to using the Cloud include Big Data: access to updated libraries of images, maps, and object/product data; and Parallel Computation: access to parallel grid computing for statistical analysis, machine learning, and planning~\cite{kehoe2015survey}.
-The advantages have recently been used in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
+These benefits have recently been demonstrated in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
 This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, and environment configurations~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.
@@
 \centering
-\includegraphics[scale=0.08]{figures/dexnet_collage.jpg}
-\caption{Sample of 3D mesh models from the Dex-Net dataset that currently includes over 10,000 models from the KIT object database~\cite{kasper2012kit}, the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20153d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}.
-}
-\figlabel{dexnet-teaser}
-\vspace*{-15pt}
+\includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
+\caption{Average normalized grasp quality versus iteration over 25 trials for the Dex-Net 10 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle.
+We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation.
+(Top) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set.
+(Bottom) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp with 10,000 prior objects.}
+\figlabel{avg-reward-spray}
+\vspace*{-20pt}
 \end{figure}
+The primary contribution of this paper is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
+The algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
 
-Our primary contribution is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
-Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
+To study scaling effects we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
+Dex-Net also contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
+To the best of our knowledge, this is the largest dataset used for grasping research to-date.
+We also incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.
 
-To study scaling effects we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
-~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
-%Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
-%The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
-Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
-To the best of our knowledge, this is the largest dataset used for grasping research to-date.
-We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.
-
-We implement our algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
-Experiments on planning parallel-jaw grasps with high probability of force closure with our algorithm suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to identify a grasp with high quality by $3.5\times$.
-\TODO{Update with final results}
+We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
+Experiments suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to plan robust parallel-jaw grasps by up to $3.5\times$.
+%\TODO{Update with final results}

### 2015-09-15 ICRA2016/bandits_docs/includes/problem_statement.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 
-We consider the robust grasp planning problem for a single 3D object model and parallel-jaw grippers using probability force closure, $P_F$,  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
+We consider the robust grasp planning problem for a single 3D object model and parallel-jaw grippers using probability force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
 We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within.
@@
 \seclabel{grasp-param}
-Our grasp parameterization is illustrated in~\figref{grasp-model}.
+The grasp parameters are illustrated in~\figref{grasp-model}.
 Let $\bg = (\bx, \bv)$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
@@
 Let $\mG = \{ (\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
-We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.
+We denote by $\mM = \mG \times \mH$ the Grasp Moduli Space of all parallel-jaw grasps and objects~\cite{pokorny2013grasp}.
 
@@
 \seclabel{uncertainty}
-We assume Gaussian distributions on object pose, gripper pose, and friction coefficient.
+We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively.  
 Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
@@
 Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
-We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of object pose, gripper pose, and friction coefficient, respectively. 
-%Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.
+We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of the random variables.
 
@@
 \seclabel{contact}
-%Our contact model is illustrated in the right panel .
 Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface as shown in \figref{grasp-model}.
-Each contact $\bc_i = \bx + (-1)^{i} (t_i^* - w / 2) \bv$ where~\cite{mahler2015gp}:
+Each contact $\bc_i = \bx + (-1)^{i} (w / 2 - t_i^*) \bv$ where~\cite{mahler2015gp}:
 %\vspace{-1ex}
 \begin{align*}
-	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (t - w / 2) \bv\right) = 0.
+	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (w / 2 - t) \bv\right) = 0.
 \end{align*}
@@
 Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.
-Under our soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
-Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
+Under the soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
+Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under the model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
 
@@
 \seclabel{quality}
-In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as our quality metric.
+In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as the quality metric.
 $P_F$ has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
@@
 To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
-Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.
+Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.
 
 \subsection{Objective}
-We are interested in finding $\bg^*$, the grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
+We are interested in finding $\bg^*$, a grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
 To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
 As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
-In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the samples needed to converge to $\bg^*$.
+In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

### 2015-09-15 ICRA2016/bandits_docs/includes/related_work.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 
-Robust grasp planning considers the problem of finding a set of grasps for an object that may succeed over perturbations in object shape,  object pose, and environment configurations due to uncertainty resulting from imprecision in perception and control.
-Research on grasp planning for precisely known objects and environments has largely focused on finding grasps by maximizing an analytic grasp quality metric based on a Wrench Space (WS)~\cite{pokorny2013c}.
-The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{bohg2014data}.
-To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated in GraspIt!.
-%, and matched robot sensor data to synthetic depth maps of objects in the database using Iterated Closest Point to retrieve precomputed grasps for execution on a physical robot~\cite{goldfeder2011data}.
-This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
+Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric~\cite{pokorny2013c}.
+Usually it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
+Robust grasp planning considers the same problem in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
+One way to treat perturbations is statistical sampling.
+Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasps computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
+To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt!
+stochastic sampling-based grasp planner.
+%This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
 
@@
 Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic WS metrics.
+Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.
 Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.
 
-Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps decided by humans~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
+Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
 Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
 The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
-In comparison, we learn a model predictive model of $P_F$ for parallel-jaw grasps on a new object based on similarity to prior 3D objects and grasps, and use our model for robust grasp planning with Multi-Armed Bandits (MAB).
+We estimate $P_F$ using similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.
 
@@
 Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
-Oberlin and Tellex~\cite{oberlin2015autonomously} developed a confidence-bound based MAB algorithm for planning parallel-jaw grasps using prior information on short time horizons, but do not study the effects of orders of magnitude of prior data on convergence.
+Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps a using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
 Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.

### 2015-09-15 ICRA2016/bandits_docs/paper.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

@@
 
-%\benkhide
+\benkhide
 
@@
 \begin{document}
-\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and a Multi-Armed Bandit Model with Correlated Rewards to Accelerate Robust Grasp Planning
-	%\vspace{-2ex}
-	\versionline{9}}
+\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards
+	\vspace{-2ex}
+	\versionline{11}}
 \author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
@@
 %\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
-\TODO{Trim paper to 8 pages}
+%\TODO{Trim paper to 8 pages}
 \input{includes/abstract}

### 2015-09-16 ICRA2016/bandits_docs/includes/abstract.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
-Experiments suggest that prior data can speed robust grasp planning by a factor of up to 3 and that average grasp quality increases with the number of similar objects in the dataset.
+Experiments suggest that prior data can speed up robust grasp planning by a factor of up to 2 on average and that the quality of planned grasps increases with the number of similar objects in the dataset.
 We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
-Code, data, and additional information can be found at: \TODO{Url}.
+Code and additional information can be found at: \url{http://berkeleyautomation.github.io/dex-net/}.
 \end{abstract}

### 2015-09-16 ICRA2016/bandits_docs/includes/conclusion.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
-Experiments suggest that prior data can speed robust grasp planning by a factor of 3 and that average grasp quality increases with the number of similar objects in the dataset.
-We reported on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
+Experiments suggest that prior data can speed robust grasp planning by a factor of 2 and that average grasp quality increases with the number of similar objects in the dataset.
+We reported on sensitivity to varying similarity metrics and pose and friction uncertainty levels.
 
@@
 We also hope to release subsets of Dex-Net 1.0 with an open-source API to explore robust grasping as a service (RGaaS).
-
-%We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model with correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
-%To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{aubry2015understanding, su2015multi} to efficiently index similar objects.
-%Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
-%
-%One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
-%Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
-%We are also interested in an end-to-end approach that integrates research on deep learning to map directly from images to motor torques that control a grasp.
-%To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}.
-%%We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
-%
-%In future work, we will also add grasp and object data to Dex-Net, such as more 3D models, task constraints, the outcomes of physical trials, or human annotations.
-%%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
-%%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
-%We will also explore additional analytic grasp metrics to Dex-Net such as cages, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
-%We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.
-%Our goal is to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
-%

### 2015-09-16 ICRA2016/bandits_docs/includes/dataset.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 The Dexterity Network (Dex-Net) 1.0 dataset is a growing set that currently includes over 10,000 prior 3D object models annotated with 2.5 million parallel-jaw grasps.
-Dex-Net 1.0 contains 13,252 models from the following sources: 8,987 from the SHREC 2014 challenge dataset~\cite{li2015comparison}, 2,539 from ModelNet40~\cite{wu20153d}, 1,371 from 3DNet~\cite{wohlkinger20123dnet}, 129 from the KIT object database~\cite{kasper2012kit}, 120 from BigBIRD~\cite{singh2014bigbird}, 80 from the Yale-CMU-Berkeley dataset~\cite{calli2015benchmarking}, and 26 from the Amazon Picking Challenge scans.
 
-\subsection{Data Cleaning}
-Each object in Dex-Net is specified as a 3D mesh.
+\subsection{Data}
+Dex-Net 1.0 contains 13,252 3D mesh models: 8,987 from the SHREC 2014 challenge dataset~\cite{li2015comparison}, 2,539 from ModelNet40~\cite{wu20153d}, 1,371 from 3DNet~\cite{wohlkinger20123dnet}, 129 from the KIT object database$^*$~\cite{kasper2012kit}, 120 from BigBIRD$^*$~\cite{singh2014bigbird}, 80 from the Yale-CMU-Berkeley dataset$^*$~\cite{calli2015benchmarking}, and 26 from the Amazon Picking Challenge$^*$ scans ($^*$ indicates laser-scanner data).
 We preprocess each mesh by removing unreferenced vertices, computing a reference frame with Principal Component Analysis (PCA) on the mesh vertices, setting the mesh center of mass $\bz$ to the center of the mesh bounding box, and rescaling the synthetic meshes to fit the smallest dimension of the bounding box within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
+To resolve orientation ambiguity in the reference frame, we orient the positive axes of the $z$-axis toward the side of the $xy$ plane with more vertices. 
 We also convert each mesh to an SDF $f$ using SDFGen~\cite{sdfgen}.
@@
 To measure grasp similarity, we embed each grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
-Let $d_h \in \mathbb{Z}$ be a number of pixels for the projection, let $\mP = \{-d_h, ..., d_h\}$ be row / column pixel indices, let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
+Let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
 %Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-The heightmap at contact $\bc_i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane to the grasp axis $\bv$ specified by $\bt_1, \bt_2$ to the distance to the surface along $\bv$.
-To compute the value at pixel $u,v \in \mP$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
+The heightmap $\bh_{i}$ at contact $\bc_i$ maps locations along the tangent plane to the grasp axis $\bv$ specified by $\bt_1, \bt_2$ to the distance to the surface along $\bv$.
+To compute the value at pixel $u,v$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
 \begin{align*}
@@
 \seclabel{object-similarity}
-We use Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{aubry2015understanding, su2015multi} to efficiently index prior 3D object and grasp data from Dex-Net by embedding each object in a vector space where distance represents object similarity, as shown in \figref{global-feature-model}.
+We use Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to efficiently index prior 3D object and grasp data from Dex-Net by embedding each object in a vector space where distance represents object similarity, as shown in \figref{global-feature-model}.
 We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$, where $R$ is the maximum dimension of the object bounding box.

### 2015-09-16 ICRA2016/bandits_docs/includes/experiments.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 \seclabel{experiments}
-
-\TODO{Update results with any experiments. The current section basically reflects what we should expect but I'm running a few with slightly more test objects to see what happens}
 
@@
 We ran the algorithm with $N_n = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1.0$~\cite{laskey2015bandits}, and a lower confidence bound for 75\% of the belief distribution.
-We used isotropic uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+We used isotropic Gaussian uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
 
-The bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma = 1.75$ for the differential heightmap features, and $C_s = 0.001 I$ for the shape similarity features, for $\sigma \in \bR$.
+The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma = 1.75$ for the differential heightmap features, and $C_s = 0.001 I$ for the shape similarity features.
 The bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
@@
 We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
-The system launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of experiments by over $1000\times$.
+The system launched up to 1500 GCE single core instances each with 3.75 GB of memory at once for hyperparameter tuning and convergence analysis, reducing the runtime of experiments by over 1000$\times$.
 
@@
 To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran the Dex-Net 1.0 algorithm on the test objects with priors computed from 1,000 and 10,000 objects from Dex-Net.
-~\figref{avg-reward} shows the normalized $P_F$ versus iteration averaged over 25 trials for each of the test objects for 4,000 iterations.
-The plot compares the Dex-Net algorithm to Thompson sampling without priors and uniform allocation~\cite{laskey2015bandits}.
-The algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling without priors.
+~\figref{avg-reward} shows the normalized $P_F$ versus iteration averaged over 25 trials for each of the test objects for 2,000 iterations.
+The plot compares the Dex-Net algorithm to Thompson sampling without priors (TS) and uniform allocation (UA)~\cite{laskey2015bandits}.
+The algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by TS.
 Furthermore, the 10,000 object curve does not fall below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
@@
 \includegraphics[scale=0.40]{figures/illustrations/avg_reward.eps}
-\caption{Average normalized grasp quality versus iteration over 20 test objects and 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
+\caption{Average normalized grasp quality versus iteration over 45 test objects and 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
 We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation.
@@
 \seclabel{shape-sens}
-To understand the behavior of the Dex-Net algorithm on individual 3D objects, we examined the convergnce rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
-\figref{avg-reward-spray} and  \figref{avg-reward-drill} show the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on the spray bottle and drill, respectively.
+To understand the behavior of the Dex-Net algorithm on individual 3D objects, we examined the convergence rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
+\figref{avg-reward-spray} and  \figref{avg-reward-drill} show the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 2,000 iterations on the spray bottle and drill, respectively.
 We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
@@
 \centering
-\includegraphics[scale=0.43]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
+\includegraphics[scale=0.41]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
 \caption{Average normalized grasp quality versus iteration over 25 trials for the Dex-Net 10 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a drill.
@@
 \figlabel{avg-reward-drill}
-\vspace*{-15pt}
+\vspace*{-10pt}
 \end{figure}
@@
 
-\subsection{Sensitivity to Similarity and Pose and Friction Uncertainty}
+\subsection{Sensitivity to Similarity and Uncertainty}
 \seclabel{band-sens}
-We also studied the sensitivity of the Dex-Net algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
-We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$, and tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
-\figref{bnu-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
-The results suggest that conservative setting of similiarity kernel bandwidth is important for convergence, and a mismatch between the uncertainty for a test object and the objects in Dex-Net diminishes the effects of scaling with prior data.
+We also studied the sensitivity of the Dex-Net algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of pose an friction uncertainty for the test object.
+We varied the inverse bandwidths of the kernel for the grasp parameters and differential heightmaps gradients to the lower values $C_g = diag(0,0,15, 15)$, $\mu_d = 350.0$,  and $\sigma = 3.0$ as well as the higher values $C_g = diag(0,0,300, 300)$, $\mu_d = 750.0$,  and $\sigma = 1.75$.
+We also tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high uncertainty: $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
+\figref{bnu-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 2,000 iterations on the 45 test objects.
+The results suggest that conservative setting of similiarity kernel bandwidth is important for convergence and that the algorithm is not sensitive to uncertainty levels.
 
@@
 %with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
-(Top-left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
-(Top-right) A lower kernel bandwith decreases the convergence rate, but the Dex-Net Algorithm still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.
-(Bottom-left) Lower uncertainty increases the quality for all methods and (bottom-right) higher uncertainty decreases the quality for all methods.
-Interestingly, for variation in pose and friction uncertainty the convergence rate is still on par with Thompson sampling with no prior data.
+(Top-left) Using a higher inverse bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
+(Top-right) A lower inverse bandwith decreases the convergence rate, but on average the Dex-Net Algorithm still selects a grasp within approximately 85\% of the grasp with highest $P_F$ for all iterations.
+(Bottom-left) Lower uncertainty increases the quality for all methods and (bottom-right) higher uncertainty decreases the quality for all methods, and the Dex-Net algorithm with 10,000 prior objects still converges approximately 2$\times$ faster than Thompson sampling without priors.
 }

### 2015-09-16 ICRA2016/bandits_docs/includes/introduction.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 Dex-Net also contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
-To the best of our knowledge, this is the largest dataset used for grasping research to-date.
+To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
 We also incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.
@@
 We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
-Experiments suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to plan robust parallel-jaw grasps by up to $3.5\times$.
+Experiments suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$.
 %\TODO{Update with final results}

### 2015-09-16 ICRA2016/bandits_docs/includes/problem_statement.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 
-We consider the robust grasp planning problem for a single 3D object model and parallel-jaw grippers using probability force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
+We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
 We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within.
@@
 We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively. 
+We denote by $\mN(\mu,\Sigma)$ a Gaussian distribution with mean $\mu$ and variance $\Sigma$.
 Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
@@
 \begin{align*}
-	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (w / 2 - t) \bv\right) = 0.
+	t_i^* &= \myargmin{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (w / 2 - t) \bv\right) = 0.
 \end{align*}
@@
 \subsection{Objective}
-We are interested in finding $\bg^*$, a grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
+We are interested in finding a grasp $\bg^*$ that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
 To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
 As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
-In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.
+In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

### 2015-09-16 ICRA2016/bandits_docs/paper.tex
Added feedback from Mathieu and Florian and new experimental results

@@
 The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
-We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
+We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
 }

### 2015-09-16 ICRA2016/bandits_docs/includes/abstract.tex
Adding tex for submitted version of paper

@@
 \begin{abstract}
-This paper presents Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and cloud computation on robust grasp planning. 
+This paper presents Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning. 
 The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models in a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps.
 Each grasp includes an estimate of the probability of force closure under uncertainty in object and gripper pose and friction.
-Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
-Experiments suggest that prior data can speed up robust grasp planning by a factor of up to 2 on average and that the quality of planned grasps increases with the number of similar objects in the dataset.
+Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual cores, reducing runtime by three orders of magnitude.
+Experiments suggest that using prior data can significantly benefit the quality and complexity of robust grasp planning.
 We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.

### 2015-09-16 ICRA2016/bandits_docs/includes/algorithm.tex
Added feedback from Mathieu and Florian and new experimental results
Adding tex for submitted version of paper

@@
 \seclabel{algorithm}
-The Dex-Net 1.0 algorithm (see below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
-We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
+The Dex-Net 1.0 algorithm (see pseudocode below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
+We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior belief distribution for each grasp using the Dex-Net database $\mD$.
 Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from the uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
-Finally, we rank the grasps in $\Gamma$ by the maximum $p$-lower confidence bound, a conservative estimate of the $P_F$ of each grasp, and store the ranking in the database.
+Finally, we rank the grasps in $\Gamma$ by the maximum lower confidence bound of the belief distribution, a conservative estimate of the $P_F$ of each grasp, and store the ranking in the database.
 We use Thompson sampling to study the scaling effects for a fixed grasp selection method and plan to study other methods based on confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.
+
+\subsection{Belief Distribution Model}
+\seclabel{belief}
+Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
+We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
+Under the model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
+Since $\theta_j$ is unknown, the algorithm maintains a posterior Beta belief distribution on the Bernoulli parameter $\theta_{j}$ that is updated with every new observation of $F$, assigning increasingly high probability to the true $P_F$.
+The Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits} is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+
+\vspace{-4ex}
+\begin{align*}
+	\betadist(\alpha, \beta) = Z(\alpha, \beta) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
+\end{align*}
+\noindent where $Z(\alpha, \beta)$ is a normalization constant.
+
+\subsection{Predicting Grasp Quality Using Prior Data}
+\seclabel{ccbps}
+We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net.
+CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
+Two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp wrench space metrics~\cite{pokorny2013c}.
+
+A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
+The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
+
+We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
+The first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
+To capture local surface geometry, the second feature map $\phi_{2}(\mY) = \eta(\bg, \mO)$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
+To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similarity map described in \secref{object-similarity}.
+Given the feature maps, we use the squared exponential kernel 
+\begin{align*}
+	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
+\end{align*}
+\noindent where $C_m \in \bR^{d_m \times d_m}$ is the inverse bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^T C_m \by$.
+The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.
+
+We form a prior belief distribution for each candidate grasp in $\Gamma$ based on its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
+%\vspace{-2ex}
+\begin{align}
+	%p \left(\theta_{j} | \mD \right) &= \betadist\left( \alpha_{j,0}, \beta_{j,0} \right) \notag \\
+	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g} k(\mY_{j}, \mY_{i, k}) S_{i,k} \label{eq:alpha-prior} \\
+	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g}  k(\mY_{j}, \mY_{i,k}) (N_s - S_{i,k}) \label{eq:beta-prior}
+\end{align}
+\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled to evaluate $P_F$.
+In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.
+Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:
+
+\vspace{-2ex}
+\begin{align}
+	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
+	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}.
+\end{align}
 
@@
     \SetAlgoLined
-    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Samples $N_s$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Features maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
+    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Features maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
     \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}
@@
 		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
-		$F_{j} = $ EvaluateForceClosure($\bg_j, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
+		$F_{j} = $ EvaluateForceClosure($\bg_j, \mO, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
 		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
@@
 	return $\bg_T^*$\;
-    \nonl {\bf Dex-Net 1.0 Algorithm}: Robust Grasp Planning Using Multi-Armed Bandits With Correlated Rewards
-    \label{alg:full}
+    \nonl {\bf Dex-Net 1.0 Algorithm}: Robust Grasp Planning Using Multi-Armed Bandits with Correlated Rewards
 }
 \end{algorithm}
-
-\subsection{Belief Distribution Model}
-\seclabel{belief}
-Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
-We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
-Under the model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
-Since $\theta_j$ is unknown, the algorithm maintains a posterior Beta belief distribution on the Bernoulli parameter $\theta_{j}$ that is updated with every new observation of $F$, assigning increasingly high probability to the true $P_F$.
-The Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits} is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
-
-\vspace{-4ex}
-\begin{align*}
-	\betadist(\alpha, \beta) = \left( 1 / B(\alpha, \beta) \right) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
-\end{align*}
-\noindent where $B$ is a normalization constant.
-
-\subsection{Predicting Grasp Quality Using Prior Data}
-\seclabel{ccbps}
-We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net.
-CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
-Two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.
-
-A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
-The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
-
-We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
-The first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
-To capture local surface geometry, the second feature map $\phi_{2}(\mY) = \eta(\bg, \mO)$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
-To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
-Given the feature maps, we use the squared exponential kernel 
-\begin{align*}
-	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
-\end{align*}
-\noindent where $C_m \in \bR^{d_m \times d_m}$ is the inverse bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^T C_m \by$.
-The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.
-
-We form a prior belief distribution for each candidate grasp in $\Gamma$ based on its its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
-%\vspace{-2ex}
-\begin{align}
-	%p \left(\theta_{j} | \mD \right) &= \betadist\left( \alpha_{j,0}, \beta_{j,0} \right) \notag \\
-	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g} k(\mY_{j}, \mY_{i, k}) S_{i,k} \label{eq:alpha-prior} \\
-	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g}  k(\mY_{j}, \mY_{i,k}) (N_s - S_{i,k}) \label{eq:beta-prior}
-\end{align}
-\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled for evaluate $P_F$.
-In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.
-Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:
-
-\vspace{-2ex}
-\begin{align}
-	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
-	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}.
-\end{align}
-
-%\subsection{Feature Representation}
-%\seclabel{features}
-%\TODO{Condense section / possibly move earlier.}
-%We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.
-%
-%\subsubsection{Grasp Parameters}
-%\seclabel{param-features}
-%Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx \in bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
-%The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
-%However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).
-
-%\subsubsection{Local Surface Heightmaps}
-%\seclabel{heightmaps}
-%We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging} to capture local surface geometry.
-%Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
-%Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-%Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
-%To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
-%Then we assign the heightmap value
-%\begin{align*}
-%	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + s_i \bv \right) = 0
-%\end{align*}
-%\noindent where $s_1 = -1$, $s_2 = 1$, and $f$ is the SDF of object $\mO$. 
-%We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
-%\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
-%Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients to form local surface normal maps $\bd_{i,x}$ and $\bd_{i,y}$.
-%Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
-%
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
-%\caption{Three local surface heightmaps extracted on a teapot.
-Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.
-We extract the gradients of these heightmaps as features in our robust grasp planning algorithm.}
-%\figlabel{local-feature-model}
-%\vspace*{-15pt}
-%\end{figure}
-%
-%\subsubsection{Shape Features}
-%\seclabel{global-sim}
-%While force closure is based on local surface properties of an object around contact points, measuring global similarity may be useful because the heightmap gradients may not capture all possible contact locations for a grasp under perturbations in object and gripper pose.
-%Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.
-
-%\subsection{Thompson Sampling}
-%\seclabel{thompson}
-%
-%Following Laskey et al.~\cite{laskey2015bandits}, we use Thompson sampling to select the next grasp to evaluate given belief distributions on the $P_F$ for each grasp on iteration $t$ specified by estimates $\mA_t = \{\alpha_{1,t}, ..., \alpha_{K,t}\}$ and $\mB_t = \{\beta_{1,t}, ..., \beta_{K,t}\}$.
-%Thompson sampling samples a probability of force closure $\hat{\theta}_{j,t} \sim B(\alpha_{j,t}, \beta_{j,t})$ for all grasps $j = 1, ..., K$, then selects the grasp $j_t^* = \myargmax{j} \hat{\theta}_{j,t}$ to evaluate next.
-%Several other criteria exist for selecting the next evaluation in MAB, such as Gittins indices~\cite{laskey2015bandits}, Upper Confidence Bounds~\cite{boularias2015learning}, and Expected Improvement~\cite{montesano2012active}.

### 2015-09-16 ICRA2016/bandits_docs/includes/conclusion.tex
Adding tex for submitted version of paper

@@
 
-In future work, we will develop metrics to pre-compute grasps that adequately "cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
+In future work, we will develop metrics to pre-compute grasps that adequately ``cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
 We will also explore how Deep Learning~\cite{krizhevsky2012imagenet} can be used in other parts of a grasp planning pipeline, for example to recognize object pose and shape from images~\cite{aubry2015understanding}, to learn grasp and object features robust to shape variation using prior evaluations from bandit algorithms, and perhaps even to determine motor torques based on images and precomputed grasps~\cite{levine2015end}.

### 2015-09-16 ICRA2016/bandits_docs/includes/dataset.tex
Adding tex for submitted version of paper

@@
 
-The Dexterity Network (Dex-Net) 1.0 dataset is a growing set that currently includes over 10,000 prior 3D object models annotated with 2.5 million parallel-jaw grasps.
+The Dexterity Network (Dex-Net) 1.0 dataset is a growing set that currently includes over 10,000 unique 3D object models annotated with 2.5 million parallel-jaw grasps.
 
@@
 Dex-Net 1.0 contains 13,252 3D mesh models: 8,987 from the SHREC 2014 challenge dataset~\cite{li2015comparison}, 2,539 from ModelNet40~\cite{wu20153d}, 1,371 from 3DNet~\cite{wohlkinger20123dnet}, 129 from the KIT object database$^*$~\cite{kasper2012kit}, 120 from BigBIRD$^*$~\cite{singh2014bigbird}, 80 from the Yale-CMU-Berkeley dataset$^*$~\cite{calli2015benchmarking}, and 26 from the Amazon Picking Challenge$^*$ scans ($^*$ indicates laser-scanner data).
-We preprocess each mesh by removing unreferenced vertices, computing a reference frame with Principal Component Analysis (PCA) on the mesh vertices, setting the mesh center of mass $\bz$ to the center of the mesh bounding box, and rescaling the synthetic meshes to fit the smallest dimension of the bounding box within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
-To resolve orientation ambiguity in the reference frame, we orient the positive axes of the $z$-axis toward the side of the $xy$ plane with more vertices. 
-We also convert each mesh to an SDF $f$ using SDFGen~\cite{sdfgen}.
+We preprocess each mesh by removing unreferenced vertices, computing a reference frame with Principal Component Analysis (PCA) on the mesh vertices, setting the mesh center of mass $\bz$ to the center of the mesh bounding box, and rescaling the synthetic meshes to fit the smallest dimension of the bounding box within $w = 0.1m$.
+To resolve orientation ambiguity in the reference frame, we orient the positive $z$-axis toward the side of the $xy$ plane with more vertices. 
+We also convert each mesh to an SDF using SDFGen~\cite{sdfgen}.
 
@@
 Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS$ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
-To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$.% using rejection sampling.
-Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute $\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv$ and $\bx = 0.5 (\bc_1 + \bc_2)$, where $t_2^*$ is defined in \secref{contact}.
+To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$.
+Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute $\bc_2 = \bc_1 + (w - t_2^*) \bv$ and $\bx = 0.5 (\bc_1 + \bc_2)$, where $t_2^*$ is defined as in \secref{contact}.
 This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
@@
 We evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
-The full dataset of $N_o$ 3D objects and $N_g$ grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.
+The dataset of $N_o$ objects and $N_g$ candidate grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.
 
@@
 \seclabel{grasp-similarity}
-To measure grasp similarity, we embed each grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
+To measure grasp similarity, we embed each grasp $\bg = (\bx ,\bv)$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
 Let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
 %Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-The heightmap $\bh_{i}$ at contact $\bc_i$ maps locations along the tangent plane to the grasp axis $\bv$ specified by $\bt_1, \bt_2$ to the distance to the surface along $\bv$.
+The heightmap $\bh_{i}$ at contact $\bc_i$ maps points $\bp \in \bR^3$ on the tangent plane $\bv^T(\bp - \bc_1) = 0$ to the distance to the surface along $\bv$.
 To compute the value at pixel $u,v$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
@@
 Since force closure depends on object surface normals at contacts~\cite{pokorny2013c}, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
-The full feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
+The feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
 
@@
 We use Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to efficiently index prior 3D object and grasp data from Dex-Net by embedding each object in a vector space where distance represents object similarity, as shown in \figref{global-feature-model}.
-We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$, where $R$ is the maximum dimension of the object bounding box.
+We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and spaced on a grid of angle increments $\delta_{\theta} = \frac{2 \pi}{5}$ and $\delta_{\phi} = \frac{2 \pi}{5}$ on a viewing sphere with radii $r = R, 2R$, where $R$ is the maximum dimension of the object bounding box.
 Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
@@
 For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
-In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD.
+In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison}, which has 171 unique categories, for 500,000 iterations of SGD.
 %The final PCA step captured approximately 85\% of the variance of the vectors.
@@
 \includegraphics[scale=0.275]{figures/illustrations/cnn_model.eps}
-\caption{Illustration of our Multi-View Convolutional Neural Network (MV-CNN) deep learning method for embedding 3D object models in a Euclidean vector space to compu global shape similiarty.
+\caption{Illustration of our Multi-View Convolutional Neural Network (MV-CNN) deep learning method for embedding 3D object models in a Euclidean vector space to compute global shape similarity.
 We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture.

### 2015-09-16 ICRA2016/bandits_docs/includes/experiments.tex
Adding tex for submitted version of paper

@@
 We evaluate the convergence rate of the Dex-Net 1.0 algorithm for varying sizes of prior data used from Dex-Net and explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
-We created two training sets of 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
+We created two training sets of 1,000, and 10,000 objects by uniformly sampling objects from Dex-Net.
 We uniformly sampled a set of 300 validation objects for selecting algorithm hyperparameters and selected a set of 45 test objects from the remaining objects.
-We ran the algorithm with $N_n = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1.0$~\cite{laskey2015bandits}, and a lower confidence bound for 75\% of the belief distribution.
+We ran the algorithm with $N_n = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1.0$~\cite{laskey2015bandits}, and a lower confidence bound containing $p=75\%$ of the belief distribution.
 We used isotropic Gaussian uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
+For each experiment we compare the Dex-Net algorithm to Thompson sampling without priors (TS) and uniform allocation (UA)~\cite{laskey2015bandits}.
 
-The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma = 1.75$ for the differential heightmap features, and $C_s = 0.001 I$ for the shape similarity features.
-The bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
+The inverse kernel bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
+The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma_d = 1.75$ for the differential heightmap features, and $C_s = 0.001 * I$ for the shape similarity features.
 
@@
 We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
-The system launched up to 1500 GCE single core instances each with 3.75 GB of memory at once for hyperparameter tuning and convergence analysis, reducing the runtime of experiments by over 1000$\times$.
+The system launched up to 1,500 GCE virtual instances at once for experiments, reducing the runtime by three orders of magnitude.
+Each virtual instance ran Ubuntu 12.04 on a single core with 3.75 GB of RAM.
 
@@
 To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran the Dex-Net 1.0 algorithm on the test objects with priors computed from 1,000 and 10,000 objects from Dex-Net.
-~\figref{avg-reward} shows the normalized $P_F$ versus iteration averaged over 25 trials for each of the test objects for 2,000 iterations.
-The plot compares the Dex-Net algorithm to Thompson sampling without priors (TS) and uniform allocation (UA)~\cite{laskey2015bandits}.
-The algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by TS.
-Furthermore, the 10,000 object curve does not fall below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
+~\figref{avg-reward} shows the normalized $P_F$  (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the test objects over 2,000 iterations.
+The average runtime per iteration was 16 ms for UA, 17 ms for TS, and 22 ms for Dex-Net 1.0.
+The algorithm with 10,000 objects takes approximately 2$\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by TS.
+Furthermore, the 10,000 object curve does not fall below approximately 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
 
@@
 \includegraphics[scale=0.40]{figures/illustrations/avg_reward.eps}
-\caption{Average normalized grasp quality versus iteration over 45 test objects and 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
+\caption{Average normalized grasp quality versus iteration over 45 test objects and 25 trials per object for the Dex-Net1.0 algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
 We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation.
-The algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from the 250 candidate set.}
+The algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from a set of 250 candidate grasps.}
 \figlabel{avg-reward}
@@
 To understand the behavior of the Dex-Net algorithm on individual 3D objects, we examined the convergence rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
-\figref{avg-reward-spray} and  \figref{avg-reward-drill} show the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 2,000 iterations on the spray bottle and drill, respectively.
+\figref{avg-reward-spray} and  \figref{avg-reward-drill} show the normalized $P_F$ versus iteration averaged over 25 trials for 2,000 iterations on the spray bottle and drill, respectively.
 We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
@@
 \figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
-However, performance on the drill does not increase using either 1,000 or 10,000 objects, as the closest model in all of Dex-Net according to the similarity metric is a phone.
+On the other hand, performance on the drill does not increase using either 1,000 or 10,000 objects, as the closest model in all of Dex-Net according to the similarity metric is a phone.
 
@@
 \includegraphics[scale=0.41]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
-\caption{Average normalized grasp quality versus iteration over 25 trials for the Dex-Net 10 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a drill.
+\caption{Failure object for the Dex-Net 1.0 algorithm.
 (Top) The drill, which is relatively rare in the dataset, has no geometrically similar neighbors even with 10,000 objects.
-(Bottom) This leads to no significant performance increase over Thompson sampling.}
+(Bottom) Plotted is the average normalized grasp quality versus iteration over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects.
+The lack of similar objects leads to no significant performance increase over Thompson sampling without priors.
+}
 \figlabel{avg-reward-drill}
@@
 \centering
-\includegraphics[scale=0.28]{figures/illustrations/spray_grasps.eps}
-\caption{Illustation of the grasps predicted to have the highest $P_F$ after only 100 iterations by Thompson sampling without priors and the Dex-Net algorithm with 1,000 and 10,000 prior objects.
-Thompson sampling chooses a grasp near the edge of the object, while the Dex-Net algorithm selects grasps closer to the center-of-mass of the object.}
+\includegraphics[scale=0.29]{figures/illustrations/spray_grasps.eps}
+\caption{Illustration of the grasps predicted to have the highest $P_F$ after only 100 iterations by Thompson sampling without priors and the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior objects.
+Thompson sampling without priors chooses a grasp near the edge of the object, while the Dex-Net algorithm selects grasps closer to the object center-of-mass.}
 \figlabel{spray-grasps}
@@
 \seclabel{band-sens}
-We also studied the sensitivity of the Dex-Net algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of pose an friction uncertainty for the test object.
-We varied the inverse bandwidths of the kernel for the grasp parameters and differential heightmaps gradients to the lower values $C_g = diag(0,0,15, 15)$, $\mu_d = 350.0$,  and $\sigma = 3.0$ as well as the higher values $C_g = diag(0,0,300, 300)$, $\mu_d = 750.0$,  and $\sigma = 1.75$.
-We also tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high uncertainty: $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
+We also studied the sensitivity of the Dex-Net algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of pose and friction uncertainty for the test object.
+We varied the inverse bandwidths of the kernel for the grasp parameters and differential heightmaps gradients to the lower values $C_g = diag(0,0,15, 15)$, $\mu_d = 350.0$,  and $\sigma_d = 3.0$ as well as the higher values $C_g = diag(0,0,300, 300)$, $\mu_d = 750.0$,  and $\sigma_d = 1.75$.
+We also tested low uncertainty with variances $(\sigma_{t}, \sigma_{r}, \sigma_{\gamma}) = (0.0025, 0.05, 0.05)$ and high uncertainty with variances $(\sigma_{t}, \sigma_{r}, \sigma_{\gamma}) = (0.01, 0.2, 0.2)$ .
 \figref{bnu-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 2,000 iterations on the 45 test objects.
@@
 \centering
-\includegraphics[scale=0.22]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
-\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the average normalized grasp quality versus iteration over 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects.
+\includegraphics[scale=0.21]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
+\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the normalized grasp quality versus iteration averaged over 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects.
 %with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
@@
 (Top-right) A lower inverse bandwith decreases the convergence rate, but on average the Dex-Net Algorithm still selects a grasp within approximately 85\% of the grasp with highest $P_F$ for all iterations.
-(Bottom-left) Lower uncertainty increases the quality for all methods and (bottom-right) higher uncertainty decreases the quality for all methods, and the Dex-Net algorithm with 10,000 prior objects still converges approximately 2$\times$ faster than Thompson sampling without priors.
+(Bottom-left) Lower uncertainty increases the quality for all methods, (bottom-right) higher uncertainty decreases the quality for all methods, and the Dex-Net algorithm with 10,000 prior objects still converges approximately 2$\times$ faster than Thompson sampling without priors.
 }

### 2015-09-16 ICRA2016/bandits_docs/includes/introduction.tex
Adding tex for submitted version of paper

@@
 \includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
-\caption{Average normalized grasp quality versus iteration over 25 trials for the Dex-Net 10 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle.
+\caption{Normalized grasp quality versus iteration averaged over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle.
 We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation.
@@
 
-To study scaling effects we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
-Dex-Net also contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
+To study scaling effects, we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 unique 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
+Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
 To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
@@
 We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
-Experiments suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$.
+Experiments suggest that using 10,000 prior object models from Dex-Net reduces the number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$ on average over 45 objects.
 %\TODO{Update with final results}

### 2015-09-16 ICRA2016/bandits_docs/includes/problem_statement.tex
Adding tex for submitted version of paper

@@
 
-We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
-We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within.
+We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability of force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
+We assume the nominal object shape is given as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within.
 The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
@@
 Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
-We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
-Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote a Gaussian distribution on gripper pose with mean $\mu_{\nu} \in \mG$.
+We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$~\cite{barfoot2014associating}.
+Let $\nu \sim \mN\left(\mathbf{0}, \Sigma_{\nu}\right)$ denote zero-mean Gaussian gripper pose uncertainty with mean $\mu_{\nu} \in \mG$.
 Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
@@
 Let $F \in \{0, 1\}$ denote the occurrence of force closure.
-Then for a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
+For a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
 To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
@@
 To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
-As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
+Since the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
 In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

### 2015-09-16 ICRA2016/bandits_docs/includes/related_work.tex
Adding tex for submitted version of paper

@@
 One way to treat perturbations is statistical sampling.
-Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasps computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
+Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasp computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
 To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt!
@@
 Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
-Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic WS metrics.
+Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic wrench space metrics.
 Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.
@@
 Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
-Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
+Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances, each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
 The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
@@
 Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
-Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps a using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
+Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
 Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
@@
 One line of research has focused on shape geometry, such as characteristics of harmonic functions on the shape~\cite{bronstein2011shape}, or CNNs trained on a voxel representation of shape~\cite{maturana2015voxnet, wu20153d}.
-Onother line of research relies on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
-One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented inconsistently.
+Another line of research relies on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
+One of the key difficulty of these methods is comparing views from different objects, which may be oriented inconsistently.
 The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views and aggregating them with a second CNN that learns the invariance to orientation.

### 2015-09-16 ICRA2016/bandits_docs/paper.tex
Adding tex for submitted version of paper

@@
 The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
-We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
+We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
 }

### 2016-02-05 ICRA2016/bandits_docs/includes/abstract.tex
Made first round of ICRA revisions, v14 of the paper

@@
 \begin{abstract}
-This paper presents Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning. 
+This paper presents the Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on the number of samples required for robust grasp planning.
 The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models in a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps.
 Each grasp includes an estimate of the probability of force closure under uncertainty in object and gripper pose and friction.
-Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual cores, reducing runtime by three orders of magnitude.
-Experiments suggest that using prior data can significantly benefit the quality and complexity of robust grasp planning.
+Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual cores, reducing experiment runtime by up to three orders of magnitude.
+Experiments suggest that using prior data can significantly reduce the number of samples required to plan robust grasps.
 We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.

### 2016-02-05 ICRA2016/bandits_docs/includes/algorithm.tex
Made first round of ICRA revisions, v14 of the paper

@@
 \seclabel{algorithm}
-The Dex-Net 1.0 algorithm (see pseudocode below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
-We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior belief distribution for each grasp using the Dex-Net database $\mD$.
-Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from the uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
-Finally, we rank the grasps in $\Gamma$ by the maximum lower confidence bound of the belief distribution, a conservative estimate of the $P_F$ of each grasp, and store the ranking in the database.
-We use Thompson sampling to study the scaling effects for a fixed grasp selection method and plan to study other methods based on confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.
+The Dex-Net 1.0 algorithm (see pseudocode below) optimizes the probability of success $P_S$ (Equation~\ref{eq:obj}) for a binary quality metric $S$ such as force closure over a set of candidate grasps for an object $\mO$ using a Bayesian Multi-Armed Bandit (MAB) model~\cite{laskey2015bandits, srinivas10gaussian} with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
+We first generate a set of $K$ candidate grasps, or ``arms", $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling}.
+Next, we predict $P_S$ for each grasp using the $M$ most similar objects from the Dex-Net 1.0 dataset and estimate a Bayesian posterior distribution on our prediction.
+Then, for iterations $t=1,...,T$ we use Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously} to select a grasp $\bg_{t,k} \in \Gamma$ to evaluate, sample the quality $S(\bg_{t,k})$, and update a posterior belief distribution on $P_S$ for each grasp.
+Finally, we rank $\Gamma$ by the $q$-lower confidence bound on $P_S$ for each grasp and store the ranking in the database.
+To illustrate convergence of the algorithm, we use force closure~\cite{zheng2005} as our binary quality metric.
+We plan to study other quality metrics such as success on physical trials~\cite{kroemer2010combining, montesano2012active} and alternate MAB methods based on upper confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.
 
-\subsection{Belief Distribution Model}
+\subsection{Model of Correlated Rewards}
 \seclabel{belief}
-Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
-We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
-Under the model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
-Since $\theta_j$ is unknown, the algorithm maintains a posterior Beta belief distribution on the Bernoulli parameter $\theta_{j}$ that is updated with every new observation of $F$, assigning increasingly high probability to the true $P_F$.
-The Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits} is specified by shape parameters $\alpha > 0$ and $\beta > 0$:
+Let $\mO$ denote the test object to label with the Dex-Net algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
+Let $S_{j} = S(\bg_{j}) \in \{0, 1\}$ be a random binary quality metric evaluated on grasp $\bg_{j} \in \Gamma$.
+For example, $S_j$ might model force closure under uncertainty in object pose, gripper pose, or friction. 
+$S_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_S(\bg_{j})$.
 
-\vspace{-4ex}
+We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model a joint posterior belief distribution over the $\theta_j$ for all grasps in Dex-Net, which enables us to predict $\theta_j$ from prior grasp and object data in Dex-Net 1.0 using a closed-form posterior update.
+The joint distribution models pairwise correlations of $P_S$ between grasp-object pairs $\mP = (\bg, \mO)$ measured using a normalized kernel function $k(\mP_i, \mP_j)$.
+%Such correlations may occur between grasps contacting an object at similar locations.
+The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
+
+We measure similarity using a set of feature maps $\phi_m \in \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
+The first feature map $\phi_{1}(\mP) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the approach axis, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
+To capture local surface geometry, the second feature map $\phi_{2}(\mP) = \eta(\bg, \mO)$, the differential depthmap described in \secref{grasp-similarity}.
+To capture global shape information, our third feature map $\phi_{3}(\mP) = \psi(\mO)$, where $\psi$ is our object similarity map described in \secref{object-similarity}.
+Given the feature maps, we use the squared exponential kernel 
 \begin{align*}
-	\betadist(\alpha, \beta) = Z(\alpha, \beta) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
+	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mP_p) - \phi_m(\mP_q)\|_{C_m}^2 \right).
 \end{align*}
-\noindent where $Z(\alpha, \beta)$ is a normalization constant.
+\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^{-1} \by$.
+The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_S$ under the CCBP on a set of training data.
+
+%We maintain a posterior C belief distribution~\cite{hoffman2013exploiting, laskey2015bandits} on $\theta_{j}$ based on samples of $S_j$. 
+% TODO: why introduce this, put CCBP model here
+
+%The algorithm approximately optimizes Equation~\ref{eq:obj} following the Bayesian MAB model~\cite{oberlin2015autonomously, srinivas10gaussian} by selecting a grasp $\bg_{k,t}$ on iteration $t$ from our set of ``arms" $\Gamma$ using Thompson Sampling~\cite{laskey2015bandits}, observing $S(\bg_{k,t})$, and updating a Bayesian posterior on $P_S(\bg_{k,t})$.
+
+%The Beta distribution $\betadist(\alpha, \beta) = Z(\alpha, \beta) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}$, where $\alpha > 0$ and $\beta > 0$ are shape parameters and $Z(\alpha, \beta)$ is a normalization constant.
+%One benefit of $\betadist$ is the closed-form updates to $\alpha$ and $\beta$ upon observing a quality evaluation $S_{j,t}$:
+%TODO: closed form updates
 
@@
 \seclabel{ccbps}
-We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net.
-CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
-Two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp wrench space metrics~\cite{pokorny2013c}.
-
-A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
-The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
-
-We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
-The first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
-To capture local surface geometry, the second feature map $\phi_{2}(\mY) = \eta(\bg, \mO)$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
-To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similarity map described in \secref{object-similarity}.
-Given the feature maps, we use the squared exponential kernel 
-\begin{align*}
-	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
-\end{align*}
-\noindent where $C_m \in \bR^{d_m \times d_m}$ is the inverse bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^T C_m \by$.
-The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.
-
-We form a prior belief distribution for each candidate grasp in $\Gamma$ based on its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
+Before evaluating any grasps in $\Gamma$, the Dex-Net 1.0 algorithm predicts $\theta_j$ for each candidate grasp $\bg_j$ based on its kernel similarity to all grasps and objects from the Dex-Net 1.0 dataset $\mD$.
+In particular, we estimate a Bayesian posterior density $p(\theta_j)$ by treating $\mD$ as prior observations and using the closed form posterior update for CCBPs~\cite{goetschalckx2011continuous}:
 %\vspace{-2ex}
 \begin{align}
-	%p \left(\theta_{j} | \mD \right) &= \betadist\left( \alpha_{j,0}, \beta_{j,0} \right) \notag \\
-	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g} k(\mY_{j}, \mY_{i, k}) S_{i,k} \label{eq:alpha-prior} \\
-	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g}  k(\mY_{j}, \mY_{i,k}) (N_s - S_{i,k}) \label{eq:beta-prior}
+ 	p(\theta_j \mid \alpha_{j,0}, \beta_{j,0} ) &\propto \theta_j^{\alpha_{j,0}-1} (1 - \theta_j)^{\beta_{j,0}-1} \\
+	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{| \mD |} \sum \limits_{k=1}^{K} k(\mP_{j}, \mP_{i, k}) Z_{i,k} \label{eq:alpha-prior} \\
+	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{| \mD |} \sum \limits_{k=1}^{K}  k(\mP_{j}, \mP_{i,k}) (N - Z_{i,k}) \label{eq:beta-prior}
 \end{align}
-\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled to evaluate $P_F$.
-In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.
-Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:
+\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits}, $N$ is the number of times each grasp $\bg_{i,k} \in \mD$ was sampled to estimate $\theta_i$, and $Z_{i,k}$ is the number of observed successes for $\bg_{i,k}$.
+Intuitively, the prior dataset contributes fractional observations of successes and failures for the grasp candidates $\Gamma$ proportional to the kernel similarity.
+We estimate the above sums using the $M$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.
+
+\subsection{Grasp Selection Policy}
+On iteration $t$ we select the next grasp to sample $\bg_j \in \Gamma$ using Thompson Sampling.
+In Thompson Sampling we draw a sample $\hat{\theta_{\ell}} \sim p(\theta_{\ell} \mid \alpha_{\ell,t}, \beta_{\ell,t} )$ for each grasp $\bg_{\ell} \in \Gamma$, then choose the grasp $\bg_j$ with the highest $\hat{\theta_j}$~\cite{laskey2015bandits}.
+After observing $S_{j}$, we update our belief for all grasps $\bg_{\ell} \in \Gamma$ by updating a running count of the fractional successes and failures~\cite{goetschalckx2011continuous}:
 
@@
 \begin{align}
-	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
-	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}.
+	\alpha_{\ell,t} &= \alpha_{\ell,t-1} + k(\mP_{\ell}, \mP_{j}) S_{j} \label{eq:alpha} \\
+	\beta_{\ell,t} &= \beta_{\ell,t-1} + k(\mP_{\ell}, \mP_{j}) (1 - S_{j})\label{eq:beta}.
 \end{align}
@@
     \SetAlgoLined
-    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Features maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
+    {\bf Input:} Object $\mO$, Number of Candidate Grasps $K$, Number of Nearest Neighbors $M$, Dex-Net 1.0 Dataset $\mD$, Feature maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $q$, Quality Metric $S$ \\
     \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}
@@
     \tcp{Generate candidate grasps and priors}
-	$\Gamma$ = AntipodalGraspSample($\mO, N_g$) \;
+	$\Gamma$ = AntipodalGraspSample($\mO, K$) \;
 	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
@@
 		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
-		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD, N_n, \psi$)\; 
+		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD, M, \psi$)\; 
 		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
@@
 		$j = $ ThompsonSample($\mA_{t-1}, \mB_{t-1}$)\;
-		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
-		$F_{j} = $ EvaluateForceClosure($\bg_j, \mO, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
+		$S_{j} = $ SampleQuality($\bg_j, \mO$)\;
 		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
-		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, F_j, \Gamma$)\; 
-		$\bg_{t}^* = $MaxLowerConfidence($\mA_{t}, \mB_{t}, p$)\;
+		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, S_j, \Gamma$)\; 
+		$\bg_{t}^* = $MaxLowerConfidence($q, \mA_{t}, \mB_{t}$)\;
 	}

### 2016-02-05 ICRA2016/bandits_docs/includes/conclusion.tex
Made first round of ICRA revisions, v14 of the paper

--- 2015-09-16 ICRA2016/bandits_docs/includes/conclusion.tex
@@
 \seclabel{conclusion}
-We presented Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning.
+We presented Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning with binary grasp quality metrics.
 The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models and Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects.
-In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
+In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by approximately three orders of magnitude.
 Experiments suggest that prior data can speed robust grasp planning by a factor of 2 and that average grasp quality increases with the number of similar objects in the dataset.
-We reported on sensitivity to varying similarity metrics and pose and friction uncertainty levels.
 
-In future work, we will develop metrics to pre-compute grasps that adequately "cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
-We will also explore how Deep Learning~\cite{krizhevsky2012imagenet} can be used in other parts of a grasp planning pipeline, for example to recognize object pose and shape from images~\cite{aubry2015understanding}, to learn grasp and object features robust to shape variation using prior evaluations from bandit algorithms, and perhaps even to determine motor torques based on images and precomputed grasps~\cite{levine2015end}.
+In future work, we will develop metrics and algorithms for pre-computing a set of grasps that adequately ``cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
+We also plan to evaluate the Dex-Net 1.0 algorithm in physical experiments and study convergence rates when using various analytic (e.g.
+force closure) and simulation-based grasp quality labels from Dex-Net 1.0 to pre-predict physical grasp successes.
+We will also explore Deep Learning~\cite{krizhevsky2012imagenet} to estimate grasp quality from surface depthmaps and rendered object images for further accelerating convergence.
 We also hope to release subsets of Dex-Net 1.0 with an open-source API to explore robust grasping as a service (RGaaS).

### 2016-02-05 ICRA2016/bandits_docs/includes/dataset.tex
Made first round of ICRA revisions, v14 of the paper

@@
 Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and their $P_F$.
-We generate $N_g$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
-Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS$ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
-To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$.
-Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute $\bc_2 = \bc_1 + (w - t_2^*) \bv$ and $\bx = 0.5 (\bc_1 + \bc_2)$, where $t_2^*$ is defined as in \secref{contact}.
-This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
-We add $\bg_{i,k}$ to the candidate set if the contacts are antipodal~\cite{mahler2015gp}, or $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.
-
-We evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
-The dataset of $N_o$ objects and $N_g$ candidate grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.
+We generate $K$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
+To sample a single grasp, we generate a contact point $\bc_1$ by sampling uniformly from the object surface $\mS$, sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone, and find an antipodal contact $\bc_2$ on the line $\bc_1 + t\bv$ where $t \geq 0$.
+We add the grasp $\bg_{i,k} = (0.5(\bc_1 + \bc_2), \bv)$ to the candidate set if the contacts are antipodal~\cite{mahler2015gp}.
+We evaluated $P_F(\bg_{i,k})$ using Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} by sampling the object pose, gripper pose, and friction random variables $N=500$ times and recording $Z_{i,k}$, the number of samples for which $\bg_{i,k}$ achieved force closure ($F=1$).
 
@@
 
-\subsection{Grasp Differential Heightmap Features}
+\subsection{Grasp Differential Depthmap Features}
 \seclabel{grasp-similarity}
-To measure grasp similarity, we embed each grasp $\bg = (\bx ,\bv)$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
-Let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
-%Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
-The heightmap $\bh_{i}$ at contact $\bc_i$ maps points $\bp \in \bR^3$ on the tangent plane $\bv^T(\bp - \bc_1) = 0$ to the distance to the surface along $\bv$.
-To compute the value at pixel $u,v$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
-\begin{align*}
-	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + (-1)^{i} t \bv \right) = 0
-\end{align*}
-\noindent where $f$ is the SDF of object $\mO$. 
-We make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{salti2014shot}.
+To measure grasp similarity, we embed each grasp $\bg = (\bx ,\bv)$ on object $\mO$ in Dex-Net in a feature space based on a 2D map of the  local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
+We generate a depthmap $\bd_{i}$ for contact $\bc_i$ by orthogonally projecting the local object surface onto an $m \times m$ grid centered at $\bc_i$ and oriented along the line to the object center of mass, $\ba_i = \bz - \bc_i$.
+Since $F$ only depends on $\bc_i$ and its surface normal, rotations of $\bd_i$ about $\ba_i$ correspond to grasps of the equivalent quality.
+We therefore make each $\bd_i$ rotation-invariant by orienting its axes along the eigenvectors of a weighted covariance matrix of the 3D surface points that generate $\bd_i$ as described in~\cite{salti2014shot}.
 \figref{local-feature-model} illustrates local surface patches extracted by this procedure.
-Since force closure depends on object surface normals at contacts~\cite{pokorny2013c}, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
-The feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.
+We finally take the $x$- and $y$-image gradients of $\bd_i$ to form differential depthmaps $\nabla_x \bd_{i}$ and $\nabla_y \bd_{i}$, motivated by the dependence of $F$ on surface normals~\cite{pokorny2013c},
+The feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\nabla_x \bd_{1}, \nabla_y \bd_{1}, \nabla_x \bd_{2}, \nabla_x \bd_{2})$.
 
@@
 \includegraphics[scale=0.30]{figures/illustrations/local_feature_model.eps}
-\caption{Illustration of three local surface heightmaps extracted on a teapot.
-Each heightmap is ``rendered" along the grasp axis $\bv_i$ at contact $\bc_i$ and oriented by the directions of maximum variation in the heightmap.
-We use gradients of the heightmaps for similiarity between grasps in Dex-Net.}
+\caption{Illustration of three local surface depthmaps extracted on a teapot.
+Each depthmap is ``rendered" along the grasp axis $\bv_i$ at contact $\bc_i$ and oriented by the directions of maximum variation in the depthmap.
+We use gradients of the depthmaps for similiarity between grasps in Dex-Net.}
 \figlabel{local-feature-model}
@@
 Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
-Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4,096 dimensions to 100 dimensions.
-This yields the representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
+Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4,096 dimensions to a 100 dimensional feature vector $\psi(\mO)$.
 
@@
 For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
-In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison}, which has 171 unique categories, for 500,000 iterations of SGD.
+In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models sampled from the SHREC 2014~\cite{li2015comparison} portion of Dex-Net, which has 171 unique categories, for 500,000 iterations of SGD.
 %The final PCA step captured approximately 85\% of the variance of the vectors.

### 2016-02-05 ICRA2016/bandits_docs/includes/experiments.tex
Made first round of ICRA revisions, v14 of the paper

@@
 
-We evaluate the convergence rate of the Dex-Net 1.0 algorithm for varying sizes of prior data used from Dex-Net and explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
+We evaluate the convergence rate of the Dex-Net 1.0 algorithm using force closure as our binary quality metric for varying sizes of prior data used from Dex-Net, and we explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
 We created two training sets of 1,000, and 10,000 objects by uniformly sampling objects from Dex-Net.
 We uniformly sampled a set of 300 validation objects for selecting algorithm hyperparameters and selected a set of 45 test objects from the remaining objects.
-We ran the algorithm with $N_n = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1.0$~\cite{laskey2015bandits}, and a lower confidence bound containing $p=75\%$ of the belief distribution.
+We ran the algorithm with $M = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1$~\cite{laskey2015bandits}, and a lower confidence bound containing $q=75\%$ of the belief distribution.
 We used isotropic Gaussian uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
-For each experiment we compare the Dex-Net algorithm to Thompson sampling without priors (TS) and uniform allocation (UA)~\cite{laskey2015bandits}.
+For each experiment we compare the Dex-Net algorithm to Thompson sampling without priors (TS)~\cite{laskey2015bandits}, a state-of-the-art method for robust grasp planning, and uniform allocation (UA), a widely-used method for robust grasp planning the selects the next grasp to evaluate uniformly at random~\cite{kehoe2012toward, kim2012physically, weisz2012pose}.
 
 The inverse kernel bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
-The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma_d = 1.75$ for the differential heightmap features, and $C_s = 0.001 * I$ for the shape similarity features.
+The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,3e-5, 3e-5)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma_d = 0.33$ for the differential heightmap features, and $C_s = 1e6 * I$ for the shape similarity features.
 
-To scale the experiments, we developed a Cloud-based system on top of Google Cloud Platform.
-We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
-The system launched up to 1,500 GCE virtual instances at once for experiments, reducing the runtime by three orders of magnitude.
+To scale experiments, we developed a Cloud-based system on top of Google Cloud Platform.
+We used Google Compute Engine (GCE) to construct the Dex-Net 1.0 dataset and to distribute subsets of objects to virtual machines for MAB experiments, and we used Google Cloud Storage to store Dex-Net.
+The system launched up to 1,500 GCE virtual instances at once for experiments, reducing the runtime by an estimated three orders of magnitude to approximately 315 seconds per object.
 Each virtual instance ran Ubuntu 12.04 on a single core with 3.75 GB of RAM.
@@
 To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran the Dex-Net 1.0 algorithm on the test objects with priors computed from 1,000 and 10,000 objects from Dex-Net.
-~\figref{avg-reward} shows the normalized $P_F$  (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the test objects over 2,000 iterations.
+~\figref{avg-reward} shows the normalized $P_F$  (the ratio of the $P_F$ for the best grasp predicted by the algorithm on iteration $t$ to the highest $P_F$ of the candidate grasps) versus iteration averaged over 25 trials for each of the test objects over 2,000 iterations.
 The average runtime per iteration was 16 ms for UA, 17 ms for TS, and 22 ms for Dex-Net 1.0.
@@
 Furthermore, the 10,000 object curve does not fall below approximately 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
+This speedup is promising for binary success metrics that are expensive to  evaluate, such as human labels or physical grasping trials.
 
@@
 \centering
-\includegraphics[scale=0.41]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
+\includegraphics[scale=0.39]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
 \caption{Failure object for the Dex-Net 1.0 algorithm.
@@
 (Top-left) Using a higher inverse bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
-(Top-right) A lower inverse bandwith decreases the convergence rate, but on average the Dex-Net Algorithm still selects a grasp within approximately 85\% of the grasp with highest $P_F$ for all iterations.
+(Top-right) A lower inverse bandwith decreases the convergence rate, but on average the Dex-Net algorithm still selects a grasp within approximately 85\% of the grasp with highest $P_F$ for all iterations.
 (Bottom-left) Lower uncertainty increases the quality for all methods, (bottom-right) higher uncertainty decreases the quality for all methods, and the Dex-Net algorithm with 10,000 prior objects still converges approximately 2$\times$ faster than Thompson sampling without priors.

### 2016-02-05 ICRA2016/bandits_docs/includes/introduction.tex
Made first round of ICRA revisions, v14 of the paper

@@
 Potential advantages to using the Cloud include Big Data: access to updated libraries of images, maps, and object/product data; and Parallel Computation: access to parallel grid computing for statistical analysis, machine learning, and planning~\cite{kehoe2015survey}.
-These benefits have recently been demonstrated in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
+These benefits have recently been demonstrated in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of previous research.
 This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, and environment configurations~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.
@@
 \includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
-\caption{Normalized grasp quality versus iteration averaged over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle.
-We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation.
+\caption{Average normalized grasp quality versus iteration for 25 trials for the Dex-Net1.0 algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle.
+We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors~\cite{laskey2015bandits} and uniform allocation~\cite{kehoe2012toward, weisz2012pose}.
 (Top) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set.
-(Bottom) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp with 10,000 prior objects.}
+(Bottom) As a result, the Dex-Net 1.0 algorithm quickly converges to the optimal grasp with 10,000 prior objects.}
 \figlabel{avg-reward-spray}
@@
 \end{figure}
-The primary contribution of this paper is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
-The algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.
+
+The primary contribution of this paper is the Dex-Net 1.0 algorithm for quickly finding a grasp with high probability of success for a binary grasp quality metric under uncertainty based on Multi-Armed Bandits (MABs).
+The algorithm speeds up robust grasp planning by learning from a large dataset of prior grasps and 3D object models using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a distribution on the quality of each grasp from prior data.
 
@@
 To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
-We also incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.
+We incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects for predicting robust grasp quality with CCBPs.
 
-We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
-Experiments suggest that using 10,000 prior object models from Dex-Net reduces the number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$ on average over 45 objects.
+We implement the Dex-Net 1.0 algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
+Experiments suggest that using 10,000 prior object models from Dex-Net reduces the number of samples needed to plan parallel-jaw grasps by up to 2$\times$ on average over 45 objects using the probability of force closure as a success metric.
 %\TODO{Update with final results}

### 2016-02-05 ICRA2016/bandits_docs/includes/problem_statement.tex
Made first round of ICRA revisions, v14 of the paper

@@
 
-We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability of force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
+We consider the problem of planning a grasp that maximizes an expected binary quality metric, such as the probability of force closure ($P_F$), for a given 3D object model and parallel-jaw grippers under uncertainty in object pose, gripper pose, and friction coefficient in as few samples as possible.
+%We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability of force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
 We assume the nominal object shape is given as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within.
@@
 %Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
-We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$, and specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
-Let $\mG = \{ (\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
-We denote by $\mM = \mG \times \mH$ the Grasp Moduli Space of all parallel-jaw grasps and objects~\cite{pokorny2013grasp}.
+We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$.
+We specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
 
@@
 
+\subsection{Objective}
+Our objective is to find grasp $\bg^*$ that maximizes the probability of success $P_S(\bg))$ for a binary grasp quality metric $S(\bg) \in \{0, 1\}$ such as force closure~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to uncertainty in the state of the object, environment, or robot.
+Since sampling in high-dimensional spaces can be computationally expensive, we attempt to solve for $\bg^*$ in as few samples $T$ as possible by maximizing over the sum of $P_S(\bg_t)$ for grasps sampled at times $t=1, ..., T$~\cite{laskey2015bandits, srinivas10gaussian}:
+%\vspace{-2ex}
+\begin{align*}
+	\underset{\bg_1, .., \bg_T \in \mG}{\text{maximum }} {\textstyle \sum_{t=1}^T \nolimits } P_S(\bg_t). \label{eq:obj}
+\end{align*}
+
+Since maximizing over a high-dimensional continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating and ranking a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ using Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
+In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.
+
+\subsection{Quality Metric}
+\seclabel{quality}
+In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as the quality metric.
+$P_F$ is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data on convergence of Equation~\ref{eq:obj}, and has shown some promise in physical experiments~\cite{kim2012physically, weisz2012pose}.
+
+Let $F \in \{0, 1\}$ denote the occurrence of force closure.
+For a grasp $\bg$ on object $\mO$ under uncertainty in object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$ the probability of force closure $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$,
+To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute a set of possible contact wrenches $\mW$ using a soft finger contact model~\cite{zheng2005}.
+Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.
+
 \subsection{Sources of Uncertainty}
 \seclabel{uncertainty}
-We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively. 
-We denote by $\mN(\mu,\Sigma)$ a Gaussian distribution with mean $\mu$ and variance $\Sigma$.
-Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
+For $P_F$ evaluation we assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification of material properties.
+Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be the mean object pose.
 We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$~\cite{barfoot2014associating}.
@@
 \seclabel{contact}
-Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface as shown in \figref{grasp-model}.
-Each contact $\bc_i = \bx + (-1)^{i} (w / 2 - t_i^*) \bv$ where~\cite{mahler2015gp}:
-%\vspace{-1ex}
-\begin{align*}
-	t_i^* &= \myargmin{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (w / 2 - t) \bv\right) = 0.
-\end{align*}
-\noindent Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
-To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
-Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.
-Under the soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
-Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under the model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.
-
-\subsection{Quality Metric}
-\seclabel{quality}
-In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as the quality metric.
-$P_F$ has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.
-
-Let $F \in \{0, 1\}$ denote the occurrence of force closure.
-For a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
-To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
-Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.
-
-\subsection{Objective}
-We are interested in finding a grasp $\bg^*$ that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
-To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
-Since the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
-In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.
+Given a grasp $\bg$ on object surface $f$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ denote the 3D contact location between the $i$-th jaw and surface as shown in \figref{grasp-model}.
+Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal and let $\bt_{i,1}, \bt_{i,2} \in \bS^2$ be its tangent vectors.
+To compute the forces that each soft contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
+Thus the set of wrenches that $\bg$ can apply to $\mO$ is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \bbf_{i,j} \times \rho_i) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.

### 2016-02-05 ICRA2016/bandits_docs/includes/related_work.tex
Made first round of ICRA revisions, v14 of the paper

@@
 
-Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric~\cite{pokorny2013c}.
-Usually it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
-Robust grasp planning considers the same problem in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
-One way to treat perturbations is statistical sampling.
-Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasp computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
+Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric, such as the epsilon quality~\cite{pokorny2013c}, correlation with human labels~\cite{balasubramanian2012physical, kappler2015leveraging}, or success in physical trials.
+Often it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
+As computing quality metrics can be time consuming, recent work has explored how a robust grasp computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
 To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt!
 stochastic sampling-based grasp planner.
-%This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
 
-Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
+Robust grasp planning considers optimizing a grasp quality metric in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
+One way to perturbations is statistical sampling.
+Since sampling in high dimensions can be computationally demanding, recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
 Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic wrench space metrics.
@@
 The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
-We estimate $P_F$ using similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.
+In comparison, we estimate $P_F$ given a known 3D object model from similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.
 
@@
 Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
+Pinto et al.~\cite{pinto2016supersizing} used importance sampling over grasp success probabilities predicted from images by a Convolutional Neural Network to actively acquire over 700 hours of labels for successful and unsuccessful grasps.
 Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
-Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
+%Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
 %MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
-In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.
+In this work we extend the MAB model of~\cite{laskey2015bandits} from 2D to 3D and study the scaling effects of using prior data from Dex-Net on the rate of convergence to a grasp with high $P_F$.
 

### 2016-02-05 ICRA2016/bandits_docs/paper.tex
Made first round of ICRA revisions, v14 of the paper

@@
 	\vspace{-2ex}
-	\versionline{11}}
+	\versionline{14}}
 \author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
@@
 This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
-The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
+The authors were supported in part by the U.S.
+National Science Foundation under NRI Award IIS-1227536, by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab; and by the Department of Defense (DoD) through the National Defense Science \& Engineering Graduate Fellowship (NDSEG) Program.
 We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.

### 2016-08-04 ICRA2017/includes/related_work.tex
Added wrench resistance paper

\section{Related work}
\seclabel{related-work}

In practice a robot may only need to resist a set of task-specific wrenches on an object, such as gravity for lifting, rather than attempting to resist all possible wrenches, as has been observed for human grasps~\cite{cutkosky1985grasping, feix2016grasp}.
Li and Sastry~\cite{li1988task} modeled task-specific wrenches with an ellipsoid and proposed a grasp metric based on the largest radius of the task ellipsoid such that the grasp can resist any wrench in the task ellipsoid with unit-magnitude finger forces.
However, not all tasks will have wrench distributions well-modeled by an ellipsoid, and furthermore the ratios of expected forces and torques needed to compute a task ellipsoid may be unknown.
Thus much past research has modeled the task ellipsoid as a unit ball~\cite{ferrari1992, pokorny2013classical}.
Han et al.~\cite{han2000grasp} showed that the question of whether or not a multifinger hand can exert a given force on an object can be reduced to a linear matrix inequality problem. 
Haschke et al.~\cite{haschke2005task} defined a task-specific grasp metric that can be computed by convex optimization when the task wrenches can be described as a cone or a polytope.
Kruger and van der Stappen~\cite{kruger2011partial} described two grasp metrics that measure the sum and maximum of finger forces required to exert a given wrench on an object, and later extended the notion to local force closure grasps~\cite{kruger2012local}, which can resist wrenches in a neighborhood if a desired target wrench.
....
Recent research has focused on data-driven prediction the probability of grasp success for a specific task from features describing the grasp and object, for example using Bayesian Networks~\cite{bekiroglu2013probabilistic}...

### 2016-08-04 ICRA2017/paper.tex
Added wrench resistance paper

--- 2015-09-16 ICRA2016/bandits_docs/paper.tex
@@
 \begin{document}
-\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards
+\title{\LARGE \bf Robust Task Wrench Resistance
 	\vspace{-2ex}
-	\versionline{11}}
-\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
-Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
+	\versionline{0}}
+\author{Jeffrey Mahler$^1$, Jacky Liang$^1$, Ken Goldberg$^1$
 %\vspace{-2ex}
-\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
-%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
-%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
-\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
-\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
+\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, jackyliang, goldberg\}@berkeley.edu}}}% }
 }
@@
 
-%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
-%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
-%\TODO{Trim paper to 8 pages}
 \input{includes/abstract}
-%
+
 \input{includes/introduction}
+
 \input{includes/related_work}
-%
-\input{includes/problem_statement}
-\input{includes/dataset}
-%\input{includes/background}
-\input{includes/algorithm}
-\input{includes/experiments}
-\input{includes/conclusion}
-
-%%\appendix
-%\include{includes/proofs}
 
 \section{Acknowledgments}
-{\small
-This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
-The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
-We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
+{\footnotesize
+This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) ``People and Robots" Initiative: http://robotics.citris-uc.org.
+The authors were supported in part by the U.S.
+National Science Foundation under NRI Award IIS-1227536, by grants from Google, UC Berkeley's Algorithms, Machines, and People Lab; the Knut and Alice Wallenberg Foundation; the NSF-Graduate Research Fellowship; and the Department of Defense (DoD) through the National Defense Science \& Engineering Graduate Fellowship (NDSEG) Program.
+We thank our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Animesh Garg, Kevin Jamieson, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, and Nan Tian.
 }
